### 2020-04-01 chemev/MWbimodality/synopsis1/synopsis.tex
plots: synopsis progress

\documentclass[12pt]{report} 
\usepackage{hyperref} 
\usepackage{amsmath} 
\usepackage{amssymb}
\usepackage{caption} 
\usepackage{float} 
\usepackage{adjustbox} 
\usepackage[margin = 1in]{geometry} 
\pagestyle{myheadings} 
\hypersetup{
	colorlinks 		= true, 
	urlcolor 		= red, 
	linkcolor		= blue, 
	citecolor 		= blue 
}

\begin{document} 
\noindent 
\textbf{Synopsis of Multizone Simulation Results} 
\par\noindent 
\today 
\par\null\par

\begin{center} 
\hypertarget{sec:params}{\textbf{Simulation Parameters}} 
\end{center} 
\par\noindent 
These simulations treat the disk of a Milky Way-like galaxy as a series of 
annular zones with width $\Delta r$ = 250 pc from $R_\text{gal}$ = 0 to 30 kpc. 
These simulations start at time $t$ = 0 with an exponential surface density 
gas disk, which is assumed to be primordial gas:

\begin{equation} 
\label{eq:sigma_gas} 
\Sigma_g \propto e^{-r/r_\text{s}} 
\end{equation} 
This gas disk is static throughout the simulation; here I'm running VICE in 
\texttt{gas} mode, meaning the mass of the interstellar medium (ISM) is what 
is specified, and I've specified it to be a constant with time for each zone. 
There are inflows and outflows, but with a constant gas mass in each zone, 
VICE is simply solving for the necessary infall rate to balance the mass lost 
to outflows and star formation. Gas is also not migrating between zones in 
this model; there are no radial gas flows. 
\par 
This is running with an implementation of the Kennicutt-Schmidt relation: 
$\dot{M}_\star \propto \Sigma_g^N$, where $N = 1.4 \pm 0.15$ (Kennicutt 1998, 
ApJ, 498, 541). Due to the definition of the star formation efficiency (SFE) 
timescale $\tau_\star \equiv M_g/\dot{M}_\star$: 
\begin{equation}\begin{aligned} 
\dot{M}_\star &\propto \Sigma_g^N \\ 
\implies M_g\tau_\star^{-1} &\propto \Sigma_g^N \\ 
\implies \tau_\star &\propto \Sigma_g^{1 - N} 
\end{aligned}\end{equation} 
With the gas supply given by equation~\ref{eq:sigma_gas}, this mandates a 
scaling of $\tau_\star$ with radius of: 
\begin{equation}
\tau_\star \propto e^{(N - 1)r/r_\text{s}} 
\end{equation}
where $r_\text{s}$ is the scale radius of the gas disk. Beyond 15.5 kpc, I 
have artifically set $\tau_\star = 0$ to shut off star formation and all 
entrainment fractions $\epsilon = 0$. The latter ensures that newly 
synthesized material from stars in a region where star formation is shut off 
is added directly to the outflow as opposed to the ISM. Here I'm showing the 
$\tau_\star(0\text{ kpc})$ = 0.2 Gyr models; even though this model has 
star formation that is likely too vigorous to be realistic, it does the best 
yet at reproducing the observational trends. 
\par 
Prior to the start of VICE's multizone simulation, I assign each star particle 
that will form an ``analog'' from the UW hydro simulation file that Jon Bird 
sent us. To do so, I first set up 40 bins between 0 and 12.8 Gyr (320 Myr width 
time bins), and allow VICE's star particles to find an analog in the hydro 
sim that formed in that time bin and in the same radial bin to the annular 
zone it was born in. If a star does not find an analog here, it is allowed 
to find on in a neighboring zone. If it does not find one in a neighboring 
zone, it stays in the zone it was born in. This ensures that the majority of 
stars in the VICE simulation are radially migrating based on stars that formed 
within approximately one dynamical time (or slightly larger) and at a similar 
radius. 
\par 
\textbf{Only bother reading this paragraph if you want some technical 
justification as to why we don't need to worry about the stars that don't 
find an analog}. 
In the model plotted in this synopsis, VICE formed 317,936 stars. 6743 of 
those stars did not find an analog, 4360 of which formed in the 
$R_\text{gal}$ = 0-250 pc zone. Since we are interested in the disk and not 
the very central region of the galaxy, it's safe to ignore these stars. This 
leaves 2383 star particles which formed in the disk that did not 
find an analog from the hydro simulation - only~$\sim$0.75\% of the star 
particles by number, and~$\sim$1.7\% of the star particles by mass. These 
star particles have a mean (median) formation radius of 2.68 (2.25) kpc with a 
standard deviation of 2.48 kpc, and a mean (median) formation time of 
1.52 (0.18) Gyr with a standard deviation of 3.89 Gyr. Therefore, while these 
``no analog stars'' form somewhat preferentially at early times and small 
radii, they're distributions in $T_\text{form}$ and $R_\text{form}$ are 
sufficiently wide and their contribution to the mass budget sufficiently small 
that they're negligible. 
\par 
This model adopts the following scaling of the mass loading factor 
$\eta = \dot{M}_\text{out}/\dot{M}_\star$ with galactocentric radius: 
\begin{equation} 
\label{eq:eta_r} 
\eta(r) = \frac{y_\text{O}^\text{CC}}{Z_{\text{O},\odot}} 
10^{(0.06\text{ kpc}^{-1})(R_\text{gal} - 4\text{ kpc}) - 0.3} - 0.6 
\end{equation}
This is derived by taking a by-eye linear fit to the mode of the stellar 
[Mg/H] distribution as a function of radius for $0 \leq |z| \leq$ 0.5 kpc 
stars from figure 23 of Weinberg et al. (2018), ApJ, 874, 102 and assuming 
that this corresponds to the equilibrium Mg abundance. This scaling of $\eta$ 
corresponds to $\eta$ = 0.16 at $R_\text{gal}$ = 0 and 1.68 at $R_\text{gal}$ 
= 8 kpc under our yields. This functional form corresponds to the blue line 
in the panel below, while the red line is the linear scaling that we employed 
in some of our first models.

\begin{figure*}[!h] 
\centering 
\includegraphics[scale = 0.5]{../plots/eta_r.pdf} 
\caption{In blue is the scaling of $\eta$ with galactocentric radius given by 
equation~\ref{eq:eta_r}.}
\end{figure*}

\begin{figure*}[!h] 
\centering 
\includegraphics[scale = 0.3]{../plots/rgal_birth/hayden2015plot/moddisk_vigorousSF.png} 
\caption{Each panel corresponds to a bin in galactocentric radius 
$R_\text{gal}$ (denoted at the top of each column) and height above/below the 
plane $\left|z\right|$ (denoted in the middle panel of each column). Points 
are color-coded according to the $R_\text{gal}$ at which each star was born, 
and their size scales linearly with their mass. There is a bimodality most 
apparent in the $R_\text{gal}$ = 5 - 7 kpc bin, in agreement with 
observations.} 
\end{figure*}

\begin{figure*}[!h] 
\centering 
\includegraphics[scale = 0.3]{../plots/age/hayden2015plot/moddisk_vigorousSF.png}
\caption{
Same as above, but points are color-coded by age in Gyr. Of particular 
interest is the population of young (age $\lesssim$ 1 Gyr) stars with mild 
$\alpha$-enhancements seen in many of these panels; this suggests that a 
population of young $\alpha$-rich stars is a natural consequence of radial 
migration. 
} 
\end{figure*}

\begin{figure*}[!h] 
\centering 
\includegraphics[scale = 0.3]{../plots/age-metallicity/moddisk_vigorousSF.png} 
\caption{
The age-metallicity relation as predicted for the solar annulus (7 kpc $\leq$ 
$R_\text{gal} \leq$ 9 kpc). Points are color-coded according to their 
galactocentric radius of birth, and their size scales linearly with their 
mass. Black stars are plotted at the mass-weighted median age of stars in 
0.1-dex width bins in [O/H]. The model predicts an old, metal rich population 
to originate from the inner regions of the disk, and the young $\alpha$-rich 
population to originate from the outer regions of the disk. 
}
\end{figure*}

\begin{figure*}[!h] 
\centering 
\includegraphics[scale = 0.5]{../plots/gradients/stellar_surface_density/moddisk_vigorousSF.png} 
\caption{
The stellar mass surface density defined by 
$\Sigma_\star \equiv M_\star / (\pi(r_\text{out}^2 - r_\text{in}^2))$ as a 
function of galactocentric radius, normalized to an arbitrary constant. While 
this model was ran with a scale radius of the gas disk of $R_\text{s,g}$ = 3 
kpc, the stellar disk has a scale radius of $R_{\text{s,}\star}$ = 2 kpc, and 
is well-described by the exponential. 
}
\end{figure*}

\begin{figure*}[!h] 
\centering 
\includegraphics[scale = 0.4]{../plots/gradients/metallicity/moddisk_vigorousSF.pdf} 
\caption{
The gradients in [O/H] (left; red), [Fe/H] (left; blue), and [O/Fe] (right). 
Stars represent the mode of the stellar metallicity distribution in their zone, 
shaded regions represent the 16th and 84th percentiles thereof, and the lines 
denote the metallicity of the gas in that zone at the final timestep. The 
drop in overall abundance [X/H] and the increase in [O/Fe] at $R_\text{gal}$ = 
15.5 kpc is due to the artificial shut-off of star formation at radii larger 
than this and the entrainment fractions to zero (all nucleosynthetic products 
go directly to the outflow at these radii). 
}
\end{figure*}

\begin{figure*}[!h] 
\centering 
\includegraphics[scale = 0.7]{../plots/Ia_rate/moddisk_vigorousSF.png} 
\caption{
Proxies for the SN Ia rate as a function of cosmic time at 
$R_\text{gal} \approx$ 5 kpc (blue), 10 kpc (green), and 15 kpc (red) compared 
to what is expected in a one-zone model with the same parameters (dashed lines 
of the same colors). All three rates show low-amplitude white noise on top of 
higher-amplitude variability on Gyr timescales which is not sinusoidal, 
introducing scatter in the relationship between age and [Fe/H], and by 
extension [O/Fe]. In the $R_\text{gal}$ = 15 kpc bin, the fractional amplitude 
of the variability is much larger, and the rate overall is considerably lower 
than the corresponding one-zone model prediction for the majority of the 
simulation. This suggests that the migration of star particles out of this 
zone is not balanced by the migration of star particles from other zones, when 
weighted by the SN Ia rate. Stars migrate away from these radii on short 
timescales, while stars migrate toward these radii on long timescales, leaving 
the outskirts of the disk Fe-poor. This suggests that the young $\alpha$-rich 
stars seen in our simulations are not necessarily $\alpha$-rich but Fe-poor. 
}
\end{figure*}

\end{document}

### 2020-04-01 chemev/MWbimodality/plots/Ia_rate/mpl.vs_time.py

@@ -30,7 +30,7 @@ def setup_axis():
 
 
 def get_proxies(zone): 
-	mir = vice.mirror(zone) 
+	mir = vice.singlezone.from_output(zone) 
 	proxies = (len(zone.history["time"]) - 1) * [0.] 
 	for i in range(len(proxies)): 
 		if zone.history["time"][i] > mir.delay: 
@@ -39,16 +39,12 @@ def get_proxies(zone):
 			) / (
 				zone.history["time"][i + 1] - zone.history["time"][i] 
 			) 
-			if i == 8: print(proxies[i]) 
 			proxies[i] -= (
 				vice.yields.ccsne.settings["fe"] * zone.history["sfr"][i] * 1e9 
 			) 
-			if i == 8: print(proxies[i]) 
 			proxies[i] += zone.history["z(fe)"][i] * zone.history["sfr"][i] * (
 				1 + mir.eta - 0.4) * 1e9 
-			if i == 8: print(proxies[i]) 
 			proxies[i] /= zone.history["mass(fe)"][i] 
-			if i == 8: print(proxies[i]) 
 			if proxies[i] < 0: proxies[i] = 0
 		else: pass 
 	return proxies 
@@ -61,18 +57,16 @@ def plot_actual(ax, zone, color, norm, label):
 		"c": 		plots.mpltoolkit.named_colors()[color] 
 	}
 	if label is not None: kwargs["label"] = label 
-	print(proxies[:15]) 
 	ax.plot(zone.history["time"][:-1], proxies, **kwargs) 
 
 
 def plot_comparison(ax, zone, color): 
-	sz = vice.mirror(zone) 
+	sz = vice.singlezone.from_output(zone) 
 	sz.func = lambda t: zone.history["mgas"][0] 
 	sz.name = "comparison" 
 	comp = sz.run(np.linspace(0, 14, 1401), overwrite = True, capture = True) 
 	# proxies = [i / comp.history["mass(fe)"][-1] for i in get_proxies(comp)] 
 	proxies = get_proxies(comp) 
-	print(proxies[:15]) 
 	ax.plot(comp.history["time"][:-1], proxies, 
 		c = plots.mpltoolkit.named_colors()[color], linestyle = '--') 
 	return comp.history["mass(fe)"][-1] 

### 2020-04-01 chemev/MWbimodality/plots/age/hayden2015plot/mpl.hayden2015plot.py

@@ -21,8 +21,8 @@ import os
 
 REF_ELEMENT = "Fe" 
 SEC_ELEMENT = "O" 
-XLIM = [-1.7, 0.4] 
-YLIM = [-0.02, 0.52] 
+XLIM = [-1.2, 0.6] 
+YLIM = [-0.05, 0.55] 
 CMAP = "plasma_r" 
 
 
@@ -30,7 +30,7 @@ def setup_axes():
 	""" 
 	Setup the 3x5 matplotlib axes. 
 	""" 
-	fig, axes = plt.subplots(ncols = 5, nrows = 3, figsize = (35, 21)) 
+	fig, axes = plt.subplots(ncols = 5, nrows = 3, figsize = (20, 12)) 
 	for i in range(3): 
 		for j in range(5): 
 			if i != 2: plt.setp(axes[i][j].get_xticklabels(), visible = False) 
@@ -38,12 +38,12 @@ def setup_axes():
 			axes[i][j].set_xlim(XLIM) 
 			axes[i][j].set_ylim(YLIM) 
 			if i == 0: axes[i][j].set_title(
-				r"%g kpc $\leq$ Final $R_\text{gal}\ \leq$ %g kpc" % (
+				r"Final $R_\text{gal}$ = %g - %g kpc" % ( 
 					[3, 5, 7, 9, 11][j], [5, 7, 9, 11, 13][j]), 
 				fontsize = 25) 
 			if j == 2: 
-				axes[i][j].text(-0.5, 0.45, 
-					r"%g kpc $\leq \left|z\right| \leq$ %g kpc" % (
+				axes[i][j].text(-0.8, 0.47, 
+					r"$\left|z\right|$ = %g - %g kpc" % ( 
 						[1, 0.5, 0][i], [2, 1, 0.5][i]), 
 					fontsize = 25) 
 	axes[2][2].set_xlabel("[%s/H]" % (REF_ELEMENT)) 
@@ -69,7 +69,7 @@ def plot_stars(ax, stars, zone_bounds, zbounds):
 	stars = stars.filter("zone_final", "<=", zone_bounds[1]) 
 	stars = stars.filter("abszfinal", ">=", zbounds[0]) 
 	stars = stars.filter("abszfinal", "<=", zbounds[1]) 
-	sizes = [i["mass"] / 1e6 * 4 * (1 - 
+	sizes = [i["mass"] / 1e7 * 4 * (1 - 
[…]

### 2020-04-01 chemev/MWbimodality/plots/gradients/metallicity/mpl.metallicity.py

@@ -28,7 +28,7 @@ def setup_axes():
 		axes[i] = fig.add_subplot(121 + i, facecolor = "white") 
 		axes[i].set_xlabel(r"$R_\text{gal}$ [kpc]") 
 		axes[i].set_xlim([-1, 21]) 
-	axes[0].set_ylim([-0.55, 0.55]) 
+	axes[0].set_ylim([-0.55, 0.65]) 
 	axes[1].set_ylim([-0.1, 0.5]) 
 	axes[0].set_ylabel("[X/H]") 
 	axes[1].set_ylabel("[O/Fe]") 

### 2020-04-01 chemev/MWbimodality/plots/rgal_birth/hayden2015plot/mpl.hayden2015plot.py

@@ -21,8 +21,8 @@ import os
 
 REF_ELEMENT = "Fe" 
 SEC_ELEMENT = "O" 
-XLIM = [-1.2, 0.7] 
-YLIM = [-0.02, 0.52] 
+XLIM = [-1.2, 0.6] 
+YLIM = [-0.05, 0.55] 
 CMAP = "plasma_r" 
 
 
@@ -30,7 +30,7 @@ def setup_axes():
 	""" 
 	Setup the 3x5 matplotlib axes. 
 	""" 
-	fig, axes = plt.subplots(ncols = 5, nrows = 3, figsize = (35, 21)) 
+	fig, axes = plt.subplots(ncols = 5, nrows = 3, figsize = (20, 12)) 
 	for i in range(3): 
 		for j in range(5): 
 			if i != 2: plt.setp(axes[i][j].get_xticklabels(), visible = False) 
@@ -38,12 +38,12 @@ def setup_axes():
 			axes[i][j].set_xlim(XLIM) 
 			axes[i][j].set_ylim(YLIM) 
 			if i == 0: axes[i][j].set_title(
-				r"%g kpc $\leq$ Final $R_\text{gal}\ \leq$ %g kpc" % (
+				r"Final $R_\text{gal}$ = %g - %g kpc" % ( 
 					[3, 5, 7, 9, 11][j], [5, 7, 9, 11, 13][j]), 
 				fontsize = 25) 
 			if j == 2: 
-				axes[i][j].text(-0.5, 0.45, 
-					r"%g kpc $\leq \left|z\right| \leq$ %g kpc" % (
+				axes[i][j].text(-0.8, 0.47, 
+					r"$\left|z\right|$ = %g - %g kpc" % ( 
 						[1, 0.5, 0][i], [2, 1, 0.5][i]), 
 					fontsize = 25) 
 	axes[2][2].set_xlabel("[%s/H]" % (REF_ELEMENT)) 
@@ -70,7 +70,7 @@ def plot_stars(ax, stars, zone_bounds, zbounds):
 	stars = stars.filter("abszfinal", ">=", zbounds[0]) 
 	stars = stars.filter("abszfinal", "<=", zbounds[1]) 
 	colors = [i["zone_origin"] * 0.25 for i in stars] 
-	sizes = [i["mass"] / 1e6 * 4 * (1 - 
+	sizes = [i["mass"] / 1e7 * 4 * (1 - 
[…]

### 2020-04-27 chemev/MWbimodality/synopsis1/synopsis.tex
plots: density map of lintexp models ; synopsis: minor updates

@@
 observations.} 
+\label{fig:rgal_birth:hayden2015plot:moddisk_vigorousSF} 
 \end{figure*}
@@
 } 
+\label{fig:age:hayden2015plot:moddisk_vigorousSF} 
 \end{figure*}
@@
 
+\begin{figure*} 
+\centering 
+\includegraphics[scale = 0.3]{../plots/stellarMDFS/hayden2015plot/moddisk_vigorousSF.png} 
+\caption{
+Probability distribution functions of stars in [O/Fe] in bins of [Fe/H], 
+present-day galactocentric radius $R_\text{gal}$, and present-day height 
+above/below the plane $\left|z\right|$. Rows correspond to bins in 
+$\left|z\right|$ as noted in the middle-right column. Columns correspond to 
+bins in $R_\text{gal}$ as noted at the top of each column. Different colors 
+denote different bins in metallicity as noted by the legend in the right-hand 
+column. There is a bimodality most apparent in the 5-7 kpc and 7-9 kpc bins; 
+the high-$\alpha$ population is most pronounced at low $R_\text{gal}$ and 
+high $\left|z\right|$, and the opposite for the low-$\alpha$ population, 
+in qualitative agreement with observational results. 
+}
+\end{figure*}
+
+\begin{figure*} 
+\centering 
+\includegraphics[scale = 0.3]{../plots/rgal_birth/hayden2015plot/iodisk_reference.png} 
+\caption{
+Same as figure~\ref{fig:rgal_birth:hayden2015plot:moddisk_vigorousSF}, but for 
+an inside-out formation model in which each annulus has an exponential infall 
+history and an initial gas supply of 0. 
+}
+\end{figure*}
+
+\begin{figure*} 
+\centering 
+\includegraphics[scale = 0.3]{../plots/age/hayden2015plot/iodisk_reference.png} 
+\caption{Same as figure~\ref{fig:age:hayden2015plot:moddisk_vigorousSF}, but 
+for an inside-out formation model in which each annulus has an exponential 
+infall history and an initial gas supply of 0. }
+\end{figure*}
+
 \end{document}

### 2020-04-27 chemev/MWbimodality/plots/Ia_rate/mpl.vs_time.py

@@ -18,6 +18,8 @@ import math as m
 import vice 
 import sys 
 import os 
+sys.path.append("../../simulations/") 
+import gas_disks 
 
 
 def setup_axis(): 

### 2020-04-27 chemev/MWbimodality/plots/hayden2015plot/mpl.hayden2015plot.py

@@ -1,0 +1,89 @@
+r""" 
+This script creates a heatmap in grayscale of the stellar number density in 
+the [O/Fe]-[Fe/H] plane 
+
+ARGV 
+----
+1) 		The name of the multizone output 
+2) 		The name of the output image (without extension) 
+""" 
+
+import matplotlib.pyplot as plt 
+import plots 
+plots.mpltoolkit.load_mpl_presets() 
+import numpy as np 
+import vice 
+import sys 
+
+CMAP = "Greys" 
+XLIM = [-1.2, 1.2] 
+YLIM = [-0.3, 0.55] 
+
+
+def setup_axes(): 
+	r""" 
+	Sets up the 3x5 matplotlib axes to plot on 
+	""" 
+	fig, axes = plt.subplots(ncols = 5, nrows = 3, figsize = (20, 12)) 
+	for i in range(3): 
+		for j in range(5): 
+			if i != 2: plt.setp(axes[i][j].get_xticklabels(), visible = False) 
+			if j != 0: plt.setp(axes[i][j].get_yticklabels(), visible = False) 
+			axes[i][j].set_xlim(XLIM) 
+			axes[i][j].set_ylim(YLIM) 
+			if i == 0: axes[i][j].set_title(
+				r"Final $R_\text{gal}$ = %g - %g kpc" % (
+					[3, 5, 7, 9, 11][j], [5, 7, 9, 11, 13][j]), 
+				fontsize = 25) 
+			if j == 2: axes[i][j].text(-1, -0.2, 
+				r"$\left|z\right|$ = %g - %g kpc" % (
+					[1, 0.5, 0][i], [2, 1, 0.5][i]), 
+				fontsize = 25) 
+	axes[2][2].set_xlabel("[Fe/H]") 
+	axes[1][0].set_ylabel("[O/Fe]") 
+	return fig, axes 
+
+
+def plot_density(ax, out, minrgal, maxrgal, minabsz, maxabsz): 
+	r""" 
+	Plot the 2D density of stars 
+
+	ax : The matplotlib axis to plot the heatmap on 
+	out : The VICE multioutput object 
+	minrgal : Minimum galactocentric radius in kpc 
+	maxrgal : Maximum galactocentric radius in kpc 
+	minabsz : Minimum |z| in kpc 
+	maxabsz : Maximum |z| in kpc 
+	""" 
+	stars = out.stars.filter("mass", ">", 0) 
[…]

### 2020-04-27 chemev/MWbimodality/simulations/iodisk.py

@@ -34,7 +34,7 @@ def tau_in(rgal):
 	tau_in : real number 
 		The infall timescale in Gyr. 
 	""" 
-	return 1 + (rgal + 1.e-12) / 1.5 
+	return 4 + (rgal + 1.e-12) / 3.5 
 	# return 6 
 
 
@@ -70,12 +70,12 @@ def lintexp_sfr_norm(r, rs = 3, k = 1000):
 def run_simulation(): 
 	mz = vice.multizone(name = sys.argv[1], n_zones = len(RAD_BINS) - 1, 
 		n_stars = 4, verbose = True, simple = False) 
-	mz.migration.stars = tracers.UWhydro(TIME_BINS, RAD_BINS, 
+	# mz.migration.stars = tracers.UWhydro(TIME_BINS, RAD_BINS, 
+	# 	n_stars = mz.n_stars, 
+	# 	filename = "%s_extra_tracer_data.out" % (mz.name)) 
+	mz.migration.stars = tracers.UWhydro_1event(TIME_BINS, RAD_BINS, 
 		n_stars = mz.n_stars, 
 		filename = "%s_extra_tracer_data.out" % (mz.name)) 
-	# mz.migration.stars = tracers.UWhydro_1event(TIME_BINS, RAD_BINS, 
-	# 	n_stars = mz.n_stars, 
-		# filename = "%s_extra_tracer_data.out" % (mz.name)) 
 	for i in range(mz.n_zones): 
 		# mz.zones[i].mode = "ifr" 
 		mz.zones[i].mode = "sfr" 

### 2021-08-04 chemev/MWbimodality/paper/response/response.tex
migration paper referee response

\documentclass{report} 
\usepackage[margin = 0.6in]{geometry} 
\usepackage{amssymb} 
\usepackage{amsmath}
% \linespread{1.8}

\newcommand{\breakline}{\noindent\rule{\textwidth}{1pt}}

\begin{document} 
Dear editor, 
\par\null\par 
We thank our referee, Dr. J. Ted Mackereth, for his thorough comments on our 
submission. 
We greatly appreciate his insight, and we believe our manuscript 
has improved as a result of his efforts. 
\par
Our responses are below, interleaved with comments from Dr. Mackereth in 
bold. 
Substantial changes to the revised manuscript are marked in red.

\par\null\par 
\breakline 
\par\null\par 
\textbf{
	The paper is well put together, if quite long and detailed! 
	Much of the latter portion of the paper is given over to detailed 
	descriptions of comparisons between the model predictions and the APOGEE 
	data. 
	The authors are refreshingly upfront about places where their model fails 
	to correctly predict observations. 
	However, I felt in general the authors might have more strongly emphasised 
	what new predictions the models provide for the Milky Way's formation and 
	evolution. 
	As an example, more than 50\% of the abstract is a list of agreement rather 
	than any novel predictions! 
	This is subjective, of course, so I am not explicitly asking for changes 
	here.
} 
\par 
Having strived for transparency, we are glad that Dr. Mackereth believes that 
we achieved this goal and that it improves the quality of the paper! 
Although novel predictions are always interesting, we believe that one of the 
most important results from this paper is that some observables can be 
explained by ongoing star formation combined with stellar migration, but that 
simultaneously fitting all of them is extremely challenging. 
None of the models we present are able to achieve this goal despite how well 
one model may agree with a particular observable. 
Largely because we find that different observables from the same dataset favor 
different models, an important lesson to learn from this paper is that we as a 
community need to be careful to compare our models to as many observables in as 
many Galactic regions as possible. 
This was our motivation behind emphasizing the comparison with data.

\par\null\par 
\breakline 
\par\null\par 
\textbf{
	Does the imposed SFH match in any quantitative way that from the 
	simulation? 
	I was concerned that this model imposes some star formation beyond R $>$ 
	13kpc at times as early as 11-12 Gyr ago. 
	While small, I would presume that these annuli try to match at least a few 
	star particles from the simulation at these times. 
	Given the birth radii distribution of the simulations at 8-10Gyr old, then 
	I would expect that the model tags an 'analogue' at a very different radius 
	to the implied birth radius (given the current description of the tagging 
	process). 
	Is this the case? 
	If not, how is this handled? 
	If so, how important is this for the radial migration prescription? 
	Some text describes this, but I felt that the paper would benefit from some 
	more detail here. 
	I would imagine that the dynamics of stars forming at R $<$ 5kpc are very 
	different to those forming at large radii at early times. 
} 
\par 
The imposed SFH is not taken from the simulation. 
Instead, it is intended to resemble a simple assumption that one might take for 
a galaxy like the Milky Way, where ``simple'' for the sake of chemical 
evolution models often means neglecting effects like the radial growth of the 
Galaxy. 
Dr. Mackereth's understanding of the tagging process is accurate; the model 
indeed matches these stellar populations born at large radii and early times 
with star particles from the h277 simulation, but the number of star particles 
in our sample is sufficiently large that this is not a cause for concern. 
For each of the stellar population and star particle pairs in our fiducial 
model, we have recorded the difference in birth radius between the two and 
analyzed the resulting distributions. 
We find that even at large radii (R $\gtrsim$ 10 kpc) and early times (age $>$ 
10 Gyr), the majority of stellar populations are assigned an analogue that 
formed within~$\sim$2 kpc of its birth radius. 
Stellar populations born at, e.g., R = 13 kpc are in general not being tagged 
with analogues that formed as far in as R = 5 kpc, instead finding star 
particles that formed at~$\sim$11 kpc if the search widens that far without 
finding another analogue first. 
We have added a few sentences to this effect to paragraph 4 of~\S~2.2 so 
that uninitiated readers can be assured that our models assign outer rather 
than inner disc star particles to these outer disc stellar populations. 
\par 
This issue is of little importance to the conclusions presented in this paper. 
In our exploratory work, we originally used an algorithm in which stellar 
populations that did not find an analogue within~$R~\pm$~500 pc and~$T~\pm$~500 
Myr simply stayed at their radius of birth. 
These models make similar predictions to the ones presented in the paper, which 
we take as an indication that the fine details of the dynamical history do 
not impact our results. 
In general, the conclusions we discuss are impacted more so by the 
fact~\textit{that} stars are migrating and not so much by~\textit{how} stars 
are migrating. We have also added two sentences to this effect to paragraph 4 
of~\S~2.2.

\par\null\par 
\breakline 
\par\null\par 
\textbf{
	Similarly to above, my reading of the current procedure is that it may 
	imply some biases as to where the analogues are selected. 
	Since the search is conducted in cylindrical coordinates, then surely the 
	search volume will be vastly different dependent on the radii at which it 
	is conducted (since delta R is constant)? 
	i.e at R = 1kpc, a~$\pm$250pc annulus is~$\sim$10 times smaller than one at 
	15kpc. 
	Perhaps this has no effect, but to the uninitiated reader this seemed like 
	it could be a concern.
} 
\par 
It is true that the search annuli increase in size with increasing radius, but 
we do not believe that this has any effect on the model. 
This point is actually closely connected to the previous question; the larger 
search annuli at large~$R$ help ensure that the stellar populations born there 
are able to find an analogue born at a similar radius without having to extend 
the search too far inward. 
A change to our model such that stars stay at their birth radius if they do not 
find an analogue within~$R~\pm$~500 pc and~$T~\pm$~500 Myr makes similar 
predictions (see previous). 
Particularly at large~$R$, this is a substantial change to the dynamics of the 
stellar populations such that the search may as well have not even been 
conducted for some of them, and our conclusions are still unaffected. 
We hope that the aforementioned addition of text to paragraph 4 of~\S~2.2 
helps mitigate this concern. 
There may be interesting regions of parameter space where the model predictions 
are sensitive to the fine details of the dynamical history and decisions like 
this would matter, but in practice we find that the models in the present paper 
are unaffected.

\par\null\par 
\breakline 
\par\null\par 
\textbf{
	Finally, the authors use the $z$ dependence in their comparisons but (as 
	far as I could see) did not mention how this was handled. 
	I assumed that the final $z$ of the simulation particles is adopted, but it 
	would be good to state this somewhere explicitly. 
} 
\par 
We thank Dr. Mackereth for letting us know that this was not made clear enough. 
His assumption was correct; it is indeed taken from the h277 analogue assigned 
to a stellar population. 
To address this, we have modified sentence 5 in paragraph 3 of~\S~2.2 to say 
that the stellar population adopts the present-day midplane distance~$z$ and 
the change in radius~$\Delta R_\text{gal}$ from its analogue. 
This sentence previously stated this only for the change in radius. 
We have also added a table of our model parameters near the end of~\S~2, and 
it is stated there that both~$\Delta R_\text{gal}$ and~$z$ are taken from 
the h277 analogue.

\par\null\par 
\breakline 
\par\null\par 
\textbf{
	I think it would be good to explicitly mention that h277 has~$\sim$the same 
	final scale length as the Milky Way, I had to go digging for that 
	information when I was thinking about the above points.
} 
\par 
We have added this statement near the end of paragraph 3 of~\S~2.2.

\par\null\par 
\breakline 
\par\null\par 
\textbf{
	The 'inside-out' SFH implies that star formation peaked at 10-11 Gyr ago in 
	the very outer disc - is this really a good assumption? 
}
\par 
For reference, we are duplicating equation 10 in section 2.5 here, which 
describes the time-dependence of the SFH in the fiducial model: 
\begin{equation} 
f_\text{IO}(t|R_\text{gal}) = (1 - e^{-t/\tau_\text{rise}})
e^{-t/\tau_\text{sfh}}. 
\end{equation} 
As mentioned in the text, this equation does have a peak 
near~$\tau_\text{rise}$, but in detail the time of the peak increases with 
increasing~$\tau_\text{sfh}$ (i.e. with increasing~$R_\text{gal}$). 
When~$\tau_\text{sfh}$ is as high as~$\sim$30 Gyr, the peak in star formation 
instead occurs~$\sim$7.5 - 8 Gyr ago. 
Whether or not this is accurate for the Milky Way, it at least to some extent 
reflects the radial growth of the Galaxy. 
We have added a couple of sentences to the discussion of equation 10 in~\S~2.5 
to clarify this.

\par\null\par 
\breakline 
\par\null\par 
\textbf{
	An assumption is made that suggests radial migration does not alter the 
	surface density profile of the Galaxy. 
	Is this assumption backed up by the simulation that is used? 
} 
\par 
Our star particle sample from h277 indeed supports this assumption. 
We have added such a statement to the first paragraph of~\S~2.5 and the third 
paragraph of~\S~2.7.

\par\null\par 
\breakline 
\par\null\par 
\textbf{
	A tabulated version of the free parameters of the model would be a useful 
	reference, as I found myself flicking back and forth quite a lot while 
	reading the paper. 
} 
\par 
We have constructed such a table, and placed it near the and of our methods 
section. 
It is referenced in the text at the beginning of~\S~2 (in the final sentence 
before~\S~2.1) and again at the beginning of~\S~2.8.

\par\null\par 
\breakline 
\par\null\par 
\textbf{
	How does the inclusion of bulge-like particles from the simulation change 
	things in the inner disk? 
} 
\par 
Although they are included in VICE's public code base, bulge-like particles are 
not included in the sample used in the models for this paper. 
We state this in the final two sentences of paragraph 4 in~\S~2.1. 
As a result, every star particle assigned as an analogue is one with disc-like 
kinematics. 
We have added a statement to paragraph 3 of~\S~2.2 to clarify this at the same 
time the analogue search process is described.

\par\null\par 
\breakline 
\par\null\par 
\textbf{ 
	The paper discusses intermediate-age alpha-enhanced stars at length but 
	does not provide an idea of their [Fe/H], which would of course provide a 
	more detailed constraint as to their origin in the model. 
} 
\par 
This is an excellent suggestion for further discussion on this prediction of 
our model. 
We have added the relevant statements to the end of paragraph 5 of~\S~3.4.

\par\null\par 
\breakline 
\par\null\par 
\textbf{
	Fig 10: I wondered how much the noted difference between the model and the 
	observations at 3-5kpc might be due to the presence of low metallicity bar 
	stars at this annulus in the data (for example those noted in Bovy et al. 
	2019). 
	A flattening of the surface density profile implied in the central region 
	may make differences here too, I think?
} 
\par 
This is an excellent point! 
We have added a reference to the metallicity map published in Bovy et al. 
(2019) to paragraph 3 of~\S~3.2. 
However, these models are generally independent of the mass normalization - it 
matters in determining how far up the~$\Sigma_\text{gas}-\dot{\Sigma}_\star$ 
relation our models go, but this has only a small effect on chemistry. 
For this reason, we are skeptical that changing the surface density profile 
would significantly impact the MDFs, but we have not ran models with different 
choices for the surface density gradient, so we cannot say for certain. 
We refrain from mentioning anything about surface density in our additions 
to the text.

\par\null\par 
\breakline 
\par\null\par 
\textbf{ 
	Sec 3.4, paragraph 4: The description of the SN Ia rate dropping causing an 
	increase in [O/Fe] is confusing. 
	Especially since gas is not mixing between annuli, I would be surprised if 
	CCSNe could raise the [O/Fe] again once any SNIa had occurred? 
	(I think this implies that at some annuli the radial migration is extremely 
	rapid/efficient and mixing stars out of the annulus on timescales far less 
	than the SNIa timescale, right?) 
} 
\par 
We thank Dr. Mackereth for pointing out that this is confusing. 
It is true that at some annuli radial migration is efficient and mixes stars 
on timescales shorter than or comparable to the SN Ia timescale, but that's 
only one piece of this puzzle. 
There's also migration on longer timescales coupled with the long tail of the 
SN Ia DTD - our DTD is nearly a~$t^{-1}$ power-law, and in that case only half 
of the SNe Ia explode between 100 Myr and 1 Gyr, the other half occurring 
between 1 Gyr and 10 Gyr, leaving plenty of time for radial migration. 
\par 
It is true that [O/Fe] can increase again once SNe Ia have started to go 
off; indeed this is what happens during a starburst event (for details, see the 
Johnson \& Weinberg 2020 paper). 
The reason for this is that it's not the supernovae since~$t = 0$ that 
establish the current chemical composition of the ISM, but rather those that 
occurred approximately within the previous depletion time (see the Weinberg, 
Andrews \& Freudenburg 2017 paper). 
In our models, the depletion time is short at large radii due to the 
substantial mass loading factors there, so the ISM responds quickly to 
perturbations in the core-collapse to type Ia supernova ratio. 
We have expanded our discussion in paragraph 4 of~\S~3.4 in order to 
communicate this more clearly.

\par\null\par 
\breakline 
\par\null\par 
\textbf{
	Sec 3.4: I think the Miglio+ 2020 paper suggests that at least all the 
	Kepler over-massive alpha-rich stars are all explained by mass-transfer, 
	but I could be wrong. 
	I think the age-difference scale between this study and the Warfield+ paper 
	are also significantly different, and likely are due to different 
	phenomena, but I may be wrong! 
} 
\par 
Our understanding of Miglio et al. (2021)'s argument is that at least a 
substantial fraction of the young~$\alpha$-rich population can be attributed 
to mass transfer, but a comparison to binary population synthesis models is 
necessary to make stronger claims. 
The Hekker \& Johnson (2019) paper argues that a portion of the 
young~$\alpha$-rich stars seen in APOGEE are intrinsically young, because 
otherwise their data would make sense only if they're the result of mergers on 
the main sequence. 
These two papers are consistent with one another if a smaller but still 
statistically significant portion of the young~$\alpha$-rich population is made 
of truly young stars not formed via mass transfer. 
Our interpretation isn't mutually exclusive with the mass transfer scenario, 
because they would simply explain different sub-populations of 
young~$\alpha$-rich stars - the model successfully reproduces those which are 
intrinsically young, but we do not correct our abundances for any binary star 
interactions. 
We have added additional discussion to paragraph 5 of~\S~3.4 to make this 
distinction a little clearer.

\par\null\par 
\breakline 
\par\null\par 
\textbf{
	I was confused as to why the 'Late-burst' model was described as having a 
	better agreement to Feuillet et al than the Inside-Out. 
	To an untrained eye they appear to both match the data in some regions 
	better than the other. 
	I think this is further evidence that a more definite bimodality might be 
	achieved by a double burst SFH? 
} 
\par 
We thank Dr. Mackereth for letting us know that this explanation is confusing. 
In general, the inside-out model overpredicts ages for solar and sub-solar 
metallicity stars at~$R = 5 - 7$ kpc, an issue which is mitigated by the 
late-burst model. 
In the outer Galaxy, the late-burst model better reproduces the C-shaped nature 
of the AMR as observed by Feuillet et al. (2019). 
Although there appears to be a difference in normalization at large~$R$ in the 
late-burst model, this could be due to a number of minor details: a 
mis-calibration of our yields or the mass-loading factor, slight differences in 
the time-dependence of the burst as a function of radius, etc. 
We have revised our discussion in~\S~3.5 to address this. 
Perhaps this difference is shown more clearly in the age-[O/H] relation, which 
is unaffected by SN Ia enrichment; this is shown in Fig. 18.

\par\null\par 
\breakline 
\par\null\par 
\textbf{
	I believe that you meant to cite Mackereth et al (2018) in the introduction 
	when referring to the bimodality in simulations. The Mackereth et al (2017) 
	paper which is cited currently concerns modelling of the stellar surface 
	density (and may be of relevance to your discussion of that!). 
} 
\par 
We thank Dr. Mackereth for pointing this out! 
We have updated the draft to cite his 2018 paper.

\par\null\par 
\breakline 
\par\null\par 
\textbf{
	Further, the results and discussion in Mackereth et al (2018) may be 
	relevant to your discussion at the tail-end of section 3.3 - since we also 
	concluded that a hybrid two-infall + migration is needed for bimodality, 
	and we suggested the cause of this in the Milky Way was an atypical early 
	mass assembly. 
} 
\par 
We have added a sentence referencing this.

\par\null\par 
\breakline 
\par\null\par 
\textbf{
	A couple of typos I spotted along the way: 
	\begin{itemize} 
    \item{
	    intro: Rejuvinate~$\rightarrow$ rejuvenate
    }
    \item{
    	Sec 3.3, para 2: I think the bins are 0.04 dex, not 0.4? 
    }
	\end{itemize} 
}
\par 
We thank Dr. Mackereth for catching these editing mistakes!

\end{document}

### 2021-08-04 chemev/MWbimodality/paper/davids_abstract.tex
migration paper referee response

We develop a hybrid model of galactic chemical evolution that combines a
multi-ring computation of chemical enrichment with the predictions of a 
cosmological hydrodynamic disk galaxy simulation for the radial migration and
vertical distribution of stellar populations.  Our fiducial enrichment model 
adopts empirically motivated forms of the star formation law and star formation 
history, and a gradient in outflow mass-loading $\eta(\Rgal)$ tuned to 
reproduce the observed metallicity gradient.  With the simulation-based
migration recipe, this model reproduces many of the striking qualitative 
features of the Milky Way disk's abundance structure: (i) the dependence
of the [O/Fe]-[Fe/H] distribution on $\Rgal$ and midplane distance $|z|$;
(ii) the changing shapes of the [O/H] and [Fe/H] distributions with $\Rgal$
and $|z|$; (iii) a broad distribution of [O/Fe] at sub-solar metallicity and
shifts of the [O/Fe] distribution with $\Rgal$, $|z|$, and [Fe/H]; (iv) a
tight correlation between [O/Fe] and stellar age for [O/Fe]$>0.1$; (v) a
population of young and intermediate-age $\alpha$-enhanced stars caused by
migration-induced fluctuations in the Type Ia supernova rate; 
(vi) non-monotonic [O/H]-age and [Fe/H]-age relations, with large scatter
and a median age $\sim 4\Gyr$ near solar metallicity.  Observationally 
motivated models with a burst of star formation $\sim 2\Gyr$ ago produce
better agreement with the observed [Fe/H]-age relation but worse agreement 
with the observed [O/Fe]-age relation.  None of our models produces an [O/Fe] 
distribution with the distinct bimodality seen in the observations, which 
suggests that more discontinuous forms of the early star formation history 
are required in addition to radial migration.  All code and tables used for 
our models are publicly available through {\tt github.com/giganano/VICE}.

### 2021-08-04 chemev/MWbimodality/paper/davids_conclusion.tex
migration paper referee response

We have compared our fiducial inside-out SFH model and its variants to a 
variety of observations, most of them derived from the SDSS APOGEE survey
\citep{Majewski2017}, finding a number of qualitative successes but also
some significant quantitative discrepancies.

\begin{enumerate}

\item The relative number of high-$\alpha$ and low-$\alpha$ stars and the
  $\feh$ distribution of these two populations changes systematically with
  $\Rgal$ and $|z|$, in qualitative agreement with the findings of 
  \cite{Nidever2014} and \cite{Hayden2015}.  See Fig.~\ref{fig7}.
%%%
\item The $\feh$ and $\oh$ distributions of stars near the Galactic plane
  ($|z|<0.5\kpc$) change shape, from negatively skewed at small $\Rgal$
  to roughly symmetric in the solar neighborhood to positively skewed in
  the outer Galaxy, in agreement with the findings of \cite{Hayden2015}
  and our new measurements based on APOGEE DR16.  The influence of radial
  migration on MDF shape agrees with the simplified model presented
  by \cite{Hayden2015} and with the numerical simulation results of
  \cite{Loebman2016}.  See Figs.~\ref{fig10} and~\ref{fig11}.
%%%
\item Moving up from the midplane, the $\feh$ and $\oh$ MDFs become more
  symmetric and less dependent on $\Rgal$, again in agreement with the
  observational findings of \cite{Hayden2015} and the simulation results
  of \cite{Loebman2016}.  However, the high-$|z|$ MDFs are not a perfect
  match to the APOGEE data, especially at $|z|=0.5-1\kpc$ where they 
  remain too skewed and too $\Rgal$-dependent.  See Figs.~\ref{fig10}
  and~\ref{fig11}.
%%%
\item The distributions of $\ofe$ in bins of $\feh$ are broad, and their
  skewness and width change with $\Rgal$ and $|z|$ in qualitative 
  agreement with the APOGEE-based measurements of \cite{Vincenzo2021}.
  However, the model $\ofe$ distributions at sub-solar $\feh$ do not
  reproduce the pronounced bimodality found by \cite{Vincenzo2021}, and
  the centroid of the model $\ofe$ distribution at super-solar $\feh$
  shifts upwards with increasing $|z|$, a trend not seen in the data.
  See Fig.~\ref{fig12}.
%%%
\item The trend of median stellar age in bins of $\ofe$ agrees with the
  measurements of \cite{Feuillet2019} in the solar neighborhood.  The 
  width of the log(age) distribution is narrow at high $\ofe$ and
  broad near solar $\ofe$, again in agreement with the data.  The model
  predicts a median $\ofe$-age relation that is nearly constant over the
  range $\Rgal=5-13\kpc$ and $|z|=0-2\kpc$, but \cite{Feuillet2019} find
  a $\sim 20\%$ reduction in the median age of high-$\ofe$ stars at high $|z|$.
  See Figs.~\ref{fig13} and~\ref{fig14}.
%%%
\item While most stars with $\ofe \geq 0.1$ are old, the model predicts a
  significant population of young and intermediate-age $\alpha$-rich stars.
  These stars form in the outer Galaxy ($\Rgal > 10\kpc$) at times
  when the local SNIa rate, and thus iron enrichment, has fluctuated to low
  values because stellar populations have migrated away before most of their
  SNIa have time to explode (Fig.~\ref{fig8}).  This mechanism, which is
  only realized because we track SNIa enrichment through annuli as 
  populations migrate (\S\ref{sec:2p2}), offers a novel explanation for the
  existence of young and intermediate-age $\alpha$-rich stars seen in
  APOGEE \citep{Chiappini2015,Martig2015,Warfield2021}.  
  See Figs.~\ref{fig13} and~\ref{fig14}.
%%%
\item In the solar neighbourhood, the predicted distribution of stellar age
  at solar $\feh$ or $\oh$ is broad, and the trend of median age with 
  metallicity is non-monotonic, with both sub-solar and super-solar metallicity
  stars being older on average than solar metallicity stars.  These 
  predictions agree with the observational results of \cite{Feuillet2019},
  though the age scatter is larger than \cite{Feuillet2019} infer, and
  the agreement of median trends is better for $\oh$ than for $\feh$.
  The old population at super-solar metallicity has migrated from the 
  inner Galaxy, as suggested by \cite{Feuillet2018,Feuillet2019}, and 
  migration produces a non-monotonic age-metallicity relation in the
  solar neighborhood even if the SFH is constant throughout the disc.
  The agreement between predicted and observed age-$\feh$ relations is
  noticeably worse at $\Rgal=5-7\kpc$ and somewhat worse at $\Rgal=11-13\kpc$.
  See Figs.~\ref{fig15}-\ref{fig17}.
%%%
\item The models with late bursts of star formation, either throughout the
  disc or at $\Rgal > 6\kpc$ only (see Fig.~\ref{fig4}), achieve better
  agreement with the \cite{Feuillet2019} age-$\feh$ relation over a range
  of $\Rgal$.  In particular, these models better reproduce the young median
  ages of solar metallicity stars and the C-shaped form of the observed
  relation.  However, they predict a $\sim 0.1$-dex uptick of $\ofe$ at
  ages of $\sim 2\Gyr$ that is not seen in the data.  The SFH of these 
  models is empirically motivated \citep{Isern2019,Mor2019}, and we do not
  know if there is some variation of our implementation that would
  preserve their improved agreement with age-$\feh$ while mitigating
  their mismatch to age-$\ofe$.  For the other measures listed above, the
  predictions of these models are qualitatively similar to those of 
  the inside-out model.  See Figs.~\ref{fig14} and~\ref{fig17}.
\end{enumerate}

All of these predictions are affected by radial migration, and those involving
vertical trends also inherit the simulation's predicted correlations between
final $|z|$ and the age, birth radius, and final radius of a stellar population.
We regard the overall level of agreement with many distinctive features of the
Milky Way disc's abundance structure as a signficant success of the models.
However, at least within the range explored here, it appears that models
with smooth star formation, accretion, and outflow histories coupled to
stellar migration are not able to explain the pronounced bimodality of 
the observed $\afe$ distribution.  As discussed by \cite{Vincenzo2021},
we expect that this problem is generic: a one-zone model with a smooth
SFH produces an $\afe$ distribution that peaks at low values, so it is
difficult to create a superposition of such models that has a bimodal 
distribution.

The most widely explored solution to this problem involves a two-phase SFH,
with gas accretion resetting the ISM to low metallicity in between.
Versions of this scenario arise in two-infall GCE models
\citep{Chiappini1997,Spintoni2018,Khoperskov2021} and in cosmological
simulations that give rise to bimodal $\afe$
\citep{Mackereth2017,Grand2018,Buck2020}.  
An alternative scenario proposed by \cite{Clarke2019}, motivated by
hydrodynamic simulations, attributes the low-$\alpha$ sequence to an
evolutionary track with low star formation efficiency and the high-$\alpha$
sequence to clumpy bursts of star formation that self-enrich with
$\alpha$ elements.  In a third, possibly fanciful scenario proposed by
\cite{Weinberg2017}, increased outflow efficiency at late times causes
the low-$\alpha$ population to evolve ``backwards'' to lower $\feh$, after
formation of the high-$\alpha$ sequence.  Radial migration is likely
to reshape the predictions of any of these scenarios, even if it does not
fully explain bimodality on its own.  These scenarios can be easily realized
within our modeling framework by changing SFH, star formation efficiency,
and outflow parameterizations.  We intend to explore the in future work,
seeking observable signatures that can distinguish these alternative 
explanations for one of the most striking features of the disc abundance
distribution.

The computational speed of our hybrid chemical evolution methodology makes it
a valuable complement to calculating chemical evolution within full 
hydrodynamic cosmological simulations 
(e.g., \citealt{Mackereth2017,Grand2018,Naiman2018,Buck2020,Vincenzo2020}).
% Others to cite here?
For a given cosmological simulation, we can consider many different choices
of yields and chemical evolution parameters, varying them individually to
isolate physical effects and exploring parameter space to identify good
fits, degeneracies, and persistent discrepancies with data.  There are 
many obvious directions to go in extending this approach.  One is to apply
it to additional cosmological simulations to understand the impact of 
different dynamical histories, and to add the ability to model stellar
populations accreted from satellites.  A second is to consider additional
elements that probe different nucleosynthetic pathways; many of these are
already incorporated in \vice, and it is easy to add other elements and sources.
A third is to include treatment of radial gas flows and fountains, both
of which have been explored in more idealized GCE models
(e.g., \citealt{Lacey1985,Bilitewski2012,Kubryk2015a,Kubryk2015b,
Spitoni2013,Pezzuli2016,Sharda2021}).  More ambitious is to implement
treatments of stochastic enrichment and incomplete ISM mixing
(e.g., \citealt{Montes2016,Krumholz2018b,Beniamini2020}), which have so 
far been little explored in the context of Milky Way disc evolution
but which are likely important in understanding the detailed correlations
of elemental abundances \citep{Ting2021}.  As multi-element spectroscopic
surveys grow even further in scope and precision, efficient and flexible
theoretical models will be essential for extracting the lessons they
have to teach about the origin of elements and the history of the Milky Way.

### 2021-08-04 chemev/MWbimodality/paper/davids_intro.tex
migration paper referee response

\newcommand{\afe}{[\alpha/{\rm Fe}]}
\newcommand{\ofe}{[{\rm O}/{\rm Fe}]}
\newcommand{\feh}{[{\rm Fe}/{\rm H}]}
\newcommand{\oh}{[{\rm O}/{\rm H}]}
\newcommand{\h277}{{\tt h277}}

The large dispersion in the age-metallicity relation of local disk stars and
the high metallicity of the sun relative to nearby stars of similar age
provided early evidence that stars in the Milky Way disc can migrate many
kpc from the Galactocentric radius at which they formed
\citep{Edvardsson1993,Wielen1996}.
Interest in radial migration as an important element of galactic chemical
evolution (GCE) grew further with the demonstration by \cite{Sellwood2002}
that resonant interactions with transient spiral perturbations could change
stars' orbital guiding center radii without increasing orbital eccentricity,
and with subsequent studies showing ubiquitous radial migration in 
numerical simulations of disc galaxies (e.g., 
\citealt{Roskar2008a,Roskar2008b,Loebman2011,Bird2012,Bird2013,Grand2012,
Kubryk2013}).
% This list could get much longer if we went past 2013, but given the
% historical nature of the paragraph I think it is reasonable to focus
% on the earliest examples.  However, my list there might still be incomplete.
\cite{Schoenrich2009a,Schoenrich2009b} developed the first detailed GCE
models incorporating radial migration, describing it with a flexible
dynamically motivated parameterization constrained simultaneously with
other GCE parameters when fitting to observations.  A number of subsequent
studies have incorporated radial migration using similar analytic or
parameterized models (e.g.,
\citealt{Bilitewski2012,Hayden2015,Kubryk2015a,Kubryk2015b,Feuillet2018,
Sharma2020}), and
\cite{Frankel2018,Frankel2019,Frankel2020} have used stellar abundances,
ages, and kinematics to constrain radial migration empirically.

In this paper we construct evolutionary models for the Milky Way disc that
combine a classic multi-ring GCE approach (e.g.,
\citealt{Matteucci1989,Wyse1989,Prantzos1995})
with the stellar migration predicted by a hydrodynamic simulation of disc
galaxy formation from cosmological initial conditions.  Our methodology
is similar to that of \cite{Minchev2013,Minchev2014} and has similar 
motivations.  The use of a cosmological simulation that agrees with
many observed properties of the Milky Way assures that our stellar 
migration scenario is physically plausible, including any correlations 
of migration in time and space that might be difficult to capture in a
parameterized description.  Most hydrodynamic cosmological simulations include
metal enrichment, and direct comparison between the predicted and observed
abundance patterns can provide valuable insights into the accuracy of the
simulations and the possible origin of the observed element structure (e.g., 
\citealt{Mackereth2017,Grand2018,Buck2020,Vincenzo2020}.
% The reference list for this sentence is potentially semi-infinite.
% As a motivated way to make it finite, I restricted to cases using fully
% cosmological initial conditions (zoom in or large box) that go into some
% detail with, e.g., distributions of abundance ratios in stars, not just
% overall metallicity and gradients.  Within these restrictions there still
% may be multiple papers to add.
However, many ingredients of the simulations' enrichment recipes are uncertain,
and metal transport and mixing within the interstellar medium (ISM) are
sensitive to numerical resolution and to details of the hydrodynamics and
star formation algorithms.  Our hybrid approach allows us to consider many
choices for uncertain GCE parameters, tuning them to reproduce some 
observations while leaving others as independent empirical tests.
This flexible approach also allows us to isolate the impact of different
GCE model ingredients and to zero-in on the ways that stellar migration
influences the predicted chemical evolution.  
The hybrid model is not fully self-consistent, since it adopts its own 
accretion, star formation, and outflow histories rather than the simulation's.
In this paper, furthermore, we use a single cosmological simulation and 
therefore a single realization of migration history, though one could
apply the same method to multiple simulations to predict a statistical
distribution of outcomes.

We focus our predictions and observational comparisons on oxygen, a 
representative $\alpha$-element produced almost exclusively by core
collapse supernovae (CCSN), and iron, which at solar abundances has
roughly equal contributions from CCSN and Type Ia supernovae (SNIa).
We will consider other elements with other nucleosynthetic sources in
future work, but observed trends of $\feh$ and 
$\afe$\footnote{We follow standard
notation $[{\rm X}/{\rm Y}] = \log_{10}[(X/Y)\div (X/Y)_\odot]$.  Different
observational studies use different $\alpha$-elements (or combinations
thereof) in abundance ratios, and we will generally use $\ofe$ and $\afe$
synonymously.} 
in the Milky Way disk already display a number of striking features, including:
\begin{itemize}
\item At sub-solar $\feh$, the distribution of $\afe$ is bimodal, with a
  ``high-$\alpha$'' sequence and ``low-$\alpha$ sequence'' typically
  separated by 0.1-0.4 dex (e.g., 
  \citealt{Furhmann1998,Bensby2003,Adibekyan2012,Vincenzo2021}).
\item The location of the high-$\alpha$ and low-$\alpha$ sequences is nearly
  independent of position in the disc, but the relative number of stars
  in these sequences and the distribution of those stars in $\feh$ changes
  systematically with Galactocentric radius $\Rgal$ and midplane distance $|z|$
  \citep{Nidever2014,Hayden2015,Weinberg2019}.
\item In addition to an overall radial gradient, the shape of the $\feh$
  distribution for stars with $|z|<0.5\kpc$ changes from negatively skewed
  in the inner disc to roughly symmetric at the solar neighbourhood to
  positively skewed in the outer disc \citep{Hayden2015,Weinberg2019}.
\item With increasing $|z|$, $\feh$ distributions become more symmetric
  and less dependent on $\Rgal$ \citep{Hayden2015}.
\item The age-metallicity relation (AMR) is broad, with a wide range of
  $\feh$ at fixed stellar age and vice versa, in the solar neighbourhood
  \citep{Edvardsson1993} and beyond \citep{Feuillet2019}.  The trend of
  median age with $\feh$ or $\oh$ is non-monotonic, with solar metallicity
  stars being younger on average than both metal-poor {\it and} metal-rich
  stars \citep{Feuillet2018,Feuillet2019}.
\item The trend of stellar age with $\afe$ is much tighter than the trend
  with $\feh$, becoming broad near $\afe \approx 0$ 
  \citep{Feuillet2018,Feuillet2019}.  Although most stars with $\afe \geq 0.1$
  are old, observations have revealed a significant population of
  $\alpha$-rich stars that appear to be young or intermediate age
  \citep{Chiappini2015,Martig2015,Warfield2021}.  Some of these stars
  may have been ``rejuvenated'' by stellar mergers or mass transfer 
  \citep{Izzard2018}, and the question of what fraction are truly much
  younger than the median age-$\afe$ relation remains open \citep{Hekker2019}.
\end{itemize}
Many of these results have emerged most clearly from the Apache Point 
Observatory Galactic Evolution Experiment (APOGEE; \citealt{Majewski2017})
of the Sloan Digital Sky Survey (SDSS-III, \citealt{Eisenstein2011};
SDSS-IV, \citealt{Blanton2017}), sometimes confirming and extending trends
suggested by earlier observational data.  We will assess the degree to 
which models with fairly conventional GCE assumptions coupled to 
simulation-based radial and vertical migration of stars can explain, or
fail to explain, these observations.

Relative to \cite{Minchev2013,Minchev2014}, our base GCE model has many 
differences of detail, the most important being our inclusion of outflows,
which is in turn connected to our different choice of oxygen and iron yields.
Our simulation, the galaxy \h277\ from the \cite{Christensen2012} suite
evolved with the N-body+SPH code {\sc GASOLINE}	\citep{Wadsley2004}, is
fully cosmological, while the simulation used by \cite{Minchev2013,Minchev2014}
has a more idealized geometry with merger and accretion history drawn from
a larger cosmological volume \citep{Martig2012}.  
The \cite{Minchev2013,Minchev2014} simulation has a fairly strong, long-lived
bar while \h277\ has only a weak, transient bar, and this difference could
have some impact on radial migration.  Another methodological difference, 
which turns out to be important for some observables, is that we track 
enrichment from stellar populations as they migrate (see \S\ref{sec:2p2} below),
while \cite{Minchev2013,Minchev2014} assume that populations enrich only
the radial zone in which they were born.

Previous studies have shown that \h277\ and other disc galaxies evolved with
similar physics have realistic rotation curves 
\citep{Governato2012,Christensen2014},
stellar mass \citep{Munshi2013}, metallicity \citep{Christensen2016},
dwarf satellite populations \citep{Zolotov2012,Brooks2014}, and 
HI properties \citep{Brooks2017}.  
% List cribbed from Jon's paper; I didn't re-examine.
Most directly relevant to this study,
\cite{Bird2020} show that \h277\ accurately reproduces the observed relation
between stellar age and vertical velocity dispersion $\sigma_z$.
This relation arises in part because of ``upside down'' disc formation in
which the star-forming gas layer becomes thinner with time
\citep{Bournaud2009,Forbes2012,Bird2013} and in part because stars are
dynamically heated over time.
\cite{Schoenrich2009a} distinguish between the radial mixing caused by
``blurring'' of stars on moderately eccentric orbits and ``churning'' that
changes the guiding center radii of their orbits.  Both phenomena occur in
our simulation and we do not attempt to separate them, using the terms
``radial migration'' or ``radial mixing'' to cover their combined effect.
In addition to radial migration, we use the \h277\ predictions for the
vertical locations (i.e., midplane distances $|z|$) of stars at the 
present day.  Our GCE model assumes that the gas disk is vertically well
mixed, so a stellar population's birth abundances depend only on $\Rgal$
and time.  Vertical gradients arise because older populations have
larger $\sigma_z$ and thus larger average $|z|$, and also because radial
migration is coupled to changes in $\sigma_z$ \citep{Solway2012}.
%% JON: OTHER PAPERS WE SHOULD CITE HERE?
The good match to the observed age-velocity relation found by \cite{Bird2020}
allows us to use vertical trends of abundance distributions as a further
test of our chemical evolution model.

We describe the \h277\ simulation further in \S\ref{sec:2p1} and our
implementation of radial migration in \S\ref{sec:2p2}.
We describe the base GCE model in \S\S\ref{sec:2p3}-\ref{sec:2p6}.
Distinctive features of our GCE model are the use of radially dependent
mass outflow loading $\eta(\Rgal)$ to tune the metallicity gradient,
our implementation of a star formation law motivated by spatially resolved
studies of nearby galaxies and high-redshift studies of its time dependence,
and our use of mean radial age trends of disc galaxies to set the radial
dependence of the star formation history (SFH).  Our fiducial model adopts
a smooth SFH with an ``inside out'' radial trend in which star formation
proceeds more rapidly in the inner Galaxy.  Motivated by the observational
analysis of \cite{Isern2019} and \cite{Mor2019}, we also consider models with
a burst of star formation centred $\approx 2\Gyr$ in the past, similar to 
the one-zone models investigated by \cite{Johnson2020}.  Other authors have
suggested multiple bursts in the Milky Way's SFH 
(e.g., \citealt{Lian2020a,Lian2020b,Sysoliatina2021}, OTHERS?),
perhaps triggered by satellite interactions, while others have advocated
a two-phase star formation history to explain the $\afe$ dichotomy
(e.g., \citealt{Chiappini1997,Haywood2016,Spitoni2019,Buck2020,Khoperskov2021}).
% I don't think this is the place to reference every paper using the 2-infall
% model, but we could add one or two more references if they clearly belong
% with this sentence, especially if they bring in a distinct group.
We do not investigate these more complex SFHs here, but we plan to do so
in future work.

### 2021-08-04 chemev/MWbimodality/paper/draft1/draft1.tex
migration paper referee response

\documentclass[fleqn, usenatbib]{mnras} 
\usepackage{newtxtext, newtxmath} 	% Required for MNRAS 
\usepackage[T1]{fontenc} 
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{multicol}
\usepackage{bm}
\usepackage{pdflscape}
\usepackage{natbib}
\usepackage[section]{placeins}
\usepackage{lipsum}
\usepackage{etoolbox} 
\usepackage{tabularx} 
\usepackage{xcolor} 
\usepackage[toc, page]{appendix} 
% \hypersetup{draft} 
% \linespread{1.8} 
\hypersetup{ 
	colorlinks		= true, 
	urlcolor 		= blue, 
	linkcolor 		= blue, 
	citecolor 		= blue 
}

\newcommand{\ddfrac}[2]{\frac{\displaystyle #1}{\displaystyle #2}} 
\newcommand{\refp}[1]{(\ref{#1})} 
\newcommand{\msun}{\ensuremath{\text{M}_\odot}} 
\newcommand{\persqkpc}{\ensuremath{\text{kpc}^{-2}}} 
\providecommand{\noopsort}[1]{} 
\graphicspath{ {../plots/} }

\interfootnotelinepenalty = 10000 
\defcitealias{Kroupa2001}{Kroupa} 
\defcitealias{Salpeter1955}{Salpeter}

\title[Stellar Migration and Chemical Enrichment]{Stellar Migration and 
Chemical Enrichment in the Milky Way Disc: A Hybrid Model}

\author[J.W. Johnson et al.]{
	James W. Johnson,$^{1}$\thanks{Contanct e-mail: \href{mailto:
	johnson.7419@osu.edu}{johnson.7419@osu.edu}} 
	David H. Weinberg,$^{1, 2, 3}$ 
	Fiorenzo Vincenzo,$^{2}$ 
	Jonathan C. Bird,$^{4}$ 
	\newauthor 
	Sarah R. Loebman,$^{5}$ 
	Alyson Brooks,$^{6}$ 
	Thomas R. Quinn,$^{7}$ 
	Charlotte R. Christensen,$^{8}$ 
	\newauthor 
	et al.?
	\\
	$^{1}$ Department of Astronomy, The Ohio State University, 
	140 W. 18th Ave., Columbus, OH, 43210, USA 
	\\ 
	$^{2}$ Center for Cosmology and Astroparticle Physics (CCAPP), 
	The Ohio State University, 191 W. Woodruff Ave, Columbus, OH, 43210, USA 
	\\ 
	$^{3}$ Institute for Advanced Study, 1 Einstein Dr., Princeton, NJ, 08540, 
	USA 
	\\ 
	$^{4}$ Department of Physics \& Astronomy, Vanderbilt University, 
	2301 Vanderbilt Place, Nashville, TN, 37235, USA 
	\\ 
	$^{5}$ Department of Physics, University of California Merced, 
	5200 North Lake Rd., Merced, CA, 95343, USA 
	\\ 
	$^{6}$ Department of Physics \& Astronomy, Rutgers University, 136 
	Frelinghuysen Rd, Piscataway, NJ, 08854, USA 
	\\ 
	$^{7}$ Department of Astronomy, University of Washinton, Box 351580, 
	Seattle, WA, 98195, USA 
	\\ 
	$^{8}$ Department of Physics, Grinnell College, 1116 8th Ave., Grinnell, 
	IA, 50112, USA 
}

\date{Accepted XXX; Received YYY; in original form ZZZ} 
\pubyear{2020}

\begin{document} 
\label{firstpage} 
\pagerange{\pageref{firstpage}--\pageref{lastpage}} 
\maketitle

\begin{abstract} 
We investigate the impact of stellar migration on galactic chemical evolution 
models, considering a handful of assumptions for the star formation history 
and time-dependence of radial migration based on a zoom-in, hydrodynamical 
simulation of galaxy evolution. When stars migrate with a smooth, continuous 
time dependence, the type Ia supernova rate exhibits significant variability in 
our models. We demonstrate that this is a means with which young, super-solar 
[$\alpha$/Fe] in the solar neighbourhood can arise naturally out of inside-out 
Galaxy growth with stellar migration. We find 
that the observed age-[$\alpha$/Fe] relation is well-fit by an inside-out star 
formation history, while the age-[$\alpha$/H] and age-[Fe/H] relations are 
well-fit by a late starburst model; no one model investigated here fits both 
simultaneously. Our model successfully reproduces the broad nature of the 
[$\alpha$/Fe] distribution at fixed [Fe/H] in a given Galactic region; however, 
an overprediction of the frequency of intermediate [$\alpha$/Fe] stars prevents 
it from explaining the observed results in detail. This suggests 
that inside-out galaxy growth combined with stellar migration, even with a late 
starburst, is not conducive to forming the infamous bimodality as it is 
observed. We postulate that more dramatic evolutionary scenarios (e.g. a 
two-infall model) may be necessary to describe the observed results. In 
conducting this analysis, we developed and made use of newly released features 
in the \texttt{Versatile Integrator for Chemical Evolution} (\texttt{VICE}) 
which are built to handle these models under a wide variety of 
assumptions. \texttt{VICE} is publicly available 
at~\url{https://pypi.org/project/vice}. 
\end{abstract}

\begin{keywords} 
methods: numerical -- galaxies: abundances, evolution, star formation, stellar 
content 
\end{keywords}

\section{Introduction} 
\label{sec:intro} 
The orbits of stars are not unchanging. While it has been known for some time 
that stars undergo radial migration (e.g.~\citealp*{Wielen1996}; 
\citealp{Roskar2008a,Loebman2011,Minchev2012}), the true impact of this process 
on galactic chemical evolution (GCE) remains under debate. By mixing stellar 
populations which formed in Galactic regions with significantly different 
enrichment histories, in principle the impact could be considerable. While some 
authors argue that radial migration has only a small impact on GCE 
(e.g.~\citealp*{Kubryk2013};~\citealp{Khoperskov2021}), there are others who 
argue the contrary (e.g.~\citealp{Schoenrich2009};~\citealp*{Sharma2020}). 
Aside from the chemodynamical simulations involving N-body integrations 
\citep[e.g.][]{Kubryk2013, Vincenzo2020, Khoperskov2021}, there are to date 
only a handful of GCE models that take this effect into account (e.g. 
\citealp{Matteucci1989, Schoenrich2009};~\citealp*{Minchev2013}; 
\citealp{Sharma2020}). These studies treat the Milky Way as a series of 
concentric annuli, each described by a conventional one-zone GCE model with 
parameters that change from annulus to annulus. In the resultant ``multi-zone'' 
model, stars and gas can migrate between zones under some prescription to 
account for time-dependent mixing processes. We retain such methodology in this 
paper, allowing star particles from a hydrodynamical simulation ran from 
cosmological initial conditions to inform our implemented mixing process; 
\citet{Minchev2013} employ a similar technique. With parameters tuned to 
reproduce certain observed results (e.g. abundance and surface density 
gradients), we can then assess the model predictions to address the following 
question: when combining simple, conventional assumptions about the star 
formation and dynamical histories of the Milky Way, what observed results can 
be replicated? In the present paper, we focus on the following observables: 
metallicity distributions functions (MDFs) and abundance gradients, the 
[$\alpha$/Fe] bimodality, the age-metallicity relation (AMR), and the young, 
$\alpha$-rich population. 
\par 
Stars in the inner regions of the Milky Way tend to be more metal-rich than 
those found in the outskirts~\citep{Nordstroem2004b, Daflon2009, 
Frinchaboy2013, Hayden2014}, with slight variations in quantitative results 
based on what type of stars are considered and what metallicity tracers are 
analysed. Such behavior is also seen in the gas-phase gradients of 
low-redshift spirals (see, e.g., the results from the CHAOS project using HII 
regions;~\citealp{Berg2015, Berg2020}). Using the 12th data release of the 
Apache Point Observatory Galaxy Evolution Experiment (APOGEE), 
\citet{Hayden2015} demonstrate that the observed MDF has a metal-rich mode and 
is skew-negative in the inner galaxy (and conversely, metal-poor and 
skew-positive in the outer galaxy). These variations in the skewness of the 
distributions with Galactocentric radius are usually attribute to the migration 
of metal-rich (metal-poor) stars from smaller (larger) orbital radii. Similar 
arguments are used by~\citet{Sellwood2002} to interpret the results of 
\citet{Edvardsson1993} on scatter in the age-metallicity relation observed in 
the solar neighbourhood. 
\par 
Abundance gradients have been the focus of many studies and are quantified 
rather extensively, but their origin is somewhat up for debate. Applying the 
analytic models of~\citet*{Weinberg2017}, one could argue that the gradient 
arises out of variations in the local gas-phase equilibrium abundance as a 
function of Galactocentric radius. For $\alpha$-elements, the equilibrium 
abundance is determined to first order by their yield and the efficiency of 
outflows in removing metals from the star forming reservoir. With a stronger 
gravitational potential in the inner regions of the Galaxy, one might 
reasonably expect outflows to be weaker there, thereby increasing the 
equilibrium abundance.~\citet{Nidever2014} used such an approach to reproduce 
the width of the [Fe/H] distribution for low-$\alpha$ sequence stars in 
APOGEE. However, recent chemical evolution models have successfully replicated 
the gradient with no outflowing winds at all~\citep[e.g.][]{Minchev2013, 
Spitoni2019a}. This is based on arguments from~\citet{Melioli2008, Melioli2009}, 
\citet*{Spitoni2008}, and~\citet{Spitoni2009} who studied Galactic fountains 
using hydrodynamical simulations and numerical models, finding that ejected 
metals tend to reaccrete to a Galactocentric radius similar to where they 
originated. With this result, some authors argue that such outflows do not 
significantly alter the chemical evolution of a Galactic disc, and that instead 
the gradient arises from the higher normalization of the star formation history 
in the inner Galaxy. 
\par 
Like radial abundance gradients, the reality of the infamous [$\alpha$/Fe] 
dichotomy is well established (in Gaia-ESO:~\citealp{Recio-Blanco2014, 
Rojas-Arriagada2017}; in APOGEE:~\citealp{Nidever2014, Hayden2015, 
Weinberg2019}), but its origin is a topic of intense debate. In general, stars 
in the Milky Way tend to fall in one of two populations - the roughly solar 
[Fe/H], solar [$\alpha$/Fe] stars commonly referred to as the low-$\alpha$ 
sequence, and the high-$\alpha$ sequence made up of sub-solar [Fe/H], 
super-solar [$\alpha$/Fe] stars. Recently explored with more current data by 
\citet{Sharma2020}, the notion that it could in principle arise out of radial 
migration traces back to~\citet{Schoenrich2009}. Applying the analytic models 
of~\citet{Weinberg2017}, an alternative pathway to such abundance patterns is 
by an increase in the strength of outflows at late times. Such an evolutionary 
model would predict a decrease in the equilibrium abundance, forming stars 
along the low-$\alpha$ sequence. This scenario has not yet been explored in 
combination with radial migration. 
\par 
Other authors argue that more dramatic evolutionary events are necessary to 
explain the observed results, such as the two-infall model 
(\citealp*{Chiappini1997, Chiappini2001};~\citealp{Romano2010, Grisoni2017, 
Noguchi2018, Palla2020, Spitoni2016, Spitoni2018}). 
In these models, the high-$\alpha$ sequence forms during the Galaxy's initial 
collapse before feedback processes shut off star formation and expel gas into 
the Galactic halo. Then, this material can cool and reaccrete along with 
additional, metal-poor gas from the intergalactic medium, producing a second 
episode of star formation. The dilution associated with the second accretion 
event lowers the gas-phase Fe abundance at fixed [$\alpha$/Fe], forming stars 
along the low-$\alpha$ sequence.~\citet{Spitoni2019a, Spitoni2020} demonstrated 
using the APOKASC sample~\citep{Pinsonneault2014, SilvaAguirre2018} that such 
models can explain the abundances observed in the solar annulus. Although 
\citet{Spitoni2021} recently extended this model to Galactic regions beyond 
the solar annulus, their model did not account for the mixing of stellar 
populations between regions. Though they invoke~\citet{Kubryk2013} and 
\citet{Khoperskov2021} as arguments that it shouldn't impact their results, 
this nonetheless means that two-infall models have not yet been explored in 
combination with a treatment for stellar migration. 
\par 
Recent cosmological zoom-in simulations have found results qualitatively 
similar to the arguments of~\citet{Spitoni2019a, Spitoni2020, Spitoni2021}. 
Using the Auriga simulation suite~\citep{Grand2017},~\citet{Grand2018} 
demonstrate that an early, accretion induced starburst can populate the 
high-$\alpha$ sequence, followed by low-level, sustained star formation on the 
low-$\alpha$ sequence. In this pathway, there is either a rapid transition 
between the two phases, ensuring the chemical space between the sequences is 
relatively unpopulated, or low-metallicity gas accretion dilutes the star 
forming reservoir at fixed [$\alpha$/Fe], populating the low [Fe/H], low 
[$\alpha$/Fe] portion of the low-$\alpha$ sequence.~\citet{Buck2020b} finds 
the dilution scenario in the NIHAO simulation suite as well~\citep{Wang2015, 
Buck2020a}. Although the~\citet{Spitoni2021} model did not implement mixing of 
stellar populations, these studies using hydrodynamical simulations would 
suggest pathways qualitatively similar to their two-infall model. 
\par 
Contrary to this scenario,~\citet{Clarke2019} demonstrate that star formation 
proceeded in clumps in an SPH simulation using GASOLINE~\citep*{Wadsley2017}. 
These clumps self-enrich, forming stars on the high-$\alpha$ sequence due to 
the perturbed ratio of core collapse to type Ia supernova rates within the 
star forming regions. The more spatially extended, smooth star formation 
populates the low-$\alpha$ sequence. Suffice it to say that there are no 
shortage of models which reproduce the dichotomy, but only those done with 
hydrodynamical simulations and a handful of others 
\citep[e.g.][]{Schoenrich2009, Minchev2013, Sharma2020} have taken into account 
stellar migration. 
\par 
Besides abundance gradients and the [$\alpha$/Fe] dichotomy, another 
observable of interest in this paper is the age-metallicity relation (AMR): the 
correlation between stellar ages and metallicities. The observed AMR in the 
solar neighbourhood is known to exhibit considerable intrinsic scatter 
\citep{Edvardsson1993}; this is usually attributed to radial migration of 
metal-rich (metal-poor) stars from smaller (larger) Galactocentric radii 
\citep{Sellwood2002, Haywood2008, Roskar2008b, Schoenrich2009}. 
In the solar neighbourhood,~\citet{Feuillet2018} reveal that super-solar 
metallicity stars are statistically older than solar metallicity stars (see 
their Fig. 3). This contrasts with the predictions of simple one-zone models of 
GCE where enrichment proceeds alongside star formation, yielding a monotonic 
AMR~\citep[e.g.][]{Andrews2017, Weinberg2017}. Although one-zone models of 
starbursts can predict a non-monotonic AMR due to the effect of dilution 
\citep{Johnson2020}, by construction they do not predict multiple abundances at 
fixed age as~\citet{Feuillet2018} reports. Using the~\citet{Weinberg2017} 
analytic models,~\citet{Feuillet2018} argues that this is a consequence of 
radial migration. For a smooth star formation history, the youngest stars at a 
given radius will have compositions reflective of the local equilibrium 
abundance; only stars born at different radii will have different compositions, 
and only the old ones will have had time to migration to the solar annulus. 
\par 
While the presence of old-metal rich stars in the solar annulus is peculiar 
because they are at odds with one-zone models of chemical evolution, the 
presence of young, $\alpha$-rich stars is interesting for the same reason. 
For a smooth star formation history, the delayed nature of type Ia supernovae 
and their Fe production cause [$\alpha$/Fe] to decrease with time, predicting 
an age-[$\alpha$/Fe] relation that should increase monotonically with stellar 
age. However, these~$\sim$few Gyr old stars with [$\alpha$/Fe]~$\approx$~+0.1 - 
0.2 stars have been found using stellar ages estimated from carbon-to-nitrogen 
ratios~\citep{Martig2016}, isochrone matching~\citep{Feuillet2018, 
Feuillet2019}, and with the asterosesmic ages of the original APOKASC catalog 
\citep{Chiappini2015, SilvaAguirre2018, Pinsonneault2014}. 
\citet{SilvaAguirre2018} demonstrate that these stars have kinematics similar 
to the rest of the high-$\alpha$ population, postulating that they may be 
the consequence of stellar mergers or mass transfer events, making truly old 
stars simply appear younger. In a sample of 51 young, $\alpha$-enhanced red 
giant stars,~\citet{Hekker2019} conclude that a portion of these stars have 
carbon-to-nitrogen ratios consistent with mass transfer events, but that this 
cannot account for the entire population. This suggests that the remaining 
stars are either truly young or the result of mergers on the main sequence. 
If not, then a theoretical explanation for the origin of these stars remains 
a mystery. 
\par 
Alternatively, a recent starburst event could have produced these stars. 
\citet{Mor2019} infer a factor of~$\sim$2 enhancement in the star formation 
history (SFH) of the Milky Way~$\sim$2 Gyr ago by comparing population 
synthesis models to observed stellar luminosity functions and colour-magnitude 
diagrams from Gaia data~\citep{GaiaDR2}.~\citet{Isern2019} reach similar 
conclusions by modeling the white dwarf luminosity function in the solar 
neighbourhood with Gaia parallaxes. Motivated by these results, 
\citet{Johnson2020} demonstrate using one-zone chemical evolution models that 
a recent starburst of this nature can produce similarly young,~$\alpha$-rich 
stars. However, the caveat to this interpretation is that the starburst must be 
sufficiently localized such that the resultant stellar populations remain 
outliers from an otherwise monotonically increasing age-[$\alpha$/Fe] relation. 
\par 
The impact of such evolutionary histories combined with stellar migration is, 
to our knowledge, yet unexplored in the literature. A viable model for the 
detailed enrichment history of the Milky Way would simultaneously explain all 
of these observed results and their variations between Galactic regions, while 
also taking into account effects like mixing and observational systematics. On 
top of this, it must self-consistently calculcate enrichment rates from adopted 
nucleosynthetic yields and the SFH. In this paper, we aim to 
assess the extent to which conventional assumptions about the evolutionary 
history of the Milky Way can account for these results, entertaining a 
handful of assumptions describing the SFH and time-dependence of stellar 
radial migration. 
\par 
Motivated by the general result that galaxies grow in radius with time 
(i.e. ``inside-out'' growth;~\citealp{Bird2013}), our base-line model has a 
star formation history (SFH) whose e-folding timescales grow with 
Galactocentric radius. Based on the findings of~\citet{Mor2019} and 
\citet{Isern2019}, we also construct models in which a late starburst is 
imposed atop the inside-out SFH. In one model, this starburst occurs in all 
annuli, and in another, loosely informed by the findings of 
\citet{Vincenzo2020} suggesting such a radial dependence to accretion, it 
occurs only at~$\geq$6 kpc. We also construct a model in which the SFH is 
constant at a given Galactocentric radius; these models are interesting from a 
theoretical perspective in that they quantify the impact of stellar migration 
without the effects of a time-dependent SFH.

\section{Methods} 
\label{sec:methods} 
To fulfill the goals of this paper, we develop and make use of newly released 
features within the~\texttt{Versatile Integrator for Chemical Evolution} 
(\texttt{VICE};~\citealp{Johnson2020}). These features are designed to handle 
models such as these with a wide range of flexibility. We reserve a description 
of~\texttt{VICE}'s migration algorithm and our simulation parameters for~\S 
\ref{sec:methods:migration}, first describing our sample of star particles from 
the hydrodynamical simulation. 
\par 
Although we make use of a hydrodynamical 
simulation to drive stellar migration, we do~\textit{not} make use of its SFH. 
While our study employs similar techniques as~\citet{Minchev2013}, our differs 
in this subtle aspect. An alternative to modeling radial migration based on a 
hydrodynamical simulation is to invoke dynamical arguments; 
\citet{Schoenrich2009} and~\citet{Sharma2020} take such an approach. This 
method, however, introduces free parameters which then require fitting to 
data. An advantage of our technique is that there are no free parameters 
introduced to the model; furthermore, it's unclear the extent to which the fit 
biases the model into agreement with parts of the data not involved in the 
fitting process. The dynamical history of a hydrodynamical simulation is also 
motivated by first principles in that it models gravitational interactions via 
an N-body integration. The primary disadvantage of this approach is a 
consequence of the lack of free parameters - the model is rigid, and we cannot 
explore slight variations. However, in principle one could compare the 
predictions made by our chemical evolution models when ran using different 
hydrodynamical simulations. We emphasize that a hydrodynamical simulation 
\textit{only} informs the mixing processes in our models, and there is no 
N-body integration involved in our models aside from that which was used to run 
the hydrodynamical simulation in the first place.

\subsection{The Hydrodynamical Simulation} 
\label{sec:methods:h277} 
In this paper we make use of star particles from the~\texttt{h277} simulation 
\citep{Christensen2012, Zolotov2012, Loebman2012, Loebman2014, Brooks2014}. 
Recently employed to study the stellar age-velocity relationship, a synopsis of 
its detailed simulation parameters and cosmological model can found in~\S 2 of 
\citet{Bird2020}. We do not include any discussion of these details here, 
instead focusing on how we vet the sample of star particles for use in our 
chemical evolution models. 
\par 
It is of particular important to have accurately measured formation radii for 
each star particle that we use in our analysis.~\texttt{h277} did not record 
the exact birth radius of each star particle; however, each star particle does 
have an accurate age at each snapshot. Since stellar orbits are unlikely to 
change significantly in an adequately short time interval, the radii of 
sufficiently young stars in their first snapshot are reasonable approximations 
of their birth radii. We therefore restrict our sample to those with an age at 
first snapshot of~$\leq$~150 Myr, and adopt their Galactocentric radius at that 
time as their birth radius. We have also conducted this analysis with a maximum 
age at first snapshot of 50 Myr, and found similar results, suggesting that 
these time intervals are short enough to not impact our conclusions. In 
practice, we find that 150 Myr also provides with an adequately large number of 
star particles to sample from. Of the star particles that remain after imposing 
this cut, the oldest one is 12.26 Gyr old at the present day. Our model can 
only apply on timescales as long as or shorter than the full range of ages of 
the sample of star particles; we therefore subtract 1.5 Gyr from the formation 
times of all star particles, allowing~$T$~= 0 in our models to correspond to 
$T$~= 1.5 Gyr in~\texttt{h277}. As a consequence, our disc models trace the 
chemical evolution of the Galaxy out to a lookback time of~$\sim$12.2 Gyr, or a 
redshift of~$z \approx$~3, placing the onset of star formation at that time. 
\par 
We further restrict our sample of star particles to only those with both 
formation and final radii of~$R_\text{gal} \leq$~20 kpc, and to have formed 
within~$\left|z\right|\leq$~3 kpc of the disc midplane. These criteria ensure 
that we're only using star particles which formed in-situ. While it's possible 
that some star particles formed in a dwarf galaxy as it was infalling, a 
scenario which would satisfy these requirements, these star particles are few 
in number, and are only relevant at large~$R_\text{gal}$ and high ages - a 
region of parameter space where few stars form anyway. 
\par 
Based on a kinematic decomposition performed on the present-day phase space 
distribution of the~\texttt{h277} star particles, we include all those with 
bulge, pseudobulge, and disc-like kinematics, excluding halo stars. While we're 
not modeling the evolution of the bulge here, these star particles are 
overwhelmingly located at~$R_\text{gal}\leq$~3 kpc at the present day anyway; 
here we're much more interersted in~$R_\text{gal}\geq$~3 kpc since we're 
modeling the evolution of the disc. These cuts yield a sample of 3,000,556 star 
particles from~\texttt{h277}. 
\par 
\texttt{h277} had a transient bar during its evolution, but does not have one 
at~$z$ = 0 ({\color{red} citation?}). This is a noteworthy difference between 
our model and that of~\citet{Minchev2013}, and by extension the 
\citet*{Minchev2014} and~\citet{Minchev2017} studies which use it as well, 
because they selected a hydrodynamical simulation of a galaxy specifically so 
that it would have a strong bar at~$z$ = 0; the transient bar in~\texttt{h277} 
was not strong. This could mean that the dynamical 
history of our model Galaxy does not reflect that of~\citet{Minchev2013} and 
perhaps the Milky Way itself. However, the difference is likely within the 
uncertainties of the current understanding of the Milky Way's dynamical 
history. Although an investigation on the impact of bar evolution on stellar 
migration and thus chemical evolution is outside the scope of this paper, it is 
an interesting question which can be probed by simply swapping the 
\texttt{h277} data within~\texttt{VICE} for another simulation, then rerunning 
our numerical models and comparing the results.

% fig 1 
\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{decomposition.pdf} 
\caption{Radial distributions of our star particles from 
\texttt{h277}. In the top row, we show distributions of~\textit{final} radius 
in bins of birth radius and age, and in the bottom row, we show distributions 
of~\textit{birth} radius in bins of final radius and age. Each bin in 
Galactocentric radius is shown in its own panel, denoted in text at the top of 
each panel and by vertical black dashed lines. We colour-code the distributions 
according to the age of the star particles, denoted by the legend in the upper 
left panel. We smooth all distributions with a box-car width of 0.5 kpc to 
improve clarity. We omit the distributions for 8 - 10 Gyr old stars born in the 
9 - 11 and 11 - 13 kpc bins due to an insufficient number of star particles 
with which to calculate the distribution. } 
\label{fig:h277_decomposition} 
\end{figure*}

In the top row of Fig.~\ref{fig:h277_decomposition}, we plot the distributions 
of final radius in bins of birth radius and age for our sample of star 
particles. Conversely, the bottom rows distributions of birth radii in bins of 
final radius and age. Focusing on the top row of panels, we note that for star 
particles born at any radius and time, the distribution of final radius is 
still peaked near the birth radius, but moves slightly inward with increasing 
age. The tails of the distributions toward larger~$R_\text{gal}$ are nearly 
age-independent, while the tails toward smaller~$R_\text{gal}$ are not. This 
suggests that radial migration inward and outward occur on different timescales 
in~\texttt{h277}, specifically that inward migration is slower than outward 
migration. By extension, this suggests that the two may be tied to different 
physical processes. In a cosmological simulation,~\citet{Roskar2008a} 
demonstrate that resonant scattering at corotation causes stars to move 
outward and gas to move inward. It's possible that stellar migration inward has 
different origins. 
\par 
Focusing on the bottom row of panels in Fig.~\ref{fig:h277_decomposition}, we 
note that the mode of the birth radius distributions show a stronger dependence 
on age than the mode of the final radius distributions. At any Galactocentric 
radius at the present day, the youngest stars are overwhelmingly born at 
comparable radii, while the oldest stars are overwhelmingly born at smaller 
radii. This is most noticeable in at large~$R_\text{gal}$. The differences 
between the two can be understood by considering the steep nature of the radial 
gradient in stellar surface density. Take for example the 8 - 10 Gyr age bin in 
both~$R_\text{Birth}$ = 5 - 7 kpc and~$R_\text{Final}$ = 11 - 13 kpc bins (i.e. 
the red curves in the top-left and bottom-right panels). For these old stars 
born at 5 - 7 kpc, 11 - 13 kpc is far down the tail of the~$R_\text{Final}$ 
distribution, and yet 5 - 7 kpc is the mode~$R_\text{Birth}$ of all old stars 
presently at these radii. This implies that even though a plurality of 8 - 10 
Gyr old stars with~$R_\text{Final}$ = 11 - 13 kpc were born at 5 - 7 kpc, they 
account for only a small fraction of the stars with similar birth radii. This 
is only possible if there are many more stars born at small~$R_\text{gal}$ than 
large~$R_\text{gal}$, implying a stellar surface density which decreases as a 
strong function of Galactocentric radius. This is known to be the case 
\citep[e.g.][]{Bland-Hawthorn2016}. 
\par 
We also note that the top row of Fig.~\ref{fig:h277_decomposition} demonstrates 
that the number of stars which migrated inward and outward are comparable in 
\texttt{h277}. In fact, taking~$\left|\Delta R_\text{gal}\right| \geq$~500 pc 
between birth and final radii as the criterion for migration inward or outward, 
we indeed find as global percentages in our sample that 27\% migrated inward, 
29\% migrated outward, and the remaining 44\% stayed near their birth radius. 
Furthermore, these distributions contain some information on the timescales of 
radial migration. In all bins of birth radius, a good first-order estimate of 
the probability density that a star has a final radius in the same bin is 
$\sim$0.3. With bins in birth radius of 2 kpc, this suggests that only 
$\sim$60\% of stars remain in their birth radius bin by the time their~$\sim$2 
Gyr old. and the remaining~$\sim$40\% have migrated already. If the type Ia 
supernova delay-time distribution (SN Ia DTD) is a~$t^{-1.1}\approx t^{-1}$ 
power-law as suggested by observational results~\citep[e.g.][]{Maoz2012, 
Maoz2017}, then we expect similar numbers of SN Ia events to occur with delay 
times between 1 and 10 Gyr as we do between 100 Myr and 1 Gyr. With such an 
extended DTD, and the timescales for migration implied by Fig. 
\ref{fig:h277_decomposition}, its possible that SN Ia progenitors can migrate 
significant distances before exploding. Indeed, in the ASAS-SN bright SN 
catalog,~$\sim$10\% of SNe are seen at >10 kpc from their host galaxies 
\citep{Holoien2019}. While this catalog is for~\textit{all} supernovae seen by 
ASAS-SN, the majority of SN events are type Ia anyway. Based on this, it's 
reasonable to expect that the migration of nucleosynthetic may proceed 
alongside stellar migration. This effect has largely been neglected by GCE 
studies to date on the grounds that radial migration is a slow process, and 
thus the majority of nucleosynthesis should occur near a star's birth radius 
(e.g.~\citealp{Minchev2013}, and in the application of the 
\citealt{Weinberg2017} analytic models in~\citealt{Feuillet2018}). However, 
with the realization that the SN Ia duty cycle is also a slow process due to 
the long tail of the DTD, its possible that stellar migration and SN Ia occur 
on similar timescales. Therefore, we relax this assumption in the present 
paper. We discuss the application of the~\texttt{h277} star particle data to 
our model for radial migration and the time dependence thereof in the next 
section.

\subsection{Radial Migration} 
\label{sec:methods:migration} 
As in previous studies~\citep[e.g.][]{Schoenrich2009, Minchev2013, Sharma2020}, 
in this paper we model the Milky Way as a series of concentric annuli with a 
uniform width~$\Delta R_\text{gal}$. To run numerical simulations of these 
models, we develop and make use of~\texttt{VICE}'s~\texttt{milkyway} object, 
designed specifically for such an approach. The~\texttt{milkyway} object is a 
subclass of a more general object named~\texttt{multizone}; at its core a 
\texttt{multizone} object is an array of~\texttt{singlezone} objects, which are 
designed to handle one-zone models of GCE and were the focus of 
\citet{Johnson2020},~\texttt{VICE}'s initial release paper. The 
\texttt{multizone} object affords users full control over which zone any 
individual stellar population is in at all timesteps following its formation as 
well as the ability to move gas between any two zones with any time dependence. 
In principle this should allow for arbitrarily complex zone configurations and 
migration prescriptions. The \texttt{milkyway} object is a user-friendly 
extension of this which enforces an annular zone configuration as we take here. 
As defaults, it adopts the stellar migration model detailed in this section and 
our star formation law discussed in~\S~\ref{sec:methods:sfe}. 
\par 
As in hydrodynamical simulations, stars in~\texttt{VICE} are stand-ins for 
entire stellar populations. They're said to be in a given zone if their radius 
is between the inner and outer edges of the annulus. At all times, their 
nucleosynthetic products and returned envelopes are placed in the ISM of the 
annulus that they are in~\textit{at that time}. Where hydrodynamical and 
N-body simulations of Galaxy evolution tend to use star particles of a fixed 
mass, however,~\texttt{VICE} forms a fixed number of stellar populations per 
zone per timestep, and allows their masses to vary to account for variations 
in the star formation rate (SFR). The mass of stars formed in a given zone is 
divided evenly among the stellar populations that form in a given zone and 
timestep. 
\par 
The final radius of a stellar population is then determined based on the birth 
and final radii of star particles in a hydrodynamical simulation, for which 
we've taken~\texttt{h277} in this paper (see discussion in~\S 
\ref{sec:methods:h277}). Describing the Galaxy as a series of concentric 
annuli,~\texttt{VICE}'s~\texttt{milkyway} object assumes stellar populations 
are born at the centres of each annulus. For a stellar population born at a 
time~$T$ and Galactocentric radius~$R_\text{gal}$, it first searches for star 
particles from~\texttt{h277} that formed at~$T \pm$~250 Myr and~$R_\text{gal} 
\pm$~250 pc. It then randomly selects a star particle from this subsample with 
no bias to act as an~\textit{analog}. This stellar population then assumes the 
change in orbital radius~$\Delta R_\text{gal}$ of its analog at face value, 
and moves from its birth radius to the implied final radius at~$T$ = 12.2 Gyr 
with an assumed time dependence. If no candidate analogs are found, 
\texttt{VICE} widens the search to~$T \pm$~500 Myr and~$R_\text{gal} \pm$~500 
pc. If still no analog is found, then it finds the star particle 
with the smallest difference in birth radius still within a birth time of 
$T \pm$~500 Myr, and assigns it as the analog. 
While this prescription allows stellar populations to be assigned analogs with 
significantly different birth radii, this is only an issue for small~$T$ and 
large~$R_\text{gal}$ where there are few star particles from~\texttt{h277}, 
and where few stars form in nature anyway due to the inside-out growth of 
galaxies~\citep{Bird2013}. Furthermore, due to the similarity of the histograms 
in the top row of Fig.~\ref{fig:h277_decomposition}, we expect taking 
$\Delta R_\text{gal}$ from a star particle which formed at a similar time but 
different birth radius in these instance to be accurate enough for our 
purposes. 
\par 
Our models assume that the Galaxy is vertically and azimuthally well-mixed, and 
that the radial direction is the only one in which there are significant 
differences in composition. That is, each annulus extends from the disc 
midplane at~$z$ = 0 to~$z = \pm \infty$, and whether or not a star particle is 
in a given annulus does not depend on~$z$ at all. In fact, this information is 
\textit{not} used in integrating our models with~\texttt{VICE}. Instead, we 
simply assume that each stellar population in our models are located at the 
present day~$z_\text{final}$ of its assigned analog. Furthermore, when an 
\texttt{h277} star particle is assigned as an analog, it is~\textit{not} 
thrown out of the sample of candidate analogs, in theory allowing a star 
particle to act as an analog for multiple stellar populations. This is a 
subtle difference between the~\citet{Minchev2013} model and ours; where we 
assign star particles to stellar populations for which~\texttt{VICE} then 
calculates a stellar mass and composition based on an assumed SFH, the 
\citet{Minchev2013} uses a chemical evolution model to assign compositions to 
star particles.

% fig 2 
\begin{figure} 
\centering 
\includegraphics[scale = 0.45]{migration.pdf} 
\caption{A diagram illustrating how Galactocentric radius changes with time for 
two stellar populations under our migration schema: diffusion (crimson, solid), 
linear (lime, dot-dashed), post-process (black, dotted), and sudden (blue, 
dashed). Here the initial and final radii and birth times are chosen at random 
for illustrative purposes. With the initial and final Galactocentric radii of 
a stellar population, its birth time, and one of these assumptions regarding 
the time-dependence of radial migration, the Galactocentric radius at all times 
is known. } 
\label{fig:migration_schema} 
\end{figure}

With a known birth radius and time from our GCE model and an implied 
$\Delta R_\text{gal}$ from a stellar population's assigned analog, the final 
radius is known and the only missing piece of information is the 
time-dependence with which it moves there. In the present paper we consider 
four parameterized assumptions to describe this, each of which are illustrated 
conceptually in Fig.~\ref{fig:migration_schema}. 
\begin{itemize} 
	\item \textbf{Post-Processing}: Stars stay where they are born until the 
	final timestep, at which point they instantly migrate to their final 
	radius. This retains the assumption that stars do not contribute to 
	nucleosynthesis beyond their birth radius as employed in previous studies 
	\citep[e.g.][]{Minchev2013}. In this scenario, each annulus is treated as 
	a one-zone model independent of all other zones. We illustrate this case 
	with a black dotted line in Fig.~\ref{fig:migration_schema}.

	\item \textbf{Sudden}: A random number is drawn from a uniform distribution 
	between a stellar population's time of birth and the present day. That time 
	is taken to be the time of instantaneous migration to the present-day 
	annulus. This emulates a scenario in which a single dynamical interaction 
	changes a star's orbital radius, and be thought of mathematically as a 
	time-dependent extension of the post-processing scenario. We illustrate 
	this case with a blue dashed line in Fig.~\ref{fig:migration_schema}.

	\item \textbf{Diffusion}: Stars move to their final radii in a continuous, 
	time-dependent manner in this case. So named because it corresponds to a 
	scenario in which angular momentum diffuses via a random walk, under this 
	assumption, the mean displacement of stars that migrate similar distances 
	would scale with~$\sqrt{\text{age}}$. This is our 
	fiducial migration model, and we present results with this assumption 
	unless otherwise noted. This is qualitatively similar to 
	\citet{Frankel2018, Frankel2020}, who also model radial orbit migration 
	with a~$\sqrt{\tau}$ dependence. We illustrate this case with a red solid 
	line in Fig.~\ref{fig:migration_schema}.

	\item \textbf{Linear}: A simple variation of the diffusion model in which 
	the migration to the final radius scales linearly with age rather than with 
	$\sqrt{\text{age}}$. There is no physical motivation for this model other 
	than mathematical ease, but together with the diffusion model it 
	constitutes a test of how sensitive our conclusions are to the 
	time-dependence of stellar migration. We illustrate this case with a 
	green dot-dashed line in Fig.~\ref{fig:migration_schema}. 
\end{itemize} 
In all models, we neglect radial gas flows~\citep{Lacey1985, Bilitewski2012}, 
instead focusing on these simple assumptions describing how orbital radii 
change with time. While such an investigation would be an interesting extension 
of our study, we reserve it for future work. 
\par 
We emphasize that there is~\textit{no} N-body integration employed in our 
models aside from that which ran the~\texttt{h277} simulation. Furthermore, we 
use our sample of analog star particles from it~\textit{only} in determining 
$\Delta R_\text{gal}$ of each of our model stellar populations (see discussion 
in~\S~\ref{sec:methods:h277}). While~\texttt{h277} had its own SFH and chemical 
enrichment history, we make use of neither of these components here; rather, 
these are exactly what we seek to explore variations of. We acknowledge that 
stellar migration is often formulated using the processes ``blurring'' and 
``churning'', referring to a star's epicyclic motions and changes in the 
guiding center of its orbit~\citep[e.g.][]{Sellwood2002, Schoenrich2009, 
Minchev2011}; migration can also occur due to the overlap of spiral arm and 
bar resonances in the disc~\citep{Minchev2011}. We refrain from discussion of 
this approach here, because our models do not make use of such methodology. In 
the present paper, the orbital radii at all times are calculated and assumed at 
face value given one of the four assumptions detailed in the bullet list above. 
\par

\subsection{Nucleosynthetic Yields, Outflows, and Recycling} 
\label{sec:methods:yields} 
Nucleosynthesis proceeds in our models according to~\textit{fractional net} 
yields, as required by~\texttt{VICE}. That is, our yields quantify the mass 
of some element~$x$ ejected to the interstellar medium (ISM) in units of the 
progenitor stellar population's total initial mass, and only accounts for 
\textit{newly produced} nucleosynthetic material.~\texttt{VICE} takes into 
account the return of previously produced nucleosynthetic products with a 
separate implementation. In the present paper, we focus our analysis on 
alpha and iron-peak elements, taking oxygen (O) and iron (Fe) as the 
representative cases. The dominant enrichment channels of 
interest in our models are thus core collapse and type Ia supernovae 
\citep{Johnson2019}. Though we choose O and Fe, we expect 
similar results to be found for other alpha (e.g. Ne, Mg, Si) and iron-peak 
elements (e.g. Mn, Ni, Co), with purely quantitative differences reflective of 
the relative yields between elements. 
\par 
Enrichment from core collapse supernovae (CCSNe) happens immediately following 
the formation of progenitor stars in~\texttt{VICE}. This is an adequate 
approximation, because the lifetimes of massive stars are short compared to 
the relevant timescales for galaxy evolution. For the most massive stars, the 
lifetimes are comparable to the timestep size we adopt in this paper anyway. 
This assumption implies a linear relationship between the CCSN enrichment 
rate and the SFR: 
\begin{equation} 
\dot{M}_x^\text{CC} = y_x^\text{CC}\dot{M}_\star 
\end{equation} 
where~$y_x^\text{CC}$ is the CCSN yield of some element~$x$. Physically, this 
quantity represents the mass of an element~$x$ ejected to the interstellar 
medium (ISM) from all CCSNe events associated with a stellar population in 
units of the stellar population's initial mass. For example, if 
$y_x^\text{CC} = 0.01$, a hypothetical 100~\msun~stellar population would 
add 1~\msun~of~$x$ to the ISM immediately. This procedure neglects the mass 
that would be lost to outflows, which like recycling, have a separate 
implementation in~\texttt{VICE}. In this paper, we adopt~$y_\text{O}^\text{CC}$ 
= 0.015 and~$y_\text{Fe}^\text{CC}$~= 0.0012 from~\citet{Johnson2020}, who 
in turn adopt these values from~\citet{Weinberg2017}. 
\par 
SN Ia nucleosynthesis products are injected according to a~$t^{-1.1}$ DTD with 
a minimum delay time of~$t_\text{D}$ = 150 Myr. This is the default DTD in 
\texttt{VICE}, which was also adopted by~\citet{Johnson2020}, and is suggested 
by recent observational results comparing the cosmic SN Ia rate to the cosmic 
SFH~\citep{Maoz2012, Maoz2017}. In a one-zone model at times~$t > t_\text{D}$, 
the enrichment rate of some element~$x$~can be expressed as the product of 
some yield~$y_x^\text{Ia}$ and the SFH weighted by the DTD: 
\begin{subequations}\begin{align} 
\dot{M}_x^\text{Ia} &= y_x^\text{Ia}\langle\dot{M}_\star\rangle_\text{Ia} \\ 
&= y_x^\text{Ia}\ddfrac{
	\int_0^{t - t_\text{D}} \dot{M}_\star(t') R_\text{Ia}(t - t') dt' 
}{
	\int_{t_\text{D}}^{t_\text{max}} R_\text{Ia}(t')dt' 
} 
\label{eq:mdot_ia} 
\end{align}\end{subequations} 
where~$R_\text{Ia}$ is the DTD itself, which has units of~$M_\odot^{-1}$ 
Gyr$^{-1}$. Like the CCSN yield,~$y_x^\text{Ia}$ is the mass of some element 
$x$ produced over the SN Ia duty cycle in units of the progenitor stellar 
population's initial mass. It can also be expressed as an integral over the 
DTD: 
\begin{equation} 
y_x^\text{Ia} = m_x^\text{Ia} \int_{t_\text{D}}^{t_\text{max}} R_\text{Ia}(t') 
dt' = m_x^\text{Ia}\frac{N_\text{Ia}}{M_\star} 
\label{eq:y_x_ia} 
\end{equation} 
where~$m_x^\text{Ia}$ is the average mass of the element~$x$ produced in a 
single SN Ia event and the integral evaluates to the mean number of SN Ia 
events~$N_\text{Ia}$ per mass of stars formed~$M_\star$. \texttt{VICE} forces 
$t_\text{max}$~= 15 Gyr always, though provided one is consistent with 
equations~\refp{eq:mdot_ia} and~\refp{eq:y_x_ia}, the results are independent 
of~$t_\text{max}$ since the integrals cancel. 
\par 
Extending this formalism to multi-zone models is simple - rather than an 
integral over the star formation history of a given annulus, the rate becomes 
a sumation over all stellar populations that are in a given zone at some time: 
\begin{equation} 
\dot{M}_x^\text{Ia} = y_x^\text{Ia} \ddfrac{
	\sum_i M_i R_\text{Ia}(\tau_i) 
}{
	\int_{t_\text{D}}^{t_\text{max}} R_\text{Ia}(t')dt' 
} 
\label{eq:mdot_ia_multizone} 
\end{equation} 
where~$M_i$~and~$\tau_i$~are the mass and age of the~$i$'th stellar population, 
respectively. 
\par 
Initially, we adopt~$y_\text{O}^\text{Ia}$~= 0 and~$y_\text{Fe}^\text{Ia}$~= 
0.0017 from~\citet{Johnson2020}, who in turn adopt these values from 
\citet{Weinberg2017}. However, in practice we find that the e-folding 
timescales of star formation in our models are sufficiently long (see 
discussion in~\S~\ref{sec:methods:sfhs}) such that our fiducial, inside-out SFH 
model predicts [O/Fe]~$\approx$~+0.05 for young stars. We therefore multiply 
$y_\text{Fe}^\text{Ia}$~by~$10^{0.1}$, adopting instead~$y_\text{Fe}^\text{Ia}$ 
= 0.00214 in order for our fiducial model to predict a late-time [O/Fe] ratio 
in better agreement with observations. Although there is no motivation for such 
a change aside from this, this decision is likely within the uncertainties in 
SN Ia nucleosynthetic yields anyway. 
\par 
Our models assume that all supernova yields of O and Fe are independent of 
metallicity. While this appears to be empirically true in the Milky Way for O 
and Fe (\citealp{Weinberg2019};~\citealp*{Griffith2019}; 
\citealp{Griffith2020}), our CCSN yields are based on 
supernova explosion models in which all >8~\msun~progenitors produce a CCSN 
event~\citep[e.g.][]{Chieffi2004, Chieffi2013}. Recent findings with regard to 
black hole formation and stellar explodability have demonstrated that many 
massive stars instead collapse directly to a black hole (see theoretical 
discussion by, e.g.,~\citealp{Pejcha2015, Sukhbold2016, Ertl2016}, and 
observational evidence from~\citealp*{Gerke2015};~\citealp{Adams2017, 
Basinger2020}). Such effects would necessarily lower CCSN yields of all 
elements. While~\texttt{VICE} includes functionality with which to calculate 
$y_x^\text{CC}$~for some element~$x$~using built-in tables from supernova 
nucleosynthesis studies, an in-depth investigation of the impact of these 
effects is outside the scope of this paper. Such an investigation which expands 
the capabilities of~\texttt{VICE} will be presented in Griffith et al. (2021, 
in prep). 
\par 
With regard to our SN Ia yields,~\citet{Brown2019} demonstrate that the local 
specific SN Ia rate shows a strong, inverse dependence on galaxy stellar mass. 
They argue that this may imply a metallicity dependent~$R_\text{Ia}$ that 
produces more SN Ia events at early times when the metallicity is low. However, 
these metallicity are only present in our models at very early times. 
Furthermore, when outflows are taken into account, these yields are known to 
predict observationally plausible abundances~\citep{Andrews2017, Weinberg2017}. 
We find similar results in our models. 
\par 
\citet{Weinberg2017} demonstrate that, to first order, the nucleosynthetic 
yields of a given element and the strength of outflowing winds determine the 
late-time equilibrium abundance in the ISM. We retain their characterization 
of outflows here, in terms of a mass-loading factor~$\eta$~describing the ratio 
of the mass outflow to the SFR: 
\begin{equation} 
\eta \equiv \frac{\dot{M}_\text{out}}{\dot{M}_\star} 
\end{equation} 
Here we adopt a scaling of~$\eta$~with~$R_\text{gal}$~such that the late-time 
equilibrium abundance as a function of radius describes a metallicity 
gradient in agreement with observations;~\citet{Nidever2014} employ a similar 
methodology. 
\par 
The procedure outlined here makes two assumptions: 1) that the equilibrium 
abundance at a given radius corresponds to the mode of the observed MDF, and 2) 
that radial migration does not significantly alter the overall form of the 
gradient. We demonstrate that this holds in our models in~\S 
\ref{sec:obs_comp:gradient}. For alpha elements,~\citet{Weinberg2017} defines 
the equilibrium abundance under a constant SFH as: 
\begin{equation} 
Z_{\alpha,\text{eq}} = \frac{y_\alpha^\text{CC}}{1 + \eta(R_\text{gal}) - r} 
\end{equation} 
where~$r$~is the recycling parameter ($\approx$0.4 for the sake of this scaling 
with a~\citealp{Kroupa2001} IMF; see discussion in~\S~2.2 
of \citealp{Weinberg2017}). Solving for~$\eta(R_\text{gal})$ yields: 
\begin{equation} 
\eta(R_\text{gal}) = \frac{y_\alpha^\text{CC}}{Z_{\alpha,\text{eq}}} + r - 1 = 
\frac{y_\alpha^\text{CC}}{Z_{\alpha,\odot}}10^{-\text{mode([$\alpha$/H])}
(R_\text{gal})} + r - 1 
\end{equation} 
The metallicity gradient in the Milky Way has been the focus of a number of 
studies to date.~\citet{Nordstroem2004b} find a gradient of -0.099 kpc$^{-1}$ 
in [Fe/H] in main sequence stars from the Geneva Copenhagen Survey 
(\citealp{Nordstroem2004a};~\citealp*{Holmberg2007}).~\citet{Daflon2009} report  
-0.04 kpc$^{-1}$ in [S/H] in OB stars.~\citet{Frinchaboy2013} derive -0.09 
kpc$^{-1}$ in [M/H] in open clusters.~\citet{Hayden2014} also find -0.09 
kpc$^{-1}$ in [M/H] for~$R_\text{gal} \gtrsim$~6 kpc for low-$\alpha$ stars, 
but find the gradient to be relatively flat within~$R_\text{gal} \lesssim$~6 
kpc. \citet{Weinberg2019} report a gradient of -0.06 kpc$^{-1}$ in mode([Mg/H]) 
for upper red giant branch stars in the disc (see their Fig. 23). In tentative 
agreement with these studies, we adopt a slope of -0.08 kpc$^{-1}$. To set the 
normalization, we assume the mode([$\alpha$/H]) to be~$\sim$+0.3 at 
$R_\text{gal}$ = 4 kpc, since this would produce mode([$\alpha$/H])~$\approx$~0 
at~$R_\text{gal}$ = 7 - 9 kpc. This results in the following form for~$\eta$ 
as a function of Galactocentric radius: 
\begin{equation} 
\eta(R_\text{gal}) = \frac{y_\alpha^\text{CC}}{Z_{\alpha,\odot}} 
10^{(-0.08\text{ kpc}^{-1})(R_\text{gal} - 4\text{ kpc}) + 0.3} + r - 1 
\label{eq:eta_rgal} 
\end{equation} 
where we adopt our CCSN yield of O for~$y_\alpha^\text{CC}$ and the solar 
abundance of O of~$Z_{\text{O},\odot}$ = 0.00572 based on~\citet{Asplund2009}. 
We plot this adopted scaling in the top panel of Fig.~\ref{fig:eta_tau_sfh}, 
highlighting a value of~$\sim$2.15 for the solar circle with a red dotted line. 
This does assume a uniformly linear gradient at all~$R_\text{gal}$, in tension 
with the findings of~\citet{Hayden2014} who find it to flatten within~$\sim$6 
kpc. However, this procedure can be easily repeated for any desired gradient, 
since the functional form simply goes into the power of 10 in equation 
\refp{eq:eta_rgal}.

% fig 3 
\begin{figure} 
\centering 
\includegraphics[scale = 0.45]{eta_tau_sfh.pdf} 
\caption{\textbf{Top}: Our implemented scaling of the mass loading factor 
$\eta$~with Galactocentric radius (black) as defined by equation 
\refp{eq:eta_rgal}.~\textbf{Bottom}: The e-folding timescales of the star 
formation histories of our model galaxies (black). These values come from a 
fit to the~$\Sigma_\star$-age relation in bins of~$R/R_\text{e}$~for 
$10^{10.5}$~-~$10^{11}$~\msun~Sa/Sb Hubble type spiral galaxies as reported by 
\citet[][see discussion in~\S~\ref{sec:methods:sfhs}]{Sanchez2020}. The 
horizontal and vertical red dashed lines in both panels highlight a mass 
loading factor of~$\eta \approx$~2.15 and a star formation timescale of 
$\tau_\text{sfh} \approx$~15 Gyr at an assumed radius of the sun of 
$R_\odot$ = 8 kpc. } 
\label{fig:eta_tau_sfh} 
\end{figure}

Both AGB star enrichment and the recycling of previously produced metals in 
this paper proceed as they did in~\citet{Johnson2020}, with the caveat that the 
mass is added to the annulus that a stellar population is in at a given time, 
which may or may not be the annulus it was born in. Recycling proceeds 
according to the~\citet{Kalirai2008} initial-remnant mass relation assuming a 
\citet{Kroupa2001} IMF and a mass-lifetime relationship of 
$\tau = 1.1\tau_\odot(M/M_\odot)^{-3.5}$, where~$\tau_\odot$~= 10 Gyr is the 
main sequence lifetime of the sun and the factor of 1.1 accounts for the 
post-main sequence lifetime.~\texttt{VICE} in its current version forces an AGB 
enrichment channel in all models; it is thus included in the present paper. For 
this enrichment channel, we adopt the net yields sampled on a table of stellar 
initial mass and metallicity from the FRUITY database \citep{Cristallo2011}. 
However, the AGB star yields of O and Fe are negligible compared to their 
supernova yields; we therefore conclude discussion of this component of our 
models here. 
\par

\subsection{Star Formation Histories} 
\label{sec:methods:sfhs} 
\texttt{VICE} handles models in either infall, star formation, or gas mode, 
referring simply to which component of the evolutionary history the user has 
specified. The starburst models presented in~\citet{Johnson2020} ran in infall 
mode, but here we run~\texttt{VICE} in star formation mode, because we are 
after specific forms for the star formation histories of our models. In 
Appendix~\ref{sec:normalize_sfh}, we present justification of how we normalize 
the parameters of our star formation histories to produce a realistic model 
Galaxy at the present day. In short, it takes in a unitless description of the 
dependence of the SFH at a given Galactocentric radius, denoted 
$f(t|R_\text{gal})$, and a unitless description of the present day stellar 
surface density gradient, denoted~$g(R_\text{gal})$. We integrate 
$f(t|R_\text{gal})$ with time for each annulus, assuming~$R_\text{gal}$ to 
correspond to the centre of the zone, and attach a prefactor to 
$f(t|R_\text{gal})$ in each annulus such that the desired gradient is achieved 
with a total stellar mass similar to the Milky Way. This procedure neglects the 
impact of radial migration, assuming that it does not significantly alter the 
form of~$g(R_\text{gal})$. We demonstrate that these assumptions hold in~\S 
\ref{sec:methods:surface_density_gradient}, in which we also detail our 
adopted form of~$g(R_\text{gal})$. As long as this assumption is not violated, 
the equation derived in Appendix~\ref{sec:normalize_sfh} can be used to 
calculate these prefactors for future models of Milky Way-like galaxies. 
\par 
In the present paper, we present four fiducial SFHs, which we dub ``constant'', 
``inside-out'', ``late-burst'', and ``outer-burst''. They're defined as 
follows: 
\begin{itemize} 
	\item \textbf{Constant}: The SFH at a given radius is time-independent. 
	\begin{equation} 
	f_\text{C}(t|R_\text{gal}) = 1 
	\label{eq:constant_sfh} 
	\end{equation} 
	This case is of particular theoretical interest because it quantifies the 
	effect of stellar migration while removing the impact of a time-dependent 
	SFH.

	\item \textbf{Inside-Out}: This is our fiducial SFH. 
	\begin{equation} 
	f_\text{IO}(t|R_\text{gal}) = (1 - e^{-t / \tau_\text{rise}}) 
	e^{-t / \tau_\text{sfh}} 
	\label{eq:insideout_sfh} 
	\end{equation} 
	We adopt this mathematical form over a more traditional 
	linear-times-exponential characterization, because the latter does not 
	offer control over the position of the maximum SFR. The form we adopt has 
	a maximum near~$\tau_\text{rise}$, for which we adopt a value of 2 Gyr 
	everywhere here. This produces a peak in star formation at lookback times 
	of~$\sim$10 Gyr, roughly corresponding to a redshift of~$z \approx$~2, in 
	agreement with observational results on the cosmic SFH~\citep{Madau2014}. 
	In this paper,~$\tau_\text{sfh}$ is a function of~$R_\text{gal}$, discussed 
	in this section. We present results assuming this model throughout this 
	paper except in cases where a different SFH impacts the predictions.

	\item \textbf{Late-Burst}: In this model, the inside-out SFH is modified to 
	exhibit a recent, gradual burst in star formation described by a Gaussian: 
	\begin{equation} 
	f_\text{LB}(t|R_\text{gal}) = f_\text{IO}(r|R_\text{gal}) 
	(1 + A_be^{-(t - t_b)^2/2\sigma_b^2}) 
	\label{eq:lateburst_sfh} 
	\end{equation} 
	$A_b$ is a dimensionless parameter describing the strength of the 
	starburst,~$t_b$ is the time of the local maximum in the SFH during the 
	burst, and~$\sigma_b$ is the width of the Gaussian describing it. This 
	model being loosely motivated by the findings of~\citet{Mor2019} and 
	\citet{Isern2019}, we adopt~$A_b$ = 1.5,~$t_b$ = 10.2 Gyr, and 
	$\sigma_b$ = 1 Gyr, finding in practice that~$A_b$ = 1.5 produces a 
	local maximum SFR that is a factor of~$\sim$2 larger than the preceding 
	local minimum.

	\item \textbf{Outer-Burst}: A variation of the late-burst model in which 
	only~$R_\text{gal} \geq$~6 kpc experience the starburst. This is loosely 
	motivated by the findings of~\citet{Vincenzo2020} where a hydrodynamical 
	simulation of a Milky Way-like galaxy showed radially dependent infall. 
	\begin{equation} 
	f_\text{OB}(t|R_\text{gal}) = \begin{cases} 
	f_\text{IO}(t|R_\text{gal}) & (R_\text{gal} < 6\text{ kpc}) \\ 
	f_\text{LB}(t|R_\text{gal}) & (R_\text{gal} \geq 6\text{ kpc}) 
	\end{cases} 
	\label{eq:outerburst_sfh} 
	\end{equation} 
\end{itemize} 
Although we do not consider such models here, an investigation into the impact 
of more episodic star formation histories would be an interesting extension of 
the present paper. For example,~\texttt{VICE} has all of the necessary 
capabilities to handle models in which major episodes of star formation 
coincide with close passages of the Sagittarius dwarf 
\citep[e.g.][]{RuizLara2020}. 
\par 
We derive the scaling of the e-folding timescales of star formation 
$\tau_\text{sfh}$ with~$R_\text{gal}$ from the data in~\citet{Sanchez2020}. 
They present the stellar surface density~$\Sigma_\star$ as a function of age 
in bins of~$R/R_\text{e}$ for MaNGA galaxies, where~$R_\text{e}$ is the 
half-light radius. Here we take their~$M_\star = 10^{10.5} - 10^{11}$ 
\msun~ bin for Sa/Sb spirals and simultaneously fit the normalization and 
e-folding timescale~$\tau_\text{sfh}$ of our~$f_\text{IO}(t|R_\text{gal})$ form 
to the data. Although the normalization is irrelevant to our models and 
determined via the method outlined in Appendix~\ref{sec:normalize_sfh}, we 
adopt the resulting~$\tau_\text{sfh}-R_\text{gal}$ relation in our models. With 
our adopted stellar surface density gradient (see discussion in~\S 
\ref{sec:methods:surface_density_gradient}), we know the present-day half-mass 
radius to be very near 4 kpc. The findings of~\citet{Garcia-Benito2017} and 
\citet{GonzalezDelgado2014} suggest that half-light radii are marginally larger 
than half-mass radii. Based on equation (4) of~\citet{GonzalezDelgado2014} 
relating the two for circular apertures, we expect our model Galaxy to have a 
half-light radius near 5 kpc. We therefore adopt~$R_\text{e}$ = 5 kpc to 
convert the~$\tau_\text{sfh}-R_\text{gal}/R_\text{e}$ relation resulting from 
our fit to the~\citet{Sanchez2020} data into a~$\tau_\text{sfh}-R_\text{gal}$ 
relation. {\color{red} If there are references suggesting a similar value for 
the Milky Way, we should note them here. } 
\par 
We illustrate this relationship in the bottom panel of Fig. 
\ref{fig:eta_tau_sfh}, noting that the resulting timescales are long, 
particularly for the outer Galaxy. With a red dotted line, we highlight a value 
of~$\tau_\text{sfh} \approx$~15 Gyr at an assumed orbital radius of the sun of 
$R_\odot$ = 8 kpc. Although these timescales at most radii are considerably 
longer than a Hubble time, this is no cause for worry; this simply means that 
these regions of the Galaxy in our models experience less than 1 e-folding in 
their SFR, and that in the outer Galaxy the SFH is nearly constant after the 
initial rise in the first~$\sim$2 Gyr. It is nonetheless interesting that 
these timescales are considerably longer than that derived for the cosmic 
SFH~\citep{Madau2014}.

% fig 4 
\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{evol.pdf} 
\caption{The surface densities of star formation~$\dot{\Sigma}_\star$ (top 
row), infall $\dot{\Sigma}_\text{in}$ (middle row), and gas~$\Sigma_\text{g}$ 
(bottom row) as functions of simulation time for our four fiducial SFHs: 
constant (far left), inside-out (left middle), late-burst (right middle), and 
outer-burst (far right). We plot curves for the annuli whose inner radii are 
3 kpc (grey), 5 kpc (black), 7 kpc (red), 9 kpc (yellow), 11 kpc (green), 13 
kpc (blue), and 15 kpc (purple) (see equations~\refp{eq:constant_sfh}, 
\refp{eq:insideout_sfh},~\refp{eq:lateburst_sfh}, and~\refp{eq:outerburst_sfh} 
for the mathematical definition of each SFH). 
}
\label{fig:evol} 
\end{figure*}

We plot the resultant SFHs or our models in the top row of Fig.~\ref{fig:evol} 
for a handful of radii. At all timesteps, the gas supply is known via the star 
formation efficiency timescale~$\tau_\star$ (see discussion in~\S 
\ref{sec:methods:sfe}). This quantity is illustrated in the bottom row of 
Fig.~\ref{fig:evol}.~\texttt{VICE} automatically calculates the implied infall 
rate by comparing the amount of gas lost to outflows and star formation in a 
given timestep to that which is required to sustain the user-specified level of 
star formation at the next timestep; we assume the infalling gas to be of zero 
metallicity at all times. This quantity is shown in the middle row of Fig. 
\ref{fig:evol}.

\subsection{Star Formation Efficiency} 
\label{sec:methods:sfe} 
The term ``star formation efficiency'' (SFE) is somewhat overloaded in the 
literature. In the star formation and feedback community, it usually 
refers to the fraction of a molecular cloud's mass which will eventually be 
converted into stars. In the chemical evolution literature, however, it 
typically refers to the inverse timescale relating the SFR within some star 
forming reservoir and the mass of gas in that region: 
$\tau_\star \equiv \Sigma_\text{g}/\dot{\Sigma}_\star$. High (Low) values of 
$\tau_\star$ indicate slow (fast) star formation and thus low (high) SFE; when 
we refer to SFE here, we're referring to the definition based on this 
timescale. In the star formation and feedback literature, this is often 
referred to as the ``depletion time''. 
\par 
Based on the findings of~\citet{Kennicutt1998}, it is common practice in the 
chemical evolution literature a single power-law describing the relationship 
between the surface densities of gas and star formation~$\Sigma_\text{g}$ and 
$\dot{\Sigma}_\star$, often referred to as the star formation law or the 
Kennicutt-Schmidt relation: 
\begin{equation} 
\dot{\Sigma}_\star \sim \Sigma_\text{g}^N 
\end{equation} 
\citet{Kennicutt1998} derive~$N = 1.4 \pm 0.15$ relating the total 
$\dot{\Sigma}_\star$~and~$\Sigma_\text{g}$~within the disc across a sample of 
quiescent spiral galaxies and infrared and circumnuclear starbursts. However, 
recent studies have found evidence that much of the observed scatter in this 
relation is physical in origin~\citep{delosReyes2019} and that there are 
significant breaks in both the power-law index and zero-points 
\citep{Kennicutt2020}. Much of the uncertainty surrounding the details of the 
star formation law is a consequence of the ongoing debate about the CO-to-H$_2$ 
conversion factor (\citealp{Kennicutt2012};~\citealp*{Liu2015}). Although 
\citet{Ellison2020a} demonstrate that there are significant galaxy-to-galaxy 
variations in the star formation law, suggesting that individual galaxies do 
not follow the population averaged trend,~\citet{delosReyes2019} argue that 
this is still a reasonable recipe for Galaxy evolution models. We adopt such a 
formalism here. 
\par 
\citet{Krumholz2018} compare model-predicted star formation laws to the 
observations of~\citet{Bigiel2010} and~\citet{Leroy2013} (see their Fig. 2). We 
find that the following by-eye fit to the power-law index~$N$~is a reasonble 
description of the aggregate data: 
\begin{equation} 
N = \begin{cases} 
1.0 & (\Sigma_\text{g} \geq \Sigma_{\text{g},2}) \\ 
3.6 & (\Sigma_{\text{g},1} \leq \Sigma_\text{g} \leq \Sigma_{\text{g},2}) \\ 
1.7 & (\Sigma_\text{g} \leq \Sigma_{\text{g},1}) 
\end{cases} 
\label{eq:sf_law_indeces} 
\end{equation} 
where~$\Sigma_{\text{g},1} = 5\times10^6$~\msun~\persqkpc~and 
$\Sigma_{\text{g},2} = 2\times10^7$~\msun~\persqkpc. The apparent linearity of 
the relationship above~$\sim2\times10^7$~\msun~\persqkpc~suggests that in this 
regime, star formation proceeds at the fastest possible rate, and that 
$\tau_\star \equiv \Sigma_\text{g}/\dot{\Sigma}_\star$~= constant. The 
observations of~\citet{Leroy2013} and~\citet{Kennicutt2020} would suggest that 
these are the 
surface densities at which the molecular fraction~$f_\text{mol} = M_{\text{H}_2} 
/ (M_{\text{H}_2} + M_\text{HI}) \approx$~1. We therefore adopt the assumption 
that above~$\Sigma_\text{g} = 2\times10^7$~\msun~\persqkpc,~$\tau_\star$ 
reaches its minimum value, and increases with decreasing~$f_\text{mol}$. We 
denote this value as~$\tau_\text{mol}$, the value of~$\tau_\star$ for a gas 
reservoir with~$f_\text{mol}$~= 1. This, combined with our three-component 
power-law index N results in the following final form for our adopted star 
formation law: 
\begin{equation} 
\dot{\Sigma}_\star = \begin{cases} 
\Sigma_\text{g} \tau_\text{mol}^{-1} & 
(\Sigma_\text{g} \geq \Sigma_{\text{g},2}) 
\\ 
\Sigma_\text{g} \tau_\text{mol}^{-1} \left(\frac{
	\Sigma_\text{g}
}{
	\Sigma_{\text{g},2} 
}\right)^{2.6} & 
(\Sigma_{\text{g},1} \leq \Sigma_\text{g} \leq \Sigma_{\text{g},2}) 
\\ 
\Sigma_\text{g} \tau_\text{mol}^{-1} \left(\frac{
	\Sigma_{\text{g},1} 
}{
	\Sigma{\text{g},2} 
}\right)^{2.6}\left(\frac{
	\Sigma_\text{g}
}{
	\Sigma_{\text{g},1} 
}\right)^{0.7} & 
(\Sigma_\text{g} \leq \Sigma_{\text{g},1}) 
\end{cases} 
\label{eq:sf_law} 
\end{equation} 
where we choose the power-law indeces such that this formalism is consistent 
with equation~\refp{eq:sf_law_indeces}, and prefactors are added to ensure 
piece-wise continuity. In implementation,~\texttt{VICE} requires the 
$\tau_\star-\dot{\Sigma}_\star$ relation when ran in star formation mode and 
the~$\tau_\star-\Sigma_\text{g}$ relation when ran in infall and gas modes. 
Both follow algebraically from this relationship given the substitution 
$\tau_\star \equiv \Sigma_\text{g} / \dot{\Sigma}_\star$. 
\par 
Although it is more physically motivated to use an adopted star formation law 
to infer a star formation rate from the ISM properties at a given timestep, as 
discussed in~\S~\ref{sec:methods:sfhs}, we are using~\texttt{VICE} in star 
formation mode. This means that it is~$\dot{\Sigma}_\star$ which is specified 
\textit{a priori} by our models - not~$\Sigma_\text{g}$. That is,~\texttt{VICE} 
is inferring~$\Sigma_\text{g}$ from~$\dot{\Sigma}_\star$ in our models, not 
the other way around. While we acknowledge the findings of~\citet{Ellison2020b}, 
this another reason we must invoke a simple parameterization for the star 
formation law, which~\citet{Kennicutt2020} argue is still a reasonable 
approach. This decision also means that changing our assumptions about the 
star formation law do not impact our SFHs, instead impacting the inferred 
$\Sigma_\text{g}$ as a function of radius and time. 
\par 
Based on the observed Kennicutt-Schmidt at different redshifts, 
\citet{Tacconi2018} suggest that~$\tau_\text{mol}$ should scale with redshift 
$z$ and the deviation from the star forming main sequence~$\delta$MS via 
$\tau_\text{mol} \propto (1 + z)^{-0.6}\delta\text{MS}^-0.44$. We don't take 
into account the effect of~$\delta$MS in our models, but we do investigate the 
redshift dependence. A reasonable approximation to the~$t - z$ relation out to 
$z \approx$~3 assuming typical~$\Lambda$CDM cosmology is given by: 
\begin{equation} 
\frac{t}{t_0} \approx (1 + z)^{-5/4} 
\end{equation} 
where~$t_0$ is the present-day age of the universe, and~$t$ is not simulation 
time but the age of the universe. Plugging this relation into the 
\citet{Tacconi2018} scaling yields the following time-dependence for 
$\tau_\text{mol}$: 
\begin{equation} 
\tau_\text{mol} = \tau_{\text{mol},0}(t/t_0)^{12/25} \approx 
\tau_{\text{mol},0}(t/t_0)^{1/2} 
\end{equation} 
where~$\tau_{\text{mol},0}$ is simply~$\tau_\text{mol}$ at the present day. We 
generalize this formula to the following form: 
\begin{equation} 
\tau_\text{mol} = \tau_{\text{mol},0}(t/t_0)^\gamma 
\label{eq:tau_mol}
\end{equation} 
In this paper we present models which adopt~$\tau_{\text{mol},0}$ = 2 Gyr 
\citep{Leroy2008, Leroy2013, Tacconi2018} and~$\gamma$ = 1/2 based on this 
argument. We have also ran simulations which adopt~$\tau_{\text{mol},0}$ = 1 
Gyr and~$\gamma$ = 0 (a time-independent~$\tau_\text{mol}$), and found similar
results. In all timesteps an annnuli,~\texttt{VICE} infers~$\Sigma_\text{g}$ 
from~$\dot{\Sigma}_\star$ given our equations~\refp{eq:sf_law} and 
\refp{eq:tau_mol}.

% fig 5 
\begin{figure} 
\centering 
\includegraphics[scale = 0.45]{sfe.pdf} 
\caption{The star formation efficiency timescale~$\tau_\star$ as a function of 
Galactocentric radius at simulation times of 2 Gyr (red), 4 Gyr (yellow), 
6 Gyr (green), 8 Gyr (blue), 10 Gyr (purple), and 12.2 Gyr (the present day, 
black) predicted by our inside-out SFH model. } 
\label{fig:sfe} 
\end{figure}

In Fig.~\ref{fig:sfe}, we plot~$\tau_\star$ as a function of~$R_\text{gal}$ at 
six different time stamps predicted by our fiducial, inside-out SFH model. At 
$R_\text{gal} \lesssim$ 6 kpc,~$\tau_\star$ is near~$\tau_\text{mol}$ at all 
times, implying a molecular fraction of unity at these radii. Although this 
prediction is likely unrealistic because 21-cm line observations suggest the 
presence of neutral hydrogen as close to the Galactic centre as several hundred 
pc~\citep{Kalberla2009}, we find in practice that changing our assumptions 
about the star formation law does not impact our conclusions. In collecting 
results for this paper, we investigated purely linear, purely power-law, and 
broken power-law characterizations, finding similar predictions in all cases. 
In general we find that the detailed form of the SFH, and to some extent the 
time-dependence of radial migration, exert much greater power in establishing 
the model predictions than does the star formation law. Nonetheless it is an 
interesting result that a~$\dot{\Sigma}_\star - \Sigma_\text{g}$ relation 
informed by the observed, population averaged trend and the normalization of 
our SFHs implied by the stellar mass of the Milky Way predicts such a 
discrepancy with the observed HI distribution. We refrain from further 
discussion of this with the finding that it doesn't impact the conclusions 
detailed in the present paper.

\subsection{Surface Density Gradient} 
\label{sec:methods:surface_density_gradient}

% fig 6 
\begin{figure} 
\centering 
\includegraphics[scale = 0.45]{surface_density_gradient.pdf} 
\caption{The surface density of gas (blue) and stars (red) as predicted by our 
inside-out SFH model. The dotted black line with the higher normalization 
denotes a thin disc profile with scale length~$R_t$ = 2.5 kpc; the other 
denotes a thick disc profile with scale length~$R_T$ = 2.0 kpc, and a ratio of 
$\Sigma_T/\Sigma_t$~= 0.27 at~$R_\text{gal}$~= 0. The solid black line denotes 
the sum of the two; this is the surface density gradient of the Milky Way as 
reported by~\citet{Bland-Hawthorn2016}, renormalized to imply the same total 
stellar mass within the disc as our models. } 
\label{fig:surface_density} 
\end{figure}

As discussed in~\S~\ref{sec:methods:sfhs}, Appendix~\ref{sec:normalize_sfh} 
presents justification of a recipe in which we select a unitless function 
describing the stellar surface density gradient~$g(R_\text{gal})$. In setting 
the normalization, our model ensures that the integral of~$g(R_\text{gal})$ 
over the surface area of the disc predicts a total stellar mass in agreement 
with that observed for the Milky Way. For this value, we adopt 
$M_\star^\text{MW} = (6.08 \pm 1.14)\times10^{10}$~\msun~\citep{Licquia2015}. 
This is the total stellar mass of the Galaxy, including the bulge; 
\citet{Licquia2015} report~$(5.17 \pm 1.11)\times10^{10}$~\msun~as the mass of 
the disc alone. Although we aren't modeling the bulge here, our model extends 
to~$R_\text{gal}$ = 0 and our sample of candidate analog star particles from 
\texttt{h277} includes those with bulge-like kinematics. 
\par 
In this paper we adopt the following double exponential form for 
$g(R_\text{gal})$, describing the thin and thick disc components of the 
Galaxy: 
\begin{equation} 
g(R_\text{gal}) = e^{-R_\text{gal}/R_t} + \frac{\Sigma_T}{\Sigma_t} 
e^{-R_\text{gal}/R_T} 
\label{eq:gradient} 
\end{equation} 
where~$R_t$~and~$R_T$~are the scale radii of the thin and thick discs, 
respectively, and~$\Sigma_T/\Sigma_t$~is the ratio of their surface densities 
at~$R_\text{gal}$~= 0. We adopt~$R_t$~= 2.5 kpc,~$R_T$~= 2.0 kpc, and 
$\Sigma_T/\Sigma_t$~= 0.27 based on the findings of~\citet{Bland-Hawthorn2016}. 
We plot the single exponential forms of each disc component as a dotted black 
line in Fig.~\ref{fig:surface_density}, with the solid black line denoting the 
sum of the two. Althoug these scale radii are smaller than the commonly adopted 
scale radius for a single exponential disc of~$r_s \approx$~3 kpc 
\citep[e.g.][]{Binney2008}, our choice of a double exponential disc here 
necessitates a choice be made for not one but two scale radii. 
\par 
We plot the resultant surface density gradients from our fiducial, inside-out 
SFH model in Fig.~\ref{fig:surface_density} as well, with red denoting the 
stellar gradient and the gas in blue. We note that the stellar gradient very 
nearly follows our target gradient denoted by the solid black line and 
expressed by equation~\refp{eq:gradient}. Stellar migration has indeed not 
altered the overall form of the gradient, simply introducing scatter around the 
adopted trend. Although there are slight enhancements at small~$R_\text{gal}$ 
and deficits at large~$R_\text{gal}$, the agreement is excellent in the regions 
of the Galaxy where the gradient is best constrained observationally. The 
$R_\text{gal}$ > 15.5 kpc populations are also composed entirely of stars that 
migrated there, since that is the radius at which we shut of star formation; 
with this mind, the under-prediction at these radii is unsurprising. 
Furthermore, in this paper we are interested primarily in the~$R_\text{gal}$~= 
3 - 15 kpc range anyway, since this is the region where disc stars are the 
dominant populations. We also note that the gas gradient
shows a break in the scale radius near~$R_\text{gal} \approx$ 
6 kpc. This is a consequence of our adopted star formation law; at 
$\Sigma_\text{g} = 2\times10^7$~\msun~\persqkpc~the relation changes from 
linear at higher densities to~$\dot{\Sigma}_\star \sim \Sigma_\text{g}^{3.6}$ 
at lower densities (see discussion in~\S~\ref{sec:methods:sfe}). Because we are 
running~\texttt{VICE} in star formation mode, it's more accurate to say that 
$\Sigma_\text{g}$~is a weak function of~$\dot{\Sigma}_\star$~at 
$\Sigma_\text{g} \leq 2\times10^7$~\msun~\persqkpc~in this range as opposed to 
$\dot{\Sigma}_\star$~being a strong function of~$\Sigma_\text{g}$. When looking 
at the present-day gradient, this presents as a flattening of the gradient at 
the radius where~$\Sigma_\text{g} = 2\times10^7$~\msun~\persqkpc; further 
inspection along the y-axis of Fig.~\ref{fig:surface_density} confirms that 
this break indeed occurs at this value of~$\Sigma_\text{g}$. 
\par 
Although we adopt the~\citet{Licquia2015} stellar mass of the Milky Way here, 
we find similar results when taking a value which differs by an order of 
magnitude. While mass typically cancels in one-zone models of chemical 
evolution, the abundances instead determined by the evolutionary parameters 
(e.g.~$\eta$~and~$\tau_\star$), this value sets the normalization of the 
SFH~$\dot{\Sigma}_\star(t, R_\text{gal})$ in our models. In turn this impacts 
the surface densities of gas~$\Sigma_\text{g}$ inferred at each timestep, and 
thus the abundances to some extent. This choice only matters insofar as the 
choice of star formation law matters, which we find to not impact our 
conclusions.

\subsection{Summary} 
\label{sec:methods:summary} 
In summary, our fiducial model has an inside-out SFH with e-folding timescales 
derived from the observations of~\citet[][see discussion in~\S 
\ref{sec:methods:sfhs}]{Sanchez2020}. Radial migration proceeds in a manner in 
which our model stellar populations have a change in radius 
$\Delta R_\text{gal}$ informed from the~\texttt{h277} hydrodynamical simulation 
\citep[][see discussion in~\S~\ref{sec:methods:h277}]{Christensen2012, 
Zolotov2012, Loebman2012, Loebman2014, Brooks2014}. In the base-line model, 
stars move to their final radius with a~$\sqrt{\text{age}}$~dependence 
(\citealp{Frankel2018, Frankel2020} model stellar migration with a similar 
characterization; see discussion in~\S~\ref{sec:methods:migration}). Using 
\texttt{VICE} to calculate abundances for O and Fe in this paper, our supernova 
yields are adopted from~\citet{Johnson2020}, who in turn take these values from 
\citet{Weinberg2017}. Outflows are characterized such that the equilibrium 
abundance of oxygen under a constant SFH follows an abundance gradient in 
agreement with observational results in the Milky Way (see discussion in 
\S~\ref{sec:methods:yields};~\citet{Nidever2014} make use of similar 
methodology). Our star formation law is based on the~\citet{Bigiel2010} and 
\citet{Leroy2013} data presented in comparison with theoretical models in 
\citet[][see discussion in~\S~\ref{sec:methods:sfe}]{Krumholz2018}. To describe 
the stellar surface density gradient, we adopt the two-exponential form 
describing the thin and thick discs from~\citet[][see discussion in~\S 
\ref{sec:methods:surface_density_gradient}]{Bland-Hawthorn2016}. 
\par 
Our quality cuts imposed on the star particles from~\texttt{h277} yields a 
sample of 3,000,556 candidate analog star particles (see discussion in~\S 
\ref{sec:methods:h277}), only~$\sim$57\% of which have disc-like kinematics 
at the present day. Since we're modeling the thin and thick disc populations 
here,~$\sim$1.71 million is a much better estimate of the number of star 
particles that we can realistically sample from. We take~$\Delta R_\text{gal}$ 
= 100 pc as the width of each annulus from~$R_\text{gal} = 0$~to 20 kpc and a 
timestep size of~$\Delta T$~= 10 Myr from~$T = 0$~to 12.2 Gyr. With the 
resulting 200 zones and 1,221 timesteps, we let~\texttt{VICE} form~$n = 9$ 
stellar populations per annulus per timestep, resulting in 2,197,000 total 
stellar populations with predicted masses and abundances. While this is more 
than the number of disc particles in our sample of candidate analogs, we force 
the star formation rate to zero beyond~$R_\text{gal}$ = 15.5 kpc; while these 
stellar populations exist within~\texttt{VICE} and are a part of the 
computational overhead, they have zero mass and thus do not contribute to the 
chemical evolution in our models. This results in 1,692,306 stellar 
populations with~\textit{non-zero} masses and abundances predicted by 
\texttt{VICE}, reasonably within the limit of what we can sample. These 
simulations run in~$\sim$2.5 hours and take up~$\sim$235 MB of disc space per 
output, including the extra data that we record for each stellar population's 
analog star particle. Lastly, we adopt a~\citet{Kroupa2001} IMF throughout this 
paper. 
\par 
We have ran~\texttt{VICE} for all four of our SFHs, all four migration 
models, and all four variations in~$\tau_\text{mol}$ noted in~\S 
\ref{sec:methods:sfe} - a total of 64 simulations, as well as a variety of 
other test cases. In this paper, we present results wherever the model 
prescriptions are sensitive to the assumptions. However, in general the 
differences can be understood with only the variations in star formation 
history and the qualitative notion that many stars have moved beyond their 
birth radius. \texttt{VICE} calculates abundances for nearly 2 million stellar 
populations per model; to ensure that resolution does not impact our 
conclusions, we have also ran variations with~$n$~= 2 stellar populations per 
zone per timestep, and found similar results in all cases.

\section{Comparison to Observations} 
\label{sec:obs_comp}

% fig 7 
\begin{figure*} 
\centering 
\includegraphics[scale = 0.28]{ofe_feh_densitymap.pdf} 
\caption{[O/Fe]-[Fe/H] diagrams for 15 Galactic regions spanning five bins in 
$R_\text{gal}$ and~$\left|z\right|$. Each region has its own panel, with 
radial bins shown in columns denoted at the top, and with bins in 
$\left|z\right|$ shown in rows denoted in text in the middle column. For each 
region, we plot~$N$~= 10,000 points sampled from our simulated stellar 
populations predicted by our inside-out SFH model, where the probability of 
sampling is proportional to the present-day mass of each stellar population. 
In all panels, points are colour-coded according to the Galactocentric radius 
of birth of the stellar population. For reference, we plot in a solid black 
line in all panels the gas-phase [O/Fe]-[Fe/H] track predicted by the same 
SFH in the~$R_\text{gal}$ = 8 kpc annulus, but with the post-processing 
migration model; this curve is the same in all panels. } 
\label{fig:ofe_feh_diagram} 
\end{figure*}

We begin the comparison of our model predictions to observational data with the 
distribution of stellar populations in the [O/Fe]-[Fe/H] plane. We separate 
stars into bins based on their present-day Galactic regions defined by five 
bins in~$R_\text{gal}$ (3 - 5, 5 - 7. 7 - 9, 9 - 11, and 11 - 13 kpc) and three 
bins in~$\left|z\right|$ (0 - 0.5, 0.5 - 1, and 1 - 2 kpc). Within each of the 
resulting 15 regions, we sample 10,000 stars at random from our base-line 
inside-out SFH model. Since stars in~\texttt{VICE} are stand-ins for entire 
stellar populations, we let the probability of sampling one of them be 
proportional to its present day mass. We plot the results of this procedure in 
Fig.~\ref{fig:ofe_feh_diagram}, colour-coding each stellar population by its 
birth radius; for reference, we also plot the gas-phase track which resulted 
from the~$R_\text{gal}$ = 8 kpc annulus with the post-processing migration 
model in a black solid line in all panels. 
\par 
In Fig.~\ref{fig:ofe_feh_diagram}, we note that high-$\alpha$~sequence stars 
are predicted to be the dominant population at small~$R_\text{gal}$ and high 
$\left|z\right|$; conversely, the low-$\alpha$~sequence dominates the 
statistics at large~$R_\text{gal}$~and low~$\left|z\right|$. This is consistent 
with the observational results of~\citet{Hayden2015}, who present a density map 
in the [O/Fe]-[Fe/H] for the same Galactic regions (see their Fig. 4). 
Furthermore, the locus of the low-$\alpha$ sequence shifts from super-solar 
[Fe/H] to sub-solar [Fe/H] with increasing~$R_\text{gal}$, a shift which is 
expected given the abundance gradient that we have built into our models (see 
discussion in~\S~\ref{sec:methods:yields}). The colour-coding of the points 
further suggests that the width of the low-$\alpha$~sequence arises out of 
stellar migration. Though this wouldn't occur in our models without mixing, it 
is to some extent expected from that in combination with the built-in gradient. 
Nonetheless this theoretical interpretation of the low-$\alpha$ sequence is 
consistent with the arguments of~\citet{Schoenrich2009} and~\citet{Nidever2014}. 
\par 
We clarify that we do not claim to recover the bimodality in [$\alpha$/Fe] as 
observed here. Although there are authors who argue to have successfully 
reproduced such results using an inside-out SFH with stellar migration 
\citep[e.g.][]{Sharma2020}, we find that our fiducial model fails to reproduce 
these results (see discussion in~\S~\ref{sec:obs_comp:ofe_dists}). These 
results do nonetheless suggest that the spatial dependence of the two sequences 
can be attributed to stellar migration. Lastly, we note that we find similar 
results with our other three SFHs, increasing confidence in our argument that 
migration establishes such a spatial dependence rather than the SFH. The only 
notable difference is that the starburst models predict a slightly higher 
characteristic [O/Fe] for the low-$\alpha$ sequence ($\sim$+0.1). This is a 
natural consequence of the starburst producing young,~$\alpha$-enhanced stars 
in excess of what is predicted by the baseline model~\citep{Johnson2020}.

\subsection{Abundance Gradients} 
\label{sec:obs_comp:gradient}

% fig 8
\begin{figure*} 
\centering 
\includegraphics[scale = 0.42]{tracks.pdf} 
\caption{\textbf{Left}: Gas phase evolutionary tracks in the [O/Fe]-[Fe/H] 
plane for our inside-out SFH with either post-processing (dotted lines) or 
diffusion (solid lines) migration models. We plot tracks for seven annuli, 
colour-coded according to their Galactocentric radius and denoted by the 
legend in the lower-left. We mark simulation times of 2, 4, 6, 8, 10, and 12.2 
Gyr in X's for the diffusion model and points for the post-processing model. 
\textbf{Right}: As a function of simulation time, a proxy for the SN Ia rate 
using the total time-derivative of the Fe mass in a given annulus, calculated 
by subtracting the contribution from recycling and CCSN enrichment and adding 
back that lost to star formation and outflows. We show these rates for the 
same annuli as in the left-hand panel, multiplying them by various prefactors 
to improve clarity. } 
\label{fig:tracks} 
\end{figure*}

We continue by assessing the impact of stellar migration on the gas-phase 
tracks in the [O/Fe]-[Fe/H] plane. To this end, we compare the predictions of 
our post-processing migration model, which has stars stay at their radii of 
birth until they instantaneously migrate at the present day, and our diffusion 
model, which has stars migrating continuously with a~$\sqrt{\text{age}}$ 
dependence. In the left-hand panel of Fig.~\ref{fig:tracks}, we plot the 
[O/Fe]-[Fe/H] tracks at several radii assuming the inside-out 
SFH, with post-processing shown in dotted lines and the diffusion in solid 
lines. We also mark simulation times of 2, 4, 6, 8, 10, and 12.2 Gyr on each 
track for reference. 
\par 
We note first and foremost that there are considerable differences between the 
two sets of tracks, particularly at high [O/Fe]. We demonstrate here that this 
arises out of variability in SN Ia rates caused by the time-dependent radial 
migration of the diffusion model. From our~\texttt{VICE} outputs, the total 
time derivative of the Fe mass in a given annulus can be obtained by its change 
across a single timestep. By then subtracting the CCSN contribution (known 
exactly given our adopted yield and the SFR), approximately correcting for 
recycling, and adding back that which was lost to star formation and outflows, 
we obtain a simple estimate of the rate of Fe production by SNe Ia. 
\par 
We plot this proxy as a function of simulation time in the right-hand panel of 
Fig.~\ref{fig:tracks}, with dotted and solid lines again denoting 
post-processing and diffusion migration models and the same colour-coding as in 
the left-hand panel; we have also multiplied these curves by various prefactors 
to improve clarity. As expected, the post-processing model predicts a SN Ia 
rate which is a smooth function of time at a given~$R_\text{gal}$. The diffusion 
model on the other hand exhibits significant variability on~$\sim$Gyr 
timescales; the time-averaged SN Ia rate tends to follow the post-processing 
prediction, but the instantaneous rates do not agree. A close comparison allows 
one to realize that whenever one of the tracks in the left-hand panel shows 
higher (lower) [O/Fe] at a given [Fe/H], there is an excess (deficit) in the SN 
Ia rate at a similar time and radius. Early times in the~$R_\text{gal}$ = 15 
kpc annulus illustrates a rather extreme example whereby the SN Ia rate is 
effectively zero for nearly 3 Gyr. We also note that the fractional amplitude 
of the variability increases with~$R_\text{gal}$; the log-scaled y-axis makes 
this clear. This makes sense physically because the lower stellar number 
density in the outer Galaxy means it would be much more susceptible to sampling 
noise. That is, a single star migrating has a larger fractional impact at 
large radii than small radii.

% fig 9 
\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{metallicity_gradient.pdf} 
\caption{Radial abundance gradients in [O/H] (top, red), [Fe/H] (top, blue), 
and [O/Fe] (bottom) for our four fiducial SFHs - constant (far left), 
inside-out (left-middle), late-burst (right-middle), and outer-burst (far 
right). We plot the gas-phase abundance at the present day as a function of 
Galactocentric radius in solid lines. Stars denote the median of the stellar 
MDF of the 100-pc width annulus at a given radius, with shaded regions marking 
the 16th and 84th percentiles thereof. Black lines in the top panels denote our 
target [$\alpha$/H] gradient of mode([$\alpha$/H]) = +0.3 at~$R_\text{gal}$~= 
4 kpc with a slope of -0.08 kpc$^{-1}$. } 
\label{fig:metallicity_gradient} 
\end{figure*}

Although one may expect the rates predicted by the two migration models to 
agree based on the dynamical argument that a star migrating outward should be 
balanced by a star migrating inward due to the conservation of energy, the SN 
Ia rate depends not only on stellar number density but also on the masses and 
ages of the stellar populations. While an inwardly migrating star should be 
balanced dynamically by an outwardly migrating one, the SN Ia rate is 
unaffected only when the two have masses and ages such that the SN Ia DTD has 
the same value for both stars. Fluctuations in the SN Ia rate at these 
amplitudes can be understood through a comparison of the timescales associated 
with radial migration and SN Ia events. In Fig.~\ref{fig:h277_decomposition}, 
we plotted the distribution of final radii in bins of birth radius and age, 
which are used in driving stellar migration in our models (see discussion in~\S 
\ref{sec:methods:h277}). From this, we noted that~$\sim$40\% of~\texttt{h277} 
star particles migrated beyond their birth radius by the time they were~$\sim$2 
Gyr old. Though our adopted form differs slightly in detail, if the SN Ia DTD 
is a~$\sim t^{-1}$ power-law with a minimum delay time of~$\sim$100 Myr 
\citep{Maoz2012, Maoz2017}, then there should be similar numbers of SN Ia 
events with delay times between 1 and 10 Gyr as there are between 100 Myr and 1 
Gyr. While our~$R_\text{gal}$~= 15 kpc annulus is something of an extreme 
example, when one realizes that this means~$\sim$half of SN Ia progenitors may 
move significantly beyond their birth radius, the amplitude of the variability 
seen in the right-hand panel of Fig.~\ref{fig:tracks} is not surprising. The 
fact that >10\% of events are seen at >10 kpc from their host galaxies in the 
ASAS-SN bright SN catalog~\citep{Holoien2019} adds qualitative, observational 
support to the argument that SN Ia progenitors may often form at significantly 
different radii than where the explosions are observed. 
\par 
We thus argue that the radial migration of nucleosynthetic yields can occur 
alongside stellar migration for delayed sources. Though we do not investigate 
this effect for such elements in this paper, it would be reasonable to expect 
similar predictions for s-process elements produced in AGB stars like carbon, 
nitrogen, strontium, yttrium, and zirconium as well as r-process elements from 
neutron star mergers if the associated DTD is sufficiently long. What we really 
learn from this investigation is that tracks are not simple functions when 
stellar migration is taken into account. To first order, they're characterized 
by the late-time equilibrium abundance and the value of~$\tau_\star$~setting 
the position of the ``knee''~\citep{Weinberg2017}, though migration causes 
noticeable variations which should depend on the details of the adopted 
dynamical history. In~\S~\ref{sec:obs_comp:age_alpha}, we demonstrate that 
this is a means with which truly young, super-solar [$\alpha$/Fe] stars in the 
solar neighborhood can be explained theoretically. 
\par 
We continue with an investigation into the radial abundance gradients predicted 
by our models. To some extent, a gradient is built into our models via a 
scaling of the mass loading factor~$\eta$~with Galactocentric radius (see 
discussion in~\S~\ref{sec:methods:yields}). In parameterizing the 
$\eta-R_\text{gal}$ scaling, we assumed our constant SFH model and the 
associated equilibrium abundance for alpha elements. Like the surface density 
gradient, we also assumed that stellar migration does not alter the overall 
form. We plot the radial [O/H] and [Fe/H] gradients predicted by all our 
models in the top row of Fig.~\ref{fig:metallicity_gradient}, and the [O/Fe] 
gradients in the bottom row. In all panels, stars denote the median abundance 
in each annulus, and the shaded region denotes the 16th and 84th percentiles of 
the MDF in that zone; solid lines denote the gas-phase gradient at the present 
day. Although we built the gradient into our models based on the mode abundance, 
we illustrate them here according to the median; we find that with annuli as 
narrow as~$\Delta R_\text{gal}$~= 100 pc, the mode is a sufficiently noisy 
statistic to introduce noticeably more scatter in this relation. Nonetheless we 
have verified that it follows the trend implied by our target gradient, 
illustrated by the solid black line. The median gradient for all of our model 
SFHs follows a slightly shallower trend than the mode, which is expected when 
the metallicity distribution is skew-negative in the inner Galaxy and 
skew-positive in the outer Galaxy. 
\par 
We note that our models indeed recover an~$R_\text{gal}$-[O/H] relation 
resembling that which was adopted. As was the case for the surface density 
gradient (see discussion in~\S~\ref{sec:methods:surface_density_gradient}), 
stellar migration appears to only introduce scatter. While our procedure for 
setting setting the abundance gradient did not consider Fe, our models predict 
it to follow a gradient similar to that of O. We further note that all SFHs 
predict an [O/Fe] gradient which is relatively flat at all radii, steepening 
only at very small and very large~$R_\text{gal}$. The trend toward higher 
[O/Fe] beyond~$R_\text{gal}$~= 15.5 kpc is expected, since this is the radius 
at which we shut off star formation; all stellar populations at these radii at 
the present day formed in the disc and migrated there, meaning this region of 
space in our model is populated only by stars sufficiently old to have migrated 
such distances. Because they're old, they also tend to be~$\alpha$-enhanced. 
This is consistent with the findings of~\citet{RadburnSmith2012}, who argue 
that the outskirts of the NGC 7793 disc formed largely out of stellar 
migration. {\color{red} Observational reference on the increase in [O/Fe] at 
small~$R_\text{gal}$? Maybe~\citet{Hayden2015}, but I'm not sure.} 
\par 
We also note that our models predict differences between the stellar and 
present-day gas-phase gradients which are sensitive to the adopted SFH. In the 
constant SFH model, the gas-phase gradient follows the mode abundance by 
construction. In the inside-out, late-burst, and outer-burst models, the 
ISM at small~$R_\text{gal}$~is considerably more metal-rich than the stars at 
similar radii. The late-burst model shows the largest difference; this is a 
consequence of the starburst at small~$R_\text{gal}$, an effect which is absent 
in the outerburst model. In accretion-induced starbursts, re-enrichment can 
briefly produce super-equilibrium abundances in the gas-phase which then decay 
back to the equilibrium abundance as the SFR declines~\citep{Johnson2020}. This 
effect can also be seen in the outer-burst model; at~$R_\text{gal}$ slightly 
larger than 6 kpc where the starburst did occur, the abundances are larger than 
at slightly less than 6 kpc, where the star burst did~\textit{not} occur. 
Altogether, these differences are reflective of the notion that the stellar 
abundance gradient is sensitive to stars of all ages and thus the entire star 
formation history, while the gas-phase gradient is more reflective of 
enrichment over the previous depletion time.

\subsection{Metallicity Distributions Functions} 
\label{sec:obs_comp:mdfs}

% fig 10 
\begin{figure} 
\centering 
\includegraphics[scale = 0.34]{mdf_3panel_fe.pdf} 
\caption{Metallicity distribution functions (MDFs) in [Fe/H] predicted by our 
fiducial, inside-out model (left) and as observed in APOGEE DR16 (right), for 
stars and simulated stellar populations with present-day~$\left|z\right|$~= 0 - 
0.5 kpc (bottom), 0.5 - 1 kpc (middle), and 1 - 2 kpc (top). MDFs are shown in 
bins of Galactocentric radius: 3 - 5 kpc (black), 5 - 7 kpc (red), 7 - 9 kpc 
(yellow), 9 - 11 kpc (green), 11 - 13 kpc (blue), and 13 - 15 kpc (purple). 
The points near the top of the bottom panels denote what the mode abundance 
would be if it followed out target gradient of [Fe/H] = +0.3 at~$R_\text{gal}$ 
= 4 kpc with a slope of -0.08 kpc$^{-1}$ exactly, assuming the inner radius of 
each bins (i.e. there is no point plotted for 15 kpc). All distributions are 
smoothed with a box-car width of [Fe/H]~$\pm$~0.1 for clarity. } 
\label{fig:mdf_3panel_fe} 
\end{figure}

% fig 11 
\begin{figure} 
\centering 
\includegraphics[scale = 0.34]{mdf_3panel_o.pdf} 
\caption{The same as Fig.~\ref{fig:mdf_3panel_fe}, but for [O/H]. } 
\label{fig:mdf_3panel_o} 
\end{figure}

Metallicity distribution functions (MDFs) and how they vary with Galactic 
region are one of the core predictions of chemical evolution models. In this 
section, we compare our model predicted MDFs to those observed in the 16th 
data release of APOGEE (DR16;~\citealp{Ahumada2020, Majewski2017}). The 
data are reduced using the APOGEE Stellar Parameters and Chemical Abundances 
Pipeline (ASPCAP;~\citealp{Holtzman2015, GarciaPerez2016}). For further details 
of the APOGEE survey, a brief summary can be found in~\S~2 of 
\citet{Weinberg2019}. We restrict our sample to stars with effective 
temperatures of 4000 K~$\leq T_\text{eff} \leq$~4600 K, surface gravities of 
1.0~$\leq \log g \leq$~2.5, and signal-to-noise ratios of at least 100. These 
cuts ensure that our sample consists of stars on the upper red giant branch, 
safely excluding red clump stars to avoid obvious systematics in the 
abundance distributions. 
\par 
In the disc midplane, stars as observed by APOGEE are known to exhibit mode 
[$\alpha$/H] and [Fe/H] abundances that depend on Galactocentric radius, with a 
skew-negative distribution in the inner Galaxy and skew-positive in the outer 
Galaxy~\citep{Hayden2015, Weinberg2019}. Off the midplane, the MDFs converge on 
[$\alpha$/H]~$\approx$~[Fe/H]~$\approx$~-0.5. This result is replicated in the 
right-hand column of panels~\ref{fig:mdf_3panel_fe} and~\ref{fig:mdf_3panel_o}. 
The left-hand columns show the distributions predicted by our fiducial 
inside-out model. We note that these replicate the qualitative scaling of the 
mode [O/H] and [Fe/H] with present-day Galactocentric radius, though our APOGEE 
data suggest that the 3 - 5 and 5 - 7 kpc bins share a common mode abundance. 
This was also seen in~\citet{Hayden2015}. Our models do not predict this 
detail; this could indicate that we have incorrectly parameterized outflows in 
the inner Galaxy (see discussion regarding our scaling of the mass loading 
factor~$\eta$~with~$R_\text{gal}$ in~\S~\ref{sec:methods:yields}). We would 
expect a flat [X/H] gradient and MDFs with similar modes if we simply chose it 
to be so by letting~$\eta$~be constant at small~$R_\text{gal}$. Another 
possibility is the cessation of star formation in these regions; by tracing 
products of star formation such as HII regions~\citep{Guesten1982}, supernova 
remnants~\citep{Leahy1989}, and pulsars (\citealp*{Lyne1985}; 
\citealp{Case1998}), the surface density of star formation~$\dot{\Sigma}_\star$ 
in the Milky Way is known to reach a maximum at~$R_\text{gal} \approx$~4 kpc 
(see Fig. 1 of~\citealt{Peek2009} and Fig. 2 of~\citealt{Fraternali2012}). Our 
models by construction predict~$\dot{\Sigma}_\star$ to decrease monotonically 
with~$R_\text{gal}$~(see Fig.~\ref{fig:evol}). If the Milky Way has begun 
quenching star formation, a process which is believed to begin in the centres 
of galaxies at this mass~\citep[e.g.][]{Ellison2020b}, then fewer stars would 
form in the most metal-rich regions than do in our models, cutting off the MDF 
at high [O/H] and [Fe/H]. 
\par 
Beyond the midplane, our models fail to fully replicate the convergence of the 
MDFs at [X/H]~$\approx$~-0.5. The observed MDF at small radii shfits from 
skew-negative with a metal-rich mode to skew-positive with a metal-poor 
mode with increasing~$\left|z\right|$. In our model predicted MDFs for small 
$R_\text{gal}$, the mode does shift to lower abundances, but not to the same 
extent as in the observed sample, and with minimal change in skewness. 
Although the model predicts a portion of the effect, it cannot account for the 
entire~$\left|z\right|$-dependence of the MDF shape in the inner Galaxy.

\subsection{[O/Fe] distributions in Bins of [Fe/H]} 
\label{sec:obs_comp:ofe_dists} 
In this section we compare our predicted [O/Fe] distributions in various 
Galactic regions to those recently published in~\citet{Vincenzo2021a}. As in our 
\S~\ref{sec:obs_comp:mdfs}, they also make use of APOGEE DR16 
\citep{Ahumada2020, Majewski2017}, and impose a similar set of cuts on 
effective temperature, surface gravity, and signal-to-noise (see their~\S~2). 
These distributions are estimates of the~\textit{intrinsic} [O/Fe] 
distributions that, when 
convolved with observational uncertainties and the APOGEE selection function, 
would resemble the observed MDFs like those in~\citet{Hayden2015}. We show the 
distributions predicted by our fiducial model in~$\Delta$[O/Fe] = 0.04 bins 
across 15 Galactic regions in comparison to the~\citet{Vincenzo2021a} 
distributions shown in dashed lines in Fig.~\ref{fig:ofe_mdfs_insideout}. 
Galactic regions 
are defined by a range in~$R_\text{gal}$, shown in columns and denoted at the 
top of the figure, and a range in~$\left|z\right|$, shown in rows and denoted 
in text in the left-hand column. We show this comparison for two bins in 
[Fe/H], colour-coded according to the legend in the top-right panel.

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{ofe_mdfs.pdf} 
\caption{Predicted distributions in [O/Fe] in 15 Galactic regions and in two 
bins in [Fe/H]. Columns correspond to bins in~$R_\text{gal}$, denoted at the 
top of each column. Rows correspond to bins in~$\left|z\right|$, denoted in 
text in the left-hand column. Distributions are color-coded according to the 
[Fe/H] the sample is drawn from, denoted by the legend in the upper right 
panel. Solid lines represent that predicted by our inside-out SFH in 
$\Delta$[O/Fe] = 0.04 bins, while dashed lines correspond to the fits to the 
APOGEE DR16 data presented in~\citet{Vincenzo2021a}, which quantify the 
intrinsic distributions accounting for observational uncertainties and the 
APOGEE selection function. } 
\label{fig:ofe_mdfs_insideout} 
\end{figure*}

Finding similar results for all of our SFHs, we note that our model adequately 
reproduces the broad nature of the [O/Fe] distributions at fixed [Fe/H] seen in 
the APOGEE data. Some distributions in a specific Galactic region and [Fe/H] 
bin show a bimodality in decent agreement with the observations (e.g. the 
-0.4~$\leq$~[Fe/H]~$\leq$~-0.2 bin at~$R_\text{gal}$~= 7 - 9 kpc and 
$\left|z\right|$ = 1 - 2 kpc), but this is not true of all Galactic regions in 
both metallicity bins. Instead, the principle failure of our model is that it 
overpredicts the number of intermediate [O/Fe] stars. 
\par 
In the inner Galaxy, our model overestimates the mode [O/Fe] to some extent for 
both [Fe/H] bins, but the difference is larger for the higher of the two. This 
discrepancy also increases with increasing~$\left|z\right|$. At fixed 
$R_\text{gal}$, the~\citet{Vincenzo2021a} distributions show two peaks which do 
not change with~$\left|z\right|$; only their relative heights vary. This is 
an assumption built into the model, but the agreement with the APOGEE data is 
good. However, this is a region of the Galaxy where there aren't many APOGEE 
stars. At~$\left|z\right|$ = 1 - 2 kpc for ~$R_\text{gal}$ = 3 - 5 and 5 - 7 
kpc, the~\citet{Vincenzo2021a} model is fit to 31 and 17 stars, respectively. In 
comparison, there are 109 in the solar annulus, and all other bins have >75 
stars involved in the fit. It's possible the observed distributions shift 
slightly to higher [$\alpha$/Fe], but at most at the~$\lesssim$~0.05 level 
(see their Fig. 11). 
\par 
If this discrepancy persists in subsequent APOGEE data releases which will 
better characterize the distributions in these regions, it's possible the 
origin is tied to the Sagittarius dwarf. The~\texttt{h277} simulation, which 
drives stellar migration in our models (see discussion in~\S 
\ref{sec:methods}), did not have such an accretion event. With its most recent 
major merger occurring at a redshift of~$z \approx$~3, this galaxy has 
previously been selected for investigation expressly because of its quiescent 
merger history~\citep[e.g.][]{Zolotov2012}. N-body models for the tidal 
disruption of the Sagittarius dwarf, on the other hand, suggest pericentric 
passages around 6.5, 4.5, 2.75, 1, and 0.1 Gyr ago~\citep{Law2010}. In addition 
to potentially triggering episodes of star formation 
\citep[e.g.][]{RuizLara2020}, more frequent pericentric passages of a massive 
satellite could kinematically heat low-[$\alpha$/Fe] disc stars to higher 
$\left|z\right|_\text{max}$~orbits. Such effects are not a component of the 
dynamical history of~\texttt{h277}; this is one instance where running our 
models with a different hydrodynamical simulation's star particles may be an 
enlightening comparison. 
\par 
The notion that an [$\alpha$/Fe] dichotomy can arise out of radial migration 
alone traces back to~\citet{Schoenrich2009}, and was later explored by 
\citet{Nidever2014} and recently by~\citet{Sharma2020}. This however suggests 
that an inside-out star formation history combined with stellar migration is not 
conducive to predicting this observed result, even when a recent starburst is 
added. The primary failure being an overpredicted frequency of intermediate 
[$\alpha$/Fe] stars, this could point to a number of things. If the bimodality 
is to arise out of inside-out Galaxy evolution and stellar migration alone, 
then the transition between high- and low-$\alpha$ sequences needs to occur 
faster than it does in these models. The analytic arguments of 
\citet{Weinberg2017} suggest that the approach to equilibrium occurs on the 
order of the SFE timescale~$\tau_\star$ (see~\S~\ref{sec:methods:sfe}). 
Since we've adopted a star formation law which is motivated by observational 
results, the failure of these models to reproduce the observed dichotomy 
suggests that the typical SFE timescales as observed are not short enough to 
explain such a fast transition. This would imply that either the Milky Way 
occupied a special place in the scatter of the observed 
$\dot{\Sigma}_\star-\Sigma_\text{g}$ relation at a time early in its 
evolutionary history, or the bimodality arose out of alternative pathways. 
Under our current assumptions, the simplest way to decrease the frequency of 
intermediate [$\alpha$/Fe] stars is to simply shut off (or turn down) star 
formation when the ISM is at such a composition. This is an indication 
that two-infall evolutionary histories~\citep[e.g.][]{Chiappini1997, 
Chiappini2001, Romano2010, Grisoni2017, Noguchi2018, Palla2020, Spitoni2016, 
Spitoni2018, Spitoni2019a, Spitoni2020, Spitoni2021} would improve the 
agreement between our model predictions and the observed distributions.

\subsection{The Age-[$\alpha$/Fe] Relation} 
\label{sec:obs_comp:age_alpha} 
In this section, we assess the predicted age-[O/Fe] relations of our models, 
using the results of~\citet{Feuillet2019} as the observational benchmark; their 
stellar age measurements are based on isochrone matching. While we made 
use of APOGEE DR16 data in comparing our model predictions to the observed 
MDFs~\citep[][see~\S~\ref{sec:obs_comp:mdfs}]{Ahumada2020, Majewski2017}, they 
made use of APOGEE DR14 stars for which parallax measurements are available 
from Gaia~\citep{Abolfathi2014, GaiaDR2}. With their spatial and quality cuts, 
the final 
sample consisted of 77,562 stars. In bins of [O/Fe], they assume a gaussian 
log age distribution, fitting the mean and standard deviation to the stars in 
that bin. Because they assume a gaussian, they would report an equal mean 
and median log age. This means that a one-to-one comparison of our model 
predictions to their results is not free of nuance, because they predict 
log age distributions which are highly non-gaussian at fixed [O/Fe]. 
\par 
The stellar populations from our simulations have different masses; this 
necessitates weighting the age-distributions by present-day mass, because that 
scales with the number of stars that a model stellar population represents. We 
therefore adopt the 50th percentile of the mass-weighted age distribution in a 
bin of [O/Fe] as the characteristic age to compare to the~\citet{Feuillet2019} 
measurements. We refer to this quantity as the mass-weighted median age.

% fig 13 
\begin{figure*} 
\centering 
\includegraphics[scale = 0.34]{age_ofe_migration_comparison.pdf} 
\includegraphics[scale = 0.34]{age_ofe_sfh_comparison.pdf} 
\caption{
\textbf{Left}: A comparison of the predicted age-[O/Fe] relation for the solar 
annulus ($R_\text{gal}$ = 7 - 9 kpc and~$\left|z\right|$ = 0 - 0.5 kpc) between 
the post-processing (upper left), diffusion (upper right), sudden (lower left), 
and linear (lower right) migration models, assuming our inside-out SFH. 
\textbf{Right}: The same as the left-hand panels, instead comparing the impact 
of our constant (upper left), inside-out (upper right), late-burst (lower left), 
and outer-burst (lower right) SFHs, assuming diffusion migration. In all panels, 
red triangles and error bars denote the observed mean age and dispersion 
thereof in bins of [O/Fe] as reported by~\citet{Feuillet2019}; here we include 
only the bins containing at least 15 stars. Black squares denote the 
mass-weighted median age in 0.02-dex bins in [O/Fe] predicted by our models, 
with error bars denoting the 16th and 84th percentiles of the mass-weighted 
age distribution in those bins. Points in the background denote each individual 
stellar population from the model with a final position in the solar annulus, 
colour-coded according to their Galactocentric radius of birth. 
}
\label{fig:age_alpha} 
\end{figure*}

In the left-hand set of panels of Fig.~\ref{fig:age_alpha}, we compare the 
age-[O/Fe] relation in the solar annulus ($R_\text{gal}$~= 7 - 9 kpc and 
$\left|z\right|\leq$~0.5 kpc) predicted by our four migration models to the 
\citet{Feuillet2019} measurements, shown in red triangles. We mark the 
mass-weighted median age in bins of [O/Fe] in each model with black squares, 
and plot for reference in the background each individual stellar population in 
the solar annulus, colour-coded according to its Galactocentric radius of birth. 
\par 
We note that the inside-out SFH, assumed by all four of the models illustrated 
here, provides a reasonable description of the age-[O/Fe] relation as observed 
in APOGEE. We also note that each model for the time-dependence of stellar 
migration predicts differing amounts of scatter in the age-[O/Fe] relation. 
Diffusion has the most, followed by linear, then sudden, and lastly 
post-processing. We interpret this as a consequence of the variability in the 
SN Ia rate as a function of radius and time caused by time-dependent migration 
(see Fig.~\ref{fig:tracks} and associated discussion near the beginning of~\S 
\ref{sec:obs_comp}). When the SN Ia rate is higher or lower than expected given 
the SFH of an annulus, then the Fe abundance in that zone will increase or 
decrease accordingly. This can occur if there is a significant net gain or loss 
of SN Ia progenitors in a given time interval due to time-dependent migration. 
The gas-phase [O/Fe] then decreases or increases in turn, and the stars which 
form out of that gas inherit these compositions. When migration is taken into 
account and stellar populations are mixed as a consequence, the observational 
signature is intrinsic scatter in the age-[$\alpha$/Fe] relation. 
\par 
All of the models in the left-hand set of panels predict a correlation between 
mass-weighted median age and [O/Fe] in good agreement the~\citet{Feuillet2019} 
measurements assuming the inside-out SFH. This suggests that the population 
averaged trend is unaffected by stellar migration. However, only the diffusion 
and linear migration models predict a population of young ($\lesssim$~4 Gyr), 
[$\alpha$/Fe]~$\approx$~+0.1 - 0.2 stars in the solar neighbourhood. These 
stars are a part of the noticeable upward scatter in the relationship, and we 
therefore interpret their origin to be the same as the scatter itself - they 
formed in a region of the Galactic ISM at a time when it was particularly 
alpha-enhanced due to a rather lasting deficit in SN Ia events. These stars 
then migrated to the solar annulus, where they showed up in the APOGEE data 
when stellar ages were measured using carbon-to-nitrogen ratios 
\citep{Martig2016}, isochrone matching~\citep{Feuillet2018, Feuillet2019}, 
and with the asteroseismic ages of the origin APOKASC catalog 
\citep{Chiappini2015, SilvaAguirre2018, Pinsonneault2014}. 
\par 
\citet{SilvaAguirre2018} demonstrate that the observed young $\alpha$-rich 
stars in the solar annulus have kinematics similar to the rest of the 
high-$\alpha$ population, and suggested this may be the result of stellar 
mergers or mass transfer events. This would produce a population of truly old 
stars masquerading as young stars. In a sample of 51 young, $\alpha$-rich 
red giants,~\citet{Hekker2019} demonstrate that a portion of these stars have 
carbon-to-nitrogen ratios consistent with mass transfer events, but that others 
do not, indicating they're either truly young stars or the result of mergers 
on the main sequence. As far as we know, the mechanism discussed here is the 
first theoretical explanation of the origin of these stars. We note 
additionally that under this explanation, the young~$\alpha$-rich stars are 
not so much $\alpha$-rich as they are Fe-poor, and form overwhelmingly at 
large~$R_\text{gal}$ where the SN Ia rate is most variable (see discussion in 
\S~\ref{sec:obs_comp:gradient}). 
\par 
In the right-hand set of panels in Fig.~\ref{fig:age_alpha}, we 
compare the model predictions of our four different SFHs, assuming our 
diffusion migration model, with the same plotting scheme and colour-coding as 
in the left-hand panels. We note that the constant and inside-out SFHs describe 
the data the best. Although our e-folding timescales for star formation are 
sufficiently long at large~$R_\text{gal}$ such that there is little difference 
between the constant and inside-out SFHs there anyway (see discussion in~\S 
\ref{sec:methods:sfhs}), our constant SFH is idealized and of purely 
theoretical interest, making the inside-out model the more likely of the two. 
Below [O/Fe]~$\approx$~+0.1, the~\citet{Feuillet2019} data seem to follow a 
slightly steeper age-[$\alpha$/Fe] relation than our inside-out model 
predicts. This could point to any number of things being an inaccuracy in our 
models: the detailed form of the SFH or the SN Ia DTD, our supernova yields, 
or observational [O/Fe] errors, all of which are plausible. 
\par 
We note that our starburst models, both late-burst and outer-burst, disagree 
with the~\citet{Feuillet2019} measurements. The late starburst produces a 
population of young, $\alpha$-rich stars due to the perturbed ratio of core 
collapse to type Ia supernova rates~\citep{Johnson2020}. With the starburst 
occurring in a substantial fraction of the ISM in both models, the result is an 
increase in the bulk [$\alpha$/Fe] for young stars which simply is not seen in 
the observed sample. The effect is strong enough that at [O/Fe]~$\approx$~+0.1, 
both models considerably overpredict the width of the distribution, 
simultaneously predicting a mass-weighted median age many times the standard 
deviation younger than observed. This discrepancy is of interest, because these 
models were motivated by the observational results of~\citet{Mor2019} and 
\citet{Isern2019} which suggest such a recent starburst. Although our 
functional forms differ from what they reported in detail, they're reasonable 
descriptions of the measurements within the error bars. This suggests that the 
results of~\citet{Mor2019} and~\citet{Isern2019} are at odds with chemical 
evolution models of the Milky Way. If the Galaxy truly experienced a recent 
starburst, then something not included in our models had to prevent this global 
increase in [$\alpha$/Fe].

% fig 14 
\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{age_alpha_regions.pdf} 
\caption{The age-[O/Fe] relation in 12 Galactic regions predicted by our 
inside-out SFH. Bins in Galactocentric radius are shown in columns, and labeled 
at the top. Bins in the height~$\left|z\right|$ above/below the disc midplane 
are shown in rows, noted in the left-hand column. Red triangles, black squares, 
error bars, and background points are as in Fig.~\ref{fig:age_alpha} for the 
corresponding Galactic region. The solid black line connects the black squares 
in the bottom, left-middle panel, and is replicated elsewhere for reference. } 
\label{fig:age_alpha_regions} 
\end{figure*}

In Fig.~\ref{fig:age_alpha_regions}, we extend the comparison of our base-line, 
inside-out model and the observations of~\citet{Feuillet2019} to other 
Galactic regions. We visualize the data there in the same manner as for 
previous figures in this section. While the inside-out model shows the best 
agreement with the observed result in the solar annulus, there are some mild 
discrepancies for stars farther from the sun.~\citet{Feuillet2019} report ages 
for~$\alpha$-rich stars that are younger at large~$R_\text{gal}$ and high 
$\left|z\right|$, though in most cases only by~$\sim$20\%. Our model does not 
capture this effect. To illustrate this, we connect the black squares in the 
panel corresponding to the solar annulus with a black line, and then reproduce 
this line in all panels for reference. If the observational result is correct, 
this is an interesting effect that our model doesn't reproduce in any of the 
variants we've explored. Furthermore, we note that the model overpredicts ages 
at large~$\left|z\right|$. As with the overpredicted [O/Fe] ratios at small 
$R_\text{gal}$, we speculate that this may be tied to the Sagittarius dwarf 
(see discussion in~\S~\ref{sec:obs_comp:ofe_dists}). By using a hydrodynamical 
simulation of a 
galaxy which exhibited more pericentric passages of a massive satellite, more 
young stars may be kinematically heated to high~$\left|z\right|_\text{max}$ 
orbits. This is another instance where running our models with a different 
hydrodynamical simulation's star particles may be an enlightening comparison. 
\par 
We note that the intrinsic scatter in the age-[O/Fe] relation is predicted to 
grow with increasing~$R_\text{gal}$; this can be seen in the error bars on the 
black squares as well as the coloured points. We identify two sources of this 
dependence; the bulk of the scatter, at least at [O/Fe]~$\gtrsim$~+0.05, arises 
from the variability in the SN Ia rates as described in~\S 
\ref{sec:obs_comp:gradient}. Having demonstrated that the SN Ia rate is most 
variable at large~$R_\text{gal}$, the in-situ populations in the outskirts of 
the Galactic disc formed from an ISM whose gas-phase [O/Fe] ratio varied with 
a higher amplitude. Since the observational signature of this variability is 
scatter in the observed age-[O/Fe] relation, our model predicts the most 
intrinsic scatter in Galactic regions where that variability has the highest 
amplitude. Second, the analytic models of~\citet{Weinberg2017} suggest that 
as the e-folding timescale for star formation~$\tau_\text{sfh}$ increases, the 
model-predicted [O/Fe] of the youngest stars increases with a weak dependence. 
With a range of e-folding timescales in our model, this implies a distribution 
of [O/Fe] at age = 0 with nonzero width without considering the migration of 
nucleosynthetic yields. This can be seen in the post-processing model 
predicted age-[O/Fe] relation in Fig.~\ref{fig:age_alpha}. In this pathway, 
scatter is induced by mixing populations that follow age-[O/Fe] relations of 
slightly different normalizations which are nearly flat intrinsically, 
producing a noticeably wide age distribution near solar [O/Fe]. 
\par 
Although the iron-peak is the only class of elements with a delayed 
nucleosynthetic source that we consider in the present paper, we expect similar 
results for other delayed sources with regard to the variability in enrichment 
rates and scatter in age-[X/Y] relations. The details of SN Ia nucleosynthesis 
did not matter in our interpretations in this section; it is based purely on 
the characteristic delay-times of the source and how they compare to the 
timescales of stellar migration. Our models should then find similar 
predictions with, for example, s-process (slow neutron capture) elements like 
carbon, nitrogen, strontium, yttrium, and zirconium produced in asymptotic 
giant branch stars. In fact, using hydrodynamical simulations from the Auriga 
project~\citep{Grand2017},~\citet{vandeVoort2020} find that the intrinsic 
scatter in r-process (rapid neutron capture) abundances increases for models 
with longer characteristic delay times. Although the first observations of a 
binary neutron star merger (GW170817) exhibited an optical counterpart which 
was consistent with being powered by the radioactive decay of r-process 
elements~\citep{Abbott2017, Coulter2017, Drout2017, Pian2017}, it remains 
unclear the extent to which neutron star mergers contribute to r-process 
nucleosynthesis in the universe~\citep{Cote2019, Mishenina2019, Siegel2019, 
vandeVoort2020, Vincenzo2021b}. Although it's likely unfeasible at present due 
to the requirement for high precision abundance measurements of intrinsically 
rare elements in many stars, with future observational capabilities, the 
application of our results as well as~\citet{vandeVoort2020} suggests that the 
intrinsic scatter in r-process abundances may provide constraints on the 
characteristic delay times of such nucleosynthetic events.

\subsection{The Age-Metallicity Relation} 
\label{sec:obs_comp:amr}

% fig 15 
\begin{figure} 
\centering 
\includegraphics[scale = 0.35]{amr_static_o.pdf} 
\caption{The age-[O/H] relation predicted by our constant SFH model for 
$R_\text{gal}$~= 7 - 9 kpc (left) and 11 - 13 kpc (right). Each panel plots 
only the~$\left|z\right|\leq$~0.5 kpc population. The colored points in the 
background and the black squares with error bars are as in Fig. 
\ref{fig:age_alpha}, but with our binned, model prediction quantified in 
bins of~$\Delta$[O/H] = 0.05. } 
\label{fig:age_oh_static} 
\end{figure}

Although the age-metallicity relation (AMR) is usually formulated in terms of 
[Fe/H], it is also interesting to quantify the age-[O/H] relation, because it 
is not affected by SN Ia enrichment. The extent to which they differ indicates 
the extent to which the delayed timescale and impact of migration on SN Ia 
enrichment is important in shaping the age-[Fe/H] relation. In Fig. 
\ref{fig:age_oh_static}, we present the age-[O/H] relation predicted by our 
constant SFH model for the~$\left|z\right|\leq$~0.5 kpc population at 
$R_\text{gal}$ = 7 - 9 and 11 - 13 kpc. The black squares with error bars 
denote the mass-weighted median age as in~\S~\ref{sec:obs_comp:age_alpha}, and 
we again plot the individual stellar populations in the background for 
reference, colour-coded according to their Galactocentric radius of birth. We 
omit the~\citet{Feuillet2019} measurements from this figure, because the 
constant SFH model is of purely theoretical interest, removing the effects of 
a time-varying SFH while including the effects of stellar migration. 
\par 
The intrinsic scatter in the observed AMR has previously been interpreted as 
evidence for radial mixing~\citep{Edvardsson1993, Sellwood2002}. In the 
solar neighbourhood,~\citet{Feuillet2018} demonstrate that the most metal-rich 
stars tend to be significantly older than solar metallicity stars. Using the 
\citet{Weinberg2017} analytic models of one-zone chemical evolution, they argue 
that this is the result of old stars born at small~$R_\text{gal}$ where the 
equilibrium abundance is high. Only the old stars are able to migrate to 
the solar neighbourhood due to the time required for such a change in their 
orbital radius. 
\par 
The results of our constant SFH model illustrated in Fig. 
\ref{fig:age_oh_static} extend our understanding of this effect. In both 
regions plotted, the youngest stars form with a composition inherited from the 
local ISM, which in this model, is reflective of the late-time equilibrium 
abundance. At a given age, only stars born in a well-defined region of the 
Galaxy will have had adequate time to migrate to a given present-day radius. 
Since a range of~$R_\text{gal}$ maps directly to a range of metallicity once 
the ISM is arbitrarily close to the equilibrium abundance in our model, this 
necessitates a maximum width of the [O/H] distribution at fixed age. With 
increasing age, the [O/H] distribution then gets wider because any given 
present-day radius samples stars formed at a wider range of~$R_\text{gal}$. 
In Fig.~\ref{fig:age_oh_static}, we indeed see this effect, with the 
colour-coding of the background points making it clear that stellar migration 
is the culprit. In the outer Galaxy, migration has a particularly interesting 
effect in that it only adds old stars above the equilibrium metallicity; in 
the~$R_\text{gal}$ = 11 - 13 kpc region, our model as a consequence predicts 
an AMR where the population-averaged trend where [O/H] is nearly monotonically 
increasing with age. This is entirely backwards from what is expected from 
one-zone models of GCE~\citep[e.g.][]{Andrews2017, Weinberg2017, Johnson2020}.

% fig 16 
\begin{figure} 
\centering 
\includegraphics[scale = 0.45]{amr_solar_annulus.pdf} 
\caption{The age-[O/H] (top) and age-[Fe/H] (bottom) relations for the solar 
annulus (i.e.~$R_\text{gal}$ = 7 - 9 kpc,~$\left|z\right|\leq$~0.5 kpc) as 
predicted by our inside-out SFH. Red triangles, black squares, error bars, and 
background points are as in Fig.~\ref{fig:age_alpha}, but with our model 
predicted quantified in bins of~$\Delta$[O/H] =~$\Delta$[Fe/H] = 0.05. For 
comparison, we plot the~\citet{Feuillet2018} measurements in a dark red line, 
omitting the associated uncertainties for visual clarity. } 
\label{fig:amr_solar_annulus} 
\end{figure}

We continue our assessment of the model-predicted AMR by illustrating in Fig. 
\ref{fig:amr_solar_annulus} the age-[O/H] (top) and age-[Fe/H] (bottom) 
relations predicted for the solar annulus (i.e.~$R_\text{gal}$~= 7 - 9 kpc and 
$\left|z\right|\leq$~0.5 kpc). The red triangles, black squares, coloured 
points, and error bars are as in previous figures in~\S 
\ref{sec:obs_comp:age_alpha}. For reference, we add the solid dark red line, 
which denotes the AMR measured by~\citet{Feuillet2018}. Although our model 
shows decent agreement with the~\citet{Feuillet2019} measurements in the solar 
annulus,~\citet{Feuillet2018} report ages for solar metallicity stars which 
are considerably younger ($\sim$1 - 2 Gyr as opposed to~$\sim$3 - 4 Gyr). 
The~\citet{Feuillet2018} data would suggest our inside-out model requires an 
enhancement in the recent SFR to increase the frequency of young, solar 
metallicity stars. Although our late-burst and outer-burst models include 
such effects, motivated by recent observations suggesting this exact 
evolutionary history~\citep{Mor2019, Isern2019}, the differences between the 
\citet{Feuillet2018} and~\citet{Feuillet2019} measurements are interesting in 
and of themselves.

% fig 17 
\begin{figure*} 
\centering 
\includegraphics[scale = 0.35]{amr_insideout_vs_lateburst_fe.pdf} 
\caption{The age-[Fe/H] relation predicted by our inside-out (top) and 
late-burst (bottom) SFHs for~$R_\text{gal}$ = 5 - 7 kpc (left), 7 - 9 kpc 
(left middle), 9 - 11 kpc (right middle), and 11 - 13 kpc (right). Each panel 
shows only the~$\left|z\right|\leq$~0.5 kpc population. Red triangles, black 
squares, error bars, and coloured points are as in Fig.~\ref{fig:age_alpha} for 
the corresponding Galactic region, but with our model prediction quantified in 
bins of~$\Delta$[Fe/H] = 0.05. } 
\label{fig:amr_insideout_vs_lateburst_fe} 
\end{figure*}

Motivated by this, we compare the predictions of the inside-out and late-burst 
SFH models to the~\citet{Feuillet2019} age-[Fe/H] relation in Fig. 
\ref{fig:amr_insideout_vs_lateburst_fe}. We retain the same plotting scheme 
used throughout this section and~\S~\ref{sec:obs_comp:age_alpha}, illustrating 
the inside-out model in the top row and the late-burst model in the bottom row. 
Each column corresponds to a specific range in~$R_\text{gal}$, denoted at the 
top of the figure. Beyond the solar annulus, we note that our inside-out model 
has a number of short-comings in comparison to the~\citet{Feuillet2019} 
measurements. At~$R_\text{gal}$ = 5 - 7 kpc, it overpredicts the characteristic 
ages of [Fe/H]~$\approx$~-0.3 - 0 stars. At~$R_\text{gal}$ = 9 - 11 and 11 - 13 
kpc, it mildly overpredicts ages at most abundances, and fails to reproduce the 
trend seen in the observed sample. The same can be said about the 
$R_\text{gal}$~=5 - 7 kpc region, and although the overall agreement is 
generally good there, one could reasonably argue this for the solar annulus as 
well. 
\par 
The late-burst model improves upon these shortcomings of the inside-out model 
considerably. At~$R_\text{gal}$ = 5 - 7 kpc, the overpredicted ages at solar 
and mildly sub-solar [Fe/H] is no longer present; this is also true at 
$R_\text{gal}$~= 9 - 11 and 11 - 13 kpc. Furthermore, the trend is much better 
reproduced at all radii in the late-burst than the inside-out model. The only 
different between the late-burst and inside-out model being the recent 
enhancement in the SFR, this is what drives the differences in model 
predictions. To fuel the starburst as we have parameterized it,~\texttt{VICE} 
calculates that there must be substantial gas accretion (see the infall rate 
$\dot{\Sigma}_\text{in}$ as a function of radius and time in Fig. 
\ref{fig:evol}). In our models, we assume accretion to always be of zero 
metallicity gas. As a result, the model predicts dilution of the ISM Fe 
abundance during the starburst; this can be seen by the trend of the coloured 
points in Fig.~\ref{fig:amr_insideout_vs_lateburst_fe} to lower [Fe/H] at ages 
of~$\sim$2 - 3 Gyr. At this time, the star formation rate is elevated by 
construction. The net effect is to increase the frequency of~$\sim$2 - 3 Gyr 
old stars with near- and sub-solar abundances globally, which lowers the 
characteristic ages of stars at these metallicities relative to the inside-out 
model. Using the~\citet{Feuillet2019} measurements as the observational 
benchmark, we favor the late-burst model here. 
\par 
Although there appears to be a vertical offset between the observed result and 
the model prediction at~$R_\text{gal}$ = 9 - 11 and 11 - 13 kpc, this is still 
an improvement upon the inside-out model. It's possible that this points to a 
need for higher yields of Fe than we've adopted here, though it's unclear if 
this would negatively affect the agreement at~$R_\text{gal}$~= 5 - 7 and 7 - 9 
kpc. It's possible that our parameterization of the mass-loading factor~$\eta$ 
scales too strongly with~$R_\text{gal}$ in the outer Galaxy (see discussion in 
\S~\ref{sec:methods:yields}). Alternatively, outflows in nature may be more 
efficient at removing some elements from the ISM than others; this could impact 
the overall normalization of the AMR at different radii. Our models in the 
present paper assume that outflows always proceed exactly at the metallicity of 
the ISM, but some authors argue that outflows can have a different metallicity 
- usually a higher one - due to containing in some part the metal-rich 
supernova ejecta that was added directly to the outflow by the explosions 
(observationally:~\citealp*{Chisholm2018}; in simulations: 
\citealp{Christensen2018}). 
\par 
We also note that the late-burst model predicts particularly young 
characteristic ages for the most metal-rich bins at~$R_\text{gal}$ = 5 - 7 kpc. 
This is purely a consequence of our choice to use the mass-weighted median as 
the population-averaged age measurement at fixed abundance. In this case, our 
model is simply reporting the 50th percentile of an age-distribution 
which is noticeably bimodal; as a result, whether or not the characteristic 
ages we report there are <1 Gyr or in better agreement with the 
\citet{Feuillet2019} measurements strongly depends on how we've parameterized 
the recent starburst as a function of both time and radius. Here we've made the 
simplest assumption of letting have the same time-dependence at all radii, 
which was not necessarily the case. 
\par 
Although we demonstrate here that the late-burst model describes the age-[Fe/H] 
relation reported by~\citet{Feuillet2019} better than the inside-out model, we 
found the exact opposite with regard to the age-[$\alpha$/Fe] relation with 
the same obesrvational sample in~\S~\ref{sec:obs_comp:age_alpha}. It's unlikely 
this discrepancy can be mitigated using any model which exhibits a recent 
starburst as parameterized here; as we demonstrated in~\S 
\ref{sec:obs_comp:age_alpha}, such models predict a global increase in 
[$\alpha$/Fe] due to the perturbed ratio of CCSN and SN Ia rates 
\citep{Johnson2020}, a feature which simply isn't seen in the 
\citet{Feuillet2019} measurements. It's possible that the Milky Way experienced 
dilution with no ensuing starburst - this would be the case if the majority of 
the accreted gas was warm, neutral and ionized gas which simply hasn't yet been 
made available for star formation. Such a scenario would exhibit some of the 
predictions of the late-burst model, but without the increase in [O/Fe] at late 
times, potentially allowing it to simultaneously explain the age-[$\alpha$/Fe] 
relation and AMR as they are observed. However, these models would be at odds 
with the findings of~\citet{Mor2019} and~\citet{Isern2019}. 
\par 
We remark that we find similar results for the age-[O/H] relation; furthermore, 
as in~\S~\ref{sec:obs_comp:age_alpha} for the age-[$\alpha$/Fe] relation, we 
also find for the age-[Fe/H] and age-[O/H] relations that our models tend to 
overpredict ages with increasing~$\left|z\right|$. Lastly, we caution future 
studies against basing the likelihood of a chemical evolution model on data 
for the solar annulus alone. In Fig.~\ref{fig:amr_solar_annulus}, we 
noted that there was decent agreement between the inside-out SFH model and 
the~\citet{Feuillet2019} measurements of the age-[O/H] and age-[Fe/H] 
relations in the solar annulus, but upon extending the comparison to other 
Galactic regions in Fig.~\ref{fig:amr_insideout_vs_lateburst_fe}, a number of 
shortcomings revealed themselves. Although to some extent this is made possible 
only recently with observational capabilities now allowing statistical 
measurements of these correlations for stars at greater distances from the sun, 
had we stopped there, we would have missed this interesting and peculiar 
result.

\section{Discussion \& Conclusions} 
\label{sec:conclusions} 
In this paper, we have modeled the Milky Way as a series of concentric annuli 
with a~$\Delta R_\text{gal}$~= 100 pc width, describing each annulus as a 
conventional one-zone chemical evolution model and allowing the exchange of 
stellar populations between zones to include the impact of stellar migration in 
the model Galaxy. Though there have been a handful of studies which employ a 
similar methodology~\citep{Schoenrich2009, Nidever2015, Sharma2020}, ours and 
the~\citet{Minchev2013, Minchev2014, Minchev2017} model are the only ones which 
make use of a hydrodynamical simulation to describe radial mixing, for which we 
make use of the~\texttt{h277} zoom-in simulation~\citep{Christensen2012, 
Zolotov2012, Loebman2012, Loebman2014, Brooks2014}. This yields a model for 
migration which does not have any free parameters (see discussion in~\S 
\ref{sec:methods:h277}). 
\par 
Our model predicts masses and abundances for simple stellar populations, a 
given number of which form at each timestep. Each stellar 
population is then assigned a star particle from~\texttt{h277} which was born 
at a similar radius and time to act as an~\textit{analog}. The stellar 
population in our model then assumes the change in radius~$\Delta R_\text{gal}$ 
of the analog at face value, and is assumed to reside at the same present day 
height above/below the disc midplane~$\left|z\right|$. We then construct four 
models describing the time-dependence with which stellar populations move to 
their present-day radii, taking one in which radius changes with a 
$\sqrt{\text{age}}$-dependence in the fiducial model based on~\citet[][see 
Fig.~\ref{fig:migration_schema} and discussion in~\S 
\ref{sec:methods:migration}]{Frankel2018, Frankel2020}. 
\par 
We assume SN yields and a SN Ia delay-time distribution based on 
a combination of theoretical and empirical constraints. The main free 
parameters are the star formation law parameterizing the SFE timescale 
$\tau_\star$ (see discussion in~\S~\ref{sec:methods:sfe}), the mass-loading 
factor~$\eta(R_\text{gal})$~describing the strength of outflows (assumed to be 
time-independent; see discussion in~\S~\ref{sec:methods:yields}), and the SFH. 
The first we choose from the observed~$\dot{\Sigma}_\star - \Sigma_\text{g}$ 
relation in local spirals~\citep{Bigiel2010, Leroy2013, Krumholz2018}. The 
second is chosen to reproduce the metallicity gradient as observed 
\citep{Daflon2009, Frinchaboy2013, Hayden2014, Weinberg2019}. Our fiducial 
model then has an inside-out SFH with e-folding timescales calibrated to the 
\citet{Sanchez2020} data (see discussion in~\S~\ref{sec:methods:sfhs}). 
Motivated by the results of~\citet{Mor2019} and~\citet{Isern2019} suggesting 
such an evolutionary history, we construct models which exhibit a recent burst 
in star formation on top of the base-line model, as well as a constant SFH 
model of purely theoretical interest. 
\par 
We find that when stellar migration proceeds in a manner in which a star's 
orbital radius changes continuously with time, the SN Ia rate as a function of 
both radius and time exhibits significant variability. The characteristic delay 
time of a single SN Ia event is~$\sim$1 Gyr~\citep{Maoz2012, Maoz2017}, and 
stars are migrating a significant distance in the radial direction on similar 
timescales in our models. The result is a SN Ia rate which, at fixed radius, 
tends to follow that which is expected from the SFH when averaged with time, 
but whose instantaneous value may be considerably larger or smaller. Our model 
predicts the amplitude of this variability to grow with increasing radius due 
to sampling noise and the inverse dependence of the stellar surface density on 
$R_\text{gal}$. We demonstrate that this is a mechamism with which truly young, 
super-solar [$\alpha$/Fe] stars can form. When the SN Ia rate increases or 
decreases, the Fe abundance in the ISM increases or 
decreases accordingly; this in turn affects the gas-phase [$\alpha$/Fe] ratio, 
and the stars which form at these times inherit these compositions. Of the 
young stars, those with the highest [$\alpha$/Fe] form at large~$R_\text{gal}$ 
($\gtrsim$~12 kpc) due to the radial dependence of the amplitude; a subsample 
of these stars can then migrate to the solar annulus. 
\par 
To our knowledge, this mechanism lends the first theoretical explanation of 
truly young $\alpha$-rich stars in the solar neighbourhood, revealed recently 
by the observations of the APOGEE survey~\citep{Martig2016, Feuillet2018, 
Feuillet2019, SilvaAguirre2018}.~\citet{SilvaAguirre2018} find that 
these stars have kinematics consistent with the rest of the high-$\alpha$ 
population, and postulate based on this that these stars are the consequence 
of stellar mergers or mass transfer events, making truly old stars simply 
appear younger. In a sample of 51 young~$\alpha$-rich red giants, 
\citet{Hekker2019} demonstrate using cabon-to-nitrogen ratios that a portion of 
these stars are indeed old, but that these effects cannot account for the 
entire population. We argue based on our results that the truly young ones 
formed at large~$R_\text{gal}$~at a time when the ISM was intrinsically 
$\alpha$-rich due simply to a deficit in SN Ia events caused by a net loss of 
white dwarf progenitors to stellar migration. We remark that our model would 
sugest that these stars have super-solar [$\alpha$/Fe] not because they are 
$\alpha$-rich, but rather that they are Fe-poor. 
\par 
We find that our model adequately reproduces the variations in MDFs with 
Galactocentric radius in the disc~\citep{Hayden2015}. Although there is a 
potential for improved agreement in the~$R_\text{gal}$~= 3 - 5 kpc bin, the 
model nonetheless performs well. With increasing~$\left|z\right|$, the 
prediction breaks down somewhat. Where the observational data show a 
convergence of the MDFs at all radii to a skew-positive distribution with 
mode([O/H])~$\approx$~mode([Fe/H])~$\approx$~-0.5, our model predicts the mode 
abundance in the inner Galaxy to decrease slightly, though not to the same 
extent as in the observations, while the distributions at larger~$R_\text{gal}$ 
are less affected (see Figs.~\ref{fig:mdf_3panel_fe} and~\ref{fig:mdf_3panel_o} 
and discussion in~\S~\ref{sec:obs_comp:mdfs}). While the model accounts for a 
portion of these effects, it cannot explain the entire~$z$-dependence of the 
MDF shape. 
\par 
We demonstrate the dependence of the relative frequency of high-$\alpha$ and 
low-$\alpha$ sequence stars on Galactic position (see, e.g., Fig. 4 of 
\citealp{Hayden2015}) is at least in part a consequence of stellar migration. 
In our fiducial inside-out SFH model, low [Fe/H], high [$\alpha$/Fe] stars 
are the dominant population at small~$R_\text{gal}$~and high~$\left|z\right|$; 
conversely, low [$\alpha$/Fe] stars are most common at large~$R_\text{gal}$ 
and low~$\left|z\right|$. We clarify that this is not an explanation for the 
\textit{origin} of the two sequences - only the spatial dependence thereof. 
In fact, our model is unable to account for the presence of the infamous 
[$\alpha$/Fe] dichotomy in any of the variants we've explored. While it is able 
to reproduce the broad nature of the [O/Fe] distributions at fixed [Fe/H] and 
may show a convincing two-peaked profile in a specific Galactic region, it 
fails to do so for the entire Galaxy at all metallicities; the principle 
failure is an overpredicted frequency of intermediate [$\alpha$/Fe] stars. This 
is in contrast to the findings of~\citet{Sharma2020}, who claim to reproduce 
the bimodality in a model assuming an inside-out SFH with stellar migration. 
However, they do not demonstrate that the enrichment history of their model 
follows self-consistently from their assumed SFH. We therefore argue that 
an inside-out SFH is not conducive to forming the abundance distributions 
observed in the Milky Way. Though we don't investigate such evolutionary 
pathways in the present paper, our models fail in such a manner that suggests 
the agreement can best be improved by the three-phase SFH of the two-infall 
model~\citep{Chiappini1997, Chiappini2001, Romano2010, Grisoni2017, 
Noguchi2018, Palla2020, Spitoni2016, Spitoni2018, Spitoni2019a, Spitoni2020, 
Spitoni2021}. We reserve an investigation into more sophisticated forms of the 
Galactic SFH for future work. 
\par 
We find that the age-[O/Fe] relation as reported by~\citet{Feuillet2019} is 
well-characterized by our inside-out SFH. In the case of our recent 
starburst models motivated by~\citet{Mor2019} and~\citet{Isern2019}, the 
elevation of the SFR necessitates an increase in [$\alpha$/Fe] for young 
stars owing to the increased rate of CCSNe before the onset of SN Ia associated 
with the starburst~\citep{Johnson2020}, introducing a trend which simply isn't 
seen in the observations. This suggests that recent studies finding an 
elevation in the 
Galactic SFR~$\sim$2 Gyr ago are at odds with chemical evolution models, which 
based on the monotonic nature of the observed AMR would put constraints on the 
amount of variability out to lookback times of~$\sim$8 Gyr. Lastly, we find 
that our model predicts the intrinsic scatter in the age-[$\alpha$/Fe] relation 
to increase with~$R_\text{gal}$; this traces back to the variability in the SN 
Ia rates having a higher amplitude in the outer Galaxy, which produces an 
in-situ population with a larger dynamic range in [O/Fe]. 
\par 
We find that the AMR (both age-[O/H] and age-[Fe/H]) in the solar annulus as 
measured by~\citet{Feuillet2019} is well-described by our inside-out SFH. 
However, when this comparison is extended to other Galactic regions, the 
inside-out model overpredicts ages in multiple regions and fails to reproduce 
the population-averaged trend throughout the disc. We demonstrate that our 
late-burst model can account for these discrepancies, suggesting that the 
observed AMR favors a model with a recent enhancement in the Galactic SFR. 
Somewhat confusingly, the impact of the late-burst model is such that it is 
convincingly rejected by the age-[O/Fe] relation but convincingly favored by 
the age-[O/H] and age-[Fe/H] relations. 
\par 
We thus conclude that no single model in the present paper can explain all of 
the observables of interest here. This suggests that 
conventional assumptions about the evolution of the Milky Way, such as an 
inside-out SFH with stellar migration, are not sufficiently accurate to 
understand the enrichment history of the Milky Way in detail. This is an 
indication that at present there is more astrophysical information in already 
collected observations than the most recent GCE models can explain. It's likely 
our models are missing at least one key component with a significant impact on 
the predicted abundances. 
\par 
Lastly, we remark on the low number of multi-zone chemical evolution models in 
the literature, some with and some without migration. In this paper, we present 
only a handful of models whose predictions can be calculated with a combined 
CPU-time comparable to a single working day. These models make straight-forward 
predictions which can easily be compared to publicly-available observed data. 
Though they are extremely useful in many respects, these medium resolution, 
medium computational expense techniques can test assumptions about the 
evolutionary history of the Milky Way with more control over the parameters and 
much less computational expense than the higher overhead hydrodynamical 
simulations; our models here constitute an example of a combination of the two. 
\par 
\texttt{VICE} is publicly available and open-source;\footnote{
	Install (PyPI): \url{https://pypi.org/project/vice} \\ 
	Documentation: \url{https://vice-astro.readthedocs.io} \\ 
	Source Code: \url{https://github.com/giganano/VICE.git} 
} it can be installed in a~\texttt{Unix} terminal via~\texttt{pip install vice}. 
\texttt{Python} code which runs the simulations presented in this paper is 
included as supplementary material in the~\texttt{GitHub} repository; our 
models can be ran directly from a terminal without modifying the source code, 
and are capable of predicting abundances for~$\sim$2 million stellar 
populations in~$\sim$2.5 CPU-hours running on a single core on personal 
computers.

\section{Acknowledgements} 
\label{sec:acknowledgements} 
We acknowledge valuable discussion with, in no particular order, Emily 
Griffith, Jennifer Johnson, Todd Thompson, Jiayi Sun, Amy Sardone, Adam Leroy, 
Grace Olivier, the Ohio State Astronomy Gas, Galaxies, and Feedback group, and 
various participants of the SDSS Gotham 2020 virtual collaboration meeting and 
the virtual 236th meeting of the American Astronomical Society. This work was 
supported in part by National Science Foundation grant AST-1909841. D.H.W. 
is grateful for the hospitality of the Institute for Advanced Study and the 
support of the W.M. Keck Foundation. 
\par 
In this paper we have made use of data from SDSS-IV APOGEE-2 DR16. 
Funding for the Sloan Digital Sky 
Survey IV has been provided by the 
Alfred P. Sloan Foundation, the U.S. 
Department of Energy Office of 
Science, and the Participating 
Institutions. 
\par 
SDSS-IV acknowledges support and 
resources from the Center for High 
Performance Computing  at the 
University of Utah. The SDSS 
website is~\url{www.sdss.org}.
\par 
SDSS-IV is managed by the 
Astrophysical Research Consortium 
for the Participating Institutions 
of the SDSS Collaboration including 
the Brazilian Participation Group, 
the Carnegie Institution for Science, 
Carnegie Mellon University, Center for 
Astrophysics | Harvard \& 
Smithsonian, the Chilean Participation 
Group, the French Participation Group, 
Instituto de Astrof\'isica de 
Canarias, The Johns Hopkins 
University, Kavli Institute for the 
Physics and Mathematics of the 
Universe (IPMU) / University of 
Tokyo, the Korean Participation Group, 
Lawrence Berkeley National Laboratory, 
Leibniz Institut f\"ur Astrophysik 
Potsdam (AIP),  Max-Planck-Institut 
f\"ur Astronomie (MPIA Heidelberg), 
Max-Planck-Institut f\"ur 
Astrophysik (MPA Garching), 
Max-Planck-Institut f\"ur 
Extraterrestrische Physik (MPE), 
National Astronomical Observatories of 
China, New Mexico State University, 
New York University, University of 
Notre Dame, Observat\'ario 
Nacional / MCTI, The Ohio State 
University, Pennsylvania State 
University, Shanghai 
Astronomical Observatory, United 
Kingdom Participation Group, 
Universidad Nacional Aut\'onoma 
de M\'exico, University of Arizona, 
University of Colorado Boulder, 
University of Oxford, University of 
Portsmouth, University of Utah, 
University of Virginia, University 
of Washington, University of 
Wisconsin, Vanderbilt University, 
and Yale University.

\textit{Software}: Matplotlib~\citep{Matplotlib}; Astropy~\citep{Astropy2013, 
Astropy2018}; NumPy~\citep{NumPy}.

\section{Data Availability} 
\label{sec:data_availability} 
\texttt{VICE} is open-source software, and the code which computes abundances 
for our models is publicly available as well. In the GitHub repository, we 
provide detailed instructions on how to run our models and variations thereof. 
All observational data appearing in this paper is publicly available, and is 
also included with the source code for our models and figures.

\begin{appendices}

\section{Normalizing the Star Formation History} 
\label{sec:normalize_sfh} 
In this appendix, we derive a prescription for calculating the prefactors of an 
adopted star formation history (SFH) for each annulus in our models. As 
mentioned in~\S~\ref{sec:methods:sfhs}, this procedure requires a unitless 
description of the time-dependence of the SFH in each annulus, denoted 
$f(t|R_\text{gal})$, and a unitless description denoting the radial dependence 
of the stellar surface density~$g(R_\text{gal})$. By additionally selecting a 
total stellar mass of the present day model Galaxy, the solution to the 
detailed form of the star formation history 
$\dot{\Sigma}_\star(t, R_\text{gal})$ is unique. With this approach, we assume 
that stellar migration does not significantly impact the form of 
$g(R_\text{gal})$, an assumption we demonstrate to be accurate in~\S 
\ref{sec:methods:surface_density_gradient}. 
\par 
The surface density of star formation with units of mass per area per time can 
be expressed in terms of~$f(t|R_\text{gal})$ as: 
\begin{equation} 
\dot{\Sigma}_\star(t, R_\text{gal}) = \dot{\Sigma}_\star(t = 0, R_\text{gal}) 
f(t|R_\text{gal}) 
\label{eq:sfh_terms_of_f} 
\end{equation} 
and the present-day radial surface density gradient with units of mass per area 
as: 
\begin{equation} 
\Sigma_\star(R_\text{gal}) = \Sigma_\star(R_\text{gal} = 0) g(R_\text{gal}) 
\label{eq:sigma_terms_of_g}  
\end{equation} 
The integral of~$\dot{\Sigma}_\star$ with time should yield the surface density 
gradient at a given radius~$R_\text{gal}$, up to a prefactor accounting for the 
return of stellar envelopes to the interstellar medium (ISM): 
\begin{subequations}\begin{align} 
\Sigma_\star(R_\text{gal}) &= (1 - r)\int_0^T \dot{\Sigma}_\star(t, 
R_\text{gal}) dt 
\\ 
&= (1 - r) \dot{\Sigma}_\star(t = 0, R_\text{gal})\int_0^T f(t|R_\text{gal}) dt 
\\ 
\dot{\Sigma}_\star(t = 0, R_\text{gal}) &= \Sigma_\star(R_\text{gal}) 
\left[(1 - r) \int_0^T f(t|R_\text{gal})dt\right]^{-1} 
\\ 
&= \Sigma_\star(R_\text{gal} = 0)g(R_\text{gal}) \left[(1 - r) \int_0^T 
f(t|R_\text{gal})\right]^{-1} 
\label{eq:intermediate_1} 
\end{align}\end{subequations} 
where~$(1 - r) \approx 0.6$~is an adequate approximation for a 
\citetalias{Kroupa2001} IMF~\citep[][see discussion in their~\S 
2.2]{Weinberg2017}. This expression relates the two unkowns introduced by 
equations~\refp{eq:sfh_terms_of_f} and~\refp{eq:sigma_terms_of_g}. We continue 
by asserting that the integral of the stellar surface density over the area of 
the disc should be equal to the present-day stellar mass of the Milky Way: 
\begin{subequations}\begin{align} 
M_\star^\text{MW} &= \int_0^R \Sigma_\star(R_\text{gal}) 2\pi R_\text{gal} 
dR_\text{gal} 
\\ 
&= \Sigma_\star(R_\text{gal} = 0) \int_0^R g(R_\text{gal}) 2\pi R_\text{gal} 
dR_\text{gal} 
\\ 
\Sigma_\star(R_\text{gal} = 0) &= M_\star^\text{MW} \left[\int_0^R 
g(R_\text{gal}) 2\pi R_\text{gal}dR_\text{gal}\right]^{-1} 
\label{eq:intermediate_2} 
\end{align}\end{subequations} 
\par 
Now plugging equation~\refp{eq:intermediate_2} into equation 
\refp{eq:intermediate_1}, and then that into equation~\refp{eq:sfh_terms_of_f} 
yields the desired result: 
\begin{subequations}\begin{align} 
&\dot{\Sigma}_\star(t, R_\text{gal}) = Af(t|R_\text{gal})g(R_\text{gal}) 
\\ 
&A = M_\star^\text{MW}\left[(1 - r) \int_0^R g(R_\text{gal})2\pi R_\text{gal} 
dR_\text{gal} \int_0^T f(t|R_\text{gal})dt\right]^{-1} 
\end{align}\end{subequations} 
where the upper limits should be the maximum radius of star formation and the 
end time of the simulation (15.5 kpc and 12.2 Gyr in this paper). This result 
makes intuitive sense, simply stating that the required normalization of 
$f(t|R_\text{gal})$~is specified by two things: the total stellar mass of the 
Galaxy and how steep the stellar density falls with increasing radius. As long 
as the assumption that stellar migration does not significantly alter the form 
of~$g(R_\text{gal})$~is not violated, this procedure can be used to calculate 
prefactors for future models of disc galaxies.

\end{appendices}

\bibliographystyle{mnras} 
\bibliography{draft1}

\label{lastpage} 
\end{document}

### 2021-08-04 chemev/MWbimodality/paper/draft2/abstract.tex
migration paper referee response

\documentclass[draft2.tex]{subfiles} 
\begin{document}

\begin{abstract} 
We develop a hybrid model of galactic chemical evolution that combines a 
multi-ring computation of chemical enrichment with a prescription for stellar 
migration and the vertical distribution of stellar populations informed by a 
cosmological hydrodynamic disc galaxy simulation. 
Our fiducial model adopts empirically motivated forms of the star formation law 
and star formation history, with a gradient in outflow mass loading tuned to 
reproduce the observed metallicity gradient. 
With this approach, the model reproduces many of the striking qualitative 
features of the Milky Way disc's abundance structure: 
(i) the dependence of the [O/Fe]-[Fe/H] distribution on radius~\rgal~and 
midplane distance~\absz; 
(ii) the changing shapes of the [O/H] and [Fe/H] distributions 
with~\rgal~and~\absz; 
(iii) a broad distribution of [O/Fe] at sub-solar metallicity and changes in 
the [O/Fe] distribution with~\rgal,~\absz, and [Fe/H]; 
(iv) a tight correlation between [O/Fe] and stellar age for [O/Fe]~$>$~0.1; 
(v) a population of young and intermediate-age~$\alpha$-enhanced stars caused 
by migration-induced variability in the Type Ia supernova rate; 
(vi) non-monotonic age-[O/H] and age-[Fe/H] relations, with large scatter and a 
median age of~$\sim$4 Gyr near solar metallicity. 
Observationally motivated models with an enhanced star formation rate~$\sim$2 
Gyr ago improve agreement with the observed age-[Fe/H] and age-[O/H] relations, 
but worsen agreement with the observed age-[O/Fe] relation. 
None of our models predict an [O/Fe] distribution with the distinct bimodality 
seen in the observations, suggesting that more dramatic evolutionary pathways 
are required. 
All code and tables used for our models are publicly available through the 
\texttt{Versatile Integrator for Chemical Evolution} (\texttt{VICE}; 
\url{https://pypi.org/project/vice}). 
\end{abstract}

\end{document}

### 2021-08-04 chemev/MWbimodality/paper/draft2/acknowledgements.tex
migration paper referee response

--- 2021-08-04 chemev/MWbimodality/paper/draft1/draft1.tex
@@
-\documentclass[fleqn, usenatbib]{mnras} 
-\usepackage{newtxtext, newtxmath} 	% Required for MNRAS 
-\usepackage[T1]{fontenc} 
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{mathtools}
-\usepackage{multicol}
-\usepackage{bm}
-\usepackage{pdflscape}
-\usepackage{natbib}
-\usepackage[section]{placeins}
-\usepackage{lipsum}
-\usepackage{etoolbox} 
-\usepackage{tabularx} 
-\usepackage{xcolor} 
-\usepackage[toc, page]{appendix} 
-% \hypersetup{draft} 
-% \linespread{1.8} 
-\hypersetup{ 
-	colorlinks		= true, 
-	urlcolor 		= blue, 
-	linkcolor 		= blue, 
-	citecolor 		= blue 
-}
-
-\newcommand{\ddfrac}[2]{\frac{\displaystyle #1}{\displaystyle #2}} 
-\newcommand{\refp}[1]{(\ref{#1})} 
-\newcommand{\msun}{\ensuremath{\text{M}_\odot}} 
-\newcommand{\persqkpc}{\ensuremath{\text{kpc}^{-2}}} 
-\providecommand{\noopsort}[1]{} 
-\graphicspath{ {../plots/} }
-
-\interfootnotelinepenalty = 10000 
-\defcitealias{Kroupa2001}{Kroupa} 
-\defcitealias{Salpeter1955}{Salpeter}
-
-\title[Stellar Migration and Chemical Enrichment]{Stellar Migration and 
-Chemical Enrichment in the Milky Way Disc: A Hybrid Model}
-
-\author[J.W. Johnson et al.]{
-	James W. Johnson,$^{1}$\thanks{Contanct e-mail: \href{mailto:
-	johnson.7419@osu.edu}{johnson.7419@osu.edu}} 
-	David H. Weinberg,$^{1, 2, 3}$ 
-	Fiorenzo Vincenzo,$^{2}$ 
-	Jonathan C. Bird,$^{4}$ 
-	\newauthor 
-	Sarah R. Loebman,$^{5}$ 
-	Alyson Brooks,$^{6}$ 
-	Thomas R. Quinn,$^{7}$ 
-	Charlotte R. Christensen,$^{8}$ 
-	\newauthor 
-	et al.?
-	\\
-	$^{1}$ Department of Astronomy, The Ohio State University, 
-	140 W. 18th Ave., Columbus, OH, 43210, USA 
-	\\ 
-	$^{2}$ Center for Cosmology and Astroparticle Physics (CCAPP), 
-	The Ohio State University, 191 W. Woodruff Ave, Columbus, OH, 43210, USA 
-	\\ 
-	$^{3}$ Institute for Advanced Study, 1 Einstein Dr., Princeton, NJ, 08540, 
-	USA 
-	\\ 
-	$^{4}$ Department of Physics \& Astronomy, Vanderbilt University, 
-	2301 Vanderbilt Place, Nashville, TN, 37235, USA 
-	\\ 
-	$^{5}$ Department of Physics, University of California Merced, 
-	5200 North Lake Rd., Merced, CA, 95343, USA 
-	\\ 
-	$^{6}$ Department of Physics \& Astronomy, Rutgers University, 136 
-	Frelinghuysen Rd, Piscataway, NJ, 08854, USA 
-	\\ 
-	$^{7}$ Department of Astronomy, University of Washinton, Box 351580, 
-	Seattle, WA, 98195, USA 
-	\\ 
-	$^{8}$ Department of Physics, Grinnell College, 1116 8th Ave., Grinnell, 
-	IA, 50112, USA 
-}
-
-\date{Accepted XXX; Received YYY; in original form ZZZ} 
-\pubyear{2020}
-
+\documentclass[draft2.tex]{subfiles} 
 \begin{document}
-\label{firstpage} 
-\pagerange{\pageref{firstpage}--\pageref{lastpage}} 
-\maketitle
-
-\begin{abstract} 
-We investigate the impact of stellar migration on galactic chemical evolution 
-models, considering a handful of assumptions for the star formation history 
-and time-dependence of radial migration based on a zoom-in, hydrodynamical 
-simulation of galaxy evolution. When stars migrate with a smooth, continuous 
-time dependence, the type Ia supernova rate exhibits significant variability in 
-our models. We demonstrate that this is a means with which young, super-solar 
-[$\alpha$/Fe] in the solar neighbourhood can arise naturally out of inside-out 
-Galaxy growth with stellar migration. We find 
-that the observed age-[$\alpha$/Fe] relation is well-fit by an inside-out star 
-formation history, while the age-[$\alpha$/H] and age-[Fe/H] relations are 
-well-fit by a late starburst model; no one model investigated here fits both 
-simultaneously. Our model successfully reproduces the broad nature of the 
-[$\alpha$/Fe] distribution at fixed [Fe/H] in a given Galactic region; however, 
-an overprediction of the frequency of intermediate [$\alpha$/Fe] stars prevents 
-it from explaining the observed results in detail. This suggests 
-that inside-out galaxy growth combined with stellar migration, even with a late 
-starburst, is not conducive to forming the infamous bimodality as it is 
-observed. We postulate that more dramatic evolutionary scenarios (e.g. a 
-two-infall model) may be necessary to describe the observed results. In 
-conducting this analysis, we developed and made use of newly released features 
-in the \texttt{Versatile Integrator for Chemical Evolution} (\texttt{VICE}) 
-which are built to handle these models under a wide variety of 
-assumptions. \texttt{VICE} is publicly available 
-at~\url{https://pypi.org/project/vice}. 
-\end{abstract}
-
-\begin{keywords} 
-methods: numerical -- galaxies: abundances, evolution, star formation, stellar 
-content 
-\end{keywords}
-
-\section{Introduction} 
-\label{sec:intro} 
-The orbits of stars are not unchanging. While it has been known for some time 
-that stars undergo radial migration (e.g.~\citealp*{Wielen1996}; 
-\citealp{Roskar2008a,Loebman2011,Minchev2012}), the true impact of this process 
-on galactic chemical evolution (GCE) remains under debate. By mixing stellar 
-populations which formed in Galactic regions with significantly different 
-enrichment histories, in principle the impact could be considerable. While some 
-authors argue that radial migration has only a small impact on GCE 
-(e.g.~\citealp*{Kubryk2013};~\citealp{Khoperskov2021}), there are others who 
-argue the contrary (e.g.~\citealp{Schoenrich2009};~\citealp*{Sharma2020}). 
-Aside from the chemodynamical simulations involving N-body integrations 
-\citep[e.g.][]{Kubryk2013, Vincenzo2020, Khoperskov2021}, there are to date 
-only a handful of GCE models that take this effect into account (e.g. 
-\citealp{Matteucci1989, Schoenrich2009};~\citealp*{Minchev2013}; 
-\citealp{Sharma2020}). These studies treat the Milky Way as a series of 
-concentric annuli, each described by a conventional one-zone GCE model with 
-parameters that change from annulus to annulus. In the resultant ``multi-zone'' 
-model, stars and gas can migrate between zones under some prescription to 
-account for time-dependent mixing processes. We retain such methodology in this 
-paper, allowing star particles from a hydrodynamical simulation ran from 
-cosmological initial conditions to inform our implemented mixing process; 
-\citet{Minchev2013} employ a similar technique. With parameters tuned to 
-reproduce certain observed results (e.g. abundance and surface density 
-gradients), we can then assess the model predictions to address the following 
-question: when combining simple, conventional assumptions about the star 
-formation and dynamical histories of the Milky Way, what observed results can 
-be replicated? In the present paper, we focus on the following observables: 
-metallicity distributions functions (MDFs) and abundance gradients, the 
-[$\alpha$/Fe] bimodality, the age-metallicity relation (AMR), and the young, 
-$\alpha$-rich population. 
-\par 
-Stars in the inner regions of the Milky Way tend to be more metal-rich than 
-those found in the outskirts~\citep{Nordstroem2004b, Daflon2009, 
-Frinchaboy2013, Hayden2014}, with slight variations in quantitative results 
-based on what type of stars are considered and what metallicity tracers are 
-analysed. Such behavior is also seen in the gas-phase gradients of 
-low-redshift spirals (see, e.g., the results from the CHAOS project using HII 
-regions;~\citealp{Berg2015, Berg2020}). Using the 12th data release of the 
-Apache Point Observatory Galaxy Evolution Experiment (APOGEE), 
-\citet{Hayden2015} demonstrate that the observed MDF has a metal-rich mode and 
-is skew-negative in the inner galaxy (and conversely, metal-poor and 
-skew-positive in the outer galaxy). These variations in the skewness of the 
-distributions with Galactocentric radius are usually attribute to the migration 
-of metal-rich (metal-poor) stars from smaller (larger) orbital radii. Similar 
-arguments are used by~\citet{Sellwood2002} to interpret the results of 
-\citet{Edvardsson1993} on scatter in the age-metallicity relation observed in 
-the solar neighbourhood. 
-\par 
-Abundance gradients have been the focus of many studies and are quantified 
-rather extensively, but their origin is somewhat up for debate. Applying the 
-analytic models of~\citet*{Weinberg2017}, one could argue that the gradient 
-arises out of variations in the local gas-phase equilibrium abundance as a 
-function of Galactocentric radius. For $\alpha$-elements, the equilibrium 
-abundance is determined to first order by their yield and the efficiency of 
-outflows in removing metals from the star forming reservoir. With a stronger 
-gravitational potential in the inner regions of the Galaxy, one might 
-reasonably expect outflows to be weaker there, thereby increasing the 
-equilibrium abundance.~\citet{Nidever2014} used such an approach to reproduce 
-the width of the [Fe/H] distribution for low-$\alpha$ sequence stars in 
-APOGEE. However, recent chemical evolution models have successfully replicated 
-the gradient with no outflowing winds at all~\citep[e.g.][]{Minchev2013, 
-Spitoni2019a}. This is based on arguments from~\citet{Melioli2008, Melioli2009}, 
-\citet*{Spitoni2008}, and~\citet{Spitoni2009} who studied Galactic fountains 
-using hydrodynamical simulations and numerical models, finding that ejected 
-metals tend to reaccrete to a Galactocentric radius similar to where they 
-originated. With this result, some authors argue that such outflows do not 
-significantly alter the chemical evolution of a Galactic disc, and that instead 
-the gradient arises from the higher normalization of the star formation history 
-in the inner Galaxy. 
-\par 
-Like radial abundance gradients, the reality of the infamous [$\alpha$/Fe] 
-dichotomy is well established (in Gaia-ESO:~\citealp{Recio-Blanco2014, 
-Rojas-Arriagada2017}; in APOGEE:~\citealp{Nidever2014, Hayden2015, 
-Weinberg2019}), but its origin is a topic of intense debate. In general, stars 
-in the Milky Way tend to fall in one of two populations - the roughly solar 
-[Fe/H], solar [$\alpha$/Fe] stars commonly referred to as the low-$\alpha$ 
-sequence, and the high-$\alpha$ sequence made up of sub-solar [Fe/H], 
-super-solar [$\alpha$/Fe] stars. Recently explored with more current data by 
-\citet{Sharma2020}, the notion that it could in principle arise out of radial 
-migration traces back to~\citet{Schoenrich2009}. Applying the analytic models 
-of~\citet{Weinberg2017}, an alternative pathway to such abundance patterns is 
-by an increase in the strength of outflows at late times. Such an evolutionary 
-model would predict a decrease in the equilibrium abundance, forming stars 
-along the low-$\alpha$ sequence. This scenario has not yet been explored in 
-combination with radial migration. 
-\par 
-Other authors argue that more dramatic evolutionary events are necessary to 
-explain the observed results, such as the two-infall model 
-(\citealp*{Chiappini1997, Chiappini2001};~\citealp{Romano2010, Grisoni2017, 
-Noguchi2018, Palla2020, Spitoni2016, Spitoni2018}). 
-In these models, the high-$\alpha$ sequence forms during the Galaxy's initial 
-collapse before feedback processes shut off star formation and expel gas into 
-the Galactic halo. Then, this material can cool and reaccrete along with 
-additional, metal-poor gas from the intergalactic medium, producing a second 
-episode of star formation. The dilution associated with the second accretion 
-event lowers the gas-phase Fe abundance at fixed [$\alpha$/Fe], forming stars 
-along the low-$\alpha$ sequence.~\citet{Spitoni2019a, Spitoni2020} demonstrated 
-using the APOKASC sample~\citep{Pinsonneault2014, SilvaAguirre2018} that such 
-models can explain the abundances observed in the solar annulus. Although 
-\citet{Spitoni2021} recently extended this model to Galactic regions beyond 
-the solar annulus, their model did not account for the mixing of stellar 
-populations between regions. Though they invoke~\citet{Kubryk2013} and 
-\citet{Khoperskov2021} as arguments that it shouldn't impact their results, 
-this nonetheless means that two-infall models have not yet been explored in 
-combination with a treatment for stellar migration. 
-\par 
-Recent cosmological zoom-in simulations have found results qualitatively 
-similar to the arguments of~\citet{Spitoni2019a, Spitoni2020, Spitoni2021}. 
-Using the Auriga simulation suite~\citep{Grand2017},~\citet{Grand2018} 
-demonstrate that an early, accretion induced starburst can populate the 
-high-$\alpha$ sequence, followed by low-level, sustained star formation on the 
-low-$\alpha$ sequence. In this pathway, there is either a rapid transition 
-between the two phases, ensuring the chemical space between the sequences is 
-relatively unpopulated, or low-metallicity gas accretion dilutes the star 
-forming reservoir at fixed [$\alpha$/Fe], populating the low [Fe/H], low 
-[$\alpha$/Fe] portion of the low-$\alpha$ sequence.~\citet{Buck2020b} finds 
-the dilution scenario in the NIHAO simulation suite as well~\citep{Wang2015, 
-Buck2020a}. Although the~\citet{Spitoni2021} model did not implement mixing of 
-stellar populations, these studies using hydrodynamical simulations would 
-suggest pathways qualitatively similar to their two-infall model. 
-\par 
-Contrary to this scenario,~\citet{Clarke2019} demonstrate that star formation 
-proceeded in clumps in an SPH simulation using GASOLINE~\citep*{Wadsley2017}. 
-These clumps self-enrich, forming stars on the high-$\alpha$ sequence due to 
-the perturbed ratio of core collapse to type Ia supernova rates within the 
-star forming regions. The more spatially extended, smooth star formation 
-populates the low-$\alpha$ sequence. Suffice it to say that there are no 
-shortage of models which reproduce the dichotomy, but only those done with 
-hydrodynamical simulations and a handful of others 
-\citep[e.g.][]{Schoenrich2009, Minchev2013, Sharma2020} have taken into account 
-stellar migration. 
-\par 
-Besides abundance gradients and the [$\alpha$/Fe] dichotomy, another 
-observable of interest in this paper is the age-metallicity relation (AMR): the 
-correlation between stellar ages and metallicities. The observed AMR in the 
-solar neighbourhood is known to exhibit considerable intrinsic scatter 
-\citep{Edvardsson1993}; this is usually attributed to radial migration of 
-metal-rich (metal-poor) stars from smaller (larger) Galactocentric radii 
-\citep{Sellwood2002, Haywood2008, Roskar2008b, Schoenrich2009}. 
-In the solar neighbourhood,~\citet{Feuillet2018} reveal that super-solar 
-metallicity stars are statistically older than solar metallicity stars (see 
-their Fig. 3). This contrasts with the predictions of simple one-zone models of 
-GCE where enrichment proceeds alongside star formation, yielding a monotonic 
-AMR~\citep[e.g.][]{Andrews2017, Weinberg2017}. Although one-zone models of 
-starbursts can predict a non-monotonic AMR due to the effect of dilution 
-\citep{Johnson2020}, by construction they do not predict multiple abundances at 
-fixed age as~\citet{Feuillet2018} reports. Using the~\citet{Weinberg2017} 
-analytic models,~\citet{Feuillet2018} argues that this is a consequence of 
-radial migration. For a smooth star formation history, the youngest stars at a 
-given radius will have compositions reflective of the local equilibrium 
-abundance; only stars born at different radii will have different compositions, 
-and only the old ones will have had time to migration to the solar annulus. 
-\par 
-While the presence of old-metal rich stars in the solar annulus is peculiar 
-because they are at odds with one-zone models of chemical evolution, the 
-presence of young, $\alpha$-rich stars is interesting for the same reason. 
-For a smooth star formation history, the delayed nature of type Ia supernovae 
-and their Fe production cause [$\alpha$/Fe] to decrease with time, predicting 
-an age-[$\alpha$/Fe] relation that should increase monotonically with stellar 
-age. However, these~$\sim$few Gyr old stars with [$\alpha$/Fe]~$\approx$~+0.1 - 
-0.2 stars have been found using stellar ages estimated from carbon-to-nitrogen 
-ratios~\citep{Martig2016}, isochrone matching~\citep{Feuillet2018, 
-Feuillet2019}, and with the asterosesmic ages of the original APOKASC catalog 
-\citep{Chiappini2015, SilvaAguirre2018, Pinsonneault2014}. 
-\citet{SilvaAguirre2018} demonstrate that these stars have kinematics similar 
-to the rest of the high-$\alpha$ population, postulating that they may be 
-the consequence of stellar mergers or mass transfer events, making truly old 
-stars simply appear younger. In a sample of 51 young, $\alpha$-enhanced red 
-giant stars,~\citet{Hekker2019} conclude that a portion of these stars have 
-carbon-to-nitrogen ratios consistent with mass transfer events, but that this 
-cannot account for the entire population. This suggests that the remaining 
-stars are either truly young or the result of mergers on the main sequence. 
-If not, then a theoretical explanation for the origin of these stars remains 
-a mystery. 
-\par 
-Alternatively, a recent starburst event could have produced these stars. 
-\citet{Mor2019} infer a factor of~$\sim$2 enhancement in the star formation 
-history (SFH) of the Milky Way~$\sim$2 Gyr ago by comparing population 
-synthesis models to observed stellar luminosity functions and colour-magnitude 
-diagrams from Gaia data~\citep{GaiaDR2}.~\citet{Isern2019} reach similar 
-conclusions by modeling the white dwarf luminosity function in the solar 
-neighbourhood with Gaia parallaxes. Motivated by these results, 
-\citet{Johnson2020} demonstrate using one-zone chemical evolution models that 
-a recent starburst of this nature can produce similarly young,~$\alpha$-rich 
-stars. However, the caveat to this interpretation is that the starburst must be 
-sufficiently localized such that the resultant stellar populations remain 
-outliers from an otherwise monotonically increasing age-[$\alpha$/Fe] relation. 
-\par 
-The impact of such evolutionary histories combined with stellar migration is, 
-to our knowledge, yet unexplored in the literature. A viable model for the 
-detailed enrichment history of the Milky Way would simultaneously explain all 
-of these observed results and their variations between Galactic regions, while 
-also taking into account effects like mixing and observational systematics. On 
-top of this, it must self-consistently calculcate enrichment rates from adopted 
-nucleosynthetic yields and the SFH. In this paper, we aim to 
-assess the extent to which conventional assumptions about the evolutionary 
-history of the Milky Way can account for these results, entertaining a 
-handful of assumptions describing the SFH and time-dependence of stellar 
-radial migration. 
-\par 
-Motivated by the general result that galaxies grow in radius with time 
-(i.e. ``inside-out'' growth;~\citealp{Bird2013}), our base-line model has a 
-star formation history (SFH) whose e-folding timescales grow with 
-Galactocentric radius. Based on the findings of~\citet{Mor2019} and 
-\citet{Isern2019}, we also construct models in which a late starburst is 
-imposed atop the inside-out SFH. In one model, this starburst occurs in all 
-annuli, and in another, loosely informed by the findings of 
-\citet{Vincenzo2020} suggesting such a radial dependence to accretion, it 
-occurs only at~$\geq$6 kpc. We also construct a model in which the SFH is 
-constant at a given Galactocentric radius; these models are interesting from a 
-theoretical perspective in that they quantify the impact of stellar migration 
-without the effects of a time-dependent SFH.
-
-\section{Methods} 
-\label{sec:methods} 
-To fulfill the goals of this paper, we develop and make use of newly released 
-features within the~\texttt{Versatile Integrator for Chemical Evolution} 
-(\texttt{VICE};~\citealp{Johnson2020}). These features are designed to handle 
-models such as these with a wide range of flexibility. We reserve a description 
-of~\texttt{VICE}'s migration algorithm and our simulation parameters for~\S 
-\ref{sec:methods:migration}, first describing our sample of star particles from 
-the hydrodynamical simulation. 
-\par 
-Although we make use of a hydrodynamical 
-simulation to drive stellar migration, we do~\textit{not} make use of its SFH. 
-While our study employs similar techniques as~\citet{Minchev2013}, our differs 
-in this subtle aspect. An alternative to modeling radial migration based on a 
-hydrodynamical simulation is to invoke dynamical arguments; 
-\citet{Schoenrich2009} and~\citet{Sharma2020} take such an approach. This 
-method, however, introduces free parameters which then require fitting to 
-data. An advantage of our technique is that there are no free parameters 
-introduced to the model; furthermore, it's unclear the extent to which the fit 
-biases the model into agreement with parts of the data not involved in the 
-fitting process. The dynamical history of a hydrodynamical simulation is also 
-motivated by first principles in that it models gravitational interactions via 
-an N-body integration. The primary disadvantage of this approach is a 
-consequence of the lack of free parameters - the model is rigid, and we cannot 
-explore slight variations. However, in principle one could compare the 
-predictions made by our chemical evolution models when ran using different 
-hydrodynamical simulations. We emphasize that a hydrodynamical simulation 
-\textit{only} informs the mixing processes in our models, and there is no 
-N-body integration involved in our models aside from that which was used to run 
-the hydrodynamical simulation in the first place.
-
-\subsection{The Hydrodynamical Simulation} 
-\label{sec:methods:h277} 
-In this paper we make use of star particles from the~\texttt{h277} simulation 
-\citep{Christensen2012, Zolotov2012, Loebman2012, Loebman2014, Brooks2014}. 
-Recently employed to study the stellar age-velocity relationship, a synopsis of 
-its detailed simulation parameters and cosmological model can found in~\S 2 of 
-\citet{Bird2020}. We do not include any discussion of these details here, 
-instead focusing on how we vet the sample of star particles for use in our 
-chemical evolution models. 
-\par 
-It is of particular important to have accurately measured formation radii for 
-each star particle that we use in our analysis.~\texttt{h277} did not record 
-the exact birth radius of each star particle; however, each star particle does 
-have an accurate age at each snapshot. Since stellar orbits are unlikely to 
-change significantly in an adequately short time interval, the radii of 
-sufficiently young stars in their first snapshot are reasonable approximations 
-of their birth radii. We therefore restrict our sample to those with an age at 
-first snapshot of~$\leq$~150 Myr, and adopt their Galactocentric radius at that 
-time as their birth radius. We have also conducted this analysis with a maximum 
-age at first snapshot of 50 Myr, and found similar results, suggesting that 
-these time intervals are short enough to not impact our conclusions. In 
-practice, we find that 150 Myr also provides with an adequately large number of 
-star particles to sample from. Of the star particles that remain after imposing 
-this cut, the oldest one is 12.26 Gyr old at the present day. Our model can 
-only apply on timescales as long as or shorter than the full range of ages of 
-the sample of star particles; we therefore subtract 1.5 Gyr from the formation 
-times of all star particles, allowing~$T$~= 0 in our models to correspond to 
-$T$~= 1.5 Gyr in~\texttt{h277}. As a consequence, our disc models trace the 
-chemical evolution of the Galaxy out to a lookback time of~$\sim$12.2 Gyr, or a 
-redshift of~$z \approx$~3, placing the onset of star formation at that time. 
-\par 
-We further restrict our sample of star particles to only those with both 
-formation and final radii of~$R_\text{gal} \leq$~20 kpc, and to have formed 
-within~$\left|z\right|\leq$~3 kpc of the disc midplane. These criteria ensure 
-that we're only using star particles which formed in-situ. While it's possible 
-that some star particles formed in a dwarf galaxy as it was infalling, a 
-scenario which would satisfy these requirements, these star particles are few 
-in number, and are only relevant at large~$R_\text{gal}$ and high ages - a 
-region of parameter space where few stars form anyway. 
-\par 
-Based on a kinematic decomposition performed on the present-day phase space 
-distribution of the~\texttt{h277} star particles, we include all those with 
-bulge, pseudobulge, and disc-like kinematics, excluding halo stars. While we're 
-not modeling the evolution of the bulge here, these star particles are 
-overwhelmingly located at~$R_\text{gal}\leq$~3 kpc at the present day anyway; 
-here we're much more interersted in~$R_\text{gal}\geq$~3 kpc since we're 
-modeling the evolution of the disc. These cuts yield a sample of 3,000,556 star 
-particles from~\texttt{h277}. 
-\par 
-\texttt{h277} had a transient bar during its evolution, but does not have one 
-at~$z$ = 0 ({\color{red} citation?}). This is a noteworthy difference between 
-our model and that of~\citet{Minchev2013}, and by extension the 
-\citet*{Minchev2014} and~\citet{Minchev2017} studies which use it as well, 
-because they selected a hydrodynamical simulation of a galaxy specifically so 
-that it would have a strong bar at~$z$ = 0; the transient bar in~\texttt{h277} 
-was not strong. This could mean that the dynamical 
-history of our model Galaxy does not reflect that of~\citet{Minchev2013} and 
-perhaps the Milky Way itself. However, the difference is likely within the 
-uncertainties of the current understanding of the Milky Way's dynamical 
-history. Although an investigation on the impact of bar evolution on stellar 
-migration and thus chemical evolution is outside the scope of this paper, it is 
-an interesting question which can be probed by simply swapping the 
-\texttt{h277} data within~\texttt{VICE} for another simulation, then rerunning 
-our numerical models and comparing the results.
-
-% fig 1 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.32]{decomposition.pdf} 
-\caption{Radial distributions of our star particles from 
-\texttt{h277}. In the top row, we show distributions of~\textit{final} radius 
-in bins of birth radius and age, and in the bottom row, we show distributions 
-of~\textit{birth} radius in bins of final radius and age. Each bin in 
-Galactocentric radius is shown in its own panel, denoted in text at the top of 
-each panel and by vertical black dashed lines. We colour-code the distributions 
-according to the age of the star particles, denoted by the legend in the upper 
-left panel. We smooth all distributions with a box-car width of 0.5 kpc to 
-improve clarity. We omit the distributions for 8 - 10 Gyr old stars born in the 
-9 - 11 and 11 - 13 kpc bins due to an insufficient number of star particles 
-with which to calculate the distribution. } 
-\label{fig:h277_decomposition} 
-\end{figure*}
-
-In the top row of Fig.~\ref{fig:h277_decomposition}, we plot the distributions 
-of final radius in bins of birth radius and age for our sample of star 
-particles. Conversely, the bottom rows distributions of birth radii in bins of 
-final radius and age. Focusing on the top row of panels, we note that for star 
-particles born at any radius and time, the distribution of final radius is 
-still peaked near the birth radius, but moves slightly inward with increasing 
-age. The tails of the distributions toward larger~$R_\text{gal}$ are nearly 
-age-independent, while the tails toward smaller~$R_\text{gal}$ are not. This 
-suggests that radial migration inward and outward occur on different timescales 
-in~\texttt{h277}, specifically that inward migration is slower than outward 
-migration. By extension, this suggests that the two may be tied to different 
-physical processes. In a cosmological simulation,~\citet{Roskar2008a} 
-demonstrate that resonant scattering at corotation causes stars to move 
-outward and gas to move inward. It's possible that stellar migration inward has 
-different origins. 
-\par 
-Focusing on the bottom row of panels in Fig.~\ref{fig:h277_decomposition}, we 
-note that the mode of the birth radius distributions show a stronger dependence 
-on age than the mode of the final radius distributions. At any Galactocentric 
-radius at the present day, the youngest stars are overwhelmingly born at 
-comparable radii, while the oldest stars are overwhelmingly born at smaller 
-radii. This is most noticeable in at large~$R_\text{gal}$. The differences 
-between the two can be understood by considering the steep nature of the radial 
-gradient in stellar surface density. Take for example the 8 - 10 Gyr age bin in 
-both~$R_\text{Birth}$ = 5 - 7 kpc and~$R_\text{Final}$ = 11 - 13 kpc bins (i.e. 
-the red curves in the top-left and bottom-right panels). For these old stars 
-born at 5 - 7 kpc, 11 - 13 kpc is far down the tail of the~$R_\text{Final}$ 
-distribution, and yet 5 - 7 kpc is the mode~$R_\text{Birth}$ of all old stars 
-presently at these radii. This implies that even though a plurality of 8 - 10 
-Gyr old stars with~$R_\text{Final}$ = 11 - 13 kpc were born at 5 - 7 kpc, they 
-account for only a small fraction of the stars with similar birth radii. This 
-is only possible if there are many more stars born at small~$R_\text{gal}$ than 
-large~$R_\text{gal}$, implying a stellar surface density which decreases as a 
-strong function of Galactocentric radius. This is known to be the case 
-\citep[e.g.][]{Bland-Hawthorn2016}. 
-\par 
-We also note that the top row of Fig.~\ref{fig:h277_decomposition} demonstrates 
-that the number of stars which migrated inward and outward are comparable in 
-\texttt{h277}. In fact, taking~$\left|\Delta R_\text{gal}\right| \geq$~500 pc 
-between birth and final radii as the criterion for migration inward or outward, 
-we indeed find as global percentages in our sample that 27\% migrated inward, 
-29\% migrated outward, and the remaining 44\% stayed near their birth radius. 
-Furthermore, these distributions contain some information on the timescales of 
-radial migration. In all bins of birth radius, a good first-order estimate of 
-the probability density that a star has a final radius in the same bin is 
-$\sim$0.3. With bins in birth radius of 2 kpc, this suggests that only 
-$\sim$60\% of stars remain in their birth radius bin by the time their~$\sim$2 
-Gyr old. and the remaining~$\sim$40\% have migrated already. If the type Ia 
-supernova delay-time distribution (SN Ia DTD) is a~$t^{-1.1}\approx t^{-1}$ 
-power-law as suggested by observational results~\citep[e.g.][]{Maoz2012, 
-Maoz2017}, then we expect similar numbers of SN Ia events to occur with delay 
-times between 1 and 10 Gyr as we do between 100 Myr and 1 Gyr. With such an 
-extended DTD, and the timescales for migration implied by Fig. 
-\ref{fig:h277_decomposition}, its possible that SN Ia progenitors can migrate 
-significant distances before exploding. Indeed, in the ASAS-SN bright SN 
-catalog,~$\sim$10\% of SNe are seen at >10 kpc from their host galaxies 
-\citep{Holoien2019}. While this catalog is for~\textit{all} supernovae seen by 
-ASAS-SN, the majority of SN events are type Ia anyway. Based on this, it's 
-reasonable to expect that the migration of nucleosynthetic may proceed 
-alongside stellar migration. This effect has largely been neglected by GCE 
-studies to date on the grounds that radial migration is a slow process, and 
-thus the majority of nucleosynthesis should occur near a star's birth radius 
-(e.g.~\citealp{Minchev2013}, and in the application of the 
-\citealt{Weinberg2017} analytic models in~\citealt{Feuillet2018}). However, 
-with the realization that the SN Ia duty cycle is also a slow process due to 
-the long tail of the DTD, its possible that stellar migration and SN Ia occur 
-on similar timescales. Therefore, we relax this assumption in the present 
-paper. We discuss the application of the~\texttt{h277} star particle data to 
-our model for radial migration and the time dependence thereof in the next 
-section.
-
-\subsection{Radial Migration} 
-\label{sec:methods:migration} 
-As in previous studies~\citep[e.g.][]{Schoenrich2009, Minchev2013, Sharma2020}, 
-in this paper we model the Milky Way as a series of concentric annuli with a 
-uniform width~$\Delta R_\text{gal}$. To run numerical simulations of these 
-models, we develop and make use of~\texttt{VICE}'s~\texttt{milkyway} object, 
-designed specifically for such an approach. The~\texttt{milkyway} object is a 
-subclass of a more general object named~\texttt{multizone}; at its core a 
-\texttt{multizone} object is an array of~\texttt{singlezone} objects, which are 
-designed to handle one-zone models of GCE and were the focus of 
-\citet{Johnson2020},~\texttt{VICE}'s initial release paper. The 
-\texttt{multizone} object affords users full control over which zone any 
-individual stellar population is in at all timesteps following its formation as 
-well as the ability to move gas between any two zones with any time dependence. 
-In principle this should allow for arbitrarily complex zone configurations and 
-migration prescriptions. The \texttt{milkyway} object is a user-friendly 
-extension of this which enforces an annular zone configuration as we take here. 
-As defaults, it adopts the stellar migration model detailed in this section and 
-our star formation law discussed in~\S~\ref{sec:methods:sfe}. 
-\par 
-As in hydrodynamical simulations, stars in~\texttt{VICE} are stand-ins for 
-entire stellar populations. They're said to be in a given zone if their radius 
-is between the inner and outer edges of the annulus. At all times, their 
-nucleosynthetic products and returned envelopes are placed in the ISM of the 
-annulus that they are in~\textit{at that time}. Where hydrodynamical and 
-N-body simulations of Galaxy evolution tend to use star particles of a fixed 
-mass, however,~\texttt{VICE} forms a fixed number of stellar populations per 
-zone per timestep, and allows their masses to vary to account for variations 
-in the star formation rate (SFR). The mass of stars formed in a given zone is 
-divided evenly among the stellar populations that form in a given zone and 
-timestep. 
-\par 
-The final radius of a stellar population is then determined based on the birth 
-and final radii of star particles in a hydrodynamical simulation, for which 
-we've taken~\texttt{h277} in this paper (see discussion in~\S 
-\ref{sec:methods:h277}). Describing the Galaxy as a series of concentric 
-annuli,~\texttt{VICE}'s~\texttt{milkyway} object assumes stellar populations 
-are born at the centres of each annulus. For a stellar population born at a 
-time~$T$ and Galactocentric radius~$R_\text{gal}$, it first searches for star 
-particles from~\texttt{h277} that formed at~$T \pm$~250 Myr and~$R_\text{gal} 
-\pm$~250 pc. It then randomly selects a star particle from this subsample with 
-no bias to act as an~\textit{analog}. This stellar population then assumes the 
-change in orbital radius~$\Delta R_\text{gal}$ of its analog at face value, 
-and moves from its birth radius to the implied final radius at~$T$ = 12.2 Gyr 
-with an assumed time dependence. If no candidate analogs are found, 
-\texttt{VICE} widens the search to~$T \pm$~500 Myr and~$R_\text{gal} \pm$~500 
-pc. If still no analog is found, then it finds the star particle 
-with the smallest difference in birth radius still within a birth time of 
-$T \pm$~500 Myr, and assigns it as the analog. 
-While this prescription allows stellar populations to be assigned analogs with 
-significantly different birth radii, this is only an issue for small~$T$ and 
-large~$R_\text{gal}$ where there are few star particles from~\texttt{h277}, 
-and where few stars form in nature anyway due to the inside-out growth of 
-galaxies~\citep{Bird2013}. Furthermore, due to the similarity of the histograms 
-in the top row of Fig.~\ref{fig:h277_decomposition}, we expect taking 
-$\Delta R_\text{gal}$ from a star particle which formed at a similar time but 
-different birth radius in these instance to be accurate enough for our 
-purposes. 
-\par 
-Our models assume that the Galaxy is vertically and azimuthally well-mixed, and 
-that the radial direction is the only one in which there are significant 
-differences in composition. That is, each annulus extends from the disc 
-midplane at~$z$ = 0 to~$z = \pm \infty$, and whether or not a star particle is 
-in a given annulus does not depend on~$z$ at all. In fact, this information is 
-\textit{not} used in integrating our models with~\texttt{VICE}. Instead, we 
-simply assume that each stellar population in our models are located at the 
-present day~$z_\text{final}$ of its assigned analog. Furthermore, when an 
-\texttt{h277} star particle is assigned as an analog, it is~\textit{not} 
-thrown out of the sample of candidate analogs, in theory allowing a star 
-particle to act as an analog for multiple stellar populations. This is a 
-subtle difference between the~\citet{Minchev2013} model and ours; where we 
-assign star particles to stellar populations for which~\texttt{VICE} then 
-calculates a stellar mass and composition based on an assumed SFH, the 
-\citet{Minchev2013} uses a chemical evolution model to assign compositions to 
-star particles.
-
-% fig 2 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.45]{migration.pdf} 
-\caption{A diagram illustrating how Galactocentric radius changes with time for 
-two stellar populations under our migration schema: diffusion (crimson, solid), 
-linear (lime, dot-dashed), post-process (black, dotted), and sudden (blue, 
-dashed). Here the initial and final radii and birth times are chosen at random 
-for illustrative purposes. With the initial and final Galactocentric radii of 
-a stellar population, its birth time, and one of these assumptions regarding 
-the time-dependence of radial migration, the Galactocentric radius at all times 
-is known. } 
-\label{fig:migration_schema} 
-\end{figure}
-
-With a known birth radius and time from our GCE model and an implied 
-$\Delta R_\text{gal}$ from a stellar population's assigned analog, the final 
-radius is known and the only missing piece of information is the 
-time-dependence with which it moves there. In the present paper we consider 
-four parameterized assumptions to describe this, each of which are illustrated 
-conceptually in Fig.~\ref{fig:migration_schema}. 
-\begin{itemize} 
-	\item \textbf{Post-Processing}: Stars stay where they are born until the 
-	final timestep, at which point they instantly migrate to their final 
-	radius. This retains the assumption that stars do not contribute to 
-	nucleosynthesis beyond their birth radius as employed in previous studies 
-	\citep[e.g.][]{Minchev2013}. In this scenario, each annulus is treated as 
-	a one-zone model independent of all other zones. We illustrate this case 
-	with a black dotted line in Fig.~\ref{fig:migration_schema}.
-
-	\item \textbf{Sudden}: A random number is drawn from a uniform distribution 
-	between a stellar population's time of birth and the present day. That time 
-	is taken to be the time of instantaneous migration to the present-day 
-	annulus. This emulates a scenario in which a single dynamical interaction 
-	changes a star's orbital radius, and be thought of mathematically as a 
-	time-dependent extension of the post-processing scenario. We illustrate 
-	this case with a blue dashed line in Fig.~\ref{fig:migration_schema}.
-
-	\item \textbf{Diffusion}: Stars move to their final radii in a continuous, 
-	time-dependent manner in this case. So named because it corresponds to a 
-	scenario in which angular momentum diffuses via a random walk, under this 
-	assumption, the mean displacement of stars that migrate similar distances 
-	would scale with~$\sqrt{\text{age}}$. This is our 
-	fiducial migration model, and we present results with this assumption 
-	unless otherwise noted. This is qualitatively similar to 
-	\citet{Frankel2018, Frankel2020}, who also model radial orbit migration 
-	with a~$\sqrt{\tau}$ dependence. We illustrate this case with a red solid 
-	line in Fig.~\ref{fig:migration_schema}.
-
-	\item \textbf{Linear}: A simple variation of the diffusion model in which 
-	the migration to the final radius scales linearly with age rather than with 
-	$\sqrt{\text{age}}$. There is no physical motivation for this model other 
-	than mathematical ease, but together with the diffusion model it 
-	constitutes a test of how sensitive our conclusions are to the 
-	time-dependence of stellar migration. We illustrate this case with a 
-	green dot-dashed line in Fig.~\ref{fig:migration_schema}. 
-\end{itemize} 
-In all models, we neglect radial gas flows~\citep{Lacey1985, Bilitewski2012}, 
-instead focusing on these simple assumptions describing how orbital radii 
-change with time. While such an investigation would be an interesting extension 
-of our study, we reserve it for future work. 
-\par 
-We emphasize that there is~\textit{no} N-body integration employed in our 
-models aside from that which ran the~\texttt{h277} simulation. Furthermore, we 
-use our sample of analog star particles from it~\textit{only} in determining 
-$\Delta R_\text{gal}$ of each of our model stellar populations (see discussion 
-in~\S~\ref{sec:methods:h277}). While~\texttt{h277} had its own SFH and chemical 
-enrichment history, we make use of neither of these components here; rather, 
-these are exactly what we seek to explore variations of. We acknowledge that 
-stellar migration is often formulated using the processes ``blurring'' and 
-``churning'', referring to a star's epicyclic motions and changes in the 
-guiding center of its orbit~\citep[e.g.][]{Sellwood2002, Schoenrich2009, 
-Minchev2011}; migration can also occur due to the overlap of spiral arm and 
-bar resonances in the disc~\citep{Minchev2011}. We refrain from discussion of 
-this approach here, because our models do not make use of such methodology. In 
-the present paper, the orbital radii at all times are calculated and assumed at 
-face value given one of the four assumptions detailed in the bullet list above. 
-\par
-
-\subsection{Nucleosynthetic Yields, Outflows, and Recycling} 
-\label{sec:methods:yields} 
-Nucleosynthesis proceeds in our models according to~\textit{fractional net} 
-yields, as required by~\texttt{VICE}. That is, our yields quantify the mass 
-of some element~$x$ ejected to the interstellar medium (ISM) in units of the 
-progenitor stellar population's total initial mass, and only accounts for 
-\textit{newly produced} nucleosynthetic material.~\texttt{VICE} takes into 
-account the return of previously produced nucleosynthetic products with a 
-separate implementation. In the present paper, we focus our analysis on 
-alpha and iron-peak elements, taking oxygen (O) and iron (Fe) as the 
-representative cases. The dominant enrichment channels of 
-interest in our models are thus core collapse and type Ia supernovae 
-\citep{Johnson2019}. Though we choose O and Fe, we expect 
-similar results to be found for other alpha (e.g. Ne, Mg, Si) and iron-peak 
-elements (e.g. Mn, Ni, Co), with purely quantitative differences reflective of 
-the relative yields between elements. 
-\par 
-Enrichment from core collapse supernovae (CCSNe) happens immediately following 
-the formation of progenitor stars in~\texttt{VICE}. This is an adequate 
-approximation, because the lifetimes of massive stars are short compared to 
-the relevant timescales for galaxy evolution. For the most massive stars, the 
-lifetimes are comparable to the timestep size we adopt in this paper anyway. 
-This assumption implies a linear relationship between the CCSN enrichment 
-rate and the SFR: 
-\begin{equation} 
-\dot{M}_x^\text{CC} = y_x^\text{CC}\dot{M}_\star 
-\end{equation} 
-where~$y_x^\text{CC}$ is the CCSN yield of some element~$x$. Physically, this 
-quantity represents the mass of an element~$x$ ejected to the interstellar 
-medium (ISM) from all CCSNe events associated with a stellar population in 
-units of the stellar population's initial mass. For example, if 
-$y_x^\text{CC} = 0.01$, a hypothetical 100~\msun~stellar population would 
-add 1~\msun~of~$x$ to the ISM immediately. This procedure neglects the mass 
-that would be lost to outflows, which like recycling, have a separate 
-implementation in~\texttt{VICE}. In this paper, we adopt~$y_\text{O}^\text{CC}$ 
-= 0.015 and~$y_\text{Fe}^\text{CC}$~= 0.0012 from~\citet{Johnson2020}, who 
-in turn adopt these values from~\citet{Weinberg2017}. 
-\par 
-SN Ia nucleosynthesis products are injected according to a~$t^{-1.1}$ DTD with 
-a minimum delay time of~$t_\text{D}$ = 150 Myr. This is the default DTD in 
-\texttt{VICE}, which was also adopted by~\citet{Johnson2020}, and is suggested 
-by recent observational results comparing the cosmic SN Ia rate to the cosmic 
-SFH~\citep{Maoz2012, Maoz2017}. In a one-zone model at times~$t > t_\text{D}$, 
-the enrichment rate of some element~$x$~can be expressed as the product of 
-some yield~$y_x^\text{Ia}$ and the SFH weighted by the DTD: 
-\begin{subequations}\begin{align} 
-\dot{M}_x^\text{Ia} &= y_x^\text{Ia}\langle\dot{M}_\star\rangle_\text{Ia} \\ 
-&= y_x^\text{Ia}\ddfrac{
-	\int_0^{t - t_\text{D}} \dot{M}_\star(t') R_\text{Ia}(t - t') dt' 
-}{
-	\int_{t_\text{D}}^{t_\text{max}} R_\text{Ia}(t')dt' 
-} 
-\label{eq:mdot_ia} 
-\end{align}\end{subequations} 
-where~$R_\text{Ia}$ is the DTD itself, which has units of~$M_\odot^{-1}$ 
-Gyr$^{-1}$. Like the CCSN yield,~$y_x^\text{Ia}$ is the mass of some element 
-$x$ produced over the SN Ia duty cycle in units of the progenitor stellar 
-population's initial mass. It can also be expressed as an integral over the 
-DTD: 
-\begin{equation} 
-y_x^\text{Ia} = m_x^\text{Ia} \int_{t_\text{D}}^{t_\text{max}} R_\text{Ia}(t') 
-dt' = m_x^\text{Ia}\frac{N_\text{Ia}}{M_\star} 
-\label{eq:y_x_ia} 
-\end{equation} 
-where~$m_x^\text{Ia}$ is the average mass of the element~$x$ produced in a 
-single SN Ia event and the integral evaluates to the mean number of SN Ia 
-events~$N_\text{Ia}$ per mass of stars formed~$M_\star$. \texttt{VICE} forces 
-$t_\text{max}$~= 15 Gyr always, though provided one is consistent with 
-equations~\refp{eq:mdot_ia} and~\refp{eq:y_x_ia}, the results are independent 
-of~$t_\text{max}$ since the integrals cancel. 
-\par 
-Extending this formalism to multi-zone models is simple - rather than an 
-integral over the star formation history of a given annulus, the rate becomes 
-a sumation over all stellar populations that are in a given zone at some time: 
-\begin{equation} 
-\dot{M}_x^\text{Ia} = y_x^\text{Ia} \ddfrac{
-	\sum_i M_i R_\text{Ia}(\tau_i) 
-}{
-	\int_{t_\text{D}}^{t_\text{max}} R_\text{Ia}(t')dt' 
-} 
-\label{eq:mdot_ia_multizone} 
-\end{equation} 
-where~$M_i$~and~$\tau_i$~are the mass and age of the~$i$'th stellar population, 
-respectively. 
-\par 
-Initially, we adopt~$y_\text{O}^\text{Ia}$~= 0 and~$y_\text{Fe}^\text{Ia}$~= 
-0.0017 from~\citet{Johnson2020}, who in turn adopt these values from 
-\citet{Weinberg2017}. However, in practice we find that the e-folding 
-timescales of star formation in our models are sufficiently long (see 
-discussion in~\S~\ref{sec:methods:sfhs}) such that our fiducial, inside-out SFH 
-model predicts [O/Fe]~$\approx$~+0.05 for young stars. We therefore multiply 
-$y_\text{Fe}^\text{Ia}$~by~$10^{0.1}$, adopting instead~$y_\text{Fe}^\text{Ia}$ 
-= 0.00214 in order for our fiducial model to predict a late-time [O/Fe] ratio 
-in better agreement with observations. Although there is no motivation for such 
-a change aside from this, this decision is likely within the uncertainties in 
-SN Ia nucleosynthetic yields anyway. 
-\par 
-Our models assume that all supernova yields of O and Fe are independent of 
-metallicity. While this appears to be empirically true in the Milky Way for O 
-and Fe (\citealp{Weinberg2019};~\citealp*{Griffith2019}; 
-\citealp{Griffith2020}), our CCSN yields are based on 
-supernova explosion models in which all >8~\msun~progenitors produce a CCSN 
-event~\citep[e.g.][]{Chieffi2004, Chieffi2013}. Recent findings with regard to 
-black hole formation and stellar explodability have demonstrated that many 
-massive stars instead collapse directly to a black hole (see theoretical 
-discussion by, e.g.,~\citealp{Pejcha2015, Sukhbold2016, Ertl2016}, and 
-observational evidence from~\citealp*{Gerke2015};~\citealp{Adams2017, 
-Basinger2020}). Such effects would necessarily lower CCSN yields of all 
-elements. While~\texttt{VICE} includes functionality with which to calculate 
-$y_x^\text{CC}$~for some element~$x$~using built-in tables from supernova 
-nucleosynthesis studies, an in-depth investigation of the impact of these 
-effects is outside the scope of this paper. Such an investigation which expands 
-the capabilities of~\texttt{VICE} will be presented in Griffith et al. (2021, 
-in prep). 
-\par 
-With regard to our SN Ia yields,~\citet{Brown2019} demonstrate that the local 
-specific SN Ia rate shows a strong, inverse dependence on galaxy stellar mass. 
-They argue that this may imply a metallicity dependent~$R_\text{Ia}$ that 
-produces more SN Ia events at early times when the metallicity is low. However, 
-these metallicity are only present in our models at very early times. 
-Furthermore, when outflows are taken into account, these yields are known to 
-predict observationally plausible abundances~\citep{Andrews2017, Weinberg2017}. 
-We find similar results in our models. 
-\par 
-\citet{Weinberg2017} demonstrate that, to first order, the nucleosynthetic 
-yields of a given element and the strength of outflowing winds determine the 
-late-time equilibrium abundance in the ISM. We retain their characterization 
-of outflows here, in terms of a mass-loading factor~$\eta$~describing the ratio 
-of the mass outflow to the SFR: 
-\begin{equation} 
-\eta \equiv \frac{\dot{M}_\text{out}}{\dot{M}_\star} 
-\end{equation} 
-Here we adopt a scaling of~$\eta$~with~$R_\text{gal}$~such that the late-time 
-equilibrium abundance as a function of radius describes a metallicity 
-gradient in agreement with observations;~\citet{Nidever2014} employ a similar 
-methodology. 
-\par 
-The procedure outlined here makes two assumptions: 1) that the equilibrium 
-abundance at a given radius corresponds to the mode of the observed MDF, and 2) 
-that radial migration does not significantly alter the overall form of the 
-gradient. We demonstrate that this holds in our models in~\S 
-\ref{sec:obs_comp:gradient}. For alpha elements,~\citet{Weinberg2017} defines 
-the equilibrium abundance under a constant SFH as: 
-\begin{equation} 
-Z_{\alpha,\text{eq}} = \frac{y_\alpha^\text{CC}}{1 + \eta(R_\text{gal}) - r} 
-\end{equation} 
-where~$r$~is the recycling parameter ($\approx$0.4 for the sake of this scaling 
-with a~\citealp{Kroupa2001} IMF; see discussion in~\S~2.2 
-of \citealp{Weinberg2017}). Solving for~$\eta(R_\text{gal})$ yields: 
-\begin{equation} 
-\eta(R_\text{gal}) = \frac{y_\alpha^\text{CC}}{Z_{\alpha,\text{eq}}} + r - 1 = 
-\frac{y_\alpha^\text{CC}}{Z_{\alpha,\odot}}10^{-\text{mode([$\alpha$/H])}
-(R_\text{gal})} + r - 1 
-\end{equation} 
-The metallicity gradient in the Milky Way has been the focus of a number of 
-studies to date.~\citet{Nordstroem2004b} find a gradient of -0.099 kpc$^{-1}$ 
-in [Fe/H] in main sequence stars from the Geneva Copenhagen Survey 
-(\citealp{Nordstroem2004a};~\citealp*{Holmberg2007}).~\citet{Daflon2009} report  
--0.04 kpc$^{-1}$ in [S/H] in OB stars.~\citet{Frinchaboy2013} derive -0.09 
-kpc$^{-1}$ in [M/H] in open clusters.~\citet{Hayden2014} also find -0.09 
-kpc$^{-1}$ in [M/H] for~$R_\text{gal} \gtrsim$~6 kpc for low-$\alpha$ stars, 
-but find the gradient to be relatively flat within~$R_\text{gal} \lesssim$~6 
-kpc. \citet{Weinberg2019} report a gradient of -0.06 kpc$^{-1}$ in mode([Mg/H]) 
-for upper red giant branch stars in the disc (see their Fig. 23). In tentative 
-agreement with these studies, we adopt a slope of -0.08 kpc$^{-1}$. To set the 
-normalization, we assume the mode([$\alpha$/H]) to be~$\sim$+0.3 at 
-$R_\text{gal}$ = 4 kpc, since this would produce mode([$\alpha$/H])~$\approx$~0 
-at~$R_\text{gal}$ = 7 - 9 kpc. This results in the following form for~$\eta$ 
-as a function of Galactocentric radius: 
-\begin{equation} 
-\eta(R_\text{gal}) = \frac{y_\alpha^\text{CC}}{Z_{\alpha,\odot}} 
-10^{(-0.08\text{ kpc}^{-1})(R_\text{gal} - 4\text{ kpc}) + 0.3} + r - 1 
-\label{eq:eta_rgal} 
-\end{equation} 
-where we adopt our CCSN yield of O for~$y_\alpha^\text{CC}$ and the solar 
-abundance of O of~$Z_{\text{O},\odot}$ = 0.00572 based on~\citet{Asplund2009}. 
-We plot this adopted scaling in the top panel of Fig.~\ref{fig:eta_tau_sfh}, 
-highlighting a value of~$\sim$2.15 for the solar circle with a red dotted line. 
-This does assume a uniformly linear gradient at all~$R_\text{gal}$, in tension 
-with the findings of~\citet{Hayden2014} who find it to flatten within~$\sim$6 
-kpc. However, this procedure can be easily repeated for any desired gradient, 
-since the functional form simply goes into the power of 10 in equation 
-\refp{eq:eta_rgal}.
-
-% fig 3 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.45]{eta_tau_sfh.pdf} 
-\caption{\textbf{Top}: Our implemented scaling of the mass loading factor 
-$\eta$~with Galactocentric radius (black) as defined by equation 
-\refp{eq:eta_rgal}.~\textbf{Bottom}: The e-folding timescales of the star 
-formation histories of our model galaxies (black). These values come from a 
-fit to the~$\Sigma_\star$-age relation in bins of~$R/R_\text{e}$~for 
-$10^{10.5}$~-~$10^{11}$~\msun~Sa/Sb Hubble type spiral galaxies as reported by 
-\citet[][see discussion in~\S~\ref{sec:methods:sfhs}]{Sanchez2020}. The 
-horizontal and vertical red dashed lines in both panels highlight a mass 
-loading factor of~$\eta \approx$~2.15 and a star formation timescale of 
-$\tau_\text{sfh} \approx$~15 Gyr at an assumed radius of the sun of 
-$R_\odot$ = 8 kpc. } 
-\label{fig:eta_tau_sfh} 
-\end{figure}
-
-Both AGB star enrichment and the recycling of previously produced metals in 
-this paper proceed as they did in~\citet{Johnson2020}, with the caveat that the 
-mass is added to the annulus that a stellar population is in at a given time, 
-which may or may not be the annulus it was born in. Recycling proceeds 
-according to the~\citet{Kalirai2008} initial-remnant mass relation assuming a 
-\citet{Kroupa2001} IMF and a mass-lifetime relationship of 
-$\tau = 1.1\tau_\odot(M/M_\odot)^{-3.5}$, where~$\tau_\odot$~= 10 Gyr is the 
-main sequence lifetime of the sun and the factor of 1.1 accounts for the 
-post-main sequence lifetime.~\texttt{VICE} in its current version forces an AGB 
-enrichment channel in all models; it is thus included in the present paper. For 
-this enrichment channel, we adopt the net yields sampled on a table of stellar 
-initial mass and metallicity from the FRUITY database \citep{Cristallo2011}. 
-However, the AGB star yields of O and Fe are negligible compared to their 
-supernova yields; we therefore conclude discussion of this component of our 
-models here. 
-\par
-
-\subsection{Star Formation Histories} 
-\label{sec:methods:sfhs} 
-\texttt{VICE} handles models in either infall, star formation, or gas mode, 
-referring simply to which component of the evolutionary history the user has 
-specified. The starburst models presented in~\citet{Johnson2020} ran in infall 
-mode, but here we run~\texttt{VICE} in star formation mode, because we are 
-after specific forms for the star formation histories of our models. In 
-Appendix~\ref{sec:normalize_sfh}, we present justification of how we normalize 
-the parameters of our star formation histories to produce a realistic model 
-Galaxy at the present day. In short, it takes in a unitless description of the 
-dependence of the SFH at a given Galactocentric radius, denoted 
-$f(t|R_\text{gal})$, and a unitless description of the present day stellar 
-surface density gradient, denoted~$g(R_\text{gal})$. We integrate 
-$f(t|R_\text{gal})$ with time for each annulus, assuming~$R_\text{gal}$ to 
-correspond to the centre of the zone, and attach a prefactor to 
-$f(t|R_\text{gal})$ in each annulus such that the desired gradient is achieved 
-with a total stellar mass similar to the Milky Way. This procedure neglects the 
-impact of radial migration, assuming that it does not significantly alter the 
-form of~$g(R_\text{gal})$. We demonstrate that these assumptions hold in~\S 
-\ref{sec:methods:surface_density_gradient}, in which we also detail our 
-adopted form of~$g(R_\text{gal})$. As long as this assumption is not violated, 
-the equation derived in Appendix~\ref{sec:normalize_sfh} can be used to 
-calculate these prefactors for future models of Milky Way-like galaxies. 
-\par 
-In the present paper, we present four fiducial SFHs, which we dub ``constant'', 
-``inside-out'', ``late-burst'', and ``outer-burst''. They're defined as 
-follows: 
-\begin{itemize} 
-	\item \textbf{Constant}: The SFH at a given radius is time-independent. 
-	\begin{equation} 
-	f_\text{C}(t|R_\text{gal}) = 1 
-	\label{eq:constant_sfh} 
-	\end{equation} 
-	This case is of particular theoretical interest because it quantifies the 
-	effect of stellar migration while removing the impact of a time-dependent 
-	SFH.
-
-	\item \textbf{Inside-Out}: This is our fiducial SFH. 
-	\begin{equation} 
-	f_\text{IO}(t|R_\text{gal}) = (1 - e^{-t / \tau_\text{rise}}) 
-	e^{-t / \tau_\text{sfh}} 
-	\label{eq:insideout_sfh} 
-	\end{equation} 
-	We adopt this mathematical form over a more traditional 
-	linear-times-exponential characterization, because the latter does not 
-	offer control over the position of the maximum SFR. The form we adopt has 
-	a maximum near~$\tau_\text{rise}$, for which we adopt a value of 2 Gyr 
-	everywhere here. This produces a peak in star formation at lookback times 
-	of~$\sim$10 Gyr, roughly corresponding to a redshift of~$z \approx$~2, in 
-	agreement with observational results on the cosmic SFH~\citep{Madau2014}. 
-	In this paper,~$\tau_\text{sfh}$ is a function of~$R_\text{gal}$, discussed 
-	in this section. We present results assuming this model throughout this 
-	paper except in cases where a different SFH impacts the predictions.
-
-	\item \textbf{Late-Burst}: In this model, the inside-out SFH is modified to 
-	exhibit a recent, gradual burst in star formation described by a Gaussian: 
-	\begin{equation} 
-	f_\text{LB}(t|R_\text{gal}) = f_\text{IO}(r|R_\text{gal}) 
-	(1 + A_be^{-(t - t_b)^2/2\sigma_b^2}) 
-	\label{eq:lateburst_sfh} 
-	\end{equation} 
-	$A_b$ is a dimensionless parameter describing the strength of the 
-	starburst,~$t_b$ is the time of the local maximum in the SFH during the 
-	burst, and~$\sigma_b$ is the width of the Gaussian describing it. This 
-	model being loosely motivated by the findings of~\citet{Mor2019} and 
-	\citet{Isern2019}, we adopt~$A_b$ = 1.5,~$t_b$ = 10.2 Gyr, and 
-	$\sigma_b$ = 1 Gyr, finding in practice that~$A_b$ = 1.5 produces a 
-	local maximum SFR that is a factor of~$\sim$2 larger than the preceding 
-	local minimum.
-
-	\item \textbf{Outer-Burst}: A variation of the late-burst model in which 
-	only~$R_\text{gal} \geq$~6 kpc experience the starburst. This is loosely 
-	motivated by the findings of~\citet{Vincenzo2020} where a hydrodynamical 
-	simulation of a Milky Way-like galaxy showed radially dependent infall. 
-	\begin{equation} 
-	f_\text{OB}(t|R_\text{gal}) = \begin{cases} 
-	f_\text{IO}(t|R_\text{gal}) & (R_\text{gal} < 6\text{ kpc}) \\ 
-	f_\text{LB}(t|R_\text{gal}) & (R_\text{gal} \geq 6\text{ kpc}) 
-	\end{cases} 
-	\label{eq:outerburst_sfh} 
-	\end{equation} 
-\end{itemize} 
-Although we do not consider such models here, an investigation into the impact 
-of more episodic star formation histories would be an interesting extension of 
-the present paper. For example,~\texttt{VICE} has all of the necessary 
-capabilities to handle models in which major episodes of star formation 
-coincide with close passages of the Sagittarius dwarf 
-\citep[e.g.][]{RuizLara2020}. 
-\par 
-We derive the scaling of the e-folding timescales of star formation 
-$\tau_\text{sfh}$ with~$R_\text{gal}$ from the data in~\citet{Sanchez2020}. 
-They present the stellar surface density~$\Sigma_\star$ as a function of age 
-in bins of~$R/R_\text{e}$ for MaNGA galaxies, where~$R_\text{e}$ is the 
-half-light radius. Here we take their~$M_\star = 10^{10.5} - 10^{11}$ 
-\msun~ bin for Sa/Sb spirals and simultaneously fit the normalization and 
-e-folding timescale~$\tau_\text{sfh}$ of our~$f_\text{IO}(t|R_\text{gal})$ form 
-to the data. Although the normalization is irrelevant to our models and 
-determined via the method outlined in Appendix~\ref{sec:normalize_sfh}, we 
-adopt the resulting~$\tau_\text{sfh}-R_\text{gal}$ relation in our models. With 
-our adopted stellar surface density gradient (see discussion in~\S 
-\ref{sec:methods:surface_density_gradient}), we know the present-day half-mass 
-radius to be very near 4 kpc. The findings of~\citet{Garcia-Benito2017} and 
-\citet{GonzalezDelgado2014} suggest that half-light radii are marginally larger 
-than half-mass radii. Based on equation (4) of~\citet{GonzalezDelgado2014} 
-relating the two for circular apertures, we expect our model Galaxy to have a 
-half-light radius near 5 kpc. We therefore adopt~$R_\text{e}$ = 5 kpc to 
-convert the~$\tau_\text{sfh}-R_\text{gal}/R_\text{e}$ relation resulting from 
-our fit to the~\citet{Sanchez2020} data into a~$\tau_\text{sfh}-R_\text{gal}$ 
-relation. {\color{red} If there are references suggesting a similar value for 
-the Milky Way, we should note them here. } 
-\par 
-We illustrate this relationship in the bottom panel of Fig. 
-\ref{fig:eta_tau_sfh}, noting that the resulting timescales are long, 
-particularly for the outer Galaxy. With a red dotted line, we highlight a value 
-of~$\tau_\text{sfh} \approx$~15 Gyr at an assumed orbital radius of the sun of 
-$R_\odot$ = 8 kpc. Although these timescales at most radii are considerably 
-longer than a Hubble time, this is no cause for worry; this simply means that 
-these regions of the Galaxy in our models experience less than 1 e-folding in 
-their SFR, and that in the outer Galaxy the SFH is nearly constant after the 
-initial rise in the first~$\sim$2 Gyr. It is nonetheless interesting that 
-these timescales are considerably longer than that derived for the cosmic 
-SFH~\citep{Madau2014}.
-
-% fig 4 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.32]{evol.pdf} 
-\caption{The surface densities of star formation~$\dot{\Sigma}_\star$ (top 
-row), infall $\dot{\Sigma}_\text{in}$ (middle row), and gas~$\Sigma_\text{g}$ 
-(bottom row) as functions of simulation time for our four fiducial SFHs: 
-constant (far left), inside-out (left middle), late-burst (right middle), and 
-outer-burst (far right). We plot curves for the annuli whose inner radii are 
-3 kpc (grey), 5 kpc (black), 7 kpc (red), 9 kpc (yellow), 11 kpc (green), 13 
-kpc (blue), and 15 kpc (purple) (see equations~\refp{eq:constant_sfh}, 
-\refp{eq:insideout_sfh},~\refp{eq:lateburst_sfh}, and~\refp{eq:outerburst_sfh} 
-for the mathematical definition of each SFH). 
-}
-\label{fig:evol} 
-\end{figure*}
-
-We plot the resultant SFHs or our models in the top row of Fig.~\ref{fig:evol} 
-for a handful of radii. At all timesteps, the gas supply is known via the star 
-formation efficiency timescale~$\tau_\star$ (see discussion in~\S 
-\ref{sec:methods:sfe}). This quantity is illustrated in the bottom row of 
-Fig.~\ref{fig:evol}.~\texttt{VICE} automatically calculates the implied infall 
-rate by comparing the amount of gas lost to outflows and star formation in a 
-given timestep to that which is required to sustain the user-specified level of 
-star formation at the next timestep; we assume the infalling gas to be of zero 
-metallicity at all times. This quantity is shown in the middle row of Fig. 
-\ref{fig:evol}.
-
-\subsection{Star Formation Efficiency} 
-\label{sec:methods:sfe} 
-The term ``star formation efficiency'' (SFE) is somewhat overloaded in the 
-literature. In the star formation and feedback community, it usually 
-refers to the fraction of a molecular cloud's mass which will eventually be 
-converted into stars. In the chemical evolution literature, however, it 
-typically refers to the inverse timescale relating the SFR within some star 
-forming reservoir and the mass of gas in that region: 
-$\tau_\star \equiv \Sigma_\text{g}/\dot{\Sigma}_\star$. High (Low) values of 
-$\tau_\star$ indicate slow (fast) star formation and thus low (high) SFE; when 
-we refer to SFE here, we're referring to the definition based on this 
-timescale. In the star formation and feedback literature, this is often 
-referred to as the ``depletion time''. 
-\par 
-Based on the findings of~\citet{Kennicutt1998}, it is common practice in the 
-chemical evolution literature a single power-law describing the relationship 
-between the surface densities of gas and star formation~$\Sigma_\text{g}$ and 
-$\dot{\Sigma}_\star$, often referred to as the star formation law or the 
-Kennicutt-Schmidt relation: 
-\begin{equation} 
-\dot{\Sigma}_\star \sim \Sigma_\text{g}^N 
-\end{equation} 
-\citet{Kennicutt1998} derive~$N = 1.4 \pm 0.15$ relating the total 
-$\dot{\Sigma}_\star$~and~$\Sigma_\text{g}$~within the disc across a sample of 
-quiescent spiral galaxies and infrared and circumnuclear starbursts. However, 
-recent studies have found evidence that much of the observed scatter in this 
-relation is physical in origin~\citep{delosReyes2019} and that there are 
-significant breaks in both the power-law index and zero-points 
-\citep{Kennicutt2020}. Much of the uncertainty surrounding the details of the 
-star formation law is a consequence of the ongoing debate about the CO-to-H$_2$ 
-conversion factor (\citealp{Kennicutt2012};~\citealp*{Liu2015}). Although 
-\citet{Ellison2020a} demonstrate that there are significant galaxy-to-galaxy 
-variations in the star formation law, suggesting that individual galaxies do 
-not follow the population averaged trend,~\citet{delosReyes2019} argue that 
-this is still a reasonable recipe for Galaxy evolution models. We adopt such a 
-formalism here. 
-\par 
-\citet{Krumholz2018} compare model-predicted star formation laws to the 
-observations of~\citet{Bigiel2010} and~\citet{Leroy2013} (see their Fig. 2). We 
-find that the following by-eye fit to the power-law index~$N$~is a reasonble 
-description of the aggregate data: 
-\begin{equation} 
-N = \begin{cases} 
-1.0 & (\Sigma_\text{g} \geq \Sigma_{\text{g},2}) \\ 
-3.6 & (\Sigma_{\text{g},1} \leq \Sigma_\text{g} \leq \Sigma_{\text{g},2}) \\ 
-1.7 & (\Sigma_\text{g} \leq \Sigma_{\text{g},1}) 
-\end{cases} 
-\label{eq:sf_law_indeces} 
-\end{equation} 
-where~$\Sigma_{\text{g},1} = 5\times10^6$~\msun~\persqkpc~and 
-$\Sigma_{\text{g},2} = 2\times10^7$~\msun~\persqkpc. The apparent linearity of 
-the relationship above~$\sim2\times10^7$~\msun~\persqkpc~suggests that in this 
-regime, star formation proceeds at the fastest possible rate, and that 
-$\tau_\star \equiv \Sigma_\text{g}/\dot{\Sigma}_\star$~= constant. The 
-observations of~\citet{Leroy2013} and~\citet{Kennicutt2020} would suggest that 
-these are the 
-surface densities at which the molecular fraction~$f_\text{mol} = M_{\text{H}_2} 
-/ (M_{\text{H}_2} + M_\text{HI}) \approx$~1. We therefore adopt the assumption 
-that above~$\Sigma_\text{g} = 2\times10^7$~\msun~\persqkpc,~$\tau_\star$ 
-reaches its minimum value, and increases with decreasing~$f_\text{mol}$. We 
-denote this value as~$\tau_\text{mol}$, the value of~$\tau_\star$ for a gas 
-reservoir with~$f_\text{mol}$~= 1. This, combined with our three-component 
-power-law index N results in the following final form for our adopted star 
-formation law: 
-\begin{equation} 
-\dot{\Sigma}_\star = \begin{cases} 
-\Sigma_\text{g} \tau_\text{mol}^{-1} & 
-(\Sigma_\text{g} \geq \Sigma_{\text{g},2}) 
-\\ 
-\Sigma_\text{g} \tau_\text{mol}^{-1} \left(\frac{
-	\Sigma_\text{g}
-}{
-	\Sigma_{\text{g},2} 
-}\right)^{2.6} & 
-(\Sigma_{\text{g},1} \leq \Sigma_\text{g} \leq \Sigma_{\text{g},2}) 
-\\ 
-\Sigma_\text{g} \tau_\text{mol}^{-1} \left(\frac{
-	\Sigma_{\text{g},1} 
-}{
-	\Sigma{\text{g},2} 
-}\right)^{2.6}\left(\frac{
-	\Sigma_\text{g}
-}{
-	\Sigma_{\text{g},1} 
-}\right)^{0.7} & 
-(\Sigma_\text{g} \leq \Sigma_{\text{g},1}) 
-\end{cases} 
-\label{eq:sf_law} 
-\end{equation} 
-where we choose the power-law indeces such that this formalism is consistent 
-with equation~\refp{eq:sf_law_indeces}, and prefactors are added to ensure 
-piece-wise continuity. In implementation,~\texttt{VICE} requires the 
-$\tau_\star-\dot{\Sigma}_\star$ relation when ran in star formation mode and 
-the~$\tau_\star-\Sigma_\text{g}$ relation when ran in infall and gas modes. 
-Both follow algebraically from this relationship given the substitution 
-$\tau_\star \equiv \Sigma_\text{g} / \dot{\Sigma}_\star$. 
-\par 
-Although it is more physically motivated to use an adopted star formation law 
-to infer a star formation rate from the ISM properties at a given timestep, as 
-discussed in~\S~\ref{sec:methods:sfhs}, we are using~\texttt{VICE} in star 
-formation mode. This means that it is~$\dot{\Sigma}_\star$ which is specified 
-\textit{a priori} by our models - not~$\Sigma_\text{g}$. That is,~\texttt{VICE} 
-is inferring~$\Sigma_\text{g}$ from~$\dot{\Sigma}_\star$ in our models, not 
-the other way around. While we acknowledge the findings of~\citet{Ellison2020b}, 
-this another reason we must invoke a simple parameterization for the star 
-formation law, which~\citet{Kennicutt2020} argue is still a reasonable 
-approach. This decision also means that changing our assumptions about the 
-star formation law do not impact our SFHs, instead impacting the inferred 
-$\Sigma_\text{g}$ as a function of radius and time. 
-\par 
-Based on the observed Kennicutt-Schmidt at different redshifts, 
-\citet{Tacconi2018} suggest that~$\tau_\text{mol}$ should scale with redshift 
-$z$ and the deviation from the star forming main sequence~$\delta$MS via 
-$\tau_\text{mol} \propto (1 + z)^{-0.6}\delta\text{MS}^-0.44$. We don't take 
-into account the effect of~$\delta$MS in our models, but we do investigate the 
-redshift dependence. A reasonable approximation to the~$t - z$ relation out to 
-$z \approx$~3 assuming typical~$\Lambda$CDM cosmology is given by: 
-\begin{equation} 
-\frac{t}{t_0} \approx (1 + z)^{-5/4} 
-\end{equation} 
-where~$t_0$ is the present-day age of the universe, and~$t$ is not simulation 
-time but the age of the universe. Plugging this relation into the 
-\citet{Tacconi2018} scaling yields the following time-dependence for 
-$\tau_\text{mol}$: 
-\begin{equation} 
-\tau_\text{mol} = \tau_{\text{mol},0}(t/t_0)^{12/25} \approx 
-\tau_{\text{mol},0}(t/t_0)^{1/2} 
-\end{equation} 
-where~$\tau_{\text{mol},0}$ is simply~$\tau_\text{mol}$ at the present day. We 
-generalize this formula to the following form: 
-\begin{equation} 
-\tau_\text{mol} = \tau_{\text{mol},0}(t/t_0)^\gamma 
-\label{eq:tau_mol}
-\end{equation} 
-In this paper we present models which adopt~$\tau_{\text{mol},0}$ = 2 Gyr 
-\citep{Leroy2008, Leroy2013, Tacconi2018} and~$\gamma$ = 1/2 based on this 
-argument. We have also ran simulations which adopt~$\tau_{\text{mol},0}$ = 1 
-Gyr and~$\gamma$ = 0 (a time-independent~$\tau_\text{mol}$), and found similar
-results. In all timesteps an annnuli,~\texttt{VICE} infers~$\Sigma_\text{g}$ 
-from~$\dot{\Sigma}_\star$ given our equations~\refp{eq:sf_law} and 
-\refp{eq:tau_mol}.
-
-% fig 5 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.45]{sfe.pdf} 
-\caption{The star formation efficiency timescale~$\tau_\star$ as a function of 
-Galactocentric radius at simulation times of 2 Gyr (red), 4 Gyr (yellow), 
-6 Gyr (green), 8 Gyr (blue), 10 Gyr (purple), and 12.2 Gyr (the present day, 
-black) predicted by our inside-out SFH model. } 
-\label{fig:sfe} 
-\end{figure}
-
-In Fig.~\ref{fig:sfe}, we plot~$\tau_\star$ as a function of~$R_\text{gal}$ at 
-six different time stamps predicted by our fiducial, inside-out SFH model. At 
-$R_\text{gal} \lesssim$ 6 kpc,~$\tau_\star$ is near~$\tau_\text{mol}$ at all 
-times, implying a molecular fraction of unity at these radii. Although this 
-prediction is likely unrealistic because 21-cm line observations suggest the 
-presence of neutral hydrogen as close to the Galactic centre as several hundred 
-pc~\citep{Kalberla2009}, we find in practice that changing our assumptions 
-about the star formation law does not impact our conclusions. In collecting 
-results for this paper, we investigated purely linear, purely power-law, and 
-broken power-law characterizations, finding similar predictions in all cases. 
-In general we find that the detailed form of the SFH, and to some extent the 
-time-dependence of radial migration, exert much greater power in establishing 
-the model predictions than does the star formation law. Nonetheless it is an 
-interesting result that a~$\dot{\Sigma}_\star - \Sigma_\text{g}$ relation 
-informed by the observed, population averaged trend and the normalization of 
-our SFHs implied by the stellar mass of the Milky Way predicts such a 
-discrepancy with the observed HI distribution. We refrain from further 
-discussion of this with the finding that it doesn't impact the conclusions 
-detailed in the present paper.
-
-\subsection{Surface Density Gradient} 
-\label{sec:methods:surface_density_gradient}
-
-% fig 6 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.45]{surface_density_gradient.pdf} 
-\caption{The surface density of gas (blue) and stars (red) as predicted by our 
-inside-out SFH model. The dotted black line with the higher normalization 
-denotes a thin disc profile with scale length~$R_t$ = 2.5 kpc; the other 
-denotes a thick disc profile with scale length~$R_T$ = 2.0 kpc, and a ratio of 
-$\Sigma_T/\Sigma_t$~= 0.27 at~$R_\text{gal}$~= 0. The solid black line denotes 
-the sum of the two; this is the surface density gradient of the Milky Way as 
-reported by~\citet{Bland-Hawthorn2016}, renormalized to imply the same total 
-stellar mass within the disc as our models. } 
-\label{fig:surface_density} 
-\end{figure}
-
-As discussed in~\S~\ref{sec:methods:sfhs}, Appendix~\ref{sec:normalize_sfh} 
-presents justification of a recipe in which we select a unitless function 
-describing the stellar surface density gradient~$g(R_\text{gal})$. In setting 
-the normalization, our model ensures that the integral of~$g(R_\text{gal})$ 
-over the surface area of the disc predicts a total stellar mass in agreement 
-with that observed for the Milky Way. For this value, we adopt 
-$M_\star^\text{MW} = (6.08 \pm 1.14)\times10^{10}$~\msun~\citep{Licquia2015}. 
-This is the total stellar mass of the Galaxy, including the bulge; 
-\citet{Licquia2015} report~$(5.17 \pm 1.11)\times10^{10}$~\msun~as the mass of 
-the disc alone. Although we aren't modeling the bulge here, our model extends 
-to~$R_\text{gal}$ = 0 and our sample of candidate analog star particles from 
-\texttt{h277} includes those with bulge-like kinematics. 
-\par 
-In this paper we adopt the following double exponential form for 
-$g(R_\text{gal})$, describing the thin and thick disc components of the 
-Galaxy: 
-\begin{equation} 
-g(R_\text{gal}) = e^{-R_\text{gal}/R_t} + \frac{\Sigma_T}{\Sigma_t} 
-e^{-R_\text{gal}/R_T} 
-\label{eq:gradient} 
-\end{equation} 
-where~$R_t$~and~$R_T$~are the scale radii of the thin and thick discs, 
-respectively, and~$\Sigma_T/\Sigma_t$~is the ratio of their surface densities 
-at~$R_\text{gal}$~= 0. We adopt~$R_t$~= 2.5 kpc,~$R_T$~= 2.0 kpc, and 
-$\Sigma_T/\Sigma_t$~= 0.27 based on the findings of~\citet{Bland-Hawthorn2016}. 
-We plot the single exponential forms of each disc component as a dotted black 
-line in Fig.~\ref{fig:surface_density}, with the solid black line denoting the 
-sum of the two. Althoug these scale radii are smaller than the commonly adopted 
-scale radius for a single exponential disc of~$r_s \approx$~3 kpc 
-\citep[e.g.][]{Binney2008}, our choice of a double exponential disc here 
-necessitates a choice be made for not one but two scale radii. 
-\par 
-We plot the resultant surface density gradients from our fiducial, inside-out 
-SFH model in Fig.~\ref{fig:surface_density} as well, with red denoting the 
-stellar gradient and the gas in blue. We note that the stellar gradient very 
-nearly follows our target gradient denoted by the solid black line and 
-expressed by equation~\refp{eq:gradient}. Stellar migration has indeed not 
-altered the overall form of the gradient, simply introducing scatter around the 
-adopted trend. Although there are slight enhancements at small~$R_\text{gal}$ 
-and deficits at large~$R_\text{gal}$, the agreement is excellent in the regions 
-of the Galaxy where the gradient is best constrained observationally. The 
-$R_\text{gal}$ > 15.5 kpc populations are also composed entirely of stars that 
-migrated there, since that is the radius at which we shut of star formation; 
-with this mind, the under-prediction at these radii is unsurprising. 
-Furthermore, in this paper we are interested primarily in the~$R_\text{gal}$~= 
-3 - 15 kpc range anyway, since this is the region where disc stars are the 
-dominant populations. We also note that the gas gradient
-shows a break in the scale radius near~$R_\text{gal} \approx$ 
-6 kpc. This is a consequence of our adopted star formation law; at 
-$\Sigma_\text{g} = 2\times10^7$~\msun~\persqkpc~the relation changes from 
-linear at higher densities to~$\dot{\Sigma}_\star \sim \Sigma_\text{g}^{3.6}$ 
-at lower densities (see discussion in~\S~\ref{sec:methods:sfe}). Because we are 
-running~\texttt{VICE} in star formation mode, it's more accurate to say that 
-$\Sigma_\text{g}$~is a weak function of~$\dot{\Sigma}_\star$~at 
-$\Sigma_\text{g} \leq 2\times10^7$~\msun~\persqkpc~in this range as opposed to 
-$\dot{\Sigma}_\star$~being a strong function of~$\Sigma_\text{g}$. When looking 
-at the present-day gradient, this presents as a flattening of the gradient at 
-the radius where~$\Sigma_\text{g} = 2\times10^7$~\msun~\persqkpc; further 
-inspection along the y-axis of Fig.~\ref{fig:surface_density} confirms that 
-this break indeed occurs at this value of~$\Sigma_\text{g}$. 
-\par 
-Although we adopt the~\citet{Licquia2015} stellar mass of the Milky Way here, 
-we find similar results when taking a value which differs by an order of 
-magnitude. While mass typically cancels in one-zone models of chemical 
-evolution, the abundances instead determined by the evolutionary parameters 
-(e.g.~$\eta$~and~$\tau_\star$), this value sets the normalization of the 
-SFH~$\dot{\Sigma}_\star(t, R_\text{gal})$ in our models. In turn this impacts 
-the surface densities of gas~$\Sigma_\text{g}$ inferred at each timestep, and 
-thus the abundances to some extent. This choice only matters insofar as the 
-choice of star formation law matters, which we find to not impact our 
-conclusions.
-
-\subsection{Summary} 
-\label{sec:methods:summary} 
-In summary, our fiducial model has an inside-out SFH with e-folding timescales 
-derived from the observations of~\citet[][see discussion in~\S 
-\ref{sec:methods:sfhs}]{Sanchez2020}. Radial migration proceeds in a manner in 
-which our model stellar populations have a change in radius 
-$\Delta R_\text{gal}$ informed from the~\texttt{h277} hydrodynamical simulation 
-\citep[][see discussion in~\S~\ref{sec:methods:h277}]{Christensen2012, 
-Zolotov2012, Loebman2012, Loebman2014, Brooks2014}. In the base-line model, 
-stars move to their final radius with a~$\sqrt{\text{age}}$~dependence 
-(\citealp{Frankel2018, Frankel2020} model stellar migration with a similar 
-characterization; see discussion in~\S~\ref{sec:methods:migration}). Using 
-\texttt{VICE} to calculate abundances for O and Fe in this paper, our supernova 
-yields are adopted from~\citet{Johnson2020}, who in turn take these values from 
-\citet{Weinberg2017}. Outflows are characterized such that the equilibrium 
-abundance of oxygen under a constant SFH follows an abundance gradient in 
-agreement with observational results in the Milky Way (see discussion in 
-\S~\ref{sec:methods:yields};~\citet{Nidever2014} make use of similar 
-methodology). Our star formation law is based on the~\citet{Bigiel2010} and 
-\citet{Leroy2013} data presented in comparison with theoretical models in 
-\citet[][see discussion in~\S~\ref{sec:methods:sfe}]{Krumholz2018}. To describe 
-the stellar surface density gradient, we adopt the two-exponential form 
-describing the thin and thick discs from~\citet[][see discussion in~\S 
-\ref{sec:methods:surface_density_gradient}]{Bland-Hawthorn2016}. 
-\par 
-Our quality cuts imposed on the star particles from~\texttt{h277} yields a 
-sample of 3,000,556 candidate analog star particles (see discussion in~\S 
-\ref{sec:methods:h277}), only~$\sim$57\% of which have disc-like kinematics 
-at the present day. Since we're modeling the thin and thick disc populations 
-here,~$\sim$1.71 million is a much better estimate of the number of star 
-particles that we can realistically sample from. We take~$\Delta R_\text{gal}$ 
-= 100 pc as the width of each annulus from~$R_\text{gal} = 0$~to 20 kpc and a 
-timestep size of~$\Delta T$~= 10 Myr from~$T = 0$~to 12.2 Gyr. With the 
-resulting 200 zones and 1,221 timesteps, we let~\texttt{VICE} form~$n = 9$ 
-stellar populations per annulus per timestep, resulting in 2,197,000 total 
-stellar populations with predicted masses and abundances. While this is more 
-than the number of disc particles in our sample of candidate analogs, we force 
-the star formation rate to zero beyond~$R_\text{gal}$ = 15.5 kpc; while these 
-stellar populations exist within~\texttt{VICE} and are a part of the 
-computational overhead, they have zero mass and thus do not contribute to the 
-chemical evolution in our models. This results in 1,692,306 stellar 
-populations with~\textit{non-zero} masses and abundances predicted by 
-\texttt{VICE}, reasonably within the limit of what we can sample. These 
-simulations run in~$\sim$2.5 hours and take up~$\sim$235 MB of disc space per 
-output, including the extra data that we record for each stellar population's 
-analog star particle. Lastly, we adopt a~\citet{Kroupa2001} IMF throughout this 
-paper. 
-\par 
-We have ran~\texttt{VICE} for all four of our SFHs, all four migration 
-models, and all four variations in~$\tau_\text{mol}$ noted in~\S 
-\ref{sec:methods:sfe} - a total of 64 simulations, as well as a variety of 
-other test cases. In this paper, we present results wherever the model 
-prescriptions are sensitive to the assumptions. However, in general the 
-differences can be understood with only the variations in star formation 
-history and the qualitative notion that many stars have moved beyond their 
-birth radius. \texttt{VICE} calculates abundances for nearly 2 million stellar 
-populations per model; to ensure that resolution does not impact our 
-conclusions, we have also ran variations with~$n$~= 2 stellar populations per 
-zone per timestep, and found similar results in all cases.
-
-\section{Comparison to Observations} 
-\label{sec:obs_comp}
-
-% fig 7 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.28]{ofe_feh_densitymap.pdf} 
-\caption{[O/Fe]-[Fe/H] diagrams for 15 Galactic regions spanning five bins in 
-$R_\text{gal}$ and~$\left|z\right|$. Each region has its own panel, with 
-radial bins shown in columns denoted at the top, and with bins in 
-$\left|z\right|$ shown in rows denoted in text in the middle column. For each 
-region, we plot~$N$~= 10,000 points sampled from our simulated stellar 
-populations predicted by our inside-out SFH model, where the probability of 
-sampling is proportional to the present-day mass of each stellar population. 
-In all panels, points are colour-coded according to the Galactocentric radius 
-of birth of the stellar population. For reference, we plot in a solid black 
-line in all panels the gas-phase [O/Fe]-[Fe/H] track predicted by the same 
-SFH in the~$R_\text{gal}$ = 8 kpc annulus, but with the post-processing 
-migration model; this curve is the same in all panels. } 
-\label{fig:ofe_feh_diagram} 
-\end{figure*}
-
-We begin the comparison of our model predictions to observational data with the 
-distribution of stellar populations in the [O/Fe]-[Fe/H] plane. We separate 
-stars into bins based on their present-day Galactic regions defined by five 
-bins in~$R_\text{gal}$ (3 - 5, 5 - 7. 7 - 9, 9 - 11, and 11 - 13 kpc) and three 
-bins in~$\left|z\right|$ (0 - 0.5, 0.5 - 1, and 1 - 2 kpc). Within each of the 
-resulting 15 regions, we sample 10,000 stars at random from our base-line 
-inside-out SFH model. Since stars in~\texttt{VICE} are stand-ins for entire 
-stellar populations, we let the probability of sampling one of them be 
-proportional to its present day mass. We plot the results of this procedure in 
-Fig.~\ref{fig:ofe_feh_diagram}, colour-coding each stellar population by its 
-birth radius; for reference, we also plot the gas-phase track which resulted 
-from the~$R_\text{gal}$ = 8 kpc annulus with the post-processing migration 
-model in a black solid line in all panels. 
-\par 
-In Fig.~\ref{fig:ofe_feh_diagram}, we note that high-$\alpha$~sequence stars 
-are predicted to be the dominant population at small~$R_\text{gal}$ and high 
-$\left|z\right|$; conversely, the low-$\alpha$~sequence dominates the 
-statistics at large~$R_\text{gal}$~and low~$\left|z\right|$. This is consistent 
-with the observational results of~\citet{Hayden2015}, who present a density map 
-in the [O/Fe]-[Fe/H] for the same Galactic regions (see their Fig. 4). 
-Furthermore, the locus of the low-$\alpha$ sequence shifts from super-solar 
-[Fe/H] to sub-solar [Fe/H] with increasing~$R_\text{gal}$, a shift which is 
-expected given the abundance gradient that we have built into our models (see 
-discussion in~\S~\ref{sec:methods:yields}). The colour-coding of the points 
-further suggests that the width of the low-$\alpha$~sequence arises out of 
-stellar migration. Though this wouldn't occur in our models without mixing, it 
-is to some extent expected from that in combination with the built-in gradient. 
-Nonetheless this theoretical interpretation of the low-$\alpha$ sequence is 
-consistent with the arguments of~\citet{Schoenrich2009} and~\citet{Nidever2014}. 
-\par 
-We clarify that we do not claim to recover the bimodality in [$\alpha$/Fe] as 
-observed here. Although there are authors who argue to have successfully 
-reproduced such results using an inside-out SFH with stellar migration 
-\citep[e.g.][]{Sharma2020}, we find that our fiducial model fails to reproduce 
-these results (see discussion in~\S~\ref{sec:obs_comp:ofe_dists}). These 
-results do nonetheless suggest that the spatial dependence of the two sequences 
-can be attributed to stellar migration. Lastly, we note that we find similar 
-results with our other three SFHs, increasing confidence in our argument that 
-migration establishes such a spatial dependence rather than the SFH. The only 
-notable difference is that the starburst models predict a slightly higher 
-characteristic [O/Fe] for the low-$\alpha$ sequence ($\sim$+0.1). This is a 
-natural consequence of the starburst producing young,~$\alpha$-enhanced stars 
-in excess of what is predicted by the baseline model~\citep{Johnson2020}.
-
-\subsection{Abundance Gradients} 
-\label{sec:obs_comp:gradient}
-
-% fig 8
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.42]{tracks.pdf} 
-\caption{\textbf{Left}: Gas phase evolutionary tracks in the [O/Fe]-[Fe/H] 
-plane for our inside-out SFH with either post-processing (dotted lines) or 
-diffusion (solid lines) migration models. We plot tracks for seven annuli, 
-colour-coded according to their Galactocentric radius and denoted by the 
-legend in the lower-left. We mark simulation times of 2, 4, 6, 8, 10, and 12.2 
-Gyr in X's for the diffusion model and points for the post-processing model. 
-\textbf{Right}: As a function of simulation time, a proxy for the SN Ia rate 
-using the total time-derivative of the Fe mass in a given annulus, calculated 
-by subtracting the contribution from recycling and CCSN enrichment and adding 
-back that lost to star formation and outflows. We show these rates for the 
-same annuli as in the left-hand panel, multiplying them by various prefactors 
-to improve clarity. } 
-\label{fig:tracks} 
-\end{figure*}
-
-We continue by assessing the impact of stellar migration on the gas-phase 
-tracks in the [O/Fe]-[Fe/H] plane. To this end, we compare the predictions of 
-our post-processing migration model, which has stars stay at their radii of 
-birth until they instantaneously migrate at the present day, and our diffusion 
-model, which has stars migrating continuously with a~$\sqrt{\text{age}}$ 
-dependence. In the left-hand panel of Fig.~\ref{fig:tracks}, we plot the 
-[O/Fe]-[Fe/H] tracks at several radii assuming the inside-out 
-SFH, with post-processing shown in dotted lines and the diffusion in solid 
-lines. We also mark simulation times of 2, 4, 6, 8, 10, and 12.2 Gyr on each 
-track for reference. 
-\par 
-We note first and foremost that there are considerable differences between the 
-two sets of tracks, particularly at high [O/Fe]. We demonstrate here that this 
-arises out of variability in SN Ia rates caused by the time-dependent radial 
-migration of the diffusion model. From our~\texttt{VICE} outputs, the total 
-time derivative of the Fe mass in a given annulus can be obtained by its change 
-across a single timestep. By then subtracting the CCSN contribution (known 
-exactly given our adopted yield and the SFR), approximately correcting for 
-recycling, and adding back that which was lost to star formation and outflows, 
-we obtain a simple estimate of the rate of Fe production by SNe Ia. 
-\par 
-We plot this proxy as a function of simulation time in the right-hand panel of 
-Fig.~\ref{fig:tracks}, with dotted and solid lines again denoting 
-post-processing and diffusion migration models and the same colour-coding as in 
-the left-hand panel; we have also multiplied these curves by various prefactors 
-to improve clarity. As expected, the post-processing model predicts a SN Ia 
-rate which is a smooth function of time at a given~$R_\text{gal}$. The diffusion 
-model on the other hand exhibits significant variability on~$\sim$Gyr 
-timescales; the time-averaged SN Ia rate tends to follow the post-processing 
-prediction, but the instantaneous rates do not agree. A close comparison allows 
-one to realize that whenever one of the tracks in the left-hand panel shows 
-higher (lower) [O/Fe] at a given [Fe/H], there is an excess (deficit) in the SN 
-Ia rate at a similar time and radius. Early times in the~$R_\text{gal}$ = 15 
-kpc annulus illustrates a rather extreme example whereby the SN Ia rate is 
-effectively zero for nearly 3 Gyr. We also note that the fractional amplitude 
-of the variability increases with~$R_\text{gal}$; the log-scaled y-axis makes 
-this clear. This makes sense physically because the lower stellar number 
-density in the outer Galaxy means it would be much more susceptible to sampling 
-noise. That is, a single star migrating has a larger fractional impact at 
-large radii than small radii.
-
-% fig 9 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.32]{metallicity_gradient.pdf} 
-\caption{Radial abundance gradients in [O/H] (top, red), [Fe/H] (top, blue), 
-and [O/Fe] (bottom) for our four fiducial SFHs - constant (far left), 
-inside-out (left-middle), late-burst (right-middle), and outer-burst (far 
-right). We plot the gas-phase abundance at the present day as a function of 
-Galactocentric radius in solid lines. Stars denote the median of the stellar 
-MDF of the 100-pc width annulus at a given radius, with shaded regions marking 
-the 16th and 84th percentiles thereof. Black lines in the top panels denote our 
-target [$\alpha$/H] gradient of mode([$\alpha$/H]) = +0.3 at~$R_\text{gal}$~= 
-4 kpc with a slope of -0.08 kpc$^{-1}$. } 
-\label{fig:metallicity_gradient} 
-\end{figure*}
-
-Although one may expect the rates predicted by the two migration models to 
-agree based on the dynamical argument that a star migrating outward should be 
-balanced by a star migrating inward due to the conservation of energy, the SN 
-Ia rate depends not only on stellar number density but also on the masses and 
-ages of the stellar populations. While an inwardly migrating star should be 
-balanced dynamically by an outwardly migrating one, the SN Ia rate is 
-unaffected only when the two have masses and ages such that the SN Ia DTD has 
-the same value for both stars. Fluctuations in the SN Ia rate at these 
-amplitudes can be understood through a comparison of the timescales associated 
-with radial migration and SN Ia events. In Fig.~\ref{fig:h277_decomposition}, 
-we plotted the distribution of final radii in bins of birth radius and age, 
-which are used in driving stellar migration in our models (see discussion in~\S 
-\ref{sec:methods:h277}). From this, we noted that~$\sim$40\% of~\texttt{h277} 
-star particles migrated beyond their birth radius by the time they were~$\sim$2 
-Gyr old. Though our adopted form differs slightly in detail, if the SN Ia DTD 
-is a~$\sim t^{-1}$ power-law with a minimum delay time of~$\sim$100 Myr 
-\citep{Maoz2012, Maoz2017}, then there should be similar numbers of SN Ia 
-events with delay times between 1 and 10 Gyr as there are between 100 Myr and 1 
-Gyr. While our~$R_\text{gal}$~= 15 kpc annulus is something of an extreme 
-example, when one realizes that this means~$\sim$half of SN Ia progenitors may 
-move significantly beyond their birth radius, the amplitude of the variability 
-seen in the right-hand panel of Fig.~\ref{fig:tracks} is not surprising. The 
-fact that >10\% of events are seen at >10 kpc from their host galaxies in the 
-ASAS-SN bright SN catalog~\citep{Holoien2019} adds qualitative, observational 
-support to the argument that SN Ia progenitors may often form at significantly 
-different radii than where the explosions are observed. 
-\par 
-We thus argue that the radial migration of nucleosynthetic yields can occur 
-alongside stellar migration for delayed sources. Though we do not investigate 
-this effect for such elements in this paper, it would be reasonable to expect 
-similar predictions for s-process elements produced in AGB stars like carbon, 
-nitrogen, strontium, yttrium, and zirconium as well as r-process elements from 
-neutron star mergers if the associated DTD is sufficiently long. What we really 
-learn from this investigation is that tracks are not simple functions when 
-stellar migration is taken into account. To first order, they're characterized 
-by the late-time equilibrium abundance and the value of~$\tau_\star$~setting 
-the position of the ``knee''~\citep{Weinberg2017}, though migration causes 
-noticeable variations which should depend on the details of the adopted 
-dynamical history. In~\S~\ref{sec:obs_comp:age_alpha}, we demonstrate that 
-this is a means with which truly young, super-solar [$\alpha$/Fe] stars in the 
-solar neighborhood can be explained theoretically. 
-\par 
-We continue with an investigation into the radial abundance gradients predicted 
-by our models. To some extent, a gradient is built into our models via a 
-scaling of the mass loading factor~$\eta$~with Galactocentric radius (see 
-discussion in~\S~\ref{sec:methods:yields}). In parameterizing the 
-$\eta-R_\text{gal}$ scaling, we assumed our constant SFH model and the 
-associated equilibrium abundance for alpha elements. Like the surface density 
-gradient, we also assumed that stellar migration does not alter the overall 
-form. We plot the radial [O/H] and [Fe/H] gradients predicted by all our 
-models in the top row of Fig.~\ref{fig:metallicity_gradient}, and the [O/Fe] 
-gradients in the bottom row. In all panels, stars denote the median abundance 
-in each annulus, and the shaded region denotes the 16th and 84th percentiles of 
-the MDF in that zone; solid lines denote the gas-phase gradient at the present 
-day. Although we built the gradient into our models based on the mode abundance, 
-we illustrate them here according to the median; we find that with annuli as 
-narrow as~$\Delta R_\text{gal}$~= 100 pc, the mode is a sufficiently noisy 
-statistic to introduce noticeably more scatter in this relation. Nonetheless we 
-have verified that it follows the trend implied by our target gradient, 
-illustrated by the solid black line. The median gradient for all of our model 
-SFHs follows a slightly shallower trend than the mode, which is expected when 
-the metallicity distribution is skew-negative in the inner Galaxy and 
-skew-positive in the outer Galaxy. 
-\par 
-We note that our models indeed recover an~$R_\text{gal}$-[O/H] relation 
-resembling that which was adopted. As was the case for the surface density 
-gradient (see discussion in~\S~\ref{sec:methods:surface_density_gradient}), 
-stellar migration appears to only introduce scatter. While our procedure for 
-setting setting the abundance gradient did not consider Fe, our models predict 
-it to follow a gradient similar to that of O. We further note that all SFHs 
-predict an [O/Fe] gradient which is relatively flat at all radii, steepening 
-only at very small and very large~$R_\text{gal}$. The trend toward higher 
-[O/Fe] beyond~$R_\text{gal}$~= 15.5 kpc is expected, since this is the radius 
-at which we shut off star formation; all stellar populations at these radii at 
-the present day formed in the disc and migrated there, meaning this region of 
-space in our model is populated only by stars sufficiently old to have migrated 
-such distances. Because they're old, they also tend to be~$\alpha$-enhanced. 
-This is consistent with the findings of~\citet{RadburnSmith2012}, who argue 
-that the outskirts of the NGC 7793 disc formed largely out of stellar 
-migration. {\color{red} Observational reference on the increase in [O/Fe] at 
-small~$R_\text{gal}$? Maybe~\citet{Hayden2015}, but I'm not sure.} 
-\par 
-We also note that our models predict differences between the stellar and 
-present-day gas-phase gradients which are sensitive to the adopted SFH. In the 
-constant SFH model, the gas-phase gradient follows the mode abundance by 
-construction. In the inside-out, late-burst, and outer-burst models, the 
-ISM at small~$R_\text{gal}$~is considerably more metal-rich than the stars at 
-similar radii. The late-burst model shows the largest difference; this is a 
-consequence of the starburst at small~$R_\text{gal}$, an effect which is absent 
-in the outerburst model. In accretion-induced starbursts, re-enrichment can 
-briefly produce super-equilibrium abundances in the gas-phase which then decay 
-back to the equilibrium abundance as the SFR declines~\citep{Johnson2020}. This 
-effect can also be seen in the outer-burst model; at~$R_\text{gal}$ slightly 
-larger than 6 kpc where the starburst did occur, the abundances are larger than 
-at slightly less than 6 kpc, where the star burst did~\textit{not} occur. 
-Altogether, these differences are reflective of the notion that the stellar 
-abundance gradient is sensitive to stars of all ages and thus the entire star 
-formation history, while the gas-phase gradient is more reflective of 
-enrichment over the previous depletion time.
-
-\subsection{Metallicity Distributions Functions} 
-\label{sec:obs_comp:mdfs}
-
-% fig 10 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.34]{mdf_3panel_fe.pdf} 
-\caption{Metallicity distribution functions (MDFs) in [Fe/H] predicted by our 
-fiducial, inside-out model (left) and as observed in APOGEE DR16 (right), for 
-stars and simulated stellar populations with present-day~$\left|z\right|$~= 0 - 
-0.5 kpc (bottom), 0.5 - 1 kpc (middle), and 1 - 2 kpc (top). MDFs are shown in 
-bins of Galactocentric radius: 3 - 5 kpc (black), 5 - 7 kpc (red), 7 - 9 kpc 
-(yellow), 9 - 11 kpc (green), 11 - 13 kpc (blue), and 13 - 15 kpc (purple). 
-The points near the top of the bottom panels denote what the mode abundance 
-would be if it followed out target gradient of [Fe/H] = +0.3 at~$R_\text{gal}$ 
-= 4 kpc with a slope of -0.08 kpc$^{-1}$ exactly, assuming the inner radius of 
-each bins (i.e. there is no point plotted for 15 kpc). All distributions are 
-smoothed with a box-car width of [Fe/H]~$\pm$~0.1 for clarity. } 
-\label{fig:mdf_3panel_fe} 
-\end{figure}
-
-% fig 11 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.34]{mdf_3panel_o.pdf} 
-\caption{The same as Fig.~\ref{fig:mdf_3panel_fe}, but for [O/H]. } 
-\label{fig:mdf_3panel_o} 
-\end{figure}
-
-Metallicity distribution functions (MDFs) and how they vary with Galactic 
-region are one of the core predictions of chemical evolution models. In this 
-section, we compare our model predicted MDFs to those observed in the 16th 
-data release of APOGEE (DR16;~\citealp{Ahumada2020, Majewski2017}). The 
-data are reduced using the APOGEE Stellar Parameters and Chemical Abundances 
-Pipeline (ASPCAP;~\citealp{Holtzman2015, GarciaPerez2016}). For further details 
-of the APOGEE survey, a brief summary can be found in~\S~2 of 
-\citet{Weinberg2019}. We restrict our sample to stars with effective 
-temperatures of 4000 K~$\leq T_\text{eff} \leq$~4600 K, surface gravities of 
-1.0~$\leq \log g \leq$~2.5, and signal-to-noise ratios of at least 100. These 
-cuts ensure that our sample consists of stars on the upper red giant branch, 
-safely excluding red clump stars to avoid obvious systematics in the 
-abundance distributions. 
-\par 
-In the disc midplane, stars as observed by APOGEE are known to exhibit mode 
-[$\alpha$/H] and [Fe/H] abundances that depend on Galactocentric radius, with a 
-skew-negative distribution in the inner Galaxy and skew-positive in the outer 
-Galaxy~\citep{Hayden2015, Weinberg2019}. Off the midplane, the MDFs converge on 
-[$\alpha$/H]~$\approx$~[Fe/H]~$\approx$~-0.5. This result is replicated in the 
-right-hand column of panels~\ref{fig:mdf_3panel_fe} and~\ref{fig:mdf_3panel_o}. 
-The left-hand columns show the distributions predicted by our fiducial 
-inside-out model. We note that these replicate the qualitative scaling of the 
-mode [O/H] and [Fe/H] with present-day Galactocentric radius, though our APOGEE 
-data suggest that the 3 - 5 and 5 - 7 kpc bins share a common mode abundance. 
-This was also seen in~\citet{Hayden2015}. Our models do not predict this 
-detail; this could indicate that we have incorrectly parameterized outflows in 
-the inner Galaxy (see discussion regarding our scaling of the mass loading 
-factor~$\eta$~with~$R_\text{gal}$ in~\S~\ref{sec:methods:yields}). We would 
-expect a flat [X/H] gradient and MDFs with similar modes if we simply chose it 
-to be so by letting~$\eta$~be constant at small~$R_\text{gal}$. Another 
-possibility is the cessation of star formation in these regions; by tracing 
-products of star formation such as HII regions~\citep{Guesten1982}, supernova 
-remnants~\citep{Leahy1989}, and pulsars (\citealp*{Lyne1985}; 
-\citealp{Case1998}), the surface density of star formation~$\dot{\Sigma}_\star$ 
-in the Milky Way is known to reach a maximum at~$R_\text{gal} \approx$~4 kpc 
-(see Fig. 1 of~\citealt{Peek2009} and Fig. 2 of~\citealt{Fraternali2012}). Our 
-models by construction predict~$\dot{\Sigma}_\star$ to decrease monotonically 
-with~$R_\text{gal}$~(see Fig.~\ref{fig:evol}). If the Milky Way has begun 
-quenching star formation, a process which is believed to begin in the centres 
-of galaxies at this mass~\citep[e.g.][]{Ellison2020b}, then fewer stars would 
-form in the most metal-rich regions than do in our models, cutting off the MDF 
-at high [O/H] and [Fe/H]. 
-\par 
-Beyond the midplane, our models fail to fully replicate the convergence of the 
-MDFs at [X/H]~$\approx$~-0.5. The observed MDF at small radii shfits from 
-skew-negative with a metal-rich mode to skew-positive with a metal-poor 
-mode with increasing~$\left|z\right|$. In our model predicted MDFs for small 
-$R_\text{gal}$, the mode does shift to lower abundances, but not to the same 
-extent as in the observed sample, and with minimal change in skewness. 
-Although the model predicts a portion of the effect, it cannot account for the 
-entire~$\left|z\right|$-dependence of the MDF shape in the inner Galaxy.
-
-\subsection{[O/Fe] distributions in Bins of [Fe/H]} 
-\label{sec:obs_comp:ofe_dists} 
-In this section we compare our predicted [O/Fe] distributions in various 
-Galactic regions to those recently published in~\citet{Vincenzo2021a}. As in our 
-\S~\ref{sec:obs_comp:mdfs}, they also make use of APOGEE DR16 
-\citep{Ahumada2020, Majewski2017}, and impose a similar set of cuts on 
-effective temperature, surface gravity, and signal-to-noise (see their~\S~2). 
-These distributions are estimates of the~\textit{intrinsic} [O/Fe] 
-distributions that, when 
-convolved with observational uncertainties and the APOGEE selection function, 
-would resemble the observed MDFs like those in~\citet{Hayden2015}. We show the 
-distributions predicted by our fiducial model in~$\Delta$[O/Fe] = 0.04 bins 
-across 15 Galactic regions in comparison to the~\citet{Vincenzo2021a} 
-distributions shown in dashed lines in Fig.~\ref{fig:ofe_mdfs_insideout}. 
-Galactic regions 
-are defined by a range in~$R_\text{gal}$, shown in columns and denoted at the 
-top of the figure, and a range in~$\left|z\right|$, shown in rows and denoted 
-in text in the left-hand column. We show this comparison for two bins in 
-[Fe/H], colour-coded according to the legend in the top-right panel.
-
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.32]{ofe_mdfs.pdf} 
-\caption{Predicted distributions in [O/Fe] in 15 Galactic regions and in two 
-bins in [Fe/H]. Columns correspond to bins in~$R_\text{gal}$, denoted at the 
-top of each column. Rows correspond to bins in~$\left|z\right|$, denoted in 
-text in the left-hand column. Distributions are color-coded according to the 
-[Fe/H] the sample is drawn from, denoted by the legend in the upper right 
-panel. Solid lines represent that predicted by our inside-out SFH in 
-$\Delta$[O/Fe] = 0.04 bins, while dashed lines correspond to the fits to the 
-APOGEE DR16 data presented in~\citet{Vincenzo2021a}, which quantify the 
-intrinsic distributions accounting for observational uncertainties and the 
-APOGEE selection function. } 
-\label{fig:ofe_mdfs_insideout} 
-\end{figure*}
-
-Finding similar results for all of our SFHs, we note that our model adequately 
-reproduces the broad nature of the [O/Fe] distributions at fixed [Fe/H] seen in 
-the APOGEE data. Some distributions in a specific Galactic region and [Fe/H] 
-bin show a bimodality in decent agreement with the observations (e.g. the 
--0.4~$\leq$~[Fe/H]~$\leq$~-0.2 bin at~$R_\text{gal}$~= 7 - 9 kpc and 
-$\left|z\right|$ = 1 - 2 kpc), but this is not true of all Galactic regions in 
-both metallicity bins. Instead, the principle failure of our model is that it 
-overpredicts the number of intermediate [O/Fe] stars. 
-\par 
-In the inner Galaxy, our model overestimates the mode [O/Fe] to some extent for 
-both [Fe/H] bins, but the difference is larger for the higher of the two. This 
-discrepancy also increases with increasing~$\left|z\right|$. At fixed 
-$R_\text{gal}$, the~\citet{Vincenzo2021a} distributions show two peaks which do 
-not change with~$\left|z\right|$; only their relative heights vary. This is 
-an assumption built into the model, but the agreement with the APOGEE data is 
-good. However, this is a region of the Galaxy where there aren't many APOGEE 
-stars. At~$\left|z\right|$ = 1 - 2 kpc for ~$R_\text{gal}$ = 3 - 5 and 5 - 7 
-kpc, the~\citet{Vincenzo2021a} model is fit to 31 and 17 stars, respectively. In 
-comparison, there are 109 in the solar annulus, and all other bins have >75 
-stars involved in the fit. It's possible the observed distributions shift 
-slightly to higher [$\alpha$/Fe], but at most at the~$\lesssim$~0.05 level 
-(see their Fig. 11). 
-\par 
-If this discrepancy persists in subsequent APOGEE data releases which will 
-better characterize the distributions in these regions, it's possible the 
-origin is tied to the Sagittarius dwarf. The~\texttt{h277} simulation, which 
-drives stellar migration in our models (see discussion in~\S 
-\ref{sec:methods}), did not have such an accretion event. With its most recent 
-major merger occurring at a redshift of~$z \approx$~3, this galaxy has 
-previously been selected for investigation expressly because of its quiescent 
-merger history~\citep[e.g.][]{Zolotov2012}. N-body models for the tidal 
-disruption of the Sagittarius dwarf, on the other hand, suggest pericentric 
-passages around 6.5, 4.5, 2.75, 1, and 0.1 Gyr ago~\citep{Law2010}. In addition 
-to potentially triggering episodes of star formation 
-\citep[e.g.][]{RuizLara2020}, more frequent pericentric passages of a massive 
-satellite could kinematically heat low-[$\alpha$/Fe] disc stars to higher 
-$\left|z\right|_\text{max}$~orbits. Such effects are not a component of the 
-dynamical history of~\texttt{h277}; this is one instance where running our 
-models with a different hydrodynamical simulation's star particles may be an 
-enlightening comparison. 
-\par 
-The notion that an [$\alpha$/Fe] dichotomy can arise out of radial migration 
-alone traces back to~\citet{Schoenrich2009}, and was later explored by 
-\citet{Nidever2014} and recently by~\citet{Sharma2020}. This however suggests 
-that an inside-out star formation history combined with stellar migration is not 
-conducive to predicting this observed result, even when a recent starburst is 
-added. The primary failure being an overpredicted frequency of intermediate 
-[$\alpha$/Fe] stars, this could point to a number of things. If the bimodality 
-is to arise out of inside-out Galaxy evolution and stellar migration alone, 
-then the transition between high- and low-$\alpha$ sequences needs to occur 
-faster than it does in these models. The analytic arguments of 
-\citet{Weinberg2017} suggest that the approach to equilibrium occurs on the 
-order of the SFE timescale~$\tau_\star$ (see~\S~\ref{sec:methods:sfe}). 
-Since we've adopted a star formation law which is motivated by observational 
-results, the failure of these models to reproduce the observed dichotomy 
-suggests that the typical SFE timescales as observed are not short enough to 
-explain such a fast transition. This would imply that either the Milky Way 
-occupied a special place in the scatter of the observed 
-$\dot{\Sigma}_\star-\Sigma_\text{g}$ relation at a time early in its 
-evolutionary history, or the bimodality arose out of alternative pathways. 
-Under our current assumptions, the simplest way to decrease the frequency of 
-intermediate [$\alpha$/Fe] stars is to simply shut off (or turn down) star 
-formation when the ISM is at such a composition. This is an indication 
-that two-infall evolutionary histories~\citep[e.g.][]{Chiappini1997, 
-Chiappini2001, Romano2010, Grisoni2017, Noguchi2018, Palla2020, Spitoni2016, 
-Spitoni2018, Spitoni2019a, Spitoni2020, Spitoni2021} would improve the 
-agreement between our model predictions and the observed distributions.
-
-\subsection{The Age-[$\alpha$/Fe] Relation} 
-\label{sec:obs_comp:age_alpha} 
-In this section, we assess the predicted age-[O/Fe] relations of our models, 
-using the results of~\citet{Feuillet2019} as the observational benchmark; their 
-stellar age measurements are based on isochrone matching. While we made 
-use of APOGEE DR16 data in comparing our model predictions to the observed 
-MDFs~\citep[][see~\S~\ref{sec:obs_comp:mdfs}]{Ahumada2020, Majewski2017}, they 
-made use of APOGEE DR14 stars for which parallax measurements are available 
-from Gaia~\citep{Abolfathi2014, GaiaDR2}. With their spatial and quality cuts, 
-the final 
-sample consisted of 77,562 stars. In bins of [O/Fe], they assume a gaussian 
-log age distribution, fitting the mean and standard deviation to the stars in 
-that bin. Because they assume a gaussian, they would report an equal mean 
-and median log age. This means that a one-to-one comparison of our model 
-predictions to their results is not free of nuance, because they predict 
-log age distributions which are highly non-gaussian at fixed [O/Fe]. 
-\par 
-The stellar populations from our simulations have different masses; this 
-necessitates weighting the age-distributions by present-day mass, because that 
-scales with the number of stars that a model stellar population represents. We 
-therefore adopt the 50th percentile of the mass-weighted age distribution in a 
-bin of [O/Fe] as the characteristic age to compare to the~\citet{Feuillet2019} 
-measurements. We refer to this quantity as the mass-weighted median age.
-
-% fig 13 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.34]{age_ofe_migration_comparison.pdf} 
-\includegraphics[scale = 0.34]{age_ofe_sfh_comparison.pdf} 
-\caption{
-\textbf{Left}: A comparison of the predicted age-[O/Fe] relation for the solar 
-annulus ($R_\text{gal}$ = 7 - 9 kpc and~$\left|z\right|$ = 0 - 0.5 kpc) between 
-the post-processing (upper left), diffusion (upper right), sudden (lower left), 
-and linear (lower right) migration models, assuming our inside-out SFH. 
-\textbf{Right}: The same as the left-hand panels, instead comparing the impact 
-of our constant (upper left), inside-out (upper right), late-burst (lower left), 
-and outer-burst (lower right) SFHs, assuming diffusion migration. In all panels, 
-red triangles and error bars denote the observed mean age and dispersion 
-thereof in bins of [O/Fe] as reported by~\citet{Feuillet2019}; here we include 
-only the bins containing at least 15 stars. Black squares denote the 
-mass-weighted median age in 0.02-dex bins in [O/Fe] predicted by our models, 
-with error bars denoting the 16th and 84th percentiles of the mass-weighted 
-age distribution in those bins. Points in the background denote each individual 
-stellar population from the model with a final position in the solar annulus, 
-colour-coded according to their Galactocentric radius of birth. 
-}
-\label{fig:age_alpha} 
-\end{figure*}
-
-In the left-hand set of panels of Fig.~\ref{fig:age_alpha}, we compare the 
-age-[O/Fe] relation in the solar annulus ($R_\text{gal}$~= 7 - 9 kpc and 
-$\left|z\right|\leq$~0.5 kpc) predicted by our four migration models to the 
-\citet{Feuillet2019} measurements, shown in red triangles. We mark the 
-mass-weighted median age in bins of [O/Fe] in each model with black squares, 
-and plot for reference in the background each individual stellar population in 
-the solar annulus, colour-coded according to its Galactocentric radius of birth. 
-\par 
-We note that the inside-out SFH, assumed by all four of the models illustrated 
-here, provides a reasonable description of the age-[O/Fe] relation as observed 
-in APOGEE. We also note that each model for the time-dependence of stellar 
-migration predicts differing amounts of scatter in the age-[O/Fe] relation. 
-Diffusion has the most, followed by linear, then sudden, and lastly 
-post-processing. We interpret this as a consequence of the variability in the 
-SN Ia rate as a function of radius and time caused by time-dependent migration 
-(see Fig.~\ref{fig:tracks} and associated discussion near the beginning of~\S 
-\ref{sec:obs_comp}). When the SN Ia rate is higher or lower than expected given 
-the SFH of an annulus, then the Fe abundance in that zone will increase or 
-decrease accordingly. This can occur if there is a significant net gain or loss 
-of SN Ia progenitors in a given time interval due to time-dependent migration. 
-The gas-phase [O/Fe] then decreases or increases in turn, and the stars which 
-form out of that gas inherit these compositions. When migration is taken into 
-account and stellar populations are mixed as a consequence, the observational 
-signature is intrinsic scatter in the age-[$\alpha$/Fe] relation. 
-\par 
-All of the models in the left-hand set of panels predict a correlation between 
-mass-weighted median age and [O/Fe] in good agreement the~\citet{Feuillet2019} 
-measurements assuming the inside-out SFH. This suggests that the population 
-averaged trend is unaffected by stellar migration. However, only the diffusion 
-and linear migration models predict a population of young ($\lesssim$~4 Gyr), 
-[$\alpha$/Fe]~$\approx$~+0.1 - 0.2 stars in the solar neighbourhood. These 
-stars are a part of the noticeable upward scatter in the relationship, and we 
-therefore interpret their origin to be the same as the scatter itself - they 
-formed in a region of the Galactic ISM at a time when it was particularly 
-alpha-enhanced due to a rather lasting deficit in SN Ia events. These stars 
-then migrated to the solar annulus, where they showed up in the APOGEE data 
-when stellar ages were measured using carbon-to-nitrogen ratios 
-\citep{Martig2016}, isochrone matching~\citep{Feuillet2018, Feuillet2019}, 
-and with the asteroseismic ages of the origin APOKASC catalog 
-\citep{Chiappini2015, SilvaAguirre2018, Pinsonneault2014}. 
-\par 
-\citet{SilvaAguirre2018} demonstrate that the observed young $\alpha$-rich 
-stars in the solar annulus have kinematics similar to the rest of the 
-high-$\alpha$ population, and suggested this may be the result of stellar 
-mergers or mass transfer events. This would produce a population of truly old 
-stars masquerading as young stars. In a sample of 51 young, $\alpha$-rich 
-red giants,~\citet{Hekker2019} demonstrate that a portion of these stars have 
-carbon-to-nitrogen ratios consistent with mass transfer events, but that others 
-do not, indicating they're either truly young stars or the result of mergers 
-on the main sequence. As far as we know, the mechanism discussed here is the 
-first theoretical explanation of the origin of these stars. We note 
-additionally that under this explanation, the young~$\alpha$-rich stars are 
-not so much $\alpha$-rich as they are Fe-poor, and form overwhelmingly at 
-large~$R_\text{gal}$ where the SN Ia rate is most variable (see discussion in 
-\S~\ref{sec:obs_comp:gradient}). 
-\par 
-In the right-hand set of panels in Fig.~\ref{fig:age_alpha}, we 
-compare the model predictions of our four different SFHs, assuming our 
-diffusion migration model, with the same plotting scheme and colour-coding as 
-in the left-hand panels. We note that the constant and inside-out SFHs describe 
-the data the best. Although our e-folding timescales for star formation are 
-sufficiently long at large~$R_\text{gal}$ such that there is little difference 
-between the constant and inside-out SFHs there anyway (see discussion in~\S 
-\ref{sec:methods:sfhs}), our constant SFH is idealized and of purely 
-theoretical interest, making the inside-out model the more likely of the two. 
-Below [O/Fe]~$\approx$~+0.1, the~\citet{Feuillet2019} data seem to follow a 
-slightly steeper age-[$\alpha$/Fe] relation than our inside-out model 
-predicts. This could point to any number of things being an inaccuracy in our 
-models: the detailed form of the SFH or the SN Ia DTD, our supernova yields, 
-or observational [O/Fe] errors, all of which are plausible. 
-\par 
-We note that our starburst models, both late-burst and outer-burst, disagree 
-with the~\citet{Feuillet2019} measurements. The late starburst produces a 
-population of young, $\alpha$-rich stars due to the perturbed ratio of core 
-collapse to type Ia supernova rates~\citep{Johnson2020}. With the starburst 
-occurring in a substantial fraction of the ISM in both models, the result is an 
-increase in the bulk [$\alpha$/Fe] for young stars which simply is not seen in 
-the observed sample. The effect is strong enough that at [O/Fe]~$\approx$~+0.1, 
-both models considerably overpredict the width of the distribution, 
-simultaneously predicting a mass-weighted median age many times the standard 
-deviation younger than observed. This discrepancy is of interest, because these 
-models were motivated by the observational results of~\citet{Mor2019} and 
-\citet{Isern2019} which suggest such a recent starburst. Although our 
-functional forms differ from what they reported in detail, they're reasonable 
-descriptions of the measurements within the error bars. This suggests that the 
-results of~\citet{Mor2019} and~\citet{Isern2019} are at odds with chemical 
-evolution models of the Milky Way. If the Galaxy truly experienced a recent 
-starburst, then something not included in our models had to prevent this global 
-increase in [$\alpha$/Fe].
-
-% fig 14 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.32]{age_alpha_regions.pdf} 
-\caption{The age-[O/Fe] relation in 12 Galactic regions predicted by our 
-inside-out SFH. Bins in Galactocentric radius are shown in columns, and labeled 
-at the top. Bins in the height~$\left|z\right|$ above/below the disc midplane 
-are shown in rows, noted in the left-hand column. Red triangles, black squares, 
-error bars, and background points are as in Fig.~\ref{fig:age_alpha} for the 
-corresponding Galactic region. The solid black line connects the black squares 
-in the bottom, left-middle panel, and is replicated elsewhere for reference. } 
-\label{fig:age_alpha_regions} 
-\end{figure*}
-
-In Fig.~\ref{fig:age_alpha_regions}, we extend the comparison of our base-line, 
-inside-out model and the observations of~\citet{Feuillet2019} to other 
-Galactic regions. We visualize the data there in the same manner as for 
-previous figures in this section. While the inside-out model shows the best 
-agreement with the observed result in the solar annulus, there are some mild 
-discrepancies for stars farther from the sun.~\citet{Feuillet2019} report ages 
-for~$\alpha$-rich stars that are younger at large~$R_\text{gal}$ and high 
-$\left|z\right|$, though in most cases only by~$\sim$20\%. Our model does not 
-capture this effect. To illustrate this, we connect the black squares in the 
-panel corresponding to the solar annulus with a black line, and then reproduce 
-this line in all panels for reference. If the observational result is correct, 
-this is an interesting effect that our model doesn't reproduce in any of the 
-variants we've explored. Furthermore, we note that the model overpredicts ages 
-at large~$\left|z\right|$. As with the overpredicted [O/Fe] ratios at small 
-$R_\text{gal}$, we speculate that this may be tied to the Sagittarius dwarf 
-(see discussion in~\S~\ref{sec:obs_comp:ofe_dists}). By using a hydrodynamical 
-simulation of a 
-galaxy which exhibited more pericentric passages of a massive satellite, more 
-young stars may be kinematically heated to high~$\left|z\right|_\text{max}$ 
-orbits. This is another instance where running our models with a different 
-hydrodynamical simulation's star particles may be an enlightening comparison. 
-\par 
-We note that the intrinsic scatter in the age-[O/Fe] relation is predicted to 
-grow with increasing~$R_\text{gal}$; this can be seen in the error bars on the 
-black squares as well as the coloured points. We identify two sources of this 
-dependence; the bulk of the scatter, at least at [O/Fe]~$\gtrsim$~+0.05, arises 
-from the variability in the SN Ia rates as described in~\S 
-\ref{sec:obs_comp:gradient}. Having demonstrated that the SN Ia rate is most 
-variable at large~$R_\text{gal}$, the in-situ populations in the outskirts of 
-the Galactic disc formed from an ISM whose gas-phase [O/Fe] ratio varied with 
-a higher amplitude. Since the observational signature of this variability is 
-scatter in the observed age-[O/Fe] relation, our model predicts the most 
-intrinsic scatter in Galactic regions where that variability has the highest 
-amplitude. Second, the analytic models of~\citet{Weinberg2017} suggest that 
-as the e-folding timescale for star formation~$\tau_\text{sfh}$ increases, the 
-model-predicted [O/Fe] of the youngest stars increases with a weak dependence. 
-With a range of e-folding timescales in our model, this implies a distribution 
-of [O/Fe] at age = 0 with nonzero width without considering the migration of 
-nucleosynthetic yields. This can be seen in the post-processing model 
-predicted age-[O/Fe] relation in Fig.~\ref{fig:age_alpha}. In this pathway, 
-scatter is induced by mixing populations that follow age-[O/Fe] relations of 
-slightly different normalizations which are nearly flat intrinsically, 
-producing a noticeably wide age distribution near solar [O/Fe]. 
-\par 
-Although the iron-peak is the only class of elements with a delayed 
-nucleosynthetic source that we consider in the present paper, we expect similar 
-results for other delayed sources with regard to the variability in enrichment 
-rates and scatter in age-[X/Y] relations. The details of SN Ia nucleosynthesis 
-did not matter in our interpretations in this section; it is based purely on 
-the characteristic delay-times of the source and how they compare to the 
-timescales of stellar migration. Our models should then find similar 
-predictions with, for example, s-process (slow neutron capture) elements like 
-carbon, nitrogen, strontium, yttrium, and zirconium produced in asymptotic 
-giant branch stars. In fact, using hydrodynamical simulations from the Auriga 
-project~\citep{Grand2017},~\citet{vandeVoort2020} find that the intrinsic 
-scatter in r-process (rapid neutron capture) abundances increases for models 
-with longer characteristic delay times. Although the first observations of a 
-binary neutron star merger (GW170817) exhibited an optical counterpart which 
-was consistent with being powered by the radioactive decay of r-process 
-elements~\citep{Abbott2017, Coulter2017, Drout2017, Pian2017}, it remains 
-unclear the extent to which neutron star mergers contribute to r-process 
-nucleosynthesis in the universe~\citep{Cote2019, Mishenina2019, Siegel2019, 
-vandeVoort2020, Vincenzo2021b}. Although it's likely unfeasible at present due 
-to the requirement for high precision abundance measurements of intrinsically 
-rare elements in many stars, with future observational capabilities, the 
-application of our results as well as~\citet{vandeVoort2020} suggests that the 
-intrinsic scatter in r-process abundances may provide constraints on the 
-characteristic delay times of such nucleosynthetic events.
-
-\subsection{The Age-Metallicity Relation} 
-\label{sec:obs_comp:amr}
-
-% fig 15 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.35]{amr_static_o.pdf} 
-\caption{The age-[O/H] relation predicted by our constant SFH model for 
-$R_\text{gal}$~= 7 - 9 kpc (left) and 11 - 13 kpc (right). Each panel plots 
-only the~$\left|z\right|\leq$~0.5 kpc population. The colored points in the 
-background and the black squares with error bars are as in Fig. 
-\ref{fig:age_alpha}, but with our binned, model prediction quantified in 
-bins of~$\Delta$[O/H] = 0.05. } 
-\label{fig:age_oh_static} 
-\end{figure}
-
-Although the age-metallicity relation (AMR) is usually formulated in terms of 
-[Fe/H], it is also interesting to quantify the age-[O/H] relation, because it 
-is not affected by SN Ia enrichment. The extent to which they differ indicates 
-the extent to which the delayed timescale and impact of migration on SN Ia 
-enrichment is important in shaping the age-[Fe/H] relation. In Fig. 
-\ref{fig:age_oh_static}, we present the age-[O/H] relation predicted by our 
-constant SFH model for the~$\left|z\right|\leq$~0.5 kpc population at 
-$R_\text{gal}$ = 7 - 9 and 11 - 13 kpc. The black squares with error bars 
-denote the mass-weighted median age as in~\S~\ref{sec:obs_comp:age_alpha}, and 
-we again plot the individual stellar populations in the background for 
-reference, colour-coded according to their Galactocentric radius of birth. We 
-omit the~\citet{Feuillet2019} measurements from this figure, because the 
-constant SFH model is of purely theoretical interest, removing the effects of 
-a time-varying SFH while including the effects of stellar migration. 
-\par 
-The intrinsic scatter in the observed AMR has previously been interpreted as 
-evidence for radial mixing~\citep{Edvardsson1993, Sellwood2002}. In the 
-solar neighbourhood,~\citet{Feuillet2018} demonstrate that the most metal-rich 
-stars tend to be significantly older than solar metallicity stars. Using the 
-\citet{Weinberg2017} analytic models of one-zone chemical evolution, they argue 
-that this is the result of old stars born at small~$R_\text{gal}$ where the 
-equilibrium abundance is high. Only the old stars are able to migrate to 
-the solar neighbourhood due to the time required for such a change in their 
-orbital radius. 
-\par 
-The results of our constant SFH model illustrated in Fig. 
-\ref{fig:age_oh_static} extend our understanding of this effect. In both 
-regions plotted, the youngest stars form with a composition inherited from the 
-local ISM, which in this model, is reflective of the late-time equilibrium 
-abundance. At a given age, only stars born in a well-defined region of the 
-Galaxy will have had adequate time to migrate to a given present-day radius. 
-Since a range of~$R_\text{gal}$ maps directly to a range of metallicity once 
-the ISM is arbitrarily close to the equilibrium abundance in our model, this 
-necessitates a maximum width of the [O/H] distribution at fixed age. With 
-increasing age, the [O/H] distribution then gets wider because any given 
-present-day radius samples stars formed at a wider range of~$R_\text{gal}$. 
-In Fig.~\ref{fig:age_oh_static}, we indeed see this effect, with the 
-colour-coding of the background points making it clear that stellar migration 
-is the culprit. In the outer Galaxy, migration has a particularly interesting 
-effect in that it only adds old stars above the equilibrium metallicity; in 
-the~$R_\text{gal}$ = 11 - 13 kpc region, our model as a consequence predicts 
-an AMR where the population-averaged trend where [O/H] is nearly monotonically 
-increasing with age. This is entirely backwards from what is expected from 
-one-zone models of GCE~\citep[e.g.][]{Andrews2017, Weinberg2017, Johnson2020}.
-
-% fig 16 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.45]{amr_solar_annulus.pdf} 
-\caption{The age-[O/H] (top) and age-[Fe/H] (bottom) relations for the solar 
-annulus (i.e.~$R_\text{gal}$ = 7 - 9 kpc,~$\left|z\right|\leq$~0.5 kpc) as 
-predicted by our inside-out SFH. Red triangles, black squares, error bars, and 
-background points are as in Fig.~\ref{fig:age_alpha}, but with our model 
-predicted quantified in bins of~$\Delta$[O/H] =~$\Delta$[Fe/H] = 0.05. For 
-comparison, we plot the~\citet{Feuillet2018} measurements in a dark red line, 
-omitting the associated uncertainties for visual clarity. } 
-\label{fig:amr_solar_annulus} 
-\end{figure}
-
-We continue our assessment of the model-predicted AMR by illustrating in Fig. 
-\ref{fig:amr_solar_annulus} the age-[O/H] (top) and age-[Fe/H] (bottom) 
-relations predicted for the solar annulus (i.e.~$R_\text{gal}$~= 7 - 9 kpc and 
-$\left|z\right|\leq$~0.5 kpc). The red triangles, black squares, coloured 
-points, and error bars are as in previous figures in~\S 
-\ref{sec:obs_comp:age_alpha}. For reference, we add the solid dark red line, 
-which denotes the AMR measured by~\citet{Feuillet2018}. Although our model 
-shows decent agreement with the~\citet{Feuillet2019} measurements in the solar 
-annulus,~\citet{Feuillet2018} report ages for solar metallicity stars which 
-are considerably younger ($\sim$1 - 2 Gyr as opposed to~$\sim$3 - 4 Gyr). 
-The~\citet{Feuillet2018} data would suggest our inside-out model requires an 
-enhancement in the recent SFR to increase the frequency of young, solar 
-metallicity stars. Although our late-burst and outer-burst models include 
-such effects, motivated by recent observations suggesting this exact 
-evolutionary history~\citep{Mor2019, Isern2019}, the differences between the 
-\citet{Feuillet2018} and~\citet{Feuillet2019} measurements are interesting in 
-and of themselves.
-
-% fig 17 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.35]{amr_insideout_vs_lateburst_fe.pdf} 
-\caption{The age-[Fe/H] relation predicted by our inside-out (top) and 
-late-burst (bottom) SFHs for~$R_\text{gal}$ = 5 - 7 kpc (left), 7 - 9 kpc 
-(left middle), 9 - 11 kpc (right middle), and 11 - 13 kpc (right). Each panel 
-shows only the~$\left|z\right|\leq$~0.5 kpc population. Red triangles, black 
-squares, error bars, and coloured points are as in Fig.~\ref{fig:age_alpha} for 
-the corresponding Galactic region, but with our model prediction quantified in 
-bins of~$\Delta$[Fe/H] = 0.05. } 
-\label{fig:amr_insideout_vs_lateburst_fe} 
-\end{figure*}
-
-Motivated by this, we compare the predictions of the inside-out and late-burst 
-SFH models to the~\citet{Feuillet2019} age-[Fe/H] relation in Fig. 
-\ref{fig:amr_insideout_vs_lateburst_fe}. We retain the same plotting scheme 
-used throughout this section and~\S~\ref{sec:obs_comp:age_alpha}, illustrating 
-the inside-out model in the top row and the late-burst model in the bottom row. 
-Each column corresponds to a specific range in~$R_\text{gal}$, denoted at the 
-top of the figure. Beyond the solar annulus, we note that our inside-out model 
-has a number of short-comings in comparison to the~\citet{Feuillet2019} 
-measurements. At~$R_\text{gal}$ = 5 - 7 kpc, it overpredicts the characteristic 
-ages of [Fe/H]~$\approx$~-0.3 - 0 stars. At~$R_\text{gal}$ = 9 - 11 and 11 - 13 
-kpc, it mildly overpredicts ages at most abundances, and fails to reproduce the 
-trend seen in the observed sample. The same can be said about the 
-$R_\text{gal}$~=5 - 7 kpc region, and although the overall agreement is 
-generally good there, one could reasonably argue this for the solar annulus as 
-well. 
-\par 
-The late-burst model improves upon these shortcomings of the inside-out model 
-considerably. At~$R_\text{gal}$ = 5 - 7 kpc, the overpredicted ages at solar 
-and mildly sub-solar [Fe/H] is no longer present; this is also true at 
-$R_\text{gal}$~= 9 - 11 and 11 - 13 kpc. Furthermore, the trend is much better 
-reproduced at all radii in the late-burst than the inside-out model. The only 
-different between the late-burst and inside-out model being the recent 
-enhancement in the SFR, this is what drives the differences in model 
-predictions. To fuel the starburst as we have parameterized it,~\texttt{VICE} 
-calculates that there must be substantial gas accretion (see the infall rate 
-$\dot{\Sigma}_\text{in}$ as a function of radius and time in Fig. 
-\ref{fig:evol}). In our models, we assume accretion to always be of zero 
-metallicity gas. As a result, the model predicts dilution of the ISM Fe 
-abundance during the starburst; this can be seen by the trend of the coloured 
-points in Fig.~\ref{fig:amr_insideout_vs_lateburst_fe} to lower [Fe/H] at ages 
-of~$\sim$2 - 3 Gyr. At this time, the star formation rate is elevated by 
-construction. The net effect is to increase the frequency of~$\sim$2 - 3 Gyr 
-old stars with near- and sub-solar abundances globally, which lowers the 
-characteristic ages of stars at these metallicities relative to the inside-out 
-model. Using the~\citet{Feuillet2019} measurements as the observational 
-benchmark, we favor the late-burst model here. 
-\par 
-Although there appears to be a vertical offset between the observed result and 
-the model prediction at~$R_\text{gal}$ = 9 - 11 and 11 - 13 kpc, this is still 
-an improvement upon the inside-out model. It's possible that this points to a 
-need for higher yields of Fe than we've adopted here, though it's unclear if 
-this would negatively affect the agreement at~$R_\text{gal}$~= 5 - 7 and 7 - 9 
-kpc. It's possible that our parameterization of the mass-loading factor~$\eta$ 
-scales too strongly with~$R_\text{gal}$ in the outer Galaxy (see discussion in 
-\S~\ref{sec:methods:yields}). Alternatively, outflows in nature may be more 
-efficient at removing some elements from the ISM than others; this could impact 
-the overall normalization of the AMR at different radii. Our models in the 
-present paper assume that outflows always proceed exactly at the metallicity of 
-the ISM, but some authors argue that outflows can have a different metallicity 
-- usually a higher one - due to containing in some part the metal-rich 
-supernova ejecta that was added directly to the outflow by the explosions 
-(observationally:~\citealp*{Chisholm2018}; in simulations: 
-\citealp{Christensen2018}). 
-\par 
-We also note that the late-burst model predicts particularly young 
-characteristic ages for the most metal-rich bins at~$R_\text{gal}$ = 5 - 7 kpc. 
-This is purely a consequence of our choice to use the mass-weighted median as 
-the population-averaged age measurement at fixed abundance. In this case, our 
-model is simply reporting the 50th percentile of an age-distribution 
-which is noticeably bimodal; as a result, whether or not the characteristic 
-ages we report there are <1 Gyr or in better agreement with the 
-\citet{Feuillet2019} measurements strongly depends on how we've parameterized 
-the recent starburst as a function of both time and radius. Here we've made the 
-simplest assumption of letting have the same time-dependence at all radii, 
-which was not necessarily the case. 
-\par 
-Although we demonstrate here that the late-burst model describes the age-[Fe/H] 
-relation reported by~\citet{Feuillet2019} better than the inside-out model, we 
-found the exact opposite with regard to the age-[$\alpha$/Fe] relation with 
-the same obesrvational sample in~\S~\ref{sec:obs_comp:age_alpha}. It's unlikely 
-this discrepancy can be mitigated using any model which exhibits a recent 
-starburst as parameterized here; as we demonstrated in~\S 
-\ref{sec:obs_comp:age_alpha}, such models predict a global increase in 
-[$\alpha$/Fe] due to the perturbed ratio of CCSN and SN Ia rates 
-\citep{Johnson2020}, a feature which simply isn't seen in the 
-\citet{Feuillet2019} measurements. It's possible that the Milky Way experienced 
-dilution with no ensuing starburst - this would be the case if the majority of 
-the accreted gas was warm, neutral and ionized gas which simply hasn't yet been 
-made available for star formation. Such a scenario would exhibit some of the 
-predictions of the late-burst model, but without the increase in [O/Fe] at late 
-times, potentially allowing it to simultaneously explain the age-[$\alpha$/Fe] 
-relation and AMR as they are observed. However, these models would be at odds 
-with the findings of~\citet{Mor2019} and~\citet{Isern2019}. 
-\par 
-We remark that we find similar results for the age-[O/H] relation; furthermore, 
-as in~\S~\ref{sec:obs_comp:age_alpha} for the age-[$\alpha$/Fe] relation, we 
-also find for the age-[Fe/H] and age-[O/H] relations that our models tend to 
-overpredict ages with increasing~$\left|z\right|$. Lastly, we caution future 
-studies against basing the likelihood of a chemical evolution model on data 
-for the solar annulus alone. In Fig.~\ref{fig:amr_solar_annulus}, we 
-noted that there was decent agreement between the inside-out SFH model and 
-the~\citet{Feuillet2019} measurements of the age-[O/H] and age-[Fe/H] 
-relations in the solar annulus, but upon extending the comparison to other 
-Galactic regions in Fig.~\ref{fig:amr_insideout_vs_lateburst_fe}, a number of 
-shortcomings revealed themselves. Although to some extent this is made possible 
-only recently with observational capabilities now allowing statistical 
-measurements of these correlations for stars at greater distances from the sun, 
-had we stopped there, we would have missed this interesting and peculiar 
-result.
-
-\section{Discussion \& Conclusions} 
-\label{sec:conclusions} 
-In this paper, we have modeled the Milky Way as a series of concentric annuli 
-with a~$\Delta R_\text{gal}$~= 100 pc width, describing each annulus as a 
-conventional one-zone chemical evolution model and allowing the exchange of 
-stellar populations between zones to include the impact of stellar migration in 
-the model Galaxy. Though there have been a handful of studies which employ a 
-similar methodology~\citep{Schoenrich2009, Nidever2015, Sharma2020}, ours and 
-the~\citet{Minchev2013, Minchev2014, Minchev2017} model are the only ones which 
-make use of a hydrodynamical simulation to describe radial mixing, for which we 
-make use of the~\texttt{h277} zoom-in simulation~\citep{Christensen2012, 
-Zolotov2012, Loebman2012, Loebman2014, Brooks2014}. This yields a model for 
-migration which does not have any free parameters (see discussion in~\S 
-\ref{sec:methods:h277}). 
-\par 
-Our model predicts masses and abundances for simple stellar populations, a 
-given number of which form at each timestep. Each stellar 
-population is then assigned a star particle from~\texttt{h277} which was born 
-at a similar radius and time to act as an~\textit{analog}. The stellar 
-population in our model then assumes the change in radius~$\Delta R_\text{gal}$ 
-of the analog at face value, and is assumed to reside at the same present day 
-height above/below the disc midplane~$\left|z\right|$. We then construct four 
-models describing the time-dependence with which stellar populations move to 
-their present-day radii, taking one in which radius changes with a 
-$\sqrt{\text{age}}$-dependence in the fiducial model based on~\citet[][see 
-Fig.~\ref{fig:migration_schema} and discussion in~\S 
-\ref{sec:methods:migration}]{Frankel2018, Frankel2020}. 
-\par 
-We assume SN yields and a SN Ia delay-time distribution based on 
-a combination of theoretical and empirical constraints. The main free 
-parameters are the star formation law parameterizing the SFE timescale 
-$\tau_\star$ (see discussion in~\S~\ref{sec:methods:sfe}), the mass-loading 
-factor~$\eta(R_\text{gal})$~describing the strength of outflows (assumed to be 
-time-independent; see discussion in~\S~\ref{sec:methods:yields}), and the SFH. 
-The first we choose from the observed~$\dot{\Sigma}_\star - \Sigma_\text{g}$ 
-relation in local spirals~\citep{Bigiel2010, Leroy2013, Krumholz2018}. The 
-second is chosen to reproduce the metallicity gradient as observed 
-\citep{Daflon2009, Frinchaboy2013, Hayden2014, Weinberg2019}. Our fiducial 
-model then has an inside-out SFH with e-folding timescales calibrated to the 
-\citet{Sanchez2020} data (see discussion in~\S~\ref{sec:methods:sfhs}). 
-Motivated by the results of~\citet{Mor2019} and~\citet{Isern2019} suggesting 
-such an evolutionary history, we construct models which exhibit a recent burst 
-in star formation on top of the base-line model, as well as a constant SFH 
-model of purely theoretical interest. 
-\par 
-We find that when stellar migration proceeds in a manner in which a star's 
-orbital radius changes continuously with time, the SN Ia rate as a function of 
-both radius and time exhibits significant variability. The characteristic delay 
-time of a single SN Ia event is~$\sim$1 Gyr~\citep{Maoz2012, Maoz2017}, and 
-stars are migrating a significant distance in the radial direction on similar 
-timescales in our models. The result is a SN Ia rate which, at fixed radius, 
-tends to follow that which is expected from the SFH when averaged with time, 
-but whose instantaneous value may be considerably larger or smaller. Our model 
-predicts the amplitude of this variability to grow with increasing radius due 
-to sampling noise and the inverse dependence of the stellar surface density on 
-$R_\text{gal}$. We demonstrate that this is a mechamism with which truly young, 
-super-solar [$\alpha$/Fe] stars can form. When the SN Ia rate increases or 
-decreases, the Fe abundance in the ISM increases or 
-decreases accordingly; this in turn affects the gas-phase [$\alpha$/Fe] ratio, 
-and the stars which form at these times inherit these compositions. Of the 
-young stars, those with the highest [$\alpha$/Fe] form at large~$R_\text{gal}$ 
-($\gtrsim$~12 kpc) due to the radial dependence of the amplitude; a subsample 
-of these stars can then migrate to the solar annulus. 
-\par 
-To our knowledge, this mechanism lends the first theoretical explanation of 
-truly young $\alpha$-rich stars in the solar neighbourhood, revealed recently 
-by the observations of the APOGEE survey~\citep{Martig2016, Feuillet2018, 
-Feuillet2019, SilvaAguirre2018}.~\citet{SilvaAguirre2018} find that 
-these stars have kinematics consistent with the rest of the high-$\alpha$ 
-population, and postulate based on this that these stars are the consequence 
-of stellar mergers or mass transfer events, making truly old stars simply 
-appear younger. In a sample of 51 young~$\alpha$-rich red giants, 
-\citet{Hekker2019} demonstrate using cabon-to-nitrogen ratios that a portion of 
-these stars are indeed old, but that these effects cannot account for the 
-entire population. We argue based on our results that the truly young ones 
-formed at large~$R_\text{gal}$~at a time when the ISM was intrinsically 
-$\alpha$-rich due simply to a deficit in SN Ia events caused by a net loss of 
-white dwarf progenitors to stellar migration. We remark that our model would 
-sugest that these stars have super-solar [$\alpha$/Fe] not because they are 
-$\alpha$-rich, but rather that they are Fe-poor. 
-\par 
-We find that our model adequately reproduces the variations in MDFs with 
-Galactocentric radius in the disc~\citep{Hayden2015}. Although there is a 
-potential for improved agreement in the~$R_\text{gal}$~= 3 - 5 kpc bin, the 
-model nonetheless performs well. With increasing~$\left|z\right|$, the 
-prediction breaks down somewhat. Where the observational data show a 
-convergence of the MDFs at all radii to a skew-positive distribution with 
-mode([O/H])~$\approx$~mode([Fe/H])~$\approx$~-0.5, our model predicts the mode 
-abundance in the inner Galaxy to decrease slightly, though not to the same 
-extent as in the observations, while the distributions at larger~$R_\text{gal}$ 
-are less affected (see Figs.~\ref{fig:mdf_3panel_fe} and~\ref{fig:mdf_3panel_o} 
-and discussion in~\S~\ref{sec:obs_comp:mdfs}). While the model accounts for a 
-portion of these effects, it cannot explain the entire~$z$-dependence of the 
-MDF shape. 
-\par 
-We demonstrate the dependence of the relative frequency of high-$\alpha$ and 
-low-$\alpha$ sequence stars on Galactic position (see, e.g., Fig. 4 of 
-\citealp{Hayden2015}) is at least in part a consequence of stellar migration. 
-In our fiducial inside-out SFH model, low [Fe/H], high [$\alpha$/Fe] stars 
-are the dominant population at small~$R_\text{gal}$~and high~$\left|z\right|$; 
-conversely, low [$\alpha$/Fe] stars are most common at large~$R_\text{gal}$ 
-and low~$\left|z\right|$. We clarify that this is not an explanation for the 
-\textit{origin} of the two sequences - only the spatial dependence thereof. 
-In fact, our model is unable to account for the presence of the infamous 
-[$\alpha$/Fe] dichotomy in any of the variants we've explored. While it is able 
-to reproduce the broad nature of the [O/Fe] distributions at fixed [Fe/H] and 
-may show a convincing two-peaked profile in a specific Galactic region, it 
-fails to do so for the entire Galaxy at all metallicities; the principle 
-failure is an overpredicted frequency of intermediate [$\alpha$/Fe] stars. This 
-is in contrast to the findings of~\citet{Sharma2020}, who claim to reproduce 
-the bimodality in a model assuming an inside-out SFH with stellar migration. 
-However, they do not demonstrate that the enrichment history of their model 
-follows self-consistently from their assumed SFH. We therefore argue that 
-an inside-out SFH is not conducive to forming the abundance distributions 
-observed in the Milky Way. Though we don't investigate such evolutionary 
-pathways in the present paper, our models fail in such a manner that suggests 
-the agreement can best be improved by the three-phase SFH of the two-infall 
-model~\citep{Chiappini1997, Chiappini2001, Romano2010, Grisoni2017, 
-Noguchi2018, Palla2020, Spitoni2016, Spitoni2018, Spitoni2019a, Spitoni2020, 
-Spitoni2021}. We reserve an investigation into more sophisticated forms of the 
-Galactic SFH for future work. 
-\par 
-We find that the age-[O/Fe] relation as reported by~\citet{Feuillet2019} is 
-well-characterized by our inside-out SFH. In the case of our recent 
-starburst models motivated by~\citet{Mor2019} and~\citet{Isern2019}, the 
-elevation of the SFR necessitates an increase in [$\alpha$/Fe] for young 
-stars owing to the increased rate of CCSNe before the onset of SN Ia associated 
-with the starburst~\citep{Johnson2020}, introducing a trend which simply isn't 
-seen in the observations. This suggests that recent studies finding an 
-elevation in the 
-Galactic SFR~$\sim$2 Gyr ago are at odds with chemical evolution models, which 
-based on the monotonic nature of the observed AMR would put constraints on the 
-amount of variability out to lookback times of~$\sim$8 Gyr. Lastly, we find 
-that our model predicts the intrinsic scatter in the age-[$\alpha$/Fe] relation 
-to increase with~$R_\text{gal}$; this traces back to the variability in the SN 
-Ia rates having a higher amplitude in the outer Galaxy, which produces an 
-in-situ population with a larger dynamic range in [O/Fe]. 
-\par 
-We find that the AMR (both age-[O/H] and age-[Fe/H]) in the solar annulus as 
-measured by~\citet{Feuillet2019} is well-described by our inside-out SFH. 
-However, when this comparison is extended to other Galactic regions, the 
-inside-out model overpredicts ages in multiple regions and fails to reproduce 
-the population-averaged trend throughout the disc. We demonstrate that our 
-late-burst model can account for these discrepancies, suggesting that the 
-observed AMR favors a model with a recent enhancement in the Galactic SFR. 
-Somewhat confusingly, the impact of the late-burst model is such that it is 
-convincingly rejected by the age-[O/Fe] relation but convincingly favored by 
-the age-[O/H] and age-[Fe/H] relations. 
-\par 
-We thus conclude that no single model in the present paper can explain all of 
-the observables of interest here. This suggests that 
-conventional assumptions about the evolution of the Milky Way, such as an 
-inside-out SFH with stellar migration, are not sufficiently accurate to 
-understand the enrichment history of the Milky Way in detail. This is an 
-indication that at present there is more astrophysical information in already 
-collected observations than the most recent GCE models can explain. It's likely 
-our models are missing at least one key component with a significant impact on 
-the predicted abundances. 
-\par 
-Lastly, we remark on the low number of multi-zone chemical evolution models in 
-the literature, some with and some without migration. In this paper, we present 
-only a handful of models whose predictions can be calculated with a combined 
-CPU-time comparable to a single working day. These models make straight-forward 
-predictions which can easily be compared to publicly-available observed data. 
-Though they are extremely useful in many respects, these medium resolution, 
-medium computational expense techniques can test assumptions about the 
-evolutionary history of the Milky Way with more control over the parameters and 
-much less computational expense than the higher overhead hydrodynamical 
-simulations; our models here constitute an example of a combination of the two. 
-\par 
-\texttt{VICE} is publicly available and open-source;\footnote{
-	Install (PyPI): \url{https://pypi.org/project/vice} \\ 
-	Documentation: \url{https://vice-astro.readthedocs.io} \\ 
-	Source Code: \url{https://github.com/giganano/VICE.git} 
-} it can be installed in a~\texttt{Unix} terminal via~\texttt{pip install vice}. 
-\texttt{Python} code which runs the simulations presented in this paper is 
-included as supplementary material in the~\texttt{GitHub} repository; our 
-models can be ran directly from a terminal without modifying the source code, 
-and are capable of predicting abundances for~$\sim$2 million stellar 
-populations in~$\sim$2.5 CPU-hours running on a single core on personal 
-computers.
 
@@
 \label{sec:acknowledgements}
-We acknowledge valuable discussion with, in no particular order, Emily 
-Griffith, Jennifer Johnson, Todd Thompson, Jiayi Sun, Amy Sardone, Adam Leroy, 
-Grace Olivier, the Ohio State Astronomy Gas, Galaxies, and Feedback group, and 
-various participants of the SDSS Gotham 2020 virtual collaboration meeting and 
-the virtual 236th meeting of the American Astronomical Society. This work was 
-supported in part by National Science Foundation grant AST-1909841. D.H.W. 
-is grateful for the hospitality of the Institute for Advanced Study and the 
-support of the W.M. Keck Foundation. 
+
+% fig 18 
+\begin{figure*} 
+\includegraphics[scale = 0.32]{age_oh_comparison.pdf} 
+\caption{The same as Fig.~\ref{fig:amr_insideout_vs_lateburst_fe}, but for 
+\oh, and with an additional comparison to the outer-burst model in the 
+bottom row.} 
+\label{fig:age_oh_comparison} 
+\end{figure*}
+
+We acknowledge valuable discussion with Jennifer Johnson, Adam Leroy, Grace 
+Olivier, Amy Sardone, Jiayi Sun, Todd Thompson, and other members of the Ohio 
+State Astronomy Gas, Galaxies, and Feedback group, as well as various 
+participants of the SDSS Gotham 2020 virtual collaboration meeting and the 
+virtual 236th meeting of the American Astronomical Society. 
+We thank Diane Feuillet for providing the results of~\citet{Feuillet2019} in 
+digital form. 
+This work was supported in part by National Science Foundation grant 
+AST-1909841. 
+D.H.W. is grateful for the hospitality of the Institute for Advanced Study and 
+the support of the W.M. Keck Foundation and the Hendricks Foundation. 
+F.V. acknowledges the support of a Fellowship from the Center for Cosmology and 
+AstroParticle Physics at the Ohio State University. 
 \par 
@@
 
-\section{Data Availability} 
-\label{sec:data_availability} 
-\texttt{VICE} is open-source software, and the code which computes abundances 
-for our models is publicly available as well. In the GitHub repository, we 
-provide detailed instructions on how to run our models and variations thereof. 
-All observational data appearing in this paper is publicly available, and is 
-also included with the source code for our models and figures.
-
-\begin{appendices}
-
-\section{Normalizing the Star Formation History} 
-\label{sec:normalize_sfh} 
-In this appendix, we derive a prescription for calculating the prefactors of an 
-adopted star formation history (SFH) for each annulus in our models. As 
-mentioned in~\S~\ref{sec:methods:sfhs}, this procedure requires a unitless 
-description of the time-dependence of the SFH in each annulus, denoted 
-$f(t|R_\text{gal})$, and a unitless description denoting the radial dependence 
-of the stellar surface density~$g(R_\text{gal})$. By additionally selecting a 
-total stellar mass of the present day model Galaxy, the solution to the 
-detailed form of the star formation history 
-$\dot{\Sigma}_\star(t, R_\text{gal})$ is unique. With this approach, we assume 
-that stellar migration does not significantly impact the form of 
-$g(R_\text{gal})$, an assumption we demonstrate to be accurate in~\S 
-\ref{sec:methods:surface_density_gradient}. 
-\par 
-The surface density of star formation with units of mass per area per time can 
-be expressed in terms of~$f(t|R_\text{gal})$ as: 
-\begin{equation} 
-\dot{\Sigma}_\star(t, R_\text{gal}) = \dot{\Sigma}_\star(t = 0, R_\text{gal}) 
-f(t|R_\text{gal}) 
-\label{eq:sfh_terms_of_f} 
-\end{equation} 
-and the present-day radial surface density gradient with units of mass per area 
-as: 
-\begin{equation} 
-\Sigma_\star(R_\text{gal}) = \Sigma_\star(R_\text{gal} = 0) g(R_\text{gal}) 
-\label{eq:sigma_terms_of_g}  
-\end{equation} 
-The integral of~$\dot{\Sigma}_\star$ with time should yield the surface density 
-gradient at a given radius~$R_\text{gal}$, up to a prefactor accounting for the 
-return of stellar envelopes to the interstellar medium (ISM): 
-\begin{subequations}\begin{align} 
-\Sigma_\star(R_\text{gal}) &= (1 - r)\int_0^T \dot{\Sigma}_\star(t, 
-R_\text{gal}) dt 
-\\ 
-&= (1 - r) \dot{\Sigma}_\star(t = 0, R_\text{gal})\int_0^T f(t|R_\text{gal}) dt 
-\\ 
-\dot{\Sigma}_\star(t = 0, R_\text{gal}) &= \Sigma_\star(R_\text{gal}) 
-\left[(1 - r) \int_0^T f(t|R_\text{gal})dt\right]^{-1} 
-\\ 
-&= \Sigma_\star(R_\text{gal} = 0)g(R_\text{gal}) \left[(1 - r) \int_0^T 
-f(t|R_\text{gal})\right]^{-1} 
-\label{eq:intermediate_1} 
-\end{align}\end{subequations} 
-where~$(1 - r) \approx 0.6$~is an adequate approximation for a 
-\citetalias{Kroupa2001} IMF~\citep[][see discussion in their~\S 
-2.2]{Weinberg2017}. This expression relates the two unkowns introduced by 
-equations~\refp{eq:sfh_terms_of_f} and~\refp{eq:sigma_terms_of_g}. We continue 
-by asserting that the integral of the stellar surface density over the area of 
-the disc should be equal to the present-day stellar mass of the Milky Way: 
-\begin{subequations}\begin{align} 
-M_\star^\text{MW} &= \int_0^R \Sigma_\star(R_\text{gal}) 2\pi R_\text{gal} 
-dR_\text{gal} 
-\\ 
-&= \Sigma_\star(R_\text{gal} = 0) \int_0^R g(R_\text{gal}) 2\pi R_\text{gal} 
-dR_\text{gal} 
-\\ 
-\Sigma_\star(R_\text{gal} = 0) &= M_\star^\text{MW} \left[\int_0^R 
-g(R_\text{gal}) 2\pi R_\text{gal}dR_\text{gal}\right]^{-1} 
-\label{eq:intermediate_2} 
-\end{align}\end{subequations} 
-\par 
-Now plugging equation~\refp{eq:intermediate_2} into equation 
-\refp{eq:intermediate_1}, and then that into equation~\refp{eq:sfh_terms_of_f} 
-yields the desired result: 
-\begin{subequations}\begin{align} 
-&\dot{\Sigma}_\star(t, R_\text{gal}) = Af(t|R_\text{gal})g(R_\text{gal}) 
-\\ 
-&A = M_\star^\text{MW}\left[(1 - r) \int_0^R g(R_\text{gal})2\pi R_\text{gal} 
-dR_\text{gal} \int_0^T f(t|R_\text{gal})dt\right]^{-1} 
-\end{align}\end{subequations} 
-where the upper limits should be the maximum radius of star formation and the 
-end time of the simulation (15.5 kpc and 12.2 Gyr in this paper). This result 
-makes intuitive sense, simply stating that the required normalization of 
-$f(t|R_\text{gal})$~is specified by two things: the total stellar mass of the 
-Galaxy and how steep the stellar density falls with increasing radius. As long 
-as the assumption that stellar migration does not significantly alter the form 
-of~$g(R_\text{gal})$~is not violated, this procedure can be used to calculate 
-prefactors for future models of disc galaxies.
-
-\end{appendices}
-
-\bibliographystyle{mnras} 
-\bibliography{draft1}
-
-\label{lastpage} 
 \end{document}

### 2021-08-04 chemev/MWbimodality/paper/draft2/age_oh.tex
migration paper referee response

\documentclass[draft2.tex]{subfiles}
\begin{document}

\section{The Age-\oh~Relation} 
\label{sec:age_oh_relation}

Fig.~\ref{fig:age_oh_comparison} presents a comparison of the age-\oh~ 
relation predicted by our inside-out, late-burst, and outer-burst SFHs to 
the~\citet{Feuillet2019} measurements in the same Galactic regions as in 
Fig.~\ref{fig:amr_insideout_vs_lateburst_fe}. 
The age-\oh~relation shows a smoother population-averaged trend than the 
age-\feh~relation (see Fig.~\ref{fig:amr_insideout_vs_lateburst_fe}). 
Affected by the variability in Type Ia supernova rates discussed in 
\S~\ref{sec:obs_comp:gradient}, the gas-phase Fe abundance at fixed radius 
fluctuates as a function of simulation time, resulting in higher intrinsic 
scatter in the age-\feh~relation than in age-\oh. 
We can make similar arguments about the age-\oh~relation as we do for 
age-\feh~in~\S~\ref{sec:obs_comp:amr}: the late-burst model better reproduces 
the C-shaped nature of the AMR throughout the disc, particularly beyond the 
solar neighbourhood. 
The bin-by-bin comparison is also somewhat more convincing in age-\oh~than in 
age-\feh. 
The late-burst model improves the agreement in all annuli with the exception of 
the solar annulus, where it potentially worsens the agreement slightly, but 
both models adequately reproduce the data there anyway. 
% \par 
In comparing the late-burst model to the outer-burst model, it is clear the 
outer-burst model mitigates the very young ages of the most metal-rich stars 
at~\rgal~= 5 - 7 kpc seen in the late-burst model; this is a consequence of 
the starburst producing a bimodal age distribution at these abundances (see 
discussion in~\S~\ref{sec:obs_comp:amr}). 
% No model illustrated here reproduces the data perfectly, but we have made 
% simple assumptions regarding the enhancement in the SFR. 
% Although these assumptions are nonetheless motivated by the observations of 
% \citet{Mor2019} and~\citet{Isern2019}, the detailed form of the AMR in these 
% models is sensitive to both the strength and time-dependence of the recent SFH 
% as a function of both Galactocentric radius and time. 
% Ascertaining a best-fit set of parameters to describe the burst would require 
% running many variations of our models, perhaps within a more sophisticated 
% mathematical framework.

\end{document}

### 2021-08-04 chemev/MWbimodality/paper/draft2/comparison_observations.tex
migration paper referee response

\documentclass[draft2.tex]{subfiles} 
\begin{document}

\section{Comparison to Observations} 
\label{sec:obs_comp}

% fig 7 
\begin{figure*} 
\centering 
\includegraphics[scale = 0.28]{ofe_feh_densitymap.pdf} 
\caption{[O/Fe]-[Fe/H] diagrams for 15 Galactic regions spanning five bins in 
$R_\text{gal}$ and three in~$\left|z\right|$. Each region has its own panel, 
with radial bins shown in columns denoted at the top, and with bins in 
$\left|z\right|$ shown in rows denoted in text in the middle column. For each 
region, we plot~$N$~= 10,000 points sampled from our simulated stellar 
populations predicted by our fiducial model, where the probability of 
sampling is proportional to the present-day mass of each stellar population. 
In all panels, points are colour-coded according to the Galactocentric radius 
of birth of the stellar population. For reference, we plot in a solid black 
line in all panels the gas-phase [O/Fe]-[Fe/H] track predicted by the same 
SFH in the~$R_\text{gal}$ = 8 kpc annulus, but with the post-processing 
migration model; this curve is the same in all panels. } 
\label{fig:ofe_feh_diagram} 
\end{figure*}

We begin the comparison of our model predictions to observational data with the 
distribution of stellar populations in the [O/Fe]-[Fe/H] plane. We separate 
stars into bins based on their present-day Galactic regions defined by five 
bins in~$R_\text{gal}$ (3 - 5, 5 - 7, 7 - 9, 9 - 11, and 11 - 13 kpc) and three 
bins in~$\left|z\right|$ (0 - 0.5, 0.5 - 1, and 1 - 2 kpc). Within each of the 
resulting 15 regions, we sample 10,000 stars at random from our baseline 
inside-out SFH model. Since stars in~\texttt{VICE} are stand-ins for entire 
stellar populations, we let the probability of sampling one of them be 
proportional to its present day mass. We plot the results of this procedure in 
Fig.~\ref{fig:ofe_feh_diagram}, colour-coding each stellar population by its 
birth radius; for visual reference, we also plot the gas-phase track which 
resulted from the~$R_\text{gal}$ = 8 kpc annulus with the post-processing 
migration model in a black solid line in all panels. 
\par 
In Fig.~\ref{fig:ofe_feh_diagram}, we note that high-$\alpha$~sequence stars 
are predicted to be the dominant population at small~$R_\text{gal}$ and high 
$\left|z\right|$; conversely, the low-$\alpha$~population dominates the 
statistics at large~$R_\text{gal}$~and low~$\left|z\right|$. This is consistent 
with the observational results of~\citet{Hayden2015}, who present a density map 
in the [$\alpha$/M]-[M/H] plane for the same Galactic regions (see their Fig. 
4).\footnote{
	In~\citet{Hayden2015}, [M/H] represents an overall scaling of elements with 
	solar mixture, and [$\alpha$/M] represents a scaling of~$\alpha$-elements 
	with respect to others. To a good approximation they are proxies for 
	[Fe/H] and [O/Fe], respectively, and we will treat them as such in this 
	paper. 
} 
Furthermore, the locus of the low-$\alpha$ sequence shifts from super-solar 
[Fe/H] to sub-solar [Fe/H] with increasing~$R_\text{gal}$, a shift which is 
expected given the abundance gradient that we have built into our models (see 
discussion in~\S~\ref{sec:methods:outflows}). 
The colour-coding of the points 
shows that the width of the low-$\alpha$~sequence arises out of 
stellar migration: low-$\alpha$ stars with high [Fe/H] formed in the inner 
Galaxy, and those with low [Fe/H] formed in the outer Galaxy. 
The low-$\alpha$ locus thus represents a superposition of populations achieved 
by radial migration rather than an evolutionary sequence, the interpretation 
proposed by, e.g.,~\citet{Schoenrich2009a} and~\citet{Nidever2014}. 
\par 
In Fig.~\ref{fig:ofe_feh_diagram} one can clearly see the imprint of 
evolutionary tracks from different radii, appearing in the same present-day 
$R_\text{gal}$ bin because of radial mixing. 
Though this is to some extent a consequence of the discretization of the 
Galaxy disc in our model, it also arises out of correlated fluctuations in the 
SN Ia rate (see discussion in~\S~\ref{sec:obs_comp:gradient}). 
Observational scatter would wash out the appearance of distinct tracks, and 
intrinsic scatter might blur them if our chemical evolution model was less 
idealized. 
Our model reproduces several of the qualitative trends found by 
\citet{Hayden2015}, but the distribution is less obviously bimodal. 
We quantify this point in~\S~\ref{sec:obs_comp:ofe_dists} below. 
If we remake Fig.~\ref{fig:ofe_feh_diagram} for any of our other SFHs, or for 
our alternative migration or star formation efficiency prescriptions, the 
appearance is qualitatively similar. There are significant quantitative 
differences in some cases, which we discuss in subsequent subsections.

\subsection{Abundance Gradients} 
\label{sec:obs_comp:gradient}

The left panel of Fig.~\ref{fig:tracks} shows gas phase [O/Fe]-[Fe/H] 
evolutionary tracks at several radii assuming the inside-out SFH, using either 
our post-processing (dotted) or diffusion (solid) migration prescriptions 
(see~\S~\ref{sec:methods:migration} and Fig.~\ref{fig:migration_schema}). 
For the post-processing model the tracks are smooth and simply follow the 
predictions of one-zone GCE models with the parameters appropriate to each 
radius --- with post-processing, radial migration has no impact on the gas-phase 
evolution. 
However, some of the tracks in the diffusion model are notably 
different, especially at early times and large radii. 
These differences arise because radial migration can transport stars 
significantly over the timescale of SN Ia enrichment, as discussed in~\S 
\ref{sec:methods:h277}.
\par 
To demonstrate this point, the right panel of Fig.~\ref{fig:tracks} plots a 
proxy of the SN Ia rate\footnote{
	From our~\vice~outputs, the total time derivative of the Fe mass in a given 
	annulus can be obtained by its change across a single timestep. By then 
	subtracting the CCSN contribution (known exactly given our adopted yield 
	and the SFR), approximately correcting for recycling, and adding back that 
	which was lost to star formation and outflows, we obtain a simple estimate 
	of Fe production by SNe Ia. 
} as a function of time for the same 0.1 kpc rings plotted in the left panel. 
At large radii the sources for the diffusion model exhibit large fluctuations 
relative to the smooth predictions of the underlying one-zone models, as 
migration boosts or depletes the predicted number of SN Ia progenitors. 
The deficits or excesses in SN Ia rate in turn drive upward or downward 
deviations in [O/Fe] relative to the smooth model tracks in the left panel. 
As an extreme example, in the 15 kpc annulus the SN Ia rate is nearly zero for 
the first~$\sim$3 Gyr, and its resulting [O/Fe] track is nearly flat over this 
interval, even though the smooth model track has dropped from [O/Fe] = 0.45 to 
[O/Fe]~$\approx$ 0.2. 
Although we illustrate the SN Ia rates for only a handful of rings, we have 
found that the variations between nearby rings are highly correlated in our 
models, suggesting that regions of the Galaxy move coherently in 
[O/Fe]-[Fe/H] space; this lends further insight into the streak-like appearance 
of some sub-populations in Fig.~\ref{fig:ofe_feh_diagram}.

% fig 8
\begin{figure*} 
\centering 
\includegraphics[scale = 0.42]{tracks.pdf} 
\caption{\textbf{Left}: Gas phase evolutionary tracks in the [O/Fe]-[Fe/H] 
plane for our inside-out SFH with either post-processing (dotted lines) or 
diffusion (solid lines) migration models. We plot tracks for seven of our 
$\Delta\rgal$ = 100 pc rings, 
colour-coded according to their Galactocentric radius and denoted by the 
legend in the lower-left. We mark simulation times of 2, 4, 6, 8, 10, and 13.2 
Gyr in X's for the diffusion model and points for the post-processing model. 
\textbf{Right}: As a function of simulation time, a proxy for the SN Ia rate 
using the total time-derivative of the Fe mass in a given annulus, calculated 
by subtracting the contribution from recycling and CCSN enrichment and adding 
back that lost to star formation and outflows. We show these rates for the 
same rings as in the left-hand panel, multiplying them by various prefactors 
to improve clarity. } 
\label{fig:tracks} 
\end{figure*}

% fig 9 
\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{metallicity_gradient.pdf} 
\caption{Radial abundance gradients in [O/H] (top, red), [Fe/H] (top, blue), 
and [O/Fe] (bottom) for our four SFHs with diffusion migration - constant (far 
left), inside-out (left-middle), late-burst (right-middle), and outer-burst 
(far right). We plot the gas-phase abundance at the present day as a function 
of Galactocentric radius in solid lines. Points denote the median of the stellar 
MDF of the 100-pc width ring at a given radius, with shaded regions marking 
the 16th and 84th percentiles thereof. Black lines in the top panels denote our 
target [$\alpha$/H] gradient of mode([$\alpha$/H]) = +0.3 at~$R_\text{gal}$~= 
4 kpc with a slope of -0.08 kpc$^{-1}$. } 
\label{fig:metallicity_gradient} 
\end{figure*}

Because we are analyzing a single hydrodynamic simulation, we cannot say 
whether the systematic depression of the SN Ia rate at large radii and early 
times is a general expectation or a consequence of the specific dynamical 
history of this galaxy. 
However, greater fluctuations at large~\rgal~and small~$t$ are a natural 
consequence of the low SFR. These fluctuations can have a significant impact 
on [O/Fe]-[Fe/H] evolution even if their sign varies from galaxy to galaxy. 
The fact that >10\% of events are seen at >10 kpc from their host galaxies in 
the ASAS-SN bright SN catalog~\citep{Holoien2019} adds qualitative 
observational support to the argument that SN Ia progenitors may often form at 
significantly different radii than where their explosions are observed. 
We will show below that these SN Ia rate fluctuations lead to the formation of 
$\alpha$-enhanced intermediate age populations that do not arise in our 
post-processing radial migration model (see Fig.~\ref{fig:age_alpha}). 
\par 
Fig.~\ref{fig:metallicity_gradient} plots the radial gradients of gas phase 
and stellar abundances, [O/H], [Fe/H], and [O/Fe], for our four SFH models. 
For constant SFR, the gas phase abundances closely track the target gradient 
that we used to set our~$\eta(\rgal)$ profile (see equation~\ref{eq:eta_rgal}). 
For a declining SFR the equilibrium abundance is higher than that assumed for 
equation~\refp{eq:eta_rgal}~\citep[see][]{Weinberg2017}, and in the inside-out 
and outer-burst models the gas phase abundances rise above the target gradient 
at small~\rgal~where the decline is fastest. 
In the late-burst model the inner Galaxy abundances are further boosted by 
enhanced late-time star formation, and a similar effect is seen at~\rgal~= 6 
kpc in the outer-burst model. 
In accretion-induced starbursts, re-enrichment can briefly produce 
super-equilibrium abundances in the gas-phase, which then decay back to the 
equilibrium abundance as the SFR declines~\citep{Johnson2020}. 
\par 
The stellar metallicity gradients are shallower than in the gas phase, and 
they are similar in the four models. 
The 16th-84th percentile range at each radius is large, typically 0.3-0.5 
dex, and typically larger in [Fe/H] than [O/H]. 
The mode of the stellar metallicity distribution is a noisy quantity in our 
0.1-kpc rings, so points in Fig.~\ref{fig:metallicity_gradient} show the 
median of the distributions. 
The trends for the mode are slightly steeper, as expected given the change in 
shape of the metallicity distribution functions (see~\S 
\ref{sec:obs_comp:mdfs}), and closer to the target gradient shown by the black 
solid line. We do not include observational data in this figure, but the target 
gradient itself is observationally motivated, so Fig. 
\ref{fig:metallicity_gradient} implies that our models, by design, give a 
reasonable match to Milky Way abundance gradients. 
\par 
Median [O/Fe] values are close to solar at nearly all radii, rising at the 
smallest~\rgal~and in some models at the largest~\rgal. However, the spread in 
[O/Fe] is large at all radii, and typical values depend on~\absz~and [Fe/H] as 
shown in Fig.~\ref{fig:ofe_feh_diagram}. 
We present a comparison to observations in~\S~\ref{sec:obs_comp:ofe_dists} 
below. 
The larger values of [O/Fe] beyond~\rgal~= 15.5 kpc are expected, since this is 
the radius at which we shut off star formation. In our models, all stellar 
populations at these radii migrated there, so they tend to be old and therefore 
$\alpha$-enhanced. 
The idea that outer disc populations are dominated by migration was proposed 
by~\citet{Roskar2008b} based on simulation predictions. 
\citet{RadburnSmith2012} present observational evidence for this prediction in 
the observations of the NGC 7793 disc. 
Although we are not modeling the bulge in this paper, our model predicts the 
disc stars in these regions to have higher [O/Fe] than at larger~\rgal, in 
qualitative agreement with observations (see discussion in, e.g., 
\citealp{Duong2019, Griffith2021}).

\subsection{Metallicity Distribution Functions} 
\label{sec:obs_comp:mdfs}

Metallicity distribution functions (MDFs) and their variations with Galactic 
region are a core prediction of GCE models. 
We have computed distributions of [Fe/H] and [O/H] using abundances from the 
16th data release~\citep[DR16;][]{Ahumada2020, Joensson2020} of APOGEE 
\citep{Majewski2017}. 
Abundances are determined by the APOGEE Stellar Parameters and Chemical 
Abundances Pipeline (ASPCAP;~\citealp{Holtzman2015, GarciaPerez2016}). 
We restrict our sample to stars with effective temperatures of 4000 K 
$\leq T_\text{eff} \leq$~4600 K, surface gravities of 1.0~$\leq \log g \leq$ 
2.5, and signal-to-noise ratios of at least 100. 
These cuts ensure that our sample consists of stars on the upper red giant 
branch, luminous enough to cover all regions of the disc, while excluding red 
clump stars to avoid possible abundance offsets between these stars and stars 
on the giant branch. 
Our observational results are similar to those shown by~\citet{Hayden2015}, 
but we use a larger data set, more recent APOGEE observations, and [O/H] and 
[Fe/H] rather than [$\alpha$/H] and [M/H]. 
\par 
The left and right panels of Fig.~\ref{fig:mdf_3panel_fe} show [Fe/H] 
distributions from our fiducial inside-out model and the APOGEE data, 
respectively, in bins of~\rgal~and~\absz. 
The observed midplane distributions (\absz~$\leq$~0.5 kpc) show the striking 
phenomenon first noted by~\citet{Hayden2015}: a shift from a skew-negative form 
in the inner Galaxy to a skew-positive form in the outer Galaxy, with a roughly 
symmetric [Fe/H] distribution at the solar circle. 
The simulation reproduces this behaviour, confirming that realistic radial 
migration can explain the radial dependence of the MDF shape as conjectured by 
\citet{Hayden2015} and illustrated in a more idealized simulation by 
\citet{Loebman2016}. 
\par 
In detail, the MDFs are not as smooth at large~\rgal~as in the observations; 
they are not as skewed in the inner and outer disc either. 
Dots in the lower left panel mark the target metallicities implied by our 
$\eta(\rgal)$ prescription in equation~\refp{eq:eta_rgal}. 
The modes of the stellar MDFs track these targets quite closely, except at 
\rgal~= 13 - 15 kpc, where the migrated population is so large compared to the 
in-situ population that it reshapes the peak of the MDF as well as the tails. 
The model also predicts a continuing increase of the mode metallicity down to 
\rgal~= 3 - 5 kpc, while the observed mode is the same at 3 - 5 kpc and 5 - 7 
kpc. 
We do not view this as a serious discrepancy, as it could be reduced by a
moderate adjustment of the~$\eta(\rgal)$ recipe so that the metallicity 
gradient in these regions is flat. 
We have computed such a comparison case and find that it does indeed reproduce 
this observational result, though it still underpredicts the skewness at 
small~\rgal. 
Alternatively, the flattening of the observed gradient could be a consequence 
of more aggressive quenching of star formation than assumed in our models. 
The surface density of star formation~$\dot{\Sigma}_\star$ in the Milky Way 
is known to reach a maximum at~\rgal~$\approx$ 4 kpc and decline by a factor 
of a few at smaller radii (see Fig. 1 of~\citealp{Peek2009} and Fig. 2 
of~\citealp{Fraternali2012} and data therein). 
Early quenching could cutoff the MDF at high [O/H] and [Fe/H] if it happens 
before the ISM reaches equilibrium abundance. 
Visual inspection of Fig.~\ref{fig:tracks} suggests that this process should 
occur around~$T \approx$ 6 - 8 Gyr if the MDF is to peak at 
[Fe/H]~$\approx$~+0.2 - 0.3.

% fig 10 
\begin{figure} 
\centering 
\includegraphics[scale = 0.34]{mdf_3panel_fe.pdf} 
\caption{Metallicity distribution functions (MDFs) in [Fe/H] predicted by our 
fiducial, inside-out model (left) and as observed in APOGEE DR16 (right), for 
stars and simulated stellar populations with present-day~$\left|z\right|$~= 0 - 
0.5 kpc (bottom), 0.5 - 1 kpc (middle), and 1 - 2 kpc (top). MDFs are shown in 
bins of Galactocentric radius: 3 - 5 kpc (black), 5 - 7 kpc (red), 7 - 9 kpc 
(yellow), 9 - 11 kpc (green), 11 - 13 kpc (blue), and 13 - 15 kpc (purple). 
The points near the top of the bottom panels denote what the mode abundance 
would be if it followed out target gradient of [Fe/H] = +0.3 at~$R_\text{gal}$ 
= 4 kpc with a slope of -0.08 kpc$^{-1}$ exactly, assuming the inner radius of 
each bin (i.e. there is no point plotted for 15 kpc). All distributions are 
smoothed with a box-car width of [Fe/H]~$\pm$~0.1 for clarity. } 
\label{fig:mdf_3panel_fe} 
\end{figure}

% fig 11 
\begin{figure} 
\centering 
\includegraphics[scale = 0.34]{mdf_3panel_o.pdf} 
\caption{The same as Fig.~\ref{fig:mdf_3panel_fe}, but for [O/H]. } 
\label{fig:mdf_3panel_o} 
\end{figure}

Going up from the midplane, the observed MDFs for the four inner annuli 
(\rgal~< 11 kpc) shift to lower average metallicity, and they converge in 
location and in shape, being roughly symmetric at~\absz~= 0.5 - 1 kpc and 
mildly skew-positive at~\absz~= 1 - 2 kpc. 
Qualitatively, the simulation reproduces this shift of mean metallicity, change 
of shape, and convergence of distributions at different~\rgal, although the 
model does not account for the entirety of the effect. 
We consider this a significant success of this simulation-based approach 
because our GCE model is constructed and tuned in~\rgal~alone, so trends with 
\absz~follow from the combinations of age-metallicity trends, age-velocity 
trends arising from ``upside-down'' disc formation and dynamical heating, and 
correlations between radial migration and vertical energy. 
\citet{Freudenburg2017} showed that chemical evolution in a vertically settling 
gas disc could explain the MDF trend with~\absz~seen by APOGEE in the inner 
disc, and here we see similar behaviour in a more fully ab initio model. 
\citet{Bird2020} showed that the dynamics of the~\hsim~simulation leads to good 
agreement with the observed age-velocity relation, and here we show that 
this success extends qualitatively to the vertical trends of chemical 
abundances. 
\par 
Quantitatively, there are significant differences between the predicted and 
observed distributions above the midplane. 
The model MDFs from~\absz~= 0.5 - 1 kpc are narrower and more skewed than the 
observed MDFs, with higher median [Fe/H]. 
At~\absz~= 1 - 2 kpc, the predicted MDFs are not as strikingly converged as the 
observed MDFs. 
In both the data and the model, the high-\absz~MDFs for the 11 - 13 and 13 - 15 
kpc annuli remain closer to their midplane counterparts. 
The model [O/Fe]-[Fe/H] distributions in the outer Galaxy appear to show the 
imprint of a few large migration episodes (see Fig.~\ref{fig:ofe_feh_diagram}). 
The smoothness of the observed MDFs at these radii and their similarity across 
\absz~suggests a more vigorous stirring. 
\par 
Fig.~\ref{fig:mdf_3panel_o} plots distributions of [O/H] instead of [Fe/H]. 
The appearance is quite similar to Fig.~\ref{fig:mdf_3panel_fe}, which is 
unsurprising but non-trivial given the different timescales of CCSN and SN Ia 
enrichment. 
The agreement and disagreement between the model and data are similar, though 
the discrepancy for~\absz~= 0.5 - 1 kpc is somewhat clearer in [O/H]. 
The model's outer Galaxy MDFs are less irregular in [O/H] than in [Fe/H], an 
indication that some of the structure in the [Fe/H] distributions is caused by 
the large fluctuations in the SN Ia rate as seen in Fig.~\ref{fig:tracks}. 
We have confirmed this conjecture by computing [Fe/H] MDFs for the 
post-processing radial migration prescription, finding that they are indeed 
more smooth at~\rgal~= 11 kpc. 
\par 
The MDF predictions for our other SFH scenarios - constant SFR, late-burst, and 
outer-burst - are different in detail, but they show the same qualitative 
trends as those in Figs.~\ref{fig:mdf_3panel_fe} and~\ref{fig:mdf_3panel_o}. 
Our findings on the radial and vertical trends of the MDF are also similar 
to those of~\citet{Loebman2016}, who use a galaxy simulation evolved from 
rotating gas in a dark matter halo rather than cosmological initial conditions. 
The qualitative similarity of our results across different models implies that 
the radial and vertical trends are a generic effect of radial migration, 
upside-down disc formation, and dynamical heating in a galaxy with realistic 
abundance gradients and time evolution.

\subsection{[O/Fe] distributions in Bins of [Fe/H]} 
\label{sec:obs_comp:ofe_dists}

% fig 12 
\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{ofe_mdfs.pdf} 
\caption{Predicted distributions in [O/Fe] in 15 Galactic regions and in two 
bins in [Fe/H]. Columns correspond to bins in~$R_\text{gal}$, denoted at the 
top of each column. Rows correspond to bins in~$\left|z\right|$, denoted in 
text in the left-hand column. Distributions are color-coded according to the 
[Fe/H] the sample is drawn from, denoted by the legend in the upper right 
panel. Solid lines represent that predicted by our inside-out SFH in 
$\Delta$[O/Fe] = 0.04 bins, while dashed lines correspond to the fits to the 
APOGEE DR16 data presented in~\citet{Vincenzo2021a}, which quantify the 
intrinsic distributions accounting for observational uncertainties and the 
APOGEE selection function. } 
\label{fig:ofe_mdfs_insideout} 
\end{figure*}

Fig.~\ref{fig:ofe_mdfs_insideout} compares our predicted [O/Fe] distributions 
in Galactic zones to those recently published by 
\citet{Vincenzo2021a}.\footnote{
	\citet{Vincenzo2021a} present [Mg/Fe] distributions in their figures, but 
	they have quantified the [O/Fe] as well, and we use the latter here. 
}
As in our~\S~\ref{sec:obs_comp:mdfs}, they use APOGEE DR16 with similar cuts on 
effective temperature, surface gravity, and signal-to-noise (see their~\S~2). 
They correct for observational scatter as well as age-dependent and (more 
importantly)~\absz-dependent selection in APOGEE to infer the intrinsic 
distribution of [O/Fe] in bins of [Fe/H] that would be found for an unbiased 
sample of long-lived disc stars. 
At a given~\rgal~and [Fe/H],~\citet{Vincenzo2021a} fit a model comprised of two 
Gaussians in [O/Fe], one each for the high-$\alpha$ and low-$\alpha$ 
populations.
The~\absz-dependence of the distribution follows from the empirical scale 
heights of these two populations, taken from~\citet{Bovy2016}. 
Dotted curves in Fig.~\ref{fig:ofe_mdfs_insideout} show these models integrated 
over the corresponding ranges in~\absz.

Solid histograms in Fig.~\ref{fig:ofe_mdfs_insideout} show distributions in 
0.4-dex bins of [O/Fe] for our fiducial inside-out model. 
For clarity we have chosen to focus our comparison on two bins of [Fe/H], one 
just above solar metallicity (0.0~$\leq$ [Fe/H]~$\leq$ 0.2) and one at 
sub-solar metallicity (-0.4~$\leq$ [Fe/H]~$\leq$ -0.2) where the bimodality of 
[O/Fe] is most pronounced. Results for our other models are qualitatively 
similar, and these two [Fe/H] bins illustrate the range of model successes and 
failure. 
\par 
Beginning with the [Fe/H] = 0 - 0.2 bin, we see that the model roughly 
reproduces the observed width of the [O/Fe] distribution. 
In the midplane (\absz~$\leq$ 0.5 kpc) zones it predicts the correct 
skew-positive shape, though the peak of the observed distribution is sharper 
than the model prediction. However, the model histograms shift towards higher 
[O/Fe] with increasing~\absz~while the peak of the observationally inferred 
distributions stays fixed, a discrepancy that is most obvious in the~\rgal~= 
3 - 5 kpc and 5 - 7 kpc bins. The constancy of the observed peak is partly 
a consequence of the~\citet{Vincenzo2021a} fitting procedure, which assumes 
that the location of the high-$\alpha$ and low-$\alpha$ Gaussians stay 
constant at a given~\rgal~and [Fe/H] and only their relative amplitudes change 
with~\absz. We have gone back to the raw data histograms fit by 
\citet{Vincenzo2021a}, and while they do allow some increase in model [O/Fe] 
with~\absz, they do not allow a shift as large as that predicted by our model. 
At~\absz~= 1 - 2 and~\rgal~= 3 - 5 and 5 - 7 kpc, the number of stars 
contributing to the fit is 31 and 17 respectively, so while the shape of the 
distribution is not well constrained, the centroid is robustly determined. 
\par 
This discrepancy could reflect differences in the dynamical heating history 
of the~\hsim~simulation and the Milky Way. 
With its most recent major merger occurring at~$z \approx$ 3, this galaxy was 
previously selected for investigation for its quiescent merger history 
\citep[e.g.][]{Zolotov2012}. N-body models for the tidal disruption of the 
Sagittarius dwarf galaxy suggest repeated pericentric passages at 1 - 2 Gyr 
intervals~\citep{Law2010}, which could trigger episodes of infall and star 
formation~\citep[e.g.][]{RuizLara2020}. 
These pericentric passages might also heat low-$\alpha$ disc populations to 
higher~\absz, an effect absent in~\hsim. 
Alternatively, we have investigated the impact of changing our~$\eta(\rgal)$ 
prescription to become constant within~\rgal~= 5 kpc, as discussed previously 
in~\S~\ref{sec:obs_comp:mdfs} in the context of the [Fe/H] gradient. 
This change also dampens the predicted trend of [O/Fe] with~\absz~by bringing 
the inner Galaxy's [O/Fe]-[Fe/H] tracks closer together (see 
Figs.~\ref{fig:ofe_feh_diagram} and~\ref{fig:tracks}). 
We find that this change can account for some but not all of the discrepancy, 
shifting the peak of the distribution down by~$\sim$0.05 dex in the upper left 
panel of Fig.~\ref{fig:ofe_mdfs_insideout}. 
\par 
Turning to the -0.4~$\leq$ [Fe/H]~$\leq$ -0.2 bin, the model shows partial but 
by no means complete success. 
It does reproduce the breadth of the [O/Fe] distribution at this intermediate 
metallicity, and in nearly all~\rgal-\absz~zones it predicts skewness of the 
correct sign. 
At~\rgal~= 3 - 5 kpc, the model predicts mode([O/Fe])~$\approx$ 0.3, while 
the observed mode is at [O/Fe]~$\approx$ 0.22. 
This discrepancy is affected by our choice of CCSN yields, which produces an 
[O/Fe] plateau at +0.45. 
While this value is consistent with some observational data (e.g. the 
\citealp*{Ramirez2013} data set modeled by~\citealp{Andrews2017}), APOGEE 
measurements place the plateau at [O/Fe]~$\approx$ +0.3, so it is not 
surprising that our model overpredicts [O/Fe] at low metallicity. 
Unfortunately, uncertainties in the observed abundance scales and the 
theoretical CCSN elemental yields remain an obstacle to sharp GCE model tests. 
\par 
The most significant discrepancy with data is for~\rgal~= 7 - 9 kpc, where the 
observations show a clearly bimodal [O/Fe] distribution in all three~\absz~ 
ranges but the model predicts bimodality only near the midplane. 
This bimodality is also evident in the raw data histograms prior to model 
fitting and correction for selection effects (see Figs. 10 and 11 of 
\citealp{Vincenzo2021a}). 
The idea that radial migration could give rise to an [$\alpha$/Fe] dichotomy 
was proposed by~\citet{Schoenrich2009a}, who noted that the evolutionary tracks 
at any given~\rgal~would produce most stars at low [O/Fe] and that radial 
mixing of these populations would produce a low-$\alpha$ ``sequence'' that is 
a superposition of these evolutionary endpoints. 
\citet{Nidever2014} explored this superposition scenario in the context of 
APOGEE observations, and~\citet{Sharma2020} have recently implemented a 
detailed parameterized scenario matched to APOGEE. 
Although the superposition effect clearly operates in our model, as shown in 
Fig.~\ref{fig:ofe_feh_diagram}, the model produces too many stars at 
intermediate [O/Fe], so there is no clear minimum between the high-$\alpha$ 
and low-$\alpha$ peaks. 
As argued by~\citet{Vincenzo2021a}, the generic problem is that one-zone models 
with smooth evolutionary histories always produce most stars near the low 
[$\alpha$/Fe] endpoints and a much smaller peak at the high-$\alpha$ 
plateau, so one cannot superpose such models in a way that produces strong 
bimodality. 
The~\citet{Sharma2020} model seems like a possible counter-example, but they 
adopt parameterized evolutionary tracks and do not demonstrate that these can 
be drawn from a self-consistent chemical evolution model. 
\par 
The simplest way to produce stronger [$\alpha$/Fe] bimodality in our models 
would be to adopt a two-phase star formation model like that envisioned in 
two-infall scenarios of chemical evolution~\citep[e.g.][]{Chiappini1997, 
Chiappini2001, Romano2010, Grisoni2017, Noguchi2018, Palla2020, Spitoni2016, 
Spitoni2018, Spitoni2019a, Spitoni2020, Spitoni2021}. 
These scenarios turn down the SFR while the ISM abundances pass through the 
intermediate [$\alpha$/Fe] regime. 
Other scenarios such as large early starbursts~\citep{Clarke2019} or reverse 
[Fe/H] evolution with late-time outflows~\citep{Weinberg2017} could also 
enhance bimodality, but the late starbursts considered here are insufficient 
on their own. 
We will explore these alternative scenarios for the origin of bimodality in 
future work.

\subsection{The Age-[$\alpha$/Fe] Relation} 
\label{sec:obs_comp:age_alpha} 
In this section, we assess the predicted age-[O/Fe] relations of our models, 
using the results of~\citet{Feuillet2019} as the observational benchmark. 
Their stellar age measurements are based on isochrone matching, 
using APOGEE DR14 stars for which parallax measurements are available 
from Gaia~\citep{Abolfathi2014, GaiaDR2}. 
With their spatial and quality cuts, the final sample consisted of 77,562 
stars. 
In bins of [O/Fe], they assume a Gaussian distribution of log age, fitting the 
mean (or equivalently, the median) and standard deviation to the stars in that 
bin. 
The choice of a Gaussian distribution is driven by simplicity, enabling 
estimates of mean and spread for data with significant age errors, but because 
our model predicts non-Gaussian log age distributions at fixed [O/Fe], the 
comparison to data is not free of nuance. 
We base most of our model comparisons below on the mass-weighted median age, 
simply denoting the 50th percentile of the mass-weighted age distribution of 
some subsample. 
\par

% fig 13 
\begin{figure*} 
\centering 
\includegraphics[scale = 0.34]{age_ofe_migration_comparison.pdf} 
\includegraphics[scale = 0.34]{age_ofe_sfh_comparison.pdf} 
\caption{
\textbf{Left}: A comparison of the predicted age-[O/Fe] relation for the solar 
neighbourhood ($R_\text{gal}$ = 7 - 9 kpc and~$\left|z\right|$ = 0 - 0.5 kpc) 
between the post-processing (upper left), diffusion (upper right), sudden 
(lower left), and linear (lower right) migration models, assuming our 
inside-out SFH. 
\textbf{Right}: The same as the left-hand panels, instead comparing the impact 
of our constant (upper left), inside-out (upper right), late-burst (lower left), 
and outer-burst (lower right) SFHs, assuming diffusion migration. In all panels, 
red triangles and error bars denote the observed median age and dispersion 
thereof in bins of [O/Fe] as reported by~\citet{Feuillet2019}; here we include 
only their bins containing at least 15 stars. Black squares denote the 
mass-weighted median age in 0.02-dex bins in [O/Fe] predicted by our models, 
with error bars denoting the 16th and 84th percentiles of the mass-weighted 
age distribution in those bins. Points in the background denote each individual 
stellar population from the model with a final position in the solar 
neighbourhood, colour-coded according to their Galactocentric radius of birth. 
}
\label{fig:age_alpha} 
\end{figure*}

In the left-hand set of panels of Fig.~\ref{fig:age_alpha}, we compare the 
age-[O/Fe] relation in the solar neighbourhood ($R_\text{gal}$~= 7 - 9 kpc and 
$\left|z\right|\leq$~0.5 kpc)\footnote{
	In order to avoid confusion, we distinguish between solar ``annulus'' and 
	solar ``neighbourhood'' by defining the solar neighbourhood to be the 
	solar annulus population at~\absz~$\leq$~0.5 kpc. This definition should 
	approximate a sample within a spherical radius of~$\sim$0.5 kpc around the 
	Sun, similar to typical observational definitions. 
} predicted by our four migration models to the 
\citet{Feuillet2019} measurements, shown in red triangles. 
We mark the mass-weighted median age in bins of [O/Fe] in each model with black 
squares, and plot for reference in the background each individual stellar 
population in the solar neighbourhood, colour-coded according to its 
Galactocentric radius of birth. 
\par 
The median age-[O/Fe] trend is similar for all four migration prescriptions, 
and the model prediction is in reasonable agreement with the APOGEE 
measurements. 
From the colour-coding in the post-processing model, one can see that the 
predicted relation is insensitive to the chemical evolution parameters across 
the range represented in our Galactic radial zones, differing only in the 
precise value of [O/Fe] reached at late times. 
Nonetheless, these differences are large enough that radial mixing causes a 
large spread in age at low values of [O/Fe], where the median trend itself 
becomes shallow. 
Nearly all high [O/Fe] stars are old. 
The spread is similar, but not identical, among the four migration 
prescriptions, and it is in reasonable agreement with the observationally 
inferred spread. 
This agreement is a significant success of the migration predicted by the
\hsim~simulation in concert with our GCE model. 
% The observed [O/Fe] distribution extends to values below -0.05 that are not 
% present in our model. This difference could reflect missing stochasticity in 
% our model, or slightly incorrect yield or SFH choices, or observational errors 
% in some [O/Fe] measurements. 
\par 
Although their median trends and characteristic spreads are similar, the 
diffusion and linear migration models show a marked diffrence from the 
post-processing and sudden models, predicting populations of young 
($\lesssim$ 4 Gyr) and intermediate age (4 - 7 Gyr)~$\alpha$-enhanced stars 
([O/Fe]~$\approx$ +0.1 - 0.2) in the solar neighbourhood, which formed at large 
\rgal~with [O/Fe] values well above the main trend for their age. 
They arise from the large fluctuations in the SN Ia rate at large~\rgal~shown 
in Fig.~\ref{fig:tracks} and discussed in~\S~\ref{sec:obs_comp:gradient}, 
which occur when stellar populations migrate to different radii before 
producing most of their SNe Ia. 
When the SN Ia Fe production rate fluctuates downward, [O/Fe] fluctuates 
upward in the ISM, and the stars that form from it inherit such a composition. 
These stars then migrate to the solar annulus. 
The presence of young and intermediate-age~$\alpha$-enhanced stars in APOGEE 
has been demonstrated using ages based on carbon-to-nitrogen ratios 
\citep{Martig2016} calibrated against the asteroseismic ages of the APOKASC 
catalog~\citep{Pinsonneault2014}, and with the asteroseismic ages directly 
\citep{SilvaAguirre2018}. 
\par 
\citet{SilvaAguirre2018} demonstrate that these stars have kinematics similar 
to the rest of the high-$\alpha$ population, and they suggest that they are 
in fact old stars ``rejuvenated'' by mergers or mass transfer events. 
In a sample of 51 young,~$\alpha$-rich red giants,~\citet{Hekker2019} 
demonstrate that a portion of these stars have carbon-to-nitrogen ratios 
consistent with mass transfer events, but that others do not, indicating that 
they are either truly young stars or the result of mergers on the main 
sequence. 
\citet{Weinberg2017} and~\citet{Johnson2020} proposed that young~$\alpha$-rich 
stars could arise in bursts of star formation that enhance the rate of CCSN 
enrichment. The explanation suggested here is in some sense the opposite: the 
stars are not so much~$\alpha$-rich as they are Fe-poor because of the 
deficit in SNe Ia events. 
In our diffusion model,~$\sim$0.2\% of solar neighbourhood stars with 0.1~$\leq$ 
[O/Fe]~$\leq$ 0.2 have ages below 4 Gyr, but~$\sim$13.9\% have ages below 7 Gyr. 
\par 
The right panels of Fig.~\ref{fig:age_alpha} compare the model predictions of 
our four different SFHs, all assuming the diffusion migration prescription, 
with the same plotting scheme and colour-coding as in the left panels. 
The predicted trend for the constant SFR model is similar to that of the 
inside-out model, but the agreement with data is slightly worse because with a 
constant SFR the evolutionary tracks do not extend below solar [O/Fe]. 
The starburst models, on the other hand, predict a 0.05 - 0.1 dex upward 
fluctuation in [O/Fe] at ages of 1 - 3 Gyr due to the perturbed ratio of 
core-collapse to Type Ia supernova rates~\citep{Johnson2020}. 
In the outer-burst model, stars formed at~\rgal~> 6 kpc follow this perturbed 
track while stars from the inner Galaxy follow the original track. 
These models are motivated by observational results which provide empirical 
evidence for elevated recent star formation~\citep{Mor2019, Isern2019}. 
However, in conjunction with our chemical evolution prescriptions they produce 
clear disagreement with the age-[O/Fe] distributions of~\citet{Feuillet2019} 
and~\citet{Miglio2021}. 
This disagreement could indicate that the starbursts were more limited in 
Galactic radius than we have assumed, or that some other ingredient is missing 
from our models. 
The discrepancy in these panels also implies that if young~$\alpha$-rich stars 
do arise in a starburst, then it must remain sufficiently localized that the 
resultant stellar populations remain outliers from an otherwise monotonic 
age-[$\alpha$/Fe] relation.

% fig 14 
\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{age_alpha_regions.pdf} 
\caption{The age-[O/Fe] relation in 12 Galactic regions predicted by our 
inside-out SFH. Bins in Galactocentric radius are shown in columns, and labeled 
at the top. 
Bins in the disc midplane distance~\absz~are shown in rows, noted in the 
left-hand column. Red triangles, black squares, 
error bars, and background points are as in Fig.~\ref{fig:age_alpha} for the 
corresponding Galactic region. The solid black line connects the black squares 
in the bottom, left-middle panel, and is replicated elsewhere for reference. } 
\label{fig:age_alpha_regions} 
\end{figure*}

Fig.~\ref{fig:age_alpha_regions} extends the comparison of our baseline, 
inside-out model and the observations of~\citet{Feuillet2019} to other 
Galactic regions. 
The predicted median age-[O/Fe] trend is nearly independent of location, as we 
can see by comparing the black model points in each panel to the black line, 
which shows the solar neighbourhood prediction. 
~\citet{Feuillet2019} report ages for~$\alpha$-rich stars that are younger at 
large~$R_\text{gal}$ and high $\left|z\right|$, though in most cases only by 
$\sim$20\%. 
Our model predicts a larger population of intermediate-age~$\alpha$-rich stars 
at large~\rgal, but this effect is not large enough to reproduce the observed 
trend. 
None of our model variants reproduce this trend of age-[O/Fe] offset with~\absz, 
so if the observational result is correct then it points to a missing 
ingredient in the model. 
As with the overpredicted [O/Fe] ratios at 
small~\rgal~(\S~\ref{sec:obs_comp:ofe_dists}), dynamical stirring of younger 
disc populations to higher~\absz~by the Sagittarius dwarf could play a role in 
resolving this discrepancy. 
However, Fig.~\ref{fig:age_alpha_regions} shows that the model does not have a 
reservoir of younger high-$\alpha$ stars at low-\absz~available to be stirred, 
so some additional change would likely be needed. 
Furthermore, our model predicts the 16th-84th percentile ranges of the age 
distribution at fixed [O/Fe] to increase for [O/Fe]~$\gtrsim$ +0.1 stars, at 
least in part due to the higher frequency of young and intermediate-age 
$\alpha$-rich stars. 
This increase in the intrinsic scatter of the relation is simply a consequence 
of the SN Ia rate variability having a higher amplitude at large~\rgal~(see 
discussion in~\S~\ref{sec:obs_comp:gradient}). 
\par 
In this paper, Fe is the only element that we consider with a delayed 
nucleosynthetic source. 
Nonetheless, we expect stellar migration to induce similar variability and 
scatter for other elements with delayed sources. 
Elements such as strontium (Sr) are produced by the $s$-process in AGB stars on 
a timescale intermediate between CCSN and SN Ia enrichment (see Fig. 5 of 
\citealp{Johnson2020}), and elements with a large contribution from low mass 
AGB stars could trace longer timescales. 
The DTD for $r$-process elements such as europium (Eu) is uncertain because the 
relative importance of prompt sources (e.g., collapsars) and delayed sources 
(e.g., neutron star mergers) remains poorly constrained~\citep{Cote2019, 
Mishenina2019, Siegel2019, Vincenzo2021b}. 
Using hydrodynamical simulations from the Auriga project~\citep{Grand2017}, 
\citet{vandeVoort2020} indeed find that the intrinsic scatter in $r$-process 
abundances increases for models with longer characteristic delay times. 
Future comparisons of observed trends between age and abundance ratios with the 
predictions of models like those presented here could better isolate missing 
ingredients of the models, as well as potentially improving understanding of 
the nucleosynthetic sources. 
% \par 
% {\color{red} (The next paragraph probably moving to conclusions) I added a 
% couple sentences to the prior paragraph that, with what is currently stated in 
% the conclusions, may make this redundant. -James}  
% In our models, radial mixing of populations with different evolutionary tracks 
% is the only effect that creates a spread of abundance ([Fe/H] and [O/Fe]) at 
% fixed age at a given final~\rgal. 
% The trend of evolutionary tracks with birth radius is fairly smooth, though 
% the impact of migration on SN Ia rates creates stochastic variations that 
% give rise to the young and intermediate-age~$\alpha$-rich stars in our models. 
% Incomplete mixing of the ISM in azimuth and~\absz~\citep{Krumholz2018b} is an 
% additional source of stochasticity in chemical evolution that is currently not 
% represented in our models. 
% This stochasticity will be larger for elements produced by rare events, such as 
% neutron star mergers, and there have been some recent theoretical 
% investigations of predicted scatter in~$r$-process abundances from this source 
% \citep[e.g.][]{vandeVoort2020}. 
% Observationally, the correlation of residual abundances (i.e., of deviations 
% from mean trends) may be a more sensitive probe of stochasticity and mixing 
% than variance of abundance ratios~\citep{Ting2021}. Characterizing the physics 
% of element mixing in the ISM and the stochastic effects on chemical evolution 
% is an important frontier for models and observations.

\subsection{The Age-Metallicity Relation} 
\label{sec:obs_comp:amr}

% fig 15 
\begin{figure} 
\centering 
\includegraphics[scale = 0.35]{amr_static_o.pdf} 
\caption{The age-[O/H] relation predicted by our constant SFR model for 
$R_\text{gal}$~= 7 - 9 kpc (left) and 11 - 13 kpc (right). Each panel plots 
only the~$\left|z\right|\leq$~0.5 kpc population. The colored points in the 
background and the black squares with error bars are as in Fig. 
\ref{fig:age_alpha}, but with the model prediction quantified in bins 
of~$\Delta$[O/H] = 0.05. } 
\label{fig:age_oh_static} 
\end{figure}

Although the AMR is usually formulated in terms of 
[Fe/H], it is also interesting to quantify the age-[O/H] relation because it 
is not affected by SN Ia enrichment. 
The extent to which the two AMRs differ indicates the extent to which the 
delayed timescale and impact of migration on SN Ia enrichment are important in 
shaping the age-[Fe/H] relation. 
Fig.~\ref{fig:age_oh_static} presents the age-[O/H] relation predicted by our 
constant SFR model for the~$\left|z\right|\leq$~0.5 kpc population at 
$R_\text{gal}$ = 7 - 9 and 11 - 13 kpc. 
The black squares with error bars denote the mass-weighted median age as 
in~\S~\ref{sec:obs_comp:age_alpha}, and we again plot the individual stellar 
populations in the background for reference, colour-coded according to their 
Galactocentric radius of birth. 
We omit the~\citet{Feuillet2019} measurements from this figure but present 
observational comparisons for our more empirically motivated inside-out SFH 
model below. 
The constant SFR model allows us to isolate the effects of stellar migration 
from the time-dependent SFR. 
\par 
The intrinsic scatter in the observed AMR has previously been interpreted as 
evidence for radial mixing~\citep{Edvardsson1993, Sellwood2002}. 
In the solar neighbourhood,~\citet{Feuillet2018} demonstrate that the most 
metal-rich stars tend to be significantly older than solar metallicity stars. 
Using the \citet{Weinberg2017} analytic models of one-zone chemical evolution 
coupled to a simplified recipe for radial mixing, they argue that this 
non-monotonic trend is the result of old stars born at small~\rgal~where the 
equilibrium abundance is high. 
Only the old stars are able to migrate to the solar neighbourhood due to the 
time required for such a change in their orbital radius. 
\par 
Fig.~\ref{fig:age_oh_static} demonstrates this behaviour for our 
simulation-motivated radial migration prescription. Although it is 
observationally advantageous to measure age in bins of abundance because the 
abundance measurements are much more precise, it is conceptually easier to 
understand the model behaviour in terms of abundance spread at a given age. 
In both regions plotted, the youngest stars form with a composition inherited 
from the local ISM, which in this model is reflective of the late-time 
equilibrium abundance. 
At a given age, only stars born in a well-defined region of the 
Galaxy will have had adequate time to migrate to a given present-day radius. 
Since a range of~\rgal~maps directly to a range of metallicity once 
the ISM is close to the equilibrium abundance, this necessitates a maximum 
width of the [O/H] distribution at fixed age. 
With increasing age, the [O/H] distribution then gets wider because any given 
present-day radius samples stars formed at a wider range of~\rgal. 
We see this effect in Fig.~\ref{fig:age_oh_static}, with the colour-coding of 
the background points making it clear that stellar migration 
is the culprit. 
In the outer Galaxy, virtually all old stars added by migration lie above the 
local equilibrium metallicity. 
In the~\rgal~= 11 - 13 kpc region, our constant SFR model predicts a nearly 
monotonic increase of median population age with increasing [O/H], from 
[O/H] = -0.5 to +0.3. 
This trend is entirely backwards from that expected by simple one-zone models 
of GCE.

% fig 16 
\begin{figure} 
\centering 
\includegraphics[scale = 0.45]{amr_solar_annulus.pdf} 
\caption{The age-[O/H] (top) and age-[Fe/H] (bottom) relations for the solar 
neighbourhood (i.e.~$R_\text{gal}$ = 7 - 9 kpc,~$\left|z\right|\leq$~0.5 kpc) 
as predicted by the fiducial model. Red triangles, black squares, error bars, 
and background points are as in Fig.~\ref{fig:age_alpha}, but with the model 
prediction quantified in bins of~$\Delta$[O/H] =~$\Delta$[Fe/H] = 0.05. For 
comparison, we plot the~\citet{Feuillet2018} measurements in a dark red line, 
omitting the associated uncertainties for visual clarity. } 
\label{fig:amr_solar_annulus} 
\end{figure}

Fig.~\ref{fig:amr_solar_annulus} compares the age-[O/H] (top) and 
age-[Fe/H] (bottom) relations predicted by our inside-out SFH model for the 
solar neighbourhood (\rgal~= 7 - 9 kpc and \absz~$\leq$ 0.5 kpc) to the 
measurements from \citet{Feuillet2019}. 
For reference, we add the solid dark red line, which denotes the AMR measured 
by~\citet{Feuillet2018}. 
Although our model shows reasonable agreement with the~\citet{Feuillet2019} 
measurements in the solar annulus,~\citet{Feuillet2018} report ages for solar 
metallicity that are considerably younger ($\sim$1 - 2 Gyr as opposed to 
$\sim$3 - 4 Gyr). 
The origin of this difference is not clear, nor is it clear which AMR 
measurement is more reliable (D. Feuillet, private communication). 
Predictions for the inside-out SFH are similar to those shown previously 
for the constant SFR model, demonstrating that radial migration plays a larger 
role than the detailed SFH in determining the qualitative form of the AMR. 
The age-[O/H] and age-[Fe/H] relations are similar for both observations and 
models, a non-trivial result given the different time profile of SN Ia 
enrichment. 
Agreement between the model and the data is somewhat better for [O/H] than for 
[Fe/H]. 
The model predicts a large spread in age at fixed metallicity, comparable to 
but somewhat larger than the spread esimated by~\citet{Feuillet2019}. 
\par
Fig.~\ref{fig:amr_insideout_vs_lateburst_fe} compares the predictions of the 
inside-out (top) and late-burst (bottom) SFH models to the~\citet{Feuillet2019} 
age-[Fe/H] relation in four~\rgal~annuli, always with~\absz~$\leq$ 0.5 kpc. 
While neither model reproduces the data perfectly, the agreement is better 
overall for the late-burst model, a difference that is more evident from 
looking at all four annuli rather than the solar neighbourhood alone. 
The late-burst of star formation reduces the median age of [Fe/H]~$\approx$ 0 
stars, typically by 1 - 2 Gyr. 
The median age of the highest metallicity stars increases because the 
enhanced pristine gas accretion that fuels the starburst (see Fig. 
\ref{fig:evol}) dilutes the ISM metallicity, an effect that is evident in the 
tracks for a given birth~\rgal~in the lower panels. 
Stars from the inner Galaxy that form during the burst do so at roughly solar 
metallicity rather than appearing in the [Fe/H] = 0.2 - 0.5 bins. 
With reduced median age at [Fe/H]~$\approx$ 0 and increased median at 
[Fe/H] > 0.2, the late-burst model more consistently reproduces the C-shaped 
AMR that is the most striking qualitative feature of the observations. 
The CCSN and SN Ia associated with the burst also boost the evolutionary 
tracks of the inner Galaxy to higher [Fe/H] at late times, so the predicted 
age distribution at high [Fe/H] is bimodal, especially at~\rgal~= 5 - 7 kpc. 
The~\citet{Feuillet2019} results do not support this dichotomy, but they 
model the observations with the assumption of a Gaussian log age distribution, 
so it is worth returning to the data with the possibility of bimodal age 
distributions in mind. 
\par 
The outer-burst model mitigates this issue since it lacks the burst at small 
\rgal, predicting ages for the most metal-rich stars more in line with the 
\citet{Feuillet2019} measurements. 
We illustrate this difference in Fig.~\ref{fig:age_oh_comparison} in 
Appendix~\ref{sec:age_oh_relation} for the age-[O/H] relation. 
The detailed form of the AMR in our models is sensitive to the nature of the 
recent starburst, and its true form was likely more complicated than our 
parameterization. 
Fig.~\ref{fig:age_oh_comparison} also includes a comparison of the inside-out 
and late-burst model predictions, now without the effect of SN Ia enrichment. 
The late-burst model improves upon the inside-out model in age-[O/H] for the 
same reasons as in age-[Fe/H], but perhaps more clearly when looking 
bin-by-bin. 
% We do not believe these conclusions are impacted by further discrepancies 
% between any individual model and the observational sample, because our models 
% are not designed to reproduce the data exactly. 
\par 
The late-burst model is motivated by the star formation histories inferred 
empirically by~\citet{Isern2019} and~\citet{Mor2019}. 
Adding this late time enhancement to star formation improves agreement with the 
\citet{Feuillet2019} data, but it is not enough to reproduce the very young 
(< 2 Gyr) median ages of solar metallicity stars found by~\citet{Feuillet2018}. 
If future analyses confirm the 2018 ages rather than the 2019 ages, they would 
require a later and more extreme starburst to explain them. 
As discussed in~\S~\ref{sec:obs_comp:age_alpha}, the late-burst 
\textit{worsens} agreement with the~\citet{Feuillet2018, Feuillet2019} 
age-[O/Fe] relation because of the increased [O/Fe] at late times (see Fig. 
\ref{fig:age_alpha}). 
We do not see an obvious way to achieve good simultaneous agreement with the 
observationally inferred SFH, the age-[O/Fe] relation, and the age-[Fe/H] 
relation. 
Possibly a well-tuned choice of yields and the temporal and radial range of 
the burst could achieve such agreement; it is possible that the latter is 
related to the spatial dependence of the age-[O/Fe] relation seen in 
the~\citet{Feuillet2019} data (see Fig.~\ref{fig:age_alpha_regions}). 
Alternatively, an outflow prescription that preferentially removes CCSN 
ejecta rather than ambient ISM~\citep[see, e.g.,][]{Vincenzo2016, Chisholm2018, 
Christensen2018} could mitigate the increase in [O/Fe] during the burst (such a 
prescription is physically plausible, but it would require a wholesale 
recalibration of our model parameters). 
For now we conclude that radial migration can naturally explain otherwise 
puzzling features of the AMR and that evidence for enhanced late-time star 
formation in the Milky Way is ambiguous. 
Age-abundance relations are clearly a powerful diagnostic of GCE models, and 
observational investigations that demonstrate consistency across age 
determination methods, probe the shape of the age distribution at fixed 
abundance, and extend still further across the disc are highly desirable.

\end{document}

### 2021-08-04 chemev/MWbimodality/paper/draft2/conclusions.tex
migration paper referee response

\documentclass[draft2.tex]{subfiles} 
\begin{document}

\section{Conclusions} 
\label{sec:conclusions}

% fig 17 
\begin{figure*} 
\centering 
\includegraphics[scale = 0.35]{amr_insideout_vs_lateburst_fe.pdf} 
\caption{The age-[Fe/H] relation predicted by our inside-out (top) and 
late-burst (bottom) SFH models for~$R_\text{gal}$ = 5 - 7 kpc (left), 7 - 9 kpc 
(left middle), 9 - 11 kpc (right middle), and 11 - 13 kpc (right). Each panel 
shows only the~$\left|z\right|\leq$~0.5 kpc population. Red triangles, black 
squares, error bars, and coloured points are as in Fig.~\ref{fig:age_alpha} for 
the corresponding Galactic region, but with the model prediction quantified in 
bins of~$\Delta$[Fe/H] = 0.05. } 
\label{fig:amr_insideout_vs_lateburst_fe} 
\end{figure*}

In this paper, we have modeled the Milky Way as a series of concentric rings 
with~$\Delta R_\text{gal}$~= 100 pc width, describing each ring as a 
conventional one-zone chemical evolution model and allowing the exchange of 
stellar populations between zones to include the impact of stellar migration in 
the model Galaxy. 
Though there have been other studies that employ a similar methodology 
\citep[e.g.][]{Schoenrich2009a, Schoenrich2009b, Kubryk2015a, Kubryk2015b, 
Sharma2020}, ours and the~\citet{Minchev2013, Minchev2014, Minchev2017} model 
are the only ones that make use of a hydrodynamical simulation to describe 
radial mixing. 
In our case we use the~\hsim~zoom-in simulation of a Milky Way-like disc galaxy 
formed from cosmological initial conditions~\citep{Christensen2012, 
Zolotov2012, Loebman2012, Brooks2014, Bird2020}. 
The simulation provides a prescription for radial migration and vertical 
structure with no free parameters, though there is still a choice to be made 
about how to model the time dependence of migration for a given stellar 
population (see~\S~\ref{sec:methods:migration}). 
In our fiducial prescription, a stellar population traverses the~$\Delta\rgal$ 
between its birth and final radius with a~$\sqrt{t}$ time-dependence 
characteristic of diffusion, as in~\citet{Frankel2018, Frankel2020}. 
While CCSN nucleosynthetic products are deposited instantaneously in the 
population's birth annulus, its SN Ia iron production follows a~$t^{-1.1}$ 
delay-time distribution and is therefore spread across all the annuli that it 
traverses. 
\par 
We adopt supernova yields from oxygen and iron based on a combination of 
theoretical and empirical constraints. 
We base our star formation law on the observed 
$\dot{\Sigma}_\star - \Sigma_\text{g}$ relation in local spirals 
\citep{Bigiel2010, Leroy2013, Krumholz2018a}, with the redshift dependence 
suggested by the observations of~\citet{Tacconi2018}. 
We choose a radially dependent outflow mass loading factor~$\eta(\rgal)$ to 
reproduce observations of the Galactic disc metallicity 
gradient~\citep[e.g.][]{Frinchaboy2013, Hayden2014, Weinberg2019}. 
Our fiducial model adopts an inside-out SFH with e-folding timescales 
calibrated to the~\citet{Sanchez2020} age gradients of low redshift disc 
galaxies (see discussion in~\S~\ref{sec:methods:sfhs}). 
Motivated by the observational results of~\citet{Mor2019} and~\citet{Isern2019}, 
we construct models that exhibit a recent burst in star formation on top of the 
baseline model, as well as a constant SFH model for comparison purposes. 
\par 
We have compared our fiducial inside-out SFH model and its variants to a 
variety of observations, most of them derived from the SDSS APOGEE survey 
\citep{Majewski2017}, finding a number of qualitative successes but also some 
significant qualitative discrepancies. 
\begin{enumerate}

	\item[\textbf{1.}] The relative number of high-$\alpha$ and low-$\alpha$ 
	stars and the \feh~distribution of these two populations changes 
	systematically with~\rgal~and~\absz, in qualitative agreement with the 
	findings of~\citet{Nidever2014} and~\citet{Hayden2015}. 
	See Fig.~\ref{fig:ofe_feh_diagram}.

	\item[\textbf{2.}] The~\feh~and~\oh~distributions of stars near the 
	Galactic plane (\absz~$\leq$ 0.5 kpc) change shape, from negatively skewed 
	at small~\rgal~ to roughly symmetric in the solar neighbourhood to 
	positively skewed in the outer Galaxy, in agreement with the findings of 
	\citet{Hayden2015} and with our new measurements based on APOGEE DR16. 
	The influence of radial migration on MDF shape agrees with the simplified 
	model presented by~\citet{Hayden2015} and with the numerical simulation 
	results of~\citet{Loebman2016}. 
	See Figs.~\ref{fig:mdf_3panel_fe} and~\ref{fig:mdf_3panel_o}.

	\item[\textbf{3.}] Moving up from the midplane, the~\feh~and~\oh~MDFs 
	become more symmetric and less dependent on~\rgal, again in agreement with 
	the observational findings of~\citet{Hayden2015} and the simulation results 
	of~\citet{Loebman2016}. 
	However, the high~\absz~MDFs are not a perfect match to the APOGEE data, 
	especially at~\absz~= 0.5 - 1 kpc where they remain too skewed and too
	\rgal-dependent. 
	See Figs.~\ref{fig:mdf_3panel_fe} and~\ref{fig:mdf_3panel_o}.

	\item[\textbf{4.}] The distributions of~\ofe~in bins of~\feh~are broad, and 
	their skewness and width change with~\rgal~and~\absz~in qualitative 
	agreement with the APOGEE-based measurements of~\citet{Vincenzo2021a}. 
	However, the model~\ofe~distributions at sub-solar~\feh~do not reproduce 
	the pronounced bimodality found by~\citet{Vincenzo2021a}, and the 
	centroid of the model~\ofe~distribution at super-solar~\feh~shifts upwards 
	with increasing~\absz, a trend not seen in the data. 
	See Fig.~\ref{fig:ofe_mdfs_insideout}.

	\item[\textbf{5.}] The trend of median stellar age in bins of~\ofe~agrees 
	with the measurements of~\citet{Feuillet2019} in the solar neighbourhood. 
	The width of the log(age) distribution is narrow at high~\ofe~and broad 
	near solar~\ofe, again in agreement with the data. The model predicts a 
	median age-\ofe~relation that is nearly constant over the range 
	\rgal~= 5 - 13 kpc and~\absz~= 0 - 2 kpc, but~\citet{Feuillet2019} find a 
	$\sim$20\% reduction in the median age of high~\ofe~stars at high~\absz. 
	See Figs.~\ref{fig:age_alpha} and~\ref{fig:age_alpha_regions}.

	\item[\textbf{6.}] While most stars with~\ofe~$\geq$ 0.1 are old, the model 
	predicts a population of young and intermediate-age $\alpha$-rich stars. 
	These stars form in the outer Galaxy (\rgal~> 10 kpc) at times when the SN 
	Ia rate, and thus the iron enrichment, has fluctuated to low values because 
	stellar populations have migrated away before most of their SN Ia have time 
	to explode (see Fig.~\ref{fig:tracks}). 
	This mechanism, which is only realized because we track SN Ia enrichment 
	through rings as populations migrate (\S~\ref{sec:methods:migration}), 
	offers a novel explanation for the existence of young and intermediate-age 
	$\alpha$-rich stars seen in APOGEE~\citep{Chiappini2015, Martig2015, 
	Martig2016, Warfield2021}. 
	See Figs.~\ref{fig:age_alpha} and~\ref{fig:age_alpha_regions}.

	\item[\textbf{7.}] In the solar neighbourhood, the predicted distribution 
	of stellar age at solar~\feh~or~\oh~is broad, and the trend of median age 
	with metallicity is non-monotonic, with both sub-solar and super-solar 
	metallicity stars being older on average than solar metallicity stars. 
	These predictions agree with the observational results of 
	\citet{Feuillet2019}, though the age scatter is larger than 
	\citet{Feuillet2019} infer, and the agreement of median trends is better 
	for~\oh~than for~\feh. 
	The old population at super-solar metallicity has migrated from the inner 
	Galaxy, as suggested by~\citet{Feuillet2018, Feuillet2019}, and migration 
	produces a non-monotonic age-metallicity relation throughout the disc. 
	The agreement between predicted and observed age-\feh~realtions is 
	noticeably worse at~\rgal~= 5 - 7 kpc and somewhat worse at~\rgal~= 11 - 13 
	kpc. 
	See Figs.~\ref{fig:age_oh_static} -~\ref{fig:amr_insideout_vs_lateburst_fe}.

	\item[\textbf{8.}] The models with late bursts of star formation, either 
	throughout the disc or at~\rgal~> 6 kpc only (see Fig.~\ref{fig:evol}), 
	achieve better agreement with the~\citet{Feuillet2019} age-\feh~relation 
	over a range of~\rgal. 
	In particular, these models better reproduce the young median ages of solar 
	metallicity stars and the C-shaped form of the observed relation. 
	However, they predict a~$\sim$0.1-dex uptick of~\ofe~at ages of~$\sim$2 Gyr 
	that is not seen in the data. 
	The SFH of these models is empirically motivated~\citep{Mor2019, Isern2019}, 
	and we do not know if there is some variant of our implementation that 
	would preserve their improved agreement with age-\feh~while mitigating 
	their mismatch to age-\ofe. 
	For the other measures listed above, the predictions of these models are 
	qualitatively similar to those of the inside-out model. 
	See Figs.~\ref{fig:age_alpha_regions} and 
	\ref{fig:amr_insideout_vs_lateburst_fe}.

\end{enumerate}

All of these predictions are affected by radial migration, and those involving 
vertical trends also inherit the simulation's predicted correlations between 
final~\absz~and the age, birth radius, and final radius of a stellar 
population. 
We regard the overall level of agreement with many distinctive features of the 
Milky Way disc's abundance structure as a significant success of the models. 
However, at least within the framework explored here, it appears that models 
with smooth star formation are not able to explain the pronounced bimodality 
of the observed~\afe~distribution. As discussed by~\citet{Vincenzo2021a}, 
we expect that this problem is generic: a one-zone model with a smooth SFH 
produces an~\afe~distribution that peaks at low values, so it is difficult 
to create a superposition of such models that has a bimodal distribution. 
\par 
The most widely explored solution to this problem involves a two-phase SFH, 
with gas accretion resetting the ISM to low metallicity in between the two 
epochs. 
Versions of this scenario arise in two-infall GCE models 
\citep[e.g.][]{Chiappini1997, Spitoni2019a, Khoperskov2021} and in cosmological 
simulations that give rise to bimodal~\afe~\citep{Mackereth2017, Grand2018, 
Buck2020b}. 
An alternative scenario proposed by~\citet{Clarke2019}, motivated by 
hydrodynamic simulations, attributes the low-$\alpha$ sequence to an 
evolutionary track with low star formation efficiency and the high-$\alpha$ 
sequence to clumpy bursts of star formation that self-enrich with $\alpha$ 
elements. 
In a third, possibly fanciful scenario proposed by~\citet{Weinberg2017}, 
increased outflow efficiency at late times causes the low-$\alpha$ population 
to evolve ``backwards'' to lower~\feh, after formation of the high-$\alpha$ 
sequence. 
Radial migration is likely to reshape the predictions of any of these scenarios, 
even if it does not fully explain bimodality on its own. 
These scenarios can be easily realized within our modeling framework by 
changing the SFH, star formation efficiency, and outflow parameterizations. 
We intend to explore them in future work, seeking observable signatures that 
can distinguish these alternative explanations for one of the most striking 
features of the disc abundance distribution. 
\par 
The computational speed of our hybrid chemical evolution methodology makes it a 
valuable complement to calculating chemical evolution within full hydrodynamic 
cosmological simulations~\citep[e.g.][]{Mackereth2017, Grand2018, Naiman2018, 
Buck2020b, Vincenzo2020}. 
For a given cosmological simulation, we can consider many different choices of 
yields and chemical evolution parameters, varying them individually to isolate 
physical effects and exploring parameter space to identify good fits, 
degeneracies, and persistent discrepancies with data. 
There are many obvious directions to go in extending this approach. 
One is to apply it to additional cosmological simulations to understand the 
impact of different dynamical histories, and to add the ability to model 
stellar populations accreted from satellites. 
A second is to consider additional elements that probe different 
nucleosynthetic pathways; many of these are already incorporated in~\vice, and 
it is easy to add other elements and sources to models. 
A third is to include treatment of radial gas flows and fountains, both of 
which have been explored in more idealized GCE models (e.g.,~\citealp{Lacey1985, 
Bilitewski2012, Kubryk2015a, Kubryk2015b};~\citealp*{Spitoni2013}; 
\citealp{Pezzulli2016, Sharda2021a, Sharda2021b}). 
More ambitious is to implement treatment of stochastic enrichment and 
incomplete ISM mixing~\citep[e.g.][]{Montes2016, Krumholz2018b, Beniamini2020}, 
which have so far been little explored in the context of Milky Way disc 
evolution but which are likely important in understanding the detailed 
correlations of elemenal abundances~\citep{Ting2021}. 
As multi-element spectroscopic surveys grow even faster in scope and precision, 
efficient and flexible theoretical models will be essential for extracting the 
lessons they have to teach about the origin of elements and the history of the 
Milky Way.

\end{document}

### 2021-08-04 chemev/MWbimodality/paper/draft2/intro.tex
migration paper referee response

\documentclass[draft2.tex]{subfiles} 
\begin{document}

\section{Introduction} 
\label{sec:intro}

The orbits of stars are not fixed. The considerable intrinsic scatter in 
age-abundance relations of local disc stars~\citep{Edvardsson1993} and the high 
metallicity of the sun relative to nearby stars of similar age 
\citep*{Wielen1996} provided early evidence that stars in the Milky Way disc 
can migrate several kiloparsecs from the Galactocentric radius at which they 
formed. 
Interest in radial migration as an important element of galactic chemical 
evolution (GCE) grew further with the demonstration by~\citet{Sellwood2002} 
that resonant interactions with transient spiral perturbations could 
change stars' orbital guiding centre radii without increasing orbital 
eccentricity, and with subsequent studies showing ubiquitous radial migration 
in numerical simulations of disc galaxies (e.g.~\citealp{Roskar2008a, 
Roskar2008b, Loebman2011, Minchev2011};~\citealp*{Bird2012}; 
\citealp{Bird2013};~\citealp*{Grand2012a, Grand2012b, Kubryk2013}). 
\citet{Schoenrich2009a,Schoenrich2009b} developed the first detailed GCE 
models incorporating radial migration, describing it with a flexible, 
dynamically motivated parameterization constrained simultaneously with other 
GCE parameters when fitting to observations. A number of subsequent studies 
have incorporated radial migration using similar analytic or parameterized 
models (e.g.~\citealp{Bilitewski2012, Hayden2015};~\citealp*{Kubryk2015a, 
Kubryk2015b};~\citealp{Feuillet2018};~\citealp*{Sharma2020}), and 
\citet{Frankel2018, Frankel2019, Frankel2020} have used stellar abundances, 
ages, and kinematics to constrain radial migration empirically. 
\par 
In this paper we construct evolutionary models for the Milky Way disc that 
combine a classic multi-ring GCE approach (e.g.,~\citealp{Matteucci1989, 
Wyse1989, Prantzos1995}) with stellar migration predicted by a 
hydrodynamic simulation of disc galaxy formation from cosmological initial 
conditions. 
% Our methodology is similar to that of~\citet*{Minchev2013, Minchev2014}, but 
% the logic runs in the opposite direction of~\citet{Buck2021} who recently 
% applied chemical evolution models with~\texttt{Chempy}~\citep*{Rybizki2017} to 
% the N-body+SPH code~\texttt{Gasoline2}~\citep{Wadsley2017}. 
Our methodology is similar to that of~\citet*{Minchev2013, Minchev2014} and has 
similar motivations. 
% \citet{Buck2021} recently explored variations of chemical evolution model 
% assumptions in hydrodynamical simulations by applying~\texttt{Chempy} 
% \citep*{Rybizki2017} to the N-body+SPH code~\texttt{Gasoline2} 
% \citep{Wadsley2017}. 
The use of a cosmological simulation that agrees with many observed properties 
of the Milky Way assures that our stellar migration scenario is physically 
plausible, including any correlations of migration in time and space that might 
be difficult to capture in a parameterized description. 
Most hydrodynamic cosmological simulations include metal enrichment, and direct 
comparison between the predicted and observed abundance patterns can provide 
valuable insights into the accuracy of the simulations and the possible origin 
of the observed element structure (e.g., ~\citealt{Mackereth2017, Grand2018, 
Buck2020b, Vincenzo2020, Buck2021}). 
\par 
However, many ingredients of the simulations' enrichment recipes are 
uncertain, and metal transport and mixing within the interstellar medium (ISM) 
are sensitive to numerical resolution and to details of the hydrodynamics and 
star formation algorithms. 
Our hybrid approach allows us to consider many 
choices of uncertain GCE parameters, tuning them to reproduce some 
observations while leaving others as independent empirical tests. 
This flexible approach also allows us to isolate the impact of different 
GCE model ingredients and to zero-in on the ways that stellar migration 
influences the predicted chemical evolution. 
In exchange for this exploratory freedom, the hybrid model is not fully 
self-consistent, instead adopting its own accretion, star formation, and 
outflow histories rather than the simulation's. Although our methodology can 
be applied with any given choice of cosmological simulation, we make use of 
only one in the present paper. 
One could however apply the same method to multiple simulations to 
predict a statistical distribution of outcomes. 
\par 
We focus our predictions and observational comparisons on oxygen, a 
representative~$\alpha$-element producted almost exclusively by core 
collapse supernovae (CCSN), and iron, which at solar abundances has roughly 
equal contributions from CCSN and Type Ia supernovae (SN Ia). We will consider 
other elements with other nucleosynthetic sources in future work, but 
observed trends of~\feh~and~\afe\footnote{
	We follow standard notation where $[X/Y] = \log_{10}(X/Y) - 
	\log_{10}(X/Y)_\odot$. Different observational studies use different 
	$\alpha$-elements (or combinations thereof) in abundance ratios, and we 
	will generally use~\ofe~and~\afe~synonymously. 
} in the Milky Way disc already display a number of striking features, 
including: 
\begin{itemize} 
	\item At sub-solar~\feh, the distribution of~\afe~is bimodal, with 
	``high-$\alpha$'' and ``low-$\alpha$'' sequences typically separated by 
	0.1-0.4 dex (e.g., 
	\citealp{Fuhrmann1998};~\citealp*{Bensby2003};~\citealp{Adibekyan2012, 
	Vincenzo2021a}).

	\item The location of the high-$\alpha$ and low-$\alpha$ sequences is 
	nearly independent of position in the disc, but the relative number of 
	stars in these sequences and the distributions of those stars in 
    \feh~changes systematically with Galactocentric radius~$\rgal$~and midplane 
	distance~$\absz$~\citep{Nidever2014, Hayden2015, Weinberg2019}.

	\item In addition to an overall radial gradient, the shape of the 
	\feh~distribution for stars with~$\absz < 0.5$ kpc changes from negatively 
	skewed in the inner disc to roughly symmetric at the solar neighbourhood 
	to positively skewed in the outer disc~\citep{Hayden2015, Weinberg2019}.

	\item With increasing~$\absz$,~\feh~distributions become more symmetric 
	and less dependent on~$\rgal$~\citep{Hayden2015}.

	\item The age-metallicity relation (AMR) is broad, with a wide range of 
	\feh~at fixed stellar age and vice versa in the solar neighbourhood 
	\citep{Edvardsson1993} and beyond~\citep{Feuillet2019}. The trend of 
	median age with~\feh~or~\oh~is non-monotonic, with solar metallicity 
	stars being younger on average than both metal-poor~\textit{and} 
	metal-rich stars~\citep{Feuillet2018, Feuillet2019, Lu2021}.

	\item The trend of stellar age with~\afe~is much tighter than the trend 
	with~\feh, becoming broad near~\afe~$\approx$~0~\citep{Feuillet2018, 
	Feuillet2019}. Although most stars with~\afe~$\geq$~0.1 are old, 
	observations have revealed a significant population of~$\alpha$-rich stars 
	that appear to be young or intermediate age~\citep{Chiappini2015, 
	Martig2015, Martig2016, Warfield2021}. Some of these stars may have been 
	``rejuvinated'' by stellar mergers or mass-transfer events 
	\citep{Izzard2018, SilvaAguirre2018}, and the question of what fraction 
	are truly much younger than the median age-\afe~relation remains open 
	\citep{Hekker2019}. 
\end{itemize} 
Many of these results have emerged most clearly from the Apache Point 
Observatory Galaxy Evolution Experiment (APOGEE;~\citealp{Majewski2017}) of 
the Sloan Digital Sky Survey (SDSS-III:~\citealp{Eisenstein2011}; 
SDSS-IV:~\citealp{Blanton2017}), sometimes confirming and extending trends 
suggested by earlier observational data. We will assess the degree to which 
models with fairly conventional GCE assumptions coupled to simulation-based 
radial and vertical migration of stars can explain, or fail to explain, these 
observations. 
\par 
Relative to~\citet{Minchev2013, Minchev2014}, our base GCE model has many 
differences of detail, the most important being our inclusion of outflows, 
which is in turn connected to our different choice of oxygen and iron yields. 
Our simulation, the galaxy~\hsim~from the~\citet{Christensen2012} 
suite evolved with the N-body+SPH code~\texttt{GASOLINE}~\citep{Wadsley2004}, 
is fully cosmological, while the simulation used by~\citet{Minchev2013, 
Minchev2014} has a more idealized geometry with merger and accretion history 
drawn from a larger cosmological volume~\citep{Martig2012}. 
The~\citet{Minchev2013, Minchev2014} simulation has a fairly strong, 
long-lived bar while~\hsim~has only a weak, transient bar, and this difference 
could have some impact on radial migration. 
Another methodological difference, which turns out to be important for some 
observables, is that we track enrichment from stellar populations as they 
migrate (see~\S~\ref{sec:obs_comp:age_alpha} below), while~\citet{Minchev2013, 
Minchev2014} assume that populations enrich only the radial zone in which they 
were born. 
\par 
Previous studies have shown that~\hsim~and other disc galaxies evolved with 
similar physics have realistic rotation curves~\citep{Governato2012, 
Christensen2014a, Christensen2014b}, stellar mass~\citep{Munshi2013}, 
metallicity~\citep{Christensen2016}, dwarf satellite populations 
\citep{Zolotov2012, Brooks2014}, and HI properties~\citep{Brooks2017}. 
Most directly relevant to this study,~\citet{Bird2020} demonstrate that 
\hsim~accurately reproduces the observed relation between stellar age and 
vertical velocity dispersion~$\sigma_z$. 
This relation arises as a consequence of ``upside-down'' disc formation in 
which the star-forming gas layer becomes thinner with time as well as the 
dynamical heating of stars as they age (\citealp*{Bournaud2009a, 
Bournaud2009b, Forbes2012};~\citealp{Bird2013};~\citealp*{Vincenzo2019}; 
\citealp{Yu2021}). 
\citet{Schoenrich2009a} distinguish between the radial mixing caused by 
``blurring'' of stars on moderately eccentric orbits and ``churning'' that 
changes the guiding centre radii of their orbits. 
Both phenomena occur in our simulation and we do not attempt to separate them, 
simply using the terms ``migration'' or ``mixing'' to refer to the combined 
effect. 
In addition to radial migration, we use the~\hsim~predictions for the vertical 
locations (i.e., midplane distances~$\absz$) of stars at the present day. 
Our GCE model assumes that the gas disc is vertically well mixed, so a stellar 
population's birth abundances depend only on~$\rgal$~and time. 
Vertical gradients arise because older populations have larger~$\sigma_z$~and 
thus larger average~$\absz$, and also because radial migration is 
coupled to changes in~$\sigma_z$~\citep*{Solway2012}. 
The good match to the observed age-velocity relation found by~\citet{Bird2020} 
allows us to use vertical trends of abundance ditributions as a further test 
of our chemical evolution model. 
\par 
We describe the~\hsim simulation further in~\S~\ref{sec:methods:h277} and our 
implementation of radial migration in~\S~\ref{sec:methods:migration}. 
We describe the base GCE model in~\S\S~\ref{sec:methods:sfhs} - 
\ref{sec:methods:summary}. Distinctive features of our GCE model are the use 
of a radially dependent outflow mass loading~$\eta(\rgal)$~to tune the 
metallicity gradient, our implementation of a star formation law motivated by 
spatially resolved studies of nearby galaxies and high-redshift studies of its 
time-dependence, and our use of mean radial age trends of disc galaxies to set 
the radial dependence of the star formation history (SFH). 
Our fiducial model adopts a smooth SFH with an ``inside-out'' radial trend in 
which star formation proceeds more rapidly in the inner Galaxy. 
Motivated by the observational analyses of~\citet{Isern2019} and 
\citet{Mor2019}, we also consider models with a burst of star formation 
centred~$\approx$~2 Gyr in the past, similar to the one-zone models 
investigated by~\citet{Johnson2020}. 
Other authors have suggested multiple bursts in the Milky Way's SFH 
(e.g.,~\citealp*{Lian2020a, Lian2020b};~\citealp{RuizLara2020, 
Sysoliatina2021}), perhaps triggered by satellite interactions, while others 
have advocated a two-phase SFH to explain the~\afe dichotomy (e.g., 
\citealp*{Chiappini1997};~\citealp{Haywood2016, Spitoni2019a, Buck2020a, 
Khoperskov2021}). We do not investigate these more complex SFHs here, but we 
plan to do so in future work.

\end{document}

### 2021-08-04 chemev/MWbimodality/paper/draft2/methods.tex
migration paper referee response

\documentclass[draft2.tex]{subfiles} 
\begin{document}

\section{Methods} 
\label{sec:methods} 
To fulfill the goals of this paper, we develop and make use of newly released 
features within the~\texttt{Versatile Integrator for Chemical Evolution} 
(\vice;~\citealp{Johnson2020}), an open-source~\texttt{python} package 
available for~\texttt{Unix} system architectures (for further details, see 
Appendix~\ref{sec:vice}). 
These features are designed to handle models such as these with a wide range of 
flexibility. 
We reserve a description of~\vice's migration algorithm and our simulation 
parameters for~\S~\ref{sec:methods:migration}, first describing our sample of 
star particles from the hydrodynamic simulation. 
\par 
Although we make use of a hydrodynamic simulation to drive stellar migration, 
we do~\textit{not} make use of its SFH. 
While our study employs similar techniques as~\citet{Minchev2013}, ours differs 
slightly in that they take a single SFH which is similar, but not identical to 
that of their N-body+SPH simulation; in this paper we present a handful of 
assumptions about the SFH, which do not necessarily resemble that of~\hsim. 
An alternative to modeling radial migration based on a 
hydrodynamical simulation is to invoke dynamical arguments; 
\citet{Schoenrich2009a} and~\citet{Sharma2020} take such an approach. 
This method, however, introduces free parameters which then require fitting to 
data. 
An advantage of our technique is that there are no free parameters describing 
radial migration introduced to the model; it is unclear how much 
fitting radial migration parameters could bias the model into agreement with 
parts of the data not involved in the fitting process. 
Instead we adopt a physically motivated migration model evolved from 
cosmological initial conditions. 
We rely on a single realization of this numerical model and are thus subject to 
the differences between the dynamical history of this simulated galaxy and that 
of the Milky Way. 
However, one could compare the predictions made by our chemical evolution 
models when applied to different hydrodynamical simulations, a direction we 
plan to pursue in future work. 
We emphasize that the hydrodynamical simulation~\textit{only} informs the 
mixing processes in our models, and there is no N-body integration involved in 
our models aside from that which was used to run the~\hsim~simulation in the 
first place.

\subsection{The Hydrodynamical Simulation} 
\label{sec:methods:h277} 
In this paper we make use of star particles from the~\texttt{h277} simulation 
\citep{Christensen2012, Zolotov2012, Loebman2012, Loebman2014, Brooks2014}. 
Recently employed to study the stellar age-velocity relationship, a synopsis of 
its detailed simulation parameters and cosmological model can be found in~\S~2 
of~\citet{Bird2020}. 
We do not repeat these details here, instead focusing on how we vet the sample 
of star particles for use in our chemical evolution models. 
\par 
The parameters of stars that we use in our analysis are the birth and final 
radii and the final midplane distance. 
\hsim~did not record the exact birth radius of each star particle; however, 
each star particle does have an accurate age at each snapshot. 
The orbital radii of stars that are sufficiently young in their first snapshot 
should be good approximations of their birth radii. 
We therefore restrict our sample to those star particles with an age at first 
snapshot of~$\leq$~150 Myr, and we adopt their Galactocentric radius at that 
time as their birth radius. 
We have repeated our analysis with a maximum age at first snapshot of 50 
Myr and found similar results, indicating that these time intervals are short 
enough to not impact our conclusions. 
We adopt the 150 Myr interval because it provides a larger number of star 
particles to sample from. 
Of the star particles that remain after imposing this cut, the oldest has an 
age of 13.23 Gyr at the present day (i.e. at the simulation's final output). 
Our GCE model can only apply on timescales as long as or shorter than the full 
range of ages of the sample of star particles; we therefore subtract 0.5 Gyr 
from the formation times of all star particles, allowing~$T$~= 0 in our models 
to correspond to~$T$~= 0.5 Gyr in~\hsim. 
As a consequence, our disc models trace the chemical evolution of the Galaxy 
out to a lookback time of~$\sim$13.2 Gyr, or a redshift of~$z \approx$~9, 
placing the onset of star formation at that time. 
\par 
We further restrict our sample of star particles to only those with both 
formation and final radii of~$\rgal \leq$~20 kpc, and to have formed 
within~$\absz\leq$~3 kpc of the disc midplane. 
These criteria are intended to restrict our sample to star particles that 
formed within the disc and can therefore be described by a disc GCE model. 
While it is possible that some star particles formed in a dwarf galaxy happen 
to satisfy our geometrical cuts at the star's formation time, these particles 
are few in number, and are only relevant at large~$\rgal$ and high 
ages: a region of parameter space where few stars form anyway. 
\par 
Based on a kinematic decomposition performed on the present-day phase space 
distribution of the~\texttt{h277} star particles conducted with the 
\texttt{analysis.decomp} routine within the~\texttt{pynbody} package 
\citep{pynbody}, we classify each star particle as having thin disc, thick 
disc, bulge, pseudobulge, or halo-like kinematics.
Details on the decomposition process can be found in~\citet{Brook2012} 
and~\citet{Bird2013}. 
We include the entire sample in~\vice's public code base, but only make use of 
those with disc-like kinematics in this paper. 
Our geometric selection yields 3,152,211 star particles in total, 1,751,765 of 
which have disc-like kinematics and are included in our sample. 
% Based on a kinematic decomposition performed on the present-day phase space 
% distribution of the~\texttt{h277} star particles, we include all those with 
% bulge, pseudobulge, and disc-like kinematics, excluding halo stars. 
% While we are not modeling the evolution of the bulge here, these star particles 
% are overwhelmingly located at~$\rgal\leq$~3 kpc at the present day 
% and therefore do not enter our analysis and observational comparisons below. 
% These cuts yield a sample of 3,102,519 star particles from~\hsim. 
\par 
\hsim~had a weak and transient bar during its evolution, but it does not have 
one at~$z$~= 0. 
This is a noteworthy difference between our model and that of 
\citet{Minchev2013}, and by extension the~\citet{Minchev2014, Minchev2017} 
studies as well, because they selected a hydrodynamic simulation of a galaxy 
specifically so that it would have a strong bar at~$z$~= 0. 
This could mean that the dynamical history of our model Galaxy differs from 
that of~\citet{Minchev2013} and perhaps the Milky Way itself. 
However, the difference is likely within the uncertainties of the current 
understanding of the Milky Way's dynamical history. 
Although an investigation of the impact of bar evolution on stellar migration 
and thus chemical evolution is outside the scope of this paper, it is an 
interesting question that can be probed by simply swapping the~\hsim~data 
within~\vice~for another simulation, then rerunning our numerical models and 
comparing the results.

% fig 1 
\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{decomposition.pdf} 
\caption{Radial distributions of our sample of star particles from 
\texttt{h277}. In the top row, we show distributions of~\textit{final} radius 
in bins of birth radius and age, and in the bottom row, we show distributions 
of~\textit{birth} radius in bins of final radius and age. Each bin in 
Galactocentric radius is shown in its own panel, denoted in text at the top of 
each panel and by vertical black dashed lines. We colour-code the distributions 
according to the age of the star particles, denoted by the legend in the upper 
left panel. We smooth all distributions with a box-car width of 0.5 kpc to 
improve visual clarity. We omit the distributions for 8 - 10 Gyr old stars born 
in the 9 - 11 and 11 - 13 kpc bins due to an insufficient number of star 
particles with which to calculate the distribution. } 
\label{fig:h277_decomposition} 
\end{figure*}

In the top row of Fig.~\ref{fig:h277_decomposition}, we plot the distributions 
of final radius in bins of birth radius and age for our sample of star 
particles. 
Conversely, the bottom row shows distributions of birth radii in bins of final 
radius and age. 
Focusing on the top row of panels, we note that for star particles born at any 
radius and time, the distribution of final radius is still peaked near the 
birth radius, but the peak moves slightly inward with increasing age. 
The tails of the distributions toward larger~$\rgal$ are nearly 
age-independent, while the tails toward smaller~$\rgal$ are not. 
This suggests that radial migration inward and outward occur on different 
timescales in~\texttt{h277}, specifically that inward migration is slower than 
outward migration. 
By extension, this suggests that the two may be tied to different physical 
processes. 
Alternatively, it may simply be that stars that migrate to the outer Galaxy are 
no longer subject to strong dynamical perturbations while stars that move 
inward can still experience strong orbital disturbances. 
\par 
Focusing on the bottom row of panels in Fig.~\ref{fig:h277_decomposition}, we 
note that the modes of the birth radius distributions show a much stronger 
dependence on age than the modes of the final radius distributions. 
At any Galactocentric radius at the present day, the youngest stars are 
overwhelmingly born at comparable radii, while the oldest stars are 
overwhelmingly born at smaller radii. 
This trend is most noticeable at large~$\rgal$. 
The differences between the final radius and birth radius distributions can be 
understood by considering the radial gradient of stellar surface density: there 
are more stars at small radius to move outward than vice versa, so roughly 
symmetric evolution of~$R_\text{final}$ produces strongly asymmetric evolution 
of~$R_\text{birth}$. 
\par 
Taking~$\left|\Delta \rgal\right| \geq$~500 pc 
between birth and final radii as the criterion for migration inward or outward, 
we find as global percentages in our sample that 27\% of star particles 
migrated inward, 29\% migrated outward, and the remaining 44\% stayed near 
their birth radius. 
As one can see from the top panels of Fig.~\ref{fig:h277_decomposition}, a 
large fraction of migration away from birth radius has already occurred by the 
time stars are~$\sim$2 Gyr old. 
If the SN Ia delay-time distribution (DTD) is a~$t^{-1.1} \approx t^{-1}$ 
power-law as suggested by observational results~\citep[e.g.][]{Maoz2012, 
Maoz2017}, then we expect similar numbers of SN Ia events to occur with delay 
times between 0.1 - 1 Gyr and 1 - 10 Gyr. 
With an extended DTD and the timescales for migration implied by 
Fig.~\ref{fig:h277_decomposition}, SN Ia progenitors can migrate significant 
distances before exploding. 
This effect has largely been neglected by GCE studies to date on the grounds 
that radial migration is a slow process, and thus the majority of 
nucleosynthesis should occur near a star's birth radius (e.g. as assumed in 
\citealp{Minchev2013}, and the application of the~\citealp*{Weinberg2017} 
analytic models in~\citealp{Feuillet2018}). 
However, we show below that radial migration within the timescale of the SN Ia 
DTD can have an important impact on some aspects of chemical evolution.

\subsection{Radial Migration} 
\label{sec:methods:migration} 
As in previous studies~\citep[e.g.][]{Matteucci1989, Schoenrich2009a, 
Minchev2013, Sharma2020}, in this paper we model the Milky Way as a series of 
concentric rings\footnote{
	For clarity, we use the term ``ring'' to refer to a computational zone of 
	our calculation (100 pc in radial range) and the term ``annulus'' to refer 
	to a larger radial range (typically 2 kpc). 
} with a uniform width~$\Delta \rgal$. 
To run numerical simulations of these models, we develop and make use 
of~\vice's~\texttt{milkyway} object, designed specifically for such an 
approach. 
The~\texttt{milkyway} object is a subclass of a more general object named 
\texttt{multizone}; at its core a~\texttt{multizone} object is an array of 
\texttt{singlezone} objects, which are designed to handle one-zone models of 
GCE and were the focus of~\citet{Johnson2020},~\vice's initial release paper. 
The~\texttt{multizone} object affords users full control over which zone any 
individual stellar population is in at all timesteps following its formation as 
well as the ability to move gas between any two zones with any time dependence. 
In principle this should allow for arbitrarily complex zone configurations and 
migration prescriptions. 
The~\texttt{milkyway} object is a user-friendly extension of the 
\texttt{multizone} base class, which enforces an annular zone configuration as 
we take here. 
As defaults, it adopts the stellar migration model detailed in this section, 
our star formation law discussed in~\S~\ref{sec:methods:sfe}, and the scaling 
of the outflow mass loading factor~$\eta$ with radius~\rgal~parameterized 
in~\S~\ref{sec:methods:outflows}. 
\par 
As in hydrodynamical simulations, star particles in~\vice~are stand-ins for 
entire stellar populations. 
They are said to be in a given zone if their radius is between the inner and 
outer edges of the ring. 
At all times, their nucleosynthetic products and returned envelopes are placed 
in the ISM of the ring that they are in~\textit{at that time}. 
\vice~forms a fixed number of stellar populations per zone per timestep, and it 
allows their masses to vary to account for variations in the SFR. 
The total mass of stars formed in a given zone and timestep is divided evenly 
among the corresponding stellar populations, which can then experience 
different stellar migration histories. 
\par 
The final radius of a stellar population is then determined based on the birth 
and final radii of star particles in the hydrodynamical simulation. 
Describing the Galaxy as a series of concentric rings,~\vice's~
\texttt{milkyway} object assumes stellar populations are born at the centres of 
each ring. 
For a stellar population born at a time~$T$ and Galactocentric radius 
$\rgal$, it first searches for star particles from~\texttt{h277} that 
formed at~$T \pm$~250 Myr and~$\rgal \pm$~250 pc. 
It then randomly selects a star particle from this subsample to act as an 
\textit{analogue}. 
This stellar population then adopts the change in orbital radius 
$\Delta \rgal$ of its analogue, and moves from its birth radius to the 
implied final radius at~$T$ = 13.2 Gyr with an assumed time dependence (see 
below). 
If no candidate analogues are found,~\vice~widens the search to~$T \pm$~500 Myr 
and~$\rgal \pm$~500 pc. 
If still no analogue is found, then it finds the star particle with the 
smallest difference in birth radius still within a birth time of $T \pm$~500 
Myr, and assigns it as the analogue. 
While this prescription allows stellar populations to be assigned analogues 
with significantly different birth radii, this is only an issue for small~$T$ 
and large~$\rgal$ where there are few star particles from~\hsim, 
and where few stars form in nature anyway due to the inside-out growth of 
galaxies~\citep[e.g.][]{Bird2013}. 
Furthermore, due to the similarity of the histograms in the top row of 
Fig.~\ref{fig:h277_decomposition}, we expect taking~$\Delta \rgal$ from 
a star particle that formed at a similar time but different birth radius in 
these instances to be accurate enough for our purposes. 
When an~\hsim~star particle is assigned as an analogue, it is~\textit{not} 
thrown out of the sample of candidate analogues, in theory allowing a star 
particle to act as an analogue for multiple stellar populations. Because these 
populations will have similar~$R_\text{form}$~and~$T_\text{form}$, they will 
have similar but not identical abundances.

% fig 2 
\begin{figure} 
\centering 
\includegraphics[scale = 0.45]{migration.pdf} 
\caption{A diagram illustrating how Galactocentric radius changes with time for 
two stellar populations under our migration schema: diffusion (crimson, solid), 
linear (lime, dot-dashed), post-process (black, dotted), and sudden (blue, 
dashed). Here the initial and final radii and birth times are chosen at random 
for illustrative purposes. With the initial and final Galactocentric radii of 
a stellar population, its birth time, and one of these assumptions regarding 
the time-dependence of radial migration, the Galactocentric radius at all times 
is known. Diffusion is our default model. } 
\label{fig:migration_schema} 
\end{figure}

We neglect radial gas flows in the present paper~\citep{Bilitewski2012, 
Lacey1985}, instead focusing our comparisons on the time-dependence with which 
stars migrate. 
We consider four models describing the evolution between a star particle's 
birth and final radius: 
\begin{itemize} 
	\item \textbf{Post-Processing}: Stars stay where they are born until the 
	final timestep, at which point they instantly migrate to their final 
	radius. 
	This retains the assumption that stars do not contribute to nucleosynthesis 
	beyond their birth radius as employed in previous studies 
	\citep[e.g.][]{Minchev2013}. 
	In this scenario, the ISM of each ring is treated as a one-zone model 
	independent of all other zones. We illustrate this case with a black dotted 
	line in Fig.~\ref{fig:migration_schema}.

	\item \textbf{Sudden}: A random number is drawn from a uniform distribution 
	between a stellar population's time of birth and the present day. 
	That time is taken to be the time of instantaneous migration to the 
	present-day annulus. 
	This emulates a scenario in which a single dynamical interaction rapidly 
	changes a star's orbital radius, and it can be thought of mathematically as 
	a generalization of the post-processing scenario. 
	We illustrate this case with a blue dashed line in 
	Fig.~\ref{fig:migration_schema}.

	\item \textbf{Diffusion}: Stars move to their final radii in a continuous, 
	time-dependent manner, with displacement~$\propto \sqrt{\text{age}}$. 
	This scenario corresponds to diffusion of angular momentum by a random 
	walk, similar to the assumption used by~\citet{Frankel2018, Frankel2020}. 
	We illustrate this case with a red solid line in 
	Fig.~\ref{fig:migration_schema}.

	\item \textbf{Linear}: A simple variation of the diffusion model in which 
	the migration to the final radius scales linearly with age rather than with 
	$\sqrt{\text{age}}$. We illustrate this case with a green dot-dashed line 
	in Fig.~\ref{fig:migration_schema}. 
\end{itemize} 
The diffusion model has the clearest physical motivation, and it is our default 
assumption used in all cases unless otherwise noted. 
The other models provide illustrative contrasts and allow us to investigate our 
model's sensitivity to the details of radial migration. 
We do not distinguish between ``blurring'' and ``churning'' 
\citep{Schoenrich2009a}, terms frequenly used to refer to a star's epicyclic 
motions and changes in the guiding centre of its orbit, respectively. 
% We do not distinguish between ``blurring'' and ``churning'', terms frequently 
% used to refer to a star's epicyclic motions and changes in the guiding centre 
% of its orbit~\citep[e.g.][]{Sellwood2002, Schoenrich2009a}. 
Both effects, induced by a wide variety of underlying causes such as molecular 
cloud scattering~\citep{Mihalas1981, Jenkins1990, Jenkins1992}, orbital 
resonances with spiral arms or bars~\citep{Sellwood2002, Minchev2011}, and 
satellite perturbations~\citep{Bird2012}, are present in the~\hsim~simulation. 
\par 
Our GCE model assumes that the star-forming ISM is vertically and azimuthally 
mixed within each radial annulus. 
The abundances assigned to a stellar population depend on its birth radius and 
time, but they do not depend on its distance from the plane. 
Nonetheless, as shown below, the abundance patterns of our simulation exhibit 
clear vertical gradients because older stellar populations have thicker 
vertical distributions~\citep{Bird2020}. 
Radial migration is also coupled to vertical dynamics in complex ways 
\citep{Solway2012, Minchev2012b}. 
We will see that these effects already suffice to explain many of the observed 
vertical trends of Milky Way disc abundances.

% \subsection{Nucleosynthetic Yields, Outflows, and Recycling} 
% \label{sec:methods:yields} 
\subsection{Nucleosynthetic Yields} 
\label{sec:methods:yields} 
We focus our analysis on alpha and iron-peak elements, taking oxygen (O) and 
iron (Fe) as the representative cases. 
The dominant enrichment channels of interest in our models are thus CCSN and 
SN Ia~\citep{Johnson2019}. 
We would expect similar results for other alpha (e.g. Ne, Mg, Si) and 
iron-peak elements (e.g., Cr, Ni), with quantitative differences reflective of 
their relative yields. 
Odd-$Z$ iron-peak elements (e.g., V, Mn, Co) could behave somewhat distinctly 
because of metallicity-dependent yields. 
\par 
CCSN enrichment happens immediately following the formation of progenitor stars 
in~\vice. 
This is an adequate approximation, because the lifetimes of massive stars are 
short compared to the relevant timescales for galaxy evolution. 
For the most massive stars, the lifetimes are comparable to the timestep size 
we adopt in our numerical integrations. 
This assumption implies a linear relationship between the CCSN enrichment 
rate and the SFR: 
\begin{equation} 
\dot{M}_x^\text{CC} = y_x^\text{CC}\dot{M}_\star 
\end{equation} 
where~$y_x^\text{CC}$ is the CCSN yield of some element~$x$. Physically, this 
quantity represents the mass of an element~$x$ ejected to the ISM from all 
CCSN events associated with a stellar population in units of the stellar 
population's initial mass. 
For example, if~$y_x^\text{CC} = 0.01$, a hypothetical 100~\msun~stellar 
population would add 1~\msun~of~$x$ to the ISM immediately. 
In this paper, we adopt~$y_\text{O}^\text{CC}$ = 0.015 and 
$y_\text{Fe}^\text{CC}$~= 0.0012 from~\citet{Johnson2020}, who in turn adopt 
these values from~\citet{Weinberg2017}. 
\par 
SN Ia nucleosynthesis products are injected according to a~$t^{-1.1}$ DTD with 
a minimum delay time of~$t_\text{D}$ = 150 Myr. 
This is the default DTD in~\vice, which was also adopted by 
\citet{Johnson2020}, and is suggested by recent observational results comparing 
the cosmic SN Ia rate to the cosmic SFH~\citep{Maoz2012, Maoz2017}. 
In a one-zone model at times~$t > t_\text{D}$, the enrichment rate of some 
element~$x$~can be expressed as the product of some yield~$y_x^\text{Ia}$ and 
the SFH weighted by the DTD: 
\begin{subequations}\begin{align} 
\dot{M}_x^\text{Ia} &= y_x^\text{Ia}\langle\dot{M}_\star\rangle_\text{Ia} \\ 
&= y_x^\text{Ia}\ddfrac{
	\int_0^t \dot{M}_\star(t') R_\text{Ia}(t - t') dt' 
}{
	\int_{t_\text{D}}^{t_\text{max}} R_\text{Ia}(t')dt' 
} 
\label{eq:mdot_ia} 
\end{align}\end{subequations} 
where~$R_\text{Ia}$ is the DTD itself, which has units of~$M_\odot^{-1}$ 
Gyr$^{-1}$. 
Like the CCSN yield,~$y_x^\text{Ia}$ is the mass of some element~$x$ produced 
by SNe Ia over the time interval~$t_\text{D} - t_\text{max}$, in units of the 
stellar population's initial mass. 
It can also be expressed as an integral over the DTD: 
\begin{equation} 
y_x^\text{Ia} = m_x^\text{Ia} \int_{t_\text{D}}^{t_\text{max}} R_\text{Ia}(t') 
dt' = m_x^\text{Ia}\frac{N_\text{Ia}}{M_\star} 
\label{eq:y_x_ia} 
\end{equation} 
where~$m_x^\text{Ia}$ is the average mass of the element~$x$ produced in a 
single SN Ia event and the integral evaluates to the mean number of SN Ia 
events~$N_\text{Ia}$ per mass of stars formed~$M_\star$. 
\vice~forces~$t_\text{max}$~= 15 Gyr always, though provided one is consistent 
with equations~\refp{eq:mdot_ia} and~\refp{eq:y_x_ia}, the results are 
independent of~$t_\text{max}$ because the integrals cancel. 
Extending this formalism to multi-zone models is simple; rather than an 
integral over the star formation history of a given annulus, the rate becomes 
a summation over all stellar populations that are in a given zone at some time: 
\begin{equation} 
\dot{M}_x^\text{Ia} = y_x^\text{Ia} \ddfrac{
	\sum_i M_i R_\text{Ia}(\tau_i) 
}{
	\int_{t_\text{D}}^{t_\text{max}} R_\text{Ia}(t')dt' 
} 
\label{eq:mdot_ia_multizone} 
\end{equation} 
where~$M_i$~and~$\tau_i$~are the mass and age of the~$i$'th stellar population, 
respectively. 
\par 
Initially, we adopted~$y_\text{O}^\text{Ia}$~= 0 and~$y_\text{Fe}^\text{Ia}$~= 
0.0017 from~\citet{Johnson2020}, who in turn adopt these values from 
\citet{Weinberg2017}. 
However, we found that the e-folding timescales of star formation in our models 
are sufficiently long (see discussion in~\S~\ref{sec:methods:sfhs}) that our 
fiducial, inside-out SFH model predicted [O/Fe]~$\approx$~+0.05 for young 
stars. 
We therefore multiply~$y_\text{Fe}^\text{Ia}$~by~$10^{0.1}$, adopting 
$y_\text{Fe}^\text{Ia}$~= 0.00214 so that our fiducial model predicts a 
late-time [O/Fe] ratio in better agreement with observations. 
Changes at this level are within the uncertainties of SN Ia rates and yields, 
so we consider it reasonable to adjust the yields empirically to reproduce 
observed abundances. 
\par 
Our IMF-averaged O and Fe yields are based on a~\citet{Kroupa2001} IMF combined 
with supernova nucleosynthesis models in which most~$M > 8~\msun$ stars explode 
as a CCSN~\citep[e.g.][]{Chieffi2004, Chieffi2013}. 
Recent studies have strongly suggested that many high mass stars instead 
collapse directly to a black hole (see theoretical discussion by, e.g., 
\citealp{Pejcha2015, Sukhbold2016, Ertl2016}, and observational evidence from 
\citealp*{Gerke2015};~\citealp{Adams2017, Basinger2020}). 
Our yields would be lower in a scenario with extensive black hole formation 
and/or a steeper high mass IMF (Griffith et al. 2021). 
These effects could also introduce a metallicity dependence if the landscape of 
black hole formation changes with metallicity. 
The strong increase of the specific SN Ia rate seen at low galaxy masses 
\citep{Brown2019} provides circumstantial evidence of a higher~$R_\text{Ia}$ 
normalization at low metallicity; the stellar close binary fraction also 
depends on metallicity (\citealp{Badenes2018};~\citealp*{Moe2019}). 
However, there is presently no solid empirical basis for adopting metallicity 
dependent O and Fe yields over the range relevant to this paper (roughly 
-0.8~$\leq$~\feh~$\leq$~0.4), and some empirical evidence that any metallicity 
trends in this range are weak~\citep{Weinberg2019}. 
\vice~has capabilities to compute IMF-averaged yields for a flexible 
description of the massive star explodability landscape, as described by 
Griffith et al. (2021) and the~\vice~documentation, but we do not use this 
methodology here. 
We expect that most of our results would be largely unchanged if we were to 
lower all three yields ($y_\text{O}^\text{CC}$, $y_\text{Fe}^\text{CC}$, 
$y_\text{Fe}^\text{Ia}$) by the same factor and adjust our adopted outflow 
mass loading prescription to compensate (see below). 
\par 
Both AGB star enrichment and the recycling of previously produced metals in 
this paper proceed as they did in~\citet{Johnson2020}, with the caveat that the 
mass is added to the ring that a stellar population is in at a given time, 
which may or may not be the ring it was born in. 
Recycling proceeds according to the~\citet{Kalirai2008} initial-remnant mass 
relation assuming a~\citet{Kroupa2001} IMF and a mass-lifetime relationship of 
$\tau = 1.1\tau_\odot(M/M_\odot)^{-3.5}$, where~$\tau_\odot$~= 10 Gyr is the 
main sequence lifetime of the sun and the factor of 1.1 accounts for the 
post-main sequence lifetime. 
\vice~includes AGB enrichment in all models; here we adopt the net yields 
sampled on a table of stellar initial mass and metallicity from the FRUITY 
database \citep{Cristallo2011}. 
However, the AGB star yields of O and Fe are tiny compared to their 
supernova yields, so they have negligible impact on the results presented in 
this paper.

\subsection{Outflows} 
\label{sec:methods:outflows} 
\citet{Weinberg2017} demonstrate that, to first order, the nucleosynthetic 
yields of a given element and the strength of outflowing winds determine the 
late-time equilibrium abundance in the ISM, with a secondary dependence on the 
SFH. 
We retain their characterization of outflows here, in terms of a mass-loading 
factor~$\eta$~describing the ratio of the mass outflow to the SFR: 
\begin{equation} 
\eta \equiv \frac{\dot{M}_\text{out}}{\dot{M}_\star}. 
\end{equation} 
We adopt a scaling of~$\eta$~with~$\rgal$~such that the late-time 
equilibrium abundance as a function of radius describes a metallicity 
gradient in agreement with observations. 
For a constant SFR, the equilibrium abundance of an~$\alpha$-element, produced 
by CCSNe with a metallicity-independent yield, is given by 
\begin{equation} 
Z_{\alpha,\text{eq}} = \frac{y_\alpha^\text{CC}}{1 + \eta(\rgal) - r}, 
\end{equation} 
where~$r$~is the recycling parameter ($\approx$0.4 for the sake of this scaling 
with a~\citealp{Kroupa2001} IMF; see discussion in~\S~2.2 
of \citealp{Weinberg2017}). Solving for~$\eta(\rgal)$ yields 
\begin{equation} 
\eta(\rgal) = \frac{y_\alpha^\text{CC}}{Z_{\alpha,\text{eq}}} + r - 1 = 
\frac{y_\alpha^\text{CC}}{Z_{\alpha,\odot}}10^{-\text{mode([$\alpha$/H])}
(\rgal)} + r - 1, 
\end{equation} 
where mode([$\alpha$/H])($\rgal$) denotes the mode of the stellar 
[$\alpha$/H] distribution at a radius~$\rgal$, which we assume to correspond 
to the equilibrium abundance at that radius. 
Recent studies of the disc metallicity gradient with APOGEE find values of 
-0.09 dex/kpc to -0.06 dex/kpc~\citep[e.g.][]{Frinchaboy2013, Hayden2014, 
Weinberg2019}, consistent with earlier studies. 
Here we adopt a slope of -0.08 dex/kpc and set mode([$\alpha$/H]) to be 
$\sim$+0.3 at~$\rgal$ = 4 kpc, producing mode([$\alpha$/H])~$\approx$ 0 at 
$\rgal$ = 7 - 9 kpc. This results in the following form for~$\eta$ as a 
function of Galactocentric radius: 
\begin{equation} 
\eta(\rgal) = \frac{y_\alpha^\text{CC}}{Z_{\alpha,\odot}} 
10^{(-0.08\text{ kpc}^{-1})(\rgal - 4\text{ kpc}) + 0.3} + r - 1, 
\label{eq:eta_rgal} 
\end{equation} 
where we adopt our CCSN yield of O for~$y_\alpha^\text{CC}$ and the solar 
photospheric abundance of O of~$Z_{\text{O},\odot}$ = 0.00572 based on 
\citet{Asplund2009}. 
We plot this adopted scaling in the top panel of Fig.~\ref{fig:eta_tau_sfh}, 
highlighting a value of~$\sim$2.15 for the solar circle with a red dotted line. 
In Fig.~\ref{fig:metallicity_gradient} below, we show that our full model 
including a time-dependent SFH and radial migration produces stellar and gas 
phase gradients similar but not identical to those of equation 
\refp{eq:eta_rgal}. 
In Figs.~\ref{fig:mdf_3panel_fe} and~\ref{fig:mdf_3panel_o} below, we show that 
the model achieves qualitative agreement with the metallicity gradient observed 
by APOGEE.

% fig 3 
\begin{figure} 
\centering 
\includegraphics[scale = 0.45]{eta_tau_sfh.pdf} 
\caption{\textbf{Top}: Our implemented scaling of the mass loading factor 
$\eta$~with Galactocentric radius (black) as defined by equation 
\refp{eq:eta_rgal}.~\textbf{Bottom}: The e-folding timescales of the star 
formation histories of our model galaxies (black). These values come from a 
fit to the~$\Sigma_\star$-age relation in bins of~$R/R_\text{e}$~for 
$10^{10.5}$~-~$10^{11}$~\msun~Sa/Sb Hubble type spiral galaxies as reported by 
\citet[][see discussion in~\S~\ref{sec:methods:sfhs}]{Sanchez2020}. The 
horizontal and vertical red dashed lines in both panels highlight a mass 
loading factor of~$\eta \approx$~2.15 and a star formation timescale of 
$\tau_\text{sfh} \approx$~15 Gyr at an assumed radius of the sun of 
$R_\odot$ = 8 kpc. } 
\label{fig:eta_tau_sfh} 
\end{figure}

\subsection{Star Formation Histories} 
\label{sec:methods:sfhs} 
\vice~computes models in either ``infall'', ``star formation'', or ``gas'' 
mode, referring to which component of the evolutionary history the user has 
specified. 
The starburst models of~\citet{Johnson2020} ran in infall mode, 
meaning that the gas infall rate is specified and the SFR follows from the gas 
surface density and adopted star formation law. 
Here we run~\vice~in star formation mode so that we achieve a specified form of 
the SFHs in our models. 
In Appendix~\ref{sec:normalize_sfh}, we explain how we normalize the parameters 
of our SFHs to produce a realistic model Galaxy at the present day. 
In short, we take a unitless description of the time-dependence of the SFH at a 
given Galactocentric radius, denoted~$f(t|\rgal)$, and a unitless description 
of the present day stellar surface density gradient, denoted~$g(\rgal)$. 
We integrate~$f(t|\rgal)$ with time for each annulus, assuming~$\rgal$ to 
correspond to the centre of the zone, and attach a prefactor to 
$f(t|\rgal)$ in each annulus such that the desired gradient is achieved 
with a total stellar mass similar to the Milky Way. 
This procedure neglects the impact of radial migration, assuming that it does 
not significantly alter the form of~$g(\rgal)$. 
We demonstrate that this assumption holds 
in~\S~\ref{sec:methods:surface_density_gradient}, in which we also detail our 
adopted form of~$g(\rgal)$. 
The equation derived in Appendix~\ref{sec:normalize_sfh} can be used to 
calculate these prefactors for alternative models of Milky Way-like galaxies. 
\par 
In the present paper, we consider four forms of the SFH, which we dub 
``constant'', ``inside-out'', ``late-burst'', and ``outer-burst''. 
They are defined as follows: 
\begin{itemize} 
	\item \textbf{Constant}: The SFH at a given radius is time-independent, 
	\begin{equation} 
	f_\text{C}(t|\rgal) = 1. 
	\label{eq:constant_sfh} 
	\end{equation} 
	This case is of theoretical interest because it quantifies the effect of 
	stellar migration while removing the impact of a time-dependent SFH.

	\item \textbf{Inside-Out}: This is our fiducial SFH, 
	\begin{equation} 
	f_\text{IO}(t|\rgal) = (1 - e^{-t / \tau_\text{rise}}) 
	e^{-t / \tau_\text{sfh}}. 
	\label{eq:insideout_sfh} 
	\end{equation} 
	We adopt this mathematical form over the somewhat more common 
	$te^{-t/\tau_\text{sfh}}$ because it allows separate control over the 
	rising and falling phase of the SFH. 
	Equation~\refp{eq:insideout_sfh} has a maximum near~$\tau_\text{rise}$, 
	which in this paper we set to 2 Gyr at all radii. 
	This form produces a peak in star formation at lookback times of~$\sim$11 
	Gyr, roughly corresponding to a redsfhit of~$z \approx$ 2.5. 
	We discuss the choice of~$\tau_\text{sfh}$ below.

	\item \textbf{Late-Burst}: In this model, the inside-out SFH is modified to 
	exhibit a recent, slow ``burst'' in star formation described by a Gaussian 
	in time: 
	\begin{equation} 
	f_\text{LB}(t|\rgal) = f_\text{IO}(t|\rgal) 
	\left(1 + A_be^{-(t - t_b)^2/2\sigma_b^2}\right), 
	\label{eq:lateburst_sfh} 
	\end{equation} 
	where $A_b$ is a dimensionless parameter describing the strength of the 
	starburst,~$t_b$ is the time of the local maximum in the SFH during the 
	burst, and~$\sigma_b$ is the width of the Gaussian describing it. 
	To approximate the findings of~\citet{Mor2019} and~\citet{Isern2019}, we 
	adopt~$A_b$ = 1.5,~$t_b$ = 11.2 Gyr, and~$\sigma_b$ = 1 Gyr, finding 
	that~$A_b$ = 1.5 with a declining~$f_\text{IO}(t|\rgal)$ produces a local 
	maximum SFR that is a factor of~$\sim$2 larger than the preceding local 
	minimum.

	\item \textbf{Outer-Burst}: A variation of the late-burst model in which 
	only zones at~$\rgal \geq$~6 kpc experience the starburst, with inner 
	regions following the inside-out SFH. 
	Because the empirical evidence for elevated recent star formation comes 
	from local observations, it is useful to investigate the case where it is 
	confined to the outer Galaxy. 
	In their hydrodynamical simulation of a Milky Way-like galaxy, 
	\citet{Vincenzo2020} find that satellite perturbations enhance gas 
	accretion preferentially in the outer regions. 
\end{itemize} 
The inside-out model is our fiducial choice, and it is the model shown in 
figures unless otherwise specified. 
The constant SFR model allows us to investigate the impact of migration when 
the time-dependence of the SFH is removed, and the two burst models allow us to 
explore the consequences of elevated recent star formation supported by some 
recent data. 
More complex scenarios with multiple bursts induced by repeated satellite 
passages~\citep[e.g.][]{Lian2020a, Lian2020b, RuizLara2020, Sysoliatina2021} 
can be modeled easily in~\vice, but we do not explore them here. 
\par 
We derive the~$\tau_\text{sfh}-\rgal$ relation from the data of 
\citet{Sanchez2020}, who presents the stellar surface density~$\Sigma_\star$ as 
a function of age in bins of~$R/R_\text{e}$ for MaNGA 
galaxies~\citep{Bundy2015}, where $R_\text{e}$ is the half-light radius. 
Here we take the~$M_\star = 10^{10.5} - 10^{11}~\msun$~bin for Sa/Sb spirals 
and simultaneously fit the normalization and e-folding timescale 
$\tau_\text{sfh}$ of our~$f_\text{IO}(t|\rgal)$ form to the data. 
Although the normalization is irrelevant to our models and determined via the 
method outlined in Appendix~\ref{sec:normalize_sfh}, we adopt the resulting 
$\tau_\text{sfh}-\rgal$ relation in our models. 
Our adopted stellar surface density gradient 
(see~\S~\ref{sec:methods:surface_density_gradient}) implies a present-day 
half-mass radius near 4 kpc. 
The findings of~\citet{Garcia-Benito2017} and~\citet{GonzalezDelgado2014} 
suggest that half-light radii are marginally larger than half-mass radii. 
Based on equation (4) of~\citet{GonzalezDelgado2014} relating the two for 
circular apertures, we expect our model Galaxy to have a 
half-light radius near 5 kpc. 
We therefore adopt~$R_\text{e}$ = 5 kpc to convert the 
$\tau_\text{sfh}-\rgal/R_\text{e}$ relation resulting from our fit to the 
\citet{Sanchez2020} data into a~$\tau_\text{sfh}-\rgal$ relation. 
\par 
We illustrate this relationship in the bottom panel of Fig. 
\ref{fig:eta_tau_sfh}. 
The resulting timescales are long, particularly for the outer Galaxy. 
With a red dotted line, we highlight a value of~$\tau_\text{sfh} \approx$~15 
Gyr at an assumed orbital radius of the sun of $R_\odot$ = 8 kpc. 
The long timescales reflect the fact that the 
$\Sigma_\star(\tau_\text{lookback})$ profiles in Fig. 11 of~\citet{Sanchez2020} 
are fairly flat. 
For comparison, we have also considered the assumption that the Galactic SFH 
may have resembled the cosmic SFH by running models with e-folding timescales 
of a~$\sim$few Gyr~\citep[e.g.][]{Madau2014}. 
We find similar results in these cases, suggesting that our qualitative 
conclusions are not sensitive to the exact values of~$\tau_\text{sfh}$.

% fig 4 
\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{evol.pdf} 
\caption{The surface densities of star formation~$\dot{\Sigma}_\star$ (top 
row), infall $\dot{\Sigma}_\text{in}$ (middle row), and gas~$\Sigma_\text{g}$ 
(bottom row) as functions of simulation time for our four fiducial SFHs: 
constant (far left), inside-out (left middle), late-burst (right middle), and 
outer-burst (far right). We plot curves for the rings whose inner radii are 
3 kpc (grey), 5 kpc (black), 7 kpc (red), 9 kpc (yellow), 11 kpc (green), 13 
kpc (blue), and 15 kpc (purple) (see equations~\refp{eq:constant_sfh}, 
\refp{eq:insideout_sfh}, and~\refp{eq:lateburst_sfh} for the mathematical 
definition of each SFH). 
}
\label{fig:evol} 
\end{figure*}

We plot the resulting SFHs of our models in the top row of Fig.~\ref{fig:evol} 
for a handful of radii. 
Because of the long~$\tau_\text{sfh}$, the SFR at most radii has fallen only 
modestly from its 2 Gyr peak in the inside-out model. 
At all timesteps, the gas supply is known via the star formation efficiency 
timescale~$\tau_\star$ (see~\S~\ref{sec:methods:sfe}), which is illustrated in 
the bottom row of Fig.~\ref{fig:evol}. 
\vice~automatically calculates the implied infall rate by comparing the amount 
of gas lost to outflows and star formation in a given timestep to that which is 
required to sustain the user-specified level of star formation at the next 
timestep; we assume the infalling gas to be of zero metallicity at all times. 
This quantity is shown in the middle row of Fig.~\ref{fig:evol}.

\subsection{Star Formation Efficiency} 
\label{sec:methods:sfe} 
The term ``star formation efficiency'' (SFE) is somewhat overloaded in the 
literature. 
In the star formation and feedback community, it usually refers to the fraction 
of a molecular cloud's mass that will eventually be converted into stars. 
In the chemical evolution literature, however, it typically refers to the 
inverse timescale relating the SFR within some star forming reservoir to the 
mass of gas in that region: 
$\tau_\star \equiv \Sigma_\text{g}/\dot{\Sigma}_\star$. 
High (Low) values of~$\tau_\star$ indicate slow (fast) conversion of gas and 
thus low (high) SFE; when we refer to SFE here, we mean the definition based on 
this timescale. 
In the star formation and feedback literature,~$\tau_\star$ is sometimes 
referred to as the ``depletion time'', though here we follow the terminology of 
\citet{Weinberg2017} who call it the ``star formation efficiency timescale.'' 
\par 
Based on the findings of~\citet{Kennicutt1998}, it is common practice in the 
chemical evolution literature to adopt a single power-law describing the 
relationship between the surface densities of gas and star formation 
$\Sigma_\text{g}$ and $\dot{\Sigma}_\star$, often referred to as the star 
formation law or the Kennicutt-Schmidt relation: 
\begin{equation} 
\dot{\Sigma}_\star \propto \Sigma_\text{g}^N. 
\end{equation} 
\citet{Kennicutt1998} finds~$N = 1.4 \pm 0.15$ relating the total 
$\dot{\Sigma}_\star$~and~$\Sigma_\text{g}$~within the disc across a sample of 
quiescent spiral galaxies and infrared and circumnuclear starbursts. 
However, recent studies have found evidence that much of the observed scatter 
in this relation is physical in origin~\citep{delosReyes2019} and that there 
are significant breaks in both the power-law index and zero-points 
\citep{Kennicutt2021}. 
Some of the uncertainty surrounding the details of the star formation law is a 
consequence of the ongoing debate about the CO-to-H$_2$ conversion factor 
(\citealp{Kennicutt2012};~\citealp*{Liu2015}). 
Although~\citet{Ellison2021} demonstrate that there are significant 
galaxy-to-galaxy variations in the star formation law,~\citet{delosReyes2019} 
argue that the mean trend is still a reasonable recipe for Galaxy evolution 
models. 
However, for our purposes we also need the dependence of~$\dot{\Sigma}_\star$ 
on~$\Sigma_\text{g}$ within a galaxy. 
\par 
\citet{Krumholz2018a} compare theoretically motivated star formation laws to 
the observations of~\citet{Bigiel2010} and~\citet{Leroy2013} (see their Fig. 2). 
We find that the following by-eye fit to the power-law index~$N$~is a 
reasonable description of the aggregate data: 
\begin{equation} 
N = \begin{cases} 
1.0 & (\Sigma_\text{g} \geq \Sigma_{\text{g},2})~, \\ 
3.6 & (\Sigma_{\text{g},1} \leq \Sigma_\text{g} \leq \Sigma_{\text{g},2})~, \\ 
1.7 & (\Sigma_\text{g} \leq \Sigma_{\text{g},1})~, 
\end{cases} 
\label{eq:sf_law_indeces} 
\end{equation} 
where~$\Sigma_{\text{g},1} = 5\times10^6$~\msun~\persqkpc~and 
$\Sigma_{\text{g},2} = 2\times10^7$~\msun~\persqkpc. 
The apparent linearity of the relationship above 
$\sim2\times10^7$~\msun~\persqkpc~suggests that in this regime, star formation 
proceeds at the highest efficiency, and that 
$\tau_\star \equiv \Sigma_\text{g}/\dot{\Sigma}_\star$~= constant. 
The observational results of~\citet{Leroy2013} and~\citet{Kennicutt2021} would 
suggest that these are the surface densities at which the molecular fraction 
$f_\text{mol} = M_{\text{H}_2} / (M_{\text{H}_2} + M_\text{HI}) \approx$~1. 
We therefore adopt the assumption that above 
$\Sigma_\text{g} = 2\times10^7$~\msun~\persqkpc,~$\tau_\star$ reaches its 
minimum value, and increases with decreasing~$f_\text{mol}$. 
We denote this value as~$\tau_\text{mol}$, the value of~$\tau_\star$ for a gas 
reservoir with~$f_\text{mol}$~= 1. 
This identification, combined with our three-component power-law index~$N$ 
results in the following final form for our adopted star formation law: 
\begin{equation} 
\dot{\Sigma}_\star = \begin{cases} 
\Sigma_\text{g} \tau_\text{mol}^{-1} & 
(\Sigma_\text{g} \geq \Sigma_{\text{g},2})~, 
\\ 
\Sigma_\text{g} \tau_\text{mol}^{-1} \left(\frac{
	\Sigma_\text{g}
}{
	\Sigma_{\text{g},2} 
}\right)^{2.6} & 
(\Sigma_{\text{g},1} \leq \Sigma_\text{g} \leq \Sigma_{\text{g},2})~, 
\\ 
\Sigma_\text{g} \tau_\text{mol}^{-1} \left(\frac{
	\Sigma_{\text{g},1} 
}{
	\Sigma_{\text{g},2} 
}\right)^{2.6}\left(\frac{
	\Sigma_\text{g}
}{
	\Sigma_{\text{g},1} 
}\right)^{0.7} & 
(\Sigma_\text{g} \leq \Sigma_{\text{g},1})~. 
\end{cases} 
\label{eq:sf_law} 
\end{equation} 
We choose the power-law indices such that this formalism is consistent 
with equation~\refp{eq:sf_law_indeces}, and prefactors are added to ensure 
piece-wise continuity. 
In implementation,~\vice~requires the~$\tau_\star-\dot{\Sigma}_\star$ relation 
when running in star formation mode and the~$\tau_\star-\Sigma_\text{g}$ 
relation when running in infall and gas modes. 
Both follow algebraically from this relationship given the substitution 
$\tau_\star \equiv \Sigma_\text{g} / \dot{\Sigma}_\star$. 
\par 
Based on the observed Kennicutt-Schmidt relation at different redshifts, 
\citet{Tacconi2018} suggest that~$\tau_\text{mol}$ should scale with redshift 
$z$ and with the deviation from the star forming main sequence~$\delta$MS via 
$\tau_\text{mol} \propto (1 + z)^{-0.6}\delta\text{MS}^{-0.44}$. 
We do not account for the effect of~$\delta$MS in our models, but we do 
incorporate the redshift dependence. 
For redshifts of~$z \lesssim$~3, encompassing most of the timesteps in 
our models, a reasonable approximation to the~$t - z$ relation assuming 
typical~$\Lambda$CDM cosmology is given by: 
\begin{equation} 
\frac{t}{t_0} \approx (1 + z)^{-5/4}, 
\end{equation} 
where~$t_0$ is the present-day age of the universe, and~$t$ is not simulation 
time but the age of the universe. Plugging this relation into the 
\citet{Tacconi2018} scaling yields 
\begin{equation} 
\tau_\text{mol} = \tau_{\text{mol},0}(t/t_0)^{12/25} \approx 
\tau_{\text{mol},0}(t/t_0)^{1/2}, 
\end{equation} 
where~$\tau_{\text{mol},0}$ is simply~$\tau_\text{mol}$ at the present day. We 
generalize this formula to the following form: 
\begin{equation} 
\tau_\text{mol} = \tau_{\text{mol},0}(t/t_0)^\gamma 
\label{eq:tau_mol}
\end{equation} 
In this paper we present models which adopt~$\tau_{\text{mol},0}$ = 2 Gyr 
\citep{Leroy2008, Leroy2013, Tacconi2018} and~$\gamma$ = 1/2 based on this 
argument. 
We have also run simulations witht~$\tau_{\text{mol},0}$ = 1 
Gyr and with~$\gamma$ = 0 (a time-independent~$\tau_\text{mol}$), as well as 
combinations of the two, and found similar results. 
In all timesteps and annnuli,~\vice~infers~$\Sigma_\text{g}$ from 
$\dot{\Sigma}_\star$ given our equations~\refp{eq:sf_law} and~\refp{eq:tau_mol}.

% fig 5 
\begin{figure} 
\centering 
\includegraphics[scale = 0.45]{sfe.pdf} 
\caption{The star formation efficiency timescale~$\tau_\star$ as a function of 
Galactocentric radius at simulation times of 2 Gyr (red), 4 Gyr (yellow), 
6 Gyr (green), 8 Gyr (blue), 10 Gyr (purple), and 13.2 Gyr (the present day, 
black) predicted by our fiducial model. } 
\label{fig:sfe} 
\end{figure}

In Fig.~\ref{fig:sfe}, we plot~$\tau_\star$ as a function of~$\rgal$ at 
six different time stamps predicted by our fiducial, inside-out SFH model. 
At~$\rgal \lesssim$ 6 kpc,~$\tau_\star$ is near~$\tau_\text{mol}$ at all 
times, implying a molecular fraction of unity at these radii. 
Although this prediction is likely unrealistic because 21-cm line observations 
suggest the presence of neutral hydrogen as close to the Galactic centre as 
several hundred pc~\citep{Kalberla2009}, we find in practice that changing our 
assumptions about the star formation law does not impact our conclusions. 
In exploratory work for this paper, we investigated purely linear, purely 
power-law, and broken power-law characterizations, finding similar predictions 
in all cases. 
In general we find that the detailed form of the SFH, and to some extent the 
time-dependence of radial migration, exert much greater power in establishing 
the model predictions than does the star formation law. 
Nonetheless it is an interesting puzzle that a 
$\dot{\Sigma}_\star - \Sigma_\text{g}$ relation informed by the observed 
population-averaged trends and the normalization of SFHs implied by the stellar 
mass of the Milky Way predicts results in tension with the observed HI 
distribution. 
Because the star formation law has minimal impact on our results, we do not 
pursue this question further here.

\subsection{Surface Density Gradient} 
\label{sec:methods:surface_density_gradient}

As discussed in~\S~\ref{sec:methods:sfhs}, Appendix~\ref{sec:normalize_sfh} 
presents the recipe by which we select a unitless function describing the 
stellar surface density gradient~$g(\rgal)$. 
In setting the normalization, our model ensures that the integral of~$g(\rgal)$ 
over the surface area of the disc predicts a total stellar mass in agreement 
with that observed for the Milky Way. 
For this value, we adopt~$M_\star^\text{MW} = 5.17~\times~10^{10}~\msun$ from 
\citet[][$\pm 1.11\times10^{10}~\msun$]{Licquia2015}. 
This is the total disc mass only; when the bulge is included, the total 
becomes~$(6.08~\pm~1.17)~\times~10^{10}~\msun$. 
Since we are modeling only the disc populations here, we omit the contribution 
from the bulge to the total mass budget. 
% For this value, we adopt 
% $M_\star^\text{MW} = (5.17 \pm 1.11)\times10^{10}$~\msun~\citep{Licquia2015}. 
% This is the total disc mass of the Galaxy;~\citet{Licquia2015} report 
% $(6.08 \pm 1.17)\times10^{10}~\msun$~when the bulge is considered. 
% Since we are modeling only the disc populations here, we omit the contribution 
% the bulge would have to the total mass budget. 
% This is the total stellar mass of the Galaxy, including the bulge; 
% \citet{Licquia2015} report~$(5.17 \pm 1.11)\times10^{10}$~\msun~as the mass of 
% the disc alone. 
% Although we are not modeling the bulge here, our model extends to~$\rgal$ = 0 
% and our sample of candidate analogue star particles from~\hsim includes those 
% with bulge-like kinematics. 
\par 
We adopt a double exponential form for~$g(\rgal)$, describing the thin and 
thick disc components of the Galaxy: 
\begin{equation} 
g(\rgal) = e^{-\rgal/R_t} + \frac{\Sigma_T}{\Sigma_t} 
e^{-\rgal/R_T}~, 
\label{eq:gradient} 
\end{equation} 
where~$R_t$~and~$R_T$~are the scale radii of the thin and thick discs, 
respectively, and~$\Sigma_T/\Sigma_t$~is the ratio of their surface densities 
at~$\rgal$~= 0. 
We adopt~$R_t$~= 2.5 kpc,~$R_T$~= 2.0 kpc, and~$\Sigma_T/\Sigma_t$~= 0.27 based 
on the findings of~\citet{Bland-Hawthorn2016}. 
We plot the single exponential forms of each disc component as dotted black 
lines in Fig.~\ref{fig:surface_density}, with the solid black line denoting the 
sum of the two.

% fig 6 
\begin{figure} 
\centering 
\includegraphics[scale = 0.45]{surface_density_gradient.pdf} 
\caption{The surface density of gas (blue) and stars (red) as predicted by our 
fiducial model. The dotted black lines denote thin and thick disc 
profiles with scale lengths of~$R_t$ = 2.5 kpc and~$R_T$ = 2.0 kpc, 
respectively, with a ratio of~$\Sigma_T/\Sigma_t$ = 0.27 at~\rgal~= 0 (i.e. the 
thin disc profile has the higher normalization). 
The solid black line denotes the sum of the two; this is the stellar surface 
density gradient of the Milky Way as reported by~\citet{Bland-Hawthorn2016}, 
renormalized according to our adopted total stellar mass of 
$(5.17 \pm 1.11)\times10^{10}$~\msun~\citep{Licquia2015}. } 
\label{fig:surface_density} 
\end{figure}

We plot the resultant surface density gradients from our fiducial, inside-out 
SFH model in Fig.~\ref{fig:surface_density} as well, with red denoting the 
stellar gradient and the gas in blue. 
The stellar gradient very nearly follows our target gradient (equation 
\ref{eq:gradient}) denoted by the solid black line. 
Stellar migration has not altered the overall form of the gradient, simply 
introducing scatter around the adopted trend. 
Although there are slight enhancements at small~$\rgal$ and deficits at large 
$\rgal$, the agreement is excellent in the regions of the Galaxy where the 
gradient is best constrained observationally. 
The~$\rgal$ > 15.5 kpc populations are composed entirely of stars that 
migrated there, since that is the radius at which we shut off star formation. 
The gas gradient shows a break in the scale radius near~$\rgal \approx$ 
6 kpc. This is a consequence of our adopted star formation law; at 
$\Sigma_\text{g} = 2\times10^7$~\msun~\persqkpc~the relation changes from 
linear at higher densities to~$\dot{\Sigma}_\star \sim \Sigma_\text{g}^{3.6}$ 
at lower densities (see discussion in~\S~\ref{sec:methods:sfe}). 
\par 
Although we adopt the~\citet{Licquia2015} disc stellar mass of the Milky Way 
here, we find similar results when taking a value which differs even by an 
order of magnitude. 
If we used a linear star formation law, then our chemical evolution would be 
independent of the mass normalization as it is in corresponding one-zone 
models (\citealp*{Spitoni2017};~\citealp{Weinberg2017, Belfiore2019}). 
The mass normalization enters our calculation because it affects the transition 
between the linear and non-linear regimes of our star formation law 
(equation~\ref{eq:sf_law}), but the impact on abundance evolution is minimal.

\subsection{Summary} 
\label{sec:methods:summary} 
In summary, our fiducial model has an inside-out SFH with e-folding timescales 
derived from the observations of~\citet[][see discussion 
in~\S~\ref{sec:methods:sfhs}]{Sanchez2020}. 
Radial migration proceeds in a manner in which our model stellar populations 
have a change in radius~$\Delta \rgal$ informed from the~\texttt{h277} 
hydrodynamical simulation~\citep[][see discussion 
in~\S~\ref{sec:methods:h277}]{Christensen2012, Zolotov2012, Loebman2012, 
Loebman2014, Brooks2014}. 
In the baseline model, stars move to their final radius with a 
$\sqrt{\text{age}}$~dependence~\citep[][see discussion in 
\ref{sec:methods:migration}]{Frankel2018,Frankel2020}. 
Using~\vice~to calculate abundances for O and Fe in this paper, our supernova 
yields are adopted from~\citet{Johnson2020}, who in turn take these values from 
\citet{Weinberg2017} (see~\S~\ref{sec:methods:yields}). 
Outflows are characterized such that the equilibrium abundance of oxygen under 
a constant SFH follows an abundance gradient in agreement with observational 
results in the Milky Way (see~\S~\ref{sec:methods:outflows}). 
Our star formation law is based on the~\citet{Bigiel2010} and 
\citet{Leroy2013} data presented in comparison with theoretical models in 
\citet[][see~\S~\ref{sec:methods:sfe}]{Krumholz2018a}. 
To describe the stellar surface density gradient, we adopt the two-exponential 
form describing the thin and thick discs from 
\citet[][see~\S~\ref{sec:methods:surface_density_gradient}]{Bland-Hawthorn2016}. 
We adopt the~\citet{Kroupa2001} IMF throughout this paper. 
\par 
Our selection of star particles from~\hsim~yields a sample of 1,751,765 
candidate analogues with disc-like kinematics at the present day (see 
discussion in~\S~\ref{sec:methods:h277}). 
We take~$\Delta\rgal$ = 100 pc as the width of each annulus from~\rgal~= 0 to 
20 kpc and a timestep size of~$\Delta T$ = 10 Myr from~$T$ = 0 to 13.2 Gyr. 
With the resulting 200 zones and 1,321 timesteps (one extra so that age = 0 
stars are included), we let~\vice~form~$n$ = 8 stellar populations per zone per 
timestep, resulting in 2,113,600 total stellar populations with predicted 
masses and abundances. 
We set the SFR to zero beyond~\rgal~= 15.5 kpc; stellar populations 
do form beyond this radius and are part of the computational overhead, but they 
have zero mass and thus do not contribute to the chemical evolution in our 
models. 
This results in 1,627,472 stellar populations with~\textit{non-zero} masses and 
abundances, comparable to the total number of disc particles in our sample 
from~\hsim. 
These simulations run in~$\sim$5 hours on a single core with a 3 GHz 
processor and take up~$\sim$235 MB of disc space per output, including the 
extra data that we record for each stellar population's analogue star particle. 
We have also run variations with~$n$ = 2 stellar populations per 
zone per timestep, finding similar results in all cases. 
\par 
We have run~\vice~for all four of our SFHs, all four migration 
models, and all four variations in~$\tau_\text{mol}$ noted 
in~\S~\ref{sec:methods:sfe} --- a total of 64 simulations, as well as a variety 
of other test cases. 
For many of our results, only the SFH variations have a substantial impact. 
We discuss the impact of migration or~$\tau_\text{mol}$ variations where they 
are relevant.

\end{document}

### 2021-08-04 chemev/MWbimodality/paper/draft2/ms.tex
migration paper referee response

--- 2021-08-04 chemev/MWbimodality/paper/draft1/draft1.tex
@@
 \usepackage{amsmath}
-\usepackage{amssymb}
+% \usepackage{amssymb}
 \usepackage{mathtools}
@@
 \usepackage[toc, page]{appendix} 
+\usepackage{subfiles} 
+% \voffset-0.6in 
+% \usepackage[margin = 0.5in]{geometry} 
+\usepackage{geometry} 
+\geometry{margin=0.6in} 
+% \addtolength{\topmargin}{-0.6in} 
 % \hypersetup{draft} 
 % \linespread{1.8} 
-\hypersetup{ 
+\hypersetup{ % all blue links 
 	colorlinks		= true, 
@@
 
+% recurring expressions 
 \newcommand{\ddfrac}[2]{\frac{\displaystyle #1}{\displaystyle #2}} 
@@
 \newcommand{\persqkpc}{\ensuremath{\text{kpc}^{-2}}} 
+\newcommand{\rgal}{\ensuremath{R_\text{gal}}} 
+\newcommand{\absz}{\ensuremath{\left|z\right|}} 
+\newcommand{\afe}{[$\alpha$/Fe]} 
+\newcommand{\ofe}{[O/Fe]} 
+\newcommand{\feh}{[Fe/H]} 
+\newcommand{\oh}{[O/H]} 
+\newcommand{\hsim}{\texttt{h277}} 
+\newcommand{\vice}{\texttt{VICE}}
+
+% control over bibtex's alphabetizing 
 \providecommand{\noopsort}[1]{}
-\graphicspath{ {../plots/} }
+
+% figures for the paper in here 
+% \graphicspath{ {../plots/} }
 
@@
 
-\author[J.W. Johnson et al.]{
-	James W. Johnson,$^{1}$\thanks{Contanct e-mail: \href{mailto:
+\author[J.W. Johnson et al.]{James W. Johnson,$^{1}$\thanks{
+	Contanct e-mail: \href{mailto:
 	johnson.7419@osu.edu}{johnson.7419@osu.edu}} 
 	David H. Weinberg,$^{1, 2, 3}$ 
-	Fiorenzo Vincenzo,$^{2}$ 
+	Fiorenzo Vincenzo,$^{1, 2}$ 
 	Jonathan C. Bird,$^{4}$ 
@@
 	Sarah R. Loebman,$^{5}$ 
-	Alyson Brooks,$^{6}$ 
+	Alyson M. Brooks,$^{6}$ 
 	Thomas R. Quinn,$^{7}$ 
@@
 	\newauthor 
-	et al.?
-	\\
+	and Emily J. Griffith$^{1}$ 
+	\\ \null \\ 
 	$^{1}$ Department of Astronomy, The Ohio State University, 
@@
 	$^{2}$ Center for Cosmology and Astroparticle Physics (CCAPP), 
-	The Ohio State University, 191 W. Woodruff Ave, Columbus, OH, 43210, USA 
+	The Ohio State University, 191 W. Woodruff Ave., Columbus, OH, 43210, USA 
 	\\ 
@@
 	$^{6}$ Department of Physics \& Astronomy, Rutgers University, 136 
-	Frelinghuysen Rd, Piscataway, NJ, 08854, USA 
+	Frelinghuysen Rd., Piscataway, NJ, 08854, USA 
 	\\ 
-	$^{7}$ Department of Astronomy, University of Washinton, Box 351580, 
+	$^{7}$ Department of Astronomy, University of Washington, Box 351580, 
 	Seattle, WA, 98195, USA 
@@
 \date{Accepted XXX; Received YYY; in original form ZZZ} 
-\pubyear{2020}
+\pubyear{2021}
 
@@
 
-\begin{abstract} 
-We investigate the impact of stellar migration on galactic chemical evolution 
-models, considering a handful of assumptions for the star formation history 
-and time-dependence of radial migration based on a zoom-in, hydrodynamical 
-simulation of galaxy evolution. When stars migrate with a smooth, continuous 
-time dependence, the type Ia supernova rate exhibits significant variability in 
-our models. We demonstrate that this is a means with which young, super-solar 
-[$\alpha$/Fe] in the solar neighbourhood can arise naturally out of inside-out 
-Galaxy growth with stellar migration. We find 
-that the observed age-[$\alpha$/Fe] relation is well-fit by an inside-out star 
-formation history, while the age-[$\alpha$/H] and age-[Fe/H] relations are 
-well-fit by a late starburst model; no one model investigated here fits both 
-simultaneously. Our model successfully reproduces the broad nature of the 
-[$\alpha$/Fe] distribution at fixed [Fe/H] in a given Galactic region; however, 
-an overprediction of the frequency of intermediate [$\alpha$/Fe] stars prevents 
-it from explaining the observed results in detail. This suggests 
-that inside-out galaxy growth combined with stellar migration, even with a late 
-starburst, is not conducive to forming the infamous bimodality as it is 
-observed. We postulate that more dramatic evolutionary scenarios (e.g. a 
-two-infall model) may be necessary to describe the observed results. In 
-conducting this analysis, we developed and made use of newly released features 
-in the \texttt{Versatile Integrator for Chemical Evolution} (\texttt{VICE}) 
-which are built to handle these models under a wide variety of 
-assumptions. \texttt{VICE} is publicly available 
-at~\url{https://pypi.org/project/vice}. 
-\end{abstract}
+\subfile{abstract.tex}
 
@@
 
-\section{Introduction} 
-\label{sec:intro} 
-The orbits of stars are not unchanging. While it has been known for some time 
-that stars undergo radial migration (e.g.~\citealp*{Wielen1996}; 
-\citealp{Roskar2008a,Loebman2011,Minchev2012}), the true impact of this process 
-on galactic chemical evolution (GCE) remains under debate. By mixing stellar 
-populations which formed in Galactic regions with significantly different 
-enrichment histories, in principle the impact could be considerable. While some 
-authors argue that radial migration has only a small impact on GCE 
-(e.g.~\citealp*{Kubryk2013};~\citealp{Khoperskov2021}), there are others who 
-argue the contrary (e.g.~\citealp{Schoenrich2009};~\citealp*{Sharma2020}). 
-Aside from the chemodynamical simulations involving N-body integrations 
-\citep[e.g.][]{Kubryk2013, Vincenzo2020, Khoperskov2021}, there are to date 
-only a handful of GCE models that take this effect into account (e.g. 
-\citealp{Matteucci1989, Schoenrich2009};~\citealp*{Minchev2013}; 
-\citealp{Sharma2020}). These studies treat the Milky Way as a series of 
-concentric annuli, each described by a conventional one-zone GCE model with 
-parameters that change from annulus to annulus. In the resultant ``multi-zone'' 
-model, stars and gas can migrate between zones under some prescription to 
-account for time-dependent mixing processes. We retain such methodology in this 
-paper, allowing star particles from a hydrodynamical simulation ran from 
-cosmological initial conditions to inform our implemented mixing process; 
-\citet{Minchev2013} employ a similar technique. With parameters tuned to 
-reproduce certain observed results (e.g. abundance and surface density 
-gradients), we can then assess the model predictions to address the following 
-question: when combining simple, conventional assumptions about the star 
-formation and dynamical histories of the Milky Way, what observed results can 
-be replicated? In the present paper, we focus on the following observables: 
-metallicity distributions functions (MDFs) and abundance gradients, the 
-[$\alpha$/Fe] bimodality, the age-metallicity relation (AMR), and the young, 
-$\alpha$-rich population. 
-\par 
-Stars in the inner regions of the Milky Way tend to be more metal-rich than 
-those found in the outskirts~\citep{Nordstroem2004b, Daflon2009, 
-Frinchaboy2013, Hayden2014}, with slight variations in quantitative results 
-based on what type of stars are considered and what metallicity tracers are 
-analysed. Such behavior is also seen in the gas-phase gradients of 
-low-redshift spirals (see, e.g., the results from the CHAOS project using HII 
-regions;~\citealp{Berg2015, Berg2020}). Using the 12th data release of the 
-Apache Point Observatory Galaxy Evolution Experiment (APOGEE), 
-\citet{Hayden2015} demonstrate that the observed MDF has a metal-rich mode and 
-is skew-negative in the inner galaxy (and conversely, metal-poor and 
-skew-positive in the outer galaxy). These variations in the skewness of the 
-distributions with Galactocentric radius are usually attribute to the migration 
-of metal-rich (metal-poor) stars from smaller (larger) orbital radii. Similar 
-arguments are used by~\citet{Sellwood2002} to interpret the results of 
-\citet{Edvardsson1993} on scatter in the age-metallicity relation observed in 
-the solar neighbourhood. 
-\par 
-Abundance gradients have been the focus of many studies and are quantified 
-rather extensively, but their origin is somewhat up for debate. Applying the 
-analytic models of~\citet*{Weinberg2017}, one could argue that the gradient 
-arises out of variations in the local gas-phase equilibrium abundance as a 
-function of Galactocentric radius. For $\alpha$-elements, the equilibrium 
-abundance is determined to first order by their yield and the efficiency of 
-outflows in removing metals from the star forming reservoir. With a stronger 
-gravitational potential in the inner regions of the Galaxy, one might 
-reasonably expect outflows to be weaker there, thereby increasing the 
-equilibrium abundance.~\citet{Nidever2014} used such an approach to reproduce 
-the width of the [Fe/H] distribution for low-$\alpha$ sequence stars in 
-APOGEE. However, recent chemical evolution models have successfully replicated 
-the gradient with no outflowing winds at all~\citep[e.g.][]{Minchev2013, 
-Spitoni2019a}. This is based on arguments from~\citet{Melioli2008, Melioli2009}, 
-\citet*{Spitoni2008}, and~\citet{Spitoni2009} who studied Galactic fountains 
-using hydrodynamical simulations and numerical models, finding that ejected 
-metals tend to reaccrete to a Galactocentric radius similar to where they 
-originated. With this result, some authors argue that such outflows do not 
-significantly alter the chemical evolution of a Galactic disc, and that instead 
-the gradient arises from the higher normalization of the star formation history 
-in the inner Galaxy. 
-\par 
-Like radial abundance gradients, the reality of the infamous [$\alpha$/Fe] 
-dichotomy is well established (in Gaia-ESO:~\citealp{Recio-Blanco2014, 
-Rojas-Arriagada2017}; in APOGEE:~\citealp{Nidever2014, Hayden2015, 
-Weinberg2019}), but its origin is a topic of intense debate. In general, stars 
-in the Milky Way tend to fall in one of two populations - the roughly solar 
-[Fe/H], solar [$\alpha$/Fe] stars commonly referred to as the low-$\alpha$ 
-sequence, and the high-$\alpha$ sequence made up of sub-solar [Fe/H], 
-super-solar [$\alpha$/Fe] stars. Recently explored with more current data by 
-\citet{Sharma2020}, the notion that it could in principle arise out of radial 
-migration traces back to~\citet{Schoenrich2009}. Applying the analytic models 
-of~\citet{Weinberg2017}, an alternative pathway to such abundance patterns is 
-by an increase in the strength of outflows at late times. Such an evolutionary 
-model would predict a decrease in the equilibrium abundance, forming stars 
-along the low-$\alpha$ sequence. This scenario has not yet been explored in 
-combination with radial migration. 
-\par 
-Other authors argue that more dramatic evolutionary events are necessary to 
-explain the observed results, such as the two-infall model 
-(\citealp*{Chiappini1997, Chiappini2001};~\citealp{Romano2010, Grisoni2017, 
-Noguchi2018, Palla2020, Spitoni2016, Spitoni2018}). 
-In these models, the high-$\alpha$ sequence forms during the Galaxy's initial 
-collapse before feedback processes shut off star formation and expel gas into 
-the Galactic halo. Then, this material can cool and reaccrete along with 
-additional, metal-poor gas from the intergalactic medium, producing a second 
-episode of star formation. The dilution associated with the second accretion 
-event lowers the gas-phase Fe abundance at fixed [$\alpha$/Fe], forming stars 
-along the low-$\alpha$ sequence.~\citet{Spitoni2019a, Spitoni2020} demonstrated 
-using the APOKASC sample~\citep{Pinsonneault2014, SilvaAguirre2018} that such 
-models can explain the abundances observed in the solar annulus. Although 
-\citet{Spitoni2021} recently extended this model to Galactic regions beyond 
-the solar annulus, their model did not account for the mixing of stellar 
-populations between regions. Though they invoke~\citet{Kubryk2013} and 
-\citet{Khoperskov2021} as arguments that it shouldn't impact their results, 
-this nonetheless means that two-infall models have not yet been explored in 
-combination with a treatment for stellar migration. 
-\par 
-Recent cosmological zoom-in simulations have found results qualitatively 
-similar to the arguments of~\citet{Spitoni2019a, Spitoni2020, Spitoni2021}. 
-Using the Auriga simulation suite~\citep{Grand2017},~\citet{Grand2018} 
-demonstrate that an early, accretion induced starburst can populate the 
-high-$\alpha$ sequence, followed by low-level, sustained star formation on the 
-low-$\alpha$ sequence. In this pathway, there is either a rapid transition 
-between the two phases, ensuring the chemical space between the sequences is 
-relatively unpopulated, or low-metallicity gas accretion dilutes the star 
-forming reservoir at fixed [$\alpha$/Fe], populating the low [Fe/H], low 
-[$\alpha$/Fe] portion of the low-$\alpha$ sequence.~\citet{Buck2020b} finds 
-the dilution scenario in the NIHAO simulation suite as well~\citep{Wang2015, 
-Buck2020a}. Although the~\citet{Spitoni2021} model did not implement mixing of 
-stellar populations, these studies using hydrodynamical simulations would 
-suggest pathways qualitatively similar to their two-infall model. 
-\par 
-Contrary to this scenario,~\citet{Clarke2019} demonstrate that star formation 
-proceeded in clumps in an SPH simulation using GASOLINE~\citep*{Wadsley2017}. 
-These clumps self-enrich, forming stars on the high-$\alpha$ sequence due to 
-the perturbed ratio of core collapse to type Ia supernova rates within the 
-star forming regions. The more spatially extended, smooth star formation 
-populates the low-$\alpha$ sequence. Suffice it to say that there are no 
-shortage of models which reproduce the dichotomy, but only those done with 
-hydrodynamical simulations and a handful of others 
-\citep[e.g.][]{Schoenrich2009, Minchev2013, Sharma2020} have taken into account 
-stellar migration. 
-\par 
-Besides abundance gradients and the [$\alpha$/Fe] dichotomy, another 
-observable of interest in this paper is the age-metallicity relation (AMR): the 
-correlation between stellar ages and metallicities. The observed AMR in the 
-solar neighbourhood is known to exhibit considerable intrinsic scatter 
-\citep{Edvardsson1993}; this is usually attributed to radial migration of 
-metal-rich (metal-poor) stars from smaller (larger) Galactocentric radii 
-\citep{Sellwood2002, Haywood2008, Roskar2008b, Schoenrich2009}. 
-In the solar neighbourhood,~\citet{Feuillet2018} reveal that super-solar 
-metallicity stars are statistically older than solar metallicity stars (see 
-their Fig. 3). This contrasts with the predictions of simple one-zone models of 
-GCE where enrichment proceeds alongside star formation, yielding a monotonic 
-AMR~\citep[e.g.][]{Andrews2017, Weinberg2017}. Although one-zone models of 
-starbursts can predict a non-monotonic AMR due to the effect of dilution 
-\citep{Johnson2020}, by construction they do not predict multiple abundances at 
-fixed age as~\citet{Feuillet2018} reports. Using the~\citet{Weinberg2017} 
-analytic models,~\citet{Feuillet2018} argues that this is a consequence of 
-radial migration. For a smooth star formation history, the youngest stars at a 
-given radius will have compositions reflective of the local equilibrium 
-abundance; only stars born at different radii will have different compositions, 
-and only the old ones will have had time to migration to the solar annulus. 
-\par 
-While the presence of old-metal rich stars in the solar annulus is peculiar 
-because they are at odds with one-zone models of chemical evolution, the 
-presence of young, $\alpha$-rich stars is interesting for the same reason. 
-For a smooth star formation history, the delayed nature of type Ia supernovae 
-and their Fe production cause [$\alpha$/Fe] to decrease with time, predicting 
-an age-[$\alpha$/Fe] relation that should increase monotonically with stellar 
-age. However, these~$\sim$few Gyr old stars with [$\alpha$/Fe]~$\approx$~+0.1 - 
-0.2 stars have been found using stellar ages estimated from carbon-to-nitrogen 
-ratios~\citep{Martig2016}, isochrone matching~\citep{Feuillet2018, 
-Feuillet2019}, and with the asterosesmic ages of the original APOKASC catalog 
-\citep{Chiappini2015, SilvaAguirre2018, Pinsonneault2014}. 
-\citet{SilvaAguirre2018} demonstrate that these stars have kinematics similar 
-to the rest of the high-$\alpha$ population, postulating that they may be 
-the consequence of stellar mergers or mass transfer events, making truly old 
-stars simply appear younger. In a sample of 51 young, $\alpha$-enhanced red 
-giant stars,~\citet{Hekker2019} conclude that a portion of these stars have 
-carbon-to-nitrogen ratios consistent with mass transfer events, but that this 
-cannot account for the entire population. This suggests that the remaining 
-stars are either truly young or the result of mergers on the main sequence. 
-If not, then a theoretical explanation for the origin of these stars remains 
-a mystery. 
-\par 
-Alternatively, a recent starburst event could have produced these stars. 
-\citet{Mor2019} infer a factor of~$\sim$2 enhancement in the star formation 
-history (SFH) of the Milky Way~$\sim$2 Gyr ago by comparing population 
-synthesis models to observed stellar luminosity functions and colour-magnitude 
-diagrams from Gaia data~\citep{GaiaDR2}.~\citet{Isern2019} reach similar 
-conclusions by modeling the white dwarf luminosity function in the solar 
-neighbourhood with Gaia parallaxes. Motivated by these results, 
-\citet{Johnson2020} demonstrate using one-zone chemical evolution models that 
-a recent starburst of this nature can produce similarly young,~$\alpha$-rich 
-stars. However, the caveat to this interpretation is that the starburst must be 
-sufficiently localized such that the resultant stellar populations remain 
-outliers from an otherwise monotonically increasing age-[$\alpha$/Fe] relation. 
-\par 
-The impact of such evolutionary histories combined with stellar migration is, 
-to our knowledge, yet unexplored in the literature. A viable model for the 
-detailed enrichment history of the Milky Way would simultaneously explain all 
-of these observed results and their variations between Galactic regions, while 
-also taking into account effects like mixing and observational systematics. On 
-top of this, it must self-consistently calculcate enrichment rates from adopted 
-nucleosynthetic yields and the SFH. In this paper, we aim to 
-assess the extent to which conventional assumptions about the evolutionary 
-history of the Milky Way can account for these results, entertaining a 
-handful of assumptions describing the SFH and time-dependence of stellar 
-radial migration. 
-\par 
-Motivated by the general result that galaxies grow in radius with time 
-(i.e. ``inside-out'' growth;~\citealp{Bird2013}), our base-line model has a 
-star formation history (SFH) whose e-folding timescales grow with 
-Galactocentric radius. Based on the findings of~\citet{Mor2019} and 
-\citet{Isern2019}, we also construct models in which a late starburst is 
-imposed atop the inside-out SFH. In one model, this starburst occurs in all 
-annuli, and in another, loosely informed by the findings of 
-\citet{Vincenzo2020} suggesting such a radial dependence to accretion, it 
-occurs only at~$\geq$6 kpc. We also construct a model in which the SFH is 
-constant at a given Galactocentric radius; these models are interesting from a 
-theoretical perspective in that they quantify the impact of stellar migration 
-without the effects of a time-dependent SFH.
-
-\section{Methods} 
-\label{sec:methods} 
-To fulfill the goals of this paper, we develop and make use of newly released 
-features within the~\texttt{Versatile Integrator for Chemical Evolution} 
-(\texttt{VICE};~\citealp{Johnson2020}). These features are designed to handle 
-models such as these with a wide range of flexibility. We reserve a description 
-of~\texttt{VICE}'s migration algorithm and our simulation parameters for~\S 
-\ref{sec:methods:migration}, first describing our sample of star particles from 
-the hydrodynamical simulation. 
-\par 
-Although we make use of a hydrodynamical 
-simulation to drive stellar migration, we do~\textit{not} make use of its SFH. 
-While our study employs similar techniques as~\citet{Minchev2013}, our differs 
-in this subtle aspect. An alternative to modeling radial migration based on a 
-hydrodynamical simulation is to invoke dynamical arguments; 
-\citet{Schoenrich2009} and~\citet{Sharma2020} take such an approach. This 
-method, however, introduces free parameters which then require fitting to 
-data. An advantage of our technique is that there are no free parameters 
-introduced to the model; furthermore, it's unclear the extent to which the fit 
-biases the model into agreement with parts of the data not involved in the 
-fitting process. The dynamical history of a hydrodynamical simulation is also 
-motivated by first principles in that it models gravitational interactions via 
-an N-body integration. The primary disadvantage of this approach is a 
-consequence of the lack of free parameters - the model is rigid, and we cannot 
-explore slight variations. However, in principle one could compare the 
-predictions made by our chemical evolution models when ran using different 
-hydrodynamical simulations. We emphasize that a hydrodynamical simulation 
-\textit{only} informs the mixing processes in our models, and there is no 
-N-body integration involved in our models aside from that which was used to run 
-the hydrodynamical simulation in the first place.
-
-\subsection{The Hydrodynamical Simulation} 
-\label{sec:methods:h277} 
-In this paper we make use of star particles from the~\texttt{h277} simulation 
-\citep{Christensen2012, Zolotov2012, Loebman2012, Loebman2014, Brooks2014}. 
-Recently employed to study the stellar age-velocity relationship, a synopsis of 
-its detailed simulation parameters and cosmological model can found in~\S 2 of 
-\citet{Bird2020}. We do not include any discussion of these details here, 
-instead focusing on how we vet the sample of star particles for use in our 
-chemical evolution models. 
-\par 
-It is of particular important to have accurately measured formation radii for 
-each star particle that we use in our analysis.~\texttt{h277} did not record 
-the exact birth radius of each star particle; however, each star particle does 
-have an accurate age at each snapshot. Since stellar orbits are unlikely to 
-change significantly in an adequately short time interval, the radii of 
-sufficiently young stars in their first snapshot are reasonable approximations 
-of their birth radii. We therefore restrict our sample to those with an age at 
-first snapshot of~$\leq$~150 Myr, and adopt their Galactocentric radius at that 
-time as their birth radius. We have also conducted this analysis with a maximum 
-age at first snapshot of 50 Myr, and found similar results, suggesting that 
-these time intervals are short enough to not impact our conclusions. In 
-practice, we find that 150 Myr also provides with an adequately large number of 
-star particles to sample from. Of the star particles that remain after imposing 
-this cut, the oldest one is 12.26 Gyr old at the present day. Our model can 
-only apply on timescales as long as or shorter than the full range of ages of 
-the sample of star particles; we therefore subtract 1.5 Gyr from the formation 
-times of all star particles, allowing~$T$~= 0 in our models to correspond to 
-$T$~= 1.5 Gyr in~\texttt{h277}. As a consequence, our disc models trace the 
-chemical evolution of the Galaxy out to a lookback time of~$\sim$12.2 Gyr, or a 
-redshift of~$z \approx$~3, placing the onset of star formation at that time. 
-\par 
-We further restrict our sample of star particles to only those with both 
-formation and final radii of~$R_\text{gal} \leq$~20 kpc, and to have formed 
-within~$\left|z\right|\leq$~3 kpc of the disc midplane. These criteria ensure 
-that we're only using star particles which formed in-situ. While it's possible 
-that some star particles formed in a dwarf galaxy as it was infalling, a 
-scenario which would satisfy these requirements, these star particles are few 
-in number, and are only relevant at large~$R_\text{gal}$ and high ages - a 
-region of parameter space where few stars form anyway. 
-\par 
-Based on a kinematic decomposition performed on the present-day phase space 
-distribution of the~\texttt{h277} star particles, we include all those with 
-bulge, pseudobulge, and disc-like kinematics, excluding halo stars. While we're 
-not modeling the evolution of the bulge here, these star particles are 
-overwhelmingly located at~$R_\text{gal}\leq$~3 kpc at the present day anyway; 
-here we're much more interersted in~$R_\text{gal}\geq$~3 kpc since we're 
-modeling the evolution of the disc. These cuts yield a sample of 3,000,556 star 
-particles from~\texttt{h277}. 
-\par 
-\texttt{h277} had a transient bar during its evolution, but does not have one 
-at~$z$ = 0 ({\color{red} citation?}). This is a noteworthy difference between 
-our model and that of~\citet{Minchev2013}, and by extension the 
-\citet*{Minchev2014} and~\citet{Minchev2017} studies which use it as well, 
-because they selected a hydrodynamical simulation of a galaxy specifically so 
-that it would have a strong bar at~$z$ = 0; the transient bar in~\texttt{h277} 
-was not strong. This could mean that the dynamical 
-history of our model Galaxy does not reflect that of~\citet{Minchev2013} and 
-perhaps the Milky Way itself. However, the difference is likely within the 
-uncertainties of the current understanding of the Milky Way's dynamical 
-history. Although an investigation on the impact of bar evolution on stellar 
-migration and thus chemical evolution is outside the scope of this paper, it is 
-an interesting question which can be probed by simply swapping the 
-\texttt{h277} data within~\texttt{VICE} for another simulation, then rerunning 
-our numerical models and comparing the results.
-
-% fig 1 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.32]{decomposition.pdf} 
-\caption{Radial distributions of our star particles from 
-\texttt{h277}. In the top row, we show distributions of~\textit{final} radius 
-in bins of birth radius and age, and in the bottom row, we show distributions 
-of~\textit{birth} radius in bins of final radius and age. Each bin in 
-Galactocentric radius is shown in its own panel, denoted in text at the top of 
-each panel and by vertical black dashed lines. We colour-code the distributions 
-according to the age of the star particles, denoted by the legend in the upper 
-left panel. We smooth all distributions with a box-car width of 0.5 kpc to 
-improve clarity. We omit the distributions for 8 - 10 Gyr old stars born in the 
-9 - 11 and 11 - 13 kpc bins due to an insufficient number of star particles 
-with which to calculate the distribution. } 
-\label{fig:h277_decomposition} 
-\end{figure*}
-
-In the top row of Fig.~\ref{fig:h277_decomposition}, we plot the distributions 
-of final radius in bins of birth radius and age for our sample of star 
-particles. Conversely, the bottom rows distributions of birth radii in bins of 
-final radius and age. Focusing on the top row of panels, we note that for star 
-particles born at any radius and time, the distribution of final radius is 
-still peaked near the birth radius, but moves slightly inward with increasing 
-age. The tails of the distributions toward larger~$R_\text{gal}$ are nearly 
-age-independent, while the tails toward smaller~$R_\text{gal}$ are not. This 
-suggests that radial migration inward and outward occur on different timescales 
-in~\texttt{h277}, specifically that inward migration is slower than outward 
-migration. By extension, this suggests that the two may be tied to different 
-physical processes. In a cosmological simulation,~\citet{Roskar2008a} 
-demonstrate that resonant scattering at corotation causes stars to move 
-outward and gas to move inward. It's possible that stellar migration inward has 
-different origins. 
-\par 
-Focusing on the bottom row of panels in Fig.~\ref{fig:h277_decomposition}, we 
-note that the mode of the birth radius distributions show a stronger dependence 
-on age than the mode of the final radius distributions. At any Galactocentric 
-radius at the present day, the youngest stars are overwhelmingly born at 
-comparable radii, while the oldest stars are overwhelmingly born at smaller 
-radii. This is most noticeable in at large~$R_\text{gal}$. The differences 
-between the two can be understood by considering the steep nature of the radial 
-gradient in stellar surface density. Take for example the 8 - 10 Gyr age bin in 
-both~$R_\text{Birth}$ = 5 - 7 kpc and~$R_\text{Final}$ = 11 - 13 kpc bins (i.e. 
-the red curves in the top-left and bottom-right panels). For these old stars 
-born at 5 - 7 kpc, 11 - 13 kpc is far down the tail of the~$R_\text{Final}$ 
-distribution, and yet 5 - 7 kpc is the mode~$R_\text{Birth}$ of all old stars 
-presently at these radii. This implies that even though a plurality of 8 - 10 
-Gyr old stars with~$R_\text{Final}$ = 11 - 13 kpc were born at 5 - 7 kpc, they 
-account for only a small fraction of the stars with similar birth radii. This 
-is only possible if there are many more stars born at small~$R_\text{gal}$ than 
-large~$R_\text{gal}$, implying a stellar surface density which decreases as a 
-strong function of Galactocentric radius. This is known to be the case 
-\citep[e.g.][]{Bland-Hawthorn2016}. 
-\par 
-We also note that the top row of Fig.~\ref{fig:h277_decomposition} demonstrates 
-that the number of stars which migrated inward and outward are comparable in 
-\texttt{h277}. In fact, taking~$\left|\Delta R_\text{gal}\right| \geq$~500 pc 
-between birth and final radii as the criterion for migration inward or outward, 
-we indeed find as global percentages in our sample that 27\% migrated inward, 
-29\% migrated outward, and the remaining 44\% stayed near their birth radius. 
-Furthermore, these distributions contain some information on the timescales of 
-radial migration. In all bins of birth radius, a good first-order estimate of 
-the probability density that a star has a final radius in the same bin is 
-$\sim$0.3. With bins in birth radius of 2 kpc, this suggests that only 
-$\sim$60\% of stars remain in their birth radius bin by the time their~$\sim$2 
-Gyr old. and the remaining~$\sim$40\% have migrated already. If the type Ia 
-supernova delay-time distribution (SN Ia DTD) is a~$t^{-1.1}\approx t^{-1}$ 
-power-law as suggested by observational results~\citep[e.g.][]{Maoz2012, 
-Maoz2017}, then we expect similar numbers of SN Ia events to occur with delay 
-times between 1 and 10 Gyr as we do between 100 Myr and 1 Gyr. With such an 
-extended DTD, and the timescales for migration implied by Fig. 
-\ref{fig:h277_decomposition}, its possible that SN Ia progenitors can migrate 
-significant distances before exploding. Indeed, in the ASAS-SN bright SN 
-catalog,~$\sim$10\% of SNe are seen at >10 kpc from their host galaxies 
-\citep{Holoien2019}. While this catalog is for~\textit{all} supernovae seen by 
-ASAS-SN, the majority of SN events are type Ia anyway. Based on this, it's 
-reasonable to expect that the migration of nucleosynthetic may proceed 
-alongside stellar migration. This effect has largely been neglected by GCE 
-studies to date on the grounds that radial migration is a slow process, and 
-thus the majority of nucleosynthesis should occur near a star's birth radius 
-(e.g.~\citealp{Minchev2013}, and in the application of the 
-\citealt{Weinberg2017} analytic models in~\citealt{Feuillet2018}). However, 
-with the realization that the SN Ia duty cycle is also a slow process due to 
-the long tail of the DTD, its possible that stellar migration and SN Ia occur 
-on similar timescales. Therefore, we relax this assumption in the present 
-paper. We discuss the application of the~\texttt{h277} star particle data to 
-our model for radial migration and the time dependence thereof in the next 
-section.
-
-\subsection{Radial Migration} 
-\label{sec:methods:migration} 
-As in previous studies~\citep[e.g.][]{Schoenrich2009, Minchev2013, Sharma2020}, 
-in this paper we model the Milky Way as a series of concentric annuli with a 
-uniform width~$\Delta R_\text{gal}$. To run numerical simulations of these 
-models, we develop and make use of~\texttt{VICE}'s~\texttt{milkyway} object, 
-designed specifically for such an approach. The~\texttt{milkyway} object is a 
-subclass of a more general object named~\texttt{multizone}; at its core a 
-\texttt{multizone} object is an array of~\texttt{singlezone} objects, which are 
-designed to handle one-zone models of GCE and were the focus of 
-\citet{Johnson2020},~\texttt{VICE}'s initial release paper. The 
-\texttt{multizone} object affords users full control over which zone any 
-individual stellar population is in at all timesteps following its formation as 
-well as the ability to move gas between any two zones with any time dependence. 
-In principle this should allow for arbitrarily complex zone configurations and 
-migration prescriptions. The \texttt{milkyway} object is a user-friendly 
-extension of this which enforces an annular zone configuration as we take here. 
-As defaults, it adopts the stellar migration model detailed in this section and 
-our star formation law discussed in~\S~\ref{sec:methods:sfe}. 
-\par 
-As in hydrodynamical simulations, stars in~\texttt{VICE} are stand-ins for 
-entire stellar populations. They're said to be in a given zone if their radius 
-is between the inner and outer edges of the annulus. At all times, their 
-nucleosynthetic products and returned envelopes are placed in the ISM of the 
-annulus that they are in~\textit{at that time}. Where hydrodynamical and 
-N-body simulations of Galaxy evolution tend to use star particles of a fixed 
-mass, however,~\texttt{VICE} forms a fixed number of stellar populations per 
-zone per timestep, and allows their masses to vary to account for variations 
-in the star formation rate (SFR). The mass of stars formed in a given zone is 
-divided evenly among the stellar populations that form in a given zone and 
-timestep. 
-\par 
-The final radius of a stellar population is then determined based on the birth 
-and final radii of star particles in a hydrodynamical simulation, for which 
-we've taken~\texttt{h277} in this paper (see discussion in~\S 
-\ref{sec:methods:h277}). Describing the Galaxy as a series of concentric 
-annuli,~\texttt{VICE}'s~\texttt{milkyway} object assumes stellar populations 
-are born at the centres of each annulus. For a stellar population born at a 
-time~$T$ and Galactocentric radius~$R_\text{gal}$, it first searches for star 
-particles from~\texttt{h277} that formed at~$T \pm$~250 Myr and~$R_\text{gal} 
-\pm$~250 pc. It then randomly selects a star particle from this subsample with 
-no bias to act as an~\textit{analog}. This stellar population then assumes the 
-change in orbital radius~$\Delta R_\text{gal}$ of its analog at face value, 
-and moves from its birth radius to the implied final radius at~$T$ = 12.2 Gyr 
-with an assumed time dependence. If no candidate analogs are found, 
-\texttt{VICE} widens the search to~$T \pm$~500 Myr and~$R_\text{gal} \pm$~500 
-pc. If still no analog is found, then it finds the star particle 
-with the smallest difference in birth radius still within a birth time of 
-$T \pm$~500 Myr, and assigns it as the analog. 
-While this prescription allows stellar populations to be assigned analogs with 
-significantly different birth radii, this is only an issue for small~$T$ and 
-large~$R_\text{gal}$ where there are few star particles from~\texttt{h277}, 
-and where few stars form in nature anyway due to the inside-out growth of 
-galaxies~\citep{Bird2013}. Furthermore, due to the similarity of the histograms 
-in the top row of Fig.~\ref{fig:h277_decomposition}, we expect taking 
-$\Delta R_\text{gal}$ from a star particle which formed at a similar time but 
-different birth radius in these instance to be accurate enough for our 
-purposes. 
-\par 
-Our models assume that the Galaxy is vertically and azimuthally well-mixed, and 
-that the radial direction is the only one in which there are significant 
-differences in composition. That is, each annulus extends from the disc 
-midplane at~$z$ = 0 to~$z = \pm \infty$, and whether or not a star particle is 
-in a given annulus does not depend on~$z$ at all. In fact, this information is 
-\textit{not} used in integrating our models with~\texttt{VICE}. Instead, we 
-simply assume that each stellar population in our models are located at the 
-present day~$z_\text{final}$ of its assigned analog. Furthermore, when an 
-\texttt{h277} star particle is assigned as an analog, it is~\textit{not} 
-thrown out of the sample of candidate analogs, in theory allowing a star 
-particle to act as an analog for multiple stellar populations. This is a 
-subtle difference between the~\citet{Minchev2013} model and ours; where we 
-assign star particles to stellar populations for which~\texttt{VICE} then 
-calculates a stellar mass and composition based on an assumed SFH, the 
-\citet{Minchev2013} uses a chemical evolution model to assign compositions to 
-star particles.
-
-% fig 2 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.45]{migration.pdf} 
-\caption{A diagram illustrating how Galactocentric radius changes with time for 
-two stellar populations under our migration schema: diffusion (crimson, solid), 
-linear (lime, dot-dashed), post-process (black, dotted), and sudden (blue, 
-dashed). Here the initial and final radii and birth times are chosen at random 
-for illustrative purposes. With the initial and final Galactocentric radii of 
-a stellar population, its birth time, and one of these assumptions regarding 
-the time-dependence of radial migration, the Galactocentric radius at all times 
-is known. } 
-\label{fig:migration_schema} 
-\end{figure}
-
-With a known birth radius and time from our GCE model and an implied 
-$\Delta R_\text{gal}$ from a stellar population's assigned analog, the final 
-radius is known and the only missing piece of information is the 
-time-dependence with which it moves there. In the present paper we consider 
-four parameterized assumptions to describe this, each of which are illustrated 
-conceptually in Fig.~\ref{fig:migration_schema}. 
-\begin{itemize} 
-	\item \textbf{Post-Processing}: Stars stay where they are born until the 
-	final timestep, at which point they instantly migrate to their final 
-	radius. This retains the assumption that stars do not contribute to 
-	nucleosynthesis beyond their birth radius as employed in previous studies 
-	\citep[e.g.][]{Minchev2013}. In this scenario, each annulus is treated as 
-	a one-zone model independent of all other zones. We illustrate this case 
-	with a black dotted line in Fig.~\ref{fig:migration_schema}.
-
-	\item \textbf{Sudden}: A random number is drawn from a uniform distribution 
-	between a stellar population's time of birth and the present day. That time 
-	is taken to be the time of instantaneous migration to the present-day 
-	annulus. This emulates a scenario in which a single dynamical interaction 
-	changes a star's orbital radius, and be thought of mathematically as a 
-	time-dependent extension of the post-processing scenario. We illustrate 
-	this case with a blue dashed line in Fig.~\ref{fig:migration_schema}.
-
-	\item \textbf{Diffusion}: Stars move to their final radii in a continuous, 
-	time-dependent manner in this case. So named because it corresponds to a 
-	scenario in which angular momentum diffuses via a random walk, under this 
-	assumption, the mean displacement of stars that migrate similar distances 
-	would scale with~$\sqrt{\text{age}}$. This is our 
-	fiducial migration model, and we present results with this assumption 
-	unless otherwise noted. This is qualitatively similar to 
-	\citet{Frankel2018, Frankel2020}, who also model radial orbit migration 
-	with a~$\sqrt{\tau}$ dependence. We illustrate this case with a red solid 
-	line in Fig.~\ref{fig:migration_schema}.
-
-	\item \textbf{Linear}: A simple variation of the diffusion model in which 
-	the migration to the final radius scales linearly with age rather than with 
-	$\sqrt{\text{age}}$. There is no physical motivation for this model other 
-	than mathematical ease, but together with the diffusion model it 
-	constitutes a test of how sensitive our conclusions are to the 
-	time-dependence of stellar migration. We illustrate this case with a 
-	green dot-dashed line in Fig.~\ref{fig:migration_schema}. 
-\end{itemize} 
-In all models, we neglect radial gas flows~\citep{Lacey1985, Bilitewski2012}, 
-instead focusing on these simple assumptions describing how orbital radii 
-change with time. While such an investigation would be an interesting extension 
-of our study, we reserve it for future work. 
-\par 
-We emphasize that there is~\textit{no} N-body integration employed in our 
-models aside from that which ran the~\texttt{h277} simulation. Furthermore, we 
-use our sample of analog star particles from it~\textit{only} in determining 
-$\Delta R_\text{gal}$ of each of our model stellar populations (see discussion 
-in~\S~\ref{sec:methods:h277}). While~\texttt{h277} had its own SFH and chemical 
-enrichment history, we make use of neither of these components here; rather, 
-these are exactly what we seek to explore variations of. We acknowledge that 
-stellar migration is often formulated using the processes ``blurring'' and 
-``churning'', referring to a star's epicyclic motions and changes in the 
-guiding center of its orbit~\citep[e.g.][]{Sellwood2002, Schoenrich2009, 
-Minchev2011}; migration can also occur due to the overlap of spiral arm and 
-bar resonances in the disc~\citep{Minchev2011}. We refrain from discussion of 
-this approach here, because our models do not make use of such methodology. In 
-the present paper, the orbital radii at all times are calculated and assumed at 
-face value given one of the four assumptions detailed in the bullet list above. 
-\par
-
-\subsection{Nucleosynthetic Yields, Outflows, and Recycling} 
-\label{sec:methods:yields} 
-Nucleosynthesis proceeds in our models according to~\textit{fractional net} 
-yields, as required by~\texttt{VICE}. That is, our yields quantify the mass 
-of some element~$x$ ejected to the interstellar medium (ISM) in units of the 
-progenitor stellar population's total initial mass, and only accounts for 
-\textit{newly produced} nucleosynthetic material.~\texttt{VICE} takes into 
-account the return of previously produced nucleosynthetic products with a 
-separate implementation. In the present paper, we focus our analysis on 
-alpha and iron-peak elements, taking oxygen (O) and iron (Fe) as the 
-representative cases. The dominant enrichment channels of 
-interest in our models are thus core collapse and type Ia supernovae 
-\citep{Johnson2019}. Though we choose O and Fe, we expect 
-similar results to be found for other alpha (e.g. Ne, Mg, Si) and iron-peak 
-elements (e.g. Mn, Ni, Co), with purely quantitative differences reflective of 
-the relative yields between elements. 
-\par 
-Enrichment from core collapse supernovae (CCSNe) happens immediately following 
-the formation of progenitor stars in~\texttt{VICE}. This is an adequate 
-approximation, because the lifetimes of massive stars are short compared to 
-the relevant timescales for galaxy evolution. For the most massive stars, the 
-lifetimes are comparable to the timestep size we adopt in this paper anyway. 
-This assumption implies a linear relationship between the CCSN enrichment 
-rate and the SFR: 
-\begin{equation} 
-\dot{M}_x^\text{CC} = y_x^\text{CC}\dot{M}_\star 
-\end{equation} 
-where~$y_x^\text{CC}$ is the CCSN yield of some element~$x$. Physically, this 
-quantity represents the mass of an element~$x$ ejected to the interstellar 
-medium (ISM) from all CCSNe events associated with a stellar population in 
-units of the stellar population's initial mass. For example, if 
-$y_x^\text{CC} = 0.01$, a hypothetical 100~\msun~stellar population would 
-add 1~\msun~of~$x$ to the ISM immediately. This procedure neglects the mass 
-that would be lost to outflows, which like recycling, have a separate 
-implementation in~\texttt{VICE}. In this paper, we adopt~$y_\text{O}^\text{CC}$ 
-= 0.015 and~$y_\text{Fe}^\text{CC}$~= 0.0012 from~\citet{Johnson2020}, who 
-in turn adopt these values from~\citet{Weinberg2017}. 
-\par 
-SN Ia nucleosynthesis products are injected according to a~$t^{-1.1}$ DTD with 
-a minimum delay time of~$t_\text{D}$ = 150 Myr. This is the default DTD in 
-\texttt{VICE}, which was also adopted by~\citet{Johnson2020}, and is suggested 
-by recent observational results comparing the cosmic SN Ia rate to the cosmic 
-SFH~\citep{Maoz2012, Maoz2017}. In a one-zone model at times~$t > t_\text{D}$, 
-the enrichment rate of some element~$x$~can be expressed as the product of 
-some yield~$y_x^\text{Ia}$ and the SFH weighted by the DTD: 
-\begin{subequations}\begin{align} 
-\dot{M}_x^\text{Ia} &= y_x^\text{Ia}\langle\dot{M}_\star\rangle_\text{Ia} \\ 
-&= y_x^\text{Ia}\ddfrac{
-	\int_0^{t - t_\text{D}} \dot{M}_\star(t') R_\text{Ia}(t - t') dt' 
-}{
-	\int_{t_\text{D}}^{t_\text{max}} R_\text{Ia}(t')dt' 
-} 
-\label{eq:mdot_ia} 
-\end{align}\end{subequations} 
-where~$R_\text{Ia}$ is the DTD itself, which has units of~$M_\odot^{-1}$ 
-Gyr$^{-1}$. Like the CCSN yield,~$y_x^\text{Ia}$ is the mass of some element 
-$x$ produced over the SN Ia duty cycle in units of the progenitor stellar 
-population's initial mass. It can also be expressed as an integral over the 
-DTD: 
-\begin{equation} 
-y_x^\text{Ia} = m_x^\text{Ia} \int_{t_\text{D}}^{t_\text{max}} R_\text{Ia}(t') 
-dt' = m_x^\text{Ia}\frac{N_\text{Ia}}{M_\star} 
-\label{eq:y_x_ia} 
-\end{equation} 
-where~$m_x^\text{Ia}$ is the average mass of the element~$x$ produced in a 
-single SN Ia event and the integral evaluates to the mean number of SN Ia 
-events~$N_\text{Ia}$ per mass of stars formed~$M_\star$. \texttt{VICE} forces 
-$t_\text{max}$~= 15 Gyr always, though provided one is consistent with 
-equations~\refp{eq:mdot_ia} and~\refp{eq:y_x_ia}, the results are independent 
-of~$t_\text{max}$ since the integrals cancel. 
-\par 
-Extending this formalism to multi-zone models is simple - rather than an 
-integral over the star formation history of a given annulus, the rate becomes 
-a sumation over all stellar populations that are in a given zone at some time: 
-\begin{equation} 
-\dot{M}_x^\text{Ia} = y_x^\text{Ia} \ddfrac{
-	\sum_i M_i R_\text{Ia}(\tau_i) 
-}{
-	\int_{t_\text{D}}^{t_\text{max}} R_\text{Ia}(t')dt' 
-} 
-\label{eq:mdot_ia_multizone} 
-\end{equation} 
-where~$M_i$~and~$\tau_i$~are the mass and age of the~$i$'th stellar population, 
-respectively. 
-\par 
-Initially, we adopt~$y_\text{O}^\text{Ia}$~= 0 and~$y_\text{Fe}^\text{Ia}$~= 
-0.0017 from~\citet{Johnson2020}, who in turn adopt these values from 
-\citet{Weinberg2017}. However, in practice we find that the e-folding 
-timescales of star formation in our models are sufficiently long (see 
-discussion in~\S~\ref{sec:methods:sfhs}) such that our fiducial, inside-out SFH 
-model predicts [O/Fe]~$\approx$~+0.05 for young stars. We therefore multiply 
-$y_\text{Fe}^\text{Ia}$~by~$10^{0.1}$, adopting instead~$y_\text{Fe}^\text{Ia}$ 
-= 0.00214 in order for our fiducial model to predict a late-time [O/Fe] ratio 
-in better agreement with observations. Although there is no motivation for such 
-a change aside from this, this decision is likely within the uncertainties in 
-SN Ia nucleosynthetic yields anyway. 
-\par 
-Our models assume that all supernova yields of O and Fe are independent of 
-metallicity. While this appears to be empirically true in the Milky Way for O 
-and Fe (\citealp{Weinberg2019};~\citealp*{Griffith2019}; 
-\citealp{Griffith2020}), our CCSN yields are based on 
-supernova explosion models in which all >8~\msun~progenitors produce a CCSN 
-event~\citep[e.g.][]{Chieffi2004, Chieffi2013}. Recent findings with regard to 
-black hole formation and stellar explodability have demonstrated that many 
-massive stars instead collapse directly to a black hole (see theoretical 
-discussion by, e.g.,~\citealp{Pejcha2015, Sukhbold2016, Ertl2016}, and 
-observational evidence from~\citealp*{Gerke2015};~\citealp{Adams2017, 
-Basinger2020}). Such effects would necessarily lower CCSN yields of all 
-elements. While~\texttt{VICE} includes functionality with which to calculate 
-$y_x^\text{CC}$~for some element~$x$~using built-in tables from supernova 
-nucleosynthesis studies, an in-depth investigation of the impact of these 
-effects is outside the scope of this paper. Such an investigation which expands 
-the capabilities of~\texttt{VICE} will be presented in Griffith et al. (2021, 
-in prep). 
-\par 
-With regard to our SN Ia yields,~\citet{Brown2019} demonstrate that the local 
-specific SN Ia rate shows a strong, inverse dependence on galaxy stellar mass. 
-They argue that this may imply a metallicity dependent~$R_\text{Ia}$ that 
-produces more SN Ia events at early times when the metallicity is low. However, 
-these metallicity are only present in our models at very early times. 
-Furthermore, when outflows are taken into account, these yields are known to 
-predict observationally plausible abundances~\citep{Andrews2017, Weinberg2017}. 
-We find similar results in our models. 
-\par 
-\citet{Weinberg2017} demonstrate that, to first order, the nucleosynthetic 
-yields of a given element and the strength of outflowing winds determine the 
-late-time equilibrium abundance in the ISM. We retain their characterization 
-of outflows here, in terms of a mass-loading factor~$\eta$~describing the ratio 
-of the mass outflow to the SFR: 
-\begin{equation} 
-\eta \equiv \frac{\dot{M}_\text{out}}{\dot{M}_\star} 
-\end{equation} 
-Here we adopt a scaling of~$\eta$~with~$R_\text{gal}$~such that the late-time 
-equilibrium abundance as a function of radius describes a metallicity 
-gradient in agreement with observations;~\citet{Nidever2014} employ a similar 
-methodology. 
-\par 
-The procedure outlined here makes two assumptions: 1) that the equilibrium 
-abundance at a given radius corresponds to the mode of the observed MDF, and 2) 
-that radial migration does not significantly alter the overall form of the 
-gradient. We demonstrate that this holds in our models in~\S 
-\ref{sec:obs_comp:gradient}. For alpha elements,~\citet{Weinberg2017} defines 
-the equilibrium abundance under a constant SFH as: 
-\begin{equation} 
-Z_{\alpha,\text{eq}} = \frac{y_\alpha^\text{CC}}{1 + \eta(R_\text{gal}) - r} 
-\end{equation} 
-where~$r$~is the recycling parameter ($\approx$0.4 for the sake of this scaling 
-with a~\citealp{Kroupa2001} IMF; see discussion in~\S~2.2 
-of \citealp{Weinberg2017}). Solving for~$\eta(R_\text{gal})$ yields: 
-\begin{equation} 
-\eta(R_\text{gal}) = \frac{y_\alpha^\text{CC}}{Z_{\alpha,\text{eq}}} + r - 1 = 
-\frac{y_\alpha^\text{CC}}{Z_{\alpha,\odot}}10^{-\text{mode([$\alpha$/H])}
-(R_\text{gal})} + r - 1 
-\end{equation} 
-The metallicity gradient in the Milky Way has been the focus of a number of 
-studies to date.~\citet{Nordstroem2004b} find a gradient of -0.099 kpc$^{-1}$ 
-in [Fe/H] in main sequence stars from the Geneva Copenhagen Survey 
-(\citealp{Nordstroem2004a};~\citealp*{Holmberg2007}).~\citet{Daflon2009} report  
--0.04 kpc$^{-1}$ in [S/H] in OB stars.~\citet{Frinchaboy2013} derive -0.09 
-kpc$^{-1}$ in [M/H] in open clusters.~\citet{Hayden2014} also find -0.09 
-kpc$^{-1}$ in [M/H] for~$R_\text{gal} \gtrsim$~6 kpc for low-$\alpha$ stars, 
-but find the gradient to be relatively flat within~$R_\text{gal} \lesssim$~6 
-kpc. \citet{Weinberg2019} report a gradient of -0.06 kpc$^{-1}$ in mode([Mg/H]) 
-for upper red giant branch stars in the disc (see their Fig. 23). In tentative 
-agreement with these studies, we adopt a slope of -0.08 kpc$^{-1}$. To set the 
-normalization, we assume the mode([$\alpha$/H]) to be~$\sim$+0.3 at 
-$R_\text{gal}$ = 4 kpc, since this would produce mode([$\alpha$/H])~$\approx$~0 
-at~$R_\text{gal}$ = 7 - 9 kpc. This results in the following form for~$\eta$ 
-as a function of Galactocentric radius: 
-\begin{equation} 
-\eta(R_\text{gal}) = \frac{y_\alpha^\text{CC}}{Z_{\alpha,\odot}} 
-10^{(-0.08\text{ kpc}^{-1})(R_\text{gal} - 4\text{ kpc}) + 0.3} + r - 1 
-\label{eq:eta_rgal} 
-\end{equation} 
-where we adopt our CCSN yield of O for~$y_\alpha^\text{CC}$ and the solar 
-abundance of O of~$Z_{\text{O},\odot}$ = 0.00572 based on~\citet{Asplund2009}. 
-We plot this adopted scaling in the top panel of Fig.~\ref{fig:eta_tau_sfh}, 
-highlighting a value of~$\sim$2.15 for the solar circle with a red dotted line. 
-This does assume a uniformly linear gradient at all~$R_\text{gal}$, in tension 
-with the findings of~\citet{Hayden2014} who find it to flatten within~$\sim$6 
-kpc. However, this procedure can be easily repeated for any desired gradient, 
-since the functional form simply goes into the power of 10 in equation 
-\refp{eq:eta_rgal}.
-
-% fig 3 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.45]{eta_tau_sfh.pdf} 
-\caption{\textbf{Top}: Our implemented scaling of the mass loading factor 
-$\eta$~with Galactocentric radius (black) as defined by equation 
-\refp{eq:eta_rgal}.~\textbf{Bottom}: The e-folding timescales of the star 
-formation histories of our model galaxies (black). These values come from a 
-fit to the~$\Sigma_\star$-age relation in bins of~$R/R_\text{e}$~for 
-$10^{10.5}$~-~$10^{11}$~\msun~Sa/Sb Hubble type spiral galaxies as reported by 
-\citet[][see discussion in~\S~\ref{sec:methods:sfhs}]{Sanchez2020}. The 
-horizontal and vertical red dashed lines in both panels highlight a mass 
-loading factor of~$\eta \approx$~2.15 and a star formation timescale of 
-$\tau_\text{sfh} \approx$~15 Gyr at an assumed radius of the sun of 
-$R_\odot$ = 8 kpc. } 
-\label{fig:eta_tau_sfh} 
-\end{figure}
-
-Both AGB star enrichment and the recycling of previously produced metals in 
-this paper proceed as they did in~\citet{Johnson2020}, with the caveat that the 
-mass is added to the annulus that a stellar population is in at a given time, 
-which may or may not be the annulus it was born in. Recycling proceeds 
-according to the~\citet{Kalirai2008} initial-remnant mass relation assuming a 
-\citet{Kroupa2001} IMF and a mass-lifetime relationship of 
-$\tau = 1.1\tau_\odot(M/M_\odot)^{-3.5}$, where~$\tau_\odot$~= 10 Gyr is the 
-main sequence lifetime of the sun and the factor of 1.1 accounts for the 
-post-main sequence lifetime.~\texttt{VICE} in its current version forces an AGB 
-enrichment channel in all models; it is thus included in the present paper. For 
-this enrichment channel, we adopt the net yields sampled on a table of stellar 
-initial mass and metallicity from the FRUITY database \citep{Cristallo2011}. 
-However, the AGB star yields of O and Fe are negligible compared to their 
-supernova yields; we therefore conclude discussion of this component of our 
-models here. 
-\par
-
-\subsection{Star Formation Histories} 
-\label{sec:methods:sfhs} 
-\texttt{VICE} handles models in either infall, star formation, or gas mode, 
-referring simply to which component of the evolutionary history the user has 
-specified. The starburst models presented in~\citet{Johnson2020} ran in infall 
-mode, but here we run~\texttt{VICE} in star formation mode, because we are 
-after specific forms for the star formation histories of our models. In 
-Appendix~\ref{sec:normalize_sfh}, we present justification of how we normalize 
-the parameters of our star formation histories to produce a realistic model 
-Galaxy at the present day. In short, it takes in a unitless description of the 
-dependence of the SFH at a given Galactocentric radius, denoted 
-$f(t|R_\text{gal})$, and a unitless description of the present day stellar 
-surface density gradient, denoted~$g(R_\text{gal})$. We integrate 
-$f(t|R_\text{gal})$ with time for each annulus, assuming~$R_\text{gal}$ to 
-correspond to the centre of the zone, and attach a prefactor to 
-$f(t|R_\text{gal})$ in each annulus such that the desired gradient is achieved 
-with a total stellar mass similar to the Milky Way. This procedure neglects the 
-impact of radial migration, assuming that it does not significantly alter the 
-form of~$g(R_\text{gal})$. We demonstrate that these assumptions hold in~\S 
-\ref{sec:methods:surface_density_gradient}, in which we also detail our 
-adopted form of~$g(R_\text{gal})$. As long as this assumption is not violated, 
-the equation derived in Appendix~\ref{sec:normalize_sfh} can be used to 
-calculate these prefactors for future models of Milky Way-like galaxies. 
-\par 
-In the present paper, we present four fiducial SFHs, which we dub ``constant'', 
-``inside-out'', ``late-burst'', and ``outer-burst''. They're defined as 
-follows: 
-\begin{itemize} 
-	\item \textbf{Constant}: The SFH at a given radius is time-independent. 
-	\begin{equation} 
-	f_\text{C}(t|R_\text{gal}) = 1 
-	\label{eq:constant_sfh} 
-	\end{equation} 
-	This case is of particular theoretical interest because it quantifies the 
-	effect of stellar migration while removing the impact of a time-dependent 
-	SFH.
-
-	\item \textbf{Inside-Out}: This is our fiducial SFH. 
-	\begin{equation} 
-	f_\text{IO}(t|R_\text{gal}) = (1 - e^{-t / \tau_\text{rise}}) 
-	e^{-t / \tau_\text{sfh}} 
-	\label{eq:insideout_sfh} 
-	\end{equation} 
-	We adopt this mathematical form over a more traditional 
-	linear-times-exponential characterization, because the latter does not 
-	offer control over the position of the maximum SFR. The form we adopt has 
-	a maximum near~$\tau_\text{rise}$, for which we adopt a value of 2 Gyr 
-	everywhere here. This produces a peak in star formation at lookback times 
-	of~$\sim$10 Gyr, roughly corresponding to a redshift of~$z \approx$~2, in 
-	agreement with observational results on the cosmic SFH~\citep{Madau2014}. 
-	In this paper,~$\tau_\text{sfh}$ is a function of~$R_\text{gal}$, discussed 
-	in this section. We present results assuming this model throughout this 
-	paper except in cases where a different SFH impacts the predictions.
-
-	\item \textbf{Late-Burst}: In this model, the inside-out SFH is modified to 
-	exhibit a recent, gradual burst in star formation described by a Gaussian: 
-	\begin{equation} 
-	f_\text{LB}(t|R_\text{gal}) = f_\text{IO}(r|R_\text{gal}) 
-	(1 + A_be^{-(t - t_b)^2/2\sigma_b^2}) 
-	\label{eq:lateburst_sfh} 
-	\end{equation} 
-	$A_b$ is a dimensionless parameter describing the strength of the 
-	starburst,~$t_b$ is the time of the local maximum in the SFH during the 
-	burst, and~$\sigma_b$ is the width of the Gaussian describing it. This 
-	model being loosely motivated by the findings of~\citet{Mor2019} and 
-	\citet{Isern2019}, we adopt~$A_b$ = 1.5,~$t_b$ = 10.2 Gyr, and 
-	$\sigma_b$ = 1 Gyr, finding in practice that~$A_b$ = 1.5 produces a 
-	local maximum SFR that is a factor of~$\sim$2 larger than the preceding 
-	local minimum.
-
-	\item \textbf{Outer-Burst}: A variation of the late-burst model in which 
-	only~$R_\text{gal} \geq$~6 kpc experience the starburst. This is loosely 
-	motivated by the findings of~\citet{Vincenzo2020} where a hydrodynamical 
-	simulation of a Milky Way-like galaxy showed radially dependent infall. 
-	\begin{equation} 
-	f_\text{OB}(t|R_\text{gal}) = \begin{cases} 
-	f_\text{IO}(t|R_\text{gal}) & (R_\text{gal} < 6\text{ kpc}) \\ 
-	f_\text{LB}(t|R_\text{gal}) & (R_\text{gal} \geq 6\text{ kpc}) 
-	\end{cases} 
-	\label{eq:outerburst_sfh} 
-	\end{equation} 
-\end{itemize} 
-Although we do not consider such models here, an investigation into the impact 
-of more episodic star formation histories would be an interesting extension of 
-the present paper. For example,~\texttt{VICE} has all of the necessary 
-capabilities to handle models in which major episodes of star formation 
-coincide with close passages of the Sagittarius dwarf 
-\citep[e.g.][]{RuizLara2020}. 
-\par 
-We derive the scaling of the e-folding timescales of star formation 
-$\tau_\text{sfh}$ with~$R_\text{gal}$ from the data in~\citet{Sanchez2020}. 
-They present the stellar surface density~$\Sigma_\star$ as a function of age 
-in bins of~$R/R_\text{e}$ for MaNGA galaxies, where~$R_\text{e}$ is the 
-half-light radius. Here we take their~$M_\star = 10^{10.5} - 10^{11}$ 
-\msun~ bin for Sa/Sb spirals and simultaneously fit the normalization and 
-e-folding timescale~$\tau_\text{sfh}$ of our~$f_\text{IO}(t|R_\text{gal})$ form 
-to the data. Although the normalization is irrelevant to our models and 
-determined via the method outlined in Appendix~\ref{sec:normalize_sfh}, we 
-adopt the resulting~$\tau_\text{sfh}-R_\text{gal}$ relation in our models. With 
-our adopted stellar surface density gradient (see discussion in~\S 
-\ref{sec:methods:surface_density_gradient}), we know the present-day half-mass 
-radius to be very near 4 kpc. The findings of~\citet{Garcia-Benito2017} and 
-\citet{GonzalezDelgado2014} suggest that half-light radii are marginally larger 
-than half-mass radii. Based on equation (4) of~\citet{GonzalezDelgado2014} 
-relating the two for circular apertures, we expect our model Galaxy to have a 
-half-light radius near 5 kpc. We therefore adopt~$R_\text{e}$ = 5 kpc to 
-convert the~$\tau_\text{sfh}-R_\text{gal}/R_\text{e}$ relation resulting from 
-our fit to the~\citet{Sanchez2020} data into a~$\tau_\text{sfh}-R_\text{gal}$ 
-relation. {\color{red} If there are references suggesting a similar value for 
-the Milky Way, we should note them here. } 
-\par 
-We illustrate this relationship in the bottom panel of Fig. 
-\ref{fig:eta_tau_sfh}, noting that the resulting timescales are long, 
-particularly for the outer Galaxy. With a red dotted line, we highlight a value 
-of~$\tau_\text{sfh} \approx$~15 Gyr at an assumed orbital radius of the sun of 
-$R_\odot$ = 8 kpc. Although these timescales at most radii are considerably 
-longer than a Hubble time, this is no cause for worry; this simply means that 
-these regions of the Galaxy in our models experience less than 1 e-folding in 
-their SFR, and that in the outer Galaxy the SFH is nearly constant after the 
-initial rise in the first~$\sim$2 Gyr. It is nonetheless interesting that 
-these timescales are considerably longer than that derived for the cosmic 
-SFH~\citep{Madau2014}.
-
-% fig 4 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.32]{evol.pdf} 
-\caption{The surface densities of star formation~$\dot{\Sigma}_\star$ (top 
-row), infall $\dot{\Sigma}_\text{in}$ (middle row), and gas~$\Sigma_\text{g}$ 
-(bottom row) as functions of simulation time for our four fiducial SFHs: 
-constant (far left), inside-out (left middle), late-burst (right middle), and 
-outer-burst (far right). We plot curves for the annuli whose inner radii are 
-3 kpc (grey), 5 kpc (black), 7 kpc (red), 9 kpc (yellow), 11 kpc (green), 13 
-kpc (blue), and 15 kpc (purple) (see equations~\refp{eq:constant_sfh}, 
-\refp{eq:insideout_sfh},~\refp{eq:lateburst_sfh}, and~\refp{eq:outerburst_sfh} 
-for the mathematical definition of each SFH). 
-}
-\label{fig:evol} 
-\end{figure*}
-
-We plot the resultant SFHs or our models in the top row of Fig.~\ref{fig:evol} 
-for a handful of radii. At all timesteps, the gas supply is known via the star 
-formation efficiency timescale~$\tau_\star$ (see discussion in~\S 
-\ref{sec:methods:sfe}). This quantity is illustrated in the bottom row of 
-Fig.~\ref{fig:evol}.~\texttt{VICE} automatically calculates the implied infall 
-rate by comparing the amount of gas lost to outflows and star formation in a 
-given timestep to that which is required to sustain the user-specified level of 
-star formation at the next timestep; we assume the infalling gas to be of zero 
-metallicity at all times. This quantity is shown in the middle row of Fig. 
-\ref{fig:evol}.
-
-\subsection{Star Formation Efficiency} 
-\label{sec:methods:sfe} 
-The term ``star formation efficiency'' (SFE) is somewhat overloaded in the 
-literature. In the star formation and feedback community, it usually 
-refers to the fraction of a molecular cloud's mass which will eventually be 
-converted into stars. In the chemical evolution literature, however, it 
-typically refers to the inverse timescale relating the SFR within some star 
-forming reservoir and the mass of gas in that region: 
-$\tau_\star \equiv \Sigma_\text{g}/\dot{\Sigma}_\star$. High (Low) values of 
-$\tau_\star$ indicate slow (fast) star formation and thus low (high) SFE; when 
-we refer to SFE here, we're referring to the definition based on this 
-timescale. In the star formation and feedback literature, this is often 
-referred to as the ``depletion time''. 
-\par 
-Based on the findings of~\citet{Kennicutt1998}, it is common practice in the 
-chemical evolution literature a single power-law describing the relationship 
-between the surface densities of gas and star formation~$\Sigma_\text{g}$ and 
-$\dot{\Sigma}_\star$, often referred to as the star formation law or the 
-Kennicutt-Schmidt relation: 
-\begin{equation} 
-\dot{\Sigma}_\star \sim \Sigma_\text{g}^N 
-\end{equation} 
-\citet{Kennicutt1998} derive~$N = 1.4 \pm 0.15$ relating the total 
-$\dot{\Sigma}_\star$~and~$\Sigma_\text{g}$~within the disc across a sample of 
-quiescent spiral galaxies and infrared and circumnuclear starbursts. However, 
-recent studies have found evidence that much of the observed scatter in this 
-relation is physical in origin~\citep{delosReyes2019} and that there are 
-significant breaks in both the power-law index and zero-points 
-\citep{Kennicutt2020}. Much of the uncertainty surrounding the details of the 
-star formation law is a consequence of the ongoing debate about the CO-to-H$_2$ 
-conversion factor (\citealp{Kennicutt2012};~\citealp*{Liu2015}). Although 
-\citet{Ellison2020a} demonstrate that there are significant galaxy-to-galaxy 
-variations in the star formation law, suggesting that individual galaxies do 
-not follow the population averaged trend,~\citet{delosReyes2019} argue that 
-this is still a reasonable recipe for Galaxy evolution models. We adopt such a 
-formalism here. 
-\par 
-\citet{Krumholz2018} compare model-predicted star formation laws to the 
-observations of~\citet{Bigiel2010} and~\citet{Leroy2013} (see their Fig. 2). We 
-find that the following by-eye fit to the power-law index~$N$~is a reasonble 
-description of the aggregate data: 
-\begin{equation} 
-N = \begin{cases} 
-1.0 & (\Sigma_\text{g} \geq \Sigma_{\text{g},2}) \\ 
-3.6 & (\Sigma_{\text{g},1} \leq \Sigma_\text{g} \leq \Sigma_{\text{g},2}) \\ 
-1.7 & (\Sigma_\text{g} \leq \Sigma_{\text{g},1}) 
-\end{cases} 
-\label{eq:sf_law_indeces} 
-\end{equation} 
-where~$\Sigma_{\text{g},1} = 5\times10^6$~\msun~\persqkpc~and 
-$\Sigma_{\text{g},2} = 2\times10^7$~\msun~\persqkpc. The apparent linearity of 
-the relationship above~$\sim2\times10^7$~\msun~\persqkpc~suggests that in this 
-regime, star formation proceeds at the fastest possible rate, and that 
-$\tau_\star \equiv \Sigma_\text{g}/\dot{\Sigma}_\star$~= constant. The 
-observations of~\citet{Leroy2013} and~\citet{Kennicutt2020} would suggest that 
-these are the 
-surface densities at which the molecular fraction~$f_\text{mol} = M_{\text{H}_2} 
-/ (M_{\text{H}_2} + M_\text{HI}) \approx$~1. We therefore adopt the assumption 
-that above~$\Sigma_\text{g} = 2\times10^7$~\msun~\persqkpc,~$\tau_\star$ 
-reaches its minimum value, and increases with decreasing~$f_\text{mol}$. We 
-denote this value as~$\tau_\text{mol}$, the value of~$\tau_\star$ for a gas 
-reservoir with~$f_\text{mol}$~= 1. This, combined with our three-component 
-power-law index N results in the following final form for our adopted star 
-formation law: 
-\begin{equation} 
-\dot{\Sigma}_\star = \begin{cases} 
-\Sigma_\text{g} \tau_\text{mol}^{-1} & 
-(\Sigma_\text{g} \geq \Sigma_{\text{g},2}) 
-\\ 
-\Sigma_\text{g} \tau_\text{mol}^{-1} \left(\frac{
-	\Sigma_\text{g}
-}{
-	\Sigma_{\text{g},2} 
-}\right)^{2.6} & 
-(\Sigma_{\text{g},1} \leq \Sigma_\text{g} \leq \Sigma_{\text{g},2}) 
-\\ 
-\Sigma_\text{g} \tau_\text{mol}^{-1} \left(\frac{
-	\Sigma_{\text{g},1} 
-}{
-	\Sigma{\text{g},2} 
-}\right)^{2.6}\left(\frac{
-	\Sigma_\text{g}
-}{
-	\Sigma_{\text{g},1} 
-}\right)^{0.7} & 
-(\Sigma_\text{g} \leq \Sigma_{\text{g},1}) 
-\end{cases} 
-\label{eq:sf_law} 
-\end{equation} 
-where we choose the power-law indeces such that this formalism is consistent 
-with equation~\refp{eq:sf_law_indeces}, and prefactors are added to ensure 
-piece-wise continuity. In implementation,~\texttt{VICE} requires the 
-$\tau_\star-\dot{\Sigma}_\star$ relation when ran in star formation mode and 
-the~$\tau_\star-\Sigma_\text{g}$ relation when ran in infall and gas modes. 
-Both follow algebraically from this relationship given the substitution 
-$\tau_\star \equiv \Sigma_\text{g} / \dot{\Sigma}_\star$. 
-\par 
-Although it is more physically motivated to use an adopted star formation law 
-to infer a star formation rate from the ISM properties at a given timestep, as 
-discussed in~\S~\ref{sec:methods:sfhs}, we are using~\texttt{VICE} in star 
-formation mode. This means that it is~$\dot{\Sigma}_\star$ which is specified 
-\textit{a priori} by our models - not~$\Sigma_\text{g}$. That is,~\texttt{VICE} 
-is inferring~$\Sigma_\text{g}$ from~$\dot{\Sigma}_\star$ in our models, not 
-the other way around. While we acknowledge the findings of~\citet{Ellison2020b}, 
-this another reason we must invoke a simple parameterization for the star 
-formation law, which~\citet{Kennicutt2020} argue is still a reasonable 
-approach. This decision also means that changing our assumptions about the 
-star formation law do not impact our SFHs, instead impacting the inferred 
-$\Sigma_\text{g}$ as a function of radius and time. 
-\par 
-Based on the observed Kennicutt-Schmidt at different redshifts, 
-\citet{Tacconi2018} suggest that~$\tau_\text{mol}$ should scale with redshift 
-$z$ and the deviation from the star forming main sequence~$\delta$MS via 
-$\tau_\text{mol} \propto (1 + z)^{-0.6}\delta\text{MS}^-0.44$. We don't take 
-into account the effect of~$\delta$MS in our models, but we do investigate the 
-redshift dependence. A reasonable approximation to the~$t - z$ relation out to 
-$z \approx$~3 assuming typical~$\Lambda$CDM cosmology is given by: 
-\begin{equation} 
-\frac{t}{t_0} \approx (1 + z)^{-5/4} 
-\end{equation} 
-where~$t_0$ is the present-day age of the universe, and~$t$ is not simulation 
-time but the age of the universe. Plugging this relation into the 
-\citet{Tacconi2018} scaling yields the following time-dependence for 
-$\tau_\text{mol}$: 
-\begin{equation} 
-\tau_\text{mol} = \tau_{\text{mol},0}(t/t_0)^{12/25} \approx 
-\tau_{\text{mol},0}(t/t_0)^{1/2} 
-\end{equation} 
-where~$\tau_{\text{mol},0}$ is simply~$\tau_\text{mol}$ at the present day. We 
-generalize this formula to the following form: 
-\begin{equation} 
-\tau_\text{mol} = \tau_{\text{mol},0}(t/t_0)^\gamma 
-\label{eq:tau_mol}
-\end{equation} 
-In this paper we present models which adopt~$\tau_{\text{mol},0}$ = 2 Gyr 
-\citep{Leroy2008, Leroy2013, Tacconi2018} and~$\gamma$ = 1/2 based on this 
-argument. We have also ran simulations which adopt~$\tau_{\text{mol},0}$ = 1 
-Gyr and~$\gamma$ = 0 (a time-independent~$\tau_\text{mol}$), and found similar
-results. In all timesteps an annnuli,~\texttt{VICE} infers~$\Sigma_\text{g}$ 
-from~$\dot{\Sigma}_\star$ given our equations~\refp{eq:sf_law} and 
-\refp{eq:tau_mol}.
-
-% fig 5 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.45]{sfe.pdf} 
-\caption{The star formation efficiency timescale~$\tau_\star$ as a function of 
-Galactocentric radius at simulation times of 2 Gyr (red), 4 Gyr (yellow), 
-6 Gyr (green), 8 Gyr (blue), 10 Gyr (purple), and 12.2 Gyr (the present day, 
-black) predicted by our inside-out SFH model. } 
-\label{fig:sfe} 
-\end{figure}
-
-In Fig.~\ref{fig:sfe}, we plot~$\tau_\star$ as a function of~$R_\text{gal}$ at 
-six different time stamps predicted by our fiducial, inside-out SFH model. At 
-$R_\text{gal} \lesssim$ 6 kpc,~$\tau_\star$ is near~$\tau_\text{mol}$ at all 
-times, implying a molecular fraction of unity at these radii. Although this 
-prediction is likely unrealistic because 21-cm line observations suggest the 
-presence of neutral hydrogen as close to the Galactic centre as several hundred 
-pc~\citep{Kalberla2009}, we find in practice that changing our assumptions 
-about the star formation law does not impact our conclusions. In collecting 
-results for this paper, we investigated purely linear, purely power-law, and 
-broken power-law characterizations, finding similar predictions in all cases. 
-In general we find that the detailed form of the SFH, and to some extent the 
-time-dependence of radial migration, exert much greater power in establishing 
-the model predictions than does the star formation law. Nonetheless it is an 
-interesting result that a~$\dot{\Sigma}_\star - \Sigma_\text{g}$ relation 
-informed by the observed, population averaged trend and the normalization of 
-our SFHs implied by the stellar mass of the Milky Way predicts such a 
-discrepancy with the observed HI distribution. We refrain from further 
-discussion of this with the finding that it doesn't impact the conclusions 
-detailed in the present paper.
-
-\subsection{Surface Density Gradient} 
-\label{sec:methods:surface_density_gradient}
-
-% fig 6 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.45]{surface_density_gradient.pdf} 
-\caption{The surface density of gas (blue) and stars (red) as predicted by our 
-inside-out SFH model. The dotted black line with the higher normalization 
-denotes a thin disc profile with scale length~$R_t$ = 2.5 kpc; the other 
-denotes a thick disc profile with scale length~$R_T$ = 2.0 kpc, and a ratio of 
-$\Sigma_T/\Sigma_t$~= 0.27 at~$R_\text{gal}$~= 0. The solid black line denotes 
-the sum of the two; this is the surface density gradient of the Milky Way as 
-reported by~\citet{Bland-Hawthorn2016}, renormalized to imply the same total 
-stellar mass within the disc as our models. } 
-\label{fig:surface_density} 
-\end{figure}
-
-As discussed in~\S~\ref{sec:methods:sfhs}, Appendix~\ref{sec:normalize_sfh} 
-presents justification of a recipe in which we select a unitless function 
-describing the stellar surface density gradient~$g(R_\text{gal})$. In setting 
-the normalization, our model ensures that the integral of~$g(R_\text{gal})$ 
-over the surface area of the disc predicts a total stellar mass in agreement 
-with that observed for the Milky Way. For this value, we adopt 
-$M_\star^\text{MW} = (6.08 \pm 1.14)\times10^{10}$~\msun~\citep{Licquia2015}. 
-This is the total stellar mass of the Galaxy, including the bulge; 
-\citet{Licquia2015} report~$(5.17 \pm 1.11)\times10^{10}$~\msun~as the mass of 
-the disc alone. Although we aren't modeling the bulge here, our model extends 
-to~$R_\text{gal}$ = 0 and our sample of candidate analog star particles from 
-\texttt{h277} includes those with bulge-like kinematics. 
-\par 
-In this paper we adopt the following double exponential form for 
-$g(R_\text{gal})$, describing the thin and thick disc components of the 
-Galaxy: 
-\begin{equation} 
-g(R_\text{gal}) = e^{-R_\text{gal}/R_t} + \frac{\Sigma_T}{\Sigma_t} 
-e^{-R_\text{gal}/R_T} 
-\label{eq:gradient} 
-\end{equation} 
-where~$R_t$~and~$R_T$~are the scale radii of the thin and thick discs, 
-respectively, and~$\Sigma_T/\Sigma_t$~is the ratio of their surface densities 
-at~$R_\text{gal}$~= 0. We adopt~$R_t$~= 2.5 kpc,~$R_T$~= 2.0 kpc, and 
-$\Sigma_T/\Sigma_t$~= 0.27 based on the findings of~\citet{Bland-Hawthorn2016}. 
-We plot the single exponential forms of each disc component as a dotted black 
-line in Fig.~\ref{fig:surface_density}, with the solid black line denoting the 
-sum of the two. Althoug these scale radii are smaller than the commonly adopted 
-scale radius for a single exponential disc of~$r_s \approx$~3 kpc 
-\citep[e.g.][]{Binney2008}, our choice of a double exponential disc here 
-necessitates a choice be made for not one but two scale radii. 
-\par 
-We plot the resultant surface density gradients from our fiducial, inside-out 
-SFH model in Fig.~\ref{fig:surface_density} as well, with red denoting the 
-stellar gradient and the gas in blue. We note that the stellar gradient very 
-nearly follows our target gradient denoted by the solid black line and 
-expressed by equation~\refp{eq:gradient}. Stellar migration has indeed not 
-altered the overall form of the gradient, simply introducing scatter around the 
-adopted trend. Although there are slight enhancements at small~$R_\text{gal}$ 
-and deficits at large~$R_\text{gal}$, the agreement is excellent in the regions 
-of the Galaxy where the gradient is best constrained observationally. The 
-$R_\text{gal}$ > 15.5 kpc populations are also composed entirely of stars that 
-migrated there, since that is the radius at which we shut of star formation; 
-with this mind, the under-prediction at these radii is unsurprising. 
-Furthermore, in this paper we are interested primarily in the~$R_\text{gal}$~= 
-3 - 15 kpc range anyway, since this is the region where disc stars are the 
-dominant populations. We also note that the gas gradient
-shows a break in the scale radius near~$R_\text{gal} \approx$ 
-6 kpc. This is a consequence of our adopted star formation law; at 
-$\Sigma_\text{g} = 2\times10^7$~\msun~\persqkpc~the relation changes from 
-linear at higher densities to~$\dot{\Sigma}_\star \sim \Sigma_\text{g}^{3.6}$ 
-at lower densities (see discussion in~\S~\ref{sec:methods:sfe}). Because we are 
-running~\texttt{VICE} in star formation mode, it's more accurate to say that 
-$\Sigma_\text{g}$~is a weak function of~$\dot{\Sigma}_\star$~at 
-$\Sigma_\text{g} \leq 2\times10^7$~\msun~\persqkpc~in this range as opposed to 
-$\dot{\Sigma}_\star$~being a strong function of~$\Sigma_\text{g}$. When looking 
-at the present-day gradient, this presents as a flattening of the gradient at 
-the radius where~$\Sigma_\text{g} = 2\times10^7$~\msun~\persqkpc; further 
-inspection along the y-axis of Fig.~\ref{fig:surface_density} confirms that 
-this break indeed occurs at this value of~$\Sigma_\text{g}$. 
-\par 
-Although we adopt the~\citet{Licquia2015} stellar mass of the Milky Way here, 
-we find similar results when taking a value which differs by an order of 
-magnitude. While mass typically cancels in one-zone models of chemical 
-evolution, the abundances instead determined by the evolutionary parameters 
-(e.g.~$\eta$~and~$\tau_\star$), this value sets the normalization of the 
-SFH~$\dot{\Sigma}_\star(t, R_\text{gal})$ in our models. In turn this impacts 
-the surface densities of gas~$\Sigma_\text{g}$ inferred at each timestep, and 
-thus the abundances to some extent. This choice only matters insofar as the 
-choice of star formation law matters, which we find to not impact our 
-conclusions.
-
-\subsection{Summary} 
-\label{sec:methods:summary} 
-In summary, our fiducial model has an inside-out SFH with e-folding timescales 
-derived from the observations of~\citet[][see discussion in~\S 
-\ref{sec:methods:sfhs}]{Sanchez2020}. Radial migration proceeds in a manner in 
-which our model stellar populations have a change in radius 
-$\Delta R_\text{gal}$ informed from the~\texttt{h277} hydrodynamical simulation 
-\citep[][see discussion in~\S~\ref{sec:methods:h277}]{Christensen2012, 
-Zolotov2012, Loebman2012, Loebman2014, Brooks2014}. In the base-line model, 
-stars move to their final radius with a~$\sqrt{\text{age}}$~dependence 
-(\citealp{Frankel2018, Frankel2020} model stellar migration with a similar 
-characterization; see discussion in~\S~\ref{sec:methods:migration}). Using 
-\texttt{VICE} to calculate abundances for O and Fe in this paper, our supernova 
-yields are adopted from~\citet{Johnson2020}, who in turn take these values from 
-\citet{Weinberg2017}. Outflows are characterized such that the equilibrium 
-abundance of oxygen under a constant SFH follows an abundance gradient in 
-agreement with observational results in the Milky Way (see discussion in 
-\S~\ref{sec:methods:yields};~\citet{Nidever2014} make use of similar 
-methodology). Our star formation law is based on the~\citet{Bigiel2010} and 
-\citet{Leroy2013} data presented in comparison with theoretical models in 
-\citet[][see discussion in~\S~\ref{sec:methods:sfe}]{Krumholz2018}. To describe 
-the stellar surface density gradient, we adopt the two-exponential form 
-describing the thin and thick discs from~\citet[][see discussion in~\S 
-\ref{sec:methods:surface_density_gradient}]{Bland-Hawthorn2016}. 
-\par 
-Our quality cuts imposed on the star particles from~\texttt{h277} yields a 
-sample of 3,000,556 candidate analog star particles (see discussion in~\S 
-\ref{sec:methods:h277}), only~$\sim$57\% of which have disc-like kinematics 
-at the present day. Since we're modeling the thin and thick disc populations 
-here,~$\sim$1.71 million is a much better estimate of the number of star 
-particles that we can realistically sample from. We take~$\Delta R_\text{gal}$ 
-= 100 pc as the width of each annulus from~$R_\text{gal} = 0$~to 20 kpc and a 
-timestep size of~$\Delta T$~= 10 Myr from~$T = 0$~to 12.2 Gyr. With the 
-resulting 200 zones and 1,221 timesteps, we let~\texttt{VICE} form~$n = 9$ 
-stellar populations per annulus per timestep, resulting in 2,197,000 total 
-stellar populations with predicted masses and abundances. While this is more 
-than the number of disc particles in our sample of candidate analogs, we force 
-the star formation rate to zero beyond~$R_\text{gal}$ = 15.5 kpc; while these 
-stellar populations exist within~\texttt{VICE} and are a part of the 
-computational overhead, they have zero mass and thus do not contribute to the 
-chemical evolution in our models. This results in 1,692,306 stellar 
-populations with~\textit{non-zero} masses and abundances predicted by 
-\texttt{VICE}, reasonably within the limit of what we can sample. These 
-simulations run in~$\sim$2.5 hours and take up~$\sim$235 MB of disc space per 
-output, including the extra data that we record for each stellar population's 
-analog star particle. Lastly, we adopt a~\citet{Kroupa2001} IMF throughout this 
-paper. 
-\par 
-We have ran~\texttt{VICE} for all four of our SFHs, all four migration 
-models, and all four variations in~$\tau_\text{mol}$ noted in~\S 
-\ref{sec:methods:sfe} - a total of 64 simulations, as well as a variety of 
-other test cases. In this paper, we present results wherever the model 
-prescriptions are sensitive to the assumptions. However, in general the 
-differences can be understood with only the variations in star formation 
-history and the qualitative notion that many stars have moved beyond their 
-birth radius. \texttt{VICE} calculates abundances for nearly 2 million stellar 
-populations per model; to ensure that resolution does not impact our 
-conclusions, we have also ran variations with~$n$~= 2 stellar populations per 
-zone per timestep, and found similar results in all cases.
-
-\section{Comparison to Observations} 
-\label{sec:obs_comp}
-
-% fig 7 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.28]{ofe_feh_densitymap.pdf} 
-\caption{[O/Fe]-[Fe/H] diagrams for 15 Galactic regions spanning five bins in 
-$R_\text{gal}$ and~$\left|z\right|$. Each region has its own panel, with 
-radial bins shown in columns denoted at the top, and with bins in 
-$\left|z\right|$ shown in rows denoted in text in the middle column. For each 
-region, we plot~$N$~= 10,000 points sampled from our simulated stellar 
-populations predicted by our inside-out SFH model, where the probability of 
-sampling is proportional to the present-day mass of each stellar population. 
-In all panels, points are colour-coded according to the Galactocentric radius 
-of birth of the stellar population. For reference, we plot in a solid black 
-line in all panels the gas-phase [O/Fe]-[Fe/H] track predicted by the same 
-SFH in the~$R_\text{gal}$ = 8 kpc annulus, but with the post-processing 
-migration model; this curve is the same in all panels. } 
-\label{fig:ofe_feh_diagram} 
-\end{figure*}
-
-We begin the comparison of our model predictions to observational data with the 
-distribution of stellar populations in the [O/Fe]-[Fe/H] plane. We separate 
-stars into bins based on their present-day Galactic regions defined by five 
-bins in~$R_\text{gal}$ (3 - 5, 5 - 7. 7 - 9, 9 - 11, and 11 - 13 kpc) and three 
-bins in~$\left|z\right|$ (0 - 0.5, 0.5 - 1, and 1 - 2 kpc). Within each of the 
-resulting 15 regions, we sample 10,000 stars at random from our base-line 
-inside-out SFH model. Since stars in~\texttt{VICE} are stand-ins for entire 
-stellar populations, we let the probability of sampling one of them be 
-proportional to its present day mass. We plot the results of this procedure in 
-Fig.~\ref{fig:ofe_feh_diagram}, colour-coding each stellar population by its 
-birth radius; for reference, we also plot the gas-phase track which resulted 
-from the~$R_\text{gal}$ = 8 kpc annulus with the post-processing migration 
-model in a black solid line in all panels. 
-\par 
-In Fig.~\ref{fig:ofe_feh_diagram}, we note that high-$\alpha$~sequence stars 
-are predicted to be the dominant population at small~$R_\text{gal}$ and high 
-$\left|z\right|$; conversely, the low-$\alpha$~sequence dominates the 
-statistics at large~$R_\text{gal}$~and low~$\left|z\right|$. This is consistent 
-with the observational results of~\citet{Hayden2015}, who present a density map 
-in the [O/Fe]-[Fe/H] for the same Galactic regions (see their Fig. 4). 
-Furthermore, the locus of the low-$\alpha$ sequence shifts from super-solar 
-[Fe/H] to sub-solar [Fe/H] with increasing~$R_\text{gal}$, a shift which is 
-expected given the abundance gradient that we have built into our models (see 
-discussion in~\S~\ref{sec:methods:yields}). The colour-coding of the points 
-further suggests that the width of the low-$\alpha$~sequence arises out of 
-stellar migration. Though this wouldn't occur in our models without mixing, it 
-is to some extent expected from that in combination with the built-in gradient. 
-Nonetheless this theoretical interpretation of the low-$\alpha$ sequence is 
-consistent with the arguments of~\citet{Schoenrich2009} and~\citet{Nidever2014}. 
-\par 
-We clarify that we do not claim to recover the bimodality in [$\alpha$/Fe] as 
-observed here. Although there are authors who argue to have successfully 
-reproduced such results using an inside-out SFH with stellar migration 
-\citep[e.g.][]{Sharma2020}, we find that our fiducial model fails to reproduce 
-these results (see discussion in~\S~\ref{sec:obs_comp:ofe_dists}). These 
-results do nonetheless suggest that the spatial dependence of the two sequences 
-can be attributed to stellar migration. Lastly, we note that we find similar 
-results with our other three SFHs, increasing confidence in our argument that 
-migration establishes such a spatial dependence rather than the SFH. The only 
-notable difference is that the starburst models predict a slightly higher 
-characteristic [O/Fe] for the low-$\alpha$ sequence ($\sim$+0.1). This is a 
-natural consequence of the starburst producing young,~$\alpha$-enhanced stars 
-in excess of what is predicted by the baseline model~\citep{Johnson2020}.
-
-\subsection{Abundance Gradients} 
-\label{sec:obs_comp:gradient}
-
-% fig 8
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.42]{tracks.pdf} 
-\caption{\textbf{Left}: Gas phase evolutionary tracks in the [O/Fe]-[Fe/H] 
-plane for our inside-out SFH with either post-processing (dotted lines) or 
-diffusion (solid lines) migration models. We plot tracks for seven annuli, 
-colour-coded according to their Galactocentric radius and denoted by the 
-legend in the lower-left. We mark simulation times of 2, 4, 6, 8, 10, and 12.2 
-Gyr in X's for the diffusion model and points for the post-processing model. 
-\textbf{Right}: As a function of simulation time, a proxy for the SN Ia rate 
-using the total time-derivative of the Fe mass in a given annulus, calculated 
-by subtracting the contribution from recycling and CCSN enrichment and adding 
-back that lost to star formation and outflows. We show these rates for the 
-same annuli as in the left-hand panel, multiplying them by various prefactors 
-to improve clarity. } 
-\label{fig:tracks} 
-\end{figure*}
-
-We continue by assessing the impact of stellar migration on the gas-phase 
-tracks in the [O/Fe]-[Fe/H] plane. To this end, we compare the predictions of 
-our post-processing migration model, which has stars stay at their radii of 
-birth until they instantaneously migrate at the present day, and our diffusion 
-model, which has stars migrating continuously with a~$\sqrt{\text{age}}$ 
-dependence. In the left-hand panel of Fig.~\ref{fig:tracks}, we plot the 
-[O/Fe]-[Fe/H] tracks at several radii assuming the inside-out 
-SFH, with post-processing shown in dotted lines and the diffusion in solid 
-lines. We also mark simulation times of 2, 4, 6, 8, 10, and 12.2 Gyr on each 
-track for reference. 
-\par 
-We note first and foremost that there are considerable differences between the 
-two sets of tracks, particularly at high [O/Fe]. We demonstrate here that this 
-arises out of variability in SN Ia rates caused by the time-dependent radial 
-migration of the diffusion model. From our~\texttt{VICE} outputs, the total 
-time derivative of the Fe mass in a given annulus can be obtained by its change 
-across a single timestep. By then subtracting the CCSN contribution (known 
-exactly given our adopted yield and the SFR), approximately correcting for 
-recycling, and adding back that which was lost to star formation and outflows, 
-we obtain a simple estimate of the rate of Fe production by SNe Ia. 
-\par 
-We plot this proxy as a function of simulation time in the right-hand panel of 
-Fig.~\ref{fig:tracks}, with dotted and solid lines again denoting 
-post-processing and diffusion migration models and the same colour-coding as in 
-the left-hand panel; we have also multiplied these curves by various prefactors 
-to improve clarity. As expected, the post-processing model predicts a SN Ia 
-rate which is a smooth function of time at a given~$R_\text{gal}$. The diffusion 
-model on the other hand exhibits significant variability on~$\sim$Gyr 
-timescales; the time-averaged SN Ia rate tends to follow the post-processing 
-prediction, but the instantaneous rates do not agree. A close comparison allows 
-one to realize that whenever one of the tracks in the left-hand panel shows 
-higher (lower) [O/Fe] at a given [Fe/H], there is an excess (deficit) in the SN 
-Ia rate at a similar time and radius. Early times in the~$R_\text{gal}$ = 15 
-kpc annulus illustrates a rather extreme example whereby the SN Ia rate is 
-effectively zero for nearly 3 Gyr. We also note that the fractional amplitude 
-of the variability increases with~$R_\text{gal}$; the log-scaled y-axis makes 
-this clear. This makes sense physically because the lower stellar number 
-density in the outer Galaxy means it would be much more susceptible to sampling 
-noise. That is, a single star migrating has a larger fractional impact at 
-large radii than small radii.
-
-% fig 9 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.32]{metallicity_gradient.pdf} 
-\caption{Radial abundance gradients in [O/H] (top, red), [Fe/H] (top, blue), 
-and [O/Fe] (bottom) for our four fiducial SFHs - constant (far left), 
-inside-out (left-middle), late-burst (right-middle), and outer-burst (far 
-right). We plot the gas-phase abundance at the present day as a function of 
-Galactocentric radius in solid lines. Stars denote the median of the stellar 
-MDF of the 100-pc width annulus at a given radius, with shaded regions marking 
-the 16th and 84th percentiles thereof. Black lines in the top panels denote our 
-target [$\alpha$/H] gradient of mode([$\alpha$/H]) = +0.3 at~$R_\text{gal}$~= 
-4 kpc with a slope of -0.08 kpc$^{-1}$. } 
-\label{fig:metallicity_gradient} 
-\end{figure*}
-
-Although one may expect the rates predicted by the two migration models to 
-agree based on the dynamical argument that a star migrating outward should be 
-balanced by a star migrating inward due to the conservation of energy, the SN 
-Ia rate depends not only on stellar number density but also on the masses and 
-ages of the stellar populations. While an inwardly migrating star should be 
-balanced dynamically by an outwardly migrating one, the SN Ia rate is 
-unaffected only when the two have masses and ages such that the SN Ia DTD has 
-the same value for both stars. Fluctuations in the SN Ia rate at these 
-amplitudes can be understood through a comparison of the timescales associated 
-with radial migration and SN Ia events. In Fig.~\ref{fig:h277_decomposition}, 
-we plotted the distribution of final radii in bins of birth radius and age, 
-which are used in driving stellar migration in our models (see discussion in~\S 
-\ref{sec:methods:h277}). From this, we noted that~$\sim$40\% of~\texttt{h277} 
-star particles migrated beyond their birth radius by the time they were~$\sim$2 
-Gyr old. Though our adopted form differs slightly in detail, if the SN Ia DTD 
-is a~$\sim t^{-1}$ power-law with a minimum delay time of~$\sim$100 Myr 
-\citep{Maoz2012, Maoz2017}, then there should be similar numbers of SN Ia 
-events with delay times between 1 and 10 Gyr as there are between 100 Myr and 1 
-Gyr. While our~$R_\text{gal}$~= 15 kpc annulus is something of an extreme 
-example, when one realizes that this means~$\sim$half of SN Ia progenitors may 
-move significantly beyond their birth radius, the amplitude of the variability 
-seen in the right-hand panel of Fig.~\ref{fig:tracks} is not surprising. The 
-fact that >10\% of events are seen at >10 kpc from their host galaxies in the 
-ASAS-SN bright SN catalog~\citep{Holoien2019} adds qualitative, observational 
-support to the argument that SN Ia progenitors may often form at significantly 
-different radii than where the explosions are observed. 
-\par 
-We thus argue that the radial migration of nucleosynthetic yields can occur 
-alongside stellar migration for delayed sources. Though we do not investigate 
-this effect for such elements in this paper, it would be reasonable to expect 
-similar predictions for s-process elements produced in AGB stars like carbon, 
-nitrogen, strontium, yttrium, and zirconium as well as r-process elements from 
-neutron star mergers if the associated DTD is sufficiently long. What we really 
-learn from this investigation is that tracks are not simple functions when 
-stellar migration is taken into account. To first order, they're characterized 
-by the late-time equilibrium abundance and the value of~$\tau_\star$~setting 
-the position of the ``knee''~\citep{Weinberg2017}, though migration causes 
-noticeable variations which should depend on the details of the adopted 
-dynamical history. In~\S~\ref{sec:obs_comp:age_alpha}, we demonstrate that 
-this is a means with which truly young, super-solar [$\alpha$/Fe] stars in the 
-solar neighborhood can be explained theoretically. 
-\par 
-We continue with an investigation into the radial abundance gradients predicted 
-by our models. To some extent, a gradient is built into our models via a 
-scaling of the mass loading factor~$\eta$~with Galactocentric radius (see 
-discussion in~\S~\ref{sec:methods:yields}). In parameterizing the 
-$\eta-R_\text{gal}$ scaling, we assumed our constant SFH model and the 
-associated equilibrium abundance for alpha elements. Like the surface density 
-gradient, we also assumed that stellar migration does not alter the overall 
-form. We plot the radial [O/H] and [Fe/H] gradients predicted by all our 
-models in the top row of Fig.~\ref{fig:metallicity_gradient}, and the [O/Fe] 
-gradients in the bottom row. In all panels, stars denote the median abundance 
-in each annulus, and the shaded region denotes the 16th and 84th percentiles of 
-the MDF in that zone; solid lines denote the gas-phase gradient at the present 
-day. Although we built the gradient into our models based on the mode abundance, 
-we illustrate them here according to the median; we find that with annuli as 
-narrow as~$\Delta R_\text{gal}$~= 100 pc, the mode is a sufficiently noisy 
-statistic to introduce noticeably more scatter in this relation. Nonetheless we 
-have verified that it follows the trend implied by our target gradient, 
-illustrated by the solid black line. The median gradient for all of our model 
-SFHs follows a slightly shallower trend than the mode, which is expected when 
-the metallicity distribution is skew-negative in the inner Galaxy and 
-skew-positive in the outer Galaxy. 
-\par 
-We note that our models indeed recover an~$R_\text{gal}$-[O/H] relation 
-resembling that which was adopted. As was the case for the surface density 
-gradient (see discussion in~\S~\ref{sec:methods:surface_density_gradient}), 
-stellar migration appears to only introduce scatter. While our procedure for 
-setting setting the abundance gradient did not consider Fe, our models predict 
-it to follow a gradient similar to that of O. We further note that all SFHs 
-predict an [O/Fe] gradient which is relatively flat at all radii, steepening 
-only at very small and very large~$R_\text{gal}$. The trend toward higher 
-[O/Fe] beyond~$R_\text{gal}$~= 15.5 kpc is expected, since this is the radius 
-at which we shut off star formation; all stellar populations at these radii at 
-the present day formed in the disc and migrated there, meaning this region of 
-space in our model is populated only by stars sufficiently old to have migrated 
-such distances. Because they're old, they also tend to be~$\alpha$-enhanced. 
-This is consistent with the findings of~\citet{RadburnSmith2012}, who argue 
-that the outskirts of the NGC 7793 disc formed largely out of stellar 
-migration. {\color{red} Observational reference on the increase in [O/Fe] at 
-small~$R_\text{gal}$? Maybe~\citet{Hayden2015}, but I'm not sure.} 
-\par 
-We also note that our models predict differences between the stellar and 
-present-day gas-phase gradients which are sensitive to the adopted SFH. In the 
-constant SFH model, the gas-phase gradient follows the mode abundance by 
-construction. In the inside-out, late-burst, and outer-burst models, the 
-ISM at small~$R_\text{gal}$~is considerably more metal-rich than the stars at 
-similar radii. The late-burst model shows the largest difference; this is a 
-consequence of the starburst at small~$R_\text{gal}$, an effect which is absent 
-in the outerburst model. In accretion-induced starbursts, re-enrichment can 
-briefly produce super-equilibrium abundances in the gas-phase which then decay 
-back to the equilibrium abundance as the SFR declines~\citep{Johnson2020}. This 
-effect can also be seen in the outer-burst model; at~$R_\text{gal}$ slightly 
-larger than 6 kpc where the starburst did occur, the abundances are larger than 
-at slightly less than 6 kpc, where the star burst did~\textit{not} occur. 
-Altogether, these differences are reflective of the notion that the stellar 
-abundance gradient is sensitive to stars of all ages and thus the entire star 
-formation history, while the gas-phase gradient is more reflective of 
-enrichment over the previous depletion time.
-
-\subsection{Metallicity Distributions Functions} 
-\label{sec:obs_comp:mdfs}
-
-% fig 10 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.34]{mdf_3panel_fe.pdf} 
-\caption{Metallicity distribution functions (MDFs) in [Fe/H] predicted by our 
-fiducial, inside-out model (left) and as observed in APOGEE DR16 (right), for 
-stars and simulated stellar populations with present-day~$\left|z\right|$~= 0 - 
-0.5 kpc (bottom), 0.5 - 1 kpc (middle), and 1 - 2 kpc (top). MDFs are shown in 
-bins of Galactocentric radius: 3 - 5 kpc (black), 5 - 7 kpc (red), 7 - 9 kpc 
-(yellow), 9 - 11 kpc (green), 11 - 13 kpc (blue), and 13 - 15 kpc (purple). 
-The points near the top of the bottom panels denote what the mode abundance 
-would be if it followed out target gradient of [Fe/H] = +0.3 at~$R_\text{gal}$ 
-= 4 kpc with a slope of -0.08 kpc$^{-1}$ exactly, assuming the inner radius of 
-each bins (i.e. there is no point plotted for 15 kpc). All distributions are 
-smoothed with a box-car width of [Fe/H]~$\pm$~0.1 for clarity. } 
-\label{fig:mdf_3panel_fe} 
-\end{figure}
-
-% fig 11 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.34]{mdf_3panel_o.pdf} 
-\caption{The same as Fig.~\ref{fig:mdf_3panel_fe}, but for [O/H]. } 
-\label{fig:mdf_3panel_o} 
-\end{figure}
-
-Metallicity distribution functions (MDFs) and how they vary with Galactic 
-region are one of the core predictions of chemical evolution models. In this 
-section, we compare our model predicted MDFs to those observed in the 16th 
-data release of APOGEE (DR16;~\citealp{Ahumada2020, Majewski2017}). The 
-data are reduced using the APOGEE Stellar Parameters and Chemical Abundances 
-Pipeline (ASPCAP;~\citealp{Holtzman2015, GarciaPerez2016}). For further details 
-of the APOGEE survey, a brief summary can be found in~\S~2 of 
-\citet{Weinberg2019}. We restrict our sample to stars with effective 
-temperatures of 4000 K~$\leq T_\text{eff} \leq$~4600 K, surface gravities of 
-1.0~$\leq \log g \leq$~2.5, and signal-to-noise ratios of at least 100. These 
-cuts ensure that our sample consists of stars on the upper red giant branch, 
-safely excluding red clump stars to avoid obvious systematics in the 
-abundance distributions. 
-\par 
-In the disc midplane, stars as observed by APOGEE are known to exhibit mode 
-[$\alpha$/H] and [Fe/H] abundances that depend on Galactocentric radius, with a 
-skew-negative distribution in the inner Galaxy and skew-positive in the outer 
-Galaxy~\citep{Hayden2015, Weinberg2019}. Off the midplane, the MDFs converge on 
-[$\alpha$/H]~$\approx$~[Fe/H]~$\approx$~-0.5. This result is replicated in the 
-right-hand column of panels~\ref{fig:mdf_3panel_fe} and~\ref{fig:mdf_3panel_o}. 
-The left-hand columns show the distributions predicted by our fiducial 
-inside-out model. We note that these replicate the qualitative scaling of the 
-mode [O/H] and [Fe/H] with present-day Galactocentric radius, though our APOGEE 
-data suggest that the 3 - 5 and 5 - 7 kpc bins share a common mode abundance. 
-This was also seen in~\citet{Hayden2015}. Our models do not predict this 
-detail; this could indicate that we have incorrectly parameterized outflows in 
-the inner Galaxy (see discussion regarding our scaling of the mass loading 
-factor~$\eta$~with~$R_\text{gal}$ in~\S~\ref{sec:methods:yields}). We would 
-expect a flat [X/H] gradient and MDFs with similar modes if we simply chose it 
-to be so by letting~$\eta$~be constant at small~$R_\text{gal}$. Another 
-possibility is the cessation of star formation in these regions; by tracing 
-products of star formation such as HII regions~\citep{Guesten1982}, supernova 
-remnants~\citep{Leahy1989}, and pulsars (\citealp*{Lyne1985}; 
-\citealp{Case1998}), the surface density of star formation~$\dot{\Sigma}_\star$ 
-in the Milky Way is known to reach a maximum at~$R_\text{gal} \approx$~4 kpc 
-(see Fig. 1 of~\citealt{Peek2009} and Fig. 2 of~\citealt{Fraternali2012}). Our 
-models by construction predict~$\dot{\Sigma}_\star$ to decrease monotonically 
-with~$R_\text{gal}$~(see Fig.~\ref{fig:evol}). If the Milky Way has begun 
-quenching star formation, a process which is believed to begin in the centres 
-of galaxies at this mass~\citep[e.g.][]{Ellison2020b}, then fewer stars would 
-form in the most metal-rich regions than do in our models, cutting off the MDF 
-at high [O/H] and [Fe/H]. 
-\par 
-Beyond the midplane, our models fail to fully replicate the convergence of the 
-MDFs at [X/H]~$\approx$~-0.5. The observed MDF at small radii shfits from 
-skew-negative with a metal-rich mode to skew-positive with a metal-poor 
-mode with increasing~$\left|z\right|$. In our model predicted MDFs for small 
-$R_\text{gal}$, the mode does shift to lower abundances, but not to the same 
-extent as in the observed sample, and with minimal change in skewness. 
-Although the model predicts a portion of the effect, it cannot account for the 
-entire~$\left|z\right|$-dependence of the MDF shape in the inner Galaxy.
-
-\subsection{[O/Fe] distributions in Bins of [Fe/H]} 
-\label{sec:obs_comp:ofe_dists} 
-In this section we compare our predicted [O/Fe] distributions in various 
-Galactic regions to those recently published in~\citet{Vincenzo2021a}. As in our 
-\S~\ref{sec:obs_comp:mdfs}, they also make use of APOGEE DR16 
-\citep{Ahumada2020, Majewski2017}, and impose a similar set of cuts on 
-effective temperature, surface gravity, and signal-to-noise (see their~\S~2). 
-These distributions are estimates of the~\textit{intrinsic} [O/Fe] 
-distributions that, when 
-convolved with observational uncertainties and the APOGEE selection function, 
-would resemble the observed MDFs like those in~\citet{Hayden2015}. We show the 
-distributions predicted by our fiducial model in~$\Delta$[O/Fe] = 0.04 bins 
-across 15 Galactic regions in comparison to the~\citet{Vincenzo2021a} 
-distributions shown in dashed lines in Fig.~\ref{fig:ofe_mdfs_insideout}. 
-Galactic regions 
-are defined by a range in~$R_\text{gal}$, shown in columns and denoted at the 
-top of the figure, and a range in~$\left|z\right|$, shown in rows and denoted 
-in text in the left-hand column. We show this comparison for two bins in 
-[Fe/H], colour-coded according to the legend in the top-right panel.
-
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.32]{ofe_mdfs.pdf} 
-\caption{Predicted distributions in [O/Fe] in 15 Galactic regions and in two 
-bins in [Fe/H]. Columns correspond to bins in~$R_\text{gal}$, denoted at the 
-top of each column. Rows correspond to bins in~$\left|z\right|$, denoted in 
-text in the left-hand column. Distributions are color-coded according to the 
-[Fe/H] the sample is drawn from, denoted by the legend in the upper right 
-panel. Solid lines represent that predicted by our inside-out SFH in 
-$\Delta$[O/Fe] = 0.04 bins, while dashed lines correspond to the fits to the 
-APOGEE DR16 data presented in~\citet{Vincenzo2021a}, which quantify the 
-intrinsic distributions accounting for observational uncertainties and the 
-APOGEE selection function. } 
-\label{fig:ofe_mdfs_insideout} 
-\end{figure*}
-
-Finding similar results for all of our SFHs, we note that our model adequately 
-reproduces the broad nature of the [O/Fe] distributions at fixed [Fe/H] seen in 
-the APOGEE data. Some distributions in a specific Galactic region and [Fe/H] 
-bin show a bimodality in decent agreement with the observations (e.g. the 
--0.4~$\leq$~[Fe/H]~$\leq$~-0.2 bin at~$R_\text{gal}$~= 7 - 9 kpc and 
-$\left|z\right|$ = 1 - 2 kpc), but this is not true of all Galactic regions in 
-both metallicity bins. Instead, the principle failure of our model is that it 
-overpredicts the number of intermediate [O/Fe] stars. 
-\par 
-In the inner Galaxy, our model overestimates the mode [O/Fe] to some extent for 
-both [Fe/H] bins, but the difference is larger for the higher of the two. This 
-discrepancy also increases with increasing~$\left|z\right|$. At fixed 
-$R_\text{gal}$, the~\citet{Vincenzo2021a} distributions show two peaks which do 
-not change with~$\left|z\right|$; only their relative heights vary. This is 
-an assumption built into the model, but the agreement with the APOGEE data is 
-good. However, this is a region of the Galaxy where there aren't many APOGEE 
-stars. At~$\left|z\right|$ = 1 - 2 kpc for ~$R_\text{gal}$ = 3 - 5 and 5 - 7 
-kpc, the~\citet{Vincenzo2021a} model is fit to 31 and 17 stars, respectively. In 
-comparison, there are 109 in the solar annulus, and all other bins have >75 
-stars involved in the fit. It's possible the observed distributions shift 
-slightly to higher [$\alpha$/Fe], but at most at the~$\lesssim$~0.05 level 
-(see their Fig. 11). 
-\par 
-If this discrepancy persists in subsequent APOGEE data releases which will 
-better characterize the distributions in these regions, it's possible the 
-origin is tied to the Sagittarius dwarf. The~\texttt{h277} simulation, which 
-drives stellar migration in our models (see discussion in~\S 
-\ref{sec:methods}), did not have such an accretion event. With its most recent 
-major merger occurring at a redshift of~$z \approx$~3, this galaxy has 
-previously been selected for investigation expressly because of its quiescent 
-merger history~\citep[e.g.][]{Zolotov2012}. N-body models for the tidal 
-disruption of the Sagittarius dwarf, on the other hand, suggest pericentric 
-passages around 6.5, 4.5, 2.75, 1, and 0.1 Gyr ago~\citep{Law2010}. In addition 
-to potentially triggering episodes of star formation 
-\citep[e.g.][]{RuizLara2020}, more frequent pericentric passages of a massive 
-satellite could kinematically heat low-[$\alpha$/Fe] disc stars to higher 
-$\left|z\right|_\text{max}$~orbits. Such effects are not a component of the 
-dynamical history of~\texttt{h277}; this is one instance where running our 
-models with a different hydrodynamical simulation's star particles may be an 
-enlightening comparison. 
-\par 
-The notion that an [$\alpha$/Fe] dichotomy can arise out of radial migration 
-alone traces back to~\citet{Schoenrich2009}, and was later explored by 
-\citet{Nidever2014} and recently by~\citet{Sharma2020}. This however suggests 
-that an inside-out star formation history combined with stellar migration is not 
-conducive to predicting this observed result, even when a recent starburst is 
-added. The primary failure being an overpredicted frequency of intermediate 
-[$\alpha$/Fe] stars, this could point to a number of things. If the bimodality 
-is to arise out of inside-out Galaxy evolution and stellar migration alone, 
-then the transition between high- and low-$\alpha$ sequences needs to occur 
-faster than it does in these models. The analytic arguments of 
-\citet{Weinberg2017} suggest that the approach to equilibrium occurs on the 
-order of the SFE timescale~$\tau_\star$ (see~\S~\ref{sec:methods:sfe}). 
-Since we've adopted a star formation law which is motivated by observational 
-results, the failure of these models to reproduce the observed dichotomy 
-suggests that the typical SFE timescales as observed are not short enough to 
-explain such a fast transition. This would imply that either the Milky Way 
-occupied a special place in the scatter of the observed 
-$\dot{\Sigma}_\star-\Sigma_\text{g}$ relation at a time early in its 
-evolutionary history, or the bimodality arose out of alternative pathways. 
-Under our current assumptions, the simplest way to decrease the frequency of 
-intermediate [$\alpha$/Fe] stars is to simply shut off (or turn down) star 
-formation when the ISM is at such a composition. This is an indication 
-that two-infall evolutionary histories~\citep[e.g.][]{Chiappini1997, 
-Chiappini2001, Romano2010, Grisoni2017, Noguchi2018, Palla2020, Spitoni2016, 
-Spitoni2018, Spitoni2019a, Spitoni2020, Spitoni2021} would improve the 
-agreement between our model predictions and the observed distributions.
-
-\subsection{The Age-[$\alpha$/Fe] Relation} 
-\label{sec:obs_comp:age_alpha} 
-In this section, we assess the predicted age-[O/Fe] relations of our models, 
-using the results of~\citet{Feuillet2019} as the observational benchmark; their 
-stellar age measurements are based on isochrone matching. While we made 
-use of APOGEE DR16 data in comparing our model predictions to the observed 
-MDFs~\citep[][see~\S~\ref{sec:obs_comp:mdfs}]{Ahumada2020, Majewski2017}, they 
-made use of APOGEE DR14 stars for which parallax measurements are available 
-from Gaia~\citep{Abolfathi2014, GaiaDR2}. With their spatial and quality cuts, 
-the final 
-sample consisted of 77,562 stars. In bins of [O/Fe], they assume a gaussian 
-log age distribution, fitting the mean and standard deviation to the stars in 
-that bin. Because they assume a gaussian, they would report an equal mean 
-and median log age. This means that a one-to-one comparison of our model 
-predictions to their results is not free of nuance, because they predict 
-log age distributions which are highly non-gaussian at fixed [O/Fe]. 
-\par 
-The stellar populations from our simulations have different masses; this 
-necessitates weighting the age-distributions by present-day mass, because that 
-scales with the number of stars that a model stellar population represents. We 
-therefore adopt the 50th percentile of the mass-weighted age distribution in a 
-bin of [O/Fe] as the characteristic age to compare to the~\citet{Feuillet2019} 
-measurements. We refer to this quantity as the mass-weighted median age.
-
-% fig 13 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.34]{age_ofe_migration_comparison.pdf} 
-\includegraphics[scale = 0.34]{age_ofe_sfh_comparison.pdf} 
-\caption{
-\textbf{Left}: A comparison of the predicted age-[O/Fe] relation for the solar 
-annulus ($R_\text{gal}$ = 7 - 9 kpc and~$\left|z\right|$ = 0 - 0.5 kpc) between 
-the post-processing (upper left), diffusion (upper right), sudden (lower left), 
-and linear (lower right) migration models, assuming our inside-out SFH. 
-\textbf{Right}: The same as the left-hand panels, instead comparing the impact 
-of our constant (upper left), inside-out (upper right), late-burst (lower left), 
-and outer-burst (lower right) SFHs, assuming diffusion migration. In all panels, 
-red triangles and error bars denote the observed mean age and dispersion 
-thereof in bins of [O/Fe] as reported by~\citet{Feuillet2019}; here we include 
-only the bins containing at least 15 stars. Black squares denote the 
-mass-weighted median age in 0.02-dex bins in [O/Fe] predicted by our models, 
-with error bars denoting the 16th and 84th percentiles of the mass-weighted 
-age distribution in those bins. Points in the background denote each individual 
-stellar population from the model with a final position in the solar annulus, 
-colour-coded according to their Galactocentric radius of birth. 
-}
-\label{fig:age_alpha} 
-\end{figure*}
-
-In the left-hand set of panels of Fig.~\ref{fig:age_alpha}, we compare the 
-age-[O/Fe] relation in the solar annulus ($R_\text{gal}$~= 7 - 9 kpc and 
-$\left|z\right|\leq$~0.5 kpc) predicted by our four migration models to the 
-\citet{Feuillet2019} measurements, shown in red triangles. We mark the 
-mass-weighted median age in bins of [O/Fe] in each model with black squares, 
-and plot for reference in the background each individual stellar population in 
-the solar annulus, colour-coded according to its Galactocentric radius of birth. 
-\par 
-We note that the inside-out SFH, assumed by all four of the models illustrated 
-here, provides a reasonable description of the age-[O/Fe] relation as observed 
-in APOGEE. We also note that each model for the time-dependence of stellar 
-migration predicts differing amounts of scatter in the age-[O/Fe] relation. 
-Diffusion has the most, followed by linear, then sudden, and lastly 
-post-processing. We interpret this as a consequence of the variability in the 
-SN Ia rate as a function of radius and time caused by time-dependent migration 
-(see Fig.~\ref{fig:tracks} and associated discussion near the beginning of~\S 
-\ref{sec:obs_comp}). When the SN Ia rate is higher or lower than expected given 
-the SFH of an annulus, then the Fe abundance in that zone will increase or 
-decrease accordingly. This can occur if there is a significant net gain or loss 
-of SN Ia progenitors in a given time interval due to time-dependent migration. 
-The gas-phase [O/Fe] then decreases or increases in turn, and the stars which 
-form out of that gas inherit these compositions. When migration is taken into 
-account and stellar populations are mixed as a consequence, the observational 
-signature is intrinsic scatter in the age-[$\alpha$/Fe] relation. 
-\par 
-All of the models in the left-hand set of panels predict a correlation between 
-mass-weighted median age and [O/Fe] in good agreement the~\citet{Feuillet2019} 
-measurements assuming the inside-out SFH. This suggests that the population 
-averaged trend is unaffected by stellar migration. However, only the diffusion 
-and linear migration models predict a population of young ($\lesssim$~4 Gyr), 
-[$\alpha$/Fe]~$\approx$~+0.1 - 0.2 stars in the solar neighbourhood. These 
-stars are a part of the noticeable upward scatter in the relationship, and we 
-therefore interpret their origin to be the same as the scatter itself - they 
-formed in a region of the Galactic ISM at a time when it was particularly 
-alpha-enhanced due to a rather lasting deficit in SN Ia events. These stars 
-then migrated to the solar annulus, where they showed up in the APOGEE data 
-when stellar ages were measured using carbon-to-nitrogen ratios 
-\citep{Martig2016}, isochrone matching~\citep{Feuillet2018, Feuillet2019}, 
-and with the asteroseismic ages of the origin APOKASC catalog 
-\citep{Chiappini2015, SilvaAguirre2018, Pinsonneault2014}. 
-\par 
-\citet{SilvaAguirre2018} demonstrate that the observed young $\alpha$-rich 
-stars in the solar annulus have kinematics similar to the rest of the 
-high-$\alpha$ population, and suggested this may be the result of stellar 
-mergers or mass transfer events. This would produce a population of truly old 
-stars masquerading as young stars. In a sample of 51 young, $\alpha$-rich 
-red giants,~\citet{Hekker2019} demonstrate that a portion of these stars have 
-carbon-to-nitrogen ratios consistent with mass transfer events, but that others 
-do not, indicating they're either truly young stars or the result of mergers 
-on the main sequence. As far as we know, the mechanism discussed here is the 
-first theoretical explanation of the origin of these stars. We note 
-additionally that under this explanation, the young~$\alpha$-rich stars are 
-not so much $\alpha$-rich as they are Fe-poor, and form overwhelmingly at 
-large~$R_\text{gal}$ where the SN Ia rate is most variable (see discussion in 
-\S~\ref{sec:obs_comp:gradient}). 
-\par 
-In the right-hand set of panels in Fig.~\ref{fig:age_alpha}, we 
-compare the model predictions of our four different SFHs, assuming our 
-diffusion migration model, with the same plotting scheme and colour-coding as 
-in the left-hand panels. We note that the constant and inside-out SFHs describe 
-the data the best. Although our e-folding timescales for star formation are 
-sufficiently long at large~$R_\text{gal}$ such that there is little difference 
-between the constant and inside-out SFHs there anyway (see discussion in~\S 
-\ref{sec:methods:sfhs}), our constant SFH is idealized and of purely 
-theoretical interest, making the inside-out model the more likely of the two. 
-Below [O/Fe]~$\approx$~+0.1, the~\citet{Feuillet2019} data seem to follow a 
-slightly steeper age-[$\alpha$/Fe] relation than our inside-out model 
-predicts. This could point to any number of things being an inaccuracy in our 
-models: the detailed form of the SFH or the SN Ia DTD, our supernova yields, 
-or observational [O/Fe] errors, all of which are plausible. 
-\par 
-We note that our starburst models, both late-burst and outer-burst, disagree 
-with the~\citet{Feuillet2019} measurements. The late starburst produces a 
-population of young, $\alpha$-rich stars due to the perturbed ratio of core 
-collapse to type Ia supernova rates~\citep{Johnson2020}. With the starburst 
-occurring in a substantial fraction of the ISM in both models, the result is an 
-increase in the bulk [$\alpha$/Fe] for young stars which simply is not seen in 
-the observed sample. The effect is strong enough that at [O/Fe]~$\approx$~+0.1, 
-both models considerably overpredict the width of the distribution, 
-simultaneously predicting a mass-weighted median age many times the standard 
-deviation younger than observed. This discrepancy is of interest, because these 
-models were motivated by the observational results of~\citet{Mor2019} and 
-\citet{Isern2019} which suggest such a recent starburst. Although our 
-functional forms differ from what they reported in detail, they're reasonable 
-descriptions of the measurements within the error bars. This suggests that the 
-results of~\citet{Mor2019} and~\citet{Isern2019} are at odds with chemical 
-evolution models of the Milky Way. If the Galaxy truly experienced a recent 
-starburst, then something not included in our models had to prevent this global 
-increase in [$\alpha$/Fe].
-
-% fig 14 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.32]{age_alpha_regions.pdf} 
-\caption{The age-[O/Fe] relation in 12 Galactic regions predicted by our 
-inside-out SFH. Bins in Galactocentric radius are shown in columns, and labeled 
-at the top. Bins in the height~$\left|z\right|$ above/below the disc midplane 
-are shown in rows, noted in the left-hand column. Red triangles, black squares, 
-error bars, and background points are as in Fig.~\ref{fig:age_alpha} for the 
-corresponding Galactic region. The solid black line connects the black squares 
-in the bottom, left-middle panel, and is replicated elsewhere for reference. } 
-\label{fig:age_alpha_regions} 
-\end{figure*}
-
-In Fig.~\ref{fig:age_alpha_regions}, we extend the comparison of our base-line, 
-inside-out model and the observations of~\citet{Feuillet2019} to other 
-Galactic regions. We visualize the data there in the same manner as for 
-previous figures in this section. While the inside-out model shows the best 
-agreement with the observed result in the solar annulus, there are some mild 
-discrepancies for stars farther from the sun.~\citet{Feuillet2019} report ages 
-for~$\alpha$-rich stars that are younger at large~$R_\text{gal}$ and high 
-$\left|z\right|$, though in most cases only by~$\sim$20\%. Our model does not 
-capture this effect. To illustrate this, we connect the black squares in the 
-panel corresponding to the solar annulus with a black line, and then reproduce 
-this line in all panels for reference. If the observational result is correct, 
-this is an interesting effect that our model doesn't reproduce in any of the 
-variants we've explored. Furthermore, we note that the model overpredicts ages 
-at large~$\left|z\right|$. As with the overpredicted [O/Fe] ratios at small 
-$R_\text{gal}$, we speculate that this may be tied to the Sagittarius dwarf 
-(see discussion in~\S~\ref{sec:obs_comp:ofe_dists}). By using a hydrodynamical 
-simulation of a 
-galaxy which exhibited more pericentric passages of a massive satellite, more 
-young stars may be kinematically heated to high~$\left|z\right|_\text{max}$ 
-orbits. This is another instance where running our models with a different 
-hydrodynamical simulation's star particles may be an enlightening comparison. 
-\par 
-We note that the intrinsic scatter in the age-[O/Fe] relation is predicted to 
-grow with increasing~$R_\text{gal}$; this can be seen in the error bars on the 
-black squares as well as the coloured points. We identify two sources of this 
-dependence; the bulk of the scatter, at least at [O/Fe]~$\gtrsim$~+0.05, arises 
-from the variability in the SN Ia rates as described in~\S 
-\ref{sec:obs_comp:gradient}. Having demonstrated that the SN Ia rate is most 
-variable at large~$R_\text{gal}$, the in-situ populations in the outskirts of 
-the Galactic disc formed from an ISM whose gas-phase [O/Fe] ratio varied with 
-a higher amplitude. Since the observational signature of this variability is 
-scatter in the observed age-[O/Fe] relation, our model predicts the most 
-intrinsic scatter in Galactic regions where that variability has the highest 
-amplitude. Second, the analytic models of~\citet{Weinberg2017} suggest that 
-as the e-folding timescale for star formation~$\tau_\text{sfh}$ increases, the 
-model-predicted [O/Fe] of the youngest stars increases with a weak dependence. 
-With a range of e-folding timescales in our model, this implies a distribution 
-of [O/Fe] at age = 0 with nonzero width without considering the migration of 
-nucleosynthetic yields. This can be seen in the post-processing model 
-predicted age-[O/Fe] relation in Fig.~\ref{fig:age_alpha}. In this pathway, 
-scatter is induced by mixing populations that follow age-[O/Fe] relations of 
-slightly different normalizations which are nearly flat intrinsically, 
-producing a noticeably wide age distribution near solar [O/Fe]. 
-\par 
-Although the iron-peak is the only class of elements with a delayed 
-nucleosynthetic source that we consider in the present paper, we expect similar 
-results for other delayed sources with regard to the variability in enrichment 
-rates and scatter in age-[X/Y] relations. The details of SN Ia nucleosynthesis 
-did not matter in our interpretations in this section; it is based purely on 
-the characteristic delay-times of the source and how they compare to the 
-timescales of stellar migration. Our models should then find similar 
-predictions with, for example, s-process (slow neutron capture) elements like 
-carbon, nitrogen, strontium, yttrium, and zirconium produced in asymptotic 
-giant branch stars. In fact, using hydrodynamical simulations from the Auriga 
-project~\citep{Grand2017},~\citet{vandeVoort2020} find that the intrinsic 
-scatter in r-process (rapid neutron capture) abundances increases for models 
-with longer characteristic delay times. Although the first observations of a 
-binary neutron star merger (GW170817) exhibited an optical counterpart which 
-was consistent with being powered by the radioactive decay of r-process 
-elements~\citep{Abbott2017, Coulter2017, Drout2017, Pian2017}, it remains 
-unclear the extent to which neutron star mergers contribute to r-process 
-nucleosynthesis in the universe~\citep{Cote2019, Mishenina2019, Siegel2019, 
-vandeVoort2020, Vincenzo2021b}. Although it's likely unfeasible at present due 
-to the requirement for high precision abundance measurements of intrinsically 
-rare elements in many stars, with future observational capabilities, the 
-application of our results as well as~\citet{vandeVoort2020} suggests that the 
-intrinsic scatter in r-process abundances may provide constraints on the 
-characteristic delay times of such nucleosynthetic events.
-
-\subsection{The Age-Metallicity Relation} 
-\label{sec:obs_comp:amr}
-
-% fig 15 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.35]{amr_static_o.pdf} 
-\caption{The age-[O/H] relation predicted by our constant SFH model for 
-$R_\text{gal}$~= 7 - 9 kpc (left) and 11 - 13 kpc (right). Each panel plots 
-only the~$\left|z\right|\leq$~0.5 kpc population. The colored points in the 
-background and the black squares with error bars are as in Fig. 
-\ref{fig:age_alpha}, but with our binned, model prediction quantified in 
-bins of~$\Delta$[O/H] = 0.05. } 
-\label{fig:age_oh_static} 
-\end{figure}
-
-Although the age-metallicity relation (AMR) is usually formulated in terms of 
-[Fe/H], it is also interesting to quantify the age-[O/H] relation, because it 
-is not affected by SN Ia enrichment. The extent to which they differ indicates 
-the extent to which the delayed timescale and impact of migration on SN Ia 
-enrichment is important in shaping the age-[Fe/H] relation. In Fig. 
-\ref{fig:age_oh_static}, we present the age-[O/H] relation predicted by our 
-constant SFH model for the~$\left|z\right|\leq$~0.5 kpc population at 
-$R_\text{gal}$ = 7 - 9 and 11 - 13 kpc. The black squares with error bars 
-denote the mass-weighted median age as in~\S~\ref{sec:obs_comp:age_alpha}, and 
-we again plot the individual stellar populations in the background for 
-reference, colour-coded according to their Galactocentric radius of birth. We 
-omit the~\citet{Feuillet2019} measurements from this figure, because the 
-constant SFH model is of purely theoretical interest, removing the effects of 
-a time-varying SFH while including the effects of stellar migration. 
-\par 
-The intrinsic scatter in the observed AMR has previously been interpreted as 
-evidence for radial mixing~\citep{Edvardsson1993, Sellwood2002}. In the 
-solar neighbourhood,~\citet{Feuillet2018} demonstrate that the most metal-rich 
-stars tend to be significantly older than solar metallicity stars. Using the 
-\citet{Weinberg2017} analytic models of one-zone chemical evolution, they argue 
-that this is the result of old stars born at small~$R_\text{gal}$ where the 
-equilibrium abundance is high. Only the old stars are able to migrate to 
-the solar neighbourhood due to the time required for such a change in their 
-orbital radius. 
-\par 
-The results of our constant SFH model illustrated in Fig. 
-\ref{fig:age_oh_static} extend our understanding of this effect. In both 
-regions plotted, the youngest stars form with a composition inherited from the 
-local ISM, which in this model, is reflective of the late-time equilibrium 
-abundance. At a given age, only stars born in a well-defined region of the 
-Galaxy will have had adequate time to migrate to a given present-day radius. 
-Since a range of~$R_\text{gal}$ maps directly to a range of metallicity once 
-the ISM is arbitrarily close to the equilibrium abundance in our model, this 
-necessitates a maximum width of the [O/H] distribution at fixed age. With 
-increasing age, the [O/H] distribution then gets wider because any given 
-present-day radius samples stars formed at a wider range of~$R_\text{gal}$. 
-In Fig.~\ref{fig:age_oh_static}, we indeed see this effect, with the 
-colour-coding of the background points making it clear that stellar migration 
-is the culprit. In the outer Galaxy, migration has a particularly interesting 
-effect in that it only adds old stars above the equilibrium metallicity; in 
-the~$R_\text{gal}$ = 11 - 13 kpc region, our model as a consequence predicts 
-an AMR where the population-averaged trend where [O/H] is nearly monotonically 
-increasing with age. This is entirely backwards from what is expected from 
-one-zone models of GCE~\citep[e.g.][]{Andrews2017, Weinberg2017, Johnson2020}.
-
-% fig 16 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.45]{amr_solar_annulus.pdf} 
-\caption{The age-[O/H] (top) and age-[Fe/H] (bottom) relations for the solar 
-annulus (i.e.~$R_\text{gal}$ = 7 - 9 kpc,~$\left|z\right|\leq$~0.5 kpc) as 
-predicted by our inside-out SFH. Red triangles, black squares, error bars, and 
-background points are as in Fig.~\ref{fig:age_alpha}, but with our model 
-predicted quantified in bins of~$\Delta$[O/H] =~$\Delta$[Fe/H] = 0.05. For 
-comparison, we plot the~\citet{Feuillet2018} measurements in a dark red line, 
-omitting the associated uncertainties for visual clarity. } 
-\label{fig:amr_solar_annulus} 
-\end{figure}
-
-We continue our assessment of the model-predicted AMR by illustrating in Fig. 
-\ref{fig:amr_solar_annulus} the age-[O/H] (top) and age-[Fe/H] (bottom) 
-relations predicted for the solar annulus (i.e.~$R_\text{gal}$~= 7 - 9 kpc and 
-$\left|z\right|\leq$~0.5 kpc). The red triangles, black squares, coloured 
-points, and error bars are as in previous figures in~\S 
-\ref{sec:obs_comp:age_alpha}. For reference, we add the solid dark red line, 
-which denotes the AMR measured by~\citet{Feuillet2018}. Although our model 
-shows decent agreement with the~\citet{Feuillet2019} measurements in the solar 
-annulus,~\citet{Feuillet2018} report ages for solar metallicity stars which 
-are considerably younger ($\sim$1 - 2 Gyr as opposed to~$\sim$3 - 4 Gyr). 
-The~\citet{Feuillet2018} data would suggest our inside-out model requires an 
-enhancement in the recent SFR to increase the frequency of young, solar 
-metallicity stars. Although our late-burst and outer-burst models include 
-such effects, motivated by recent observations suggesting this exact 
-evolutionary history~\citep{Mor2019, Isern2019}, the differences between the 
-\citet{Feuillet2018} and~\citet{Feuillet2019} measurements are interesting in 
-and of themselves.
-
-% fig 17 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.35]{amr_insideout_vs_lateburst_fe.pdf} 
-\caption{The age-[Fe/H] relation predicted by our inside-out (top) and 
-late-burst (bottom) SFHs for~$R_\text{gal}$ = 5 - 7 kpc (left), 7 - 9 kpc 
-(left middle), 9 - 11 kpc (right middle), and 11 - 13 kpc (right). Each panel 
-shows only the~$\left|z\right|\leq$~0.5 kpc population. Red triangles, black 
-squares, error bars, and coloured points are as in Fig.~\ref{fig:age_alpha} for 
-the corresponding Galactic region, but with our model prediction quantified in 
-bins of~$\Delta$[Fe/H] = 0.05. } 
-\label{fig:amr_insideout_vs_lateburst_fe} 
-\end{figure*}
-
-Motivated by this, we compare the predictions of the inside-out and late-burst 
-SFH models to the~\citet{Feuillet2019} age-[Fe/H] relation in Fig. 
-\ref{fig:amr_insideout_vs_lateburst_fe}. We retain the same plotting scheme 
-used throughout this section and~\S~\ref{sec:obs_comp:age_alpha}, illustrating 
-the inside-out model in the top row and the late-burst model in the bottom row. 
-Each column corresponds to a specific range in~$R_\text{gal}$, denoted at the 
-top of the figure. Beyond the solar annulus, we note that our inside-out model 
-has a number of short-comings in comparison to the~\citet{Feuillet2019} 
-measurements. At~$R_\text{gal}$ = 5 - 7 kpc, it overpredicts the characteristic 
-ages of [Fe/H]~$\approx$~-0.3 - 0 stars. At~$R_\text{gal}$ = 9 - 11 and 11 - 13 
-kpc, it mildly overpredicts ages at most abundances, and fails to reproduce the 
-trend seen in the observed sample. The same can be said about the 
-$R_\text{gal}$~=5 - 7 kpc region, and although the overall agreement is 
-generally good there, one could reasonably argue this for the solar annulus as 
-well. 
-\par 
-The late-burst model improves upon these shortcomings of the inside-out model 
-considerably. At~$R_\text{gal}$ = 5 - 7 kpc, the overpredicted ages at solar 
-and mildly sub-solar [Fe/H] is no longer present; this is also true at 
-$R_\text{gal}$~= 9 - 11 and 11 - 13 kpc. Furthermore, the trend is much better 
-reproduced at all radii in the late-burst than the inside-out model. The only 
-different between the late-burst and inside-out model being the recent 
-enhancement in the SFR, this is what drives the differences in model 
-predictions. To fuel the starburst as we have parameterized it,~\texttt{VICE} 
-calculates that there must be substantial gas accretion (see the infall rate 
-$\dot{\Sigma}_\text{in}$ as a function of radius and time in Fig. 
-\ref{fig:evol}). In our models, we assume accretion to always be of zero 
-metallicity gas. As a result, the model predicts dilution of the ISM Fe 
-abundance during the starburst; this can be seen by the trend of the coloured 
-points in Fig.~\ref{fig:amr_insideout_vs_lateburst_fe} to lower [Fe/H] at ages 
-of~$\sim$2 - 3 Gyr. At this time, the star formation rate is elevated by 
-construction. The net effect is to increase the frequency of~$\sim$2 - 3 Gyr 
-old stars with near- and sub-solar abundances globally, which lowers the 
-characteristic ages of stars at these metallicities relative to the inside-out 
-model. Using the~\citet{Feuillet2019} measurements as the observational 
-benchmark, we favor the late-burst model here. 
-\par 
-Although there appears to be a vertical offset between the observed result and 
-the model prediction at~$R_\text{gal}$ = 9 - 11 and 11 - 13 kpc, this is still 
-an improvement upon the inside-out model. It's possible that this points to a 
-need for higher yields of Fe than we've adopted here, though it's unclear if 
-this would negatively affect the agreement at~$R_\text{gal}$~= 5 - 7 and 7 - 9 
-kpc. It's possible that our parameterization of the mass-loading factor~$\eta$ 
-scales too strongly with~$R_\text{gal}$ in the outer Galaxy (see discussion in 
-\S~\ref{sec:methods:yields}). Alternatively, outflows in nature may be more 
-efficient at removing some elements from the ISM than others; this could impact 
-the overall normalization of the AMR at different radii. Our models in the 
-present paper assume that outflows always proceed exactly at the metallicity of 
-the ISM, but some authors argue that outflows can have a different metallicity 
-- usually a higher one - due to containing in some part the metal-rich 
-supernova ejecta that was added directly to the outflow by the explosions 
-(observationally:~\citealp*{Chisholm2018}; in simulations: 
-\citealp{Christensen2018}). 
-\par 
-We also note that the late-burst model predicts particularly young 
-characteristic ages for the most metal-rich bins at~$R_\text{gal}$ = 5 - 7 kpc. 
-This is purely a consequence of our choice to use the mass-weighted median as 
-the population-averaged age measurement at fixed abundance. In this case, our 
-model is simply reporting the 50th percentile of an age-distribution 
-which is noticeably bimodal; as a result, whether or not the characteristic 
-ages we report there are <1 Gyr or in better agreement with the 
-\citet{Feuillet2019} measurements strongly depends on how we've parameterized 
-the recent starburst as a function of both time and radius. Here we've made the 
-simplest assumption of letting have the same time-dependence at all radii, 
-which was not necessarily the case. 
-\par 
-Although we demonstrate here that the late-burst model describes the age-[Fe/H] 
-relation reported by~\citet{Feuillet2019} better than the inside-out model, we 
-found the exact opposite with regard to the age-[$\alpha$/Fe] relation with 
-the same obesrvational sample in~\S~\ref{sec:obs_comp:age_alpha}. It's unlikely 
-this discrepancy can be mitigated using any model which exhibits a recent 
-starburst as parameterized here; as we demonstrated in~\S 
-\ref{sec:obs_comp:age_alpha}, such models predict a global increase in 
-[$\alpha$/Fe] due to the perturbed ratio of CCSN and SN Ia rates 
-\citep{Johnson2020}, a feature which simply isn't seen in the 
-\citet{Feuillet2019} measurements. It's possible that the Milky Way experienced 
-dilution with no ensuing starburst - this would be the case if the majority of 
-the accreted gas was warm, neutral and ionized gas which simply hasn't yet been 
-made available for star formation. Such a scenario would exhibit some of the 
-predictions of the late-burst model, but without the increase in [O/Fe] at late 
-times, potentially allowing it to simultaneously explain the age-[$\alpha$/Fe] 
-relation and AMR as they are observed. However, these models would be at odds 
-with the findings of~\citet{Mor2019} and~\citet{Isern2019}. 
-\par 
-We remark that we find similar results for the age-[O/H] relation; furthermore, 
-as in~\S~\ref{sec:obs_comp:age_alpha} for the age-[$\alpha$/Fe] relation, we 
-also find for the age-[Fe/H] and age-[O/H] relations that our models tend to 
-overpredict ages with increasing~$\left|z\right|$. Lastly, we caution future 
-studies against basing the likelihood of a chemical evolution model on data 
-for the solar annulus alone. In Fig.~\ref{fig:amr_solar_annulus}, we 
-noted that there was decent agreement between the inside-out SFH model and 
-the~\citet{Feuillet2019} measurements of the age-[O/H] and age-[Fe/H] 
-relations in the solar annulus, but upon extending the comparison to other 
-Galactic regions in Fig.~\ref{fig:amr_insideout_vs_lateburst_fe}, a number of 
-shortcomings revealed themselves. Although to some extent this is made possible 
-only recently with observational capabilities now allowing statistical 
-measurements of these correlations for stars at greater distances from the sun, 
-had we stopped there, we would have missed this interesting and peculiar 
-result.
-
-\section{Discussion \& Conclusions} 
-\label{sec:conclusions} 
-In this paper, we have modeled the Milky Way as a series of concentric annuli 
-with a~$\Delta R_\text{gal}$~= 100 pc width, describing each annulus as a 
-conventional one-zone chemical evolution model and allowing the exchange of 
-stellar populations between zones to include the impact of stellar migration in 
-the model Galaxy. Though there have been a handful of studies which employ a 
-similar methodology~\citep{Schoenrich2009, Nidever2015, Sharma2020}, ours and 
-the~\citet{Minchev2013, Minchev2014, Minchev2017} model are the only ones which 
-make use of a hydrodynamical simulation to describe radial mixing, for which we 
-make use of the~\texttt{h277} zoom-in simulation~\citep{Christensen2012, 
-Zolotov2012, Loebman2012, Loebman2014, Brooks2014}. This yields a model for 
-migration which does not have any free parameters (see discussion in~\S 
-\ref{sec:methods:h277}). 
-\par 
-Our model predicts masses and abundances for simple stellar populations, a 
-given number of which form at each timestep. Each stellar 
-population is then assigned a star particle from~\texttt{h277} which was born 
-at a similar radius and time to act as an~\textit{analog}. The stellar 
-population in our model then assumes the change in radius~$\Delta R_\text{gal}$ 
-of the analog at face value, and is assumed to reside at the same present day 
-height above/below the disc midplane~$\left|z\right|$. We then construct four 
-models describing the time-dependence with which stellar populations move to 
-their present-day radii, taking one in which radius changes with a 
-$\sqrt{\text{age}}$-dependence in the fiducial model based on~\citet[][see 
-Fig.~\ref{fig:migration_schema} and discussion in~\S 
-\ref{sec:methods:migration}]{Frankel2018, Frankel2020}. 
-\par 
-We assume SN yields and a SN Ia delay-time distribution based on 
-a combination of theoretical and empirical constraints. The main free 
-parameters are the star formation law parameterizing the SFE timescale 
-$\tau_\star$ (see discussion in~\S~\ref{sec:methods:sfe}), the mass-loading 
-factor~$\eta(R_\text{gal})$~describing the strength of outflows (assumed to be 
-time-independent; see discussion in~\S~\ref{sec:methods:yields}), and the SFH. 
-The first we choose from the observed~$\dot{\Sigma}_\star - \Sigma_\text{g}$ 
-relation in local spirals~\citep{Bigiel2010, Leroy2013, Krumholz2018}. The 
-second is chosen to reproduce the metallicity gradient as observed 
-\citep{Daflon2009, Frinchaboy2013, Hayden2014, Weinberg2019}. Our fiducial 
-model then has an inside-out SFH with e-folding timescales calibrated to the 
-\citet{Sanchez2020} data (see discussion in~\S~\ref{sec:methods:sfhs}). 
-Motivated by the results of~\citet{Mor2019} and~\citet{Isern2019} suggesting 
-such an evolutionary history, we construct models which exhibit a recent burst 
-in star formation on top of the base-line model, as well as a constant SFH 
-model of purely theoretical interest. 
-\par 
-We find that when stellar migration proceeds in a manner in which a star's 
-orbital radius changes continuously with time, the SN Ia rate as a function of 
-both radius and time exhibits significant variability. The characteristic delay 
-time of a single SN Ia event is~$\sim$1 Gyr~\citep{Maoz2012, Maoz2017}, and 
-stars are migrating a significant distance in the radial direction on similar 
-timescales in our models. The result is a SN Ia rate which, at fixed radius, 
-tends to follow that which is expected from the SFH when averaged with time, 
-but whose instantaneous value may be considerably larger or smaller. Our model 
-predicts the amplitude of this variability to grow with increasing radius due 
-to sampling noise and the inverse dependence of the stellar surface density on 
-$R_\text{gal}$. We demonstrate that this is a mechamism with which truly young, 
-super-solar [$\alpha$/Fe] stars can form. When the SN Ia rate increases or 
-decreases, the Fe abundance in the ISM increases or 
-decreases accordingly; this in turn affects the gas-phase [$\alpha$/Fe] ratio, 
-and the stars which form at these times inherit these compositions. Of the 
-young stars, those with the highest [$\alpha$/Fe] form at large~$R_\text{gal}$ 
-($\gtrsim$~12 kpc) due to the radial dependence of the amplitude; a subsample 
-of these stars can then migrate to the solar annulus. 
-\par 
-To our knowledge, this mechanism lends the first theoretical explanation of 
-truly young $\alpha$-rich stars in the solar neighbourhood, revealed recently 
-by the observations of the APOGEE survey~\citep{Martig2016, Feuillet2018, 
-Feuillet2019, SilvaAguirre2018}.~\citet{SilvaAguirre2018} find that 
-these stars have kinematics consistent with the rest of the high-$\alpha$ 
-population, and postulate based on this that these stars are the consequence 
-of stellar mergers or mass transfer events, making truly old stars simply 
-appear younger. In a sample of 51 young~$\alpha$-rich red giants, 
-\citet{Hekker2019} demonstrate using cabon-to-nitrogen ratios that a portion of 
-these stars are indeed old, but that these effects cannot account for the 
-entire population. We argue based on our results that the truly young ones 
-formed at large~$R_\text{gal}$~at a time when the ISM was intrinsically 
-$\alpha$-rich due simply to a deficit in SN Ia events caused by a net loss of 
-white dwarf progenitors to stellar migration. We remark that our model would 
-sugest that these stars have super-solar [$\alpha$/Fe] not because they are 
-$\alpha$-rich, but rather that they are Fe-poor. 
-\par 
-We find that our model adequately reproduces the variations in MDFs with 
-Galactocentric radius in the disc~\citep{Hayden2015}. Although there is a 
-potential for improved agreement in the~$R_\text{gal}$~= 3 - 5 kpc bin, the 
-model nonetheless performs well. With increasing~$\left|z\right|$, the 
-prediction breaks down somewhat. Where the observational data show a 
-convergence of the MDFs at all radii to a skew-positive distribution with 
-mode([O/H])~$\approx$~mode([Fe/H])~$\approx$~-0.5, our model predicts the mode 
-abundance in the inner Galaxy to decrease slightly, though not to the same 
-extent as in the observations, while the distributions at larger~$R_\text{gal}$ 
-are less affected (see Figs.~\ref{fig:mdf_3panel_fe} and~\ref{fig:mdf_3panel_o} 
-and discussion in~\S~\ref{sec:obs_comp:mdfs}). While the model accounts for a 
-portion of these effects, it cannot explain the entire~$z$-dependence of the 
-MDF shape. 
-\par 
-We demonstrate the dependence of the relative frequency of high-$\alpha$ and 
-low-$\alpha$ sequence stars on Galactic position (see, e.g., Fig. 4 of 
-\citealp{Hayden2015}) is at least in part a consequence of stellar migration. 
-In our fiducial inside-out SFH model, low [Fe/H], high [$\alpha$/Fe] stars 
-are the dominant population at small~$R_\text{gal}$~and high~$\left|z\right|$; 
-conversely, low [$\alpha$/Fe] stars are most common at large~$R_\text{gal}$ 
-and low~$\left|z\right|$. We clarify that this is not an explanation for the 
-\textit{origin} of the two sequences - only the spatial dependence thereof. 
-In fact, our model is unable to account for the presence of the infamous 
-[$\alpha$/Fe] dichotomy in any of the variants we've explored. While it is able 
-to reproduce the broad nature of the [O/Fe] distributions at fixed [Fe/H] and 
-may show a convincing two-peaked profile in a specific Galactic region, it 
-fails to do so for the entire Galaxy at all metallicities; the principle 
-failure is an overpredicted frequency of intermediate [$\alpha$/Fe] stars. This 
-is in contrast to the findings of~\citet{Sharma2020}, who claim to reproduce 
-the bimodality in a model assuming an inside-out SFH with stellar migration. 
-However, they do not demonstrate that the enrichment history of their model 
-follows self-consistently from their assumed SFH. We therefore argue that 
-an inside-out SFH is not conducive to forming the abundance distributions 
-observed in the Milky Way. Though we don't investigate such evolutionary 
-pathways in the present paper, our models fail in such a manner that suggests 
-the agreement can best be improved by the three-phase SFH of the two-infall 
-model~\citep{Chiappini1997, Chiappini2001, Romano2010, Grisoni2017, 
-Noguchi2018, Palla2020, Spitoni2016, Spitoni2018, Spitoni2019a, Spitoni2020, 
-Spitoni2021}. We reserve an investigation into more sophisticated forms of the 
-Galactic SFH for future work. 
-\par 
-We find that the age-[O/Fe] relation as reported by~\citet{Feuillet2019} is 
-well-characterized by our inside-out SFH. In the case of our recent 
-starburst models motivated by~\citet{Mor2019} and~\citet{Isern2019}, the 
-elevation of the SFR necessitates an increase in [$\alpha$/Fe] for young 
-stars owing to the increased rate of CCSNe before the onset of SN Ia associated 
-with the starburst~\citep{Johnson2020}, introducing a trend which simply isn't 
-seen in the observations. This suggests that recent studies finding an 
-elevation in the 
-Galactic SFR~$\sim$2 Gyr ago are at odds with chemical evolution models, which 
-based on the monotonic nature of the observed AMR would put constraints on the 
-amount of variability out to lookback times of~$\sim$8 Gyr. Lastly, we find 
-that our model predicts the intrinsic scatter in the age-[$\alpha$/Fe] relation 
-to increase with~$R_\text{gal}$; this traces back to the variability in the SN 
-Ia rates having a higher amplitude in the outer Galaxy, which produces an 
-in-situ population with a larger dynamic range in [O/Fe]. 
-\par 
-We find that the AMR (both age-[O/H] and age-[Fe/H]) in the solar annulus as 
-measured by~\citet{Feuillet2019} is well-described by our inside-out SFH. 
-However, when this comparison is extended to other Galactic regions, the 
-inside-out model overpredicts ages in multiple regions and fails to reproduce 
-the population-averaged trend throughout the disc. We demonstrate that our 
-late-burst model can account for these discrepancies, suggesting that the 
-observed AMR favors a model with a recent enhancement in the Galactic SFR. 
-Somewhat confusingly, the impact of the late-burst model is such that it is 
-convincingly rejected by the age-[O/Fe] relation but convincingly favored by 
-the age-[O/H] and age-[Fe/H] relations. 
-\par 
-We thus conclude that no single model in the present paper can explain all of 
-the observables of interest here. This suggests that 
-conventional assumptions about the evolution of the Milky Way, such as an 
-inside-out SFH with stellar migration, are not sufficiently accurate to 
-understand the enrichment history of the Milky Way in detail. This is an 
-indication that at present there is more astrophysical information in already 
-collected observations than the most recent GCE models can explain. It's likely 
-our models are missing at least one key component with a significant impact on 
-the predicted abundances. 
-\par 
-Lastly, we remark on the low number of multi-zone chemical evolution models in 
-the literature, some with and some without migration. In this paper, we present 
-only a handful of models whose predictions can be calculated with a combined 
-CPU-time comparable to a single working day. These models make straight-forward 
-predictions which can easily be compared to publicly-available observed data. 
-Though they are extremely useful in many respects, these medium resolution, 
-medium computational expense techniques can test assumptions about the 
-evolutionary history of the Milky Way with more control over the parameters and 
-much less computational expense than the higher overhead hydrodynamical 
-simulations; our models here constitute an example of a combination of the two. 
-\par 
-\texttt{VICE} is publicly available and open-source;\footnote{
-	Install (PyPI): \url{https://pypi.org/project/vice} \\ 
-	Documentation: \url{https://vice-astro.readthedocs.io} \\ 
-	Source Code: \url{https://github.com/giganano/VICE.git} 
-} it can be installed in a~\texttt{Unix} terminal via~\texttt{pip install vice}. 
-\texttt{Python} code which runs the simulations presented in this paper is 
-included as supplementary material in the~\texttt{GitHub} repository; our 
-models can be ran directly from a terminal without modifying the source code, 
-and are capable of predicting abundances for~$\sim$2 million stellar 
-populations in~$\sim$2.5 CPU-hours running on a single core on personal 
-computers.
-
-\section{Acknowledgements} 
-\label{sec:acknowledgements} 
-We acknowledge valuable discussion with, in no particular order, Emily 
-Griffith, Jennifer Johnson, Todd Thompson, Jiayi Sun, Amy Sardone, Adam Leroy, 
-Grace Olivier, the Ohio State Astronomy Gas, Galaxies, and Feedback group, and 
-various participants of the SDSS Gotham 2020 virtual collaboration meeting and 
-the virtual 236th meeting of the American Astronomical Society. This work was 
-supported in part by National Science Foundation grant AST-1909841. D.H.W. 
-is grateful for the hospitality of the Institute for Advanced Study and the 
-support of the W.M. Keck Foundation. 
-\par 
-In this paper we have made use of data from SDSS-IV APOGEE-2 DR16. 
-Funding for the Sloan Digital Sky 
-Survey IV has been provided by the 
-Alfred P. Sloan Foundation, the U.S. 
-Department of Energy Office of 
-Science, and the Participating 
-Institutions. 
-\par 
-SDSS-IV acknowledges support and 
-resources from the Center for High 
-Performance Computing  at the 
-University of Utah. The SDSS 
-website is~\url{www.sdss.org}.
-\par 
-SDSS-IV is managed by the 
-Astrophysical Research Consortium 
-for the Participating Institutions 
-of the SDSS Collaboration including 
-the Brazilian Participation Group, 
-the Carnegie Institution for Science, 
-Carnegie Mellon University, Center for 
-Astrophysics | Harvard \& 
-Smithsonian, the Chilean Participation 
-Group, the French Participation Group, 
-Instituto de Astrof\'isica de 
-Canarias, The Johns Hopkins 
-University, Kavli Institute for the 
-Physics and Mathematics of the 
-Universe (IPMU) / University of 
-Tokyo, the Korean Participation Group, 
-Lawrence Berkeley National Laboratory, 
-Leibniz Institut f\"ur Astrophysik 
-Potsdam (AIP),  Max-Planck-Institut 
-f\"ur Astronomie (MPIA Heidelberg), 
-Max-Planck-Institut f\"ur 
-Astrophysik (MPA Garching), 
-Max-Planck-Institut f\"ur 
-Extraterrestrische Physik (MPE), 
-National Astronomical Observatories of 
-China, New Mexico State University, 
-New York University, University of 
-Notre Dame, Observat\'ario 
-Nacional / MCTI, The Ohio State 
-University, Pennsylvania State 
-University, Shanghai 
-Astronomical Observatory, United 
-Kingdom Participation Group, 
-Universidad Nacional Aut\'onoma 
-de M\'exico, University of Arizona, 
-University of Colorado Boulder, 
-University of Oxford, University of 
-Portsmouth, University of Utah, 
-University of Virginia, University 
-of Washington, University of 
-Wisconsin, Vanderbilt University, 
-and Yale University.
-
-\textit{Software}: Matplotlib~\citep{Matplotlib}; Astropy~\citep{Astropy2013, 
-Astropy2018}; NumPy~\citep{NumPy}.
-
-\section{Data Availability} 
-\label{sec:data_availability} 
-\texttt{VICE} is open-source software, and the code which computes abundances 
-for our models is publicly available as well. In the GitHub repository, we 
-provide detailed instructions on how to run our models and variations thereof. 
-All observational data appearing in this paper is publicly available, and is 
-also included with the source code for our models and figures.
+\subfile{intro.tex} 
+\subfile{methods.tex} 
+\subfile{comparison_observations.tex} 
+\subfile{conclusions.tex} 
+\subfile{acknowledgements.tex} 
+\subfile{data_availability.tex}
 
 \begin{appendices} 
-
-\section{Normalizing the Star Formation History} 
-\label{sec:normalize_sfh} 
-In this appendix, we derive a prescription for calculating the prefactors of an 
-adopted star formation history (SFH) for each annulus in our models. As 
-mentioned in~\S~\ref{sec:methods:sfhs}, this procedure requires a unitless 
-description of the time-dependence of the SFH in each annulus, denoted 
-$f(t|R_\text{gal})$, and a unitless description denoting the radial dependence 
-of the stellar surface density~$g(R_\text{gal})$. By additionally selecting a 
-total stellar mass of the present day model Galaxy, the solution to the 
-detailed form of the star formation history 
-$\dot{\Sigma}_\star(t, R_\text{gal})$ is unique. With this approach, we assume 
-that stellar migration does not significantly impact the form of 
-$g(R_\text{gal})$, an assumption we demonstrate to be accurate in~\S 
-\ref{sec:methods:surface_density_gradient}. 
-\par 
-The surface density of star formation with units of mass per area per time can 
-be expressed in terms of~$f(t|R_\text{gal})$ as: 
-\begin{equation} 
-\dot{\Sigma}_\star(t, R_\text{gal}) = \dot{\Sigma}_\star(t = 0, R_\text{gal}) 
-f(t|R_\text{gal}) 
-\label{eq:sfh_terms_of_f} 
-\end{equation} 
-and the present-day radial surface density gradient with units of mass per area 
-as: 
-\begin{equation} 
-\Sigma_\star(R_\text{gal}) = \Sigma_\star(R_\text{gal} = 0) g(R_\text{gal}) 
-\label{eq:sigma_terms_of_g}  
-\end{equation} 
-The integral of~$\dot{\Sigma}_\star$ with time should yield the surface density 
-gradient at a given radius~$R_\text{gal}$, up to a prefactor accounting for the 
-return of stellar envelopes to the interstellar medium (ISM): 
-\begin{subequations}\begin{align} 
-\Sigma_\star(R_\text{gal}) &= (1 - r)\int_0^T \dot{\Sigma}_\star(t, 
-R_\text{gal}) dt 
-\\ 
-&= (1 - r) \dot{\Sigma}_\star(t = 0, R_\text{gal})\int_0^T f(t|R_\text{gal}) dt 
-\\ 
-\dot{\Sigma}_\star(t = 0, R_\text{gal}) &= \Sigma_\star(R_\text{gal}) 
-\left[(1 - r) \int_0^T f(t|R_\text{gal})dt\right]^{-1} 
-\\ 
-&= \Sigma_\star(R_\text{gal} = 0)g(R_\text{gal}) \left[(1 - r) \int_0^T 
-f(t|R_\text{gal})\right]^{-1} 
-\label{eq:intermediate_1} 
-\end{align}\end{subequations} 
-where~$(1 - r) \approx 0.6$~is an adequate approximation for a 
-\citetalias{Kroupa2001} IMF~\citep[][see discussion in their~\S 
-2.2]{Weinberg2017}. This expression relates the two unkowns introduced by 
-equations~\refp{eq:sfh_terms_of_f} and~\refp{eq:sigma_terms_of_g}. We continue 
-by asserting that the integral of the stellar surface density over the area of 
-the disc should be equal to the present-day stellar mass of the Milky Way: 
-\begin{subequations}\begin{align} 
-M_\star^\text{MW} &= \int_0^R \Sigma_\star(R_\text{gal}) 2\pi R_\text{gal} 
-dR_\text{gal} 
-\\ 
-&= \Sigma_\star(R_\text{gal} = 0) \int_0^R g(R_\text{gal}) 2\pi R_\text{gal} 
-dR_\text{gal} 
-\\ 
-\Sigma_\star(R_\text{gal} = 0) &= M_\star^\text{MW} \left[\int_0^R 
-g(R_\text{gal}) 2\pi R_\text{gal}dR_\text{gal}\right]^{-1} 
-\label{eq:intermediate_2} 
-\end{align}\end{subequations} 
-\par 
-Now plugging equation~\refp{eq:intermediate_2} into equation 
-\refp{eq:intermediate_1}, and then that into equation~\refp{eq:sfh_terms_of_f} 
-yields the desired result: 
-\begin{subequations}\begin{align} 
-&\dot{\Sigma}_\star(t, R_\text{gal}) = Af(t|R_\text{gal})g(R_\text{gal}) 
-\\ 
-&A = M_\star^\text{MW}\left[(1 - r) \int_0^R g(R_\text{gal})2\pi R_\text{gal} 
-dR_\text{gal} \int_0^T f(t|R_\text{gal})dt\right]^{-1} 
-\end{align}\end{subequations} 
-where the upper limits should be the maximum radius of star formation and the 
-end time of the simulation (15.5 kpc and 12.2 Gyr in this paper). This result 
-makes intuitive sense, simply stating that the required normalization of 
-$f(t|R_\text{gal})$~is specified by two things: the total stellar mass of the 
-Galaxy and how steep the stellar density falls with increasing radius. As long 
-as the assumption that stellar migration does not significantly alter the form 
-of~$g(R_\text{gal})$~is not violated, this procedure can be used to calculate 
-prefactors for future models of disc galaxies.
-
+\subfile{age_oh.tex} 
+\subfile{normalize_sfh.tex} 
+\subfile{vice.tex} 
 \end{appendices}
@@
 \bibliographystyle{mnras} 
-\bibliography{draft1}
+\bibliography{ms}
 

### 2021-08-04 chemev/MWbimodality/paper/draft2/normalize_sfh.tex
migration paper referee response

--- 2021-08-04 chemev/MWbimodality/paper/draft1/draft1.tex
@@
-\documentclass[fleqn, usenatbib]{mnras} 
-\usepackage{newtxtext, newtxmath} 	% Required for MNRAS 
-\usepackage[T1]{fontenc} 
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{mathtools}
-\usepackage{multicol}
-\usepackage{bm}
-\usepackage{pdflscape}
-\usepackage{natbib}
-\usepackage[section]{placeins}
-\usepackage{lipsum}
-\usepackage{etoolbox} 
-\usepackage{tabularx} 
-\usepackage{xcolor} 
-\usepackage[toc, page]{appendix} 
-% \hypersetup{draft} 
-% \linespread{1.8} 
-\hypersetup{ 
-	colorlinks		= true, 
-	urlcolor 		= blue, 
-	linkcolor 		= blue, 
-	citecolor 		= blue 
-}
-
-\newcommand{\ddfrac}[2]{\frac{\displaystyle #1}{\displaystyle #2}} 
-\newcommand{\refp}[1]{(\ref{#1})} 
-\newcommand{\msun}{\ensuremath{\text{M}_\odot}} 
-\newcommand{\persqkpc}{\ensuremath{\text{kpc}^{-2}}} 
-\providecommand{\noopsort}[1]{} 
-\graphicspath{ {../plots/} }
-
-\interfootnotelinepenalty = 10000 
-\defcitealias{Kroupa2001}{Kroupa} 
-\defcitealias{Salpeter1955}{Salpeter}
-
-\title[Stellar Migration and Chemical Enrichment]{Stellar Migration and 
-Chemical Enrichment in the Milky Way Disc: A Hybrid Model}
-
-\author[J.W. Johnson et al.]{
-	James W. Johnson,$^{1}$\thanks{Contanct e-mail: \href{mailto:
-	johnson.7419@osu.edu}{johnson.7419@osu.edu}} 
-	David H. Weinberg,$^{1, 2, 3}$ 
-	Fiorenzo Vincenzo,$^{2}$ 
-	Jonathan C. Bird,$^{4}$ 
-	\newauthor 
-	Sarah R. Loebman,$^{5}$ 
-	Alyson Brooks,$^{6}$ 
-	Thomas R. Quinn,$^{7}$ 
-	Charlotte R. Christensen,$^{8}$ 
-	\newauthor 
-	et al.?
-	\\
-	$^{1}$ Department of Astronomy, The Ohio State University, 
-	140 W. 18th Ave., Columbus, OH, 43210, USA 
-	\\ 
-	$^{2}$ Center for Cosmology and Astroparticle Physics (CCAPP), 
-	The Ohio State University, 191 W. Woodruff Ave, Columbus, OH, 43210, USA 
-	\\ 
-	$^{3}$ Institute for Advanced Study, 1 Einstein Dr., Princeton, NJ, 08540, 
-	USA 
-	\\ 
-	$^{4}$ Department of Physics \& Astronomy, Vanderbilt University, 
-	2301 Vanderbilt Place, Nashville, TN, 37235, USA 
-	\\ 
-	$^{5}$ Department of Physics, University of California Merced, 
-	5200 North Lake Rd., Merced, CA, 95343, USA 
-	\\ 
-	$^{6}$ Department of Physics \& Astronomy, Rutgers University, 136 
-	Frelinghuysen Rd, Piscataway, NJ, 08854, USA 
-	\\ 
-	$^{7}$ Department of Astronomy, University of Washinton, Box 351580, 
-	Seattle, WA, 98195, USA 
-	\\ 
-	$^{8}$ Department of Physics, Grinnell College, 1116 8th Ave., Grinnell, 
-	IA, 50112, USA 
-}
-
-\date{Accepted XXX; Received YYY; in original form ZZZ} 
-\pubyear{2020}
-
+\documentclass[draft2.tex]{subfiles} 
 \begin{document}
-\label{firstpage} 
-\pagerange{\pageref{firstpage}--\pageref{lastpage}} 
-\maketitle
-
-\begin{abstract} 
-We investigate the impact of stellar migration on galactic chemical evolution 
-models, considering a handful of assumptions for the star formation history 
-and time-dependence of radial migration based on a zoom-in, hydrodynamical 
-simulation of galaxy evolution. When stars migrate with a smooth, continuous 
-time dependence, the type Ia supernova rate exhibits significant variability in 
-our models. We demonstrate that this is a means with which young, super-solar 
-[$\alpha$/Fe] in the solar neighbourhood can arise naturally out of inside-out 
-Galaxy growth with stellar migration. We find 
-that the observed age-[$\alpha$/Fe] relation is well-fit by an inside-out star 
-formation history, while the age-[$\alpha$/H] and age-[Fe/H] relations are 
-well-fit by a late starburst model; no one model investigated here fits both 
-simultaneously. Our model successfully reproduces the broad nature of the 
-[$\alpha$/Fe] distribution at fixed [Fe/H] in a given Galactic region; however, 
-an overprediction of the frequency of intermediate [$\alpha$/Fe] stars prevents 
-it from explaining the observed results in detail. This suggests 
-that inside-out galaxy growth combined with stellar migration, even with a late 
-starburst, is not conducive to forming the infamous bimodality as it is 
-observed. We postulate that more dramatic evolutionary scenarios (e.g. a 
-two-infall model) may be necessary to describe the observed results. In 
-conducting this analysis, we developed and made use of newly released features 
-in the \texttt{Versatile Integrator for Chemical Evolution} (\texttt{VICE}) 
-which are built to handle these models under a wide variety of 
-assumptions. \texttt{VICE} is publicly available 
-at~\url{https://pypi.org/project/vice}. 
-\end{abstract}
-
-\begin{keywords} 
-methods: numerical -- galaxies: abundances, evolution, star formation, stellar 
-content 
-\end{keywords}
-
-\section{Introduction} 
-\label{sec:intro} 
-The orbits of stars are not unchanging. While it has been known for some time 
-that stars undergo radial migration (e.g.~\citealp*{Wielen1996}; 
-\citealp{Roskar2008a,Loebman2011,Minchev2012}), the true impact of this process 
-on galactic chemical evolution (GCE) remains under debate. By mixing stellar 
-populations which formed in Galactic regions with significantly different 
-enrichment histories, in principle the impact could be considerable. While some 
-authors argue that radial migration has only a small impact on GCE 
-(e.g.~\citealp*{Kubryk2013};~\citealp{Khoperskov2021}), there are others who 
-argue the contrary (e.g.~\citealp{Schoenrich2009};~\citealp*{Sharma2020}). 
-Aside from the chemodynamical simulations involving N-body integrations 
-\citep[e.g.][]{Kubryk2013, Vincenzo2020, Khoperskov2021}, there are to date 
-only a handful of GCE models that take this effect into account (e.g. 
-\citealp{Matteucci1989, Schoenrich2009};~\citealp*{Minchev2013}; 
-\citealp{Sharma2020}). These studies treat the Milky Way as a series of 
-concentric annuli, each described by a conventional one-zone GCE model with 
-parameters that change from annulus to annulus. In the resultant ``multi-zone'' 
-model, stars and gas can migrate between zones under some prescription to 
-account for time-dependent mixing processes. We retain such methodology in this 
-paper, allowing star particles from a hydrodynamical simulation ran from 
-cosmological initial conditions to inform our implemented mixing process; 
-\citet{Minchev2013} employ a similar technique. With parameters tuned to 
-reproduce certain observed results (e.g. abundance and surface density 
-gradients), we can then assess the model predictions to address the following 
-question: when combining simple, conventional assumptions about the star 
-formation and dynamical histories of the Milky Way, what observed results can 
-be replicated? In the present paper, we focus on the following observables: 
-metallicity distributions functions (MDFs) and abundance gradients, the 
-[$\alpha$/Fe] bimodality, the age-metallicity relation (AMR), and the young, 
-$\alpha$-rich population. 
-\par 
-Stars in the inner regions of the Milky Way tend to be more metal-rich than 
-those found in the outskirts~\citep{Nordstroem2004b, Daflon2009, 
-Frinchaboy2013, Hayden2014}, with slight variations in quantitative results 
-based on what type of stars are considered and what metallicity tracers are 
-analysed. Such behavior is also seen in the gas-phase gradients of 
-low-redshift spirals (see, e.g., the results from the CHAOS project using HII 
-regions;~\citealp{Berg2015, Berg2020}). Using the 12th data release of the 
-Apache Point Observatory Galaxy Evolution Experiment (APOGEE), 
-\citet{Hayden2015} demonstrate that the observed MDF has a metal-rich mode and 
-is skew-negative in the inner galaxy (and conversely, metal-poor and 
-skew-positive in the outer galaxy). These variations in the skewness of the 
-distributions with Galactocentric radius are usually attribute to the migration 
-of metal-rich (metal-poor) stars from smaller (larger) orbital radii. Similar 
-arguments are used by~\citet{Sellwood2002} to interpret the results of 
-\citet{Edvardsson1993} on scatter in the age-metallicity relation observed in 
-the solar neighbourhood. 
-\par 
-Abundance gradients have been the focus of many studies and are quantified 
-rather extensively, but their origin is somewhat up for debate. Applying the 
-analytic models of~\citet*{Weinberg2017}, one could argue that the gradient 
-arises out of variations in the local gas-phase equilibrium abundance as a 
-function of Galactocentric radius. For $\alpha$-elements, the equilibrium 
-abundance is determined to first order by their yield and the efficiency of 
-outflows in removing metals from the star forming reservoir. With a stronger 
-gravitational potential in the inner regions of the Galaxy, one might 
-reasonably expect outflows to be weaker there, thereby increasing the 
-equilibrium abundance.~\citet{Nidever2014} used such an approach to reproduce 
-the width of the [Fe/H] distribution for low-$\alpha$ sequence stars in 
-APOGEE. However, recent chemical evolution models have successfully replicated 
-the gradient with no outflowing winds at all~\citep[e.g.][]{Minchev2013, 
-Spitoni2019a}. This is based on arguments from~\citet{Melioli2008, Melioli2009}, 
-\citet*{Spitoni2008}, and~\citet{Spitoni2009} who studied Galactic fountains 
-using hydrodynamical simulations and numerical models, finding that ejected 
-metals tend to reaccrete to a Galactocentric radius similar to where they 
-originated. With this result, some authors argue that such outflows do not 
-significantly alter the chemical evolution of a Galactic disc, and that instead 
-the gradient arises from the higher normalization of the star formation history 
-in the inner Galaxy. 
-\par 
-Like radial abundance gradients, the reality of the infamous [$\alpha$/Fe] 
-dichotomy is well established (in Gaia-ESO:~\citealp{Recio-Blanco2014, 
-Rojas-Arriagada2017}; in APOGEE:~\citealp{Nidever2014, Hayden2015, 
-Weinberg2019}), but its origin is a topic of intense debate. In general, stars 
-in the Milky Way tend to fall in one of two populations - the roughly solar 
-[Fe/H], solar [$\alpha$/Fe] stars commonly referred to as the low-$\alpha$ 
-sequence, and the high-$\alpha$ sequence made up of sub-solar [Fe/H], 
-super-solar [$\alpha$/Fe] stars. Recently explored with more current data by 
-\citet{Sharma2020}, the notion that it could in principle arise out of radial 
-migration traces back to~\citet{Schoenrich2009}. Applying the analytic models 
-of~\citet{Weinberg2017}, an alternative pathway to such abundance patterns is 
-by an increase in the strength of outflows at late times. Such an evolutionary 
-model would predict a decrease in the equilibrium abundance, forming stars 
-along the low-$\alpha$ sequence. This scenario has not yet been explored in 
-combination with radial migration. 
-\par 
-Other authors argue that more dramatic evolutionary events are necessary to 
-explain the observed results, such as the two-infall model 
-(\citealp*{Chiappini1997, Chiappini2001};~\citealp{Romano2010, Grisoni2017, 
-Noguchi2018, Palla2020, Spitoni2016, Spitoni2018}). 
-In these models, the high-$\alpha$ sequence forms during the Galaxy's initial 
-collapse before feedback processes shut off star formation and expel gas into 
-the Galactic halo. Then, this material can cool and reaccrete along with 
-additional, metal-poor gas from the intergalactic medium, producing a second 
-episode of star formation. The dilution associated with the second accretion 
-event lowers the gas-phase Fe abundance at fixed [$\alpha$/Fe], forming stars 
-along the low-$\alpha$ sequence.~\citet{Spitoni2019a, Spitoni2020} demonstrated 
-using the APOKASC sample~\citep{Pinsonneault2014, SilvaAguirre2018} that such 
-models can explain the abundances observed in the solar annulus. Although 
-\citet{Spitoni2021} recently extended this model to Galactic regions beyond 
-the solar annulus, their model did not account for the mixing of stellar 
-populations between regions. Though they invoke~\citet{Kubryk2013} and 
-\citet{Khoperskov2021} as arguments that it shouldn't impact their results, 
-this nonetheless means that two-infall models have not yet been explored in 
-combination with a treatment for stellar migration. 
-\par 
-Recent cosmological zoom-in simulations have found results qualitatively 
-similar to the arguments of~\citet{Spitoni2019a, Spitoni2020, Spitoni2021}. 
-Using the Auriga simulation suite~\citep{Grand2017},~\citet{Grand2018} 
-demonstrate that an early, accretion induced starburst can populate the 
-high-$\alpha$ sequence, followed by low-level, sustained star formation on the 
-low-$\alpha$ sequence. In this pathway, there is either a rapid transition 
-between the two phases, ensuring the chemical space between the sequences is 
-relatively unpopulated, or low-metallicity gas accretion dilutes the star 
-forming reservoir at fixed [$\alpha$/Fe], populating the low [Fe/H], low 
-[$\alpha$/Fe] portion of the low-$\alpha$ sequence.~\citet{Buck2020b} finds 
-the dilution scenario in the NIHAO simulation suite as well~\citep{Wang2015, 
-Buck2020a}. Although the~\citet{Spitoni2021} model did not implement mixing of 
-stellar populations, these studies using hydrodynamical simulations would 
-suggest pathways qualitatively similar to their two-infall model. 
-\par 
-Contrary to this scenario,~\citet{Clarke2019} demonstrate that star formation 
-proceeded in clumps in an SPH simulation using GASOLINE~\citep*{Wadsley2017}. 
-These clumps self-enrich, forming stars on the high-$\alpha$ sequence due to 
-the perturbed ratio of core collapse to type Ia supernova rates within the 
-star forming regions. The more spatially extended, smooth star formation 
-populates the low-$\alpha$ sequence. Suffice it to say that there are no 
-shortage of models which reproduce the dichotomy, but only those done with 
-hydrodynamical simulations and a handful of others 
-\citep[e.g.][]{Schoenrich2009, Minchev2013, Sharma2020} have taken into account 
-stellar migration. 
-\par 
-Besides abundance gradients and the [$\alpha$/Fe] dichotomy, another 
-observable of interest in this paper is the age-metallicity relation (AMR): the 
-correlation between stellar ages and metallicities. The observed AMR in the 
-solar neighbourhood is known to exhibit considerable intrinsic scatter 
-\citep{Edvardsson1993}; this is usually attributed to radial migration of 
-metal-rich (metal-poor) stars from smaller (larger) Galactocentric radii 
-\citep{Sellwood2002, Haywood2008, Roskar2008b, Schoenrich2009}. 
-In the solar neighbourhood,~\citet{Feuillet2018} reveal that super-solar 
-metallicity stars are statistically older than solar metallicity stars (see 
-their Fig. 3). This contrasts with the predictions of simple one-zone models of 
-GCE where enrichment proceeds alongside star formation, yielding a monotonic 
-AMR~\citep[e.g.][]{Andrews2017, Weinberg2017}. Although one-zone models of 
-starbursts can predict a non-monotonic AMR due to the effect of dilution 
-\citep{Johnson2020}, by construction they do not predict multiple abundances at 
-fixed age as~\citet{Feuillet2018} reports. Using the~\citet{Weinberg2017} 
-analytic models,~\citet{Feuillet2018} argues that this is a consequence of 
-radial migration. For a smooth star formation history, the youngest stars at a 
-given radius will have compositions reflective of the local equilibrium 
-abundance; only stars born at different radii will have different compositions, 
-and only the old ones will have had time to migration to the solar annulus. 
-\par 
-While the presence of old-metal rich stars in the solar annulus is peculiar 
-because they are at odds with one-zone models of chemical evolution, the 
-presence of young, $\alpha$-rich stars is interesting for the same reason. 
-For a smooth star formation history, the delayed nature of type Ia supernovae 
-and their Fe production cause [$\alpha$/Fe] to decrease with time, predicting 
-an age-[$\alpha$/Fe] relation that should increase monotonically with stellar 
-age. However, these~$\sim$few Gyr old stars with [$\alpha$/Fe]~$\approx$~+0.1 - 
-0.2 stars have been found using stellar ages estimated from carbon-to-nitrogen 
-ratios~\citep{Martig2016}, isochrone matching~\citep{Feuillet2018, 
-Feuillet2019}, and with the asterosesmic ages of the original APOKASC catalog 
-\citep{Chiappini2015, SilvaAguirre2018, Pinsonneault2014}. 
-\citet{SilvaAguirre2018} demonstrate that these stars have kinematics similar 
-to the rest of the high-$\alpha$ population, postulating that they may be 
-the consequence of stellar mergers or mass transfer events, making truly old 
-stars simply appear younger. In a sample of 51 young, $\alpha$-enhanced red 
-giant stars,~\citet{Hekker2019} conclude that a portion of these stars have 
-carbon-to-nitrogen ratios consistent with mass transfer events, but that this 
-cannot account for the entire population. This suggests that the remaining 
-stars are either truly young or the result of mergers on the main sequence. 
-If not, then a theoretical explanation for the origin of these stars remains 
-a mystery. 
-\par 
-Alternatively, a recent starburst event could have produced these stars. 
-\citet{Mor2019} infer a factor of~$\sim$2 enhancement in the star formation 
-history (SFH) of the Milky Way~$\sim$2 Gyr ago by comparing population 
-synthesis models to observed stellar luminosity functions and colour-magnitude 
-diagrams from Gaia data~\citep{GaiaDR2}.~\citet{Isern2019} reach similar 
-conclusions by modeling the white dwarf luminosity function in the solar 
-neighbourhood with Gaia parallaxes. Motivated by these results, 
-\citet{Johnson2020} demonstrate using one-zone chemical evolution models that 
-a recent starburst of this nature can produce similarly young,~$\alpha$-rich 
-stars. However, the caveat to this interpretation is that the starburst must be 
-sufficiently localized such that the resultant stellar populations remain 
-outliers from an otherwise monotonically increasing age-[$\alpha$/Fe] relation. 
-\par 
-The impact of such evolutionary histories combined with stellar migration is, 
-to our knowledge, yet unexplored in the literature. A viable model for the 
-detailed enrichment history of the Milky Way would simultaneously explain all 
-of these observed results and their variations between Galactic regions, while 
-also taking into account effects like mixing and observational systematics. On 
-top of this, it must self-consistently calculcate enrichment rates from adopted 
-nucleosynthetic yields and the SFH. In this paper, we aim to 
-assess the extent to which conventional assumptions about the evolutionary 
-history of the Milky Way can account for these results, entertaining a 
-handful of assumptions describing the SFH and time-dependence of stellar 
-radial migration. 
-\par 
-Motivated by the general result that galaxies grow in radius with time 
-(i.e. ``inside-out'' growth;~\citealp{Bird2013}), our base-line model has a 
-star formation history (SFH) whose e-folding timescales grow with 
-Galactocentric radius. Based on the findings of~\citet{Mor2019} and 
-\citet{Isern2019}, we also construct models in which a late starburst is 
-imposed atop the inside-out SFH. In one model, this starburst occurs in all 
-annuli, and in another, loosely informed by the findings of 
-\citet{Vincenzo2020} suggesting such a radial dependence to accretion, it 
-occurs only at~$\geq$6 kpc. We also construct a model in which the SFH is 
-constant at a given Galactocentric radius; these models are interesting from a 
-theoretical perspective in that they quantify the impact of stellar migration 
-without the effects of a time-dependent SFH.
-
-\section{Methods} 
-\label{sec:methods} 
-To fulfill the goals of this paper, we develop and make use of newly released 
-features within the~\texttt{Versatile Integrator for Chemical Evolution} 
-(\texttt{VICE};~\citealp{Johnson2020}). These features are designed to handle 
-models such as these with a wide range of flexibility. We reserve a description 
-of~\texttt{VICE}'s migration algorithm and our simulation parameters for~\S 
-\ref{sec:methods:migration}, first describing our sample of star particles from 
-the hydrodynamical simulation. 
-\par 
-Although we make use of a hydrodynamical 
-simulation to drive stellar migration, we do~\textit{not} make use of its SFH. 
-While our study employs similar techniques as~\citet{Minchev2013}, our differs 
-in this subtle aspect. An alternative to modeling radial migration based on a 
-hydrodynamical simulation is to invoke dynamical arguments; 
-\citet{Schoenrich2009} and~\citet{Sharma2020} take such an approach. This 
-method, however, introduces free parameters which then require fitting to 
-data. An advantage of our technique is that there are no free parameters 
-introduced to the model; furthermore, it's unclear the extent to which the fit 
-biases the model into agreement with parts of the data not involved in the 
-fitting process. The dynamical history of a hydrodynamical simulation is also 
-motivated by first principles in that it models gravitational interactions via 
-an N-body integration. The primary disadvantage of this approach is a 
-consequence of the lack of free parameters - the model is rigid, and we cannot 
-explore slight variations. However, in principle one could compare the 
-predictions made by our chemical evolution models when ran using different 
-hydrodynamical simulations. We emphasize that a hydrodynamical simulation 
-\textit{only} informs the mixing processes in our models, and there is no 
-N-body integration involved in our models aside from that which was used to run 
-the hydrodynamical simulation in the first place.
-
-\subsection{The Hydrodynamical Simulation} 
-\label{sec:methods:h277} 
-In this paper we make use of star particles from the~\texttt{h277} simulation 
-\citep{Christensen2012, Zolotov2012, Loebman2012, Loebman2014, Brooks2014}. 
-Recently employed to study the stellar age-velocity relationship, a synopsis of 
-its detailed simulation parameters and cosmological model can found in~\S 2 of 
-\citet{Bird2020}. We do not include any discussion of these details here, 
-instead focusing on how we vet the sample of star particles for use in our 
-chemical evolution models. 
-\par 
-It is of particular important to have accurately measured formation radii for 
-each star particle that we use in our analysis.~\texttt{h277} did not record 
-the exact birth radius of each star particle; however, each star particle does 
-have an accurate age at each snapshot. Since stellar orbits are unlikely to 
-change significantly in an adequately short time interval, the radii of 
-sufficiently young stars in their first snapshot are reasonable approximations 
-of their birth radii. We therefore restrict our sample to those with an age at 
-first snapshot of~$\leq$~150 Myr, and adopt their Galactocentric radius at that 
-time as their birth radius. We have also conducted this analysis with a maximum 
-age at first snapshot of 50 Myr, and found similar results, suggesting that 
-these time intervals are short enough to not impact our conclusions. In 
-practice, we find that 150 Myr also provides with an adequately large number of 
-star particles to sample from. Of the star particles that remain after imposing 
-this cut, the oldest one is 12.26 Gyr old at the present day. Our model can 
-only apply on timescales as long as or shorter than the full range of ages of 
-the sample of star particles; we therefore subtract 1.5 Gyr from the formation 
-times of all star particles, allowing~$T$~= 0 in our models to correspond to 
-$T$~= 1.5 Gyr in~\texttt{h277}. As a consequence, our disc models trace the 
-chemical evolution of the Galaxy out to a lookback time of~$\sim$12.2 Gyr, or a 
-redshift of~$z \approx$~3, placing the onset of star formation at that time. 
-\par 
-We further restrict our sample of star particles to only those with both 
-formation and final radii of~$R_\text{gal} \leq$~20 kpc, and to have formed 
-within~$\left|z\right|\leq$~3 kpc of the disc midplane. These criteria ensure 
-that we're only using star particles which formed in-situ. While it's possible 
-that some star particles formed in a dwarf galaxy as it was infalling, a 
-scenario which would satisfy these requirements, these star particles are few 
-in number, and are only relevant at large~$R_\text{gal}$ and high ages - a 
-region of parameter space where few stars form anyway. 
-\par 
-Based on a kinematic decomposition performed on the present-day phase space 
-distribution of the~\texttt{h277} star particles, we include all those with 
-bulge, pseudobulge, and disc-like kinematics, excluding halo stars. While we're 
-not modeling the evolution of the bulge here, these star particles are 
-overwhelmingly located at~$R_\text{gal}\leq$~3 kpc at the present day anyway; 
-here we're much more interersted in~$R_\text{gal}\geq$~3 kpc since we're 
-modeling the evolution of the disc. These cuts yield a sample of 3,000,556 star 
-particles from~\texttt{h277}. 
-\par 
-\texttt{h277} had a transient bar during its evolution, but does not have one 
-at~$z$ = 0 ({\color{red} citation?}). This is a noteworthy difference between 
-our model and that of~\citet{Minchev2013}, and by extension the 
-\citet*{Minchev2014} and~\citet{Minchev2017} studies which use it as well, 
-because they selected a hydrodynamical simulation of a galaxy specifically so 
-that it would have a strong bar at~$z$ = 0; the transient bar in~\texttt{h277} 
-was not strong. This could mean that the dynamical 
-history of our model Galaxy does not reflect that of~\citet{Minchev2013} and 
-perhaps the Milky Way itself. However, the difference is likely within the 
-uncertainties of the current understanding of the Milky Way's dynamical 
-history. Although an investigation on the impact of bar evolution on stellar 
-migration and thus chemical evolution is outside the scope of this paper, it is 
-an interesting question which can be probed by simply swapping the 
-\texttt{h277} data within~\texttt{VICE} for another simulation, then rerunning 
-our numerical models and comparing the results.
-
-% fig 1 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.32]{decomposition.pdf} 
-\caption{Radial distributions of our star particles from 
-\texttt{h277}. In the top row, we show distributions of~\textit{final} radius 
-in bins of birth radius and age, and in the bottom row, we show distributions 
-of~\textit{birth} radius in bins of final radius and age. Each bin in 
-Galactocentric radius is shown in its own panel, denoted in text at the top of 
-each panel and by vertical black dashed lines. We colour-code the distributions 
-according to the age of the star particles, denoted by the legend in the upper 
-left panel. We smooth all distributions with a box-car width of 0.5 kpc to 
-improve clarity. We omit the distributions for 8 - 10 Gyr old stars born in the 
-9 - 11 and 11 - 13 kpc bins due to an insufficient number of star particles 
-with which to calculate the distribution. } 
-\label{fig:h277_decomposition} 
-\end{figure*}
-
-In the top row of Fig.~\ref{fig:h277_decomposition}, we plot the distributions 
-of final radius in bins of birth radius and age for our sample of star 
-particles. Conversely, the bottom rows distributions of birth radii in bins of 
-final radius and age. Focusing on the top row of panels, we note that for star 
-particles born at any radius and time, the distribution of final radius is 
-still peaked near the birth radius, but moves slightly inward with increasing 
-age. The tails of the distributions toward larger~$R_\text{gal}$ are nearly 
-age-independent, while the tails toward smaller~$R_\text{gal}$ are not. This 
-suggests that radial migration inward and outward occur on different timescales 
-in~\texttt{h277}, specifically that inward migration is slower than outward 
-migration. By extension, this suggests that the two may be tied to different 
-physical processes. In a cosmological simulation,~\citet{Roskar2008a} 
-demonstrate that resonant scattering at corotation causes stars to move 
-outward and gas to move inward. It's possible that stellar migration inward has 
-different origins. 
-\par 
-Focusing on the bottom row of panels in Fig.~\ref{fig:h277_decomposition}, we 
-note that the mode of the birth radius distributions show a stronger dependence 
-on age than the mode of the final radius distributions. At any Galactocentric 
-radius at the present day, the youngest stars are overwhelmingly born at 
-comparable radii, while the oldest stars are overwhelmingly born at smaller 
-radii. This is most noticeable in at large~$R_\text{gal}$. The differences 
-between the two can be understood by considering the steep nature of the radial 
-gradient in stellar surface density. Take for example the 8 - 10 Gyr age bin in 
-both~$R_\text{Birth}$ = 5 - 7 kpc and~$R_\text{Final}$ = 11 - 13 kpc bins (i.e. 
-the red curves in the top-left and bottom-right panels). For these old stars 
-born at 5 - 7 kpc, 11 - 13 kpc is far down the tail of the~$R_\text{Final}$ 
-distribution, and yet 5 - 7 kpc is the mode~$R_\text{Birth}$ of all old stars 
-presently at these radii. This implies that even though a plurality of 8 - 10 
-Gyr old stars with~$R_\text{Final}$ = 11 - 13 kpc were born at 5 - 7 kpc, they 
-account for only a small fraction of the stars with similar birth radii. This 
-is only possible if there are many more stars born at small~$R_\text{gal}$ than 
-large~$R_\text{gal}$, implying a stellar surface density which decreases as a 
-strong function of Galactocentric radius. This is known to be the case 
-\citep[e.g.][]{Bland-Hawthorn2016}. 
-\par 
-We also note that the top row of Fig.~\ref{fig:h277_decomposition} demonstrates 
-that the number of stars which migrated inward and outward are comparable in 
-\texttt{h277}. In fact, taking~$\left|\Delta R_\text{gal}\right| \geq$~500 pc 
-between birth and final radii as the criterion for migration inward or outward, 
-we indeed find as global percentages in our sample that 27\% migrated inward, 
-29\% migrated outward, and the remaining 44\% stayed near their birth radius. 
-Furthermore, these distributions contain some information on the timescales of 
-radial migration. In all bins of birth radius, a good first-order estimate of 
-the probability density that a star has a final radius in the same bin is 
-$\sim$0.3. With bins in birth radius of 2 kpc, this suggests that only 
-$\sim$60\% of stars remain in their birth radius bin by the time their~$\sim$2 
-Gyr old. and the remaining~$\sim$40\% have migrated already. If the type Ia 
-supernova delay-time distribution (SN Ia DTD) is a~$t^{-1.1}\approx t^{-1}$ 
-power-law as suggested by observational results~\citep[e.g.][]{Maoz2012, 
-Maoz2017}, then we expect similar numbers of SN Ia events to occur with delay 
-times between 1 and 10 Gyr as we do between 100 Myr and 1 Gyr. With such an 
-extended DTD, and the timescales for migration implied by Fig. 
-\ref{fig:h277_decomposition}, its possible that SN Ia progenitors can migrate 
-significant distances before exploding. Indeed, in the ASAS-SN bright SN 
-catalog,~$\sim$10\% of SNe are seen at >10 kpc from their host galaxies 
-\citep{Holoien2019}. While this catalog is for~\textit{all} supernovae seen by 
-ASAS-SN, the majority of SN events are type Ia anyway. Based on this, it's 
-reasonable to expect that the migration of nucleosynthetic may proceed 
-alongside stellar migration. This effect has largely been neglected by GCE 
-studies to date on the grounds that radial migration is a slow process, and 
-thus the majority of nucleosynthesis should occur near a star's birth radius 
-(e.g.~\citealp{Minchev2013}, and in the application of the 
-\citealt{Weinberg2017} analytic models in~\citealt{Feuillet2018}). However, 
-with the realization that the SN Ia duty cycle is also a slow process due to 
-the long tail of the DTD, its possible that stellar migration and SN Ia occur 
-on similar timescales. Therefore, we relax this assumption in the present 
-paper. We discuss the application of the~\texttt{h277} star particle data to 
-our model for radial migration and the time dependence thereof in the next 
-section.
-
-\subsection{Radial Migration} 
-\label{sec:methods:migration} 
-As in previous studies~\citep[e.g.][]{Schoenrich2009, Minchev2013, Sharma2020}, 
-in this paper we model the Milky Way as a series of concentric annuli with a 
-uniform width~$\Delta R_\text{gal}$. To run numerical simulations of these 
-models, we develop and make use of~\texttt{VICE}'s~\texttt{milkyway} object, 
-designed specifically for such an approach. The~\texttt{milkyway} object is a 
-subclass of a more general object named~\texttt{multizone}; at its core a 
-\texttt{multizone} object is an array of~\texttt{singlezone} objects, which are 
-designed to handle one-zone models of GCE and were the focus of 
-\citet{Johnson2020},~\texttt{VICE}'s initial release paper. The 
-\texttt{multizone} object affords users full control over which zone any 
-individual stellar population is in at all timesteps following its formation as 
-well as the ability to move gas between any two zones with any time dependence. 
-In principle this should allow for arbitrarily complex zone configurations and 
-migration prescriptions. The \texttt{milkyway} object is a user-friendly 
-extension of this which enforces an annular zone configuration as we take here. 
-As defaults, it adopts the stellar migration model detailed in this section and 
-our star formation law discussed in~\S~\ref{sec:methods:sfe}. 
-\par 
-As in hydrodynamical simulations, stars in~\texttt{VICE} are stand-ins for 
-entire stellar populations. They're said to be in a given zone if their radius 
-is between the inner and outer edges of the annulus. At all times, their 
-nucleosynthetic products and returned envelopes are placed in the ISM of the 
-annulus that they are in~\textit{at that time}. Where hydrodynamical and 
-N-body simulations of Galaxy evolution tend to use star particles of a fixed 
-mass, however,~\texttt{VICE} forms a fixed number of stellar populations per 
-zone per timestep, and allows their masses to vary to account for variations 
-in the star formation rate (SFR). The mass of stars formed in a given zone is 
-divided evenly among the stellar populations that form in a given zone and 
-timestep. 
-\par 
-The final radius of a stellar population is then determined based on the birth 
-and final radii of star particles in a hydrodynamical simulation, for which 
-we've taken~\texttt{h277} in this paper (see discussion in~\S 
-\ref{sec:methods:h277}). Describing the Galaxy as a series of concentric 
-annuli,~\texttt{VICE}'s~\texttt{milkyway} object assumes stellar populations 
-are born at the centres of each annulus. For a stellar population born at a 
-time~$T$ and Galactocentric radius~$R_\text{gal}$, it first searches for star 
-particles from~\texttt{h277} that formed at~$T \pm$~250 Myr and~$R_\text{gal} 
-\pm$~250 pc. It then randomly selects a star particle from this subsample with 
-no bias to act as an~\textit{analog}. This stellar population then assumes the 
-change in orbital radius~$\Delta R_\text{gal}$ of its analog at face value, 
-and moves from its birth radius to the implied final radius at~$T$ = 12.2 Gyr 
-with an assumed time dependence. If no candidate analogs are found, 
-\texttt{VICE} widens the search to~$T \pm$~500 Myr and~$R_\text{gal} \pm$~500 
-pc. If still no analog is found, then it finds the star particle 
-with the smallest difference in birth radius still within a birth time of 
-$T \pm$~500 Myr, and assigns it as the analog. 
-While this prescription allows stellar populations to be assigned analogs with 
-significantly different birth radii, this is only an issue for small~$T$ and 
-large~$R_\text{gal}$ where there are few star particles from~\texttt{h277}, 
-and where few stars form in nature anyway due to the inside-out growth of 
-galaxies~\citep{Bird2013}. Furthermore, due to the similarity of the histograms 
-in the top row of Fig.~\ref{fig:h277_decomposition}, we expect taking 
-$\Delta R_\text{gal}$ from a star particle which formed at a similar time but 
-different birth radius in these instance to be accurate enough for our 
-purposes. 
-\par 
-Our models assume that the Galaxy is vertically and azimuthally well-mixed, and 
-that the radial direction is the only one in which there are significant 
-differences in composition. That is, each annulus extends from the disc 
-midplane at~$z$ = 0 to~$z = \pm \infty$, and whether or not a star particle is 
-in a given annulus does not depend on~$z$ at all. In fact, this information is 
-\textit{not} used in integrating our models with~\texttt{VICE}. Instead, we 
-simply assume that each stellar population in our models are located at the 
-present day~$z_\text{final}$ of its assigned analog. Furthermore, when an 
-\texttt{h277} star particle is assigned as an analog, it is~\textit{not} 
-thrown out of the sample of candidate analogs, in theory allowing a star 
-particle to act as an analog for multiple stellar populations. This is a 
-subtle difference between the~\citet{Minchev2013} model and ours; where we 
-assign star particles to stellar populations for which~\texttt{VICE} then 
-calculates a stellar mass and composition based on an assumed SFH, the 
-\citet{Minchev2013} uses a chemical evolution model to assign compositions to 
-star particles.
-
-% fig 2 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.45]{migration.pdf} 
-\caption{A diagram illustrating how Galactocentric radius changes with time for 
-two stellar populations under our migration schema: diffusion (crimson, solid), 
-linear (lime, dot-dashed), post-process (black, dotted), and sudden (blue, 
-dashed). Here the initial and final radii and birth times are chosen at random 
-for illustrative purposes. With the initial and final Galactocentric radii of 
-a stellar population, its birth time, and one of these assumptions regarding 
-the time-dependence of radial migration, the Galactocentric radius at all times 
-is known. } 
-\label{fig:migration_schema} 
-\end{figure}
-
-With a known birth radius and time from our GCE model and an implied 
-$\Delta R_\text{gal}$ from a stellar population's assigned analog, the final 
-radius is known and the only missing piece of information is the 
-time-dependence with which it moves there. In the present paper we consider 
-four parameterized assumptions to describe this, each of which are illustrated 
-conceptually in Fig.~\ref{fig:migration_schema}. 
-\begin{itemize} 
-	\item \textbf{Post-Processing}: Stars stay where they are born until the 
-	final timestep, at which point they instantly migrate to their final 
-	radius. This retains the assumption that stars do not contribute to 
-	nucleosynthesis beyond their birth radius as employed in previous studies 
-	\citep[e.g.][]{Minchev2013}. In this scenario, each annulus is treated as 
-	a one-zone model independent of all other zones. We illustrate this case 
-	with a black dotted line in Fig.~\ref{fig:migration_schema}.
-
-	\item \textbf{Sudden}: A random number is drawn from a uniform distribution 
-	between a stellar population's time of birth and the present day. That time 
-	is taken to be the time of instantaneous migration to the present-day 
-	annulus. This emulates a scenario in which a single dynamical interaction 
-	changes a star's orbital radius, and be thought of mathematically as a 
-	time-dependent extension of the post-processing scenario. We illustrate 
-	this case with a blue dashed line in Fig.~\ref{fig:migration_schema}.
-
-	\item \textbf{Diffusion}: Stars move to their final radii in a continuous, 
-	time-dependent manner in this case. So named because it corresponds to a 
-	scenario in which angular momentum diffuses via a random walk, under this 
-	assumption, the mean displacement of stars that migrate similar distances 
-	would scale with~$\sqrt{\text{age}}$. This is our 
-	fiducial migration model, and we present results with this assumption 
-	unless otherwise noted. This is qualitatively similar to 
-	\citet{Frankel2018, Frankel2020}, who also model radial orbit migration 
-	with a~$\sqrt{\tau}$ dependence. We illustrate this case with a red solid 
-	line in Fig.~\ref{fig:migration_schema}.
-
-	\item \textbf{Linear}: A simple variation of the diffusion model in which 
-	the migration to the final radius scales linearly with age rather than with 
-	$\sqrt{\text{age}}$. There is no physical motivation for this model other 
-	than mathematical ease, but together with the diffusion model it 
-	constitutes a test of how sensitive our conclusions are to the 
-	time-dependence of stellar migration. We illustrate this case with a 
-	green dot-dashed line in Fig.~\ref{fig:migration_schema}. 
-\end{itemize} 
-In all models, we neglect radial gas flows~\citep{Lacey1985, Bilitewski2012}, 
-instead focusing on these simple assumptions describing how orbital radii 
-change with time. While such an investigation would be an interesting extension 
-of our study, we reserve it for future work. 
-\par 
-We emphasize that there is~\textit{no} N-body integration employed in our 
-models aside from that which ran the~\texttt{h277} simulation. Furthermore, we 
-use our sample of analog star particles from it~\textit{only} in determining 
-$\Delta R_\text{gal}$ of each of our model stellar populations (see discussion 
-in~\S~\ref{sec:methods:h277}). While~\texttt{h277} had its own SFH and chemical 
-enrichment history, we make use of neither of these components here; rather, 
-these are exactly what we seek to explore variations of. We acknowledge that 
-stellar migration is often formulated using the processes ``blurring'' and 
-``churning'', referring to a star's epicyclic motions and changes in the 
-guiding center of its orbit~\citep[e.g.][]{Sellwood2002, Schoenrich2009, 
-Minchev2011}; migration can also occur due to the overlap of spiral arm and 
-bar resonances in the disc~\citep{Minchev2011}. We refrain from discussion of 
-this approach here, because our models do not make use of such methodology. In 
-the present paper, the orbital radii at all times are calculated and assumed at 
-face value given one of the four assumptions detailed in the bullet list above. 
-\par
-
-\subsection{Nucleosynthetic Yields, Outflows, and Recycling} 
-\label{sec:methods:yields} 
-Nucleosynthesis proceeds in our models according to~\textit{fractional net} 
-yields, as required by~\texttt{VICE}. That is, our yields quantify the mass 
-of some element~$x$ ejected to the interstellar medium (ISM) in units of the 
-progenitor stellar population's total initial mass, and only accounts for 
-\textit{newly produced} nucleosynthetic material.~\texttt{VICE} takes into 
-account the return of previously produced nucleosynthetic products with a 
-separate implementation. In the present paper, we focus our analysis on 
-alpha and iron-peak elements, taking oxygen (O) and iron (Fe) as the 
-representative cases. The dominant enrichment channels of 
-interest in our models are thus core collapse and type Ia supernovae 
-\citep{Johnson2019}. Though we choose O and Fe, we expect 
-similar results to be found for other alpha (e.g. Ne, Mg, Si) and iron-peak 
-elements (e.g. Mn, Ni, Co), with purely quantitative differences reflective of 
-the relative yields between elements. 
-\par 
-Enrichment from core collapse supernovae (CCSNe) happens immediately following 
-the formation of progenitor stars in~\texttt{VICE}. This is an adequate 
-approximation, because the lifetimes of massive stars are short compared to 
-the relevant timescales for galaxy evolution. For the most massive stars, the 
-lifetimes are comparable to the timestep size we adopt in this paper anyway. 
-This assumption implies a linear relationship between the CCSN enrichment 
-rate and the SFR: 
-\begin{equation} 
-\dot{M}_x^\text{CC} = y_x^\text{CC}\dot{M}_\star 
-\end{equation} 
-where~$y_x^\text{CC}$ is the CCSN yield of some element~$x$. Physically, this 
-quantity represents the mass of an element~$x$ ejected to the interstellar 
-medium (ISM) from all CCSNe events associated with a stellar population in 
-units of the stellar population's initial mass. For example, if 
-$y_x^\text{CC} = 0.01$, a hypothetical 100~\msun~stellar population would 
-add 1~\msun~of~$x$ to the ISM immediately. This procedure neglects the mass 
-that would be lost to outflows, which like recycling, have a separate 
-implementation in~\texttt{VICE}. In this paper, we adopt~$y_\text{O}^\text{CC}$ 
-= 0.015 and~$y_\text{Fe}^\text{CC}$~= 0.0012 from~\citet{Johnson2020}, who 
-in turn adopt these values from~\citet{Weinberg2017}. 
-\par 
-SN Ia nucleosynthesis products are injected according to a~$t^{-1.1}$ DTD with 
-a minimum delay time of~$t_\text{D}$ = 150 Myr. This is the default DTD in 
-\texttt{VICE}, which was also adopted by~\citet{Johnson2020}, and is suggested 
-by recent observational results comparing the cosmic SN Ia rate to the cosmic 
-SFH~\citep{Maoz2012, Maoz2017}. In a one-zone model at times~$t > t_\text{D}$, 
-the enrichment rate of some element~$x$~can be expressed as the product of 
-some yield~$y_x^\text{Ia}$ and the SFH weighted by the DTD: 
-\begin{subequations}\begin{align} 
-\dot{M}_x^\text{Ia} &= y_x^\text{Ia}\langle\dot{M}_\star\rangle_\text{Ia} \\ 
-&= y_x^\text{Ia}\ddfrac{
-	\int_0^{t - t_\text{D}} \dot{M}_\star(t') R_\text{Ia}(t - t') dt' 
-}{
-	\int_{t_\text{D}}^{t_\text{max}} R_\text{Ia}(t')dt' 
-} 
-\label{eq:mdot_ia} 
-\end{align}\end{subequations} 
-where~$R_\text{Ia}$ is the DTD itself, which has units of~$M_\odot^{-1}$ 
-Gyr$^{-1}$. Like the CCSN yield,~$y_x^\text{Ia}$ is the mass of some element 
-$x$ produced over the SN Ia duty cycle in units of the progenitor stellar 
-population's initial mass. It can also be expressed as an integral over the 
-DTD: 
-\begin{equation} 
-y_x^\text{Ia} = m_x^\text{Ia} \int_{t_\text{D}}^{t_\text{max}} R_\text{Ia}(t') 
-dt' = m_x^\text{Ia}\frac{N_\text{Ia}}{M_\star} 
-\label{eq:y_x_ia} 
-\end{equation} 
-where~$m_x^\text{Ia}$ is the average mass of the element~$x$ produced in a 
-single SN Ia event and the integral evaluates to the mean number of SN Ia 
-events~$N_\text{Ia}$ per mass of stars formed~$M_\star$. \texttt{VICE} forces 
-$t_\text{max}$~= 15 Gyr always, though provided one is consistent with 
-equations~\refp{eq:mdot_ia} and~\refp{eq:y_x_ia}, the results are independent 
-of~$t_\text{max}$ since the integrals cancel. 
-\par 
-Extending this formalism to multi-zone models is simple - rather than an 
-integral over the star formation history of a given annulus, the rate becomes 
-a sumation over all stellar populations that are in a given zone at some time: 
-\begin{equation} 
-\dot{M}_x^\text{Ia} = y_x^\text{Ia} \ddfrac{
-	\sum_i M_i R_\text{Ia}(\tau_i) 
-}{
-	\int_{t_\text{D}}^{t_\text{max}} R_\text{Ia}(t')dt' 
-} 
-\label{eq:mdot_ia_multizone} 
-\end{equation} 
-where~$M_i$~and~$\tau_i$~are the mass and age of the~$i$'th stellar population, 
-respectively. 
-\par 
-Initially, we adopt~$y_\text{O}^\text{Ia}$~= 0 and~$y_\text{Fe}^\text{Ia}$~= 
-0.0017 from~\citet{Johnson2020}, who in turn adopt these values from 
-\citet{Weinberg2017}. However, in practice we find that the e-folding 
-timescales of star formation in our models are sufficiently long (see 
-discussion in~\S~\ref{sec:methods:sfhs}) such that our fiducial, inside-out SFH 
-model predicts [O/Fe]~$\approx$~+0.05 for young stars. We therefore multiply 
-$y_\text{Fe}^\text{Ia}$~by~$10^{0.1}$, adopting instead~$y_\text{Fe}^\text{Ia}$ 
-= 0.00214 in order for our fiducial model to predict a late-time [O/Fe] ratio 
-in better agreement with observations. Although there is no motivation for such 
-a change aside from this, this decision is likely within the uncertainties in 
-SN Ia nucleosynthetic yields anyway. 
-\par 
-Our models assume that all supernova yields of O and Fe are independent of 
-metallicity. While this appears to be empirically true in the Milky Way for O 
-and Fe (\citealp{Weinberg2019};~\citealp*{Griffith2019}; 
-\citealp{Griffith2020}), our CCSN yields are based on 
-supernova explosion models in which all >8~\msun~progenitors produce a CCSN 
-event~\citep[e.g.][]{Chieffi2004, Chieffi2013}. Recent findings with regard to 
-black hole formation and stellar explodability have demonstrated that many 
-massive stars instead collapse directly to a black hole (see theoretical 
-discussion by, e.g.,~\citealp{Pejcha2015, Sukhbold2016, Ertl2016}, and 
-observational evidence from~\citealp*{Gerke2015};~\citealp{Adams2017, 
-Basinger2020}). Such effects would necessarily lower CCSN yields of all 
-elements. While~\texttt{VICE} includes functionality with which to calculate 
-$y_x^\text{CC}$~for some element~$x$~using built-in tables from supernova 
-nucleosynthesis studies, an in-depth investigation of the impact of these 
-effects is outside the scope of this paper. Such an investigation which expands 
-the capabilities of~\texttt{VICE} will be presented in Griffith et al. (2021, 
-in prep). 
-\par 
-With regard to our SN Ia yields,~\citet{Brown2019} demonstrate that the local 
-specific SN Ia rate shows a strong, inverse dependence on galaxy stellar mass. 
-They argue that this may imply a metallicity dependent~$R_\text{Ia}$ that 
-produces more SN Ia events at early times when the metallicity is low. However, 
-these metallicity are only present in our models at very early times. 
-Furthermore, when outflows are taken into account, these yields are known to 
-predict observationally plausible abundances~\citep{Andrews2017, Weinberg2017}. 
-We find similar results in our models. 
-\par 
-\citet{Weinberg2017} demonstrate that, to first order, the nucleosynthetic 
-yields of a given element and the strength of outflowing winds determine the 
-late-time equilibrium abundance in the ISM. We retain their characterization 
-of outflows here, in terms of a mass-loading factor~$\eta$~describing the ratio 
-of the mass outflow to the SFR: 
-\begin{equation} 
-\eta \equiv \frac{\dot{M}_\text{out}}{\dot{M}_\star} 
-\end{equation} 
-Here we adopt a scaling of~$\eta$~with~$R_\text{gal}$~such that the late-time 
-equilibrium abundance as a function of radius describes a metallicity 
-gradient in agreement with observations;~\citet{Nidever2014} employ a similar 
-methodology. 
-\par 
-The procedure outlined here makes two assumptions: 1) that the equilibrium 
-abundance at a given radius corresponds to the mode of the observed MDF, and 2) 
-that radial migration does not significantly alter the overall form of the 
-gradient. We demonstrate that this holds in our models in~\S 
-\ref{sec:obs_comp:gradient}. For alpha elements,~\citet{Weinberg2017} defines 
-the equilibrium abundance under a constant SFH as: 
-\begin{equation} 
-Z_{\alpha,\text{eq}} = \frac{y_\alpha^\text{CC}}{1 + \eta(R_\text{gal}) - r} 
-\end{equation} 
-where~$r$~is the recycling parameter ($\approx$0.4 for the sake of this scaling 
-with a~\citealp{Kroupa2001} IMF; see discussion in~\S~2.2 
-of \citealp{Weinberg2017}). Solving for~$\eta(R_\text{gal})$ yields: 
-\begin{equation} 
-\eta(R_\text{gal}) = \frac{y_\alpha^\text{CC}}{Z_{\alpha,\text{eq}}} + r - 1 = 
-\frac{y_\alpha^\text{CC}}{Z_{\alpha,\odot}}10^{-\text{mode([$\alpha$/H])}
-(R_\text{gal})} + r - 1 
-\end{equation} 
-The metallicity gradient in the Milky Way has been the focus of a number of 
-studies to date.~\citet{Nordstroem2004b} find a gradient of -0.099 kpc$^{-1}$ 
-in [Fe/H] in main sequence stars from the Geneva Copenhagen Survey 
-(\citealp{Nordstroem2004a};~\citealp*{Holmberg2007}).~\citet{Daflon2009} report  
--0.04 kpc$^{-1}$ in [S/H] in OB stars.~\citet{Frinchaboy2013} derive -0.09 
-kpc$^{-1}$ in [M/H] in open clusters.~\citet{Hayden2014} also find -0.09 
-kpc$^{-1}$ in [M/H] for~$R_\text{gal} \gtrsim$~6 kpc for low-$\alpha$ stars, 
-but find the gradient to be relatively flat within~$R_\text{gal} \lesssim$~6 
-kpc. \citet{Weinberg2019} report a gradient of -0.06 kpc$^{-1}$ in mode([Mg/H]) 
-for upper red giant branch stars in the disc (see their Fig. 23). In tentative 
-agreement with these studies, we adopt a slope of -0.08 kpc$^{-1}$. To set the 
-normalization, we assume the mode([$\alpha$/H]) to be~$\sim$+0.3 at 
-$R_\text{gal}$ = 4 kpc, since this would produce mode([$\alpha$/H])~$\approx$~0 
-at~$R_\text{gal}$ = 7 - 9 kpc. This results in the following form for~$\eta$ 
-as a function of Galactocentric radius: 
-\begin{equation} 
-\eta(R_\text{gal}) = \frac{y_\alpha^\text{CC}}{Z_{\alpha,\odot}} 
-10^{(-0.08\text{ kpc}^{-1})(R_\text{gal} - 4\text{ kpc}) + 0.3} + r - 1 
-\label{eq:eta_rgal} 
-\end{equation} 
-where we adopt our CCSN yield of O for~$y_\alpha^\text{CC}$ and the solar 
-abundance of O of~$Z_{\text{O},\odot}$ = 0.00572 based on~\citet{Asplund2009}. 
-We plot this adopted scaling in the top panel of Fig.~\ref{fig:eta_tau_sfh}, 
-highlighting a value of~$\sim$2.15 for the solar circle with a red dotted line. 
-This does assume a uniformly linear gradient at all~$R_\text{gal}$, in tension 
-with the findings of~\citet{Hayden2014} who find it to flatten within~$\sim$6 
-kpc. However, this procedure can be easily repeated for any desired gradient, 
-since the functional form simply goes into the power of 10 in equation 
-\refp{eq:eta_rgal}.
-
-% fig 3 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.45]{eta_tau_sfh.pdf} 
-\caption{\textbf{Top}: Our implemented scaling of the mass loading factor 
-$\eta$~with Galactocentric radius (black) as defined by equation 
-\refp{eq:eta_rgal}.~\textbf{Bottom}: The e-folding timescales of the star 
-formation histories of our model galaxies (black). These values come from a 
-fit to the~$\Sigma_\star$-age relation in bins of~$R/R_\text{e}$~for 
-$10^{10.5}$~-~$10^{11}$~\msun~Sa/Sb Hubble type spiral galaxies as reported by 
-\citet[][see discussion in~\S~\ref{sec:methods:sfhs}]{Sanchez2020}. The 
-horizontal and vertical red dashed lines in both panels highlight a mass 
-loading factor of~$\eta \approx$~2.15 and a star formation timescale of 
-$\tau_\text{sfh} \approx$~15 Gyr at an assumed radius of the sun of 
-$R_\odot$ = 8 kpc. } 
-\label{fig:eta_tau_sfh} 
-\end{figure}
-
-Both AGB star enrichment and the recycling of previously produced metals in 
-this paper proceed as they did in~\citet{Johnson2020}, with the caveat that the 
-mass is added to the annulus that a stellar population is in at a given time, 
-which may or may not be the annulus it was born in. Recycling proceeds 
-according to the~\citet{Kalirai2008} initial-remnant mass relation assuming a 
-\citet{Kroupa2001} IMF and a mass-lifetime relationship of 
-$\tau = 1.1\tau_\odot(M/M_\odot)^{-3.5}$, where~$\tau_\odot$~= 10 Gyr is the 
-main sequence lifetime of the sun and the factor of 1.1 accounts for the 
-post-main sequence lifetime.~\texttt{VICE} in its current version forces an AGB 
-enrichment channel in all models; it is thus included in the present paper. For 
-this enrichment channel, we adopt the net yields sampled on a table of stellar 
-initial mass and metallicity from the FRUITY database \citep{Cristallo2011}. 
-However, the AGB star yields of O and Fe are negligible compared to their 
-supernova yields; we therefore conclude discussion of this component of our 
-models here. 
-\par
-
-\subsection{Star Formation Histories} 
-\label{sec:methods:sfhs} 
-\texttt{VICE} handles models in either infall, star formation, or gas mode, 
-referring simply to which component of the evolutionary history the user has 
-specified. The starburst models presented in~\citet{Johnson2020} ran in infall 
-mode, but here we run~\texttt{VICE} in star formation mode, because we are 
-after specific forms for the star formation histories of our models. In 
-Appendix~\ref{sec:normalize_sfh}, we present justification of how we normalize 
-the parameters of our star formation histories to produce a realistic model 
-Galaxy at the present day. In short, it takes in a unitless description of the 
-dependence of the SFH at a given Galactocentric radius, denoted 
-$f(t|R_\text{gal})$, and a unitless description of the present day stellar 
-surface density gradient, denoted~$g(R_\text{gal})$. We integrate 
-$f(t|R_\text{gal})$ with time for each annulus, assuming~$R_\text{gal}$ to 
-correspond to the centre of the zone, and attach a prefactor to 
-$f(t|R_\text{gal})$ in each annulus such that the desired gradient is achieved 
-with a total stellar mass similar to the Milky Way. This procedure neglects the 
-impact of radial migration, assuming that it does not significantly alter the 
-form of~$g(R_\text{gal})$. We demonstrate that these assumptions hold in~\S 
-\ref{sec:methods:surface_density_gradient}, in which we also detail our 
-adopted form of~$g(R_\text{gal})$. As long as this assumption is not violated, 
-the equation derived in Appendix~\ref{sec:normalize_sfh} can be used to 
-calculate these prefactors for future models of Milky Way-like galaxies. 
-\par 
-In the present paper, we present four fiducial SFHs, which we dub ``constant'', 
-``inside-out'', ``late-burst'', and ``outer-burst''. They're defined as 
-follows: 
-\begin{itemize} 
-	\item \textbf{Constant}: The SFH at a given radius is time-independent. 
-	\begin{equation} 
-	f_\text{C}(t|R_\text{gal}) = 1 
-	\label{eq:constant_sfh} 
-	\end{equation} 
-	This case is of particular theoretical interest because it quantifies the 
-	effect of stellar migration while removing the impact of a time-dependent 
-	SFH.
-
-	\item \textbf{Inside-Out}: This is our fiducial SFH. 
-	\begin{equation} 
-	f_\text{IO}(t|R_\text{gal}) = (1 - e^{-t / \tau_\text{rise}}) 
-	e^{-t / \tau_\text{sfh}} 
-	\label{eq:insideout_sfh} 
-	\end{equation} 
-	We adopt this mathematical form over a more traditional 
-	linear-times-exponential characterization, because the latter does not 
-	offer control over the position of the maximum SFR. The form we adopt has 
-	a maximum near~$\tau_\text{rise}$, for which we adopt a value of 2 Gyr 
-	everywhere here. This produces a peak in star formation at lookback times 
-	of~$\sim$10 Gyr, roughly corresponding to a redshift of~$z \approx$~2, in 
-	agreement with observational results on the cosmic SFH~\citep{Madau2014}. 
-	In this paper,~$\tau_\text{sfh}$ is a function of~$R_\text{gal}$, discussed 
-	in this section. We present results assuming this model throughout this 
-	paper except in cases where a different SFH impacts the predictions.
-
-	\item \textbf{Late-Burst}: In this model, the inside-out SFH is modified to 
-	exhibit a recent, gradual burst in star formation described by a Gaussian: 
-	\begin{equation} 
-	f_\text{LB}(t|R_\text{gal}) = f_\text{IO}(r|R_\text{gal}) 
-	(1 + A_be^{-(t - t_b)^2/2\sigma_b^2}) 
-	\label{eq:lateburst_sfh} 
-	\end{equation} 
-	$A_b$ is a dimensionless parameter describing the strength of the 
-	starburst,~$t_b$ is the time of the local maximum in the SFH during the 
-	burst, and~$\sigma_b$ is the width of the Gaussian describing it. This 
-	model being loosely motivated by the findings of~\citet{Mor2019} and 
-	\citet{Isern2019}, we adopt~$A_b$ = 1.5,~$t_b$ = 10.2 Gyr, and 
-	$\sigma_b$ = 1 Gyr, finding in practice that~$A_b$ = 1.5 produces a 
-	local maximum SFR that is a factor of~$\sim$2 larger than the preceding 
-	local minimum.
-
-	\item \textbf{Outer-Burst}: A variation of the late-burst model in which 
-	only~$R_\text{gal} \geq$~6 kpc experience the starburst. This is loosely 
-	motivated by the findings of~\citet{Vincenzo2020} where a hydrodynamical 
-	simulation of a Milky Way-like galaxy showed radially dependent infall. 
-	\begin{equation} 
-	f_\text{OB}(t|R_\text{gal}) = \begin{cases} 
-	f_\text{IO}(t|R_\text{gal}) & (R_\text{gal} < 6\text{ kpc}) \\ 
-	f_\text{LB}(t|R_\text{gal}) & (R_\text{gal} \geq 6\text{ kpc}) 
-	\end{cases} 
-	\label{eq:outerburst_sfh} 
-	\end{equation} 
-\end{itemize} 
-Although we do not consider such models here, an investigation into the impact 
-of more episodic star formation histories would be an interesting extension of 
-the present paper. For example,~\texttt{VICE} has all of the necessary 
-capabilities to handle models in which major episodes of star formation 
-coincide with close passages of the Sagittarius dwarf 
-\citep[e.g.][]{RuizLara2020}. 
-\par 
-We derive the scaling of the e-folding timescales of star formation 
-$\tau_\text{sfh}$ with~$R_\text{gal}$ from the data in~\citet{Sanchez2020}. 
-They present the stellar surface density~$\Sigma_\star$ as a function of age 
-in bins of~$R/R_\text{e}$ for MaNGA galaxies, where~$R_\text{e}$ is the 
-half-light radius. Here we take their~$M_\star = 10^{10.5} - 10^{11}$ 
-\msun~ bin for Sa/Sb spirals and simultaneously fit the normalization and 
-e-folding timescale~$\tau_\text{sfh}$ of our~$f_\text{IO}(t|R_\text{gal})$ form 
-to the data. Although the normalization is irrelevant to our models and 
-determined via the method outlined in Appendix~\ref{sec:normalize_sfh}, we 
-adopt the resulting~$\tau_\text{sfh}-R_\text{gal}$ relation in our models. With 
-our adopted stellar surface density gradient (see discussion in~\S 
-\ref{sec:methods:surface_density_gradient}), we know the present-day half-mass 
-radius to be very near 4 kpc. The findings of~\citet{Garcia-Benito2017} and 
-\citet{GonzalezDelgado2014} suggest that half-light radii are marginally larger 
-than half-mass radii. Based on equation (4) of~\citet{GonzalezDelgado2014} 
-relating the two for circular apertures, we expect our model Galaxy to have a 
-half-light radius near 5 kpc. We therefore adopt~$R_\text{e}$ = 5 kpc to 
-convert the~$\tau_\text{sfh}-R_\text{gal}/R_\text{e}$ relation resulting from 
-our fit to the~\citet{Sanchez2020} data into a~$\tau_\text{sfh}-R_\text{gal}$ 
-relation. {\color{red} If there are references suggesting a similar value for 
-the Milky Way, we should note them here. } 
-\par 
-We illustrate this relationship in the bottom panel of Fig. 
-\ref{fig:eta_tau_sfh}, noting that the resulting timescales are long, 
-particularly for the outer Galaxy. With a red dotted line, we highlight a value 
-of~$\tau_\text{sfh} \approx$~15 Gyr at an assumed orbital radius of the sun of 
-$R_\odot$ = 8 kpc. Although these timescales at most radii are considerably 
-longer than a Hubble time, this is no cause for worry; this simply means that 
-these regions of the Galaxy in our models experience less than 1 e-folding in 
-their SFR, and that in the outer Galaxy the SFH is nearly constant after the 
-initial rise in the first~$\sim$2 Gyr. It is nonetheless interesting that 
-these timescales are considerably longer than that derived for the cosmic 
-SFH~\citep{Madau2014}.
-
-% fig 4 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.32]{evol.pdf} 
-\caption{The surface densities of star formation~$\dot{\Sigma}_\star$ (top 
-row), infall $\dot{\Sigma}_\text{in}$ (middle row), and gas~$\Sigma_\text{g}$ 
-(bottom row) as functions of simulation time for our four fiducial SFHs: 
-constant (far left), inside-out (left middle), late-burst (right middle), and 
-outer-burst (far right). We plot curves for the annuli whose inner radii are 
-3 kpc (grey), 5 kpc (black), 7 kpc (red), 9 kpc (yellow), 11 kpc (green), 13 
-kpc (blue), and 15 kpc (purple) (see equations~\refp{eq:constant_sfh}, 
-\refp{eq:insideout_sfh},~\refp{eq:lateburst_sfh}, and~\refp{eq:outerburst_sfh} 
-for the mathematical definition of each SFH). 
-}
-\label{fig:evol} 
-\end{figure*}
-
-We plot the resultant SFHs or our models in the top row of Fig.~\ref{fig:evol} 
-for a handful of radii. At all timesteps, the gas supply is known via the star 
-formation efficiency timescale~$\tau_\star$ (see discussion in~\S 
-\ref{sec:methods:sfe}). This quantity is illustrated in the bottom row of 
-Fig.~\ref{fig:evol}.~\texttt{VICE} automatically calculates the implied infall 
-rate by comparing the amount of gas lost to outflows and star formation in a 
-given timestep to that which is required to sustain the user-specified level of 
-star formation at the next timestep; we assume the infalling gas to be of zero 
-metallicity at all times. This quantity is shown in the middle row of Fig. 
-\ref{fig:evol}.
-
-\subsection{Star Formation Efficiency} 
-\label{sec:methods:sfe} 
-The term ``star formation efficiency'' (SFE) is somewhat overloaded in the 
-literature. In the star formation and feedback community, it usually 
-refers to the fraction of a molecular cloud's mass which will eventually be 
-converted into stars. In the chemical evolution literature, however, it 
-typically refers to the inverse timescale relating the SFR within some star 
-forming reservoir and the mass of gas in that region: 
-$\tau_\star \equiv \Sigma_\text{g}/\dot{\Sigma}_\star$. High (Low) values of 
-$\tau_\star$ indicate slow (fast) star formation and thus low (high) SFE; when 
-we refer to SFE here, we're referring to the definition based on this 
-timescale. In the star formation and feedback literature, this is often 
-referred to as the ``depletion time''. 
-\par 
-Based on the findings of~\citet{Kennicutt1998}, it is common practice in the 
-chemical evolution literature a single power-law describing the relationship 
-between the surface densities of gas and star formation~$\Sigma_\text{g}$ and 
-$\dot{\Sigma}_\star$, often referred to as the star formation law or the 
-Kennicutt-Schmidt relation: 
-\begin{equation} 
-\dot{\Sigma}_\star \sim \Sigma_\text{g}^N 
-\end{equation} 
-\citet{Kennicutt1998} derive~$N = 1.4 \pm 0.15$ relating the total 
-$\dot{\Sigma}_\star$~and~$\Sigma_\text{g}$~within the disc across a sample of 
-quiescent spiral galaxies and infrared and circumnuclear starbursts. However, 
-recent studies have found evidence that much of the observed scatter in this 
-relation is physical in origin~\citep{delosReyes2019} and that there are 
-significant breaks in both the power-law index and zero-points 
-\citep{Kennicutt2020}. Much of the uncertainty surrounding the details of the 
-star formation law is a consequence of the ongoing debate about the CO-to-H$_2$ 
-conversion factor (\citealp{Kennicutt2012};~\citealp*{Liu2015}). Although 
-\citet{Ellison2020a} demonstrate that there are significant galaxy-to-galaxy 
-variations in the star formation law, suggesting that individual galaxies do 
-not follow the population averaged trend,~\citet{delosReyes2019} argue that 
-this is still a reasonable recipe for Galaxy evolution models. We adopt such a 
-formalism here. 
-\par 
-\citet{Krumholz2018} compare model-predicted star formation laws to the 
-observations of~\citet{Bigiel2010} and~\citet{Leroy2013} (see their Fig. 2). We 
-find that the following by-eye fit to the power-law index~$N$~is a reasonble 
-description of the aggregate data: 
-\begin{equation} 
-N = \begin{cases} 
-1.0 & (\Sigma_\text{g} \geq \Sigma_{\text{g},2}) \\ 
-3.6 & (\Sigma_{\text{g},1} \leq \Sigma_\text{g} \leq \Sigma_{\text{g},2}) \\ 
-1.7 & (\Sigma_\text{g} \leq \Sigma_{\text{g},1}) 
-\end{cases} 
-\label{eq:sf_law_indeces} 
-\end{equation} 
-where~$\Sigma_{\text{g},1} = 5\times10^6$~\msun~\persqkpc~and 
-$\Sigma_{\text{g},2} = 2\times10^7$~\msun~\persqkpc. The apparent linearity of 
-the relationship above~$\sim2\times10^7$~\msun~\persqkpc~suggests that in this 
-regime, star formation proceeds at the fastest possible rate, and that 
-$\tau_\star \equiv \Sigma_\text{g}/\dot{\Sigma}_\star$~= constant. The 
-observations of~\citet{Leroy2013} and~\citet{Kennicutt2020} would suggest that 
-these are the 
-surface densities at which the molecular fraction~$f_\text{mol} = M_{\text{H}_2} 
-/ (M_{\text{H}_2} + M_\text{HI}) \approx$~1. We therefore adopt the assumption 
-that above~$\Sigma_\text{g} = 2\times10^7$~\msun~\persqkpc,~$\tau_\star$ 
-reaches its minimum value, and increases with decreasing~$f_\text{mol}$. We 
-denote this value as~$\tau_\text{mol}$, the value of~$\tau_\star$ for a gas 
-reservoir with~$f_\text{mol}$~= 1. This, combined with our three-component 
-power-law index N results in the following final form for our adopted star 
-formation law: 
-\begin{equation} 
-\dot{\Sigma}_\star = \begin{cases} 
-\Sigma_\text{g} \tau_\text{mol}^{-1} & 
-(\Sigma_\text{g} \geq \Sigma_{\text{g},2}) 
-\\ 
-\Sigma_\text{g} \tau_\text{mol}^{-1} \left(\frac{
-	\Sigma_\text{g}
-}{
-	\Sigma_{\text{g},2} 
-}\right)^{2.6} & 
-(\Sigma_{\text{g},1} \leq \Sigma_\text{g} \leq \Sigma_{\text{g},2}) 
-\\ 
-\Sigma_\text{g} \tau_\text{mol}^{-1} \left(\frac{
-	\Sigma_{\text{g},1} 
-}{
-	\Sigma{\text{g},2} 
-}\right)^{2.6}\left(\frac{
-	\Sigma_\text{g}
-}{
-	\Sigma_{\text{g},1} 
-}\right)^{0.7} & 
-(\Sigma_\text{g} \leq \Sigma_{\text{g},1}) 
-\end{cases} 
-\label{eq:sf_law} 
-\end{equation} 
-where we choose the power-law indeces such that this formalism is consistent 
-with equation~\refp{eq:sf_law_indeces}, and prefactors are added to ensure 
-piece-wise continuity. In implementation,~\texttt{VICE} requires the 
-$\tau_\star-\dot{\Sigma}_\star$ relation when ran in star formation mode and 
-the~$\tau_\star-\Sigma_\text{g}$ relation when ran in infall and gas modes. 
-Both follow algebraically from this relationship given the substitution 
-$\tau_\star \equiv \Sigma_\text{g} / \dot{\Sigma}_\star$. 
-\par 
-Although it is more physically motivated to use an adopted star formation law 
-to infer a star formation rate from the ISM properties at a given timestep, as 
-discussed in~\S~\ref{sec:methods:sfhs}, we are using~\texttt{VICE} in star 
-formation mode. This means that it is~$\dot{\Sigma}_\star$ which is specified 
-\textit{a priori} by our models - not~$\Sigma_\text{g}$. That is,~\texttt{VICE} 
-is inferring~$\Sigma_\text{g}$ from~$\dot{\Sigma}_\star$ in our models, not 
-the other way around. While we acknowledge the findings of~\citet{Ellison2020b}, 
-this another reason we must invoke a simple parameterization for the star 
-formation law, which~\citet{Kennicutt2020} argue is still a reasonable 
-approach. This decision also means that changing our assumptions about the 
-star formation law do not impact our SFHs, instead impacting the inferred 
-$\Sigma_\text{g}$ as a function of radius and time. 
-\par 
-Based on the observed Kennicutt-Schmidt at different redshifts, 
-\citet{Tacconi2018} suggest that~$\tau_\text{mol}$ should scale with redshift 
-$z$ and the deviation from the star forming main sequence~$\delta$MS via 
-$\tau_\text{mol} \propto (1 + z)^{-0.6}\delta\text{MS}^-0.44$. We don't take 
-into account the effect of~$\delta$MS in our models, but we do investigate the 
-redshift dependence. A reasonable approximation to the~$t - z$ relation out to 
-$z \approx$~3 assuming typical~$\Lambda$CDM cosmology is given by: 
-\begin{equation} 
-\frac{t}{t_0} \approx (1 + z)^{-5/4} 
-\end{equation} 
-where~$t_0$ is the present-day age of the universe, and~$t$ is not simulation 
-time but the age of the universe. Plugging this relation into the 
-\citet{Tacconi2018} scaling yields the following time-dependence for 
-$\tau_\text{mol}$: 
-\begin{equation} 
-\tau_\text{mol} = \tau_{\text{mol},0}(t/t_0)^{12/25} \approx 
-\tau_{\text{mol},0}(t/t_0)^{1/2} 
-\end{equation} 
-where~$\tau_{\text{mol},0}$ is simply~$\tau_\text{mol}$ at the present day. We 
-generalize this formula to the following form: 
-\begin{equation} 
-\tau_\text{mol} = \tau_{\text{mol},0}(t/t_0)^\gamma 
-\label{eq:tau_mol}
-\end{equation} 
-In this paper we present models which adopt~$\tau_{\text{mol},0}$ = 2 Gyr 
-\citep{Leroy2008, Leroy2013, Tacconi2018} and~$\gamma$ = 1/2 based on this 
-argument. We have also ran simulations which adopt~$\tau_{\text{mol},0}$ = 1 
-Gyr and~$\gamma$ = 0 (a time-independent~$\tau_\text{mol}$), and found similar
-results. In all timesteps an annnuli,~\texttt{VICE} infers~$\Sigma_\text{g}$ 
-from~$\dot{\Sigma}_\star$ given our equations~\refp{eq:sf_law} and 
-\refp{eq:tau_mol}.
-
-% fig 5 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.45]{sfe.pdf} 
-\caption{The star formation efficiency timescale~$\tau_\star$ as a function of 
-Galactocentric radius at simulation times of 2 Gyr (red), 4 Gyr (yellow), 
-6 Gyr (green), 8 Gyr (blue), 10 Gyr (purple), and 12.2 Gyr (the present day, 
-black) predicted by our inside-out SFH model. } 
-\label{fig:sfe} 
-\end{figure}
-
-In Fig.~\ref{fig:sfe}, we plot~$\tau_\star$ as a function of~$R_\text{gal}$ at 
-six different time stamps predicted by our fiducial, inside-out SFH model. At 
-$R_\text{gal} \lesssim$ 6 kpc,~$\tau_\star$ is near~$\tau_\text{mol}$ at all 
-times, implying a molecular fraction of unity at these radii. Although this 
-prediction is likely unrealistic because 21-cm line observations suggest the 
-presence of neutral hydrogen as close to the Galactic centre as several hundred 
-pc~\citep{Kalberla2009}, we find in practice that changing our assumptions 
-about the star formation law does not impact our conclusions. In collecting 
-results for this paper, we investigated purely linear, purely power-law, and 
-broken power-law characterizations, finding similar predictions in all cases. 
-In general we find that the detailed form of the SFH, and to some extent the 
-time-dependence of radial migration, exert much greater power in establishing 
-the model predictions than does the star formation law. Nonetheless it is an 
-interesting result that a~$\dot{\Sigma}_\star - \Sigma_\text{g}$ relation 
-informed by the observed, population averaged trend and the normalization of 
-our SFHs implied by the stellar mass of the Milky Way predicts such a 
-discrepancy with the observed HI distribution. We refrain from further 
-discussion of this with the finding that it doesn't impact the conclusions 
-detailed in the present paper.
-
-\subsection{Surface Density Gradient} 
-\label{sec:methods:surface_density_gradient}
-
-% fig 6 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.45]{surface_density_gradient.pdf} 
-\caption{The surface density of gas (blue) and stars (red) as predicted by our 
-inside-out SFH model. The dotted black line with the higher normalization 
-denotes a thin disc profile with scale length~$R_t$ = 2.5 kpc; the other 
-denotes a thick disc profile with scale length~$R_T$ = 2.0 kpc, and a ratio of 
-$\Sigma_T/\Sigma_t$~= 0.27 at~$R_\text{gal}$~= 0. The solid black line denotes 
-the sum of the two; this is the surface density gradient of the Milky Way as 
-reported by~\citet{Bland-Hawthorn2016}, renormalized to imply the same total 
-stellar mass within the disc as our models. } 
-\label{fig:surface_density} 
-\end{figure}
-
-As discussed in~\S~\ref{sec:methods:sfhs}, Appendix~\ref{sec:normalize_sfh} 
-presents justification of a recipe in which we select a unitless function 
-describing the stellar surface density gradient~$g(R_\text{gal})$. In setting 
-the normalization, our model ensures that the integral of~$g(R_\text{gal})$ 
-over the surface area of the disc predicts a total stellar mass in agreement 
-with that observed for the Milky Way. For this value, we adopt 
-$M_\star^\text{MW} = (6.08 \pm 1.14)\times10^{10}$~\msun~\citep{Licquia2015}. 
-This is the total stellar mass of the Galaxy, including the bulge; 
-\citet{Licquia2015} report~$(5.17 \pm 1.11)\times10^{10}$~\msun~as the mass of 
-the disc alone. Although we aren't modeling the bulge here, our model extends 
-to~$R_\text{gal}$ = 0 and our sample of candidate analog star particles from 
-\texttt{h277} includes those with bulge-like kinematics. 
-\par 
-In this paper we adopt the following double exponential form for 
-$g(R_\text{gal})$, describing the thin and thick disc components of the 
-Galaxy: 
-\begin{equation} 
-g(R_\text{gal}) = e^{-R_\text{gal}/R_t} + \frac{\Sigma_T}{\Sigma_t} 
-e^{-R_\text{gal}/R_T} 
-\label{eq:gradient} 
-\end{equation} 
-where~$R_t$~and~$R_T$~are the scale radii of the thin and thick discs, 
-respectively, and~$\Sigma_T/\Sigma_t$~is the ratio of their surface densities 
-at~$R_\text{gal}$~= 0. We adopt~$R_t$~= 2.5 kpc,~$R_T$~= 2.0 kpc, and 
-$\Sigma_T/\Sigma_t$~= 0.27 based on the findings of~\citet{Bland-Hawthorn2016}. 
-We plot the single exponential forms of each disc component as a dotted black 
-line in Fig.~\ref{fig:surface_density}, with the solid black line denoting the 
-sum of the two. Althoug these scale radii are smaller than the commonly adopted 
-scale radius for a single exponential disc of~$r_s \approx$~3 kpc 
-\citep[e.g.][]{Binney2008}, our choice of a double exponential disc here 
-necessitates a choice be made for not one but two scale radii. 
-\par 
-We plot the resultant surface density gradients from our fiducial, inside-out 
-SFH model in Fig.~\ref{fig:surface_density} as well, with red denoting the 
-stellar gradient and the gas in blue. We note that the stellar gradient very 
-nearly follows our target gradient denoted by the solid black line and 
-expressed by equation~\refp{eq:gradient}. Stellar migration has indeed not 
-altered the overall form of the gradient, simply introducing scatter around the 
-adopted trend. Although there are slight enhancements at small~$R_\text{gal}$ 
-and deficits at large~$R_\text{gal}$, the agreement is excellent in the regions 
-of the Galaxy where the gradient is best constrained observationally. The 
-$R_\text{gal}$ > 15.5 kpc populations are also composed entirely of stars that 
-migrated there, since that is the radius at which we shut of star formation; 
-with this mind, the under-prediction at these radii is unsurprising. 
-Furthermore, in this paper we are interested primarily in the~$R_\text{gal}$~= 
-3 - 15 kpc range anyway, since this is the region where disc stars are the 
-dominant populations. We also note that the gas gradient
-shows a break in the scale radius near~$R_\text{gal} \approx$ 
-6 kpc. This is a consequence of our adopted star formation law; at 
-$\Sigma_\text{g} = 2\times10^7$~\msun~\persqkpc~the relation changes from 
-linear at higher densities to~$\dot{\Sigma}_\star \sim \Sigma_\text{g}^{3.6}$ 
-at lower densities (see discussion in~\S~\ref{sec:methods:sfe}). Because we are 
-running~\texttt{VICE} in star formation mode, it's more accurate to say that 
-$\Sigma_\text{g}$~is a weak function of~$\dot{\Sigma}_\star$~at 
-$\Sigma_\text{g} \leq 2\times10^7$~\msun~\persqkpc~in this range as opposed to 
-$\dot{\Sigma}_\star$~being a strong function of~$\Sigma_\text{g}$. When looking 
-at the present-day gradient, this presents as a flattening of the gradient at 
-the radius where~$\Sigma_\text{g} = 2\times10^7$~\msun~\persqkpc; further 
-inspection along the y-axis of Fig.~\ref{fig:surface_density} confirms that 
-this break indeed occurs at this value of~$\Sigma_\text{g}$. 
-\par 
-Although we adopt the~\citet{Licquia2015} stellar mass of the Milky Way here, 
-we find similar results when taking a value which differs by an order of 
-magnitude. While mass typically cancels in one-zone models of chemical 
-evolution, the abundances instead determined by the evolutionary parameters 
-(e.g.~$\eta$~and~$\tau_\star$), this value sets the normalization of the 
-SFH~$\dot{\Sigma}_\star(t, R_\text{gal})$ in our models. In turn this impacts 
-the surface densities of gas~$\Sigma_\text{g}$ inferred at each timestep, and 
-thus the abundances to some extent. This choice only matters insofar as the 
-choice of star formation law matters, which we find to not impact our 
-conclusions.
-
-\subsection{Summary} 
-\label{sec:methods:summary} 
-In summary, our fiducial model has an inside-out SFH with e-folding timescales 
-derived from the observations of~\citet[][see discussion in~\S 
-\ref{sec:methods:sfhs}]{Sanchez2020}. Radial migration proceeds in a manner in 
-which our model stellar populations have a change in radius 
-$\Delta R_\text{gal}$ informed from the~\texttt{h277} hydrodynamical simulation 
-\citep[][see discussion in~\S~\ref{sec:methods:h277}]{Christensen2012, 
-Zolotov2012, Loebman2012, Loebman2014, Brooks2014}. In the base-line model, 
-stars move to their final radius with a~$\sqrt{\text{age}}$~dependence 
-(\citealp{Frankel2018, Frankel2020} model stellar migration with a similar 
-characterization; see discussion in~\S~\ref{sec:methods:migration}). Using 
-\texttt{VICE} to calculate abundances for O and Fe in this paper, our supernova 
-yields are adopted from~\citet{Johnson2020}, who in turn take these values from 
-\citet{Weinberg2017}. Outflows are characterized such that the equilibrium 
-abundance of oxygen under a constant SFH follows an abundance gradient in 
-agreement with observational results in the Milky Way (see discussion in 
-\S~\ref{sec:methods:yields};~\citet{Nidever2014} make use of similar 
-methodology). Our star formation law is based on the~\citet{Bigiel2010} and 
-\citet{Leroy2013} data presented in comparison with theoretical models in 
-\citet[][see discussion in~\S~\ref{sec:methods:sfe}]{Krumholz2018}. To describe 
-the stellar surface density gradient, we adopt the two-exponential form 
-describing the thin and thick discs from~\citet[][see discussion in~\S 
-\ref{sec:methods:surface_density_gradient}]{Bland-Hawthorn2016}. 
-\par 
-Our quality cuts imposed on the star particles from~\texttt{h277} yields a 
-sample of 3,000,556 candidate analog star particles (see discussion in~\S 
-\ref{sec:methods:h277}), only~$\sim$57\% of which have disc-like kinematics 
-at the present day. Since we're modeling the thin and thick disc populations 
-here,~$\sim$1.71 million is a much better estimate of the number of star 
-particles that we can realistically sample from. We take~$\Delta R_\text{gal}$ 
-= 100 pc as the width of each annulus from~$R_\text{gal} = 0$~to 20 kpc and a 
-timestep size of~$\Delta T$~= 10 Myr from~$T = 0$~to 12.2 Gyr. With the 
-resulting 200 zones and 1,221 timesteps, we let~\texttt{VICE} form~$n = 9$ 
-stellar populations per annulus per timestep, resulting in 2,197,000 total 
-stellar populations with predicted masses and abundances. While this is more 
-than the number of disc particles in our sample of candidate analogs, we force 
-the star formation rate to zero beyond~$R_\text{gal}$ = 15.5 kpc; while these 
-stellar populations exist within~\texttt{VICE} and are a part of the 
-computational overhead, they have zero mass and thus do not contribute to the 
-chemical evolution in our models. This results in 1,692,306 stellar 
-populations with~\textit{non-zero} masses and abundances predicted by 
-\texttt{VICE}, reasonably within the limit of what we can sample. These 
-simulations run in~$\sim$2.5 hours and take up~$\sim$235 MB of disc space per 
-output, including the extra data that we record for each stellar population's 
-analog star particle. Lastly, we adopt a~\citet{Kroupa2001} IMF throughout this 
-paper. 
-\par 
-We have ran~\texttt{VICE} for all four of our SFHs, all four migration 
-models, and all four variations in~$\tau_\text{mol}$ noted in~\S 
-\ref{sec:methods:sfe} - a total of 64 simulations, as well as a variety of 
-other test cases. In this paper, we present results wherever the model 
-prescriptions are sensitive to the assumptions. However, in general the 
-differences can be understood with only the variations in star formation 
-history and the qualitative notion that many stars have moved beyond their 
-birth radius. \texttt{VICE} calculates abundances for nearly 2 million stellar 
-populations per model; to ensure that resolution does not impact our 
-conclusions, we have also ran variations with~$n$~= 2 stellar populations per 
-zone per timestep, and found similar results in all cases.
-
-\section{Comparison to Observations} 
-\label{sec:obs_comp}
-
-% fig 7 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.28]{ofe_feh_densitymap.pdf} 
-\caption{[O/Fe]-[Fe/H] diagrams for 15 Galactic regions spanning five bins in 
-$R_\text{gal}$ and~$\left|z\right|$. Each region has its own panel, with 
-radial bins shown in columns denoted at the top, and with bins in 
-$\left|z\right|$ shown in rows denoted in text in the middle column. For each 
-region, we plot~$N$~= 10,000 points sampled from our simulated stellar 
-populations predicted by our inside-out SFH model, where the probability of 
-sampling is proportional to the present-day mass of each stellar population. 
-In all panels, points are colour-coded according to the Galactocentric radius 
-of birth of the stellar population. For reference, we plot in a solid black 
-line in all panels the gas-phase [O/Fe]-[Fe/H] track predicted by the same 
-SFH in the~$R_\text{gal}$ = 8 kpc annulus, but with the post-processing 
-migration model; this curve is the same in all panels. } 
-\label{fig:ofe_feh_diagram} 
-\end{figure*}
-
-We begin the comparison of our model predictions to observational data with the 
-distribution of stellar populations in the [O/Fe]-[Fe/H] plane. We separate 
-stars into bins based on their present-day Galactic regions defined by five 
-bins in~$R_\text{gal}$ (3 - 5, 5 - 7. 7 - 9, 9 - 11, and 11 - 13 kpc) and three 
-bins in~$\left|z\right|$ (0 - 0.5, 0.5 - 1, and 1 - 2 kpc). Within each of the 
-resulting 15 regions, we sample 10,000 stars at random from our base-line 
-inside-out SFH model. Since stars in~\texttt{VICE} are stand-ins for entire 
-stellar populations, we let the probability of sampling one of them be 
-proportional to its present day mass. We plot the results of this procedure in 
-Fig.~\ref{fig:ofe_feh_diagram}, colour-coding each stellar population by its 
-birth radius; for reference, we also plot the gas-phase track which resulted 
-from the~$R_\text{gal}$ = 8 kpc annulus with the post-processing migration 
-model in a black solid line in all panels. 
-\par 
-In Fig.~\ref{fig:ofe_feh_diagram}, we note that high-$\alpha$~sequence stars 
-are predicted to be the dominant population at small~$R_\text{gal}$ and high 
-$\left|z\right|$; conversely, the low-$\alpha$~sequence dominates the 
-statistics at large~$R_\text{gal}$~and low~$\left|z\right|$. This is consistent 
-with the observational results of~\citet{Hayden2015}, who present a density map 
-in the [O/Fe]-[Fe/H] for the same Galactic regions (see their Fig. 4). 
-Furthermore, the locus of the low-$\alpha$ sequence shifts from super-solar 
-[Fe/H] to sub-solar [Fe/H] with increasing~$R_\text{gal}$, a shift which is 
-expected given the abundance gradient that we have built into our models (see 
-discussion in~\S~\ref{sec:methods:yields}). The colour-coding of the points 
-further suggests that the width of the low-$\alpha$~sequence arises out of 
-stellar migration. Though this wouldn't occur in our models without mixing, it 
-is to some extent expected from that in combination with the built-in gradient. 
-Nonetheless this theoretical interpretation of the low-$\alpha$ sequence is 
-consistent with the arguments of~\citet{Schoenrich2009} and~\citet{Nidever2014}. 
-\par 
-We clarify that we do not claim to recover the bimodality in [$\alpha$/Fe] as 
-observed here. Although there are authors who argue to have successfully 
-reproduced such results using an inside-out SFH with stellar migration 
-\citep[e.g.][]{Sharma2020}, we find that our fiducial model fails to reproduce 
-these results (see discussion in~\S~\ref{sec:obs_comp:ofe_dists}). These 
-results do nonetheless suggest that the spatial dependence of the two sequences 
-can be attributed to stellar migration. Lastly, we note that we find similar 
-results with our other three SFHs, increasing confidence in our argument that 
-migration establishes such a spatial dependence rather than the SFH. The only 
-notable difference is that the starburst models predict a slightly higher 
-characteristic [O/Fe] for the low-$\alpha$ sequence ($\sim$+0.1). This is a 
-natural consequence of the starburst producing young,~$\alpha$-enhanced stars 
-in excess of what is predicted by the baseline model~\citep{Johnson2020}.
-
-\subsection{Abundance Gradients} 
-\label{sec:obs_comp:gradient}
-
-% fig 8
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.42]{tracks.pdf} 
-\caption{\textbf{Left}: Gas phase evolutionary tracks in the [O/Fe]-[Fe/H] 
-plane for our inside-out SFH with either post-processing (dotted lines) or 
-diffusion (solid lines) migration models. We plot tracks for seven annuli, 
-colour-coded according to their Galactocentric radius and denoted by the 
-legend in the lower-left. We mark simulation times of 2, 4, 6, 8, 10, and 12.2 
-Gyr in X's for the diffusion model and points for the post-processing model. 
-\textbf{Right}: As a function of simulation time, a proxy for the SN Ia rate 
-using the total time-derivative of the Fe mass in a given annulus, calculated 
-by subtracting the contribution from recycling and CCSN enrichment and adding 
-back that lost to star formation and outflows. We show these rates for the 
-same annuli as in the left-hand panel, multiplying them by various prefactors 
-to improve clarity. } 
-\label{fig:tracks} 
-\end{figure*}
-
-We continue by assessing the impact of stellar migration on the gas-phase 
-tracks in the [O/Fe]-[Fe/H] plane. To this end, we compare the predictions of 
-our post-processing migration model, which has stars stay at their radii of 
-birth until they instantaneously migrate at the present day, and our diffusion 
-model, which has stars migrating continuously with a~$\sqrt{\text{age}}$ 
-dependence. In the left-hand panel of Fig.~\ref{fig:tracks}, we plot the 
-[O/Fe]-[Fe/H] tracks at several radii assuming the inside-out 
-SFH, with post-processing shown in dotted lines and the diffusion in solid 
-lines. We also mark simulation times of 2, 4, 6, 8, 10, and 12.2 Gyr on each 
-track for reference. 
-\par 
-We note first and foremost that there are considerable differences between the 
-two sets of tracks, particularly at high [O/Fe]. We demonstrate here that this 
-arises out of variability in SN Ia rates caused by the time-dependent radial 
-migration of the diffusion model. From our~\texttt{VICE} outputs, the total 
-time derivative of the Fe mass in a given annulus can be obtained by its change 
-across a single timestep. By then subtracting the CCSN contribution (known 
-exactly given our adopted yield and the SFR), approximately correcting for 
-recycling, and adding back that which was lost to star formation and outflows, 
-we obtain a simple estimate of the rate of Fe production by SNe Ia. 
-\par 
-We plot this proxy as a function of simulation time in the right-hand panel of 
-Fig.~\ref{fig:tracks}, with dotted and solid lines again denoting 
-post-processing and diffusion migration models and the same colour-coding as in 
-the left-hand panel; we have also multiplied these curves by various prefactors 
-to improve clarity. As expected, the post-processing model predicts a SN Ia 
-rate which is a smooth function of time at a given~$R_\text{gal}$. The diffusion 
-model on the other hand exhibits significant variability on~$\sim$Gyr 
-timescales; the time-averaged SN Ia rate tends to follow the post-processing 
-prediction, but the instantaneous rates do not agree. A close comparison allows 
-one to realize that whenever one of the tracks in the left-hand panel shows 
-higher (lower) [O/Fe] at a given [Fe/H], there is an excess (deficit) in the SN 
-Ia rate at a similar time and radius. Early times in the~$R_\text{gal}$ = 15 
-kpc annulus illustrates a rather extreme example whereby the SN Ia rate is 
-effectively zero for nearly 3 Gyr. We also note that the fractional amplitude 
-of the variability increases with~$R_\text{gal}$; the log-scaled y-axis makes 
-this clear. This makes sense physically because the lower stellar number 
-density in the outer Galaxy means it would be much more susceptible to sampling 
-noise. That is, a single star migrating has a larger fractional impact at 
-large radii than small radii.
-
-% fig 9 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.32]{metallicity_gradient.pdf} 
-\caption{Radial abundance gradients in [O/H] (top, red), [Fe/H] (top, blue), 
-and [O/Fe] (bottom) for our four fiducial SFHs - constant (far left), 
-inside-out (left-middle), late-burst (right-middle), and outer-burst (far 
-right). We plot the gas-phase abundance at the present day as a function of 
-Galactocentric radius in solid lines. Stars denote the median of the stellar 
-MDF of the 100-pc width annulus at a given radius, with shaded regions marking 
-the 16th and 84th percentiles thereof. Black lines in the top panels denote our 
-target [$\alpha$/H] gradient of mode([$\alpha$/H]) = +0.3 at~$R_\text{gal}$~= 
-4 kpc with a slope of -0.08 kpc$^{-1}$. } 
-\label{fig:metallicity_gradient} 
-\end{figure*}
-
-Although one may expect the rates predicted by the two migration models to 
-agree based on the dynamical argument that a star migrating outward should be 
-balanced by a star migrating inward due to the conservation of energy, the SN 
-Ia rate depends not only on stellar number density but also on the masses and 
-ages of the stellar populations. While an inwardly migrating star should be 
-balanced dynamically by an outwardly migrating one, the SN Ia rate is 
-unaffected only when the two have masses and ages such that the SN Ia DTD has 
-the same value for both stars. Fluctuations in the SN Ia rate at these 
-amplitudes can be understood through a comparison of the timescales associated 
-with radial migration and SN Ia events. In Fig.~\ref{fig:h277_decomposition}, 
-we plotted the distribution of final radii in bins of birth radius and age, 
-which are used in driving stellar migration in our models (see discussion in~\S 
-\ref{sec:methods:h277}). From this, we noted that~$\sim$40\% of~\texttt{h277} 
-star particles migrated beyond their birth radius by the time they were~$\sim$2 
-Gyr old. Though our adopted form differs slightly in detail, if the SN Ia DTD 
-is a~$\sim t^{-1}$ power-law with a minimum delay time of~$\sim$100 Myr 
-\citep{Maoz2012, Maoz2017}, then there should be similar numbers of SN Ia 
-events with delay times between 1 and 10 Gyr as there are between 100 Myr and 1 
-Gyr. While our~$R_\text{gal}$~= 15 kpc annulus is something of an extreme 
-example, when one realizes that this means~$\sim$half of SN Ia progenitors may 
-move significantly beyond their birth radius, the amplitude of the variability 
-seen in the right-hand panel of Fig.~\ref{fig:tracks} is not surprising. The 
-fact that >10\% of events are seen at >10 kpc from their host galaxies in the 
-ASAS-SN bright SN catalog~\citep{Holoien2019} adds qualitative, observational 
-support to the argument that SN Ia progenitors may often form at significantly 
-different radii than where the explosions are observed. 
-\par 
-We thus argue that the radial migration of nucleosynthetic yields can occur 
-alongside stellar migration for delayed sources. Though we do not investigate 
-this effect for such elements in this paper, it would be reasonable to expect 
-similar predictions for s-process elements produced in AGB stars like carbon, 
-nitrogen, strontium, yttrium, and zirconium as well as r-process elements from 
-neutron star mergers if the associated DTD is sufficiently long. What we really 
-learn from this investigation is that tracks are not simple functions when 
-stellar migration is taken into account. To first order, they're characterized 
-by the late-time equilibrium abundance and the value of~$\tau_\star$~setting 
-the position of the ``knee''~\citep{Weinberg2017}, though migration causes 
-noticeable variations which should depend on the details of the adopted 
-dynamical history. In~\S~\ref{sec:obs_comp:age_alpha}, we demonstrate that 
-this is a means with which truly young, super-solar [$\alpha$/Fe] stars in the 
-solar neighborhood can be explained theoretically. 
-\par 
-We continue with an investigation into the radial abundance gradients predicted 
-by our models. To some extent, a gradient is built into our models via a 
-scaling of the mass loading factor~$\eta$~with Galactocentric radius (see 
-discussion in~\S~\ref{sec:methods:yields}). In parameterizing the 
-$\eta-R_\text{gal}$ scaling, we assumed our constant SFH model and the 
-associated equilibrium abundance for alpha elements. Like the surface density 
-gradient, we also assumed that stellar migration does not alter the overall 
-form. We plot the radial [O/H] and [Fe/H] gradients predicted by all our 
-models in the top row of Fig.~\ref{fig:metallicity_gradient}, and the [O/Fe] 
-gradients in the bottom row. In all panels, stars denote the median abundance 
-in each annulus, and the shaded region denotes the 16th and 84th percentiles of 
-the MDF in that zone; solid lines denote the gas-phase gradient at the present 
-day. Although we built the gradient into our models based on the mode abundance, 
-we illustrate them here according to the median; we find that with annuli as 
-narrow as~$\Delta R_\text{gal}$~= 100 pc, the mode is a sufficiently noisy 
-statistic to introduce noticeably more scatter in this relation. Nonetheless we 
-have verified that it follows the trend implied by our target gradient, 
-illustrated by the solid black line. The median gradient for all of our model 
-SFHs follows a slightly shallower trend than the mode, which is expected when 
-the metallicity distribution is skew-negative in the inner Galaxy and 
-skew-positive in the outer Galaxy. 
-\par 
-We note that our models indeed recover an~$R_\text{gal}$-[O/H] relation 
-resembling that which was adopted. As was the case for the surface density 
-gradient (see discussion in~\S~\ref{sec:methods:surface_density_gradient}), 
-stellar migration appears to only introduce scatter. While our procedure for 
-setting setting the abundance gradient did not consider Fe, our models predict 
-it to follow a gradient similar to that of O. We further note that all SFHs 
-predict an [O/Fe] gradient which is relatively flat at all radii, steepening 
-only at very small and very large~$R_\text{gal}$. The trend toward higher 
-[O/Fe] beyond~$R_\text{gal}$~= 15.5 kpc is expected, since this is the radius 
-at which we shut off star formation; all stellar populations at these radii at 
-the present day formed in the disc and migrated there, meaning this region of 
-space in our model is populated only by stars sufficiently old to have migrated 
-such distances. Because they're old, they also tend to be~$\alpha$-enhanced. 
-This is consistent with the findings of~\citet{RadburnSmith2012}, who argue 
-that the outskirts of the NGC 7793 disc formed largely out of stellar 
-migration. {\color{red} Observational reference on the increase in [O/Fe] at 
-small~$R_\text{gal}$? Maybe~\citet{Hayden2015}, but I'm not sure.} 
-\par 
-We also note that our models predict differences between the stellar and 
-present-day gas-phase gradients which are sensitive to the adopted SFH. In the 
-constant SFH model, the gas-phase gradient follows the mode abundance by 
-construction. In the inside-out, late-burst, and outer-burst models, the 
-ISM at small~$R_\text{gal}$~is considerably more metal-rich than the stars at 
-similar radii. The late-burst model shows the largest difference; this is a 
-consequence of the starburst at small~$R_\text{gal}$, an effect which is absent 
-in the outerburst model. In accretion-induced starbursts, re-enrichment can 
-briefly produce super-equilibrium abundances in the gas-phase which then decay 
-back to the equilibrium abundance as the SFR declines~\citep{Johnson2020}. This 
-effect can also be seen in the outer-burst model; at~$R_\text{gal}$ slightly 
-larger than 6 kpc where the starburst did occur, the abundances are larger than 
-at slightly less than 6 kpc, where the star burst did~\textit{not} occur. 
-Altogether, these differences are reflective of the notion that the stellar 
-abundance gradient is sensitive to stars of all ages and thus the entire star 
-formation history, while the gas-phase gradient is more reflective of 
-enrichment over the previous depletion time.
-
-\subsection{Metallicity Distributions Functions} 
-\label{sec:obs_comp:mdfs}
-
-% fig 10 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.34]{mdf_3panel_fe.pdf} 
-\caption{Metallicity distribution functions (MDFs) in [Fe/H] predicted by our 
-fiducial, inside-out model (left) and as observed in APOGEE DR16 (right), for 
-stars and simulated stellar populations with present-day~$\left|z\right|$~= 0 - 
-0.5 kpc (bottom), 0.5 - 1 kpc (middle), and 1 - 2 kpc (top). MDFs are shown in 
-bins of Galactocentric radius: 3 - 5 kpc (black), 5 - 7 kpc (red), 7 - 9 kpc 
-(yellow), 9 - 11 kpc (green), 11 - 13 kpc (blue), and 13 - 15 kpc (purple). 
-The points near the top of the bottom panels denote what the mode abundance 
-would be if it followed out target gradient of [Fe/H] = +0.3 at~$R_\text{gal}$ 
-= 4 kpc with a slope of -0.08 kpc$^{-1}$ exactly, assuming the inner radius of 
-each bins (i.e. there is no point plotted for 15 kpc). All distributions are 
-smoothed with a box-car width of [Fe/H]~$\pm$~0.1 for clarity. } 
-\label{fig:mdf_3panel_fe} 
-\end{figure}
-
-% fig 11 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.34]{mdf_3panel_o.pdf} 
-\caption{The same as Fig.~\ref{fig:mdf_3panel_fe}, but for [O/H]. } 
-\label{fig:mdf_3panel_o} 
-\end{figure}
-
-Metallicity distribution functions (MDFs) and how they vary with Galactic 
-region are one of the core predictions of chemical evolution models. In this 
-section, we compare our model predicted MDFs to those observed in the 16th 
-data release of APOGEE (DR16;~\citealp{Ahumada2020, Majewski2017}). The 
-data are reduced using the APOGEE Stellar Parameters and Chemical Abundances 
-Pipeline (ASPCAP;~\citealp{Holtzman2015, GarciaPerez2016}). For further details 
-of the APOGEE survey, a brief summary can be found in~\S~2 of 
-\citet{Weinberg2019}. We restrict our sample to stars with effective 
-temperatures of 4000 K~$\leq T_\text{eff} \leq$~4600 K, surface gravities of 
-1.0~$\leq \log g \leq$~2.5, and signal-to-noise ratios of at least 100. These 
-cuts ensure that our sample consists of stars on the upper red giant branch, 
-safely excluding red clump stars to avoid obvious systematics in the 
-abundance distributions. 
-\par 
-In the disc midplane, stars as observed by APOGEE are known to exhibit mode 
-[$\alpha$/H] and [Fe/H] abundances that depend on Galactocentric radius, with a 
-skew-negative distribution in the inner Galaxy and skew-positive in the outer 
-Galaxy~\citep{Hayden2015, Weinberg2019}. Off the midplane, the MDFs converge on 
-[$\alpha$/H]~$\approx$~[Fe/H]~$\approx$~-0.5. This result is replicated in the 
-right-hand column of panels~\ref{fig:mdf_3panel_fe} and~\ref{fig:mdf_3panel_o}. 
-The left-hand columns show the distributions predicted by our fiducial 
-inside-out model. We note that these replicate the qualitative scaling of the 
-mode [O/H] and [Fe/H] with present-day Galactocentric radius, though our APOGEE 
-data suggest that the 3 - 5 and 5 - 7 kpc bins share a common mode abundance. 
-This was also seen in~\citet{Hayden2015}. Our models do not predict this 
-detail; this could indicate that we have incorrectly parameterized outflows in 
-the inner Galaxy (see discussion regarding our scaling of the mass loading 
-factor~$\eta$~with~$R_\text{gal}$ in~\S~\ref{sec:methods:yields}). We would 
-expect a flat [X/H] gradient and MDFs with similar modes if we simply chose it 
-to be so by letting~$\eta$~be constant at small~$R_\text{gal}$. Another 
-possibility is the cessation of star formation in these regions; by tracing 
-products of star formation such as HII regions~\citep{Guesten1982}, supernova 
-remnants~\citep{Leahy1989}, and pulsars (\citealp*{Lyne1985}; 
-\citealp{Case1998}), the surface density of star formation~$\dot{\Sigma}_\star$ 
-in the Milky Way is known to reach a maximum at~$R_\text{gal} \approx$~4 kpc 
-(see Fig. 1 of~\citealt{Peek2009} and Fig. 2 of~\citealt{Fraternali2012}). Our 
-models by construction predict~$\dot{\Sigma}_\star$ to decrease monotonically 
-with~$R_\text{gal}$~(see Fig.~\ref{fig:evol}). If the Milky Way has begun 
-quenching star formation, a process which is believed to begin in the centres 
-of galaxies at this mass~\citep[e.g.][]{Ellison2020b}, then fewer stars would 
-form in the most metal-rich regions than do in our models, cutting off the MDF 
-at high [O/H] and [Fe/H]. 
-\par 
-Beyond the midplane, our models fail to fully replicate the convergence of the 
-MDFs at [X/H]~$\approx$~-0.5. The observed MDF at small radii shfits from 
-skew-negative with a metal-rich mode to skew-positive with a metal-poor 
-mode with increasing~$\left|z\right|$. In our model predicted MDFs for small 
-$R_\text{gal}$, the mode does shift to lower abundances, but not to the same 
-extent as in the observed sample, and with minimal change in skewness. 
-Although the model predicts a portion of the effect, it cannot account for the 
-entire~$\left|z\right|$-dependence of the MDF shape in the inner Galaxy.
-
-\subsection{[O/Fe] distributions in Bins of [Fe/H]} 
-\label{sec:obs_comp:ofe_dists} 
-In this section we compare our predicted [O/Fe] distributions in various 
-Galactic regions to those recently published in~\citet{Vincenzo2021a}. As in our 
-\S~\ref{sec:obs_comp:mdfs}, they also make use of APOGEE DR16 
-\citep{Ahumada2020, Majewski2017}, and impose a similar set of cuts on 
-effective temperature, surface gravity, and signal-to-noise (see their~\S~2). 
-These distributions are estimates of the~\textit{intrinsic} [O/Fe] 
-distributions that, when 
-convolved with observational uncertainties and the APOGEE selection function, 
-would resemble the observed MDFs like those in~\citet{Hayden2015}. We show the 
-distributions predicted by our fiducial model in~$\Delta$[O/Fe] = 0.04 bins 
-across 15 Galactic regions in comparison to the~\citet{Vincenzo2021a} 
-distributions shown in dashed lines in Fig.~\ref{fig:ofe_mdfs_insideout}. 
-Galactic regions 
-are defined by a range in~$R_\text{gal}$, shown in columns and denoted at the 
-top of the figure, and a range in~$\left|z\right|$, shown in rows and denoted 
-in text in the left-hand column. We show this comparison for two bins in 
-[Fe/H], colour-coded according to the legend in the top-right panel.
-
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.32]{ofe_mdfs.pdf} 
-\caption{Predicted distributions in [O/Fe] in 15 Galactic regions and in two 
-bins in [Fe/H]. Columns correspond to bins in~$R_\text{gal}$, denoted at the 
-top of each column. Rows correspond to bins in~$\left|z\right|$, denoted in 
-text in the left-hand column. Distributions are color-coded according to the 
-[Fe/H] the sample is drawn from, denoted by the legend in the upper right 
-panel. Solid lines represent that predicted by our inside-out SFH in 
-$\Delta$[O/Fe] = 0.04 bins, while dashed lines correspond to the fits to the 
-APOGEE DR16 data presented in~\citet{Vincenzo2021a}, which quantify the 
-intrinsic distributions accounting for observational uncertainties and the 
-APOGEE selection function. } 
-\label{fig:ofe_mdfs_insideout} 
-\end{figure*}
-
-Finding similar results for all of our SFHs, we note that our model adequately 
-reproduces the broad nature of the [O/Fe] distributions at fixed [Fe/H] seen in 
-the APOGEE data. Some distributions in a specific Galactic region and [Fe/H] 
-bin show a bimodality in decent agreement with the observations (e.g. the 
--0.4~$\leq$~[Fe/H]~$\leq$~-0.2 bin at~$R_\text{gal}$~= 7 - 9 kpc and 
-$\left|z\right|$ = 1 - 2 kpc), but this is not true of all Galactic regions in 
-both metallicity bins. Instead, the principle failure of our model is that it 
-overpredicts the number of intermediate [O/Fe] stars. 
-\par 
-In the inner Galaxy, our model overestimates the mode [O/Fe] to some extent for 
-both [Fe/H] bins, but the difference is larger for the higher of the two. This 
-discrepancy also increases with increasing~$\left|z\right|$. At fixed 
-$R_\text{gal}$, the~\citet{Vincenzo2021a} distributions show two peaks which do 
-not change with~$\left|z\right|$; only their relative heights vary. This is 
-an assumption built into the model, but the agreement with the APOGEE data is 
-good. However, this is a region of the Galaxy where there aren't many APOGEE 
-stars. At~$\left|z\right|$ = 1 - 2 kpc for ~$R_\text{gal}$ = 3 - 5 and 5 - 7 
-kpc, the~\citet{Vincenzo2021a} model is fit to 31 and 17 stars, respectively. In 
-comparison, there are 109 in the solar annulus, and all other bins have >75 
-stars involved in the fit. It's possible the observed distributions shift 
-slightly to higher [$\alpha$/Fe], but at most at the~$\lesssim$~0.05 level 
-(see their Fig. 11). 
-\par 
-If this discrepancy persists in subsequent APOGEE data releases which will 
-better characterize the distributions in these regions, it's possible the 
-origin is tied to the Sagittarius dwarf. The~\texttt{h277} simulation, which 
-drives stellar migration in our models (see discussion in~\S 
-\ref{sec:methods}), did not have such an accretion event. With its most recent 
-major merger occurring at a redshift of~$z \approx$~3, this galaxy has 
-previously been selected for investigation expressly because of its quiescent 
-merger history~\citep[e.g.][]{Zolotov2012}. N-body models for the tidal 
-disruption of the Sagittarius dwarf, on the other hand, suggest pericentric 
-passages around 6.5, 4.5, 2.75, 1, and 0.1 Gyr ago~\citep{Law2010}. In addition 
-to potentially triggering episodes of star formation 
-\citep[e.g.][]{RuizLara2020}, more frequent pericentric passages of a massive 
-satellite could kinematically heat low-[$\alpha$/Fe] disc stars to higher 
-$\left|z\right|_\text{max}$~orbits. Such effects are not a component of the 
-dynamical history of~\texttt{h277}; this is one instance where running our 
-models with a different hydrodynamical simulation's star particles may be an 
-enlightening comparison. 
-\par 
-The notion that an [$\alpha$/Fe] dichotomy can arise out of radial migration 
-alone traces back to~\citet{Schoenrich2009}, and was later explored by 
-\citet{Nidever2014} and recently by~\citet{Sharma2020}. This however suggests 
-that an inside-out star formation history combined with stellar migration is not 
-conducive to predicting this observed result, even when a recent starburst is 
-added. The primary failure being an overpredicted frequency of intermediate 
-[$\alpha$/Fe] stars, this could point to a number of things. If the bimodality 
-is to arise out of inside-out Galaxy evolution and stellar migration alone, 
-then the transition between high- and low-$\alpha$ sequences needs to occur 
-faster than it does in these models. The analytic arguments of 
-\citet{Weinberg2017} suggest that the approach to equilibrium occurs on the 
-order of the SFE timescale~$\tau_\star$ (see~\S~\ref{sec:methods:sfe}). 
-Since we've adopted a star formation law which is motivated by observational 
-results, the failure of these models to reproduce the observed dichotomy 
-suggests that the typical SFE timescales as observed are not short enough to 
-explain such a fast transition. This would imply that either the Milky Way 
-occupied a special place in the scatter of the observed 
-$\dot{\Sigma}_\star-\Sigma_\text{g}$ relation at a time early in its 
-evolutionary history, or the bimodality arose out of alternative pathways. 
-Under our current assumptions, the simplest way to decrease the frequency of 
-intermediate [$\alpha$/Fe] stars is to simply shut off (or turn down) star 
-formation when the ISM is at such a composition. This is an indication 
-that two-infall evolutionary histories~\citep[e.g.][]{Chiappini1997, 
-Chiappini2001, Romano2010, Grisoni2017, Noguchi2018, Palla2020, Spitoni2016, 
-Spitoni2018, Spitoni2019a, Spitoni2020, Spitoni2021} would improve the 
-agreement between our model predictions and the observed distributions.
-
-\subsection{The Age-[$\alpha$/Fe] Relation} 
-\label{sec:obs_comp:age_alpha} 
-In this section, we assess the predicted age-[O/Fe] relations of our models, 
-using the results of~\citet{Feuillet2019} as the observational benchmark; their 
-stellar age measurements are based on isochrone matching. While we made 
-use of APOGEE DR16 data in comparing our model predictions to the observed 
-MDFs~\citep[][see~\S~\ref{sec:obs_comp:mdfs}]{Ahumada2020, Majewski2017}, they 
-made use of APOGEE DR14 stars for which parallax measurements are available 
-from Gaia~\citep{Abolfathi2014, GaiaDR2}. With their spatial and quality cuts, 
-the final 
-sample consisted of 77,562 stars. In bins of [O/Fe], they assume a gaussian 
-log age distribution, fitting the mean and standard deviation to the stars in 
-that bin. Because they assume a gaussian, they would report an equal mean 
-and median log age. This means that a one-to-one comparison of our model 
-predictions to their results is not free of nuance, because they predict 
-log age distributions which are highly non-gaussian at fixed [O/Fe]. 
-\par 
-The stellar populations from our simulations have different masses; this 
-necessitates weighting the age-distributions by present-day mass, because that 
-scales with the number of stars that a model stellar population represents. We 
-therefore adopt the 50th percentile of the mass-weighted age distribution in a 
-bin of [O/Fe] as the characteristic age to compare to the~\citet{Feuillet2019} 
-measurements. We refer to this quantity as the mass-weighted median age.
-
-% fig 13 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.34]{age_ofe_migration_comparison.pdf} 
-\includegraphics[scale = 0.34]{age_ofe_sfh_comparison.pdf} 
-\caption{
-\textbf{Left}: A comparison of the predicted age-[O/Fe] relation for the solar 
-annulus ($R_\text{gal}$ = 7 - 9 kpc and~$\left|z\right|$ = 0 - 0.5 kpc) between 
-the post-processing (upper left), diffusion (upper right), sudden (lower left), 
-and linear (lower right) migration models, assuming our inside-out SFH. 
-\textbf{Right}: The same as the left-hand panels, instead comparing the impact 
-of our constant (upper left), inside-out (upper right), late-burst (lower left), 
-and outer-burst (lower right) SFHs, assuming diffusion migration. In all panels, 
-red triangles and error bars denote the observed mean age and dispersion 
-thereof in bins of [O/Fe] as reported by~\citet{Feuillet2019}; here we include 
-only the bins containing at least 15 stars. Black squares denote the 
-mass-weighted median age in 0.02-dex bins in [O/Fe] predicted by our models, 
-with error bars denoting the 16th and 84th percentiles of the mass-weighted 
-age distribution in those bins. Points in the background denote each individual 
-stellar population from the model with a final position in the solar annulus, 
-colour-coded according to their Galactocentric radius of birth. 
-}
-\label{fig:age_alpha} 
-\end{figure*}
-
-In the left-hand set of panels of Fig.~\ref{fig:age_alpha}, we compare the 
-age-[O/Fe] relation in the solar annulus ($R_\text{gal}$~= 7 - 9 kpc and 
-$\left|z\right|\leq$~0.5 kpc) predicted by our four migration models to the 
-\citet{Feuillet2019} measurements, shown in red triangles. We mark the 
-mass-weighted median age in bins of [O/Fe] in each model with black squares, 
-and plot for reference in the background each individual stellar population in 
-the solar annulus, colour-coded according to its Galactocentric radius of birth. 
-\par 
-We note that the inside-out SFH, assumed by all four of the models illustrated 
-here, provides a reasonable description of the age-[O/Fe] relation as observed 
-in APOGEE. We also note that each model for the time-dependence of stellar 
-migration predicts differing amounts of scatter in the age-[O/Fe] relation. 
-Diffusion has the most, followed by linear, then sudden, and lastly 
-post-processing. We interpret this as a consequence of the variability in the 
-SN Ia rate as a function of radius and time caused by time-dependent migration 
-(see Fig.~\ref{fig:tracks} and associated discussion near the beginning of~\S 
-\ref{sec:obs_comp}). When the SN Ia rate is higher or lower than expected given 
-the SFH of an annulus, then the Fe abundance in that zone will increase or 
-decrease accordingly. This can occur if there is a significant net gain or loss 
-of SN Ia progenitors in a given time interval due to time-dependent migration. 
-The gas-phase [O/Fe] then decreases or increases in turn, and the stars which 
-form out of that gas inherit these compositions. When migration is taken into 
-account and stellar populations are mixed as a consequence, the observational 
-signature is intrinsic scatter in the age-[$\alpha$/Fe] relation. 
-\par 
-All of the models in the left-hand set of panels predict a correlation between 
-mass-weighted median age and [O/Fe] in good agreement the~\citet{Feuillet2019} 
-measurements assuming the inside-out SFH. This suggests that the population 
-averaged trend is unaffected by stellar migration. However, only the diffusion 
-and linear migration models predict a population of young ($\lesssim$~4 Gyr), 
-[$\alpha$/Fe]~$\approx$~+0.1 - 0.2 stars in the solar neighbourhood. These 
-stars are a part of the noticeable upward scatter in the relationship, and we 
-therefore interpret their origin to be the same as the scatter itself - they 
-formed in a region of the Galactic ISM at a time when it was particularly 
-alpha-enhanced due to a rather lasting deficit in SN Ia events. These stars 
-then migrated to the solar annulus, where they showed up in the APOGEE data 
-when stellar ages were measured using carbon-to-nitrogen ratios 
-\citep{Martig2016}, isochrone matching~\citep{Feuillet2018, Feuillet2019}, 
-and with the asteroseismic ages of the origin APOKASC catalog 
-\citep{Chiappini2015, SilvaAguirre2018, Pinsonneault2014}. 
-\par 
-\citet{SilvaAguirre2018} demonstrate that the observed young $\alpha$-rich 
-stars in the solar annulus have kinematics similar to the rest of the 
-high-$\alpha$ population, and suggested this may be the result of stellar 
-mergers or mass transfer events. This would produce a population of truly old 
-stars masquerading as young stars. In a sample of 51 young, $\alpha$-rich 
-red giants,~\citet{Hekker2019} demonstrate that a portion of these stars have 
-carbon-to-nitrogen ratios consistent with mass transfer events, but that others 
-do not, indicating they're either truly young stars or the result of mergers 
-on the main sequence. As far as we know, the mechanism discussed here is the 
-first theoretical explanation of the origin of these stars. We note 
-additionally that under this explanation, the young~$\alpha$-rich stars are 
-not so much $\alpha$-rich as they are Fe-poor, and form overwhelmingly at 
-large~$R_\text{gal}$ where the SN Ia rate is most variable (see discussion in 
-\S~\ref{sec:obs_comp:gradient}). 
-\par 
-In the right-hand set of panels in Fig.~\ref{fig:age_alpha}, we 
-compare the model predictions of our four different SFHs, assuming our 
-diffusion migration model, with the same plotting scheme and colour-coding as 
-in the left-hand panels. We note that the constant and inside-out SFHs describe 
-the data the best. Although our e-folding timescales for star formation are 
-sufficiently long at large~$R_\text{gal}$ such that there is little difference 
-between the constant and inside-out SFHs there anyway (see discussion in~\S 
-\ref{sec:methods:sfhs}), our constant SFH is idealized and of purely 
-theoretical interest, making the inside-out model the more likely of the two. 
-Below [O/Fe]~$\approx$~+0.1, the~\citet{Feuillet2019} data seem to follow a 
-slightly steeper age-[$\alpha$/Fe] relation than our inside-out model 
-predicts. This could point to any number of things being an inaccuracy in our 
-models: the detailed form of the SFH or the SN Ia DTD, our supernova yields, 
-or observational [O/Fe] errors, all of which are plausible. 
-\par 
-We note that our starburst models, both late-burst and outer-burst, disagree 
-with the~\citet{Feuillet2019} measurements. The late starburst produces a 
-population of young, $\alpha$-rich stars due to the perturbed ratio of core 
-collapse to type Ia supernova rates~\citep{Johnson2020}. With the starburst 
-occurring in a substantial fraction of the ISM in both models, the result is an 
-increase in the bulk [$\alpha$/Fe] for young stars which simply is not seen in 
-the observed sample. The effect is strong enough that at [O/Fe]~$\approx$~+0.1, 
-both models considerably overpredict the width of the distribution, 
-simultaneously predicting a mass-weighted median age many times the standard 
-deviation younger than observed. This discrepancy is of interest, because these 
-models were motivated by the observational results of~\citet{Mor2019} and 
-\citet{Isern2019} which suggest such a recent starburst. Although our 
-functional forms differ from what they reported in detail, they're reasonable 
-descriptions of the measurements within the error bars. This suggests that the 
-results of~\citet{Mor2019} and~\citet{Isern2019} are at odds with chemical 
-evolution models of the Milky Way. If the Galaxy truly experienced a recent 
-starburst, then something not included in our models had to prevent this global 
-increase in [$\alpha$/Fe].
-
-% fig 14 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.32]{age_alpha_regions.pdf} 
-\caption{The age-[O/Fe] relation in 12 Galactic regions predicted by our 
-inside-out SFH. Bins in Galactocentric radius are shown in columns, and labeled 
-at the top. Bins in the height~$\left|z\right|$ above/below the disc midplane 
-are shown in rows, noted in the left-hand column. Red triangles, black squares, 
-error bars, and background points are as in Fig.~\ref{fig:age_alpha} for the 
-corresponding Galactic region. The solid black line connects the black squares 
-in the bottom, left-middle panel, and is replicated elsewhere for reference. } 
-\label{fig:age_alpha_regions} 
-\end{figure*}
-
-In Fig.~\ref{fig:age_alpha_regions}, we extend the comparison of our base-line, 
-inside-out model and the observations of~\citet{Feuillet2019} to other 
-Galactic regions. We visualize the data there in the same manner as for 
-previous figures in this section. While the inside-out model shows the best 
-agreement with the observed result in the solar annulus, there are some mild 
-discrepancies for stars farther from the sun.~\citet{Feuillet2019} report ages 
-for~$\alpha$-rich stars that are younger at large~$R_\text{gal}$ and high 
-$\left|z\right|$, though in most cases only by~$\sim$20\%. Our model does not 
-capture this effect. To illustrate this, we connect the black squares in the 
-panel corresponding to the solar annulus with a black line, and then reproduce 
-this line in all panels for reference. If the observational result is correct, 
-this is an interesting effect that our model doesn't reproduce in any of the 
-variants we've explored. Furthermore, we note that the model overpredicts ages 
-at large~$\left|z\right|$. As with the overpredicted [O/Fe] ratios at small 
-$R_\text{gal}$, we speculate that this may be tied to the Sagittarius dwarf 
-(see discussion in~\S~\ref{sec:obs_comp:ofe_dists}). By using a hydrodynamical 
-simulation of a 
-galaxy which exhibited more pericentric passages of a massive satellite, more 
-young stars may be kinematically heated to high~$\left|z\right|_\text{max}$ 
-orbits. This is another instance where running our models with a different 
-hydrodynamical simulation's star particles may be an enlightening comparison. 
-\par 
-We note that the intrinsic scatter in the age-[O/Fe] relation is predicted to 
-grow with increasing~$R_\text{gal}$; this can be seen in the error bars on the 
-black squares as well as the coloured points. We identify two sources of this 
-dependence; the bulk of the scatter, at least at [O/Fe]~$\gtrsim$~+0.05, arises 
-from the variability in the SN Ia rates as described in~\S 
-\ref{sec:obs_comp:gradient}. Having demonstrated that the SN Ia rate is most 
-variable at large~$R_\text{gal}$, the in-situ populations in the outskirts of 
-the Galactic disc formed from an ISM whose gas-phase [O/Fe] ratio varied with 
-a higher amplitude. Since the observational signature of this variability is 
-scatter in the observed age-[O/Fe] relation, our model predicts the most 
-intrinsic scatter in Galactic regions where that variability has the highest 
-amplitude. Second, the analytic models of~\citet{Weinberg2017} suggest that 
-as the e-folding timescale for star formation~$\tau_\text{sfh}$ increases, the 
-model-predicted [O/Fe] of the youngest stars increases with a weak dependence. 
-With a range of e-folding timescales in our model, this implies a distribution 
-of [O/Fe] at age = 0 with nonzero width without considering the migration of 
-nucleosynthetic yields. This can be seen in the post-processing model 
-predicted age-[O/Fe] relation in Fig.~\ref{fig:age_alpha}. In this pathway, 
-scatter is induced by mixing populations that follow age-[O/Fe] relations of 
-slightly different normalizations which are nearly flat intrinsically, 
-producing a noticeably wide age distribution near solar [O/Fe]. 
-\par 
-Although the iron-peak is the only class of elements with a delayed 
-nucleosynthetic source that we consider in the present paper, we expect similar 
-results for other delayed sources with regard to the variability in enrichment 
-rates and scatter in age-[X/Y] relations. The details of SN Ia nucleosynthesis 
-did not matter in our interpretations in this section; it is based purely on 
-the characteristic delay-times of the source and how they compare to the 
-timescales of stellar migration. Our models should then find similar 
-predictions with, for example, s-process (slow neutron capture) elements like 
-carbon, nitrogen, strontium, yttrium, and zirconium produced in asymptotic 
-giant branch stars. In fact, using hydrodynamical simulations from the Auriga 
-project~\citep{Grand2017},~\citet{vandeVoort2020} find that the intrinsic 
-scatter in r-process (rapid neutron capture) abundances increases for models 
-with longer characteristic delay times. Although the first observations of a 
-binary neutron star merger (GW170817) exhibited an optical counterpart which 
-was consistent with being powered by the radioactive decay of r-process 
-elements~\citep{Abbott2017, Coulter2017, Drout2017, Pian2017}, it remains 
-unclear the extent to which neutron star mergers contribute to r-process 
-nucleosynthesis in the universe~\citep{Cote2019, Mishenina2019, Siegel2019, 
-vandeVoort2020, Vincenzo2021b}. Although it's likely unfeasible at present due 
-to the requirement for high precision abundance measurements of intrinsically 
-rare elements in many stars, with future observational capabilities, the 
-application of our results as well as~\citet{vandeVoort2020} suggests that the 
-intrinsic scatter in r-process abundances may provide constraints on the 
-characteristic delay times of such nucleosynthetic events.
-
-\subsection{The Age-Metallicity Relation} 
-\label{sec:obs_comp:amr}
-
-% fig 15 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.35]{amr_static_o.pdf} 
-\caption{The age-[O/H] relation predicted by our constant SFH model for 
-$R_\text{gal}$~= 7 - 9 kpc (left) and 11 - 13 kpc (right). Each panel plots 
-only the~$\left|z\right|\leq$~0.5 kpc population. The colored points in the 
-background and the black squares with error bars are as in Fig. 
-\ref{fig:age_alpha}, but with our binned, model prediction quantified in 
-bins of~$\Delta$[O/H] = 0.05. } 
-\label{fig:age_oh_static} 
-\end{figure}
-
-Although the age-metallicity relation (AMR) is usually formulated in terms of 
-[Fe/H], it is also interesting to quantify the age-[O/H] relation, because it 
-is not affected by SN Ia enrichment. The extent to which they differ indicates 
-the extent to which the delayed timescale and impact of migration on SN Ia 
-enrichment is important in shaping the age-[Fe/H] relation. In Fig. 
-\ref{fig:age_oh_static}, we present the age-[O/H] relation predicted by our 
-constant SFH model for the~$\left|z\right|\leq$~0.5 kpc population at 
-$R_\text{gal}$ = 7 - 9 and 11 - 13 kpc. The black squares with error bars 
-denote the mass-weighted median age as in~\S~\ref{sec:obs_comp:age_alpha}, and 
-we again plot the individual stellar populations in the background for 
-reference, colour-coded according to their Galactocentric radius of birth. We 
-omit the~\citet{Feuillet2019} measurements from this figure, because the 
-constant SFH model is of purely theoretical interest, removing the effects of 
-a time-varying SFH while including the effects of stellar migration. 
-\par 
-The intrinsic scatter in the observed AMR has previously been interpreted as 
-evidence for radial mixing~\citep{Edvardsson1993, Sellwood2002}. In the 
-solar neighbourhood,~\citet{Feuillet2018} demonstrate that the most metal-rich 
-stars tend to be significantly older than solar metallicity stars. Using the 
-\citet{Weinberg2017} analytic models of one-zone chemical evolution, they argue 
-that this is the result of old stars born at small~$R_\text{gal}$ where the 
-equilibrium abundance is high. Only the old stars are able to migrate to 
-the solar neighbourhood due to the time required for such a change in their 
-orbital radius. 
-\par 
-The results of our constant SFH model illustrated in Fig. 
-\ref{fig:age_oh_static} extend our understanding of this effect. In both 
-regions plotted, the youngest stars form with a composition inherited from the 
-local ISM, which in this model, is reflective of the late-time equilibrium 
-abundance. At a given age, only stars born in a well-defined region of the 
-Galaxy will have had adequate time to migrate to a given present-day radius. 
-Since a range of~$R_\text{gal}$ maps directly to a range of metallicity once 
-the ISM is arbitrarily close to the equilibrium abundance in our model, this 
-necessitates a maximum width of the [O/H] distribution at fixed age. With 
-increasing age, the [O/H] distribution then gets wider because any given 
-present-day radius samples stars formed at a wider range of~$R_\text{gal}$. 
-In Fig.~\ref{fig:age_oh_static}, we indeed see this effect, with the 
-colour-coding of the background points making it clear that stellar migration 
-is the culprit. In the outer Galaxy, migration has a particularly interesting 
-effect in that it only adds old stars above the equilibrium metallicity; in 
-the~$R_\text{gal}$ = 11 - 13 kpc region, our model as a consequence predicts 
-an AMR where the population-averaged trend where [O/H] is nearly monotonically 
-increasing with age. This is entirely backwards from what is expected from 
-one-zone models of GCE~\citep[e.g.][]{Andrews2017, Weinberg2017, Johnson2020}.
-
-% fig 16 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.45]{amr_solar_annulus.pdf} 
-\caption{The age-[O/H] (top) and age-[Fe/H] (bottom) relations for the solar 
-annulus (i.e.~$R_\text{gal}$ = 7 - 9 kpc,~$\left|z\right|\leq$~0.5 kpc) as 
-predicted by our inside-out SFH. Red triangles, black squares, error bars, and 
-background points are as in Fig.~\ref{fig:age_alpha}, but with our model 
-predicted quantified in bins of~$\Delta$[O/H] =~$\Delta$[Fe/H] = 0.05. For 
-comparison, we plot the~\citet{Feuillet2018} measurements in a dark red line, 
-omitting the associated uncertainties for visual clarity. } 
-\label{fig:amr_solar_annulus} 
-\end{figure}
-
-We continue our assessment of the model-predicted AMR by illustrating in Fig. 
-\ref{fig:amr_solar_annulus} the age-[O/H] (top) and age-[Fe/H] (bottom) 
-relations predicted for the solar annulus (i.e.~$R_\text{gal}$~= 7 - 9 kpc and 
-$\left|z\right|\leq$~0.5 kpc). The red triangles, black squares, coloured 
-points, and error bars are as in previous figures in~\S 
-\ref{sec:obs_comp:age_alpha}. For reference, we add the solid dark red line, 
-which denotes the AMR measured by~\citet{Feuillet2018}. Although our model 
-shows decent agreement with the~\citet{Feuillet2019} measurements in the solar 
-annulus,~\citet{Feuillet2018} report ages for solar metallicity stars which 
-are considerably younger ($\sim$1 - 2 Gyr as opposed to~$\sim$3 - 4 Gyr). 
-The~\citet{Feuillet2018} data would suggest our inside-out model requires an 
-enhancement in the recent SFR to increase the frequency of young, solar 
-metallicity stars. Although our late-burst and outer-burst models include 
-such effects, motivated by recent observations suggesting this exact 
-evolutionary history~\citep{Mor2019, Isern2019}, the differences between the 
-\citet{Feuillet2018} and~\citet{Feuillet2019} measurements are interesting in 
-and of themselves.
-
-% fig 17 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.35]{amr_insideout_vs_lateburst_fe.pdf} 
-\caption{The age-[Fe/H] relation predicted by our inside-out (top) and 
-late-burst (bottom) SFHs for~$R_\text{gal}$ = 5 - 7 kpc (left), 7 - 9 kpc 
-(left middle), 9 - 11 kpc (right middle), and 11 - 13 kpc (right). Each panel 
-shows only the~$\left|z\right|\leq$~0.5 kpc population. Red triangles, black 
-squares, error bars, and coloured points are as in Fig.~\ref{fig:age_alpha} for 
-the corresponding Galactic region, but with our model prediction quantified in 
-bins of~$\Delta$[Fe/H] = 0.05. } 
-\label{fig:amr_insideout_vs_lateburst_fe} 
-\end{figure*}
-
-Motivated by this, we compare the predictions of the inside-out and late-burst 
-SFH models to the~\citet{Feuillet2019} age-[Fe/H] relation in Fig. 
-\ref{fig:amr_insideout_vs_lateburst_fe}. We retain the same plotting scheme 
-used throughout this section and~\S~\ref{sec:obs_comp:age_alpha}, illustrating 
-the inside-out model in the top row and the late-burst model in the bottom row. 
-Each column corresponds to a specific range in~$R_\text{gal}$, denoted at the 
-top of the figure. Beyond the solar annulus, we note that our inside-out model 
-has a number of short-comings in comparison to the~\citet{Feuillet2019} 
-measurements. At~$R_\text{gal}$ = 5 - 7 kpc, it overpredicts the characteristic 
-ages of [Fe/H]~$\approx$~-0.3 - 0 stars. At~$R_\text{gal}$ = 9 - 11 and 11 - 13 
-kpc, it mildly overpredicts ages at most abundances, and fails to reproduce the 
-trend seen in the observed sample. The same can be said about the 
-$R_\text{gal}$~=5 - 7 kpc region, and although the overall agreement is 
-generally good there, one could reasonably argue this for the solar annulus as 
-well. 
-\par 
-The late-burst model improves upon these shortcomings of the inside-out model 
-considerably. At~$R_\text{gal}$ = 5 - 7 kpc, the overpredicted ages at solar 
-and mildly sub-solar [Fe/H] is no longer present; this is also true at 
-$R_\text{gal}$~= 9 - 11 and 11 - 13 kpc. Furthermore, the trend is much better 
-reproduced at all radii in the late-burst than the inside-out model. The only 
-different between the late-burst and inside-out model being the recent 
-enhancement in the SFR, this is what drives the differences in model 
-predictions. To fuel the starburst as we have parameterized it,~\texttt{VICE} 
-calculates that there must be substantial gas accretion (see the infall rate 
-$\dot{\Sigma}_\text{in}$ as a function of radius and time in Fig. 
-\ref{fig:evol}). In our models, we assume accretion to always be of zero 
-metallicity gas. As a result, the model predicts dilution of the ISM Fe 
-abundance during the starburst; this can be seen by the trend of the coloured 
-points in Fig.~\ref{fig:amr_insideout_vs_lateburst_fe} to lower [Fe/H] at ages 
-of~$\sim$2 - 3 Gyr. At this time, the star formation rate is elevated by 
-construction. The net effect is to increase the frequency of~$\sim$2 - 3 Gyr 
-old stars with near- and sub-solar abundances globally, which lowers the 
-characteristic ages of stars at these metallicities relative to the inside-out 
-model. Using the~\citet{Feuillet2019} measurements as the observational 
-benchmark, we favor the late-burst model here. 
-\par 
-Although there appears to be a vertical offset between the observed result and 
-the model prediction at~$R_\text{gal}$ = 9 - 11 and 11 - 13 kpc, this is still 
-an improvement upon the inside-out model. It's possible that this points to a 
-need for higher yields of Fe than we've adopted here, though it's unclear if 
-this would negatively affect the agreement at~$R_\text{gal}$~= 5 - 7 and 7 - 9 
-kpc. It's possible that our parameterization of the mass-loading factor~$\eta$ 
-scales too strongly with~$R_\text{gal}$ in the outer Galaxy (see discussion in 
-\S~\ref{sec:methods:yields}). Alternatively, outflows in nature may be more 
-efficient at removing some elements from the ISM than others; this could impact 
-the overall normalization of the AMR at different radii. Our models in the 
-present paper assume that outflows always proceed exactly at the metallicity of 
-the ISM, but some authors argue that outflows can have a different metallicity 
-- usually a higher one - due to containing in some part the metal-rich 
-supernova ejecta that was added directly to the outflow by the explosions 
-(observationally:~\citealp*{Chisholm2018}; in simulations: 
-\citealp{Christensen2018}). 
-\par 
-We also note that the late-burst model predicts particularly young 
-characteristic ages for the most metal-rich bins at~$R_\text{gal}$ = 5 - 7 kpc. 
-This is purely a consequence of our choice to use the mass-weighted median as 
-the population-averaged age measurement at fixed abundance. In this case, our 
-model is simply reporting the 50th percentile of an age-distribution 
-which is noticeably bimodal; as a result, whether or not the characteristic 
-ages we report there are <1 Gyr or in better agreement with the 
-\citet{Feuillet2019} measurements strongly depends on how we've parameterized 
-the recent starburst as a function of both time and radius. Here we've made the 
-simplest assumption of letting have the same time-dependence at all radii, 
-which was not necessarily the case. 
-\par 
-Although we demonstrate here that the late-burst model describes the age-[Fe/H] 
-relation reported by~\citet{Feuillet2019} better than the inside-out model, we 
-found the exact opposite with regard to the age-[$\alpha$/Fe] relation with 
-the same obesrvational sample in~\S~\ref{sec:obs_comp:age_alpha}. It's unlikely 
-this discrepancy can be mitigated using any model which exhibits a recent 
-starburst as parameterized here; as we demonstrated in~\S 
-\ref{sec:obs_comp:age_alpha}, such models predict a global increase in 
-[$\alpha$/Fe] due to the perturbed ratio of CCSN and SN Ia rates 
-\citep{Johnson2020}, a feature which simply isn't seen in the 
-\citet{Feuillet2019} measurements. It's possible that the Milky Way experienced 
-dilution with no ensuing starburst - this would be the case if the majority of 
-the accreted gas was warm, neutral and ionized gas which simply hasn't yet been 
-made available for star formation. Such a scenario would exhibit some of the 
-predictions of the late-burst model, but without the increase in [O/Fe] at late 
-times, potentially allowing it to simultaneously explain the age-[$\alpha$/Fe] 
-relation and AMR as they are observed. However, these models would be at odds 
-with the findings of~\citet{Mor2019} and~\citet{Isern2019}. 
-\par 
-We remark that we find similar results for the age-[O/H] relation; furthermore, 
-as in~\S~\ref{sec:obs_comp:age_alpha} for the age-[$\alpha$/Fe] relation, we 
-also find for the age-[Fe/H] and age-[O/H] relations that our models tend to 
-overpredict ages with increasing~$\left|z\right|$. Lastly, we caution future 
-studies against basing the likelihood of a chemical evolution model on data 
-for the solar annulus alone. In Fig.~\ref{fig:amr_solar_annulus}, we 
-noted that there was decent agreement between the inside-out SFH model and 
-the~\citet{Feuillet2019} measurements of the age-[O/H] and age-[Fe/H] 
-relations in the solar annulus, but upon extending the comparison to other 
-Galactic regions in Fig.~\ref{fig:amr_insideout_vs_lateburst_fe}, a number of 
-shortcomings revealed themselves. Although to some extent this is made possible 
-only recently with observational capabilities now allowing statistical 
-measurements of these correlations for stars at greater distances from the sun, 
-had we stopped there, we would have missed this interesting and peculiar 
-result.
-
-\section{Discussion \& Conclusions} 
-\label{sec:conclusions} 
-In this paper, we have modeled the Milky Way as a series of concentric annuli 
-with a~$\Delta R_\text{gal}$~= 100 pc width, describing each annulus as a 
-conventional one-zone chemical evolution model and allowing the exchange of 
-stellar populations between zones to include the impact of stellar migration in 
-the model Galaxy. Though there have been a handful of studies which employ a 
-similar methodology~\citep{Schoenrich2009, Nidever2015, Sharma2020}, ours and 
-the~\citet{Minchev2013, Minchev2014, Minchev2017} model are the only ones which 
-make use of a hydrodynamical simulation to describe radial mixing, for which we 
-make use of the~\texttt{h277} zoom-in simulation~\citep{Christensen2012, 
-Zolotov2012, Loebman2012, Loebman2014, Brooks2014}. This yields a model for 
-migration which does not have any free parameters (see discussion in~\S 
-\ref{sec:methods:h277}). 
-\par 
-Our model predicts masses and abundances for simple stellar populations, a 
-given number of which form at each timestep. Each stellar 
-population is then assigned a star particle from~\texttt{h277} which was born 
-at a similar radius and time to act as an~\textit{analog}. The stellar 
-population in our model then assumes the change in radius~$\Delta R_\text{gal}$ 
-of the analog at face value, and is assumed to reside at the same present day 
-height above/below the disc midplane~$\left|z\right|$. We then construct four 
-models describing the time-dependence with which stellar populations move to 
-their present-day radii, taking one in which radius changes with a 
-$\sqrt{\text{age}}$-dependence in the fiducial model based on~\citet[][see 
-Fig.~\ref{fig:migration_schema} and discussion in~\S 
-\ref{sec:methods:migration}]{Frankel2018, Frankel2020}. 
-\par 
-We assume SN yields and a SN Ia delay-time distribution based on 
-a combination of theoretical and empirical constraints. The main free 
-parameters are the star formation law parameterizing the SFE timescale 
-$\tau_\star$ (see discussion in~\S~\ref{sec:methods:sfe}), the mass-loading 
-factor~$\eta(R_\text{gal})$~describing the strength of outflows (assumed to be 
-time-independent; see discussion in~\S~\ref{sec:methods:yields}), and the SFH. 
-The first we choose from the observed~$\dot{\Sigma}_\star - \Sigma_\text{g}$ 
-relation in local spirals~\citep{Bigiel2010, Leroy2013, Krumholz2018}. The 
-second is chosen to reproduce the metallicity gradient as observed 
-\citep{Daflon2009, Frinchaboy2013, Hayden2014, Weinberg2019}. Our fiducial 
-model then has an inside-out SFH with e-folding timescales calibrated to the 
-\citet{Sanchez2020} data (see discussion in~\S~\ref{sec:methods:sfhs}). 
-Motivated by the results of~\citet{Mor2019} and~\citet{Isern2019} suggesting 
-such an evolutionary history, we construct models which exhibit a recent burst 
-in star formation on top of the base-line model, as well as a constant SFH 
-model of purely theoretical interest. 
-\par 
-We find that when stellar migration proceeds in a manner in which a star's 
-orbital radius changes continuously with time, the SN Ia rate as a function of 
-both radius and time exhibits significant variability. The characteristic delay 
-time of a single SN Ia event is~$\sim$1 Gyr~\citep{Maoz2012, Maoz2017}, and 
-stars are migrating a significant distance in the radial direction on similar 
-timescales in our models. The result is a SN Ia rate which, at fixed radius, 
-tends to follow that which is expected from the SFH when averaged with time, 
-but whose instantaneous value may be considerably larger or smaller. Our model 
-predicts the amplitude of this variability to grow with increasing radius due 
-to sampling noise and the inverse dependence of the stellar surface density on 
-$R_\text{gal}$. We demonstrate that this is a mechamism with which truly young, 
-super-solar [$\alpha$/Fe] stars can form. When the SN Ia rate increases or 
-decreases, the Fe abundance in the ISM increases or 
-decreases accordingly; this in turn affects the gas-phase [$\alpha$/Fe] ratio, 
-and the stars which form at these times inherit these compositions. Of the 
-young stars, those with the highest [$\alpha$/Fe] form at large~$R_\text{gal}$ 
-($\gtrsim$~12 kpc) due to the radial dependence of the amplitude; a subsample 
-of these stars can then migrate to the solar annulus. 
-\par 
-To our knowledge, this mechanism lends the first theoretical explanation of 
-truly young $\alpha$-rich stars in the solar neighbourhood, revealed recently 
-by the observations of the APOGEE survey~\citep{Martig2016, Feuillet2018, 
-Feuillet2019, SilvaAguirre2018}.~\citet{SilvaAguirre2018} find that 
-these stars have kinematics consistent with the rest of the high-$\alpha$ 
-population, and postulate based on this that these stars are the consequence 
-of stellar mergers or mass transfer events, making truly old stars simply 
-appear younger. In a sample of 51 young~$\alpha$-rich red giants, 
-\citet{Hekker2019} demonstrate using cabon-to-nitrogen ratios that a portion of 
-these stars are indeed old, but that these effects cannot account for the 
-entire population. We argue based on our results that the truly young ones 
-formed at large~$R_\text{gal}$~at a time when the ISM was intrinsically 
-$\alpha$-rich due simply to a deficit in SN Ia events caused by a net loss of 
-white dwarf progenitors to stellar migration. We remark that our model would 
-sugest that these stars have super-solar [$\alpha$/Fe] not because they are 
-$\alpha$-rich, but rather that they are Fe-poor. 
-\par 
-We find that our model adequately reproduces the variations in MDFs with 
-Galactocentric radius in the disc~\citep{Hayden2015}. Although there is a 
-potential for improved agreement in the~$R_\text{gal}$~= 3 - 5 kpc bin, the 
-model nonetheless performs well. With increasing~$\left|z\right|$, the 
-prediction breaks down somewhat. Where the observational data show a 
-convergence of the MDFs at all radii to a skew-positive distribution with 
-mode([O/H])~$\approx$~mode([Fe/H])~$\approx$~-0.5, our model predicts the mode 
-abundance in the inner Galaxy to decrease slightly, though not to the same 
-extent as in the observations, while the distributions at larger~$R_\text{gal}$ 
-are less affected (see Figs.~\ref{fig:mdf_3panel_fe} and~\ref{fig:mdf_3panel_o} 
-and discussion in~\S~\ref{sec:obs_comp:mdfs}). While the model accounts for a 
-portion of these effects, it cannot explain the entire~$z$-dependence of the 
-MDF shape. 
-\par 
-We demonstrate the dependence of the relative frequency of high-$\alpha$ and 
-low-$\alpha$ sequence stars on Galactic position (see, e.g., Fig. 4 of 
-\citealp{Hayden2015}) is at least in part a consequence of stellar migration. 
-In our fiducial inside-out SFH model, low [Fe/H], high [$\alpha$/Fe] stars 
-are the dominant population at small~$R_\text{gal}$~and high~$\left|z\right|$; 
-conversely, low [$\alpha$/Fe] stars are most common at large~$R_\text{gal}$ 
-and low~$\left|z\right|$. We clarify that this is not an explanation for the 
-\textit{origin} of the two sequences - only the spatial dependence thereof. 
-In fact, our model is unable to account for the presence of the infamous 
-[$\alpha$/Fe] dichotomy in any of the variants we've explored. While it is able 
-to reproduce the broad nature of the [O/Fe] distributions at fixed [Fe/H] and 
-may show a convincing two-peaked profile in a specific Galactic region, it 
-fails to do so for the entire Galaxy at all metallicities; the principle 
-failure is an overpredicted frequency of intermediate [$\alpha$/Fe] stars. This 
-is in contrast to the findings of~\citet{Sharma2020}, who claim to reproduce 
-the bimodality in a model assuming an inside-out SFH with stellar migration. 
-However, they do not demonstrate that the enrichment history of their model 
-follows self-consistently from their assumed SFH. We therefore argue that 
-an inside-out SFH is not conducive to forming the abundance distributions 
-observed in the Milky Way. Though we don't investigate such evolutionary 
-pathways in the present paper, our models fail in such a manner that suggests 
-the agreement can best be improved by the three-phase SFH of the two-infall 
-model~\citep{Chiappini1997, Chiappini2001, Romano2010, Grisoni2017, 
-Noguchi2018, Palla2020, Spitoni2016, Spitoni2018, Spitoni2019a, Spitoni2020, 
-Spitoni2021}. We reserve an investigation into more sophisticated forms of the 
-Galactic SFH for future work. 
-\par 
-We find that the age-[O/Fe] relation as reported by~\citet{Feuillet2019} is 
-well-characterized by our inside-out SFH. In the case of our recent 
-starburst models motivated by~\citet{Mor2019} and~\citet{Isern2019}, the 
-elevation of the SFR necessitates an increase in [$\alpha$/Fe] for young 
-stars owing to the increased rate of CCSNe before the onset of SN Ia associated 
-with the starburst~\citep{Johnson2020}, introducing a trend which simply isn't 
-seen in the observations. This suggests that recent studies finding an 
-elevation in the 
-Galactic SFR~$\sim$2 Gyr ago are at odds with chemical evolution models, which 
-based on the monotonic nature of the observed AMR would put constraints on the 
-amount of variability out to lookback times of~$\sim$8 Gyr. Lastly, we find 
-that our model predicts the intrinsic scatter in the age-[$\alpha$/Fe] relation 
-to increase with~$R_\text{gal}$; this traces back to the variability in the SN 
-Ia rates having a higher amplitude in the outer Galaxy, which produces an 
-in-situ population with a larger dynamic range in [O/Fe]. 
-\par 
-We find that the AMR (both age-[O/H] and age-[Fe/H]) in the solar annulus as 
-measured by~\citet{Feuillet2019} is well-described by our inside-out SFH. 
-However, when this comparison is extended to other Galactic regions, the 
-inside-out model overpredicts ages in multiple regions and fails to reproduce 
-the population-averaged trend throughout the disc. We demonstrate that our 
-late-burst model can account for these discrepancies, suggesting that the 
-observed AMR favors a model with a recent enhancement in the Galactic SFR. 
-Somewhat confusingly, the impact of the late-burst model is such that it is 
-convincingly rejected by the age-[O/Fe] relation but convincingly favored by 
-the age-[O/H] and age-[Fe/H] relations. 
-\par 
-We thus conclude that no single model in the present paper can explain all of 
-the observables of interest here. This suggests that 
-conventional assumptions about the evolution of the Milky Way, such as an 
-inside-out SFH with stellar migration, are not sufficiently accurate to 
-understand the enrichment history of the Milky Way in detail. This is an 
-indication that at present there is more astrophysical information in already 
-collected observations than the most recent GCE models can explain. It's likely 
-our models are missing at least one key component with a significant impact on 
-the predicted abundances. 
-\par 
-Lastly, we remark on the low number of multi-zone chemical evolution models in 
-the literature, some with and some without migration. In this paper, we present 
-only a handful of models whose predictions can be calculated with a combined 
-CPU-time comparable to a single working day. These models make straight-forward 
-predictions which can easily be compared to publicly-available observed data. 
-Though they are extremely useful in many respects, these medium resolution, 
-medium computational expense techniques can test assumptions about the 
-evolutionary history of the Milky Way with more control over the parameters and 
-much less computational expense than the higher overhead hydrodynamical 
-simulations; our models here constitute an example of a combination of the two. 
-\par 
-\texttt{VICE} is publicly available and open-source;\footnote{
-	Install (PyPI): \url{https://pypi.org/project/vice} \\ 
-	Documentation: \url{https://vice-astro.readthedocs.io} \\ 
-	Source Code: \url{https://github.com/giganano/VICE.git} 
-} it can be installed in a~\texttt{Unix} terminal via~\texttt{pip install vice}. 
-\texttt{Python} code which runs the simulations presented in this paper is 
-included as supplementary material in the~\texttt{GitHub} repository; our 
-models can be ran directly from a terminal without modifying the source code, 
-and are capable of predicting abundances for~$\sim$2 million stellar 
-populations in~$\sim$2.5 CPU-hours running on a single core on personal 
-computers.
-
-\section{Acknowledgements} 
-\label{sec:acknowledgements} 
-We acknowledge valuable discussion with, in no particular order, Emily 
-Griffith, Jennifer Johnson, Todd Thompson, Jiayi Sun, Amy Sardone, Adam Leroy, 
-Grace Olivier, the Ohio State Astronomy Gas, Galaxies, and Feedback group, and 
-various participants of the SDSS Gotham 2020 virtual collaboration meeting and 
-the virtual 236th meeting of the American Astronomical Society. This work was 
-supported in part by National Science Foundation grant AST-1909841. D.H.W. 
-is grateful for the hospitality of the Institute for Advanced Study and the 
-support of the W.M. Keck Foundation. 
-\par 
-In this paper we have made use of data from SDSS-IV APOGEE-2 DR16. 
-Funding for the Sloan Digital Sky 
-Survey IV has been provided by the 
-Alfred P. Sloan Foundation, the U.S. 
-Department of Energy Office of 
-Science, and the Participating 
-Institutions. 
-\par 
-SDSS-IV acknowledges support and 
-resources from the Center for High 
-Performance Computing  at the 
-University of Utah. The SDSS 
-website is~\url{www.sdss.org}.
-\par 
-SDSS-IV is managed by the 
-Astrophysical Research Consortium 
-for the Participating Institutions 
-of the SDSS Collaboration including 
-the Brazilian Participation Group, 
-the Carnegie Institution for Science, 
-Carnegie Mellon University, Center for 
-Astrophysics | Harvard \& 
-Smithsonian, the Chilean Participation 
-Group, the French Participation Group, 
-Instituto de Astrof\'isica de 
-Canarias, The Johns Hopkins 
-University, Kavli Institute for the 
-Physics and Mathematics of the 
-Universe (IPMU) / University of 
-Tokyo, the Korean Participation Group, 
-Lawrence Berkeley National Laboratory, 
-Leibniz Institut f\"ur Astrophysik 
-Potsdam (AIP),  Max-Planck-Institut 
-f\"ur Astronomie (MPIA Heidelberg), 
-Max-Planck-Institut f\"ur 
-Astrophysik (MPA Garching), 
-Max-Planck-Institut f\"ur 
-Extraterrestrische Physik (MPE), 
-National Astronomical Observatories of 
-China, New Mexico State University, 
-New York University, University of 
-Notre Dame, Observat\'ario 
-Nacional / MCTI, The Ohio State 
-University, Pennsylvania State 
-University, Shanghai 
-Astronomical Observatory, United 
-Kingdom Participation Group, 
-Universidad Nacional Aut\'onoma 
-de M\'exico, University of Arizona, 
-University of Colorado Boulder, 
-University of Oxford, University of 
-Portsmouth, University of Utah, 
-University of Virginia, University 
-of Washington, University of 
-Wisconsin, Vanderbilt University, 
-and Yale University.
-
-\textit{Software}: Matplotlib~\citep{Matplotlib}; Astropy~\citep{Astropy2013, 
-Astropy2018}; NumPy~\citep{NumPy}.
-
-\section{Data Availability} 
-\label{sec:data_availability} 
-\texttt{VICE} is open-source software, and the code which computes abundances 
-for our models is publicly available as well. In the GitHub repository, we 
-provide detailed instructions on how to run our models and variations thereof. 
-All observational data appearing in this paper is publicly available, and is 
-also included with the source code for our models and figures.
-
-\begin{appendices}
 
@@
 \label{sec:normalize_sfh}
+
 In this appendix, we derive a prescription for calculating the prefactors of an 
@@
 description of the time-dependence of the SFH in each annulus, denoted 
-$f(t|R_\text{gal})$, and a unitless description denoting the radial dependence 
-of the stellar surface density~$g(R_\text{gal})$. By additionally selecting a 
+$f(t|R_\text{gal})$, and a unitless description of the radial dependence 
+of the stellar surface density, denoted~$g(R_\text{gal})$. 
+By additionally selecting a 
 total stellar mass of the present day model Galaxy, the solution to the 
@@
 that stellar migration does not significantly impact the form of 
-$g(R_\text{gal})$, an assumption we demonstrate to be accurate in~\S 
-\ref{sec:methods:surface_density_gradient}. 
+$g(R_\text{gal})$, an assumption we demonstrate to be accurate 
+in~\S~\ref{sec:methods:surface_density_gradient}. 
 \par 
@@
 \begin{equation} 
-\Sigma_\star(R_\text{gal}) = \Sigma_\star(R_\text{gal} = 0) g(R_\text{gal}) 
+\Sigma_\star(R_\text{gal}) = \Sigma_\star(R_\text{gal} = 0) g(R_\text{gal}). 
 \label{eq:sigma_terms_of_g}  
@@
 where~$(1 - r) \approx 0.6$~is an adequate approximation for a 
-\citetalias{Kroupa2001} IMF~\citep[][see discussion in their~\S 
-2.2]{Weinberg2017}. This expression relates the two unkowns introduced by 
+\citetalias{Kroupa2001} IMF~\citep[][see discussion in 
+their~\S~2.2]{Weinberg2017}. 
+This expression relates the two unkowns introduced by 
 equations~\refp{eq:sfh_terms_of_f} and~\refp{eq:sigma_terms_of_g}. We continue 
@@
 \Sigma_\star(R_\text{gal} = 0) &= M_\star^\text{MW} \left[\int_0^R 
-g(R_\text{gal}) 2\pi R_\text{gal}dR_\text{gal}\right]^{-1} 
+g(R_\text{gal}) 2\pi R_\text{gal}dR_\text{gal}\right]^{-1}. 
 \label{eq:intermediate_2} 
@@
 &A = M_\star^\text{MW}\left[(1 - r) \int_0^R g(R_\text{gal})2\pi R_\text{gal} 
-dR_\text{gal} \int_0^T f(t|R_\text{gal})dt\right]^{-1} 
+dR_\text{gal} \int_0^T f(t|R_\text{gal})dt\right]^{-1}, 
 \end{align}\end{subequations} 
 where the upper limits should be the maximum radius of star formation and the 
-end time of the simulation (15.5 kpc and 12.2 Gyr in this paper). This result 
+end time of the simulation (15.5 kpc and 13.2 Gyr in this paper). This result 
 makes intuitive sense, simply stating that the required normalization of 
 $f(t|R_\text{gal})$~is specified by two things: the total stellar mass of the 
-Galaxy and how steep the stellar density falls with increasing radius. As long 
-as the assumption that stellar migration does not significantly alter the form 
-of~$g(R_\text{gal})$~is not violated, this procedure can be used to calculate 
-prefactors for future models of disc galaxies.
+Galaxy and how steeply the stellar density falls with increasing radius. As 
+long as the assumption that stellar migration does not significantly alter the 
+form of~$g(R_\text{gal})$~is not violated, this procedure can be used to 
+calculate prefactors for future models of disc galaxies.
 
-\end{appendices}
-
-\bibliographystyle{mnras} 
-\bibliography{draft1}
-
-\label{lastpage} 
 \end{document}

### 2021-08-04 chemev/MWbimodality/paper/draft3/acknowledgements.tex
migration paper referee response

--- 2021-08-04 chemev/MWbimodality/paper/draft2/acknowledgements.tex
@@
 
+{\color{red} 
+We are grateful to Ted Mackereth for valuable comments which helped improve 
+this manuscript. 
+} 
 We acknowledge valuable discussion with Jennifer Johnson, Adam Leroy, Grace 
@@
 F.V. acknowledges the support of a Fellowship from the Center for Cosmology and 
-AstroParticle Physics at the Ohio State University. 
+AstroParticle Physics at The Ohio State University. 
 \par 

### 2021-08-04 chemev/MWbimodality/paper/draft3/comparison_observations.tex
migration paper referee response

--- 2021-08-04 chemev/MWbimodality/paper/draft2/comparison_observations.tex
@@
 
-% fig 7 
+% fig 8
 \begin{figure*} 
 \centering 
-\includegraphics[scale = 0.28]{ofe_feh_densitymap.pdf} 
-\caption{[O/Fe]-[Fe/H] diagrams for 15 Galactic regions spanning five bins in 
-$R_\text{gal}$ and three in~$\left|z\right|$. Each region has its own panel, 
-with radial bins shown in columns denoted at the top, and with bins in 
-$\left|z\right|$ shown in rows denoted in text in the middle column. For each 
-region, we plot~$N$~= 10,000 points sampled from our simulated stellar 
-populations predicted by our fiducial model, where the probability of 
-sampling is proportional to the present-day mass of each stellar population. 
-In all panels, points are colour-coded according to the Galactocentric radius 
-of birth of the stellar population. For reference, we plot in a solid black 
-line in all panels the gas-phase [O/Fe]-[Fe/H] track predicted by the same 
-SFH in the~$R_\text{gal}$ = 8 kpc annulus, but with the post-processing 
-migration model; this curve is the same in all panels. } 
-\label{fig:ofe_feh_diagram} 
+\includegraphics[scale = 0.42]{tracks.pdf} 
+\caption{\textbf{Left}: Gas phase evolutionary tracks in the [O/Fe]-[Fe/H] 
+plane for our inside-out SFH with either post-processing (dotted lines) or 
+diffusion (solid lines) migration models. We plot tracks for seven of our 
+$\delta\rgal$ = 100 pc rings, 
+colour-coded according to their Galactocentric radius and denoted by the 
+legend in the lower-left. We mark simulation times of 2, 4, 6, 8, 10, and 13.2 
+Gyr in X's for the diffusion model and points for the post-processing model. 
+\textbf{Right}: As a function of simulation time, a proxy for the SN Ia rate 
+using the total time-derivative of the Fe mass in a given annulus, calculated 
+by subtracting the contribution from recycling and CCSN enrichment and adding 
+back that lost to star formation and outflows. We show these rates for the 
+same rings as in the left-hand panel, multiplying them by various prefactors 
+to improve clarity. } 
+\label{fig:tracks} 
+\end{figure*}
+
+% fig 9 
+\begin{figure*} 
+\centering 
+\includegraphics[scale = 0.32]{metallicity_gradient.pdf} 
+\caption{Radial abundance gradients in [O/H] (top, red), [Fe/H] (top, blue), 
+and [O/Fe] (bottom) for our four SFHs with diffusion migration - constant (far 
+left), inside-out (left-middle), late-burst (right-middle), and outer-burst 
+(far right). We plot the gas-phase abundance at the present day as a function 
+of Galactocentric radius in solid lines. Points denote the median of the stellar 
+MDF of the 100-pc width ring at a given radius, with shaded regions marking 
+the 16th and 84th percentiles thereof. Black lines in the top panels denote our 
+target [$\alpha$/H] gradient of mode([$\alpha$/H]) = +0.3 at~$R_\text{gal}$~= 
+4 kpc with a slope of -0.08 kpc$^{-1}$. } 
+\label{fig:metallicity_gradient} 
 \end{figure*}
@@
 of some sub-populations in Fig.~\ref{fig:ofe_feh_diagram}. 
-
-% fig 8
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.42]{tracks.pdf} 
-\caption{\textbf{Left}: Gas phase evolutionary tracks in the [O/Fe]-[Fe/H] 
-plane for our inside-out SFH with either post-processing (dotted lines) or 
-diffusion (solid lines) migration models. We plot tracks for seven of our 
-$\Delta\rgal$ = 100 pc rings, 
-colour-coded according to their Galactocentric radius and denoted by the 
-legend in the lower-left. We mark simulation times of 2, 4, 6, 8, 10, and 13.2 
-Gyr in X's for the diffusion model and points for the post-processing model. 
-\textbf{Right}: As a function of simulation time, a proxy for the SN Ia rate 
-using the total time-derivative of the Fe mass in a given annulus, calculated 
-by subtracting the contribution from recycling and CCSN enrichment and adding 
-back that lost to star formation and outflows. We show these rates for the 
-same rings as in the left-hand panel, multiplying them by various prefactors 
-to improve clarity. } 
-\label{fig:tracks} 
-\end{figure*}
-
-% fig 9 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.32]{metallicity_gradient.pdf} 
-\caption{Radial abundance gradients in [O/H] (top, red), [Fe/H] (top, blue), 
-and [O/Fe] (bottom) for our four SFHs with diffusion migration - constant (far 
-left), inside-out (left-middle), late-burst (right-middle), and outer-burst 
-(far right). We plot the gas-phase abundance at the present day as a function 
-of Galactocentric radius in solid lines. Points denote the median of the stellar 
-MDF of the 100-pc width ring at a given radius, with shaded regions marking 
-the 16th and 84th percentiles thereof. Black lines in the top panels denote our 
-target [$\alpha$/H] gradient of mode([$\alpha$/H]) = +0.3 at~$R_\text{gal}$~= 
-4 kpc with a slope of -0.08 kpc$^{-1}$. } 
-\label{fig:metallicity_gradient} 
-\end{figure*}
-
+\par 
 Because we are analyzing a single hydrodynamic simulation, we cannot say 
@@
 qualitative agreement with observations (see discussion in, e.g., 
-\citealp{Duong2019, Griffith2021}).
+\citealp{Duong2019, Griffith2021a}).
 
@@
 \label{sec:obs_comp:mdfs}
+
+% fig 10 
+\begin{figure} 
+\centering 
+\includegraphics[scale = 0.34]{mdf_3panel_fe.pdf} 
+\caption{Metallicity distribution functions (MDFs) in [Fe/H] predicted by our 
+fiducial, inside-out model (left) and as observed in APOGEE DR16 (right), for 
+stars and simulated stellar populations with present-day~$\left|z\right|$~= 0 - 
+0.5 kpc (bottom), 0.5 - 1 kpc (middle), and 1 - 2 kpc (top). MDFs are shown in 
+bins of Galactocentric radius: 3 - 5 kpc (black), 5 - 7 kpc (red), 7 - 9 kpc 
+(yellow), 9 - 11 kpc (green), 11 - 13 kpc (blue), and 13 - 15 kpc (purple). 
+The points near the top of the bottom panels denote what the mode abundance 
+would be if it followed out target gradient of [Fe/H] = +0.3 at~$R_\text{gal}$ 
+= 4 kpc with a slope of -0.08 kpc$^{-1}$ exactly, assuming the inner radius of 
+each bin (i.e. there is no point plotted for 15 kpc). All distributions are 
+smoothed with a box-car width of [Fe/H]~$\pm$~0.1 for clarity. } 
+\label{fig:mdf_3panel_fe} 
+\end{figure}
+
+% fig 11 
+\begin{figure} 
+\centering 
+\includegraphics[scale = 0.34]{mdf_3panel_o.pdf} 
+\caption{The same as Fig.~\ref{fig:mdf_3panel_fe}, but for [O/H]. } 
+\label{fig:mdf_3panel_o} 
+\end{figure}
 
@@
 small~\rgal. 
+{\color{red} 
+It's also possible that the differences at 3 - 5 kpc are due to stars 
+associated with the Milky Way's strong bar, which~\citet{Bovy2019} demonstrate 
+to be low metallicity (see their Fig. 5). 
+With only a weak and transient bar in~\hsim, this is a dynamical effect not 
+included in our models (see discussion in~\S~\ref{sec:methods:h277}). 
+% It's also possible that the differences at 3 - 5 kpc are due to low metallicity 
+% bar stars in the data~\citep[e.g. those observed by][]{Bovy2019}, a dynamical 
+% effect not present in~\hsim~(see discussion in~\S~\ref{sec:methods:h277}). 
+}
 Alternatively, the flattening of the observed gradient could be a consequence 
@@
 [Fe/H]~$\approx$~+0.2 - 0.3. 
-
-% fig 10 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.34]{mdf_3panel_fe.pdf} 
-\caption{Metallicity distribution functions (MDFs) in [Fe/H] predicted by our 
-fiducial, inside-out model (left) and as observed in APOGEE DR16 (right), for 
-stars and simulated stellar populations with present-day~$\left|z\right|$~= 0 - 
-0.5 kpc (bottom), 0.5 - 1 kpc (middle), and 1 - 2 kpc (top). MDFs are shown in 
-bins of Galactocentric radius: 3 - 5 kpc (black), 5 - 7 kpc (red), 7 - 9 kpc 
-(yellow), 9 - 11 kpc (green), 11 - 13 kpc (blue), and 13 - 15 kpc (purple). 
-The points near the top of the bottom panels denote what the mode abundance 
-would be if it followed out target gradient of [Fe/H] = +0.3 at~$R_\text{gal}$ 
-= 4 kpc with a slope of -0.08 kpc$^{-1}$ exactly, assuming the inner radius of 
-each bin (i.e. there is no point plotted for 15 kpc). All distributions are 
-smoothed with a box-car width of [Fe/H]~$\pm$~0.1 for clarity. } 
-\label{fig:mdf_3panel_fe} 
-\end{figure}
-
-% fig 11 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.34]{mdf_3panel_o.pdf} 
-\caption{The same as Fig.~\ref{fig:mdf_3panel_fe}, but for [O/H]. } 
-\label{fig:mdf_3panel_o} 
-\end{figure}
-
+\par 
 Going up from the midplane, the observed MDFs for the four inner annuli 
@@
 disc, and here we see similar behaviour in a more fully ab initio model. 
-\citet{Bird2020} showed that the dynamics of the~\hsim~simulation leads to good 
+\citet{Bird2021} showed that the dynamics of the~\hsim~simulation leads to good 
 agreement with the observed age-velocity relation, and here we show that 
@@
 over the corresponding ranges in~\absz. 
-
+\par 
 Solid histograms in Fig.~\ref{fig:ofe_mdfs_insideout} show distributions in 
-0.4-dex bins of [O/Fe] for our fiducial inside-out model. 
+0.04-dex bins of [O/Fe] for our fiducial inside-out model. 
 For clarity we have chosen to focus our comparison on two bins of [Fe/H], one 
@@
 failure.
-\par 
+
+% fig 13 
+\begin{figure*} 
+\centering 
+\includegraphics[scale = 0.34]{age_ofe_migration_comparison.pdf} 
+\includegraphics[scale = 0.34]{age_ofe_sfh_comparison.pdf} 
+\caption{
+\textbf{Left}: A comparison of the predicted age-[O/Fe] relation for the solar 
+neighbourhood ($R_\text{gal}$ = 7 - 9 kpc and~$\left|z\right|$ = 0 - 0.5 kpc) 
+between the post-processing (upper left), diffusion (upper right), sudden 
+(lower left), and linear (lower right) migration models, assuming our 
+inside-out SFH. 
+\textbf{Right}: The same as the left-hand panels, instead comparing the impact 
+of our constant (upper left), inside-out (upper right), late-burst (lower left), 
+and outer-burst (lower right) SFHs, assuming diffusion migration. In all panels, 
+red triangles and error bars denote the observed median age and dispersion 
+thereof in bins of [O/Fe] as reported by~\citet{Feuillet2019}; here we include 
+only their bins containing at least 15 stars. Black squares denote the 
+mass-weighted median age in 0.02-dex bins in [O/Fe] predicted by our models, 
+with error bars denoting the 16th and 84th percentiles of the mass-weighted 
+age distribution in those bins. Points in the background denote each individual 
+stellar population from the model with a final position in the solar 
+neighbourhood, colour-coded according to their Galactocentric radius of birth. 
+}
+\label{fig:age_alpha} 
+\end{figure*}
+
 Beginning with the [Fe/H] = 0 - 0.2 bin, we see that the model roughly 
@@
 With its most recent major merger occurring at~$z \approx$ 3, this galaxy was 
-previously selected for investigation for its quiescent merger history 
+previously selected for investigation because of its quiescent merger history 
 \citep[e.g.][]{Zolotov2012}. N-body models for the tidal disruption of the 
@@
 Spitoni2018, Spitoni2019a, Spitoni2020, Spitoni2021}. 
+{\color{red} 
+\citet{Mackereth2018} find similar conclusions in a sample of 133 Milky 
+Way-like galaxies from the EAGLE simulation.
+} 
 These scenarios turn down the SFR while the ISM abundances pass through the 
@@
 \label{sec:obs_comp:age_alpha}
+
+% fig 14 
+\begin{figure*} 
+\centering 
+\includegraphics[scale = 0.32]{age_alpha_regions.pdf} 
+\caption{The age-[O/Fe] relation in 12 Galactic regions predicted by our 
+inside-out SFH. Bins in Galactocentric radius are shown in columns, and labeled 
+at the top. 
+Bins in the disc midplane distance~\absz~are shown in rows, noted in the 
+left-hand column. Red triangles, black squares, 
+error bars, and background points are as in Fig.~\ref{fig:age_alpha} for the 
+corresponding Galactic region. The solid black line connects the black squares 
+in the bottom, left-middle panel, and is replicated elsewhere for reference. } 
+\label{fig:age_alpha_regions} 
+\end{figure*}
+
 In this section, we assess the predicted age-[O/Fe] relations of our models, 
@@
 \par 
-
-% fig 13 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.34]{age_ofe_migration_comparison.pdf} 
-\includegraphics[scale = 0.34]{age_ofe_sfh_comparison.pdf} 
-\caption{
-\textbf{Left}: A comparison of the predicted age-[O/Fe] relation for the solar 
-neighbourhood ($R_\text{gal}$ = 7 - 9 kpc and~$\left|z\right|$ = 0 - 0.5 kpc) 
-between the post-processing (upper left), diffusion (upper right), sudden 
-(lower left), and linear (lower right) migration models, assuming our 
-inside-out SFH. 
-\textbf{Right}: The same as the left-hand panels, instead comparing the impact 
-of our constant (upper left), inside-out (upper right), late-burst (lower left), 
-and outer-burst (lower right) SFHs, assuming diffusion migration. In all panels, 
-red triangles and error bars denote the observed median age and dispersion 
-thereof in bins of [O/Fe] as reported by~\citet{Feuillet2019}; here we include 
-only their bins containing at least 15 stars. Black squares denote the 
-mass-weighted median age in 0.02-dex bins in [O/Fe] predicted by our models, 
-with error bars denoting the 16th and 84th percentiles of the mass-weighted 
-age distribution in those bins. Points in the background denote each individual 
-stellar population from the model with a final position in the solar 
-neighbourhood, colour-coded according to their Galactocentric radius of birth. 
-}
-\label{fig:age_alpha} 
-\end{figure*}
-
 In the left-hand set of panels of Fig.~\ref{fig:age_alpha}, we compare the 
@@
 producing most of their SNe Ia. 
-When the SN Ia Fe production rate fluctuates downward, [O/Fe] fluctuates 
-upward in the ISM, and the stars that form from it inherit such a composition. 
-These stars then migrate to the solar annulus. 
+% When the SN Ia Fe production rate fluctuates downward, [O/Fe] fluctuates 
+% upward in the ISM, and the stars that form from it inherit such a composition. 
+% These stars then migrate to the solar annulus. 
+% These stars can then migrate to the solar annulus. 
+{\color{red} 
+SNe Ia account for~$\sim$60\% of the Fe production at all metallicities 
+in our models (see discussion in~\S~\ref{sec:methods:yields}). 
+Visual inspection of Fig.~\ref{fig:tracks} indicates that the SN Ia rate can 
+vary by as much as a factor of~$\sim$3 at~$\rgal\gtrsim$~9 kpc in our models, 
+sometimes more in extreme cases, simply because their progenitors are 
+migrating; this corresponds to variability as large as~$\sim$40\% in the total 
+Fe enrichment rate if everything else is constant. 
+This variability can arise in part out of efficient radial migration moving 
+stars away from their birth radii faster than the SN Ia timescale as well as 
+the combination of the long tail of the SN Ia DTD and migration on longer 
+timescales (see discussion at the end of~\S~\ref{sec:methods:h277}). 
+The [$\alpha$/Fe] ratio at a given time is approximately determined by the 
+ratio of core collapse to type Ia supernova events occurring over the previous 
+depletion time~\citep{Weinberg2017}, which can be short in the outer Galaxy in 
+our models due to the substantial outflows at these radii (see discussion 
+in~\S~\ref{sec:methods:outflows}). 
+Consequently, when the SN Ia Fe production rate fluctuates downward, [O/Fe] 
+fluctuates upward in the ISM. 
+In a starburst event, the ISM becomes~$\alpha$-enhanced because the CCSN rate 
+increases~\citep{Johnson2020}. 
+The explanation suggested here is in some sense the opposite: the ISM 
+becomes not necessarily~$\alpha$-rich but Fe-poor because of fewer SNe Ia. 
+The stars that form inherit such a composition and can then migrate to 
+the solar annulus, and our models predict the variability to be sufficiently 
+large to explain the high [$\alpha$/Fe] ratios seen in APOGEE. 
+}
+\par 
 The presence of young and intermediate-age~$\alpha$-enhanced stars in APOGEE 
@@
 catalog~\citep{Pinsonneault2014}, and with the asteroseismic ages directly 
-\citep{SilvaAguirre2018}. 
-\par 
+\citep{Martig2015, Jofre2016, Izzard2018, SilvaAguirre2018}. 
+% \par 
 \citet{SilvaAguirre2018} demonstrate that these stars have kinematics similar 
 to the rest of the high-$\alpha$ population, and they suggest that they are 
-in fact old stars ``rejuvenated'' by mergers or mass transfer events. 
+in fact old stars ``rejuvenated'' by mergers or mass transfer events 
+{\color{red} 
+as postulated by~\citet{Jofre2016} and~\citet{Izzard2018}. 
+In a sample of four young~$\alpha$-enhanced stars observed with Gemini-GRACES, 
+\citet{Yong2016} find that two (possibly three) of them show evidence of a 
+debris disc, indicative of previous interactions with a binary companion. 
+} 
 In a sample of 51 young,~$\alpha$-rich red giants,~\citet{Hekker2019} 
@@
 sequence. 
-\citet{Weinberg2017} and~\citet{Johnson2020} proposed that young~$\alpha$-rich 
-stars could arise in bursts of star formation that enhance the rate of CCSN 
-enrichment. The explanation suggested here is in some sense the opposite: the 
-stars are not so much~$\alpha$-rich as they are Fe-poor because of the 
-deficit in SNe Ia events. 
+% \citet{Weinberg2017} and~\citet{Johnson2020} proposed that
+% young~$\alpha$-rich stars could arise in bursts of star formation that 
+% enhance the rate of CCSN enrichment. 
+% The explanation suggested here is in some sense the opposite: the 
+% stars are not so much~$\alpha$-rich as they are Fe-poor because of the 
+% deficit in SNe Ia events. 
+{\color{red} 
+We clarify that this result does not refute the previously suggested mass 
+transfer origin; this mechanism explains the truly young, 
+intrinsically~$\alpha$-enhanced stars which appear to make up a portion of the 
+young~$\alpha$-rich population separate from those which formed via mass 
+transfer~\citep{Yong2016, Hekker2019}. 
+}
 In our diffusion model,~$\sim$0.2\% of solar neighbourhood stars with 0.1~$\leq$ 
 [O/Fe]~$\leq$ 0.2 have ages below 4 Gyr, but~$\sim$13.9\% have ages below 7 Gyr. 
+{\color{red} 
+They have a broad distribution in metallicity spanning from [Fe/H]~$\approx-1$ 
+to~$\sim$solar, with multiple peaks indicative of separate sub-populations. 
+Although small sample sizes have prevented the detailed analaysis of 
+the [Fe/H] distribution of the young~$\alpha$-rich population, this 
+qualitatively agrees with the findings of~\citet{SilvaAguirre2018} (see their 
+Figs. 8 and 10) and~\citet{Miglio2021} (see their Fig. 5). 
+However, a direct comparison to data is not free of nuance, because the 
+young~$\alpha$-rich stars which formed via mass transfer likely outnumber those 
+which are intrinsically young~\citep{Miglio2021}. 
+} 
 \par 
@@
 age-[$\alpha$/Fe] relation. 
-
-% fig 14 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.32]{age_alpha_regions.pdf} 
-\caption{The age-[O/Fe] relation in 12 Galactic regions predicted by our 
-inside-out SFH. Bins in Galactocentric radius are shown in columns, and labeled 
-at the top. 
-Bins in the disc midplane distance~\absz~are shown in rows, noted in the 
-left-hand column. Red triangles, black squares, 
-error bars, and background points are as in Fig.~\ref{fig:age_alpha} for the 
-corresponding Galactic region. The solid black line connects the black squares 
-in the bottom, left-middle panel, and is replicated elsewhere for reference. } 
-\label{fig:age_alpha_regions} 
-\end{figure*}
-
+\par 
 Fig.~\ref{fig:age_alpha_regions} extends the comparison of our baseline, 
@@
 
+% fig 16 
+\begin{figure} 
+\centering 
+\includegraphics[scale = 0.44]{amr_solar_annulus.pdf} 
+\caption{The age-[O/H] (top) and age-[Fe/H] (bottom) relations for the solar 
+neighbourhood (i.e.~$R_\text{gal}$ = 7 - 9 kpc,~$\left|z\right|\leq$~0.5 kpc) 
+as predicted by the fiducial model. Red triangles, black squares, error bars, 
+and background points are as in Fig.~\ref{fig:age_alpha}, but with the model 
+prediction quantified in bins of~$\Delta$[O/H] =~$\Delta$[Fe/H] = 0.05. For 
+comparison, we plot the~\citet{Feuillet2018} measurements in a dark red line, 
+omitting the associated uncertainties for visual clarity. } 
+\label{fig:amr_solar_annulus} 
+\end{figure}
+
+% fig 17 
+\begin{figure*} 
+\centering 
+\includegraphics[scale = 0.35]{amr_insideout_vs_lateburst_fe.pdf} 
+\caption{The age-[Fe/H] relation predicted by our inside-out (top) and 
+late-burst (bottom) SFH models for~$R_\text{gal}$ = 5 - 7 kpc (left), 7 - 9 kpc 
+(left middle), 9 - 11 kpc (right middle), and 11 - 13 kpc (right). Each panel 
+shows only the~$\left|z\right|\leq$~0.5 kpc population. Red triangles, black 
+squares, error bars, and coloured points are as in Fig.~\ref{fig:age_alpha} for 
+the corresponding Galactic region, but with the model prediction quantified in 
+bins of~$\Delta$[Fe/H] = 0.05. } 
+\label{fig:amr_insideout_vs_lateburst_fe} 
+\end{figure*}
+
 Although the AMR is usually formulated in terms of 
@@
 of GCE. 
-
-% fig 16 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.45]{amr_solar_annulus.pdf} 
-\caption{The age-[O/H] (top) and age-[Fe/H] (bottom) relations for the solar 
-neighbourhood (i.e.~$R_\text{gal}$ = 7 - 9 kpc,~$\left|z\right|\leq$~0.5 kpc) 
-as predicted by the fiducial model. Red triangles, black squares, error bars, 
-and background points are as in Fig.~\ref{fig:age_alpha}, but with the model 
-prediction quantified in bins of~$\Delta$[O/H] =~$\Delta$[Fe/H] = 0.05. For 
-comparison, we plot the~\citet{Feuillet2018} measurements in a dark red line, 
-omitting the associated uncertainties for visual clarity. } 
-\label{fig:amr_solar_annulus} 
-\end{figure}
-
+\par 
 Fig.~\ref{fig:amr_solar_annulus} compares the age-[O/H] (top) and 
@@
 age-[Fe/H] relation in four~\rgal~annuli, always with~\absz~$\leq$ 0.5 kpc. 
-While neither model reproduces the data perfectly, the agreement is better 
-overall for the late-burst model, a difference that is more evident from 
-looking at all four annuli rather than the solar neighbourhood alone. 
-The late-burst of star formation reduces the median age of [Fe/H]~$\approx$ 0 
-stars, typically by 1 - 2 Gyr. 
-The median age of the highest metallicity stars increases because the 
-enhanced pristine gas accretion that fuels the starburst (see Fig. 
-\ref{fig:evol}) dilutes the ISM metallicity, an effect that is evident in the 
-tracks for a given birth~\rgal~in the lower panels. 
+% While neither model reproduces the data perfectly, the agreement is better 
+% overall for the late-burst model, a difference that is more evident from 
+% looking at all four annuli rather than the solar neighbourhood alone. 
+{\color{red} 
+At~\rgal~= 5 - 7 kpc, the inside-out model overpredicts the ages of solar and 
+sub-solar metallicity stars, an issue which is mitigated by the late-burst 
+model. 
+The late-burst of star formation reduces the median age of these stars, 
+typically by 1 - 2 Gyr, simply because more young stars form with the burst 
+than without. 
+The late-burst model also more convincingly reproduces the C-shaped AMR, the 
+most striking qualitative feature of the observations. 
+} 
+The median age of the highest metallicity stars increases because the enhanced 
+pristine gas accretion that fuels the starburst (see Fig.~\ref{fig:evol}) 
+dilutes the ISM metallicity, an effect that is evident in the tracks for a 
+given birth~\rgal~in the lower panels. 
 Stars from the inner Galaxy that form during the burst do so at roughly solar 
 metallicity rather than appearing in the [Fe/H] = 0.2 - 0.5 bins. 
-With reduced median age at [Fe/H]~$\approx$ 0 and increased median at 
-[Fe/H] > 0.2, the late-burst model more consistently reproduces the C-shaped 
-AMR that is the most striking qualitative feature of the observations. 
+{\color{red} 
+Both the increase in ages for the most metal-rich stars and decrease in ages 
+for solar and sub-solar metallicity stars contribute to the late-burst model 
+reproducing this C-shape better than the inside-out model. 
+The top two rows of Fig.~\ref{fig:age_oh_comparison} in 
+Appendix~\ref{sec:age_oh_relation} present the same comparison for the 
+age-[O/H] relation, which is unaffected by SN Ia enrichment. 
+The late-burst model improves upon the inside-out model there for the same 
+reasons as in age-[Fe/H], but perhaps more clearly when comparing bin-by-bin. 
+Although none of these models reproduce the data perfectly, the detailed form 
+of the AMR in our models is sensitive to the nature of the recent starburst or 
+lackthereof, and its true form was likely more complicated than our 
+parameterization. 
+} 
+\par 
+% The late-burst of star formation reduces the median age of [Fe/H]~$\approx$ 0 
+% stars, typically by 1 - 2 Gyr. 
+% The median age of the highest metallicity stars increases because the 
+% enhanced pristine gas accretion that fuels the starburst (see Fig. 
+% \ref{fig:evol}) dilutes the ISM metallicity, an effect that is evident in the 
+% tracks for a given birth~\rgal~in the lower panels. 
+% Stars from the inner Galaxy that form during the burst do so at roughly solar 
+% metallicity rather than appearing in the [Fe/H] = 0.2 - 0.5 bins. 
+% With reduced median age at [Fe/H]~$\approx$ 0 and increased median at 
+% [Fe/H] > 0.2, the late-burst model more consistently reproduces the C-shaped 
+% AMR that is the most striking qualitative feature of the observations. 
 The CCSN and SN Ia associated with the burst also boost the evolutionary 
@@
 distributions in mind. 
-\par 
-The outer-burst model mitigates this issue since it lacks the burst at small 
-\rgal, predicting ages for the most metal-rich stars more in line with the 
-\citet{Feuillet2019} measurements. 
-We illustrate this difference in Fig.~\ref{fig:age_oh_comparison} in 
-Appendix~\ref{sec:age_oh_relation} for the age-[O/H] relation. 
-The detailed form of the AMR in our models is sensitive to the nature of the 
-recent starburst, and its true form was likely more complicated than our 
-parameterization. 
-Fig.~\ref{fig:age_oh_comparison} also includes a comparison of the inside-out 
-and late-burst model predictions, now without the effect of SN Ia enrichment. 
-The late-burst model improves upon the inside-out model in age-[O/H] for the 
-same reasons as in age-[Fe/H], but perhaps more clearly when looking 
-bin-by-bin. 
+% \par 
+{\color{red} 
+The outer-burst model, illustrated for the age-[O/H] relation in the bottom 
+row of panels in Fig.~\ref{fig:age_oh_comparison} in 
+Appendix~\ref{sec:age_oh_relation}, mitigates this issue since it lacks the 
+burst at small~\rgal, predicting ages for the most metal-rich stars more in line 
+with the~\citet{Feuillet2019} measurements. 
+}
+% The outer-burst model mitigates this issue since it lacks the burst at small 
+% \rgal, predicting ages for the most metal-rich stars more in line with the 
+% \citet{Feuillet2019} measurements. 
+% We illustrate this difference in Fig.~\ref{fig:age_oh_comparison} in 
+% Appendix~\ref{sec:age_oh_relation} for the age-[O/H] relation. 
+% The detailed form of the AMR in our models is sensitive to the nature of the 
+% recent starburst, and its true form was likely more complicated than our 
+% parameterization. 
+% Fig.~\ref{fig:age_oh_comparison} also includes a comparison of the inside-out 
+% and late-burst model predictions, now without the effect of SN Ia enrichment. 
+% The late-burst model improves upon the inside-out model in age-[O/H] for the 
+% same reasons as in age-[Fe/H], but perhaps more clearly when looking 
+% bin-by-bin. 
 % We do not believe these conclusions are impacted by further discrepancies 

### 2021-08-04 chemev/MWbimodality/paper/draft3/conclusions.tex
migration paper referee response

--- 2021-08-04 chemev/MWbimodality/paper/draft2/conclusions.tex
@@
 
-% fig 17 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.35]{amr_insideout_vs_lateburst_fe.pdf} 
-\caption{The age-[Fe/H] relation predicted by our inside-out (top) and 
-late-burst (bottom) SFH models for~$R_\text{gal}$ = 5 - 7 kpc (left), 7 - 9 kpc 
-(left middle), 9 - 11 kpc (right middle), and 11 - 13 kpc (right). Each panel 
-shows only the~$\left|z\right|\leq$~0.5 kpc population. Red triangles, black 
-squares, error bars, and coloured points are as in Fig.~\ref{fig:age_alpha} for 
-the corresponding Galactic region, but with the model prediction quantified in 
-bins of~$\Delta$[Fe/H] = 0.05. } 
-\label{fig:amr_insideout_vs_lateburst_fe} 
-\end{figure*}
-
 In this paper, we have modeled the Milky Way as a series of concentric rings 
-with~$\Delta R_\text{gal}$~= 100 pc width, describing each ring as a 
+with~$\delta R_\text{gal}$~= 100 pc width, describing each ring as a 
 conventional one-zone chemical evolution model and allowing the exchange of 
@@
 formed from cosmological initial conditions~\citep{Christensen2012, 
-Zolotov2012, Loebman2012, Brooks2014, Bird2020}. 
+Zolotov2012, Loebman2012, Brooks2014, Bird2021}. 
 The simulation provides a prescription for radial migration and vertical 
@@
 	$\alpha$-rich stars seen in APOGEE~\citep{Chiappini2015, Martig2015, 
-	Martig2016, Warfield2021}. 
+	Martig2016, Jofre2016, Yong2016, Izzard2018, SilvaAguirre2018, 
+	Warfield2021}. 
 	See Figs.~\ref{fig:age_alpha} and~\ref{fig:age_alpha_regions}.
@@
 \citep[e.g.][]{Chiappini1997, Spitoni2019a, Khoperskov2021} and in cosmological 
-simulations that give rise to bimodal~\afe~\citep{Mackereth2017, Grand2018, 
+simulations that give rise to bimodal~\afe~\citep{Mackereth2018, Grand2018, 
 Buck2020b}. 
@@
 valuable complement to calculating chemical evolution within full hydrodynamic 
-cosmological simulations~\citep[e.g.][]{Mackereth2017, Grand2018, Naiman2018, 
+cosmological simulations~\citep[e.g.][]{Mackereth2018, Grand2018, Naiman2018, 
 Buck2020b, Vincenzo2020}. 

### 2021-08-04 chemev/MWbimodality/paper/draft3/data_availability.tex
migration paper referee response

\documentclass[draft2.tex]{subfiles} 
\begin{document}

\section{Data Availability} 
\label{sec:data_availability}

\vice~is open-source software, and the code that computes abundances for our 
models is publicly available as well. 
In its GitHub repository, we provide detailed instructions on how to run our 
models and variations thereof; information on their computational overhead and 
other aspects of~\vice~can be found in Appendix~\ref{sec:vice}. 
All observational data appearing in this paper is publicly available, and is 
also included with the source code for our models and figures. 
Our sample of star particles from~\hsim, including those with bulge and 
halo-like kinematics, is available through~\vice, which will download the files 
automatically the first time it needs them. The rest of the data 
from~\texttt{h277} can be accessed at~\url{https://nbody.shop/data.html}.

\end{document}

### 2021-08-04 chemev/MWbimodality/paper/draft3/intro.tex
migration paper referee response

--- 2021-08-04 chemev/MWbimodality/paper/draft2/intro.tex
@@
 \par 
+\null\par 
 In this paper we construct evolutionary models for the Milky Way disc that 
@@
 valuable insights into the accuracy of the simulations and the possible origin 
-of the observed element structure (e.g., ~\citealt{Mackereth2017, Grand2018, 
+of the observed element structure (e.g.,~\citealt{Mackereth2018, Grand2018, 
 Buck2020b, Vincenzo2020, Buck2021}). 
@@
 We focus our predictions and observational comparisons on oxygen, a 
-representative~$\alpha$-element producted almost exclusively by core 
+representative~$\alpha$-element produced almost exclusively by core 
 collapse supernovae (CCSN), and iron, which at solar abundances has roughly 
@@
 	Martig2015, Martig2016, Warfield2021}. Some of these stars may have been 
-	``rejuvinated'' by stellar mergers or mass-transfer events 
-	\citep{Izzard2018, SilvaAguirre2018}, and the question of what fraction 
-	are truly much younger than the median age-\afe~relation remains open 
-	\citep{Hekker2019}. 
+	``rejuvenated'' by stellar mergers or mass-transfer events 
+	\citep{Jofre2016, Yong2016, Izzard2018, SilvaAguirre2018}, and 
+	the question of what fraction are truly much younger than the median 
+	age-\afe~relation remains open~\citep{Hekker2019, Miglio2021}. 
 \end{itemize} 
@@
 \citep{Zolotov2012, Brooks2014}, and HI properties~\citep{Brooks2017}. 
-Most directly relevant to this study,~\citet{Bird2020} demonstrate that 
+Most directly relevant to this study,~\citet{Bird2021} demonstrate that 
 \hsim~accurately reproduces the observed relation between stellar age and 
@@
 coupled to changes in~$\sigma_z$~\citep*{Solway2012}. 
-The good match to the observed age-velocity relation found by~\citet{Bird2020} 
+The good match to the observed age-velocity relation found by~\citet{Bird2021} 
 allows us to use vertical trends of abundance ditributions as a further test 
@@
 Sysoliatina2021}), perhaps triggered by satellite interactions, while others 
-have advocated a two-phase SFH to explain the~\afe dichotomy (e.g., 
-\citealp*{Chiappini1997};~\citealp{Haywood2016, Spitoni2019a, Buck2020a, 
-Khoperskov2021}). We do not investigate these more complex SFHs here, but we 
-plan to do so in future work.
+have advocated a two-phase SFH to explain the~\afe~dichotomy (e.g., 
+\citealp*{Chiappini1997};~\citealp{Haywood2016, Mackereth2018, Spitoni2019a, 
+Buck2020a, Khoperskov2021}). We do not investigate these more complex SFHs 
+here, but we plan to do so in future work.
 

### 2021-08-04 chemev/MWbimodality/paper/draft3/methods.tex
migration paper referee response

--- 2021-08-04 chemev/MWbimodality/paper/draft2/methods.tex
@@
 first place. 
+{\color{red} 
+A summary of our chemical evolution model parameters can be found in 
+Table~\ref{tab:params}. 
+}
 
@@
 its detailed simulation parameters and cosmological model can be found in~\S~2 
-of~\citet{Bird2020}. 
+of~\citet{Bird2021}. 
 We do not repeat these details here, instead focusing on how we vet the sample 
@@
 radii and the final midplane distance. 
+{\color{red}\textit{
+	We emphasize that these are the only quantities from~\hsim~which we make 
+	use of in our model; our Galaxies have their own star formation histories, 
+	nucleosynthetic yields, outflow prescriptions, etc.
+}}
 \hsim~did not record the exact birth radius of each star particle; however, 
@@
 and~\citet{Bird2013}. 
-We include the entire sample in~\vice's public code base, but only make use of 
+We include the entire sample in~\vice's public code base, but make use of only 
 those with disc-like kinematics in this paper. 
@@
 
+% \begin{table} 
+% % \color{red} 
+% \caption{
+% For a given quantity in the model, this table summarizes whether it is 
+% adopted from~\hsim~or if it is specified as a model parameter. 
+% } 
+% \begin{tabularx}{\columnwidth}{l @{\extracolsep{\fill}} r} 
+% % \resizebox{\columnwidth}{!}{ 
+% % \begin{tabular}{l r} 
+% \hline 
+% \hline 
+% Quantity & Source 
+% \\ 
+% \hline 
+% Birth orbital radius of a stellar population & Model 
+% \\ 
+% Change in orbital radius of a stellar population & \hsim 
+% \\ 
+% Time-dependence of the change in orbital radius & Model 
+% \\ 
+% Present-day midplane distance of a stellar population (\absz) & \hsim 
+% \\ 
+% Star Formation History & Model 
+% \\ 
+% Nucleosynthetic Yields & Model 
+% \\ 
+% Outflows from the ISM & Model 
+% \\ 
+% Star Formation Law & Model 
+% \\ 
+% Surface Density Gradient & Model 
+% \\ 
+% \hline 
+% \end{tabularx} 
+% % } 
+% % \label{tab:params} 
+% \label{tab:which} 
+% \end{table}
+
 \subsection{Radial Migration} 
@@
 	to a larger radial range (typically 2 kpc). 
-} with a uniform width~$\Delta \rgal$. 
+} with a uniform width~$\delta \rgal$. 
 To run numerical simulations of these models, we develop and make use 
@@
 \textit{analogue}. 
-This stellar population then adopts the change in orbital radius 
+This stellar population then adopts the {\color{red} present day midplane 
+distance~$z$ and the} change in orbital radius 
 $\Delta \rgal$ of its analogue, and moves from its birth radius to the 
@@
 Myr, and assigns it as the analogue. 
-While this prescription allows stellar populations to be assigned analogues 
-with significantly different birth radii, this is only an issue for small~$T$ 
-and large~$\rgal$ where there are few star particles from~\hsim, 
-and where few stars form in nature anyway due to the inside-out growth of 
-galaxies~\citep[e.g.][]{Bird2013}. 
-Furthermore, due to the similarity of the histograms in the top row of 
-Fig.~\ref{fig:h277_decomposition}, we expect taking~$\Delta \rgal$ from 
-a star particle that formed at a similar time but different birth radius in 
-these instances to be accurate enough for our purposes. 
+{\color{red} 
+Because we remove bulge, pseudobulge, and halo star particles from our sample 
+(see discussion in~\S~\ref{sec:methods:h277}), every assigned analogue is a 
+star particle with disc-like kinematics. 
+Since~\hsim~has a similar final disc scale length as the Milky 
+Way~\citep{Bird2021}, we do not normalize radii by this quantity prior to 
+conducting the analogue search. 
 When an~\hsim~star particle is assigned as an analogue, it is~\textit{not} 
@@
 have similar but not identical abundances. 
+}
+\par 
+While this prescription allows stellar populations to be assigned analogues 
+with significantly different birth radii, this is only an issue for small~$T$ 
+and large~$\rgal$ where {\color{red} only a small fraction of~\hsim's star 
+particles reside,} 
+% there are few star particles from~\hsim, 
+and where few stars form in nature anyway due to the inside-out growth of 
+galaxies~\citep[e.g.][]{Bird2013}. 
+{\color{red} 
+In practice, we find that our sample of star particles is sufficiently large 
+such that our model is still able to assign the vast majority of stellar 
+populations born at large~\rgal~($\gtrsim$10 kpc) and small~$T$ 
+(age~$\gtrsim$10 Gyr) an analogue which formed within~$\sim$2 kpc of its birth 
+radius. 
+Although the models we present in this paper do impose a small but non-zero 
+level of star formation at early times and large radii (see Fig.~\ref{fig:evol} 
+and the associated discussion in~\S~\ref{sec:methods:sfhs}), this ensures that 
+those stellar populations inherit plausible dynamics from the~\hsim~star 
+particles. 
+}
+Furthermore, due to the similarity of the histograms in the top row of 
+Fig.~\ref{fig:h277_decomposition}, we expect taking~$\Delta \rgal$ from 
+a star particle that formed at a similar time but different birth radius in 
+these instances to be accurate enough for our purposes. 
+{\color{red}
+In exploratory work for this paper, we also considered a migration model in 
+which stellar populations remain at their birth radius if no analogue born 
+within~$\rgal~\pm$~500 pc and~$T~\pm$~500 Myr is found. 
+We find similar results in this case, suggesting that our qualitative 
+conclusions are largely unaffected by the fine details of the dynamical 
+history. 
+}
+% When an~\hsim~star particle is assigned as an analogue, it is~\textit{not} 
+% thrown out of the sample of candidate analogues, in theory allowing a star 
+% particle to act as an analogue for multiple stellar populations. Because these 
+% populations will have similar~$R_\text{form}$~and~$T_\text{form}$, they will 
+% have similar but not identical abundances.
 
@@
 clear vertical gradients because older stellar populations have thicker 
-vertical distributions~\citep{Bird2020}. 
+vertical distributions~\citep{Bird2021}. 
 Radial migration is also coupled to vertical dynamics in complex ways 
@@
 Our yields would be lower in a scenario with extensive black hole formation 
-and/or a steeper high mass IMF (Griffith et al. 2021). 
+and/or a steeper high mass IMF~\citep{Griffith2021b}. 
 These effects could also introduce a metallicity dependence if the landscape of 
@@
 \vice~has capabilities to compute IMF-averaged yields for a flexible 
-description of the massive star explodability landscape, as described by 
-Griffith et al. (2021) and the~\vice~documentation, but we do not use this 
+description of the massive star explodability landscape, as described 
+by~\citet{Griffith2021b} and the~\vice~documentation, but we do not use this 
 methodology here. 
@@
 \eta(\rgal) = \frac{y_\alpha^\text{CC}}{Z_{\alpha,\odot}} 
-10^{(-0.08\text{ kpc}^{-1})(\rgal - 4\text{ kpc}) + 0.3} + r - 1, 
+10^{(0.08\text{ kpc}^{-1})(\rgal - 4\text{ kpc}) - 0.3} + r - 1, 
 \label{eq:eta_rgal} 
@@
 not significantly alter the form of~$g(\rgal)$. 
-We demonstrate that this assumption holds 
-in~\S~\ref{sec:methods:surface_density_gradient}, in which we also detail our 
+{\color{red} 
+We find this to be true for our sample of~\hsim~star particles, and we 
+demonstrate that this assumption holds in our chemical evolution models 
+in~\S~\ref{sec:methods:surface_density_gradient}, where we also detail our 
 adopted form of~$g(\rgal)$. 
+}
+% We demonstrate that this assumption holds 
+% in~\S~\ref{sec:methods:surface_density_gradient}, in which we also detail our 
+% adopted form of~$g(\rgal)$. 
 The equation derived in Appendix~\ref{sec:normalize_sfh} can be used to 
@@
 	Gyr, roughly corresponding to a redsfhit of~$z \approx$ 2.5. 
-	We discuss the choice of~$\tau_\text{sfh}$ below.
+	{\color{red} 
+	In detail, however, the time of peak star formation increases 
+	with~$\tau_\text{sfh}$, which in turn increases with~\rgal~in our models 
+	(see discussion below). 
+	As a result,~$\dot{\Sigma}_\star$ in the outer disc instead reaches its 
+	peak at lookback times of~$\sim$7 - 8 Gyr, qualitatively consistent with 
+	the radial growth of the Galaxy~\citep[e.g.][]{Bird2012, Bird2013}. 
+	} 
+	% We discuss the choice of~$\tau_\text{sfh}$ below.
 
@@
 \end{itemize}
+
+% fig 4 
+\begin{figure*} 
+\centering 
+\includegraphics[scale = 0.32]{evol.pdf} 
+\caption{The surface densities of star formation~$\dot{\Sigma}_\star$ (top 
+row), infall $\dot{\Sigma}_\text{in}$ (middle row), and gas~$\Sigma_\text{g}$ 
+(bottom row) as functions of simulation time for our four fiducial SFHs: 
+constant (far left), inside-out (left middle), late-burst (right middle), and 
+outer-burst (far right). We plot curves for the rings whose inner radii are 
+3 kpc (grey), 5 kpc (black), 7 kpc (red), 9 kpc (yellow), 11 kpc (green), 13 
+kpc (blue), and 15 kpc (purple) (see equations~\refp{eq:constant_sfh}, 
+\refp{eq:insideout_sfh}, and~\refp{eq:lateburst_sfh} for the mathematical 
+definition of each SFH). 
+}
+\label{fig:evol} 
+\end{figure*}
+
 The inside-out model is our fiducial choice, and it is the model shown in 
@@
 recent data. 
-More complex scenarios with multiple bursts induced by repeated satellite 
-passages~\citep[e.g.][]{Lian2020a, Lian2020b, RuizLara2020, Sysoliatina2021} 
-can be modeled easily in~\vice, but we do not explore them here. 
+{\color{red} 
+More complex scenarios, such as multiple bursts induced by repeated satellite 
+passages~\citep[e.g.][]{Lian2020a, Lian2020b, RuizLara2020, Sysoliatina2021} or 
+the onset of star formation occurring later in the outer disc to better capture 
+the radial growth of the Galaxy~\citep[e.g.][]{Bird2012, Bird2013}, can be 
+explored easily using~\vice, but we do not explore such models here. 
+} 
+% More complex scenarios with multiple bursts induced by repeated satellite 
+% passages~\citep[e.g.][]{Lian2020a, Lian2020b, RuizLara2020, Sysoliatina2021} 
+% can be modeled easily in~\vice, but we do not explore them here. 
 \par 
@@
 
-% fig 4 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.32]{evol.pdf} 
-\caption{The surface densities of star formation~$\dot{\Sigma}_\star$ (top 
-row), infall $\dot{\Sigma}_\text{in}$ (middle row), and gas~$\Sigma_\text{g}$ 
-(bottom row) as functions of simulation time for our four fiducial SFHs: 
-constant (far left), inside-out (left middle), late-burst (right middle), and 
-outer-burst (far right). We plot curves for the rings whose inner radii are 
-3 kpc (grey), 5 kpc (black), 7 kpc (red), 9 kpc (yellow), 11 kpc (green), 13 
-kpc (blue), and 15 kpc (purple) (see equations~\refp{eq:constant_sfh}, 
-\refp{eq:insideout_sfh}, and~\refp{eq:lateburst_sfh} for the mathematical 
-definition of each SFH). 
-}
-\label{fig:evol} 
-\end{figure*}
-
 We plot the resulting SFHs of our models in the top row of Fig.~\ref{fig:evol} 
@@
 modestly from its 2 Gyr peak in the inside-out model. 
-At all timesteps, the gas supply is known via the star formation efficiency 
-timescale~$\tau_\star$ (see~\S~\ref{sec:methods:sfe}), which is illustrated in 
-the bottom row of Fig.~\ref{fig:evol}. 
+{\color{red} 
+The gas supply, whose value at all timesteps is known via the star formation 
+efficiency timescale~$\tau_\star$ (see~\S~\ref{sec:methods:sfe}), is 
+illustrated in the bottom row of Fig.~\ref{fig:evol}. 
+}
+% At all timesteps, the gas supply is known via the star formation efficiency 
+% timescale~$\tau_\star$ (see~\S~\ref{sec:methods:sfe}), which is illustrated in 
+% the bottom row of Fig.~\ref{fig:evol}. 
 \vice~automatically calculates the implied infall rate by comparing the amount 
@@
 on~$\Sigma_\text{g}$ within a galaxy. 
-\par 
+% \par
+
+% fig 5 
+\begin{figure} 
+\centering 
+\includegraphics[scale = 0.45]{sfe.pdf} 
+\caption{The star formation efficiency timescale~$\tau_\star$ as a function of 
+Galactocentric radius at simulation times of 2 Gyr (red), 4 Gyr (yellow), 
+6 Gyr (green), 8 Gyr (blue), 10 Gyr (purple), and 13.2 Gyr (the present day, 
+black) predicted by our fiducial model. } 
+\label{fig:sfe} 
+\end{figure}
+
 \citet{Krumholz2018a} compare theoretically motivated star formation laws to 
@@
 $\dot{\Sigma}_\star$ given our equations~\refp{eq:sf_law} and~\refp{eq:tau_mol}. 
-
-% fig 5 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.45]{sfe.pdf} 
-\caption{The star formation efficiency timescale~$\tau_\star$ as a function of 
-Galactocentric radius at simulation times of 2 Gyr (red), 4 Gyr (yellow), 
-6 Gyr (green), 8 Gyr (blue), 10 Gyr (purple), and 13.2 Gyr (the present day, 
-black) predicted by our fiducial model. } 
-\label{fig:sfe} 
-\end{figure}
-
+\par
 In Fig.~\ref{fig:sfe}, we plot~$\tau_\star$ as a function of~$\rgal$ at 
@@
 
+\begin{table*} 
+% \color{red} 
+\caption{
+A summary of our chemical evolution model parameters, their fiducial values, 
+and in what section of the text relevant discussion can be found. 
+}
+\begin{tabularx}{\textwidth}{l @{\extracolsep{\fill}} l l r} 
+\hline 
+\hline 
+Quantity & Section & Description & Fiducial Value(s) 
+\\ 
+\hline 
+\rgal & N/A & Galactocentric Radius & $0 - 20$ kpc 
+\\ 
+$\delta$\rgal & \ref{sec:methods:summary} & Width of each concentric ring & 
+100 pc 
+\\ 
+$\Delta$\rgal & \ref{sec:methods:migration} & Change in orbital radius due to 
+stellar migration; adopted from~\hsim~analogue star particle & N/A 
+\\ 
+$z$ & \ref{sec:methods:migration} & Present day distance to Galactic midplane; 
+adopted from~\hsim~analogue star particle & $-3 - +3$ kpc 
+\\ 
+$T_\text{max}$ & \ref{sec:methods:h277} & Time interval over which our models 
+are integrated & 13.2 Gyr 
+\\ 
+$\delta T$ & \ref{sec:methods:summary} & Timestep size & 10 Myr 
+\\ 
+$n$ & \ref{sec:methods:summary} & Number of stellar populations formed per ring 
+per timestep & 8 
+\\ 
+$R_\text{SF}$  & \ref{sec:methods:summary} & Maximum radius of star formation 
+(i.e.~$\dot{\Sigma}_\star$ = 0 at~\rgal~>~$R_\text{SF}$) & 15.5 kpc 
+\\ 
+$\tau_\star$ & \ref{sec:methods:sfe} & The SFE timescale of the ISM: 
+$\tau_\star \equiv \Sigma_\text{gas} / \dot{\Sigma}_\star$ & N/A 
+\\ 
+$\tau_{\text{mol},0}$ & \ref{sec:methods:sfe} & The SFE timescale of molecular 
+hydrogen at the present day & 2 Gyr 
+\\ 
+$\gamma$ & \ref{sec:methods:sfe} & The power-law index describing the 
+time-dependence of the molecular hydrogen SFE timescale 
+(i.e.~$\tau_\text{mol}\sim t^\gamma$) & 1/2 
+\\ 
+$\eta$ & \ref{sec:methods:outflows} & The outflow mass-loading factor: 
+$\eta \equiv \dot{\Sigma}_\text{out}/\dot{\Sigma}_\star$ (assumed to be 
+time-independent) & equation~\refp{eq:eta_rgal} 
+\\ 
+$y_\text{O}^\text{CC}$ & \ref{sec:methods:yields} & CCSN yield of O & 0.015 
+\\ 
+$y_\text{Fe}^\text{CC}$ & \ref{sec:methods:yields} & CCSN yield of Fe & 0.0012 
+\\ 
+$y_\text{O}^\text{Ia}$ & \ref{sec:methods:yields} & SN Ia yield of O & 0 
+\\ 
+$y_\text{Fe}^\text{Ia}$ & \ref{sec:methods:yields} & SN Ia yield of Fe & 0.00214 
+\\ 
+$\dot{\Sigma}_\star$ & \ref{sec:methods:sfhs} & Surface density of star 
+formation & N/A
+\\ 
+$f_\text{IO}(t|\rgal)$ & \ref{sec:methods:sfhs} & The time-dependence of the 
+star formation history in the inside-out model & 
+equation~\refp{eq:insideout_sfh} 
+\\ 
+$f_\text{LB}(t|\rgal)$ & \ref{sec:methods:sfhs} & The time-dependence of the 
+star formation history in the late-burst model & 
+equation~\refp{eq:lateburst_sfh} 
+\\ 
+\hline 
+\end{tabularx} 
+\label{tab:params} 
+\end{table*}
+
+% As discussed in~\S~\ref{sec:methods:sfhs}, Appendix~\ref{sec:normalize_sfh} 
+% presents the recipe by which we select a unitless function describing the 
+% stellar surface density gradient~$g(\rgal)$. 
+{\color{red} 
 As discussed in~\S~\ref{sec:methods:sfhs}, Appendix~\ref{sec:normalize_sfh} 
-presents the recipe by which we select a unitless function describing the 
-stellar surface density gradient~$g(\rgal)$. 
+presents the recipe by which we normalize our star formation histories, a 
+necessary component of which is a unitless function describing the stellar 
+surface density gradient~$g(\rgal)$. 
+}
 In setting the normalization, our model ensures that the integral of~$g(\rgal)$ 
@@
 \ref{eq:gradient}) denoted by the solid black line. 
-Stellar migration has not altered the overall form of the gradient, simply 
-introducing scatter around the adopted trend. 
+{\color{red} 
+Simply introducing scatter around the adopted trend, stellar migration has 
+not significantly altered the overall form of the gradient, as we assumed in 
+Appendix~\ref{sec:normalize_sfh}; we find this to also be true for our sample 
+of star particles from~\hsim. 
+}
+% Stellar migration has not altered the overall form of the gradient, simply 
+% introducing scatter around the adopted trend. 
 Although there are slight enhancements at small~$\rgal$ and deficits at large 
@@
 \label{sec:methods:summary}
+
+% fig 7 
+\begin{figure*} 
+\centering 
+\includegraphics[scale = 0.28]{ofe_feh_densitymap.pdf} 
+\caption{[O/Fe]-[Fe/H] diagrams for 15 Galactic regions spanning five bins in 
+$R_\text{gal}$ and three in~$\left|z\right|$. Each region has its own panel, 
+with radial bins shown in columns denoted at the top, and with bins in 
+$\left|z\right|$ shown in rows denoted in text in the middle column. For each 
+region, we plot~$N$~= 10,000 points sampled from our simulated stellar 
+populations predicted by our fiducial model, where the probability of 
+sampling is proportional to the present-day mass of each stellar population. 
+In all panels, points are colour-coded according to the Galactocentric radius 
+of birth of the stellar population. For reference, we plot in a solid black 
+line in all panels the gas-phase [O/Fe]-[Fe/H] track predicted by the same 
+SFH in the~$R_\text{gal}$ = 8 kpc annulus, but with the post-processing 
+migration model; this curve is the same in all panels. } 
+\label{fig:ofe_feh_diagram} 
+\end{figure*}
+
+{\color{red} 
+Table~\ref{tab:params} presents a breakdown of our model parameters, their 
+values, and references to the sections where relevant discussion can be found. 
+}
 In summary, our fiducial model has an inside-out SFH with e-folding timescales 
@@
 discussion in~\S~\ref{sec:methods:h277}). 
-We take~$\Delta\rgal$ = 100 pc as the width of each annulus from~\rgal~= 0 to 
-20 kpc and a timestep size of~$\Delta T$ = 10 Myr from~$T$ = 0 to 13.2 Gyr. 
+We take~$\delta\rgal$ = 100 pc as the width of each annulus from~\rgal~= 0 to 
+20 kpc and a timestep size of~$\delta T$ = 10 Myr from~$T$ = 0 to 13.2 Gyr. 
 With the resulting 200 zones and 1,321 timesteps (one extra so that age = 0 

### 2021-08-04 chemev/MWbimodality/paper/draft3/vice.tex
migration paper referee response

\documentclass[draft2.tex]{subfiles} 
\begin{document}

\section{\texttt{VICE}} 
\label{sec:vice}

\vice~is an open-source~\texttt{python} package available for Linux and Mac OS 
X.\footnote{ 
	Install (PyPI): \url{https://pypi.org/project/vice} \\ 
	Documentation: \url{https://vice-astro.readthedocs.io} \\ 
	Source Code: \url{https://github.com/giganano/VICE.git} 
} 
Windows users should install and use~\vice~entirely within the Windows Subsystem 
for Linux. 
It requires~\texttt{python >=}~3.6 and can be installed in a terminal via 
\texttt{pip install vice}, after which~\texttt{vice -{}-docs} will launch a web 
browser to the documentation at \url{https://vice-astro.readthedocs.io}. 
\texttt{vice -{}-tutorial} will also 
launch a web browser, but to a jupyter notebook in the GitHub repository 
intended to familiarize first-time users with~\vice's API. 
\texttt{Python} code that runs the simulations presented in this paper is 
included as supplementary material in the GitHub repository; they can be run 
from a terminal without modifying the source code. 
When taking into account time-dependent stellar migration,~\vice~requires 
$\sim$2.5 CPU-hours per chemical element to compute masses, abundances, and 
initial and final Galactic regions for~$\sim$1.6 million stellar populations 
spanning a little over 1,300 timesteps. 
This estimate was made using a single core with a 3 GHz processor. 
Although their outputs require only~$\sim$235 MB of disc space each, our models 
as computed in this paper can require up to~$\sim$3 GB of RAM at any given 
time owing to the number of timesteps and stellar populations used, but these 
can be adjusted via command line arguments. 
Beyond what has been presented in this paper,~\vice's capabilities include 
user-defined, arbitrary functions of time describing star formation and infall 
histories, star formation laws, outflow prescriptions, SN Ia delay-time 
distributions, and element-by-element infall metallicities. 
It allows the IMF to be a user-defined function of stellar mass. 
It will compute yields from supernova and asymptotic giant branch star 
nucleosynthesis studies, but allows the user to specify arbitrary mathematical 
forms for use in chemical evolution models. 
A complete breakdown of its abilities can be found in the documentation. 
While providing this level of versatility in a~\texttt{python} package, 
\vice~also enjoys a backend implemented in ANSI/ISO~\texttt{C}, providing it 
with the powerful computing speeds of a compiled library; with typical 
parameters, yield calculations and one-zone model integrations require only a 
fraction of a second.

\end{document}

### 2021-08-04 chemev/MWbimodality/paper/figures/figures.tex
migration paper referee response

\documentclass{report} 
\usepackage{graphics} 
\usepackage{graphicx} 
\usepackage{mathtools} 
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage[margin = 1in]{geometry}

\graphicspath{
	{/Users/astrobeard/Work/Research/VICErepos/VICE/migration/figures/}
}

\begin{document}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.5]{migration.pdf} 
\caption{A diagram illustrating our migration schema: diffusion (crimson, 
solid), linear (lime, dot-dashed), post-process (black, dotted), and sudden 
(blue, dashed), for three sets of initial and final radii and birth times. 
These values are pseudorandom numbers drawn from a uniform distribution for 
illustrative purposes. With the initial and final Galactocentric radii of a 
stellar population, its birth time, and one of these assumptions about the 
time-dependence of radial migration, the Galactocentric radius at all times 
is known. } 
\end{figure*}

\begin{figure} 
\centering 
\includegraphics[scale = 0.5]{h277/birth_final_radii_pdfs.pdf} 
\caption{Distributions of~\texttt{h277} star particles in their birth (left) 
and final (right) Galactocentric radii. Distributions are shown for thin 
disk (crimson), thick disk (blue), bulge (black), and pseudobulge (lime) 
populations according to the kinematic decomposition described in~\S~X. 
In the right-hand panel we denote the number of star particles in each 
population according to the same color-coding. } 
\label{fig:h277_birth_final_radii_pdfs} 
\end{figure}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.5]{tau_sfh.pdf} 
\caption{The e-folding timescale of the SFH as a function of Galactocentric 
radius adopted in this work, as reported by Sanchez (2020) for their 
M$_\star$ = $10^{10.5}$ M$_\odot$ - $10^{11.0}$ M$_\odot$ mass bin. The 
horizontal and vertical red dotted lines highlight $\tau_\text{sfh} \approx$ 
15 Gyr at an assumed orbital radius of the sun of R$_\odot$ = 8 kpc. }
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{evol/2Gyr_timedep/diffusion.pdf} 
\caption{The surface densities of star formation $\dot{\Sigma}_\star$ (top 
row), infall $\dot{\Sigma}_\text{in}$ (middle row), and gas $\Sigma_\text{gas}$ 
(bottom row) as functions of simulation time in Gyr for our four fiducial 
models - Constant SFR (far left), inside-out (left-middle), late-burst 
(right-middle), and outer-burst (far right). Curves are shown for the annuli 
whose inner radius is 3 kpc (grey), 5 kpc (black), 7 kpc (red), 9 kpc (yellow), 
11 kpc (green), 13 kpc (blue), and 15 kpc (purple). }
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{sfe/2Gyr_timedep/diffusion.pdf} 
\caption{The star formation efficiency (SFE) timescale $\tau_\star$ in Gyr 
as a function of Galactocentric radius at simulation times of 2 Gyr (red), 
4 Gyr (yellow), 6 Gyr (green), 8 Gyr (blue), 10 Gyr (purple), and 12.8 Gyr 
(black) for our four fiducial models - Constant SFR (far left), inside-out 
(left-middle), late-burst (right-middle), and outer-burst (far right). }
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.5]{eta.pdf} 
\caption{Our implemented scaling of the mass loading factor $\eta$ with 
Galactocentric radius (black) as defined by equation X. The horizontal and 
vertical red dashed lines denote the value of $\eta\approx$ 1.7 at an assumed 
orbital radius of the sun of R$_\odot$ = 8 kpc. }
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.5]{surface_density_gradient_timedep.pdf} 
\caption{The surface density of gas (blue) and stars (red) as predicted by 
our inside-out evolutionary model with diffusion migration and 
$\tau_\star^\text{mol} = (\text{2 Gyr})(t/t_0)^{1/2}$. For comparison, we 
plot the surface density gradient of the Milky Way thin and thick disks as 
reported by Bland-Hawthorn \& Gerhard (2016) in a black solid line. Black 
dotted lines show the individual thin and thick disk components. }
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{metallicity_gradient/2Gyr_timedep/diffusion.pdf} 
\caption{Radial abundance gradients in [O/H] (top, red), [Fe/H] (top, blue), 
and [O/Fe] (bottom) for our four fiducial models - Constant SFR (far left), 
inside-out (left-middle), late-burst (right-middle), and outer-burst 
(far right). We plot the gas-phase abundance at the present day as a function 
of Galactocentric radius in solid lines. Stars denote the mode of the stellar 
MDF of the 100-pc width annulus at a given radius, with shaded regions marking 
the 16th and 84th percentiles thereof. Black lines in the top panels denote 
our target [$\alpha$/H] gradient of mode([$\alpha$/H]) = +0.3 at 
$R_\text{gal}$ = 4 kpc with a slope of -0.06 kpc$^{-1}$. }
\label{fig:metallicity_gradient} 
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.45]{tracks/diffusion_2Gyr_timedep.pdf} 
\caption{\textbf{Left}: Evolutionary tracks for the gas phase in the 
[O/Fe]-[Fe/H] plane for models with 
$\tau_\star^\text{mol} = (\text{2 Gyr})(t/t_0)^{1/2}$, our inside-out SFH, and 
either post-processing (dotted lines) or diffusion (solid lines) migration 
models. We plot tracks for seven annuli, color-coded according to their 
Galactocentric radius and denoted by the legend in the lower-left. We mark 
simulation times of 2, 4, 6, 8, 10, and 12.7 Gyr in X's for the diffusion 
model and points for the post-processing model. 
\textbf{Right}: The proxy for the SN Ia rate defined in equation X as a 
function of simulation time for the same annuli as in the left-hand panel. 
We multiply rates at each radii here by various prefactors in the interest of 
clarity. } 
\label{fig:tracks_diffusion} 
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.5]{age_ofe/2Gyr_timedep/Rgal_7_9/insideout.pdf} 
\caption{
A comparison of the predicted age-[O/Fe] relation for the solar annulus 
($R_\text{gal}$ = 7 - 9 kpc and $\left|z\right|\leq$ 0.5 kpc) between the 
post-processing (upper left), diffusion (upper right), sudden (lower left), 
and linear (lower right) migration models, assuming our inside-out SFH and 
$\tau_\star^\text{mol} = (\text{2 Gyr})(t/t_0)^{1/2}$. Red triangles and error 
bars denote the observed mean age and dispersion thereof in bins of [O/Fe] as 
reported by Feuillet et al. (2019); here we include only the bins containing 
at least 15 stars. Black squares denote the mass-weighted median age in 
0.02-dex bins in [O/Fe], with error bars denoting the 16th and 84th 
percentiles of the mass-weighted age distribution in those bins. Points in the 
background denote each individual stellar population from the simulation with 
a final position in the solar annulus, color-coded according to their 
Galactocentric radius of birth. 
}
\label{fig:age_ofe_migration_comp}
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.5]{age_ofe/2Gyr_timedep/Rgal_7_9/diffusion.pdf} 
\caption{
The same as Fig.~\ref{fig:age_ofe_migration_comp}, instead comparing the 
impact of our constant (upper left), inside-out (upper right), late-burst 
(lower left), and outer-burst (lower right) SFHs, assuming diffusion migration 
and $\tau_\star^\text{mol} = (\text{2 Gyr})(t/t_0)^{1/2}$. 
}
\label{fig:age_ofe_sfh_comp} 
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{amr/2Gyr_timedep/diffusion/insideout_O_Fe.pdf} 
\caption{The age-[O/Fe] relation in different galactic regions predicted by 
our inside-out evolutionary model with 
$\tau_\star^\text{mol} = (\text{2 Gyr})(t/t_0)^{1/2}$ and diffusion migration. 
Bins in Galactocentric radius are shown in columns, and labeled at the top. 
Bins in the height $\left|z\right|$ above/below the disk midplane are shown in 
rows, noted in the left-hand column. Red triangles and error bars denote the 
observed mean age and dispersion thereof in bins of [O/Fe] as reported by 
Feuillet et al. (2019); here we include only the bins containing at least 
15 stars. Black squares denote the mass-weighted median age in 0.02-dex bins 
in [O/Fe], with error bars denoting the 16th and 84th percentiles of the 
mass-weighted age distribution in those bins. Points in the background denote 
each individual stellar population from the simulation with a final position 
in that Galactic region, color-coded according to their Galactocentric radius 
of birth. 
} 
\label{fig:galactic_regions_ofe} 
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{amr/2Gyr_timedep/diffusion_O.pdf} 
\caption{
The age-[O/H] relation predicted by our constant (top), inside-out (top 
middle), late-burst (bottom middle), and outer-burst (bottom) SFHs for 
$R_\text{gal}$ = 5 - 7 kpc (left), 7 - 9 kpc (left middle), 9 - 11 kpc (right 
middle), and 11 - 13 kpc (right). Each panel plots only the 
$\left|z\right|\leq$ 0.5 kpc population. Background points, red triangles with 
error bars, and black squares with error bars are as in 
Fig.~\ref{fig:galactic_regions_ofe}, but with our binned, simulated relation 
quantified in 0.05-dex bins in [O/H]. 
}
\label{fig:disk_comp_o} 
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{amr/2Gyr_timedep/diffusion_Fe.pdf} 
\caption{The same as Fig.~\ref{fig:disk_comp_o}, but for the age-[Fe/H] 
relation.} 
\label{fig:disk_comp_fe} 
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{amr/2Gyr_timedep/diffusion/outerburst_O.pdf} 
\caption{The same as Fig.~\ref{fig:galactic_regions_ofe}, but for the age-[O/H] 
relation, the outer-burst rather than inside-out SFH, and with our binned, 
simulated relation quantified in 0.05-dex bins in [O/H].} 
\label{fig:galactic_regions_o}
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{amr/2Gyr_timedep/diffusion/outerburst_Fe.pdf} 
\caption{The same as Fig.~\ref{fig:galactic_regions_ofe}, but for the 
age-[Fe/H] relation, the outer-burst rather than inside-out SFH, and with our 
binned, simulated relation quantified in 0.05-dex bin in [Fe/H].}
\label{fig:galactic_regions_fe}
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.4]{mdf_3panel/2Gyr_timedep/diffusion/insideout.pdf} 
\caption{Metallicity distribution functions (MDFs) in [Fe/H] for our 
inside-out SFH with $\tau_\star^\text{mol} = (\text{2 Gyr})(t/t_0)^{1/2}$ and 
diffusion migration. Distributions are shown in bins of present-day 
Galactocentric radius noted in the legend in the top panel, with each panel 
showing distributions in bins of $\left|z\right|$ noted at the top-center of 
each panel.}
\label{fig:mdf_3panel_insideout} 
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.4]{mdf_3panel/2Gyr_timedep/diffusion/lateburst.pdf} 
\caption{Same Fig.~\ref{fig:mdf_3panel_insideout}, but for our late-burst SFH.}
\end{figure*}

\end{document}

### 2021-08-04 chemev/MWbimodality/paper/outline/outline.tex
migration paper referee response

\documentclass[a4paper, fleqn, usenatbib, useAMS]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae, aecompl}			% Required for MNRAS
\usepackage{newtxtext, newtxmath} 	% Required for MNRAS 
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage{bm}
\usepackage{pdflscape}
\usepackage{natbib}
\usepackage[section]{placeins}
\usepackage{lipsum}
\usepackage{etoolbox} 
\usepackage{tabularx} 
\usepackage{xcolor} 
\usepackage[toc, page]{appendix} 
% \hypersetup{draft} 
\hypersetup{ 
	colorlinks		= true, 
	urlcolor 		= blue, 
	linkcolor 		= blue, 
	citecolor 		= blue 
}

\newcommand{\ddfrac}[2]{\frac{\displaystyle #1}{\displaystyle #2}} 
\newcommand{\refp}[1]{(\ref{#1})} 
\graphicspath{ {../plots/} }

\interfootnotelinepenalty = 10000 
\defcitealias{Kroupa2001}{Kroupa} 
\defcitealias{Salpeter1955}{Salpeter}

% \title[The Pivotal Role of Radial Migration]{The Pivotal Role of Radial 
% Migration in the Chemical Enrichment of the Milky Way} 
% \title[Galactic Archaeology with Stellar Migration]{Galactic Archaeology with 
% Stellar Migration} 
\title{Stellar Migration and Chemical Enrichment in the Milky Way}

\author[J.W. Johnson et al.]{
	James W. Johnson,$^{1}$\thanks{Contanct e-mail: \href{mailto:
	johnson.7419@osu.edu}{johnson.7419@osu.edu}} 
	David H. Weinberg,$^{1, 2}$ 
	Fiorenzo Vincenzo,$^{2}$ 
	Jonathan C. Bird,$^{3}$ 
	\newauthor 
	Sarah R. Loebman,$^{4}$ 
	Alyson Brooks,$^{5}$ 
	Thomas R. Quinn,$^{6}$ 
	Charlotte R. Christensen,$^{7}$ 
	\newauthor 
	et al.?
	\\
	$^{1}$ Department of Astronomy, The Ohio State University, 
	140 W. 18th Ave., Columbus, OH, 43210, USA 
	\\ 
	$^{2}$ Center for Cosmology and Astroparticle Physics (CCAPP), 
	The Ohio State University, 191 W. Woodruff Ave, Columbus, OH, 43210, USA 
	\\ 
	$^{3}$ Department of Physics \& Astronomy, Vanderbilt University, 
	2301 Vanderbilt Place, Nashville, TN, 37235, USA 
	\\ 
	$^{4}$ Department of Physics, University of California Merced, 
	5200 North Lake Rd., Merced, CA, 95343, USA 
	\\ 
	$^{5}$ Department of Physics \& Astronomy, Rutgers University, 136 
	Frelinghuysen Rd, Piscataway, NJ, 08854, USA 
	\\ 
	$^{6}$ Department of Astronomy, University of Washinton, Box 351580, 
	Seattle, WA, 98195, USA 
	\\ 
	$^{7}$ Department of Physics, Grinnell College, 1116 8th Ave., Grinnell, 
	IA, 50112, USA 
}

\date{Accepted XXX; Received YYY; in original form ZZZ} 
\pubyear{2020}

\begin{document} 
\label{firstpage} 
\pagerange{\pageref{firstpage}--\pageref{lastpage}} 
\maketitle

\begin{abstract} 
We investigate the impact of stellar migration on galactic chemical evolution 
models, considering a handful of assumptions for the star formation history 
and time-dependence of radial migration based on a zoom-in, hydrodynamical 
N-body simulation of galaxy evolution. To this end, we extend the 
\texttt{Versatile Integrator for Chemical Evolution} (\texttt{VICE}), 
developing and making use of its~\texttt{milkyway} object, built to handle 
these models under a wide variety of assumptions. We find that models for the 
time-dependence of radial migration impact the type Ia supernova rate as a 
function of both time and radius, inducing significant variability. We 
demonstrate that this is a means with which young, $\alpha$-enhanced stars can 
arise naturally out of inside-out galaxy growth with stellar migration. We find 
that the observed age-[$\alpha$/Fe] relation is well-fit by an inside-out star 
formation history, while the age-[O/H] and age-[Fe/H] relations are well-fit by 
a late starburst model; no one model investigated here fits both 
simultaneously. Lastly, we find that none of our models predict an 
[$\alpha$/Fe] dichotomy resembling that observed in the Milky Way. This 
suggests that inside-out galaxy growth combined with radial migration, even 
with a late starburst, is not conducive to forming the infamous bimodality. 
We postulate that more dramatic evolutionary events (e.g. a two-infall model) 
are necessary to describe the observed results.~\texttt{VICE} is publicly 
available at~\url{https://pypi.org/project/vice}. 
\end{abstract}

\begin{keywords} 
methods: numerical -- galaxies: abundances, evolution, star formation, stellar 
content 
\end{keywords}

\section{Introduction} 
\label{sec:intro} 
\begin{itemize} 
	\item The Age-Metallicity Relation (AMR) 
	\begin{itemize}

		\item Known for some time that stars undergo radial migration, 
		but to date there are only a handful of chemical evolution models that 
		take this into account~\citep{Wielen1996, Edvardsson1993, Sellwood2002, 
		Schoenrich2009, Minchev2013, Minchev2014, Minchev2017, Sharma2020}.

		\item Age-metallicity relation in the solar neighbourhood exhibits 
		considerable intrinsic scatter~\citep{Edvardsson1993}, usually 
		attributed to radial migration of metal-rich (metal-poor) stars formed 
		at smaller (larger) Galactocentric radii~\citep{Sellwood2002, 
		Haywood2008, Roskar2008b, Schoenrich2009}.

		\item \citet{Feuillet2018} reveal that super-solar metallicity stars 
		are statistically older than solar metallicity stars (their Fig. 3). 
		Contrasts with simple one-zone models where enrichment proceeds 
		alongside star formation yielding a monotonic 
		AMR~\citep[e.g.][]{Andrews2017, Weinberg2017}. One-zone models of 
		starbursts can produce non-monotonic AMR due to the effect of 
		dilution~\citep{Johnson2020}, but they by construction do not predict 
		multiple abundances at fixed age. 
	\end{itemize}

	\item The Young Alpha-Rich Population 
	\begin{itemize} 
		\item Population of young ($\sim$few Gyr), [$\alpha$/Fe]~$\sim$ 
		0.1-0.2 stars in the solar neighbourhood.

		\item Found using stellar ages estimated carbon-to-nitrogen 
		ratios~\citep{Martig2016}, isochrone matching~\citep{Feuillet2018, 
		Feuillet2019}, and with the asteroseismic ages in the original APOKASC 
		catalog~\citep{SilvaAguirre2018, Pinsonneault2014}.

		\item \citet{Mor2019} infer a factor of~$\sim$2 enhancement in the 
		SFH of the Milky Way~$\sim$2 Gyr ago by comparing population synthesis 
		models to observed stellar luminosity functions and color-magnitude 
		diagrams from Gaia data~\citep{GaiaDR2}.~\citet{Isern2019} reach 
		similar conclusions by modeling the white dwarf luminosity function in 
		the solar neighbourhood with Gaia parallaxes. Motivated by these 
		results, \citet{Johnson2020} demonstrate using one-zone chemical 
		evolution models that a recent starburst can produce young, 
		$\alpha$-enhanced stars. Caveat: burst would have had to be 
		sufficiently localized such that the young,~$\alpha$-rich stars remain 
		outliers from an otherwise monotonically descreasing age-[$\alpha$/Fe] 
		relation. 
	\end{itemize}

	\item The [$\alpha$/Fe] bimodality 
	\begin{itemize} 
		\item Milky Way stars segregate themselves into the low- and 
		high-$\alpha$ sequences, a bimodality found in, e.g., 
		Gaia ESO~\citep{Recio-Blanco2014, Rojas-Arriagada2017}, and 
		APOGEE~\citep{Nidever2014, Hayden2015, Weinberg2019}.

		\item Presence is well established, though origin a topic of intense 
		debate.

		\item Notion that it could arise out of radial migration traces back 
		to~\citet{Schoenrich2009}.

		\item \citet{Weinberg2017} models suggest increase in strength of the 
		mass-loading factor $\eta$ at late times would lower the equilibrium 
		abundance, forming stars along the low-$\alpha$ sequence. This plus 
		radial migration is yet unexplored.

		\item \citet{Spitoni2019} demonstrate that two-infall models can 
		reproduce solar annulus data with good agreement. This plus 
		radial migration is yet unexplored.

		\item \citet{Grand2018} find with Auriga~\citep{Grand2017} that early, 
		accretion induced starburst populates the high-$\alpha$ sequence, 
		followed by low-level, sustained star formation on low-$\alpha$ 
		sequence, and a rapid transition between the two ensures chemical space 
		relatively unpopulated. This would imply short $\tau_\star$ (see 
		justification in~\citealp{Weinberg2017}). Ongoing, low-metallicity 
		gas accretion can also populate low-$\alpha$ sequence.~\citet{Buck2020b} 
		find results qualitatively similar to second scenario in NIHAO 
		simulation suite~\citep{Wang2015, Buck2020a}. Hydrodynamical 
		simulations take into account radial migration by construction.

		\item \citet{Clarke2019} show that star formation proceeded in clumps 
		in an SPH simulation of an NFW halo using GASOLINE~\citep{NFW1997, 
		Wadsley2017}. The clumps self-enrich, forming stars on the 
		high-$\alpha$ sequence, while more spatially extended, smooth star 
		formation populated the low-$\alpha$ sequence.

		\item No shortage of models that reproduce the dichotomy, yet only 
		those done with hydrodynamical simulations and a handful of others 
		have taken into account radial migration. 
	\end{itemize}

\end{itemize}

\section{Data and Methods} 
\label{sec:methods}

\begin{itemize} 
	\item This paper is meant to address the simple question of: ``When 
	combining simple, realistic assumptions about the star formation and 
	dynamical histories of the Milky Way, what observed results can be 
	replicated?'' 
\end{itemize}

\subsection{Multi-Zone models} 
\label{sec:methods:multizone} 
\begin{itemize} 
	\item Multizone models are a means of extending traditional one-zone 
	models to take into account the motions of stars and gas by allowing the 
	exchange of both between zones.

	\item Qualitatively similar approach in~\citet{Matteucci1989, 
	Schoenrich2009, Minchev2013}.

	\item \texttt{VICE} released in~\citet{Johnson2020}, presented first 
	results from~\texttt{singlezone} object. Develop the~\texttt{multizone} 
	object and the~\texttt{milkyway} extension of that, and make use of them 
	here.~\texttt{multizone} simply provides an array of~\texttt{singlezone} 
	objects and allows the exchange of gas and individual stellar populations 
	between any two zones at any given simulation time.~\texttt{milkyway} 
	forces an annular model, where here we take a width of 100 pc, and 
	adopts by default the migration scheme discussed in the next subsection.

	\item Don't go into gory detail here, but provide a brief summary 
	of~\texttt{VICE}'s algorithm. Further details can be found in the 
	science documentation. 
	\begin{itemize} 
		\item At it's core, the~\texttt{multizone} object is an array 
		of~\texttt{singlezone} objects, each with its own ISM mass, star 
		formation rate, and infall rate.~\texttt{multizone} migration 
		prescriptions describe how gas and stars move between zones. Gas can be 
		moved between any pair of zones according to user-constructed functions 
		of time. Stars are stand-ins for entire stellar populations, and the 
		user has full control over what zone every single stellar population 
		is in at every single timestep. This should allow arbitrarily complex 
		zone schema to be implemented. Hydrodynamical simulations form varying 
		numbers of star particles of fixed mass, but~\texttt{VICE} forms a 
		fixed number of stellar populations per zone per timestep, each with a 
		mass that is simply~$\dot{M}_\star\Delta t / n$ where~$\dot{M}_\star$ 
		is the star formation rate, $\Delta t$ is the timestep size, 
		and~$n$ is the number of stellar populations per zone per timestep.

		\item \texttt{milkyway} object extends the~\texttt{multizone} object 
		and assumes an annular zone configuration, automatically adopting the 
		migration schema from this paper as a default. There is thus a fixed 
		number of stellar populations per annulus per timestep. 
	\end{itemize} 
\end{itemize}

\subsection{Radial Migration} 
\label{sec:methods:migration} 
\begin{itemize} 
	\item Algorithm based on initial and final radii of star particles in 
	hydrodynamical simulations.

	\item Stellar populations assumed to be born at centres of their annuli. 
	For a stellar population born at time $T$ and Galactocentric radius 
	$R_\text{gal}$,~\texttt{VICE} searches for star particles formed at 
	$T \pm$ 300 Myr and $R_\text{gal} \pm$ 250 pc. It then randomly selects 
	a star particle from this subsample with no bias to act as 
	an~\textit{analog}. Adopts the final radius of the star particle at face 
	value, and moves from its radius of birth to the final radius at $T$ = 
	12.7 Gyr with some time dependence. If no candidate analogs are found, 
	search is widened to $T \pm$ 600 Myr and $R_\text{gal} \pm$ 500 pc. If 
	still no candidate analogs are found in this widened search, the stellar 
	population is assumed to remain at its birth radius {\color{red} and to 
	have a final height above the disk midplane of $z$ = 100 kpc.} These 
	stellar populations are few in number. 
	\begin{itemize} 
		\item We have zones only for each annulus from $R_\text{gal}$ = 0 to 
		20 kpc; there are no zones off the midplane, retaining the assumption 
		that the gas-phase abundances are vertically well mixed as well as 
		azimuthally. Each stellar population simply assumes the final height 
		$\left|z\right|$ of its assigned analog, though this doesn't enter 
		into the simulations at all; it's purely post-processing information. 
	\end{itemize}

	\item When a star particle is assigned as an analog to a stellar 
	population in our simulations, it is~\textit{not} thrown out of the sample 
	of candidate analogs, allowing star particles to in theory act as analogs 
	for multiple stellar populations. This is a difference between 
	the~\citet{Minchev2013} model and ours.

\begin{figure} 
\centering 
\includegraphics[scale = 0.45]{migration.pdf} 
\caption{A diagram illustrating how Galactocentric radius changes with time 
for three stellar populations under our migration schema: diffusion (crimson, 
solid), linear (lime, dot-dashed), post-process (black, dotted), and 
sudden (blue, dashed). Here the initial and final radii and birth times are 
pseudorandom numbers drawn from a uniform distribution for illustrative 
purposes. With the initial and final Galactocentric radii of a stellar 
population, its birth time, and one of these assumptions about the 
time-dependence of migration, the Galactocentric radius at all times is 
known. } 
\label{fig:migration_schema} 
\end{figure}

	\item Our migration models 
	\begin{itemize} 
		\item All neglect radial gas flows, this paper instead focusing on 
		four simple models for how the radius of a stellar population's orbit 
		changes with time. Investigation of our models with radial gas flows 
		would be an interesting extension to this paper.

		\item \textbf{Post-processing}: Stars stay where they are born until 
		the final timestep. Based on the assumption that stellar populations 
		do not contribute to enrichment beyond their birth 
		radius~\citep[e.g.][]{Minchev2013}. Each annulus simulated as a 
		one-zone model independent of all other zones. Shown in black dotted 
		line in Fig.~\ref{fig:migration_schema}.

		\item \textbf{Sudden}: A random number is drawn from a uniform 
		distribution between the time of birth and the present day. That time 
		is taken to be the time of instantaneous migration ot the present-day 
		annulus. Emulates a scenario in which a single dynamical interaction 
		changes the orbital radius of a star. Can be thought of as a 
		time-dependent extension of the post-processing scenario. Shown in 
		blue dashed line in Fig.~\ref{fig:migration_schema}.

		\item \textbf{Diffusion}: Continuous, time-dependent migration with a 
		$\sqrt{\text{age}}$ dependence. Emulates a scenario in which angular 
		momentum diffuses throughout the disk via a random walk, in which 
		case the mean displacement of a star from its birth radius would 
		scale with $\sqrt{t}$. Shown in red solid line in 
		Fig.~\ref{fig:migration_schema}.

		\item \textbf{Linear}: A simple time-dependent variation of the 
		diffusion model. Has no physical motivation other than numerical 
		ease, but together with the diffusion model constitutes a test of how 
		sensitive our models are to the assumed time-dependence of radial 
		migration. Demonstrated by green dot-dashed line in 
		Fig.~\ref{fig:migration_schema}. 
	\end{itemize} 
\end{itemize}

\subsection{The Hydrodynamical Simulation} 
\label{sec:methods:h277}

\begin{figure} 
\centering 
\includegraphics[scale = 0.32]{birth_final_radii_pdfs.pdf} 
\caption{Distributions of~\texttt{h277} star particles in their birth (left) 
and final (right) Galactocentric radii. Distributions are shown for thin 
disk (crimson), thick disk (blue), bulge (black), and pseudobulge (lime) 
populations according to the kinematic decomposition described in~\S~X. 
In the right-hand panel we denote the number of star particles in each 
population according to the same color-coding. {\color{red} I cut off 
$R_\text{Form}$ at 15.5 kpc in my reduction from Jon's file of star 
particles. Extend it to 20 kpc, just for the sake of having candidate analogs 
out there for future papers? We can still cut off star formation here at 
15.5 kpc, so any stars that form out there and migrate inward will have zero 
mass and thus no effect, but maybe worth it for showing the distributions. 
I'd only have to change one line of code and rerun things. }} 
\label{fig:h277_birth_final_radii_pdfs} 
\end{figure}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{decomposition2.pdf} 
\caption{Radial distributions of our candidate analog star particles 
from~\texttt{h277}. In the top row, we show distributions of~\textit{birth} 
radius in bins of final radius and age. In the bottom row, we show 
distributions of~\textit{final} radius in bins of birth radius and age. Each 
bin in Galactocentric radius is shown in its own panel, denoted in text at the 
top the panels and by vertical black dashed lines. We color-code the 
distributions according to the age of the star particles and the legend in the 
upper left panel. We smooth all distributions with a box-car width of 0.5 kpc 
to improve clarity. We omit the distributions for 8 - 10 Gyr old stars born in 
the 9 - 11 and 11 - 13 kpc bins due to an insufficient number of star particles 
with which to calculate the distribution. }
\label{fig:h277_decomposition} 
\end{figure*}

\begin{itemize} 
	\item In this paper we take~\texttt{h277}~\citep{Christensen2012, 
	Zolotov2012, Loebman2012, Loebman2014, Brooks2014}. Its data and our 
	migration schema are built directly into~\texttt{VICE}'s~\texttt{milkyway} 
	object as defaults for ease of use. A synopsis of the simulation parameters 
	can be found in~\S~2 of~\citet{Bird2020}.

	\item Find that~\texttt{h277} has only a small fraction of star 
	particles born in the first 1 Gyr of its 13.7 Gyr run, so $T$ = 1 Gyr 
	is a much better estimate of the onset of star formation than 
	$T$ = 0 Gyr. Chop off the star particles born in the first Gyr of 
	evolution, and subtract 1 Gyr from their formation times, thus running 
	disk models for 12.7 Gyr.

	\item Of particular importance to have accurately measured formation radii 
	for each star particle that we use as candidate analogs as discussed 
	in~\S~\ref{sec:methods:migration}.~\texttt{h277} did not record the 
	exact birth radius of each star particle; however, each star particle does 
	have an accurate age at each snapshot. Therefore, one has a reasonable 
	approximation of the birth radius of each star particle that is 
	sufficiently young in the first snapshot in which it was recorded. 
	Therefore, we restrict our sample of candidate analogs to those with an 
	age at first snapshot of~$\leq$ 150 Myr, and adopt their Galactocentric 
	radius at first snapshot as the birth radius. Also conducted the analysis 
	with age at first snapshot of~$\leq$50 Myr, and found similar results, 
	suggesting this choice does not impact our conclusions. In practice find 
	that 150 Myr also provides us with an adequately large number of star 
	particles to sample analogs from, such that our predicted abundance 
	distributions in various Galactic regions are not limited by stellar 
	population counts (in particular far off the plane).

	\item Excluding halo stars, but including bulge, pseudobulge, and thin- 
	and thick-disk stars yields sample of 3,019,521 candidate analog star 
	particles. Included those because it's likely the majority formed within 
	a reasonably spatially confined region around the disk, suggesting they 
	contributed at least in part to its chemical evolution. 
	{\color{red} Expand on this: disk stars are only about 45\% of the total 
	sample, so our simulations run with~$\sim$1.5 million stellar populations 
	with assigned analogs to avoid oversampling. Plot distributions of 
	initial and final radii. }

	\item Can be thought of as adopting the dynamical history of~\texttt{h277} 
	in our disk models. Advantage to this approach is that we get a migration 
	model with no free parameteres.~\citet{Minchev2013} adopts similar 
	approach with a hydrodynamical simulation, but did not investigate 
	time-dependent migration.~\citet{Schoenrich2009} did investigate 
	time-dependent migration, though their algorithm was based on dynamical 
	arguments rather than a hydrodynamical simulation, and required fitting 
	to observed data, for which they employed the Geneva-Copenhagen Survey of 
	solar neighbourhood stars~\citep{Nordstroem2004b, Holmberg2007}. We're 
	unaware of any studies to date which employ a hydrodynamical simulation 
	to drive radial migration while simultaneously allowing stars to 
	contribute to enrichment beyond their birth radius.

	\item \texttt{h277} had a transient bar during its evolution, but does 
	not have a bar at $z$ = 0. This could mean that the star particles 
	in~\texttt{h277} migrated in a manner which does not reflect the dynamical 
	history of the Milky Way, but at present inferring a star's birth radius 
	observationally is notoriously difficult anyway ({\color{red} citation 
	needed}), so its likely the impact of this decision is within current 
	observational uncertainties. Nonetheless, it is worth noting that 
	the~\citet{Minchev2013} model, and by extension the~\citet{Minchev2014} 
	and~\citet{Minchev2017} models as well, selected a hydrodynamical 
	simulation specifically so that it would have a bar at $z$ = 0. A detailed 
	investigation of the impact of bar evolution on radial migration and thus 
	chemical evolution is outside the scope of this paper, though can be 
	conducted by simply swapping the birth times and initial and final radii 
	of~\texttt{h277} within~\texttt{VICE} and rerunning the simulations.

	\item Distributions of birth radii in bins of final radii and age are 
	shown in the top row of Fig.~\ref{fig:h277_decomposition}. Conversely, the 
	bottom row shows distributions of final radii in bins of birth radii and 
	age. 
	\begin{itemize} 
		\item Focusing on the top row of panels in 
		Fig.~\ref{fig:h277_decomposition}, we note that the oldest stars at any 
		Galactocentric radius at the present day were overwhelmingly born at 
		smaller radii. The youngest stars, however, were overwhelmingly born at 
		that radius, and the stars of intermediate ages simply span the range 
		in radii between the two. With increasing radius, the differences in 
		the mode of the birth radius distribution between age bins gets larger.

		\item Focusing on the bottom row of panels in 
		Fig.~\ref{fig:h277_decomposition}, we note that for stars born at any 
		radius and time, the distribution of final radii is still peaked near 
		the birth radius. With increasing age, it appears the mode final radius 
		may move slightly inward. The tails of the distributions to large radii 
		are relatively age-independent - some differences between the 0 - 2 and 
		8 - 10 Gyr age bins, but not much. However, the tails of the 
		distributions to small radii are not age-independent, and move toward 
		smaller $R_\text{gal}$ with increasing age. This suggests that radial 
		migration inward and outward occur on different timescales, in 
		particular that inward migration occurs on longer timescales than 
		outward migration. By extension this may suggest that inward and 
		outward migration are tied to different physical 
		processes.~\citet{Roskar2008a} demonstrate using a cosmological 
		simulation that resonant scattering at corotation causes stars to 
		move outward and gas to move inward. It's possible that radial 
		migration inward is has different origins.

		\item The differences in distributions shown in the top and bottom 
		panels boils down to stellar surface density being a strong function 
		of Galactocentric radius. Take for example the age = 8 - 10 Gyr bin in 
		both $R_\text{Birth}$ = 5 - 7 kpc and $R_\text{Final}$ = 11 - 13 kpc 
		bins (i.e. the red curves in the bottom-left and top-right panels). 
		For these old stars born at 5 - 7 kpc, 11 - 13 kpc is far down the tail 
		of the $R_\text{Final}$ distribution, and yet 5 - 7 kpc is the mode 
		$R_\text{Birth}$ of all old stars presently at these radii. This is 
		only possible if the stellar surface density gradient is sufficiently 
		steep, which it is known to be~\citep[e.g.][]{Bland-Hawthorn2016}. 
		\begin{itemize} 
			\item Fig.~\ref{fig:h277_decomposition} also demonstrates that the 
			numbers of stars that migrated inward and outward are comparable 
			in~\texttt{h277}. Taking a~$\left|\Delta R_\text{gal}\right| \geq$ 
			500 pc between birth and final radii as the criterion for migrating 
			inward or outward, indeed we find that in our sample of candidate 
			analogs, 27\% migrated inward, 29\% migrated outward, and the 
			remaining 44\% stayed near their birth radius. 
		\end{itemize}

		\item In all bins of birth radius, a good first-order estimate of the 
		probability density that a star has a final radius in the same bin 
		is~$\sim$0.2 - 0.3. With bins in radius on this plot of 2 kpc, that 
		suggests that 40 - 60\% of stars migrate significantly beyond their 
		birth radius by the time they're~$\sim$2 Gyr old. If the SN Ia DTD is a 
		$t^{-1.1}$ power-law as suggested by recent 
		observations~\citep[e.g.][]{Maoz2012, Maoz2017}, then we expect similar 
		numbers of SN Ia events to occur with delay times between 1 and 10 Gyr 
		as we do between 100 Myr and 1 Gyr. With such an extended DTD, and the 
		distributions in final radius shown in the bottom panel of 
		Fig.~\ref{fig:h277_decomposition}, its possible that white dwarfs 
		migrate significant distances before producing a SN Ia event. This is 
		the motivation for our test of whether or not the radial migration of 
		nucleosynthetic yields is a statistically significant effect. 
	\end{itemize} 
\end{itemize}

\subsection{Nucleosynthetic Yields} 
\label{sec:methods:yields} 
\begin{itemize} 
	\item Brief background on~\texttt{VICE}'s algorithm: we form a given 
	number of stellar populations in each zone and at each timestep. They 
	then migrate between zones according to our algorithm and eject CCSN and 
	SN Ia products as smooth functions of time according to our yields.

	\item \textit{Fractional net} yields, as required by~\texttt{VICE}.

	\item Take our yields from~\citet{Weinberg2017} and~\citet{Johnson2020}. 
	Find that our models with these yields predict [O/Fe] $\approx$ +0.05 for 
	zero age stars, so we multiply SN Ia Fe yield by $10^{0.1}$ to produce 
	more realistic late-time [O/Fe]. This is likely within the uncertainties 
	in nucleosynthetic yields.

	\item CCSN products injected immediately, and thus unaffected by 
	migration: 
	\begin{equation} 
	\dot{M}_x^\text{CC} = y_x^\text{CC}\dot{M}_\star 
	\end{equation}

	\item SN Ia products injected with a $t^{-1.1}$ DTD, with minimum delay 
	$t_\text{D}$ = 150 Myr. 
	\begin{equation} 
	\dot{M}_x^\text{Ia} = y_x^\text{Ia} \sum_i M_i R_\text{Ia}(\tau_i) 
	\end{equation} 
	where the summation is taken over all stellar populations in a given zone, 
	and $M_i$ and $\tau_i$ denote the mass and age of the $i$'th stellar 
	population in a given zone at a given time. The SN Ia rate $R_\text{Ia}$ 
	is normalized such that the integral over the time interval from 
	$t_\text{D}$ to a maximum time of 15 Gyr is equal to one.

	\item We include AGB star enrichment according to the FRUITY database net 
	yields~\citep{Cristallo2011}, though these yields are not significant 
	compared to the CCSN and SN Ia yields for O and Fe. Our results can be 
	interpreted as if they were zero. Algorithm is based on 
	calculating the mass in dying stars from previously formed stellar 
	populations at each timestep, details can be found in~\citet{Johnson2020} 
	and in~\texttt{VICE}'s science documentation\footnote{
		\url{https://vice-astro.readthedocs.io/en/latest/science_documentation/enrichment/index.html} 
	}.

	\item \citet{Minchev2013} adopt much lower nucleosynthetic yields, 
	because they don't have outflows. Discuss differences in how we obtain the 
	late-time metallicity gradient either here or at the end 
	of~\S~\ref{sec:methods:outflows}. 
\end{itemize}

\subsection{Outflows} 
\label{sec:methods:outflows}

\begin{figure} 
\centering 
\includegraphics[scale = 0.45]{eta.pdf} 
\caption{Our implemented scaling of the mass loading factor $\eta$ with 
Galactocentric radius (black) as defined by equation~\refp{eq:eta}. The 
horizontal and vertial red dashed lines highlight the value of $\eta \approx$ 
1.7 at an assumed orbital radius of the sun of $R_\odot$ = 8 kpc. } 
\label{fig:eta} 
\end{figure}

\begin{itemize} 
	\item $\eta \equiv \dot{M}_\text{out}/\dot{M}_\star$

	\item Implement a scaling of $\eta$ with $R_\text{gal}$ such that a 
	realistic metallicity gradient is produced at late times. A fundamental 
	observable, the observed metallicity gradient in the Milky Way has been the 
	focus of a considerable number of studies to date. 
	\begin{itemize} 
		\item \citet{Nordstroem2004a} find a gradient of -0.099 kpc$^{-1}$ in 
		[Fe/H] in main sequence stars from GCS~\citep{Nordstroem2004b, 
		Holmberg2007}.

		\item \citet{Daflon2009} find a gradient of -0.04 kpc$^{-1}$ in 
		[S/H] in OB stars

		\item \citet{Frinchaboy2013} find a gradient of -0.09 kpc$^{-1}$ in 
		[M/H] in open clusters.

		\item \citet{Hayden2014} also find -0.09 kpc$^{-1}$ in [M/H] for 
		$R_\text{gal}\gtrsim$ 6 kpc for low-$\alpha$ stars. For 
		$R_\text{gal}\lesssim$ 6 kpc, they find a relatively flat gradient.

		\item \citet{Weinberg2019} finds -0.06 kpc$^{-1}$ in mode([Mg/H]) for 
		upper red giant branch disk stars (see their Fig. 23). 
	\end{itemize}

	\item The procedure outlined in this section reproduces the metallicity 
	gradient while neglecting the impact of radial migration. We demonstrate 
	in~\S~\ref{sec:gradients:metallicity} that this assumption holds in our 
	simulation outputs which do take it into account.

	\item Our recipe for ensuring a reasonable gradient hinges on the 
	assumption that the mode [X/H] for any given element $x$ at any given 
	radius $R_\text{gal}$ reflects the equilibrium abundance of that element at 
	that radius.

	\item For $\alpha$ elements,~\citet{Weinberg2017} defines the equilibrium 
	abundance under a constant SFH as: 
	\begin{equation} 
	Z_{\alpha,\text{eq}} = \frac{y_\alpha^\text{CC}}{1 + \eta(R_\text{gal}) - r} 
	\end{equation} 
	where $\eta$ is the mass-loading factor at that radius $R_\text{gal}$, and 
	$r$ is the recycling parameter ($\approx$ 0.4 for the sake of this 
	scaling with a~\citetalias{Kroupa2001} IMF;~\citealp{Weinberg2017}). 
	Solving for $\eta(R_\text{gal})$ yields: 
	\begin{equation} 
	\eta(R_\text{gal}) = \frac{y_\alpha^\text{CC}}{Z_{\alpha,\text{eq}}} + r - 1 
	= \frac{y_\alpha^\text{CC}}{Z_{\alpha,\odot}}10^{-\text{mode([X/H])}
	(R_\text{gal})} + r - 1 
	\end{equation}

	\item We assume a slope of -0.08 kpc$^{-1}$, in tentative agreement with 
	the previous studies that quote the slope of the gradient mentioned above. 
	To set the normalization, we assume the mode([X/H]) to be~$\sim$+0.3 at 
	$R_\text{gal}$ = 4 kpc, since this would produce mode([X/H])~$\approx$~0 at 
	$R_\text{gal}\approx$ 7 - 9 kpc. This results in the following form for 
	$\eta$ as a function of Galactocentric radius: 
	\begin{equation} 
	\eta(R_\text{gal}) = \frac{y_\alpha^\text{CC}}{Z_{\alpha,\odot}} 
	10^{(-0.08\text{ kpc}^{-1})(R_\text{gal} - \text{4 kpc}) + 0.3} + r - 1 
	\label{eq:eta} 
	\end{equation}

	\item This does assume a uniformly linear gradient at all $R_\text{gal}$. 
	\citet{Hayden2014} do find the gradient in [M/H] to flatten for 
	$R_\text{gal}\lesssim$ 6 kpc, challenging this assumption. However, this 
	procedure can be easily repeated for any desired gradient, since the 
	functional form simply goes into the power of 10 in equation~\refp{eq:eta}.

	\item Model based on assumption that observed mode([$\alpha$/H]) as a 
	function of Galactocentric radius reflects the equilibrium $\alpha$ 
	abundance at each radius (i.e. mode([$\alpha$/H]) = 
	$\log_{10}(Z_{\alpha,\text{eq}}/Z_{\alpha,\odot})$)

	\item We adopt our yield of O for $y_\alpha^\text{CC}$ and the solar 
	abundance of O of $Z_{\text{O},\odot}$ = 0.00572 from~\citet{Asplund2009}.

	\item Fig.~\ref{fig:eta} plots this scaling of~$\eta$ with~$R_\text{gal}$, 
	highlighting the value for the solar circle.

	\item \citet{Minchev2013} did not include outflows in their model, and as 
	such have much lower yields. Discuss differences in how we obtain the 
	late-time metallicity gradient either here or at the end 
	of~\S~\ref{sec:methods:yields}. 
\end{itemize}

\subsection{Recycling} 
\label{sec:methods:recycling} 
\begin{itemize} 
	\item As mentioned in~\S~\ref{sec:methods:yields}, we're using~\textit{net} 
	rather than~\textit{gross} yields. Our yields thus only quantify the amount 
	of~\textit{newly produced} metals from each stellar population, and the 
	return of previously produced material must be taken into account.

	\item \citet{Weinberg2017} defined the~\textit{cumulative return fraction}
	$r$ to be the fraction of a single stellar population's initial mass that 
	has been returned to the ISM. In detail, $r$ is a complicated function of 
	the age of a stellar population $\tau$ which depends on the assumptions 
	about stellar lifetimes, the IMF, and an initial-remnant mass 
	relation~\citep[e.g.][]{Kalirai2008}. 
	\begin{itemize} 
		\item \citet{Weinberg2017} demonstrated that the assumption 
		of~\textit{instantaneous recycling} is a reasonable approximation, 
		where instantaneous recycling refers only to previously produced 
		material, contrary to what most people mean when the refer to 
		instantaneous recycling. They show that $r$ = 0.4 (0.2) is a good 
		approximation for a~\citetalias{Kroupa2001} (\citetalias{Salpeter1955}) 
		IMF. However, this was demonstrated for smooth star formation histories 
		and in parameter spaces conducive to analytic solution. Because 
		numerical integration of $r(\tau)$ is neither challenging nor 
		time-consuming,~\texttt{VICE} by default implements continuous recycling 
		by solving $r(\tau)$ at the beginning of each simulation given the 
		IMF, the~\citet{Kalirai2008} initial-remnant mass model, and the 
		assumption that $\tau = \tau_\odot(M/M_\odot)^{-3.5}$. We also assume 
		a post-main sequence lifetime of 10\% of the main sequence lifetime for 
		all stars. 
	\end{itemize}

	\item The detailed form the recycling rate in a given annulus and at a 
	given time is: 
	\begin{equation} 
	\dot{M}_x^\text{r} = \sum_i Z_{x,i} M_i \dot{r}(\tau_i) 
	\end{equation} 
	where $M_i$ is the mass of the $i$'th stellar population in the annulus, 
	$\tau_i$ is its age, $Z_{x,i}$ is its birth abundance of some element $x$, 
	and the summation is taken over all stellar populations in the annulus at 
	that time.

	\item We implement continuous recycling in our simulations, but at a number 
	of places in analyzing their results here, we adopt the instantaneous 
	approximation for ease. 
\end{itemize}

\subsection{Star Formation Histories} 
\label{sec:methods:sfhs}

\begin{figure} 
\centering 
\includegraphics[scale = 0.45]{tau_sfh.pdf} 
\caption{The e-folding timescales of star formation as reported 
by~\citet{Sanchez2020} for $10^{10.5}$ - $10^{11}$ M$_\odot$ Sa/Sb Hubble type 
galaxies (black), assuming a half-light radius of $R_\text{e}$ = 5 kpc and the 
mathematical form of our inside-out SFH (see equation~\refp{eq:insideout_sfh}). 
The red dotted lines highlight $\tau_\text{sfh}~\approx$ 15 Gyr at an assumed 
radius of the sun of $R_\odot$ = 8 kpc. }
\label{fig:tau_sfh}
\end{figure}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{sfh.pdf} 
\caption{The surface densities of star formation $\dot{\Sigma}_\star$ (top 
row), infall $\dot{\Sigma}_\text{in}$ (middle row), and gas $\Sigma_\text{gas}$ 
(bottom row) as functions of simulation time for our four fiducial SFHs: 
constant (far left), inside-out (left middle), late-burst (right-middle), 
and outer-burst (far right). We plot curves for the annuli whose inner radii 
are 3 kpc (grey), 5 kpc (black), 7 kpc (red), 9 kpc (yellow), 11 kpc (green), 
13 kpc (blue), and 15 kpc (purple) (see equations~\refp{eq:constant_sfh}, 
\refp{eq:insideout_sfh},~\refp{eq:lateburst_sfh}, and~\refp{eq:outerburst_sfh} 
for the mathematical definition of each SFH). } 
\label{fig:evol} 
\end{figure*}

\begin{itemize} 
	\item Appendix~\ref{sec:normalize_sfh} presents justification of how we 
	normalize our parameters to produce a realistic Milky Way at the end of 
	the simulation. In short, it takes in a unitless description of the 
	time-dependence of the SFH at a given Galactocentric radius, denoted 
	$f(t|R_\text{gal})$, and a unitless description of the radial dependence of 
	the present-day stellar surface density, denoted $g(R_\text{gal})$. 
	Neglecting radial migration, it then integrates $f(t|R_\text{gal})$ at each 
	radius with time and $g(R_\text{gal})$ over the area of the disk to ensure 
	that the correct present-day stellar mass and desired surface density 
	gradient $\Sigma_\star$ are produced by the simulation. This recipe hinges 
	on the assumption that radial migration does not significantly alter the 
	form of $\Sigma_\star$, which we demonstrate 
	in~\S~\ref{sec:gradients:density} to be the case under our model and 
	for~\texttt{h277}'s dynamical history. As long as this assumption isn't 
	violated, this recipe can be used.

	\item Adopt the~\citet{Licquia2015} total stellar mass of 
	$(6.08\pm1.14)\times10^{10}~M_\odot$. We're including bulge star particles 
	in our sample of candidate analogs from~\texttt{h277}, so we model the 
	entire stellar mass as opposed to just the disk, for 
	which~\citet{Licquia2015} found $(5.17\pm1.11)\times10^{10}~M_\odot$.

	\item Take the gradient from~\citet{Bland-Hawthorn2016}, which characterize 
	the disk as a double exponential - the sum of two single exponentials 
	representing the thin and thick disks. This has the following form: 
	\begin{equation} 
	g(R_\text{gal}) = e^{-R_\text{gal}/r_\text{t}} + 
	\frac{\Sigma_\text{T}}{\Sigma_\text{t}}e^{-R_\text{gal}/R_\text{T}} 
	\end{equation} 
	where $r_\text{t}$ and $r_\text{T}$ are the scale radii of the thin and 
	thick disks, respectively, and $\Sigma_\text{T}/\Sigma_\text{t}$ is the 
	ratio of the surface densities to thin and thick disk stars at 
	$R_\text{gal}$ = 0. Based on the results of~\citet{Bland-Hawthorn2016}, we 
	take in this paper $r_\text{t}$ = 2.5 kpc, $r_\text{T}$ = 2.0 kpc, and 
	$\Sigma_\text{T}/\Sigma_\text{t}$ = 0.27.

	\item We present four fiducial SFHs, which we dub ``constant'', 
	``inside-out'', ``late-burst'', and ``outer-burst''. They're defined as 
	follows: 
	\begin{itemize} 
		\item \textbf{Constant}: The SFH at a given radius is time-independent. 
		\begin{equation} 
		f_\text{C}(t|R_\text{gal}) = 1 
		\label{eq:constant_sfh} 
		\end{equation} 
		This case is of particular theoretical interest because it quantifies 
		the effect of ongoing with star formation with radial migration, and 
		no additional effects.

		\item \textbf{Inside-Out}: 
		\begin{equation} 
		f_\text{IO}(t|R_\text{gal}) = (1 - e^{-t/\tau_\text{rise}})
		e^{-t/\tau_\text{sfh}} 
		\label{eq:insideout_sfh} 
		\end{equation} 
		We adopt this scenario over the traditional linear-times-exponential 
		form of $f(t|R_\text{gal})~\sim~te^{-t/\tau_\text{sfh}}$, because the 
		latter does not offer control over the position of the maximum. The 
		form we adopt has a maximum near $\tau_\text{rise}$, for which we adopt 
		a value 2 Gyr everywhere in this paper. We find that this produces a 
		peak in star formation at lookback times of~$\sim$10 Gyr, corresponding 
		to a redshift of~$z \approx$~2, which is around cosmic high noon. In 
		this paper $\tau_\text{sfh}$ is a function of $R_\text{gal}$ here, and 
		we discuss it briefly in a few paragraphs.

		\item \textbf{Late-Burst}: An inside-out SFH with a gaussian describing 
		a starburst. 
		\begin{equation} 
		f_\text{LB}(t|R_\text{gal}) = f_\text{IO}(t|R_\text{gal}) 
		(1 + A_\text{b}e^{-(t - t_\text{b})^2/2\sigma_\text{b}^2}) 
		\label{eq:lateburst_sfh} 
		\end{equation} 
		$A_\text{b}$ is a dimensionless parameter describing the strength of 
		the starburst, $t_\text{b}$ is the time of the local maximum in the SFH 
		during the burst, and $\sigma_\text{b}$ is the width of the gaussian 
		describing it. Loosely motivated by the findings of~\citet{Isern2019} 
		and~\citet{Mor2019}. Here we take $A_\text{b}$ = 1.5, $t_\text{b}$ = 
		10.8 Gyr, and $\sigma_\text{b}$ = 1 Gyr.

		\item \textbf{Outer-Burst}: A variation of the late-burst model in 
		which only $R_\text{gal}\geq$ 6 kpc experience the starburst. Loosely 
		motivated by findings of~\citet{Vincenzo2020} where a hydrodynamical 
		simulation of a Milky Way-like galaxy showed radially dependent 
		infall. 
		\begin{equation} 
		f_\text{OB}(t|R_\text{gal}) = \begin{cases} 
		f_\text{IO}(t|R_\text{gal}) & (R_\text{gal}~<~\text{6 kpc}) \\ 
		f_\text{LB}(t|R_\text{gal}) & (R_\text{gal}~\geq~\text{6 kpc}) 
		\end{cases} 
		\label{eq:outerburst_sfh} 
		\end{equation} 
	\end{itemize}

	\item Derive e-folding timescales of star formation $\tau_\text{sfh}$ 
	from the data in~\citet{Sanchez2020}. 
	\begin{itemize} 
		\item They present the stellar surface density $\Sigma_\star$ as a 
		function of age in bins of $R/R_\text{e}$ for MaNGA galaxies, where 
		$R_\text{e}$ is the half-light radius. They conduct this analysis in 
		bins of stellar mass and for different Hubble types. Here take their 
		M$_\star$ = 10$^{10.5}$ - 10$^{11}$ M$_\odot$ bin for Sa/Sb spirals 
		(i.e. Milky Way-like galaxies).

		\item With our gradient, we know the present-day half-mass radius to be 
		very near 4 kpc (this is just doing a couple integrals over the area of 
		the disk). The findings of~\citet{Garcia-Benito2017} and 
		\citet{GonzalezDelgado2014} suggest that half-light radii are 
		marginally larger than half-mass radii. Based on equations (4) of 
		\citet{GonzalezDelgado2014} relation the two for circular apertures, 
		we expect our model galaxy to have a half-light radius near 5 kpc. We 
		therefore adopt $R_\text{e}$ = 5 kpc in calculating $\tau_\text{sfh}$ 
		as a function of radius. {\color{red} As I understand it, there are 
		some results that suggest this value for the Milky Way as well?}

		\item Their reported $\Sigma_\star$-age relation is not robust enough 
		to get individual SFHs directly, but does allow the parameters of some 
		fiducial mathematical model to be fit to the population-averaged data. 
		Assuming the $f_\text{IO}(t|R_\text{gal})$ form, we simultaneously fit 
		the normalization and the e-folding timescale $\tau_\text{sfh}$ to 
		these data. Although the normalization is irrelevant to our simulations 
		and determined via the method outlined in 
		Appendix~\ref{sec:normalize_sfh}, we adopt the resulting 
		$\tau_\text{sfh}$-$R_\text{gal}$ relation in our models. Results are 
		shown in Fig.~\ref{fig:tau_sfh}.

		\item Note that the star formation timescales are long, even for the 
		solar annulus ($\tau_\text{sfh} \approx$~15 Gyr at $R_\odot$ = 8 kpc) 
		and especially for the outer galaxy. Beyond the solar annulus, SFHs are 
		nearly constant after the initial rise at early times. 
	\end{itemize}

	\item Given the assumed star formation histories, the gas supply at all 
	times is known via the SFE timescale $\tau_\star$ (discussed 
	in~\S~\ref{sec:methods:sfe}). With the amount of gas lost to star formation 
	and outflows at each timestep, the infall rate is also known at all 
	timesteps. The results of all three are shown in Fig.~\ref{fig:evol}. 
\end{itemize}

\subsection{Star Formation Efficiency} 
\label{sec:methods:sfe}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{sfe.pdf} 
\caption{The star formation efficiency (SFE) timescale $\tau_\star$ as a 
function of Galactocentric radius at simulation times of 2 Gyr (red), 4 Gyr 
(yellow), 6 Gyr (green), 8 Gyr (blue), 10 Gyr (purple), and 12.7 Gyr (i.e. 
the present day, black) for our four fiducial SFHs: constant (left), inside-out 
(left-middle), late-burst (right-middle), and outer-burst (right). }
\label{fig:sfe} 
\end{figure*}

\begin{itemize} 
	\item The term ``star formation efficiency'' (SFE) is an overloaded term in 
	the literature. In the star formation/ISM literature, it usually refers to 
	the fraction of a molecular cloud's mass which will eventually be converted 
	into stars. In the chemical evolution literature, however, it usually 
	refers to the inverse timescale relating the star formation rate within 
	some gas reservoir and the mass of the gas reservoir itself: 
	$\tau_\star \equiv M_\text{gas}/\dot{M}_\star$. High (Low) values of 
	$\tau_\star$ indicate slow (fast) star formation and thus low (high) SFE; 
	when we refer to SFE here, we're referring to the definition based on this 
	timescale. 
	\begin{itemize} 
		\item Potentially note that this is often referred to as the 
		``depletion time'' in the ISM literature, and the~\citet{Weinberg2017} 
		definition of depletion 
		time:~$\tau_\text{dep} \equiv \tau_\star/ (1 + \eta - r)$.

		\item In our models, $\tau_\star$ increases with decreasing molecular 
		fraction: $\tau_\star = \tau_\star^\text{mol}/f_\text{mol}$, where 
		$\tau_\star^\text{mol}$ is the same parameter, but for gas that is 
		entirely H$_2$. We let it bottom out at this value because it's 
		believed that star formation proceeds in the molecular phase, although 
		there is significant scatter in the observed relation~\citep[e.g.][]{
		Leroy2008, Kennicutt2012, Tacconi2018}. 
	\end{itemize}

	\item Here we implement a modified Kennicutt-Schmidt Law~\citep{Schmidt1959, 
	Schmidt1963, Kennicutt1998} to describe the scaling of~$\tau_\star$ 
	with~$\Sigma_g$. Below some threshold density $\Sigma_{g,\text{Crit}}$, we 
	adopt a power-law with index $k$ = 0.5, based on the $N$ = 1.5 power-law 
	describing the~$\dot{\Sigma}_\star-\Sigma_g$ relation\footnote{
		$k = N - 1$~\citep{Johnson2020}. 
	}. Above this threshold, we assume the molecular fraction in the ISM to be 
	unity, and to form stars at the rate determined by $\tau_\star^\text{mol}$. 
	That is: 
	\begin{equation} 
	\tau_\star = \begin{cases} 
	\tau_\star^\text{mol}\left(\frac{\Sigma_g}{\Sigma_{g,\text{Crit}}}\right)^k 
	& (\Sigma_g \leq \Sigma_{g,\text{Crit}}) \\ 
	\tau_\star^\text{mol} & (\Sigma_g \geq \Sigma_{g,\text{Crit}}) 
	\end{cases} 
	\end{equation} 
	It's common in the chemical evolution literature to adopt a pure power-law 
	scaling of~$\tau_\star$ with~$\Sigma_g$; we adopt this alternate form with 
	a minimum value to ensure that the implied $\tau_\star$ is never below 
	$\tau_\star^\text{mol}$ at any redshift.

	\item Observationally,~$\Sigma_{g,\text{Crit}}$ is the surface density at 
	which the observed Kennicutt-Schmidt relation switches from quadratic to 
	linear.~\citet{Bigiel2008} present observed Kennicutt-Schmidt relations 
	from the HERACLES and BIMA surveys, and~\citet{Krumholz2018} presents a 
	compilation of Kennicutt-Schmidt relations observed by~\citet{Bigiel2010} 
	and~\citet{Leroy2013}. Both suggest that the value is at or around 
	$\sim10$~M$_\odot$~pc$^{-2}$ = $10^7$~M$_\odot$~kpc$^{-2}$. 
	{\color{red} In practice we find that this predicts a seemingly 
	unrealistically high ISM composition - $f_\text{mol}$ = 1 for 
	$R_\text{gal}\lesssim$ 6 kpc, so in this outline we've ran our simulations 
	with $\Sigma_{g,\text{Crit}} = 2\times10^7$~M$_\odot$~kpc$^{-2}$. 
	However, this did not solve the problem. We're still debating about what 
	prescription to use here, though the choice makes no difference in our 
	models. It's likely the final version of this paper will make a simple 
	assumption regarding star formation efficiency, and then demonstrate in 
	Appendix~\ref{sec:sfe_variations} that the impact is not significant. }

	% \item {\color{red} The following is not yet in this outline. The models 
	% included here are with $\Sigma_{g,\text{Crit}} = 2\times10^7$~M$_\odot$ 
	% kpc$^{-2}$. This value predicts a global $f_\text{mol}$ = 84\%, which is 
	% much higher than observations. In a subsequent version, there will be an 
	% appendix demonstrating the value of $\Sigma_{g,\text{Crit}}$ that predicts 
	% $f_\text{mol} \approx$~0.35. Based on my current estimates, it's somewhere 
	% around~$\sim5\times10^8$ M$_\odot$ kpc$^{-2}$. We've looked at models with 
	% $\Sigma_{g,\text{Crit}} = 10^8$~M$_\odot$~kpc$^{-2}$, and found similar 
	% conclusions, so we don't expect this parameter to have an impact, but we 
	% want to be presenting the most realistic galaxy in the main body of the 
	% paper. The appendix will likely also demonstrate that these variations are 
	% not impactful. }

	\item \citet{Tacconi2018} suggest that~$\tau_\star^\text{mol}$ should 
	scale with redshift~$z$ and the deviation from the star forming main 
	sequence~$\delta\text{MS}$ via~$\tau_\star^\text{mol} \propto (1 + z)^{-0.6} 
	\delta\text{MS}^{-0.44}$. We don't take into account the effect of 
	$\delta\text{MS}$ in our models, but we do investigate the redshift 
	dependence. A reasonable approximation to the $t-z$ relation out 
	to~$z \approx$~3 is: 
	\begin{equation} 
	\frac{t}{t_0} \approx (1 + z)^{-5/4} 
	\end{equation} 
	where $t_0$ is the present-day age of the universe, and $t$ is not 
	simulation time but the age of the universe at any given redshift. 
	Plugging this relation into the~\citet{Tacconi2018} scaling yields the 
	following time-dependence for~$\tau_\star^\text{mol}$: 
	\begin{equation} 
	\tau_\star^\text{mol} = \tau_{\star,0}^\text{mol}(t/t_0)^{12/25} \approx 
	\tau_{\star,0}^\text{mol}(t/t_0)^{1/2} 
	\end{equation} 
	where $\tau_{\star,0}^\text{mol}$ is simply $\tau_\star^\text{mol}$ at the 
	present day. We generalize this formula to the following form: 
	\begin{equation} 
	\tau_\star^\text{mol} = \tau_{\star,0}^\text{mol}(t/t_0)^\beta 
	\end{equation} 
	In this paper we present simulations which adopt~$\tau_{\star,0}^\text{mol}$ 
	= 2 Gyr and~$\beta$~= 1/2. We have however ran all possible combinations of 
	$\tau_{\star,0}^\text{mol}$ = 1 and 2 Gyr,~$\beta$~= 0 and 1/2, all four 
	of our fiducial SFHs, and all four migration models, a total of 64 
	simulations. Unless otherwise noted, we find similar results in all 
	dimensions except SFH.

	\item Fig.~\ref{fig:sfe} shows $\tau_\star$ as a function of $R_\text{gal}$ 
	at six different time stamps predicted by our fiducial models. 
	Wherever~$\tau_\star$ is at its minimum value is where the ISM is fully 
	molecular. 
	\begin{itemize} 
		\item From the actual value of $\tau_\star$ at a given radius and time 
		and the assumed $\tau_\star^\text{mol}$ in the model, we can derive 
		molecular fractions within the disk. In the models present here, 
		the disk is molecular out to~$R_\text{gal} \approx$~6 kpc in all models 
		at the present day. The inside-out SFH has a global molecular fraction 
		of~$f_\text{mol} \approx$~84\%. 
	\end{itemize} 
\end{itemize}

\subsection{Simulation Parameters} 
\label{sec:methods:simparams}

\begin{itemize} 
	\item \texttt{VICE}'s simulations runs in either infall, star formation, or 
	gas mode, referring simply to which one the user is specifying. The 
	fiducial starburst models presented in~\citet{Johnson2020} ran in infall 
	mode, but here we run things in star formation mode, since we are after 
	specific forms for the star formation histories of our models.

	\item We have a sample of 3,019,521 candidate analog star particles 
	from~\texttt{h277}, only~$\sim$57\% of which are disk stars. Since we're 
	modeling the thin and thick disk populations here,~$\sim$1.72 million is a 
	much better estimate of the number of analogs that we can realistically 
	sample from. We let star formation extend out to 15.5 kpc, beyond which 
	we force the star formation rate to zero at all times.~\texttt{VICE} does 
	form stellar populations at all timesteps in the annuli; they simply have 
	zero mass and thus do not contribute to the chemical evolution or recycling, 
	though they contribute to the computational overhead. With 200 zones and 
	1,271 timesteps, we let~\texttt{VICE} form~$n$ = 8 stellar populations per 
	zone per timestep, resulting in 2,033,600 stellar populations with 
	predicted masses and abundances, 1,565,872 of which form 
	between~$R_\text{gal}$ = 0 and 15.5 kpc, reasonably within the limit of 
	what we can sample. These simulations run in~$\sim$2 hours and take 
	up~$\sim$235 MB per output, including the extra data that we record for 
	each stellar population's analog star particle. 
	\begin{itemize} 
		\item To ensure that resolution does not affect our results, we ran the 
		same set of models with~$n$ = 2 stellar populations per zone per 
		timestep, and found similar predictions. 
	\end{itemize} 
\end{itemize}

\subsection{The Observed Sample} 
\label{sec:methods:observed_sample}

\begin{itemize} 
	\item For the age-metallicity and age-[$\alpha$/Fe] relations, we compare 
	to the results of~\citet{Feuillet2019}. Also compared 
	to~\citet{Feuillet2018}, the primary difference being that solar 
	metallicity stars are found to be considerably younger in the earlier 
	study.

	\item {\color{red} I pulled some of this information from David's 
	two-process paper, which used DR14. Let me know if any of the details of 
	APOGEE and the data reduction have changed since then. }
	Compare metallicity distribution functions to the 16th data release 
	(DR16;~\citealp{Ahumada2020}) of the Apache Point Observatory Galaxy 
	Evolution Experiment (APOGEE;~\citealp{Majewski2017}). A part of the Sloan 
	Digital Sky Survey (SDSS), APOGEE data is collected with a 300-fiber 
	H-band spectrograph~\citep{Wilson2020} on the 2.5-meter Sloan Foundation 
	telescope at Apache Point Observatory~\citep{Gunn2006}. The APOGEE sample 
	largely consists of evolved stars with 2MASS~\citep{Skrutskie2006} 
	magnitudes in the range 7 < $H$ < 13.8 sampled on a grid of sightlines 
	at Galactic latitudes $b$ = -8$^\circ$, -4$^\circ$, 0$^\circ$, +4$^\circ$, 
	and +8$^\circ$ and a wide range of longitudes. \citet{Nidever2015} 
	describes the data processing pipeline for APOGEE, providing the input to 
	the APOGEE Stellar Parameters and Chemical Abundances Pipeline (ASPCAP; 
	\citealp{Holtzman2015,GarciaPerez2016}). ASPCAP simultaneously fits 
	elemental abundances, effective temperatures, and surface gravities using a 
	grid of synthetic spectra predicted by 1-dimensional stellar atmospheric 
	models assuming local thermodynamic equilibrium~\citep{Meszaros2012, 
	Zamora2015} and the spectral line list provided in~\citep{Shetrone2015}. 
	{\color{red} (1-D LTE correct?)}

	\item While we make use of DR16 in comparing our predicted MDFs to the 
	APOGEE data,~\citet{Feuillet2018} and~\citet{Feuillet2019} made use of the 
	14th data release (DR14;~\citealp{Abolfathi2014}). We don't expect this 
	slight difference to impact our conclusions. 
\end{itemize}

\section{Gradients} 
\label{sec:gradients}

\begin{figure} 
\centering 
\includegraphics[scale = 0.45]{surface_density_gradient_timedep.pdf} 
\caption{The surface density of gas (blue) and stars (red) as predicted by our 
model with an inside-out SFH, diffusion migration, and 
$\tau_\star^\text{mol} = (\text{2 Gyr})(t/t_0)^{1/2}$. The dotted black lines 
denote the exponential fit to the thin- and thick-disk profiles reported 
by~\citet{Bland-Hawthorn2016}, with the black solid line denoting the sum of 
the two, all renormalized to imply the same total stellar mass within the 
disk. }
\label{fig:surface_density} 
\end{figure}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{metallicity_gradient.pdf} 
\caption{Radial abundance gradients in [O/H] (top, red) [Fe/H] (top, blue), 
and [O/Fe] (bottom) for our four fiducial SFHs - constant (far left), 
inside-out (left-middle), late-burst (right-middle), and outer-burst (far 
right). We plot the gas phase abundance at the present day as a function of 
Galactocentric radius in solid lines. Stars denote the mode of the stellar 
MDF of the 100-pc width annulus at a given radius, with shaded regions 
marking the 16th and 84th percentiles thereof. Black lines in the top panels 
denote our target [$\alpha$/H] gradient of mode([$\alpha$/H]) = +0.3 at 
$R_\text{gal}$ = 4 kpc with a slope of -0.06 kpc$^{-1}$. } 
\label{fig:metallicity_gradient} 
\end{figure*}

\subsection{Surface Density} 
\label{sec:gradients:density}

\begin{itemize} 
	\item SFH in each annulus normalized such that, neglecting radial 
	migration, a given gradient is reproduced (see 
	Appendix.~\ref{sec:normalize_sfh}). Here we've adopted a double 
	exponential with scale radii $r_\text{t}$ = 2.5 kpc, $r_\text{T}$ = 2.0 
	kpc, and $\Sigma_\text{T}/\Sigma_\text{t}$ = 0.27 at $R_\text{gal}$ = 
	0~\citep{Bland-Hawthorn2016}. Both are plotted as dotted black lines in 
	Fig.~\ref{fig:surface_density}, and the sum as a solid black line.

	\item Surface density gradient from model with inside-out SFH, diffusion 
	migration, and $\tau_\star^\text{mol} = (\text{2 Gyr})(t/t_0)^{1/2}$ 
	plotted in Fig.~\ref{fig:surface_density} as well (stars in red and gas 
	in blue). Radial migration indeed didn't change the overall scaling of 
	$\Sigma_\star$ with $R_\text{gal}$ at the radii that we care about in 
	this paper ($\gtrsim$3 kpc), only introducing scatter. Gas disk appears to 
	be well-fit by a single-exponential with scale radius of~$\sim$3-4 kpc.

	\item Increase in~$\Sigma_\star$ at~$R_\text{gal} \lesssim$ 2 kpc likely 
	due to stellar populations finding bulge or pseudobulge star particles as 
	analogs and migrating inward. {\color{red} Comment further on this, and 
	plot PDFs of the kinematically decomposed star particles 
	from~\texttt{h277}: essentially zero bulge and pseudobulge star particles 
	with either birth or final radii~$\gtrsim$ 3 kpc.} 
\end{itemize}

\subsection{Metallicity} 
\label{sec:gradients:metallicity}

\begin{itemize} 
	\item Scaling of $\eta$ with $R_\text{gal}$ based on reproducing the 
	observed mode([$\alpha$/H])-$R_\text{gal}$ trend, neglecting radial 
	migration (see~\S~\ref{sec:methods:outflows}). The target gradient is 
	shown in a solid black line in Fig.~\ref{fig:metallicity_gradient}.

	\item Gradient is indeed recovered in [O/H], and radial migration appears 
	to only induce scatter. While Fe did not enter into our procedure for 
	setting the metallicity gradient, the model predicts a similar gradient 
	for [Fe/H].

	\item Metal-poor and $\alpha$-enhanced tail in the inner galaxy predicted 
	by all models.

	\item Details of the [O/Fe] gradient seem to be sensitive to differences 
	in our SFHs.

	\item Constant SFH is the only model in which the present-day gas phase 
	gradient matches the stellar gradient at all radii. In remaining models, 
	the present-day gas-phase abundance is above the majority of the stars 
	because the star formation rate has decreased.

	\item Stellar gradient is somewhat shallower in the late-burst model; this 
	is because of the dilution associated with the starburst. Target gradient 
	represents the equilibrium abundance at all radii, and we deliberately 
	perturbed it from equilibrium, so any deviations from the expectation are 
	a consequence of that.

	\item Late-burst model has super-equilibrium gas phase abundance at the 
	present day. Can be seen in the break in the gas phase gradient in the 
	outer-burst as well. This is a consequence of the starburst - in infall 
	driven starbursts, re-enrichment can produce super-equilibrium abundances 
	which then decay back to the equilibrium abundance as the star 
	formation rate declines~\citep{Johnson2020}. 
\end{itemize}

\section{Metallicity Space} 
\label{sec:metallicity_space}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.42]{tracks_2Gyr_timedep.pdf} 
\caption{\textbf{Left}: Evolutionary tracks for the gas phase in the 
[O/Fe]-[Fe/H] plane for models with 
$\tau_\star^\text{mol} = (\text{2 Gyr})(t/t_0)^{1/2}$, our inside-out SFH, and 
either post-processing (dotted lines) or diffusion (solid lines) migration 
models. We plot tracks for seven annuli, color-coded according to their 
Galactocentric radius and denoted by the legend in the lower-left. We mark 
simulation times of 2, 4, 6, 8, 10, and 12.7 Gyr in X's for the diffusion 
model and points for the post-processing model. 
\textbf{Right}: The proxy for the SN Ia rate defined in equation 
\refp{eq:ia_rate_proxy} as a function of simulation time for the same annuli 
as in the left-hand panel. We multiply rates at each radii here by various 
prefactors in the interest of clarity. }
\label{fig:tracks} 
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.28]{ofe_feh_scatterplot_insideout.pdf} 
\caption{[O/Fe]-[Fe/H] diagrams for 15 galactic regions spanning five bins in 
$R_\text{gal}$ and~$\left|z\right|$. Each region has its own panel, with radial 
bins shown in columns denoted at the top of the figure, and with 
$\left|z\right|$ bins shown in rows denoted in text in the middle column 
panels. In each panel, we plot $N$ = 10,000 points sampled from our simulated 
stellar populations in each region predicted by our inside-out SFH, where the 
probability of sampling is proportional to the present-day mass of each stellar 
population. In all panels points are color-coded according to the 
Galactocentric radius of birth of the stellar population. For reference, we 
plot in a solid black line in all panels the gas-phase [O/Fe]-[Fe/H] track 
predicted by the same SFH in the $R_\text{gal}$ = 8 kpc annulus, but with the 
post-processing migration model; this curve is the same in all panels. }
\label{fig:ofe_feh_diagram} 
\end{figure*}

\begin{itemize} 
	\item Predicted [O/Fe]-[Fe/H] tracks for the diffusion model show 
	significant deviations from the post-processing model, and these 
	variations are due to the SN Ia rate varying in response to radial 
	migration. This challenges the assumption that stars don't contribute to 
	nucleosynthetic yields beyond their birth radius; that is, if a 
	statistically significant fraction of stars are expected to migrate 
	significantly from their birth radius when they're young ($\lesssim$ 2 
	Gyr), this approximation is invalid. This is proof of concept that the 
	radial migration of yields can occur as a consequence of the radial 
	migration of stars.

	\item For each zone,~\texttt{VICE} provies in its outputs the rates of 
	infall and star formation, the mass of the ISM, and the relevant 
	abundance information for each element along with the associated 
	MDFs at the final timestep. To determine the SN Ia rates, we therefore 
	have to approximate from the output. 
	\begin{itemize} 
		\item The time-derivative of the mass of Fe in a given annulus is 
		given by: 
		\begin{equation}
		\dot{M}_\text{Fe} \approx y_\text{Fe}^\text{CC}\dot{M}_\star + 
		y_\text{Fe}^\text{Ia}\langle\dot{M}_\star\rangle_\text{Ia} - 
		\frac{M_\text{Fe}}{M_g}\dot{M}_\star(1 + \eta(R_\text{gal}) - r) 
		\end{equation} 
		where this is an approximation because in detail, there is a small 
		contribution from AGB stars, and the recycling in the simulation is 
		done continuously, whereas here we simply take $r \approx$ 0.4 
		(appropriate for a~\citetalias{Kroupa2001} IMF;~\citealp{Weinberg2017}). 
		This equation can be derived from the~\citet{Weinberg2017} analytic 
		models assuming CCSN and SN Ia enrichment for Fe with instantaneous 
		recycling of previously produced Fe.~\texttt{VICE}'s science 
		documentation could also be referenced here; it has a nice detailed 
		section on its treatment of each term in handling enrichment rates 
		\footnote{
			\url{https://vice-astro.readthedocs.io/en/latest/science_documentation/enrichment/index.html}
		}. 
		Rearranging this for the term describing the rate of injection due to 
		SNe Ia events, and normalizing by $M_\text{Fe}$ yields the following 
		proxy with units of frequency: 
		\begin{equation} 
		\frac{
			y_\text{Fe}^\text{Ia}\langle\dot{M}_\star\rangle_\text{Ia}
		}{
			M_\text{Fe} 
		} \approx 
		\frac{\dot{M}_\text{Fe}}{M_\text{Fe}} - y_\text{Fe}^\text{CC}\frac{
			\dot{M}_\star 
		}{
			M_\text{Fe} 
		} + \frac{\dot{M}_\star}{M_g}(1 + \eta(R_\text{gal}) - r) 
		\label{eq:ia_rate_proxy} 
		\end{equation} 
		This term on the left-hand side can be substituted with 
		$m_\text{Fe}^\text{Ia}\dot{N}_\text{Ia}/M_\text{Fe}$, where 
		$m_\text{Fe}^\text{Ia}$ is the average mass of Fe produced by a single 
		SN Ia event, and $\dot{N}_\text{Ia}$ is the SN Ia rate itself. For 
		this reason, this equation constitutes a straight-forward proxy for 
		the SN Ia rate at any given time. This is the proxy that's plotted in 
		the right-hand panel of~Fig.~\ref{fig:tracks}, with multilicative 
		factors added for visual clarity. 
	\end{itemize}

	\item Some folks have assumed tracks in the [O/Fe]-[Fe/H] plane to infer 
	birth radii for observed stars. We caution against inferring birth radii 
	in this way for high-$\alpha$ stars, because there radial migration may 
	cause one to infer a considerably wrong birth radius, provided they're 
	assuming a post-processing migration model. This however doesn't seem to 
	affect the low-$\alpha$ sequence. It's possible that an additional 
	dimension such as age could mitigate these issues.

	\item Variability in the SN Ia rate shows high-amplitude on Gyr timescale, 
	low-amplitude white-noise on shorter timescales. In general the 
	time-averaged rates follow the expectation from the post-processing model. 
	Fractional amplitude of variability increases with Galactocentric radius.

	\item Demonstrate in the next section that this is a means with which to 
	form $\alpha$-rich and $\alpha$-poor stars - or rather Fe-poor and 
	Fe-rich, respectively.

	\item Fig.~\ref{fig:ofe_feh_diagram} shows a scatter plot of 10,000 
	randomly sample stellar populations in five bins of $R_\text{gal}$ and 
	three bins of $\left|z\right|$ ($R_\text{gal}$ = 3 - 5 kpc, 5 - 7 kpc, 
	7 - 9 kpc, 9 - 11 kpc, and 11 - 13 kpc; $\left|z\right|$ = 0 - 0.5 kpc, 
	0.5 - 1 kpc, and 1 - 2 kpc). These are the same bins and same scheme for 
	organizing the panels as in Fig. 4 of~\citet{Hayden2015}.

	\item The width of the low-$\alpha$ sequence predicted by the model comes 
	from radial migration, in agreement with the prediction 
	of~\citet{Schoenrich2009}.

	\item The low-$\alpha$ sequence shifts from a high [Fe/H] locus at small 
	$R_\text{gal}$ to low [Fe/H] at high~$R_\text{gal}$, in agreement with the 
	observed distributions in APOGEE presented in~\citet{Hayden2015}.

	\item High-$\alpha$ stars are most prevalent at low~$R_\text{gal}$ and 
	high~$\left|z\right|$, and conversely for the low-$\alpha$ stars, also 
	in agreement with~\citet{Hayden2015}. 
	\begin{itemize} 
		\item Similar results are found for different SFHs. This suggests that 
		this observed result is a natural consequence of stellar migration.

		\item Only minor difference worth noting is that the starburst models 
		predict a slightly higher characteristic [O/Fe] ($\sim$+0.1) for the 
		low-$\alpha$ sequence. This is a natural consequence of the starburst. 
	\end{itemize} 
\end{itemize}

\section{The Age-[$\alpha$/Fe] Relation} 
\label{sec:age_alpha}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.5]{age_ofe_migration_comparison.pdf} 
\caption{A comparison of the predicted age-[O/Fe] relation for the solar 
annulus ($R_\text{gal}$ = 7 - 9 kpc and $\left|z\right|\leq$ 0.5 kpc) 
between the post-processing (upper left), diffusion (upper right), sudden 
(lower left), and linear (lower right) migration models, assuming our 
inside-out SFH and $\tau_\star^\text{mol} = (\text{2 Gyr})(t/t_0)^{1/2}$. 
Red triangles and error bars denote the observed mean age and dispersion 
thereof in bins of [O/Fe] as reported by~\citet{Feuillet2019}; here we include 
only the bins containing at least 15 stars. Black squares denote the 
mass-weighted median age in 0.02-dex bins in [O/Fe], with error bars denoting 
the 16th and 84th percentiles of the mass-weighted age distribution in 
those bins. Points in the background denote each individual stellar population 
from the simulation with a final position in the solar annulus, color-coded 
according to their Galactocentric radius of birth. } 
\label{fig:age_alpha_migration_comparison} 
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.5]{age_ofe_sfh_comparison.pdf} 
\caption{The same as Fig.~\ref{fig:age_alpha_migration_comparison}, instead 
comparing the impact of our constant (upper left), inside-out (upper right), 
late-burst (lower left), and outer-burst (lower right) SFHs, assuming diffusion 
migration and $\tau_\star^\text{mol} = (\text{2 Gyr})(t/t_0)^{1/2}$. }
\label{fig:age_alpha_sfh_comparison} 
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{age_alpha_regions.pdf} 
\caption{The age-[O/Fe] relation in difference galactic regions predicted by 
our inside-out SFH with $\tau_\star^\text{mol} = (\text{2 Gyr})(t/t_0)^{1/2}$ 
and diffusion migration. Bins in Galactocentric radius are shown in columns, 
and labeled at the top. Bins in the height $\left|z\right|$ above/below the 
disk midplane are shown in rows, noted in the left-hand column. Red triangles 
and error bars denote the observed mean age and dispersion thereof in bins of 
[O/Fe] as reported by~\citet{Feuillet2019}; here we include only the mass bins 
containing at least 15 stars. Black squares denote the mass-weighted median 
age in 0.02-dex bins in [O/Fe], with error bars denoting the 16th and 84th 
percentiles of the mass-weighted age distribution in those bins. Points in the 
background denote each individual stellar population from the simulation with 
a final position in that Galactic region, color-coded according to their 
Galactocentric radius of birth. } 
\label{fig:age_alpha_regions} 
\end{figure*}

\begin{itemize} 
	\item \citet{Feuillet2019} make use of APOGEE DR14 stars where there are 
	Gaia parallax measurements available~\citep{GaiaDR2}. With their spatial 
	cuts, the final sample consisted of 77,562 stars. In bins of [O/Fe], they 
	assume a gaussian age distribution, and fit the mean and standard deviation 
	to the observed sample. Because they assume a gaussian, they would report 
	an equal mean and median.

	\item The stellar populations from our simulations have different masses, 
	so the age-distributions must be weighted by mass, since that scales with 
	the number of stars that each stellar population represents.

	\item Our age distributions in the vast majority of [O/Fe] bins are 
	highly non-gaussian, so we compare to~\citet{Feuillet2019} based on the 
	predicted mass-weighted median age in [O/Fe] bins (i.e. the age which 50\% 
	of the stellar mass in a given bin is younger than). For these reasons the 
	comparison between our simulations and~\citet{Feuillet2019} isn't exactly 
	one-to-one. 
\end{itemize}

\subsection{The Impact of Radial Migration} 
\label{sec:age_alpha:migration} 
\begin{itemize} 
	\item Fig.~\ref{fig:age_alpha_migration_comparison} shows a comparison 
	between the predicted age-[$\alpha$/Fe] relations in the solar annulus for 
	our four migration models assuming our inside-out SFH.

	\item All models show reasonable agreement with the~\citet{Feuillet2019} 
	data; the population-averaged trend appears insensitive to the assumed 
	migration model.

	\item Diffusion predicts the most intrinsic scatter, followed by linear, 
	then sudden, then post-processing. Further demonstration that under 
	certain migration models, the radial migration of nucleosynthetic yields 
	is statistically significant.

	\item This mechanism can produce populations of Fe-poor or Fe-rich stars, 
	which can be misinterpreted as $\alpha$-rich or $\alpha$-poor stars. Due 
	to young stars migrating into or out of a given annulus, the SN Ia rate 
	may be higher or lower than the expectation from a post-processing 
	migration model. If this difference in the SN Ia rate is sustained for of 
	order one depletion time, the ISM will be either Fe-poor or Fe-rich, and 
	the stars that form there will inherit that composition.\footnote{
		{\color{red} Potentially note the~\citet{Weinberg2017} definition: 
		$\tau_\text{dep} \equiv \tau_\star/(1 + \eta - r)$. Even with 
		$\tau_\star$ as high as~$\sim$5 Gyr at large Galactocentric radii, 
		depletion times are still short due to the high values of $\eta$ 
		there.}
	} The stars that form out of that patch of ISM can then migrate to the 
	solar annulus. This effect is most significant at large Galactocentric 
	radii where the fractional amplitude of the variability in the SN Ia rate 
	is largest, and for that reason the young Fe-poor population predicted by 
	our diffusion model originates at large radii ($\gtrsim$ 12 kpc).

	\item \citet{SilvaAguirre2018} demonstrated that the observed young 
	$\alpha$-rich stars in the solar annulus have kinematics similar to the 
	rest of the high-$\alpha$ population, and suggested that this may be the 
	result of stellar mergers or mass transfer events, producing a population 
	of truly old stars masquerading as young stars. This would imply that the 
	observed young $\alpha$-rich population is actually just older, 
	high-$\alpha$ stars that have gone through some special class of stellar 
	evolution. Our model predicts intrinsically young, Fe-poor stars to 
	explain the observations, but these interpretations are not mutually 
	exclusive. Ascertaining the origins of this population therefore has 
	implications for which of the migration models investigated here is the 
	most realistic. 
\end{itemize}

\subsection{The Impact of the Star Formation SFH} 
\label{sec:age_alpha:sfh} 
\begin{itemize} 
	\item Fig.~\ref{fig:age_alpha_sfh_comparison} shows a comparison between 
	the predicted age-[$\alpha$/Fe] relations in the solar annulus for our 
	four SFHs assuming diffusion migration.

	\item Constant and inside-out SFHs describe the observed data the best. 
	Both late starburst models show a population-averaged increase in 
	[$\alpha$/Fe] at young ages which is not observed in the data. This 
	challenges the results of~\citet{Isern2019} and~\citet{Mor2019}, 
	suggesting that these results on the Milky Way recent SFH are not 
	consistent with chemical evolution models.

	\item Below [O/Fe]~$\approx$ +0.1, the~\citet{Feuillet2019} data seem to 
	follow a slightly steeper age-[$\alpha$/Fe] than our inside-out model 
	predicts. This likely points to inaccuracies in the detailed form of the 
	SFH or the SN Ia DTD, both of which are within the uncertainties of these 
	models. 
\end{itemize}

\subsection{Beyond the Solar Annulus} 
\label{sec:age_alpha:beyond_solar_annulus} 
\begin{itemize} 
	\item Fig.~\ref{fig:age_alpha_regions} presents a comparison of our 
	simulation data to the~\citet{Feuillet2019} observational data in 12 
	Galactic regions assuming the inside-out SFH.

	\item In the disk, the inside-out SFH is a reasonable description of the 
	data for ages~$\lesssim$ 5 Gyr, above which the median ages are 
	overpredicted relative to~\citet{Feuillet2019}. Far from the midplane, our 
	model overpredicts the ages at nearly all abundances 
	where~\citet{Feuillet2019} have data, with the exception of the 
	$R_\text{gal}$ = 7 - 9 kpc and $\left|z\right|$ = 0.5 - 1 kpc region.

	\item Differences in ages are interesting though - nearly everywhere we 
	overpredict ages relative to~\citet{Feuillet2019}, their data are 
	reasonably described by the stellar populations from our simulations that 
	we would classify as Fe-poor. Especially noticeable in the $R_\text{gal}$ 
	= 5 - 7 kpc, $\left|z\right|\leq$ 0.5 regions (i.e. lower-left panel), 
	where the observed data also show an abrupt increase in age near the 
	maximum [O/Fe] ratio of one particular Fe-poor population, with one data 
	point that agrees with the population-averaged trend from the simulation. 
	\begin{itemize}
		\item Taking the~\citet{Feuillet2019} data at face value, this would 
		suggest that our simulation is overpredicting the rate of Fe injection 
		from SN Ia, implying a SN Ia DTD whose characteristic timescales are 
		longer than we employ here, thus slowing the decrease of [$\alpha$/Fe] 
		with time.

		\item \citet{Feuillet2019} made use of APOGEE DR14 data for which 
		Gaia parallax measurements are available. With their quality cuts the 
		final sample consisted of 77,562 stars. Taking the simulation results 
		at face value, this would suggest that APOGEE+Gaia target selection 
		favors the stars we would classify as Fe-poor. 
	\end{itemize} 
\end{itemize}

\section{The Age-Metallicity Relation} 
\label{sec:amr}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{age_oh_comparison.pdf} 
\caption{The age-[$\alpha$/H] relation predicted by our constant (top), 
inside-out (top middle), late-burst (bottom middle), and outer-burst (bottom) 
SFHs for $R_\text{gal}$ = 5 - 7 kpc (left), 7 - 9 kpc (left middle), 9 - 11 
kpc (right middle), and 11 - 13 kpc (right). Each panel plots only the 
$\left|z\right|\leq$ 0.5 kpc population. Background points, red triangles with 
error bars, and black squares with error bars are as in 
Fig.~\ref{fig:age_alpha_regions}, but with our binned, simulation quantified 
in 0.05-dex bins in [O/H]. } 
\label{fig:age_oh_comparison}
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{age_feh_comparison.pdf} 
\caption{The same as Fig.~\ref{fig:age_oh_comparison}, but for the age-[Fe/H] 
relation. } 
\label{fig:age_feh_comparison} 
\end{figure*}

\begin{itemize} 
	\item Fig.~\ref{fig:age_oh_comparison} shows a comparison of the 
	predicted age-[O/H] for $\left|z\right|\leq$ 0.5 stars in four bins in 
	Galactocentric radius between our four fiducial SFHs and 
	the~\citet{Feuillet2019} data. Fig.~\ref{fig:age_feh_comparison} shows 
	the same comparison but for the age-[Fe/H] relation.

	\item For a constant SFR, our model predicts a non-monotonic AMR at all 
	radii for both O and Fe; that is, the most metal-rich stars in a given 
	annulus are not the youngest stars. Under this model, the metallicity 
	of the youngest stars reflects the equilibrium abundance at a given 
	radius. This is an indication that the turnover in the observed AMR is 
	tied to the abundance gradient in our models. This supports the notion 
	first raised in~\citet{Feuillet2018} using the~\citet{Weinberg2017} 
	analytic models that the non-monotonicity of the observed AMR is a 
	consequence of radial migration. At any given annulus, a metallicity 
	significantly different than the equilibrium abundance is an indication 
	that that star migrated a significant distance, and is thus necessarily 
	old because it would need an adequate amount of time to do so. This effect 
	is also strong enough that in the 11 - 13 kpc bin, the model predicted 
	AMR is nearly monotonically increasing due to this annulus's position at 
	the tail of the abundance gradient.

	\item Inside-out SFH tends to suppress the formation of this so-called 
	young metal-rich population in the inner galaxy. The highest metallicity 
	stars are not predicted to be significantly older than lower metallicity 
	stars at 5 - 7 kpc in both [O/H] and [Fe/H], and also at 7 - 9 kpc in 
	[Fe/H]. In other words, the inside-out model predicts an AMR for the 
	inner Milky Way that follows a different trend than suggested 
	by~\citet{Feuillet2019}. In the 9 - 11 and 11 - 13 kpc bins, the 
	inside-out model in general overpredicts ages of solar and supersolar 
	metallicity stars, though the agreement is reasonable at subsolar 
	metallicity.

	\item In the late-burst model, the agreement between the simulation 
	prediction and the observational results at 5 - 7 kpc shows a noticeable 
	improvement from the inside-out model. This is because the late-burst 
	model forms an excess of mildly subsolar (-0.5~$\lesssim$ [O/H], 
	[Fe/H]~$\lesssim$ 0) at ages of~$\sim$2 Gyr. This decreases the median 
	age at that metallicity, where the inside-out model has its biggest 
	discrepancy with the observations at that radius. In the solar annulus, 
	there is little difference in the predicted age-[O/H] relations 
	between inside-out and late-burst, but there is an improvement for Fe for 
	the same reason as before. Agreement is also improved for both elements 
	in the 9 - 11 and 11 - 13 kpc bins; the trends are better reproduced in 
	the burst model, though the ages of the most metal-rich stars are still 
	overpredicted. Appears to be a slight offset between the predicted and 
	observed AMR for Fe; this could point to any number of minor modifications. 
	\begin{itemize} 
		\item Highest metallicity bins at 5 - 7 kpc are the effect of poor 
		statistics. We're taking the median of a distribution that is 
		bimodal, so the median age there is extremely sensitive to the 
		detailed timing of the starburst.

		\item Improvement in agreement due not only to the late starburst but 
		also to the effect of dilution - for this reason, not many young, 
		super-solar metallicity stars form simply because of a global decrease 
		in metallicity in the model Milky Way's evolution, visible in the 
		colored points on each panel. 
	\end{itemize}

	\item Outer-burst predicted AMR is particularly sensitive to our decision 
	to neglect radial gas flows, particularly at 5 - 7 kpc because the burst 
	is assumed to occur at~$\geq$ 6 kpc in this model, so we caution that it's 
	easy to over-interpret the quantitative interpretations of this model. In 
	detail, a more realistic model involving radial gas flows would show some 
	metal-poor gas moving inward and carry the effect of dilution in some 
	capacity down to $R_\text{gal}$ = 0. No major differences in the 
	population-averaged predictions between late- and outer-burst models aside 
	from the highest metallicity bins in the inner galaxy where the age 
	distribution was bimodal in the late-burst model.

	\item Potentially worth noting that the solar annulus is reasonably 
	described by all four models for both O and Fe. On these grounds we'd 
	advise future studies doing a detailed comparison of observed and 
	model-predicted AMRs to consider multiple Galactic regions.

	\item Conclude that the AMR reported by~\citet{Feuillet2019} is better 
	described by our late starburst models than the inside-out model, while 
	the age-[$\alpha$/Fe] relation also reported by~\citet{Feuillet2019} is 
	better described by the inside-out model. What can reconcile the 
	differences between the two. 
	\begin{itemize} 
		\item Likely not an idication that we need to relax our assumptions 
		about the detailed timing of the starburst at a given radius (i.e. 
		our assumptions about $f(t|R_\text{gal})$ in the burst models). Any 
		significant global starburst will produce a global $\alpha$-enhancement 
		that isn't seen in the observed data (see the comparison of our 
		models to the~\citet{Feuillet2019} data in~\S~\ref{sec:age_alpha}).

		\item Possibly there was a dilution event with no significant 
		resulting starburst (this could happen if the majority of the accreted 
		gas was HI that has not yet cooled). With ongoing star formation but 
		not a starburst, re-enrichment and the ensuing $\alpha$-enhancement 
		would be significantly slower, potentially to the point that no 
		significant $\alpha$-enhancement is predicted. With dilution playing 
		a role in the AMR predicted by the burst models, it's possible that 
		its agreement with the data could be retained. 
	\end{itemize} 
\end{itemize}

\subsection{Beyond the Midplane} 
\label{sec:amr:beyond_midplane}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{amr_lateburst_O.pdf} 
\caption{The same as Fig.~\ref{fig:age_alpha_regions}, but for the age-[O/H] 
relation, the late-burst rather than the inside-out SFH, and with our binned, 
simulated relation quantified in 0.05-dex bins in [O/H]. }
\label{fig:age_oh_regions} 
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{amr_lateburst_Fe.pdf} 
\caption{The same as Fig.~\ref{fig:age_alpha_regions}, but for the age-[Fe/H] 
relation, the late-burst rather than the inside-out SFH, and with our binned, 
simulated relation quantified in 0.05-dex bins in [Fe/H]. } 
\label{fig:age_feh_regions} 
\end{figure*}

\begin{itemize} 
	\item Fig.~\ref{fig:age_oh_regions} shows the predicted age-[O/H] relation 
	in 12 Galactic regions from the late-burst SFH in comparison to 
	the~\citet{Feuillet2019} data. Fig.~\ref{fig:age_feh_regions} shows the 
	same thing, but for the age-[Fe/H] relation.

	\item With increasing $\left|z\right|$, the age distribution of stellar 
	populations moves quickly to high ages, in qualitative agreement with 
	observations.

	\item Off the midplane, ages are in general overestimated at nearly all 
	radii in both O and Fe, particularly for the $\left|z\right|$ = 1 - 2 kpc 
	regions.

	\item Find similar results for our other models. What could be causing this 
	discrepancy with the observations? 
	\begin{itemize} 
		\item We assumed that the disk is vertically and azimuthally well-mixed. 
		Could this point to a breakdown in the assumption of efficient vertical 
		mixing?

		\item The dynamical history of our model is not the Milky Way's 
		dynamical history; it's~\texttt{h277}'s dynamical history. Perhaps the 
		Milky Way had a dynamical disturbance to the disk that kicked a bunch 
		of younger stars to high $\left|z\right|_\text{max}$ orbits (e.g. 
		potentially the Sagitarrius Stream). 
	\end{itemize} 
\end{itemize}

\section{Metallicity Distribution Functions} 
\label{sec:mdfs}

\begin{figure} 
\centering 
\includegraphics[scale = 0.34]{mdf_3panel_lateburst_Fe.pdf} 
\caption{Metallicity Distribution Functions in [Fe/H] predicted by our 
late-burst model (left) and as observed in APOGEE DR16 (right), for stars and 
simulated stellar populations with present day $\left|z\right|$ = 0 - 0.5 kpc 
(bottom), 0.5 - 1 kpc (middle), and 1 - 2 kpc (top). MDFs are shown in bins 
of Galactocentric radius: 3 - 5 kpc (black), 5 - 7 kpc (red), 7 - 9 kpc 
(yellow), 9 - 11 kpc (green), 11 - 13 kpc (blue), and 13 - 15 kpc (purple). 
The points near the top of the bottom panels denote what the mode abundance 
would be if it followed our target gradient of [Fe/H] = +0.3 at $R_\text{gal}$ 
= 4 kpc and a slope of -0.08 kpc$^{-1}$, assuming the inner radius of each bin 
(i.e. there is no point plotted for 15 kpc). All distributions are smoothed 
with a box-car width of [Fe/H]~$\pm$~0.1. } 
\label{fig:mdf_3panel_fe} 
\end{figure}

\begin{figure} 
\centering 
\includegraphics[scale = 0.34]{mdf_3panel_lateburst_O.pdf} 
\caption{The same as Fig.~\ref{fig:mdf_3panel_fe}, but for [O/H].} 
\label{fig:mdf_3panel_o} 
\end{figure}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{ofe_mdfs_insideout.pdf} 
\caption{Predicted distributions in [O/Fe] in 15 Galactic regions and in two 
bins in [Fe/H]. Columns correspond to bins in~$R_\text{gal}$, denoted at the 
top of each column. Rows correspond to bins in~$\left|z\right|$, denoted in 
text in the left-hand column. Distributions are color-coded according to the 
[Fe/H] the sample is drawn from, denoted by the legend in the upper right 
panel. Solid lines denote that predicted by our inside-out SFH, while dashed 
lines denote the observed distributions from APOGEE DR16, quantified in 
Vincenzo et al. (2021, in prep). 
\label{fig:ofe_mdfs_insideout} 
}
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{ofe_mdfs_lateburst.pdf} 
\caption{The same as Fig.~\ref{fig:ofe_mdfs_insideout}, but with the solid 
lines denoting the predictions of our late-burst SFH. } 
\label{fig:ofe_mdfs_lateburst} 
\end{figure*}

\subsection{[O/H] and [Fe/H]} 
\label{sec:mdfs:oh_feh}

\begin{itemize} 
	\item MDFs in bins of Galactocentric radius are a fundamental observable 
	to test the validity of any chemical evolution model.

	\item Previously known that the MDFs in the disk midplane as observed in 
	APOGEE show mode [$\alpha$/H] and [Fe/H] abundances that depend on 
	Galactocentric radius, with a skew-negative distribution in the inner 
	Galaxy and a skew-positive distribution in the outer Galaxy. Off the 
	midplane, the MDFs merge and converge on [$\alpha$/H]~$\approx$~[Fe/H] 
	$\approx$~-0.5~\citep{Hayden2015, Weinberg2019}. This result is replicated 
	in the left-hand column of panels in Fig.~\ref{fig:mdf_3panel_fe} and 
	Fig.~\ref{fig:mdf_3panel_o}. 
	\begin{itemize} 
		\item Similar mode [O/H] and [Fe/H] between the 3 - 5 and 5 - 7 kpc in 
		the APOGEE observations. What could be the origin of this? Cessation of 
		star formation in the inner Galaxy? (see Fig. 1 of~\citealp{Peek2009} 
		and Fig. 2 of~\citealp{Fraternali2012}). This would imply very few 
		stars formed in the most metal-rich regions of the Galaxy, cutting off 
		the MDF at high [O/H], [Fe/H]. 
	\end{itemize}

	\item Left-hand panels of Figs.~\ref{fig:mdf_3panel_fe} 
	and~\ref{fig:mdf_3panel_o} show the distributions predicted by our 
	late-burst model. They successfully replicate the qualitative result that 
	the mode [X/H] varies with present-day Galactocentric radius, but fail to 
	show a similar mode abundance between the 3 - 5 and 5 - 7 kpc bins. 
	Potentially linked to the cessation of star formation in inner 
	Galaxy~\citep{Peek2009, Fraternali2012}.

	\item Beyond the midplane, our models fail to fully replicate the 
	convergence of the MDFs at [x/H]~$\approx$~-0.5. The observed MDF at small 
	radii shifts from skew-negative with a metal-rich mode to skew-positive 
	with a metal-poor mode with increasing $\left|z\right|$. In our predicted 
	MDFs for the inner galaxy, the mode does shift to lower [X/H], though not 
	as low as in the observations. There is also very little change in 
	skewness with $\left|z\right|$ predicted, in tension with observations. 
	\begin{itemize} 
		\item Could this point to a breakdown of our assumption that vertical 
		mixing is efficient?

		\item Some discussion in~\S~\ref{sec:amr} that the Sagitarrius stream 
		may be responsible for the young ages observed at high~$\left|z\right|$ 
		in~\citet{Feuillet2019}. This likely wouldn't solve the problem here, 
		because our annuli are at or near equilibrium at the lookback times 
		associated with the Sagitarrius dwarf's pericentric passages, meaning 
		this effect would only kick high [X/H] stars to high~$\left|z\right|$. 
	\end{itemize}

	\item We note that our models do a good job of producing a mode [X/H] 
	abundance in each radial bin close to our target gradient. In the inner 
	galaxy bins in Figs.~\ref{fig:mdf_3panel_fe} and~\ref{fig:mdf_3panel_o}, 
	the predicted mode is moderately lower than the target, but this is due 
	to the effect of dilution (see discussion in~\S~\ref{sec:amr}). In our 
	inside-out model, the difference in target and predicted mode [X/H] is 
	considerably smaller. 
\end{itemize}

\subsection{[O/Fe]} 
\label{sec:mdfs:ofe}

\begin{itemize} 
	\item Fig.~\ref{fig:ofe_mdfs_insideout} show distributions in [O/Fe] in two 
	bins of [Fe/H] across 15 Galactic regions predicted by our inside-out SFH 
	(solid lines).

	\item Dashed lines denote the distributions quantified in Vincenzo et al. 
	(2021, in prep). These are intended to simultaneously remove the effects of 
	observational errors in [O/Fe] and the APOGEE selection function in these 
	Galactic regions; that is, these are estimates of the~\textit{intrinsic} 
	[O/Fe] distributions that, when convolved with observational uncertainties 
	and the APOGEE selection function, would resemble the observed MDFs.

	\item We note that the inside-out model fails to reproduce a Milky Way-like 
	bimodality. Such a model prediction would appear as good agreement between 
	the solid and dashed lines in Fig.~\ref{fig:ofe_mdfs_insideout}, but that 
	is not the case. There may be decent agreement in a given metallicity bin 
	and Galactic region, but the agreement would need to be seen everywhere and 
	at all metallicities.

	\item In the inner galaxy, we overestimate the [O/Fe] of the highest [Fe/H] 
	stars at all $\left|z\right|$, and the differences in the distributions 
	gets smaller with increasing~$R_\text{gal}$. The lower [Fe/H] bins don't 
	seem to have this problem. 
	\begin{itemize} 
		\item Since these are in specific bins in [Fe/H], this is an indication 
		that our model is overpredicting the O abundances of these stars, 
		rather than underpredicting [Fe/H].

		\item This could point to various things. Perhaps the Milky Way has 
		different gradients in [O/H] than [Fe/H], an effect which is not 
		captured by these models. Perhaps the innermost radii of the Milky Way 
		has some contamination from bulge stars, another effect which is not 
		captured by our models. 
	\end{itemize}

	\item Fig.~\ref{fig:ofe_mdfs_lateburst} shows the same thing as 
	Fig.~\ref{fig:ofe_mdfs_insideout}, but for the late-burst SFH.

	\item We note that this model does not predict a Milky Way-like bimodality 
	either, and still suffers from the issues facing the inside-out model 
	regarding the highest [Fe/H] stars in the inner Galaxy.

	\item While the notion that an [$\alpha$/Fe] dichotomy can arise out of 
	radial migration alone was put forth in~\citet{Schoenrich2009}, this 
	suggests that an inside-out star formation history combined with stellar 
	migration is not conducive to predicting this observed result. This is at 
	odds with the findings of~\citet{Sharma2020}, who claim to reproduce the 
	[$\alpha$/Fe] dichotomy with an analytic chemical evolution model. 
	\begin{itemize} 
		\item {\color{red} We'll need to be careful in our final draft of the 
		paper so that our language here isn't too strong. Below I've given my 
		honest critiques of the~\citet{Sharma2020} paper. }

		\item They have a single SFH.

		\item They assume a functional form for [Fe/H] and [$\alpha$/Fe] with 
		time and radius, indicating that their [$\alpha$/Fe]-[Fe/H] tracks are 
		\textit{not} model predictions, and are instead assumptions 
		characterized~\textit{a priori} by radius and time. Rather than 
		learning about the physical origins of the [$\alpha$/Fe] dichotomy, we 
		instead get a robust mathematical caricature of the data.

		\item They find a dichotomy in the [$\alpha$/Fe]-[Fe/H] plane to arise 
		out of a fast transition in the gas phase between high-$\alpha$ and 
		low-$\alpha$. In practice, we find that this is only the case if 
		$\tau_\star$ is sufficiently short; analytic justification for this is 
		also presented in~\citet{Weinberg2019} ({\color{red} We could 
		potentially demonstrate this in Appendix~\ref{sec:sfe_variations} as 
		well}). In this paper, we adopted the~\citet{Tacconi2018} scaling of 
		$\tau_\star^\text{mol}$ with redshift. We find that none of our models 
		predict a~$\tau_\star$ adequately short such as to produce an 
		adequately fast transition between high-$\alpha$ and low-$\alpha$ 
		sequences, as assumed in the~\citet{Sharma2020} analysis.

		\item For these reasons, we believe our investigation to be more robust, 
		physically motivated, and internally consistent than 
		the~\citet{Sharma2020} analysis. 
	\end{itemize}

	\item These findings suggest that an inside-out SFH combined with radial 
	migration, even when a late starburst is taken into account (as motivated 
	by the findings of~\citealp{Isern2019} and~\citealp{Mor2019}), 
	is~\textit{not} conducive to producing the observed [$\alpha$/Fe] 
	dichotomy. This suggests that more dramatic evolutionary events are likely 
	responsible, such as a two-infall model~\citep[e.g.][]{Chiappini1997, 
	Chiappini2001, Romano2010, Grisoni2017, Noguchi2018, Spitoni2009, 
	Spitoni2016, Spitoni2018, Spitoni2019, Spitoni2020}. 
\end{itemize}

\section{Conclusions} 
\label{sec:conclusions} 
\begin{itemize} 
	\item We have modeled the Milky Way as a series of concentric annuli with 
	$\Delta R_\text{gal}$ = 100 pc width. We investigated a handful of 
	assumptions about the SFH, the time-dependence of radial migration, and 
	star formation efficiency, and a multitude of combinations thereof under 
	a simulation-based model for stellar migration independent of free 
	parameters.

	\item We found that similar numbers of star particles in~\texttt{h277} 
	migrated inward as outward, and that the two proceed on different 
	timescales, indicating that they're potentially linked to different 
	physical processes.

	\item We found that the e-folding timescales for star formation indicated 
	by population averaged observations of Milky Way like galaxies are long 
	($\sim$15 Gyr in the solar annulus;~\citealp{Sanchez2020}).

	\item We found that our recipe for setting the gradients in both stellar 
	surface density and metallicity yields the correct result. This is an 
	indication that radial migration does not change the profile of these 
	observed trends, only inducing scatter. 
	\begin{itemize} 
		\item We found that slightly different predictions in the stellar 
		and gas-phase metallicity gradient are natural consequences of 
		variations in the SFH.

		\item We found that different models for the SFH predicted different 
		[O/Fe] gradients at the present day. 
	\end{itemize}

	\item We found that the time-dependence of radial migration indeed does 
	have an impact on enrichment. Previous studies in the literature have 
	assumed that this is not the case, due to the slow nature of migration 
	\citep[e.g.][]{Minchev2013}. However, we find that even for young stars, 
	the tails of the present-day $R_\text{gal}$ distribution are adequately 
	long that when age-dependent migration is taken into account, the model 
	predicts variations in the SN Ia rate that then impact predicted abundance 
	ratios. We demonstrated that this is a means with which stellar migration 
	may produce young, Fe-poor stars which can migrate to the solar annulus, 
	and potentially be misinterpreted as young, $\alpha$-rich stars. This is 
	proof of concept that the radial migration of nucleosynthetic yields can 
	proceed alongside the radial migration of stars, depending on which model 
	for migration that you believe. 
	\begin{itemize} 
		\item These stars have been seen in observed data from APOGEE 
		\citep[e.g.][]{SilvaAguirre2018}. They postulate that since these stars 
		have kinematics similar to the rest of the high-$\alpha$ population, 
		that perhaps they are the consequence of stellar mergers or mass 
		transfer events, producing truly old stars that simply appear to be 
		younger. While these interpretations are not mutually exclusive, an 
		observational test to ascertain the origins of the observed young 
		$\alpha$-rich population would have implications for which of the 
		models for radial migration investigated here are the most realistic. 
	\end{itemize}

	\item In the observations, the high-$\alpha$ sequence is known to be most 
	prominent at low~$R_\text{gal}$ and high~$\left|z\right|$, and conversely, 
	the low-$\alpha$ population at high~$R_\text{gal}$ and low~$\left|z\right|$ 
	\citep[e.g.][]{Hayden2015}.  We found that this is a natural consequence of 
	stellar migration, though the detailed distributions depend on the SFH and 
	the relative yields of $\alpha$ and iron-peak elements, both of which are 
	highly uncertain, and we do not model them in detail here.

	\item We found that our inside-out model predicts an age-[$\alpha$/Fe] 
	relation which is in good agreement with the observed relation reported 
	by~\citet{Feuillet2019}. Our recent starburst models predict a global 
	$\alpha$-enhancement that simply isn't seen in the data. This suggests 
	that our current understanding of chemical evolution may be at odds with 
	the findings of~\citet{Mor2019} and~\citet{Isern2019} suggesting a recent 
	factor of~$\sim$2 enhancement in the Milky Way SFH peaking~$\sim$2 Gyr ago.

	\item We find that where our inside-out SFH model fails to agree with the 
	age-[O/Fe] relation reported by~\citet{Feuillet2019}, it tends to 
	overpredict ages at a given [O/Fe]. However, it tends to fail in a manner 
	such that the~\citet{Feuillet2019} relation agrees with the stars that we 
	would call Fe-poor - that is, the stars that are $\alpha$-enhanced due to 
	forming out of an Fe-poor ISM due to the same variations in the SN Ia rate 
	that can produce young, $\alpha$-rich stars. While this may be coincidence, 
	if we take the observations at face value, it would suggest that our model 
	is overpredicting the rate of Fe injection, and that perhaps SN Ia yields 
	of Fe should be lower. If we take the model at face value, it suggests that 
	APOGEE+Gaia targets preferentially sample young, $\alpha$-rich stars 
	(\citealp{Feuillet2019} used APOGEE data for stars with Gaia parallaxes).

	\item We found that the age-metallicity relation (AMR) in both [O/H] and 
	[Fe/H] reported by~\citet{Feuillet2019} is better fit by our late 
	starburst models. This is at odds with the findings regarding the 
	age-[O/Fe] relation, where the inside-out model agreed with the data much 
	better than the starburst models. This is interesting, because different 
	observables are favoring different models for the SFH, suggesting that 
	something more complicated is going on. 
	\begin{itemize} 
		\item The starburst models agreeing with the observed AMR has more to 
		do with the effect of dilution than the starburst itself. In trying to 
		model the Milky Way, we might be able to have our cake and eat it too 
		if there were dilution with no ensuing starburst. This could suggest 
		some accretion event that was primarily HI gas that hasn't yet cooled 
		to be available for star formation.

		\item Off the midplane, our model-predicted AMR overestimates ages 
		relative to~\citet{Feuillet2019}, just like in the age-[O/Fe] relation. 
		We speculate that this may be related to the Sagitarrius dwarf 
		galaxy; it's important to remember that our model galaxy does not have 
		the Milky Way's dynamical history, but~\texttt{h277}'s dynamical 
		history. {\color{red} Jon and I are looking into this, but as I 
		understand it, what I've written next is in general true.}~\texttt{h277} 
		did not have a Sagitarrius-like accretion event. Since Sagitarrius 
		has made multiple pericentric passages nearly head-on with the Milky 
		Way disk, it's possible that young stars were kinematically heated to 
		high~$\left|z\right|$, an effect that would not be present in 
		\texttt{h277} without such an event. This would decrease our model 
		predicted median ages at these heights by directly adding more young 
		stars, and potentially not having noticeable effect in the midplane due 
		to the much larger number of stars there. 
	\end{itemize}

	\item We find that our models naturally reproduce the variations in the 
	observed metallicity distribution functions (MDFs) with Galactocentric 
	radius. At low~$R_\text{gal}$, the mode abundance in both [O/H] and [Fe/H] 
	is high, and conversely low at high~$R_\text{gal}$. However, our predicted 
	distributions are too narrow, where in the observations the low 
	$R_\text{gal}$ MDF is significantly skew-negative, and conversely 
	skew-positive at high~$R_\text{gal}$~\citep{Hayden2015}. Also in the 
	observed relation, the mode abundance at 3 - 5 kpc is strikingly similar to 
	the mode abundance at 5 - 7 kpc. Our models fail to reproduce this, though 
	it may be tied to a cessation of star formation in the inner galaxy as 
	suggested by~\citet{Peek2009} and~\citet{Fraternali2012}.

	\item We find that none of our models predict a Milky Way-like dichotomy 
	in [$\alpha$/Fe], as observed by many studies. This suggests that inside-out 
	galaxy growth combined with radial migration, even if a recent starburst 
	is included, is not adequate to explain the observed dichotomy. This is at 
	odds with~\citet{Sharma2020}, though we believe our study to be the more 
	robust.

	\item \texttt{VICE} is publicly available and open-source. It can be 
	installed via~\texttt{pip} (\url{https://pypi.org/project/vice}). 
	Documentation is available at~\url{https://vice-astro.readthedocs.io}. 
	Source code is hosted at~\url{https://github.com/giganano/VICE.git}. 
\end{itemize}

\section{Acknowledgements} 
\label{sec:acknowledgements} 
We are grateful to Diane Feuillet for sharing the data 
from~\citet{Feuillet2018} and~\citet{Feuillet2019} with us. {\color{red} There 
will be others added, depending on whether or not they go here or on the 
author's list. I'll also need to add the SDSS acknowledgements since we made 
use of APOGEE data.}

\section{Data Availability} 
{\color{red} In case anyone hasn't seen one of these Data Availability 
statements yet, this is now a requirement by MNRAS. It wasn't when I submitted 
my last paper, but was by the time we were finished with the referee report, 
so I wound up having to add one. They just want you to say if the data are 
available to the reader or not, and where/how they can get it if they are. }
\texttt{VICE} is open source software, and as such the source code for these 
simulations is publicly available.\footnote{
	\url{https://pypi.org/project/vice} \\ 
	\url{https://vice-astro.readthedocs.io} \\ 
	\url{https://github.com/giganano/VICE.git} 
} The source code which produces the outputs presented in this paper as well as 
the figures are included as secondary material in the GitHub repository. 
While the aggregate of all outputs analyzed in this paper are sufficiently 
large that it is not conducive to store them on GitHub, we provide instructions 
on how to run our simulations and variations thereof. All observational data 
appearing in this paper is publicly available, and is also included with the 
source code for our simulations and figures.

\newpage 
\begin{appendices}

\section{Normalizing a Fiducial Star Formation History} 
\label{sec:normalize_sfh} 
\begin{itemize} 
	\item Derive formula for normalizing an SFH given the time-dependence at 
	a given radius $f(t|R_\text{gal})$ and the radial dependence of the 
	desired surface density gradient at late times $g(R_\text{gal})$. Neither 
	need be normalized. 
	\begin{equation} 
	\dot{\Sigma}_\star(R_\text{gal}, t) = \dot{\Sigma}_{\star,0}(R_\text{gal}) 
	f(t|R_\text{gal}) 
	\end{equation} 
	\begin{equation} 
	\Sigma_\star(r) = \Sigma_{\star,0} g(R_\text{gal}) 
	\end{equation}

	\item Integrate surface density of star formation with time and you get 
	the present day surface density gradient at that radius. This yields the 
	unknown $\dot{\Sigma}_{\star,0}$ in terms of $\Sigma_\star(R_\text{gal})$ 
	and subsequently the unknown $\Sigma_{\star,0}$. 
	\begin{subequations}\begin{align} 
	\Sigma_\star(R_\text{gal}) 
	&\approx (1 - r) \int_0^T \dot{\Sigma}_\star(R_\text{gal}, t) dt \\ 
	&= (1 - r) \dot{\Sigma}_{\star,0}(R_\text{gal}) \int_0^T f(t|R_\text{gal}) 
	dt \\ 
	\implies \dot{\Sigma}_{\star,0}(R_\text{gal}) &= 
	\Sigma_\star(R_\text{gal}) \left[(1 - r)\int_0^T f(t|R_\text{gal}) dt
	\right]^{-1} \\ 
	&= \Sigma_{\star,0}g(R_\text{gal}) \left[(1 - r) \int_0^T f(t|R_\text{gal}) 
	dt\right]^{-1} 
	\end{align}\end{subequations}

	\item Integrate surface density over area of the disk and you get the 
	present day Milky Way stellar mass. This solves for the unknown 
	$\Sigma_{\star,0}$: 
	\begin{subequations}\begin{align} 
	M_\star^\text{MW} &= \int_0^R \Sigma_\star(R_\text{gal}) 2\pi R_\text{gal} 
	dR_\text{gal} \\ 
	&= \Sigma_{\star,0}\int_0^R g(R_\text{gal}) 2\pi R_\text{gal} dR_\text{gal} 
	\\ 
	\implies \Sigma_{\star,0} &= M_\star^\text{MW} 
	\left[\int_0^R g(R_\text{gal}) 2\pi R_\text{gal}dR_\text{gal}\right]^{-1} 
	\end{align}\end{subequations}

	\item Combine the last two equations into 
	$\dot{\Sigma}_\star(R_\text{gal}, t)$ and obtain the following equation: 
	\begin{equation} 
	\dot{\Sigma}_\star(R_\text{gal}, t) = A f(t|R_\text{gal}) g(R_\text{gal}) 
	\end{equation} 
	where 
	\begin{equation} 
	A = M_\star^\text{MW}\left[(1 - r)\int_0^R g(R_\text{gal}) 2\pi R_\text{gal} 
	dR_\text{gal} \int_0^T f(t|R_\text{gal}) dt\right]^{-1} 
	\end{equation} 
	This result makes intuitive sense: $f(t|R_\text{gal})$ specifies the 
	time-dependence of the SFH and $g(R_\text{gal})$ specifies the radial 
	dependence by construction, and $M_\star^\text{MW}$ sets the overall 
	normalization.

	\item This recipe implicitly assumes that radial migration does not 
	significantly alter the surface density profile, and we have demonstrated 
	in~\S~X that this is the case for the Galactocentric radii of interest in 
	this paper. It introduces scatter, but does not alter the overall 
	dependence. This recipe can be employed in disk galaxy models as long as 
	this is not violated. 
\end{itemize}

\newpage 
\section{Variations in Star Formation Efficiency} 
\label{sec:sfe_variations} 
{\color{red} Eventually there will be an appendix demonstrating that our 
assumption about~$\tau_\star$ in~\S~\ref{sec:methods:sfe} do not have an 
impact on our models. }

\end{appendices}

\newpage 
\bibliographystyle{mnras} 
\bibliography{outline}

\label{lastpage} 
\end{document}

### 2021-08-04 chemev/MWbimodality/paper/outline2/outline2.tex
migration paper referee response

% \documentclass[a4paper, fleqn, usenatbib, useAMS]{mnras}
\documentclass[fleqn, usenatbib]{mnras} 
\usepackage{newtxtext, newtxmath} 	% Required for MNRAS 
\usepackage[T1]{fontenc}
% \usepackage{ae, aecompl}			% Required for MNRAS
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{multicol}
\usepackage{bm}
\usepackage{pdflscape}
\usepackage{natbib}
\usepackage[section]{placeins}
\usepackage{lipsum}
\usepackage{etoolbox} 
\usepackage{tabularx} 
\usepackage{xcolor} 
\usepackage[toc, page]{appendix} 
% \hypersetup{draft} 
% \linespread{1.8} 
\hypersetup{ 
	colorlinks		= true, 
	urlcolor 		= blue, 
	linkcolor 		= blue, 
	citecolor 		= blue 
}

\newcommand{\ddfrac}[2]{\frac{\displaystyle #1}{\displaystyle #2}} 
\newcommand{\refp}[1]{(\ref{#1})} 
\providecommand{\noopsort}[1]{} 
\graphicspath{ {../plots/} }

\interfootnotelinepenalty = 10000 
\defcitealias{Kroupa2001}{Kroupa} 
\defcitealias{Salpeter1955}{Salpeter}

\title{Stellar Migration and Chemical Enrichment in the Milky Way}

\author[J.W. Johnson et al.]{
	James W. Johnson,$^{1}$\thanks{Contanct e-mail: \href{mailto:
	johnson.7419@osu.edu}{johnson.7419@osu.edu}} 
	David H. Weinberg,$^{1, 2}$ 
	Fiorenzo Vincenzo,$^{2}$ 
	Jonathan C. Bird,$^{3}$ 
	\newauthor 
	Sarah R. Loebman,$^{4}$ 
	Alyson Brooks,$^{5}$ 
	Thomas R. Quinn,$^{6}$ 
	Charlotte R. Christensen,$^{7}$ 
	\newauthor 
	et al.?
	\\
	$^{1}$ Department of Astronomy, The Ohio State University, 
	140 W. 18th Ave., Columbus, OH, 43210, USA 
	\\ 
	$^{2}$ Center for Cosmology and Astroparticle Physics (CCAPP), 
	The Ohio State University, 191 W. Woodruff Ave, Columbus, OH, 43210, USA 
	\\ 
	$^{3}$ Department of Physics \& Astronomy, Vanderbilt University, 
	2301 Vanderbilt Place, Nashville, TN, 37235, USA 
	\\ 
	$^{4}$ Department of Physics, University of California Merced, 
	5200 North Lake Rd., Merced, CA, 95343, USA 
	\\ 
	$^{5}$ Department of Physics \& Astronomy, Rutgers University, 136 
	Frelinghuysen Rd, Piscataway, NJ, 08854, USA 
	\\ 
	$^{6}$ Department of Astronomy, University of Washinton, Box 351580, 
	Seattle, WA, 98195, USA 
	\\ 
	$^{7}$ Department of Physics, Grinnell College, 1116 8th Ave., Grinnell, 
	IA, 50112, USA 
}

\date{Accepted XXX; Received YYY; in original form ZZZ} 
\pubyear{2020}

\begin{document} 
\label{firstpage} 
\pagerange{\pageref{firstpage}--\pageref{lastpage}} 
\maketitle

\begin{abstract} 
We investigate the impact of stellar migration on galactic chemical evolution 
models, considering a handful of assumptions for the star formation history 
and time-dependence of radial migration based on a zoom-in, hydrodynamical 
simulation of galaxy evolution. We find that models for the 
time-dependence of radial migration impact the type Ia supernova rate as a 
function of both time and radius, inducing significant variability. We 
demonstrate that this is a means with which young, $\alpha$-enhanced stars can 
arise naturally out of inside-out galaxy growth with stellar migration. We find 
that the observed age-[$\alpha$/Fe] relation is well-fit by an inside-out star 
formation history, while the age-[O/H] and age-[Fe/H] relations are well-fit by 
a late starburst model; no one model investigated here fits both 
simultaneously. We also find that our models predict a dichotomy in 
[$\alpha$/Fe], but that they do not resemble that observed in the Milky Way 
due to an overabundance of intermediate [$\alpha$/Fe] stars. This suggests 
that inside-out galaxy growth combined with radial migration, even with a late 
starburst, is not conducive to forming the infamous bimodality as it is 
observed. We postulate that more dramatic evolutionary scenarios (e.g. a 
two-infall model) may be necessary to describe the observed results. In 
conducting this analysis, we developed and made use of newly released features 
in the \texttt{Versatile Integrator for Chemical Evolution} (\texttt{VICE}) 
which are built to handle these simulations under a wide variety of 
assumptions. \texttt{VICE} is publicly available 
at~\url{https://pypi.org/project/vice}. 
\end{abstract}

\begin{keywords} 
methods: numerical -- galaxies: abundances, evolution, star formation, stellar 
content 
\end{keywords}

\section{Introduction} 
\label{sec:intro} 
\begin{itemize} 
	\item Known for some time that stars undergo radial migration 
	\citep[e.g.][]{Wielen1996}, but to date there are only a handful of 
	chemical evolution models that take this into account 
	\citep[e.g.][]{Schoenrich2009, Minchev2013, Sharma2020}. This effect can 
	have a considerable impact on observed abundance trends by mixing stars 
	that formed out of Galactic regions with significantly different 
	enrichment histories, and if not taken into account, will impact the 
	conclusions of chemical evolution studies.

	\item The Age-Metallicity Relation (AMR) 
	\begin{itemize} 
		\item Age-metallicity relation in the solar neighbourhood exhibits 
		considerable intrinsic scatter~\citep{Edvardsson1993}, usually 
		attributed to radial migration of metal-rich (metal-poor) stars formed 
		at smaller (larger) Galactocentric radii~\citep{Sellwood2002, 
		Haywood2008, Roskar2008b, Schoenrich2009}.

		\item \citet{Feuillet2018} reveal that super-solar metallicity stars 
		are statistically older than solar metallicity stars (their Fig. 3). 
		Contrasts with simple one-zone models where enrichment proceeds 
		alongside star formation yielding a monotonic 
		AMR~\citep[e.g.][]{Andrews2017, Weinberg2017}. One-zone models of 
		starbursts can produce non-monotonic AMR due to the effect of 
		dilution~\citep{Johnson2020}, but they by construction do not predict 
		multiple abundances at fixed age. Argued using 
		the~\citet{Weinberg2017} 
		% the~\mniiiauthor{Weinberg}{Andrews}{Freudenburg}  
		analytic models that this is a consequence of radial migration - for a 
		smooth star formation history (SFH), the youngest stars at any given 
		radius will have composition reflective of the local equilibrium 
		abundance, and only older stars will have had adequate time to 
		migrate to a similar Galactocentric radius. 
	\end{itemize}

	\item The Young Alpha-Rich Population 
	\begin{itemize} 
		\item Population of young ($\sim$few Gyr), [$\alpha$/Fe]~$\sim$ 
		0.1-0.2 stars in the solar neighbourhood.

		\item Found using stellar ages estimated from carbon-to-nitrogen 
		ratios~\citep{Martig2016}, isochrone matching~\citep{Feuillet2018, 
		Feuillet2019}, and with the asteroseismic ages in the original APOKASC 
		catalog~\citep{Chiappini2015, SilvaAguirre2018, Pinsonneault2014}. 
		\citet{SilvaAguirre2018} demonstrated that these stars have 
		kinematics similar to the rest of the high-$\alpha$ population, and 
		argued based on this that they may be the consequence of stellar 
		mergers or mass transfer events, making truly old stars simply appear 
		younger.

		\item \citet{Mor2019} infer a factor of~$\sim$2 enhancement in the 
		SFH of the Milky Way~$\sim$2 Gyr ago by comparing population synthesis 
		models to observed stellar luminosity functions and color-magnitude 
		diagrams from Gaia data~\citep{GaiaDR2}.~\citet{Isern2019} reach 
		similar conclusions by modeling the white dwarf luminosity function in 
		the solar neighbourhood with Gaia parallaxes. Motivated by these 
		results, \citet{Johnson2020} demonstrate using one-zone chemical 
		evolution models that a recent starburst can produce young, 
		$\alpha$-enhanced stars. Caveat: burst would have had to be 
		sufficiently localized such that the young,~$\alpha$-rich stars remain 
		outliers from an otherwise monotonically descreasing age-[$\alpha$/Fe] 
		relation. 
	\end{itemize}

	\item Metallicity Distributions and the Abundance Gradient 
	\begin{itemize} 
		\item Known for some time that the inner regions of Milky Way-like 
		spirals are more metal-rich than their outskirts (SDSS references: 
		\citealp{Nordstroem2004a, Daflon2009, Frinchaboy2013, Hayden2014}). 
		There are variations depending on what type of stars are considered 
		and what metallicity tracers are used. This qualitative result is 
		also seen in the gas-phase~\citep[see, e.g., the results from the 
		CHAOS project using HII regions;][]{Berg2015, Berg2020}.

		\item We know from APOGEE data that the observed MDF has a metal-poor 
		mode and is skew-positive in the outer galaxy (and conversely, 
		metal-rich and skew-negative in the inner galaxy; 
		\citealp{Hayden2015}). The variation with Galactocentric radius is 
		usually attributed to radial migration of metal-poor (metal-rich) 
		stars from larger (smaller) radii, the same argument that 
		\citep{Sellwood2002} used to interpret the results of 
		\citet{Edvardsson1993} on the observed AMR in the solar neighborhood.

		\item Abundance gradients have been the focus of many studies and 
		are quantified rather extensively, but 
		their origin is somewhat up for debate. Applying the analytic models 
		of~\citet{Weinberg2017}, one could argue that the gradient arises out 
		of variations in the local gas-phase equilibrium abundance as a 
		function of Galactocentric radius. This could be due to variations in 
		the efficiency of outfowing winds removing metals from the star 
		forming reservoir due to a deeper gravitational potential in the inner 
		regions of Milky Way-like spirals.~\citet{Nidever2014} used this 
		methodology to successfully reproduce the APOGEE abundance data. 
		However, recent chemical evolution models have successfully replicated 
		the gradient with no outflowing winds at all 
		\citep[e.g.][]{Minchev2013, Spitoni2019}. This is based on arguments 
		from~\citet{Melioli2008, Melioli2009} and~\citet{Spitoni2008, 
		Spitoni2009}, who studied Galactic fountains and found that ejected 
		metals tend to reaccrete to a Galactocentric radius similar to where 
		they originated. With this result, some authors argue that such 
		outflows do not significantly alter the chemical evolution of a 
		Galactic disc. A notable difference between these two models is that 
		the latter requires significantly lower nucleosynthetic yields to 
		predict physically realistic abundances. 
	\end{itemize}

	\item The [$\alpha$/Fe] bimodality 
	\begin{itemize} 
		\item Milky Way stars segregate themselves into the low- and 
		high-$\alpha$ sequences, a bimodality found in, e.g., 
		Gaia ESO~\citep{Recio-Blanco2014, Rojas-Arriagada2017}, and 
		APOGEE~\citep{Nidever2014, Hayden2015, Weinberg2019}.

		\item Presence is well established, though origin a topic of intense 
		debate.

		\item Notion that it could arise out of radial migration traces back 
		to~\citet{Schoenrich2009}.

		\item \citet{Weinberg2017} models suggest increase in strength of the 
		mass-loading factor $\eta$ at late times would lower the equilibrium 
		abundance, forming stars along the low-$\alpha$ sequence. This plus 
		radial migration is yet unexplored.

		\item \citet{Spitoni2019} demonstrate that two-infall models can 
		reproduce solar annulus data with good agreement. This plus 
		radial migration is yet unexplored.

		\item \citet{Grand2018} find with Auriga~\citep{Grand2017} that early, 
		accretion induced starburst populates the high-$\alpha$ sequence, 
		followed by low-level, sustained star formation on low-$\alpha$ 
		sequence, and a rapid transition between the two ensures chemical space 
		relatively unpopulated. This would imply short $\tau_\star$ (see 
		justification in~\citealp{Weinberg2017}). Ongoing, low-metallicity 
		gas accretion can also populate low-$\alpha$ sequence. 
		\citet{Buck2020b} find results qualitatively similar to second 
		scenario in NIHAO simulation suite~\citep{Wang2015, Buck2020a}. 
		Hydrodynamical simulations take into account radial migration by 
		construction.

		\item \citet{Clarke2019} show that star formation proceeded in clumps 
		in an SPH simulation of an NFW halo using GASOLINE~\citep{NFW1997, 
		Wadsley2017}. The clumps self-enrich, forming stars on the 
		high-$\alpha$ sequence, while more spatially extended, smooth star 
		formation populated the low-$\alpha$ sequence.

		\item No shortage of models that reproduce the dichotomy, yet only 
		those done with hydrodynamical simulations and a handful of others 
		have taken into account radial migration. 
	\end{itemize}

	\item This paper is meant to address the following simple question: When 
	combining simple, conventional assumptions about the star formation and 
	dynamical histories of the Milky Way, what observed results can be 
	replicated? 
\end{itemize}

\section{Methods} 
\label{sec:methods}

\begin{itemize} 
	\item To address the main goal of this paper, we make use of multi-zone 
	chemical evolution models in which the Milky Way is described by a series 
	of concentric annuli. Examples of similar methodologies already in 
	the literature can be found in~\citet{Matteucci1989}, 
	\citet{Schoenrich2009},~\citet{Minchev2013}, and~\citet{Sharma2020}. Here 
	we entertain a handful of models describing the star formation history and 
	the time-dependence of radial migration, then simply assess their 
	predictions in comparison to the results discussed in~\S~\ref{sec:intro}.

	\item Multizone models are a means of extending traditional one-zone 
	models to take into account the motions of stars and gas by allowing the 
	exchange of both between zones.

	\item Our fiducial model has an inside-out star formation history (SFH) 
	with parameters motivated by various observational constraints. Motivated 
	by the findings of~\citet{Mor2019} and~\citet{Isern2019}, we construct a 
	model with a late burst of star formation for comparison. A starburst of 
	similar form was investigated in one-zone models in~\citet{Johnson2020}. 
	For comparison, we also construct a model in which the SFH is constant 
	with time at fixed Galactocentric radius. This is interesting primarily 
	from a theoretical perspective; it removes the effects of a time-varying 
	SFH and quantifies what is predicted when there is ongoing star formation 
	with radial migration.

	\item To include the effects of 
	stellar migration, we make use of data from a hydrodynamical simulation, 
	discussed in~\S~\ref{sec:methods:h277}. This allows us to adopt the 
	dynamical history of a much more sophisticated simulation at face value, 
	providing us with a model for radial migration that requires no free 
	parameters. 
	\begin{itemize} 
		\item The~\citet{Schoenrich2009},~\citet{Minchev2013}, and 
		\citet{Sharma2020} studies chose a model for radial migration that 
		was based on dynamical arguments, which introduced free parameters 
		that then required fitting to data. An advantage of our decision to 
		make use of a hydrodynamical simulation over dynamical arguments is 
		that it's unclear the extent to which fitting to observed data biases 
		the model into agreement with parts of the data that weren't involved 
		in the fit. A hydrodynamical simulation, while still an approximation 
		of reality, is motivated by first principles in that it models the 
		gravitational interactions of star particles with gas and other star 
		particles as well as the diffuse dark matter halo. Furthermore, we 
		choose here a hydrodynamical simulation which is ran from cosmological 
		initial conditions.

		\item The primary disadvantage of this choice is a consequence of the 
		lack of free parameters - the model is rigid, and we cannot explore 
		slight variations. However, in principle one could compare the 
		predictions made by the same chemical evolution models but with 
		different hydrodynamical simulations. 
	\end{itemize}

	\item To fulfill the goals of this paper, we develop and make use of 
	newly released features within the~\texttt{Versatile Integrator for 
	Chemical Evolution} (\texttt{VICE}), which are designed to handle these 
	kinds of simulation with a wide range of flexibility. We reserve 
	description of~\texttt{VICE}'s algorithm for~\S 
	\ref{sec:methods:migration}, first describing our sample of star 
	particles from the hydrodynamical simulation. 
\end{itemize}

\subsection{The Hydrodynamical Simulation} 
\label{sec:methods:h277}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{decomposition.pdf} 
\caption{Radial distributions of our candidate analog star particles 
from~\texttt{h277}. In the top row, we show distributions of~\textit{final} 
radius in bins of birth radius and age. In the bottom row, we show 
distributions of~\textit{birth} radius in bins of final radius and age. Each 
bin in Galactocentric radius is shown in its own panel, denoted in text at the 
top of each panel and by vertical black dashed lines. We color-code the 
distributions according to the age of the star particles, denoted by the 
legend in the upper left panel. We smooth all distributions with a box-car 
width of 0.5 kpc to improve clarity. We omit the distributions for 8 - 10 Gyr 
old stars born in the 9 - 11 and 11 - 13 kpc bins due to an insufficient 
number of star particles with which to calculate the distribution. }
\label{fig:h277_decomposition} 
\end{figure*}

\begin{itemize} 
	\item In this paper we make use of star particles from the~\texttt{h277} 
	simulation~\citep{Christensen2012, Zolotov2012, Loebman2012, Loebman2014, 
	Brooks2014}. A synopsis of the detailed simulation parameters and 
	cosmological model can be found in~\S~2 of~\citet{Bird2020}. We do not 
	go into detail on that here, instead focusing on how we vet the sample of 
	star particles for use in our chemical evolution models.

	\item We find that only~$\sim$3\% of~\texttt{h277}'s star particles formed 
	within the first 1 Gyr of its 13.7 Gyr run, indicating that $T$ = 1 Gyr 
	is a much better estimate of the onset of star formation and thus the 
	chemical evolution in~\texttt{h277} than $T$ = 0. We thus remove the star 
	particles that were born in the first Gyr of evolution, and subtract 1 Gyr 
	from their formation times, thus running our disc models for 12.7 Gyr. As 
	a result, our simulations run from a redshift of~$z \approx$ 3 to the 
	present day.

	\item Of particular importance to have accurately measured formation radii 
	for each star particle that we use in our analysis.~\texttt{h277} did not 
	record the exact birth radius of each star particle; however, each star 
	particle does have an accurate age at each snapshot. If a star particle 
	is sufficiently young in the first snapshot it appears in, then its 
	radius in that snapshot is a reasonable approximation for its birth 
	radius, since its orbit is unlikely to have changed significantly in a 
	short enough time interval. Therefore, we restrict our sample to those 
	with an age at first snapshot of~$\leq$ 150 Myr, and adopt their 
	Galactocentric radius at first snapshot as the birth radius. Also 
	conducted the analysis with age at first snapshot of~$\leq$50 Myr, and 
	found similar results, suggesting this choice does not impact our 
	conclusions. In practice, we find that 150 Myr also provides us with an 
	adequately large number of star particles to sample from.

	\item Based on a kinematic decomposition performed on the present-day 
	phase space distribution of the~\texttt{h277} star particles, we exclude 
	halo stars, but include bulge, pseudobulge, and thin- and thick-disc 
	stars. Even though we are not modeling the abundances in the bulge in this 
	paper, the bulge is believed to have formed in-situ ({\color{red} 
	citation}), while a significant fraction of halo stars are believed to 
	have been accreted ({\color{red} citation}). It's also likely that the 
	Milky Way bulge and disc exchanged statistically significant amounts of 
	stars and gas ({\color{red} citation}), coupling the chemical evolution of 
	the two at least slightly. This effect can be addressed in our models by 
	simply including these star particles in our sample. This yields a sample 
	of 3,019,521 star particles from~\texttt{h277}.

	\item \texttt{h277} had a transient bar during its evolution, but does 
	not have a bar at $z$ = 0. This could mean that the star particles 
	in~\texttt{h277} migrated in a manner which does not reflect the dynamical 
	history of the Milky Way, but at present inferring a star's birth radius 
	observationally is notoriously difficult anyway ({\color{red} citation}), 
	so its likely the impact of this decision is within current 
	observational uncertainties. Nonetheless, it is worth noting that 
	the~\citet{Minchev2013} model, and by extension the~\citet{Minchev2014} 
	and~\citet{Minchev2017} studies as well, selected a hydrodynamical 
	simulation specifically so that it would have a bar at $z$ = 0. A detailed 
	investigation of the impact of bar evolution on stellar migration and thus 
	chemical evolution is outside the scope of this paper, though can be 
	conducted in principle by simply swapping the birth times and initial and 
	final radii of~\texttt{h277} within~\texttt{VICE}, rerunning the 
	simulations, and comparing the results.

	\item Distributions of final radii in bins of birth radii and age are 
	shown in the top row of Fig.~\ref{fig:h277_decomposition}. Conversely, the 
	bottom row shows distributions of birth radii in bins of final radii and 
	age. 
	\begin{itemize} 
		\item Focusing on the top row of panels in 
		Fig.~\ref{fig:h277_decomposition}, we note that for stars born at any 
		radius and time, the distribution of final radii is still peaked near 
		the birth radius. With increasing age, it appears the mode final radius 
		may move slightly inward. The tails of the distributions to large radii 
		are relatively age-independent - some differences between the 0 - 2 and 
		8 - 10 Gyr age bins, but not much. However, the tails of the 
		distributions to small radii are not age-independent, and move toward 
		smaller $R_\text{gal}$ with increasing age. This suggests that radial 
		migration inward and outward occur on different timescales, in 
		particular that inward migration is slower than 
		outward migration. By extension this may suggest that inward and 
		outward migration are tied to different physical 
		processes.~\citet{Roskar2008a} demonstrate using a cosmological 
		simulation that resonant scattering at corotation causes stars to 
		move outward and gas to move inward. It's possible that radial 
		migration inward has different origins.

		\item Focusing on the bottom row of panels in 
		Fig.~\ref{fig:h277_decomposition}, we note that the oldest stars at any 
		Galactocentric radius at the present day were overwhelmingly born at 
		smaller radii. The youngest stars, however, were overwhelmingly born at 
		comparable radii, and the stars of intermediate ages simply span the 
		range in radii between the two. With increasing radius, the 
		differences in the mode of the birth radius distribution between age 
		bins gets larger.

		\item The differences in distributions shown in the top and bottom 
		panels boils down to stellar surface density being a strong function 
		of Galactocentric radius. Take for example the age = 8 - 10 Gyr bin in 
		both $R_\text{Birth}$ = 5 - 7 kpc and $R_\text{Final}$ = 11 - 13 kpc 
		bins (i.e. the red curves in the top-left and bottom-right panels). 
		For these old stars born at 5 - 7 kpc, 11 - 13 kpc is far down the tail 
		of the $R_\text{Final}$ distribution, and yet 5 - 7 kpc is the mode 
		$R_\text{Birth}$ of all old stars presently at these radii. This 
		implies that even though the majority of 8 - 10 Gyr old stars with 
		$R_\text{Final}$ = 11 - 13 kpc were born at 5 - 7 kpc, they make up 
		only a small fraction of the stars with similar birth radii. This is 
		only possible if the stellar surface density gradient is sufficiently 
		steep, which it is known to be~\citep[e.g.][]{Bland-Hawthorn2016}. 
		\begin{itemize} 
			\item Fig.~\ref{fig:h277_decomposition} also demonstrates that the 
			numbers of stars that migrated inward and outward are comparable 
			in~\texttt{h277}. Taking a~$\left|\Delta R_\text{gal}\right| \geq$ 
			500 pc between birth and final radii as the criterion for migrating 
			inward or outward, indeed we find that in our sample, 27\% 
			migrated inward, 29\% migrated outward, and the remaining 44\% 
			stayed near their birth radius. These are global percentages. 
		\end{itemize}

		\item In all bins of birth radius, a good first-order estimate of the 
		probability density that a star has a final radius in the same bin 
		is~$\sim$0.3. With bins in radius on this plot of 2 kpc, this suggests 
		that ~$\sim$40\% of stars migrate significantly by the time 
		they're~$\sim$2 Gyr old. If the SN Ia DTD is a 
		$t^{-1.1} \approx t^{-1}$ power-law as suggested by recent 
		observations~\citep[e.g.][]{Maoz2012, Maoz2017}, 
		then we expect similar numbers of SN Ia events to occur with delay 
		times between 1 and 10 Gyr as we do between 100 Myr and 1 Gyr. With 
		such an extended DTD, and the distributions in final radius shown in 
		the bottom panel of Fig.~\ref{fig:h277_decomposition}, its possible 
		that white dwarfs migrate significant distances before producing a SN 
		Ia event. Indeed, in the ASAS-SN bright supernova catalog,~$\sim$10\% 
		of supernovae are seen at >10 kpc from their host galaxies 
		\citep{Holoien2019}. While this catalog is for~\textit{all} 
		supernovae, the majority of SN events are type Ia anyway. Based on 
		this, it's reasonable to expect that the migration 
		of nucleosynthetic yields may proceed alongside stellar migration, an 
		effect which is often neglected (e.g.~\citealp{Minchev2013}, and the 
		application of the~\citealp{Weinberg2017} analytic models in 
		\citealp{Feuillet2018}). In this paper, we relax this assumption. The 
		application of the~\texttt{h277} star particle data to our model for 
		radial migration and the time dependence thereof is discussed in the 
		next section.

	\end{itemize}

\end{itemize}

\subsection{Radial Migration} 
\label{sec:methods:migration} 
\begin{itemize} 
	\item To simulate our models, we develop and make use of \texttt{VICE}'s 
	\texttt{milkyway} object, an extension of a more general object named 
	\texttt{multizone}. The \texttt{multizone} object is at its core an array 
	of \texttt{singlezone} objects, which are designed to handle 
	simulations of one-zone models and were the focus of 
	\citet{Johnson2020},~\texttt{VICE}'s initial release paper. The 
	\texttt{multizone} object then affords the user the ability to move 
	gas between zones with any given time dependence, and to assign all 
	stellar populations any given zone at any given time following their 
	birth, effectively allowing arbitrarily complex zone and migration 
	schema. The \texttt{milkyway} object is a user-friendly extension of this 
	which enforces a zone configuration in which the Galaxy is modeled as a 
	series of concentric annuli of uniform width~$\Delta R_\text{gal}$. As 
	defaults, it adopts the stellar migration model described in this section 
	{\color{red}and our star formation law described in~\S 
	\ref{sec:methods:sfe}.}

	\item Stars in~\texttt{VICE} are stand-ins for entire stellar 
	populations, and in the~\texttt{milkyway} object, are said to be in a 
	given zone/annulus if their radius is between the inner and outer 
	edges. At all times, their nucleosynthetic products and returned envelopes 
	are placed in the ISM of the annulus that they are in~\textit{at that 
	time}.

	\item Where hydrodynamical and N-body simulations of galaxy evolution 
	often use star particles of a fixed mass,~\texttt{VICE} forms a fixed 
	number of stellar populations in a given zone at a given timestep, 
	and allows their masses to vary to account for variations in the star 
	formation rate. The mass of stars formed in a given zone is divided 
	evenly among the stellar populations that form during a given 
	timestep.

	\item Algorithm based on initial and final radii of star particles in 
	hydrodynamical simulations, for which we've taken~\texttt{h277} as 
	discussed in the previous section.

	\item In modeling the Milky Way as a series of concentric annuli,
	~\texttt{VICE}'s~\texttt{milkyway} object assumes stellar populations to 
	be born at the centres of each annulus. 
	For a stellar population born at time $T$ and Galactocentric radius 
	$R_\text{gal}$, it searches for star particles from~\texttt{h277} that formed at $T \pm$ 300 Myr and $R_\text{gal} \pm$ 250 pc. It then randomly 
	selects a star particle from this subsample with no bias to act as 
	an~\textit{analog}. Adopts the final radius of the analog star particle at 
	face value, and moves from its radius of birth to the final radius at $T$ 
	= 12.7 Gyr with some time dependence. If no candidate analogs are found, 
	search is widened to $T \pm$ 600 Myr and $R_\text{gal} \pm$ 500 pc. If 
	still no candidate analogs are found in this widened search, the stellar 
	population is assumed to remain at its birth radius {\color{red} and to 
	have a final height above the disc midplane of $z$ = 100 kpc.} These 
	stellar populations are few in number. In our fiducial model with an 
	inside-out SFH (see~\S~\ref{sec:methods:sfhs}), these stellar populations 
	account for~$\sim$4.9\% of the simulated stellar populations by number, 
	but only~$\sim$0.56\% by mass. Making up such a small portion of the mass 
	budget, it's not likely they contribute significantly to the chemical 
	evolution of our model Galaxy. 
	\begin{itemize} 
		\item We have zones for each annulus from $R_\text{gal}$ = 0 to 
		20 kpc; there are no zones off the midplane. This retains the 
		assumption that the gas-phase abundances are vertically and 
		azimuthally well-mixed. Each stellar population simply assumes the 
		final height~$\left|z\right|$ above the disc midplane of its assigned 
		analog, though this doesn't enter into the simulations at all; it's 
		purely post-processing information. 
	\end{itemize}

	\item When a star particle is assigned as an analog to a stellar 
	population in our simulations, it is~\textit{not} thrown out of the sample 
	of candidate analogs, in theory allowing a star particle to act as an 
	analog for multiple stellar populations. This is a difference between 
	the~\citet{Minchev2013} model and ours. Where we assign star particles to 
	stellar populations for which~\texttt{VICE} then calculates a stellar mass 
	and composition based on an assumed star formation history, the 
	\citet{Minchev2013} model assigns compositions to star particles.

\begin{figure} 
\centering 
\includegraphics[scale = 0.45]{migration.pdf} 
\caption{A diagram illustrating how Galactocentric radius changes with time 
for two stellar populations under our migration schema: diffusion (crimson, 
solid), linear (lime, dot-dashed), post-process (black, dotted), and 
sudden (blue, dashed). Here the initial and final radii and birth times are 
chosen at random for illustrative purposes. With the initial and final 
Galactocentric radii of a stellar population, its birth time, and one of these 
assumptions about the time-dependence of migration, the Galactocentric radius 
at all times is known. } 
\label{fig:migration_schema} 
\end{figure}

	\item Our migration models 
	\begin{itemize} 
		\item All neglect radial gas flows, this paper instead focusing on 
		four simple models for how the radius of a stellar population's orbit 
		changes with time. Investigation of our models with radial gas flows 
		would be an interesting extension to this paper.

		\item \textbf{Post-processing}: Stars stay where they are born until 
		the final timestep. Based on the assumption that stellar populations 
		do not contribute to enrichment beyond their birth 
		radius~\citep[e.g.][]{Minchev2013}. Each annulus simulated as a 
		one-zone model independent of all other zones. Shown in black dotted 
		line in Fig.~\ref{fig:migration_schema}.

		\item \textbf{Sudden}: A random number is drawn from a uniform 
		distribution between the time of birth and the present day. That time 
		is taken to be the time of instantaneous migration to the present-day 
		annulus. Emulates a scenario in which a single dynamical interaction 
		changes the orbital radius of a star. Can be thought of as a 
		time-dependent extension of the post-processing scenario. Shown in 
		blue dashed line in Fig.~\ref{fig:migration_schema}.

		\item \textbf{Diffusion}: A case in which stars migrate in a 
		continuous, time-dependent manner. If stars move to their final 
		radii via a random walk, then the mean displacement of stars that 
		migrate similar distances would scale with~$\sqrt{\text{age}}$. This 
		is shown in the red solid line in Fig.~\ref{fig:migration_schema}. 
		This is our fiducial migration model; we present results using this 
		model except where otherwise noted. It is so named because it 
		corresponds to a scenario in which the random walk carries out the 
		diffusion of angular momentum.

		\item \textbf{Linear}: A simple variation of the 
		diffusion model. Has no physical motivation other than numerical 
		ease, but together with the diffusion model constitutes a test of how 
		sensitive our models are to the assumed time-dependence of stellar 
		migration. Demonstrated by green dot-dashed line in 
		Fig.~\ref{fig:migration_schema}. 
	\end{itemize}

	\item Further details on the implementation of the~\texttt{milkyway} 
	object, the more general~\texttt{multizone} object, and other features of 
	\texttt{VICE} can found in its documentation.~\footnote{
		\url{https://vice-astro.readthedocs.io} 
	}

	\item We have a sample of 3,019,521 candidate analog star particles 
	from~\texttt{h277}, only~$\sim$57\% of which are disc stars. Since we're 
	modeling the thin and thick disc populations here,~$\sim$1.72 million is a 
	much better estimate of the number of analogs that we can realistically 
	sample from. We let star formation extend out to 15.5 kpc, beyond which 
	we force the star formation rate to zero at all times.~\texttt{VICE} does 
	form stellar populations at all timesteps in the annuli; they simply have 
	zero mass and thus do not contribute to the chemical evolution or 
	recycling, though they do contribute to the computational overhead. We 
	take $\Delta R_\text{gal}$ = 100 pc as the width of each annulus from 
	$R_\text{gal}$ = 0 to 20 kpc and a timestep size of $\Delta T$ = 10 Myr 
	from $T$ = 0 to 12.7 Gyr (see discussion in~\S~\ref{sec:methods:h277} for 
	our choice of time-interval). With the resulting 200 zones and 1,271 
	timesteps, we let~\texttt{VICE} form~$n$ = 8 stellar 
	populations per zone per timestep, resulting in 2,033,600 stellar 
	populations with predicted masses and abundances, 1,574,800 of which form 
	between~$R_\text{gal}$ = 0 and 15.5 kpc and have nonzero mass, reasonably 
	within the limit of what we can sample. These simulations run in~$\sim$2 
	hours and take up~$\sim$235 MB of disc space per output, including the 
	extra data that we record for each stellar population's analog star 
	particle. 
\end{itemize}

\subsection{Nucleosynthetic Yields, Outflows, and Recycling}  
\label{sec:methods:yields} 
\begin{itemize} 
	% \item Brief background on~\texttt{VICE}'s algorithm: we form a given 
	% number of stellar populations in each zone and at each timestep. They 
	% then migrate between zones according to our algorithm and eject CCSN and 
	% SN Ia products as smooth functions of time according to our yields.

	\item \textit{Fractional net} yields, as required by~\texttt{VICE}. 
	Recycling is implemented separately, such that stellar envelopes are 
	returned to the ISM at the birth composition of each stellar population. 
	\texttt{VICE} takes the general approach of returning previously produced 
	material according to a stellar lifetime model and injecting newly 
	produced nucleosynthetic products as described below. Also clarify that 
	these are not~\textit{effective} yields in that outflows are also 
	implemented separately.

	\item CCSN events are assumed to occur immediately following the formation 
	of their progenitor stars. This is an adequate approximation, because the 
	lifetimes of massive stars are short compared to the relevant timescales 
	for galaxy evolution. For the most massive stars, the lifetimes are 
	comparable to the timestep size that we take use in these simulations 
	anyway. This assumption implies a linear relationship between CCSN 
	enrichment and the star formation rate: 
	\begin{equation} 
	\dot{M}_x^\text{CC} = y_x^\text{CC}\dot{M}_\star 
	\end{equation} 
	\begin{itemize} 
		\item Physically, the CCSN yield $y_x^\text{CC}$ is the fraction of a 
		stellar population's initial mass that is converted into some element 
		$x$ and ejected to the ISM, neglecting outflows.

		\item \texttt{VICE} includes functionality with which to calculate 
		the value of $y_x^\text{CC}$ for a handful of nucleosynthetic yield 
		studies. Details can be found in~\S~2 of~\citet{Johnson2020} and in 
		\texttt{VICE}'s documentation. A detailed investigation of 
		CCSN nucleosynthetic yields which releases new features to these 
		calculations will be presented in Griffith et al. (2021, in prep).

		\item Take $y_\text{O}^\text{CC}$ = 0.015 and $y_\text{Fe}^\text{CC}$ 
		= 0.0012 from~\citet{Johnson2020}, who in turn adopt these values 
		from~\citet{Weinberg2017}. 
	\end{itemize}

	\item SN Ia products injected with a $t^{-1.1}$ delay-time distribution 
	(DTD) with a minimum delay-time of $t_\text{D}$ = 150 Myr. This is the 
	default DTD in~\texttt{VICE}, adopted in~\citet{Johnson2020}, and is 
	suggested by recent observational results comparing the cosmic SN Ia rate 
	to the cosmic SFH~\citep{Maoz2012, Maoz2017}. In a 
	one-zone model at times $t > t_\text{D}$, the enrichment rate for some 
	element~$x$ can be expressed as the product of some yield $y_x^\text{Ia}$ 
	and the star formation history weighted by the DTD: 
	\begin{subequations}\begin{align} 
	\dot{M}_x^\text{Fe} &= y_x^\text{Fe}\langle\dot{M}_\star\rangle_\text{Ia} 
	\label{eq:mdot_ia} 
	\\ 
	&= y_x^\text{Fe} \ddfrac{
		\int_0^{t - t_\text{D}} \dot{M}_\star(t') R_\text{Ia}(t - t') dt' 
	}{
		\int_{t_\text{D}}^{t_\text{max}} R_\text{Ia}(t - t') dt' 
	} 
	\label{eq:mdot_ia_expanded} 
	\end{align}\end{subequations} 
	where $R_\text{Ia}$ is the DTD itself, in units of M$_\odot^{-1}$ 
	Gyr$^{-1}$. Like the CCSN yield,~$y_x^\text{Ia}$ is simply the fraction of 
	a single stellar population's mass that is converted into the element~$x$ 
	over the ensuing SN Ia duty cycle. It can also be expressed as an integral 
	over the DTD: 
	\begin{equation} 
	y_x^\text{Ia} = m_x^\text{Ia} \int_{t_\text{D}}^{t_\text{max}} 
		R_\text{Ia}(t) dt = m_x^\text{Ia} \frac{N_\text{Ia}}{M_\star} 
	\label{eq:y_x_ia} 
	\end{equation} 
	where the~$m_x^\text{Ia}$ is the mass of some element~$x$ produced in a 
	single SN Ia event on average, and the integral evaluates to the mean 
	number of Ia events~$N_\text{Ia}$ per mass of stars formed~$M_\star$. 
	\begin{itemize} 
		\item \texttt{VICE} enforces~$t_\text{max}$ = 15 Gyr always, though 
		provided one is consistent with equations~\refp{eq:y_x_ia} and 
		\refp{eq:mdot_ia_expanded}, the results are independent of 
		$t_\text{max}$ since the integrals cancel.

		\item Extending this to multi-zone models is simple - rather than an 
		integral over the star formation history of a given annulus, the rate 
		becomes a summation over all stellar populations that are in a given 
		zone at some time: 
		\begin{equation} 
			\dot{M}_x^\text{Ia} = y_x^\text{Ia} \ddfrac{
				\sum_i M_i R_\text{Ia}(\tau_i) 
			}{
				\int_{t_\text{D}}^{t_\text{max}} R_\text{Ia}(t) dt 
			} 
		\end{equation} 
		where~$M_i$ and~$\tau_i$ are the mass and age of the~$i$'th stellar 
		population, respectively.

		\item Initially adopt~$y_\text{O}^\text{Ia}$ = 0 and 
		$y_\text{Fe}^\text{Ia}$ = 0.0017 from~\citet{Johnson2020} and 
		\citet{Weinberg2017}. However, in practice we find that the e-folding 
		timescales of star formation in our models are sufficiently long (see 
		discussion in~\S~\ref{sec:methods:sfhs}) such that our fiducial, 
		inside-out SFH model predicts [O/Fe]~$\approx$~+0.05 for 
		young stars. We therefore multiply this value by a factor of 
		10$^{0.1}$, adopting instead~$y_\text{Fe}^\text{Ia}$ = 0.00214 so 
		that our fiducial model predicts a late-time [O/Fe] ratio in better 
		agreement with observations. This change is likely within the 
		uncertainties in nucleosynthetic yields anyway.

		\item Our model assumes that all supernova yields of O and Fe are 
		independent of metallicity. While this appears to be empirically true 
		for CCSN yields of these elements~\citep[e.g.][]{Weinberg2019, 
		Griffith2020}, recent evidence by~\citet{Brown2019} suggests that 
		the local specific SN Ia rate shows a strong, inverse dependence on 
		galaxy stellar mass. They argue that this may imply a metallicity 
		dependent~$R_\text{Ia}$ that produces more SN Ia events at early times 
		when the metallicity is low. While we adopt a metallicity independent 
		$y_\text{Fe}^\text{Ia}$ in this paper,~\texttt{VICE} allows users to 
		specify any functional form for $y_\text{Fe}^\text{Ia}$ as a function 
		of the total abundance by mass $Z$, allowing future studies of the 
		impact of this to proceed straight-forwardly. 
	\end{itemize}

	\item Similar to SN Ia, the equation detailing asymptotic giant brach 
	(AGB) star enrichment changes from an integral over the SFH to a summation 
	over the stellar populations in a given zone at some time.~\texttt{VICE} 
	in its current iteration forces AGB enrichment to be included in its 
	simulations, though the yields of O and Fe from AGB stars are negligible 
	compared to their supernova yields, and the results presented in this 
	paper can be interpreted as if they were zero. 
	\begin{itemize} 
		\item The algorithm is based on determining the fraction of a single 
		stellar population's mass that is in the form of stars that will have 
		ended their post-main-sequence lifetime during the next timestep. 
		The mass of those stars and their birth metallicity can then be 
		used to determine a yield given a table of $y_x^\text{AGB}$ values 
		sampled on a grid of stellar mass and metallicity, for which we take 
		values from the FRUITY database of net yeilds~\citep{Cristallo2011}. 
		Since these yields are not important for this paper, however, we do 
		not go into further detail. More information on \texttt{VICE}'s 
		treatment of AGB enrichment can be found in its documentation and in 
		\S~2.6 of~\citet{Johnson2020}. 
	\end{itemize}

	\item Outflows are directly tied to nucleosynthetic yields, because the 
	absolute scaling of nucleosynthetic yields and the efficiency with which 
	galactic winds remove them from the star forming reservoir determine the 
	\textit{effective} yield: the amount of metals that are not only produced 
	but added to the star forming reservoir. 
	\begin{itemize} 
		\item Based on studies of galactic fountains demonstrating that 
		ejected metals tend to fall back to a similar radius at which they 
		were produced~\citep[e.g.][]{Melioli2008, Melioli2009, Spitoni2008, 
		Spitoni2009}, a number of chemical evolution models 
		\citep[e.g.][]{Minchev2013, Spitoni2019} neglect outflows, arguing 
		that they are not a necessary ingredient to chemical evolution models. 
		However, with the yields we've adopted, our models require significant 
		metal ejection to predict realistic abundances. For this reason, 
		studies which neglect outflows adopt significantly lower 
		nucleosynthetic yields as a consequence.

		\item There is a near one-to-one degeneracy between the scaling of 
		nucleosynthetic yields and the efficiency of metal ejection in 
		galaxies. With nucleosynthetic yields that were conventional at the 
		time,~\citet{Dalcanton2007} demonstrated that significant outflows 
		are required to lower effective yields and predict abundances in 
		agreement with observations. This is a solution to the so-called 
		``G-dwarf problem'' in which closed-box models of chemical evolution 
		\citep[see the review in, e.g.,][]{Tinsley1980}  catastrophically 
		over-predict the number of super-solar metallicity stars 
		\citep{vandenBergh1962, Pagel1975}. However, recent findings with 
		regard to black hole formation and stellar explodability have 
		demonstrated that many massive stars simply do not produce a supernova 
		event (see theoretical discussion by, e.g.,~\citealp{Pejcha2015, 
		Sukhbold2016}, and observation evidence from~\citealp{Gerke2015, 
		Adams2017, Basinger2020}). This challenges the results of 
		\citet{Dalcanton2007}, suggesting that nucleosynthetic yields are 
		intrinsically low, and the extent to which theoretically predicted 
		stellar explodability models reduce the need for outflowing winds 
		remains an unanswered question for future studies. 
	\end{itemize}

	\item Mass-loading factor $\eta$ defined as the ratio of mass outflow 
	rates from the ISM to the SFR: 
	\begin{equation} 
	\eta \equiv \frac{\dot{M}_\text{out}}{\dot{M}_\star} 
	\end{equation} 
	\citet{Weinberg2017} demonstrate that, to first order, this parameter and 
	the yields of a given element set the late-time equilibrium abundance. 
	Here we adopt a scaling of~$\eta$ with Galactocentric radius~$R_\text{gal}$ 
	such that the equilibrium abundance as a function of~$R_\text{gal}$ 
	reproduces a metallicity gradient in agreement with observations.

	\item A fundamental observable, the observed metallicity gradient in the 
	Milky Way has been the focus of a considerable number of studies to date. 
	\begin{itemize} 
		\item \citet{Nordstroem2004a} find a gradient of -0.099 kpc$^{-1}$ in 
		[Fe/H] in main sequence stars from GCS~\citep{Nordstroem2004b, 
		Holmberg2007}.

		\item \citet{Daflon2009} find a gradient of -0.04 kpc$^{-1}$ in 
		[S/H] in OB stars

		\item \citet{Frinchaboy2013} find a gradient of -0.09 kpc$^{-1}$ in 
		[M/H] in open clusters.

		\item \citet{Hayden2014} also find -0.09 kpc$^{-1}$ in [M/H] for 
		$R_\text{gal}\gtrsim$ 6 kpc for low-$\alpha$ stars. For 
		$R_\text{gal}\lesssim$ 6 kpc, they find a relatively flat gradient.

		\item \citet{Weinberg2019} finds -0.06 kpc$^{-1}$ in mode([Mg/H]) for 
		upper red giant branch disc stars (see their Fig. 23). 
	\end{itemize}

	\item The procedure outlined in this section makes two assumptions: 1) 
	that the mode abundance at a given radius reflects the equilibrium 
	value at that radius, and 2) that radial migration does not significantly 
	impact the overall form of the gradient. We demonstrate that this holds in 
	our simulations in~\S~\ref{sec:metallicity_gradient}.

	\item For $\alpha$ elements,~\citet{Weinberg2017} defines the equilibrium 
	abundance under a constant SFH as: 
	\begin{equation} 
	Z_{\alpha,\text{eq}} = \frac{
		y_\alpha^\text{CC}
	}{
		1 + \eta(R_\text{gal}) - r
	} 
	\end{equation} 
	where $r$ is the recycling parameter ($\approx$ 0.4 for the sake of this 
	scaling with a~\citetalias{Kroupa2001} IMF; see discussion near the end of 
	this section). Solving for $\eta(R_\text{gal})$ yields: 
	\begin{equation} 
	\eta(R_\text{gal}) = \frac{
		y_\alpha^\text{CC}
	}{
		Z_{\alpha,\text{eq}}
	} + r - 1 
	= \frac{y_\alpha^\text{CC}}{Z_{\alpha,\odot}}10^{-\text{mode([X/H])}
	(R_\text{gal})} + r - 1 
	\end{equation}

	\item We assume a slope of -0.08 kpc$^{-1}$, in tentative agreement with 
	the previous studies that quote the slope of the gradient mentioned above. 
	To set the normalization, we assume the mode([X/H]) to be~$\sim$+0.3 at 
	$R_\text{gal}$ = 4 kpc, since this would produce mode([X/H])~$\approx$~0 at 
	$R_\text{gal}\approx$ 7 - 9 kpc. This results in the following form for 
	$\eta$ as a function of Galactocentric radius: 
	\begin{equation} 
	\eta(R_\text{gal}) = \frac{y_\alpha^\text{CC}}{Z_{\alpha,\odot}} 
	10^{(-0.08\text{ kpc}^{-1})(R_\text{gal} - \text{4 kpc}) + 0.3} + r - 1 
	\label{eq:eta} 
	\end{equation} 
	where we adopt our yield of O for $y_\alpha^\text{CC}$ and the solar 
	abundance of O of $Z_{\text{O},\odot}$ = 0.00572 from~\citet{Asplund2009}.

	\item This does assume a uniformly linear gradient at all $R_\text{gal}$. 
	\citet{Hayden2014} do find the gradient in [M/H] to flatten for 
	$R_\text{gal}\lesssim$ 6 kpc, challenging this assumption. However, this 
	procedure can be easily repeated for any desired gradient, since the 
	functional form simply goes into the power of 10 in equation~\refp{eq:eta}.

	\item The top panel of Fig.~\ref{fig:eta_tau_sfh} plots this scaling of 
	$\eta$ with~$R_\text{gal}$, highlighting a value of~$\sim$2.15 for the 
	solar circle in the red dotted line. 
\end{itemize}

\begin{figure} 
\centering 
\includegraphics[scale = 0.65]{eta_tau_sfh.pdf} 
\caption{\textbf{Top}: Our implemented scaling of the mass loading factor 
$\eta$~with Galactocentric radius (black) as defined by equation 
\refp{eq:eta}.~\textbf{Bottom}: The e-folding timescales of the star formation 
histories of our model galaxies (black). These values come from a fit to the 
$\Sigma_\star$-age relation in bins of $R/R_\text{e}$ for~$10^{10.5}$~- 
$10^{11}$~M$_\odot$~Sa/Sb Hubble type spiral galaxies as reported by 
\citet[][see discussion in~\S~\ref{sec:methods:sfhs}]{Sanchez2020}. The 
horizontal and vertical red dashed lines in both panels highlight a mass 
loading factor of~$\eta \approx$ 2.15 and a star formation timescale of 
$\tau_\text{sfh} \approx$ 15 Gyr at an assumed radius of the sun of 
$R_\odot$ = 8 kpc. 
} 
\label{fig:eta_tau_sfh} 
\end{figure}

\begin{itemize} 
	\item \citet{Weinberg2017} defined the~\textit{cumulative return fraction}
	$r$ to be the fraction of a single stellar population's initial mass that 
	has been returned to the ISM. In detail, $r$ is a complicated function of 
	the age of a stellar population $\tau$ which depends on the assumptions 
	about stellar lifetimes, the IMF, and an initial-remnant mass 
	relation~\citep[e.g.][]{Kalirai2008}. 
	\begin{itemize} 
		\item \citet{Weinberg2017} demonstrated that the assumption 
		of~\textit{instantaneous recycling} is a reasonable approximation, 
		where instantaneous recycling refers only to~\textit{previously 
		produced} nucleosynthetic products. We clarify that previous studies 
		have made this approximation for newly produced material as well; 
		while that assumption is valid for prompt sources like CCSNe, it fails 
		for enrichment channels with significant DTDs, such as SNe Ia or 
		AGB stars.~\citet{Weinberg2017} demonstrate that $r$ = 0.4 (0.2) is a 
		good approximation for a~\citetalias{Kroupa2001} (
		\citetalias{Salpeter1955}) IMF. However, this was demonstrated for 
		smooth star formation histories 
		and in parameter spaces conducive to analytic solution. Because 
		numerical integration of $r(\tau)$ is neither challenging nor 
		time-consuming,~\texttt{VICE} by default implements continuous 
		recycling by solving $r(\tau)$ at the beginning of each simulation 
		given the IMF, the~\citet{Kalirai2008} initial-remnant mass model, and 
		the assumption that $\tau = \tau_\odot(M/M_\odot)^{-3.5}$. We also 
		assume a post-main sequence lifetime of 10\% of the main sequence 
		lifetime for all stars. Further details on the detailed form of 
		$r(\tau)$ and its numerical integration within~\texttt{VICE} can be 
		found in its documentation. 
	\end{itemize}

	\item In a one-zone model, the recycling rate can be expressed as an 
	integral over the star formation history: 
	\begin{equation} 
	\dot{M}_x^\text{r} = \int_0^t Z_x(t') \dot{M}_\star(t') \dot{r}(t - t') dt' 
	\end{equation} 
	where $Z_x$ is the abundance by mass of the element~$x$ in the ISM at a 
	time $t'$. Like SN Ia enrichment rates, extending this to multi-zone models 
	changes the integral over the star formation history to a summation over 
	the stellar populations in a given zone at some time: 
	\begin{equation} 
	\dot{M}_x^\text{r} = \sum_i Z_{x,i} M_i \dot{r}(\tau_i) 
	\end{equation} 
	In the case of the gas recycling rate, the equation has the same form, but 
	without the weighting by metallicity.

	\item We implement continuous recycling in our simulations, but make use 
	of the instantaneous approximation in a handful of places in this paper 
	(e.g. in our scaling of $\eta$ with $R_\text{gal}$, and in approximating 
	SN Ia rates in~\S~\ref{sec:metallicity_space}). 
\end{itemize}

\subsection{Star Formation Histories} 
\label{sec:methods:sfhs}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{evol.pdf} 
\caption{The surface densities of star formation $\dot{\Sigma}_\star$ (top 
row), infall $\dot{\Sigma}_\text{in}$ (middle row), and gas $\Sigma_\text{gas}$ 
(bottom row) as functions of simulation time for our four fiducial SFHs: 
constant (far left), inside-out (left middle), late-burst (right-middle), 
and outer-burst (far right). We plot curves for the annuli whose inner radii 
are 3 kpc (grey), 5 kpc (black), 7 kpc (red), 9 kpc (yellow), 11 kpc (green), 
13 kpc (blue), and 15 kpc (purple) (see equations~\refp{eq:constant_sfh}, 
\refp{eq:insideout_sfh},~\refp{eq:lateburst_sfh}, and~\refp{eq:outerburst_sfh} 
for the mathematical definition of each SFH). } 
\label{fig:evol} 
\end{figure*}

\begin{itemize} 
	\item \texttt{VICE}'s simulations runs in either infall, star formation, or 
	gas mode, referring simply to which component of the evolutionary history 
	the user has specified. The fiducial starburst models presented in 
	\citet{Johnson2020} ran in infall mode, but here we run things in star 
	formation mode, since we are after specific forms for the star formation 
	histories of our models.

	\item Appendix~\ref{sec:normalize_sfh} presents justification of how we 
	normalize the parameters of our star formation histories to produce a 
	realistic model Galaxy at the end of the simulation. In short, it takes in 
	a unitless description of the time-dependence of the SFH at a given 
	Galactocentric radius, denoted $f(t|R_\text{gal})$, and a unitless 
	description of the radial dependence of the present-day stellar surface 
	density, denoted $g(R_\text{gal})$. In short, we integrate 
	$f(t|R_\text{gal})$ with time for each annulus, assuming $R_\text{gal}$ to 
	correspond to the centre of the zone, and attach a prefactor to 
	$f(t|R_\text{gal})$ at each $R_\text{gal}$ such that the desired gradient 
	is achieved with a total stellar mass similar to that of the Milky Way. 
	This procedure neglects the impact of radial migration, assuming that it 
	does not significantly alter the form of $g(R_\text{gal})$. We demonstrate 
	that these assumptions hold in~\S 
	\ref{sec:methods:surface_density_gradient}, in which we also detail our 
	adopted form of $g(R_\text{gal})$. As long as this assumption is not 
	violated, the equation derived in Appendix~\ref{sec:normalize_sfh} can be 
	used to normalize the parameters of future models of spiral galaxies.

	\item We present four fiducial SFHs, which we dub ``constant'', 
	``inside-out'', ``late-burst'', and ``outer-burst''. They're defined as 
	follows: 
	\begin{itemize} 
		\item \textbf{Constant}: The SFH at a given radius is time-independent. 
		\begin{equation} 
		f_\text{C}(t|R_\text{gal}) = 1 
		\label{eq:constant_sfh} 
		\end{equation} 
		This case is of particular theoretical interest because it quantifies 
		the effect of ongoing with star formation with radial migration, and 
		no additional effects.

		\item \textbf{Inside-Out}: 
		\begin{equation} 
		f_\text{IO}(t|R_\text{gal}) = (1 - e^{-t/\tau_\text{rise}})
		e^{-t/\tau_\text{sfh}} 
		\label{eq:insideout_sfh} 
		\end{equation} 
		We adopt this scenario over the traditional linear-times-exponential 
		form of $f(t|R_\text{gal})~\sim~te^{-t/\tau_\text{sfh}}$, because the 
		latter does not offer control over the position of the maximum. The 
		form we adopt has a maximum near $\tau_\text{rise}$, for which we adopt 
		a value 2 Gyr everywhere in this paper. We find that this produces a 
		peak in star formation at lookback times of~$\sim$10 Gyr, corresponding 
		to a redshift of~$z \approx$~2, which is around cosmic high noon. In 
		this paper $\tau_\text{sfh}$ is a function of $R_\text{gal}$ here, and 
		we discuss it briefly in a few paragraphs.

		\item \textbf{Late-Burst}: An inside-out SFH with a gaussian describing 
		a starburst. 
		\begin{equation} 
		f_\text{LB}(t|R_\text{gal}) = f_\text{IO}(t|R_\text{gal}) 
		(1 + A_\text{b}e^{-(t - t_\text{b})^2/2\sigma_\text{b}^2}) 
		\label{eq:lateburst_sfh} 
		\end{equation} 
		$A_\text{b}$ is a dimensionless parameter describing the strength of 
		the starburst, $t_\text{b}$ is the time of the local maximum in the SFH 
		during the burst, and $\sigma_\text{b}$ is the width of the gaussian 
		describing it. Loosely motivated by the findings of~\citet{Isern2019} 
		and~\citet{Mor2019}. Here we take $A_\text{b}$ = 1.5, $t_\text{b}$ = 
		10.8 Gyr, and $\sigma_\text{b}$ = 1 Gyr.

		\item \textbf{Outer-Burst}: A variation of the late-burst model in 
		which only $R_\text{gal}\geq$ 6 kpc experience the starburst. Loosely 
		motivated by findings of~\citet{Vincenzo2020} where a hydrodynamical 
		simulation of a Milky Way-like galaxy showed radially dependent 
		infall. 
		\begin{equation} 
		f_\text{OB}(t|R_\text{gal}) = \begin{cases} 
		f_\text{IO}(t|R_\text{gal}) & (R_\text{gal}~<~\text{6 kpc}) \\ 
		f_\text{LB}(t|R_\text{gal}) & (R_\text{gal}~\geq~\text{6 kpc}) 
		\end{cases} 
		\label{eq:outerburst_sfh} 
		\end{equation} 
	\end{itemize}

	\item Derive e-folding timescales of star formation $\tau_\text{sfh}$ 
	from the data in~\citet{Sanchez2020}. 
	\begin{itemize} 
		\item They present the stellar surface density $\Sigma_\star$ as a 
		function of age in bins of $R/R_\text{e}$ for MaNGA galaxies, where 
		$R_\text{e}$ is the half-light radius. They conduct this analysis in 
		bins of stellar mass and for different Hubble types. Here take their 
		M$_\star$ = 10$^{10.5}$ - 10$^{11}$ M$_\odot$ bin for Sa/Sb spirals 
		(i.e. Milky Way-like galaxies).

		\item Their reported $\Sigma_\star$-age relation is not robust enough 
		to get individual SFHs directly, but does allow the parameters of some 
		fiducial mathematical model to be fit to the population-averaged 
		trends. Assuming the $f_\text{IO}(t|R_\text{gal})$ form, we 
		simultaneously fit the normalization and the e-folding timescale 
		$\tau_\text{sfh}$ to these data. Although the normalization is 
		irrelevant to our simulations and determined via the method outlined 
		in Appendix~\ref{sec:normalize_sfh}, we adopt the resulting 
		$\tau_\text{sfh}$-$R_\text{gal}$ relation in our models. Results are 
		shown in Fig.~\ref{fig:eta_tau_sfh}.

		\item Note that the star formation timescales are long, even for the 
		solar annulus ($\tau_\text{sfh} \approx$~15 Gyr at $R_\odot$ = 8 kpc) 
		and especially for the outer galaxy. Beyond the solar annulus, SFHs are 
		nearly constant after the initial rise at early times.

		\item With our adopted gradient (see~\S 
		\ref{sec:methods:surface_density_gradient}, we know the present-day 
		half-mass radius to be very near 4 kpc (this is just doing a couple 
		integrals over the area of the disc). The findings of 
		\citet{Garcia-Benito2017} and~\citet{GonzalezDelgado2014} suggest that 
		half-light radii are marginally larger than half-mass radii. Based on 
		equations (4) of~\citet{GonzalezDelgado2014} relation the two for 
		circular apertures, we expect our model galaxy to have a half-light 
		radius near 5 kpc. We therefore adopt $R_\text{e}$ = 5 kpc in 
		calculating $\tau_\text{sfh}$ as a function of radius. {\color{red} 
		As I understand it, there are some results that suggest this value for 
		the Milky Way as well?} 
	\end{itemize}

	\item Given the assumed star formation histories, the gas supply at all 
	times is known via the SFE timescale $\tau_\star$ (discussed 
	in~\S~\ref{sec:methods:sfe}). With the amount of gas lost to star formation 
	and outflows at each timestep, the infall rate is also known at all 
	timesteps. The results of all three are shown in Fig.~\ref{fig:evol}. 
\end{itemize}

\subsection{Surface Density Gradient} 
\label{sec:methods:surface_density_gradient}

\begin{figure} 
\centering 
\includegraphics[scale = 0.45]{surface_density_gradient.pdf} 
\caption{The surface density of gas (blue) and stars (red) as predicted by our 
inside-out SFH model. The dotted black line with the higher normalization 
denotes a thin disc profile with scale length $R_t$ = 2.5 kpc; the other 
denotes a thick disc profile with scale length $R_T$ = 2.0 kpc, and a ratio of 
$\Sigma_T/\Sigma_t$ = 0.27 at $R_\text{gal}$ = 0. The black line denotes the 
sum of the two; this is the surface density gradient of the Milky Way as 
reported by~\citet{Bland-Hawthorn2016}, renormalized to imply the same total 
stellar mass within the disc. } 
\label{fig:surface_density} 
\end{figure}

\begin{itemize} 
	\item As discussed in~\S~\ref{sec:methods:sfhs}, Appendix 
	\ref{sec:normalize_sfh} presents justification of a recipe in which we 
	select a unitless, unnormalized form describing the scaling of the 
	stellar surface density with Galactocentric radius, denoted 
	$g(R_\text{gal})$. Here we adopt the following double exponential form, 
	describing the thin and thick discs of the Milky Way: 
	\begin{equation} 
	g(R_\text{gal}) = e^{-R/R_t} + \frac{\Sigma_T}{\Sigma_t}e^{-R/R_T} 
	\end{equation} 
	where $R_t$ and $R_T$ are the scale radii of the thin and thick discs, 
	respectively, and $\Sigma_T/\Sigma_t$ is the ratio of their surface 
	densities at $R_\text{gal}$ = 0. In this paper, we adopt $R_t$ = 2.5 kpc, 
	$R_T$ = 2.0 kpc, and $\Sigma_T/\Sigma_t$ = 0.27 from the findings of 
	\citet{Bland-Hawthorn2016}.

	\item Adopt the~\citet{Licquia2015} total stellar mass of 
	$(6.08\pm1.14)\times10^{10}~M_\odot$. We're including bulge star particles 
	in our sample of candidate analogs from~\texttt{h277}, so we model the 
	entire stellar mass as opposed to just the disc, for 
	which~\citet{Licquia2015} found $(5.17\pm1.11)\times10^{10}~M_\odot$.

	\item Surface density gradient from fiducial model with inside-out SFH, 
	plotted in Fig.~\ref{fig:surface_density} (stars in red and gas in blue). 
	Radial migration indeed didn't change the overall scaling of 
	$\Sigma_\star$ with $R_\text{gal}$ at the radii that we care about in 
	this paper (3 kpc~$\lesssim R_\text{gal} \lesssim$~15 kpc), only 
	introducing scatter. Gas disc appears to be flatten at 
	$R_\text{gal}~\gtrsim$ 6 kpc; this is a consequence of our model for star 
	formation efficiency (see discussion in~\S~\ref{sec:methods:sfe}). Black 
	dotted lines show the individual thin and thick disc components that we 
	adopt from~\citet{Bland-Hawthorn2016}, with the solid line denoting the 
	sum of the two, all re-normalized such that the integral over the surface 
	area of the model Galaxy implies a total stellar mass in agreement with 
	our adopted value from~\citet{Licquia2015}. 
\end{itemize}

\subsection{Star Formation Efficiency} 
\label{sec:methods:sfe}

\begin{figure} 
\centering 
\includegraphics[scale = 0.6]{sfe.pdf} 
\caption{The star formation efficiency timescale $\tau_\star$ as a 
function of Galactocentric radius at simulation times of 2 Gyr (red), 4 Gyr 
(yellow), 6 Gyr (green), 8 Gyr (blue), 10 Gyr (purple), and 12.7 Gyr (i.e. 
the present day, black) predicted by our inside-out SFH model. }
\label{fig:sfe} 
\end{figure}

\begin{itemize} 
	\item The term ``star formation efficiency'' (SFE) is an overloaded term in 
	the literature. In the star formation/feedback literature, it usually 
	refers to the fraction of a molecular cloud's mass which will eventually 
	be converted into stars. In the chemical evolution literature, however, it 
	usually refers to the inverse timescale relating the star formation rate 
	within some gas reservoir and the mass of the gas reservoir itself: 
	$\tau_\star \equiv \Sigma_\text{gas}/\dot{\Sigma}_\star$. High (Low) 
	values of $\tau_\star$ indicate slow (fast) star formation and thus low 
	(high) SFE; when we refer to SFE here, we're referring to the definition 
	based on this timescale. 
	\begin{itemize} 
		\item Potentially note that this is often referred to as the 
		``depletion time'' in star formation literature, and the 
		\citet{Weinberg2017} definition of depletion 
		time:~$\tau_\text{dep} \equiv \tau_\star/ (1 + \eta - r)$. 
	\end{itemize}

	\item This is a topic of intense observational inquiry, results of which 
	we review in this section in the interest of obtaining an observationally 
	motivated star formation law. 
	\begin{itemize} 
		\item In practice, many chemical evolution studies adopt a simple 
		power-law for the Kennicutt-Schmidt law relating~$\Sigma_\text{gas}$ 
		and~$\dot{\Sigma}_\star$: $\dot{\Sigma}_\star~\sim 
		\Sigma_\text{gas}^N$, where~\citet{Kennicutt1998} infer 
		$N = 1.4 \pm 0.15$ across a sample of quiescent spiral galaxies and 
		infrared and circumnuclear starbursts.~\citet{delosReyes2019} derive a 
		similar value of $N = 1.41 \pm 0.07$ for local quiescent spiral, 
		dwarf, and low surface brightness galaxies, further demonstrating that 
		much of the observed scatter is intrinsic.

		\item \citet{Liu2015} demonstrate that the derived value of~$N$ is 
		sensitive to the assumed form of the CO-to-H$_2$ conversion factor 
		($\alpha_\text{CO}$); for fixed~$\alpha_\text{CO}$, they find 
		$N = 1.14 \pm 0.02$, but~$N = 1.60 \pm 0.03$ for a continuously varying 
		$\alpha_\text{CO}$ for a sample of 181 local galaxies with infrared 
		luminosities spanning nearly five orders of magnitude. Much of the 
		uncertainty in the detailed form of the star formation law is likely 
		a consequence of the ongoing debate about~$\alpha_\text{CO}$ (and 
		other mathematical defintions of the conversion factor as well, such 
		as X(CO); see discussion in~\citealp{Kennicutt2012}).

		\item In extending the~\citet{delosReyes2019} study to the most 
		extreme infrared-luminous and circumnuclear starburst galaxies, 
		\citet{Kennicutt2020} recently found a value of~$N = 1.50 \pm 0.05$. 
		Although they determine that a single power law is a reasonable recipe 
		for models of Galaxy evolution, they demonstrate that there is 
		evidence for significant breaks in both the power-law indeces and the 
		zeropoints. They argue that these breaks are physical in origin, and 
		speculate that it is tied to the transition from a mixed atomic and 
		molecular ISM in normal disc galaxies to a nearly fully molecular ISM 
		in starburst galaxies. A transition to a linear 
		$\dot{\Sigma}_\star-\Sigma_\text{gas}$ relation at a surface density 
		above which the molecular fraction~$f_\text{mol} \approx 1$ is 
		consistent with the finding that star formation proceeds only in the 
		molecular phase~\citep[e.g.][]{Leroy2008, Leroy2013}.

		\item Consistent with the finding that the intrinsic scatter in the 
		observed~$\dot{\Sigma}_\star-\Sigma_\text{gas}$ relation is physical 
		in origin,~\citet{Ellison2020b} demonstrate that this relation (among 
		other fundamental correlations) shows significant galaxy-to-galaxy 
		variations in both slope and normalization, suggesting that it is not 
		universal between galaxies. \citet{Leroy2013} also find evidence that 
		$\tau_\text{mol}$, the value of $\tau_\star$ for a gas reservoir with 
		$f_\text{mol}$ = 1, is multivalued at fixed $\Sigma_{\text{H}_2}$, 
		suggesting that the rate of star formation is set not only by the 
		density of the gas reservoir, but other environmental parameters as 
		well. 
	\end{itemize}

	\item Although we acknowledge the collective result that an individual 
	galaxy would not obey the observed, population-averaged 
	$\dot{\Sigma}_\star-\Sigma_\text{gas}$ relation, we decide to adopt 
	such a prescription for our models here. Our motivation for doing so 
	is two-fold. 
	\begin{itemize} 
		\item In practice, we find that our mathematical formalism for 
		$\tau_\star$ does not significantly impact our conclusions; we 
		demonstrate this in Appendix~\ref{sec:sfe_variations}. For this 
		reason, a simple formalism is its own reward for our purposes.

		\item As discussed in~\S~\ref{sec:methods:sfhs}, we are running 
		\texttt{VICE} in star formation mode; this simply means that we 
		have specified the~\textit{star formation history} of the Galaxy, 
		rather than the infall history or the ISM surface density as 
		functions of simulation time and radius. While many galaxy 
		evolution models use these observed star formation laws to infer 
		the star formation rate from the ISM surface density, here we are 
		doing the inverse - inferring the ISM surface density from the 
		star formation rate. We therefore do not know the properties of 
		the ISM in our simulations a priori, and must resort to simple 
		assumptions anyway. An investigation of more detailed 
		prescriptions for star formation efficiency in models for 
		enrichment in the Milky Way is an interesting which we must 
		reserve for future work due to how we have constructed the 
		simulations presented in this paper. 
	\end{itemize}

	\item Motivated by these recent results suggesting nuance within the 
	star formation law~\citep{Leroy2013, Ellison2020b, Kennicutt2020}, we 
	implement in our simulations a three-component power-law based on the 
	results presented in~\citet{Krumholz2018}. They construct a turbulence and 
	mass-transfer driven theoretical model for star formation in disc galaxies, 
	and present a comparison of its predictions under a handful of parameter 
	choices to the data from~\citet{Bigiel2010} and~\citet{Leroy2013} (see 
	their Fig. 2). We find that the following by-eye fit is a reasonable 
	description of the aggregate data: 
	\begin{subequations}\begin{align} 
	\dot{\Sigma}_\star &\sim \Sigma_\text{gas}^N \\ 
	N &= \begin{cases} 
	1.0 & (\Sigma_\text{gas} \geq 2\times10^7~\text{M}_\odot~\text{kpc}^{-2}) 
	\\ 
	3.6 & (5\times10^6~\text{M}_\odot~\text{kpc}^{-2} \leq \Sigma_\text{gas} 
		\leq 2\times10^7~\text{M}_\odot~\text{kpc}^{-2}) 
	\\ 
	1.7 & (\Sigma_\text{gas} \leq 5\times10^6~\text{M}_\odot~\text{kpc}^{-2}) 
	\end{cases} 
	\label{eq:ks_law} 
	\end{align}\end{subequations}

	\item The apparent linearity of the relationship above~$\sim2\times10^7$ 
	M$_\odot$ kpc$^{-2}$ suggests that in this regime, star formation is 
	proceeding at the fastest possible rate, and that $\tau_\star$ = 
	$\Sigma_\text{gas}/\dot{\Sigma}_\star$ = constant. The results of 
	\citet{Leroy2008, Leroy2013} and~\citet{Kennicutt2020} would suggest that 
	this is the regime in which~$f_\text{mol}$ = 1. We therefore adopt the 
	assumptions that $f_\text{mol}$ is unity above an ISM surface density of 
	$\Sigma_\text{gas} = 2\times10^7$~M$_\odot$~kpc$^{-2}$ and that 
	$\tau_\star$ assumes that value of $\tau_\text{mol}$ at these densities, 
	increasing with decreasing~$f_\text{mol}$.

	\item With the formulation of the Kennicutt-Schmidt Law described by 
	equation~\refp{eq:ks_law} and the mathematical definition 
	$\tau_\star \equiv \Sigma_\text{gas}/\dot{\Sigma}_\star$, we can derive 
	$\tau_\star-\Sigma_\text{gas}$ or $\tau_\star-\dot{\Sigma}_\star$ 
	relationships as required by~\texttt{VICE}. With~$\tau_\star$ = 
	$\tau_\text{mol}$ at~$\Sigma_\text{gas}~\geq~2\times10^7$~M$_\odot$ 
	kpc$^{-2}$ setting the overall normalization, the following describes the 
	resultant~$\tau_\star-\Sigma_\text{gas}$ relationship: 
	\begin{equation}
	\tau_\star = \begin{cases} 
	\tau_\text{mol} & (\Sigma_\text{gas} \geq \Sigma_\text{gas,1}) 
	\\ 
	\tau_\text{mol} \left(\frac{\Sigma_\text{gas}}{\Sigma_\text{gas,1}}
		\right)^{\beta_1} & (\Sigma_\text{gas,2} \leq \Sigma_\text{gas} \leq 
		\Sigma_\text{gas,1}) 
	\\ 
	\tau_\text{mol} \left(\frac{\Sigma_\text{gas,2}}{\Sigma_\text{gas,1}}
		\right)^{\beta_1} \left(\frac{\Sigma_\text{gas}}{\Sigma_\text{gas,2}}
		\right)^{\beta_2} & (\Sigma_\text{gas} \leq \Sigma_\text{gas,2}) 
	\end{cases} 
	\end{equation} 
	where we adopt~$\Sigma_\text{gas,1} = 2\times10^7$ M$_\odot$ kpc$^{-2}$, 
	$\Sigma_\text{gas,2} = 5\times10^6$ M$_\odot$ kpc$^{-2}$,~$\beta_1$ = 
	-2.6, and~$\beta_2$ = -0.7\footnote{
		$\beta = 1 - N$, where N is the power-law index of the 
		$\dot{\Sigma}_\star-\Sigma_\text{gas}$ relationship. 
	}. The additional factor of 
	$(\Sigma_\text{gas,2}/\Sigma_\text{gas,1})^{\beta_1}$ simply ensures that 
	this formalism is piecewise-continuous.

	\item Based on the observed Kennicutt-Schmidt relation at different 
	redshifts,~\citet{Tacconi2018} suggest that~$\tau_\text{mol}$ should 
	scale with redshift~$z$ and the deviation from the star forming main 
	sequence~$\delta\text{MS}$ via~$\tau_\text{mol} \propto (1 + z)^{-0.6} 
	\delta\text{MS}^{-0.44}$. We don't take into account the effect of 
	$\delta\text{MS}$ in our models, but we do investigate the redshift 
	dependence. A reasonable approximation to the $t-z$ relation out 
	to~$z \approx$~3 assuming typical~$\Lambda$CDM cosmology is given by: 
	\begin{equation} 
	\frac{t}{t_0} \approx (1 + z)^{-5/4} 
	\end{equation} 
	where $t_0$ is the present-day age of the universe, and $t$ is not 
	simulation time but the age of the universe at any given redshift. 
	Plugging this relation into the~\citet{Tacconi2018} scaling yields the 
	following time-dependence for~$\tau_\text{mol}$: 
	\begin{equation} 
	\tau_\text{mol} = \tau_{\text{mol},0}(t/t_0)^{12/25} \approx 
	\tau_{\text{mol},0}(t/t_0)^{1/2} 
	\end{equation} 
	where $\tau_{\text{mol},0}$ is simply $\tau_\text{mol}$ at the 
	present day. We generalize this formula to the following form: 
	\begin{equation} 
	\tau_\text{mol} = \tau_{\text{mol},0}(t/t_0)^\gamma 
	\end{equation} 
	In this paper we present simulations which adopt~$\tau_{\text{mol},0}$ 
	= 2 Gyr~\citep{Leroy2008, Leroy2013, Tacconi2018} and~$\gamma$~= 1/2 based 
	on this argument. We have also ran simulations which adopt 
	$\tau_{\text{mol},0}$ = 1 Gyr and~$\gamma$~= 0 (a time-independent 
	$\tau_{\text{mol}}$), and found similar results.

	\item Fig.~\ref{fig:sfe} shows $\tau_\star$ as a function of $R_\text{gal}$ 
	at six different time stamps predicted by our fiducial, inside-out SFH 
	model. Wherever~$\tau_\star$ is at its minimum value is where the ISM in 
	that annulus is fully molecular. 
	\begin{itemize} 
		\item In the fiducial inside-out model, the molecular fraction is near 
		unity out to~$R_\text{gal} \approx$~6 kpc at all times.

		\item From the actual value of $\tau_\star$ at a given radius and time 
		and the assumed $\tau_\text{mol}$ in the model, we can derive the 
		model predicted molecular fractions within the disk via 
		$f_\text{mol} = \tau_\text{mol}/\tau_\star$, then subsequently the 
		HI + HII and H$_2$ masses from $f_\text{mol}$ and the total gas supply 
		after subtracting 27\% to account for helium.

		\item These post-processing calculations suggest that our fiducial 
		inside-out model predicts an HI + HII mass of~$5.54\times10^9$ 
		M$_\odot$ and an H$_2$ mass of~$7.14\times10^9$~M$_\odot$ within 
		$R_\text{gal}$ = 20 kpc, the maximum radius in our model. This 
		predicts a total H mass of~$1.27\times10^{10}$~M$_\odot$, and a total 
		ISM mass of~$1.74\times10^{10}$~M$_\odot$ after adding 27\% back to 
		account for helium. This yields a global molecular fraction of 
		$f_\text{mol}$ = H$_2$ / (HI + HII + H$_2$) = 56\%. In comparison with 
		observed results, this is an overprediction of~$f_\text{mol}$; 
		\citet{Kalberla2009} report a value of~$8\times10^9$ and 
		$2.5\times10^9$~M$_\odot$ for the HI and H$_2$ masses within 60 kpc, 
		the bulk of which is in the disk. They report an additional 
		$\sim2\times10^9$~M$_\odot$ in the warm ionized medium (HII). 
		\citet{Heyer2015} argue for a lower H$_2$ mass of~$1\times10^9$ 
		M$_\odot$. Our fiducial model is over-predicting the H$_2$ mass by a 
		factor of~$\sim$3 and under-predicting the HI + HII mass by a factor 
		of~$\sim$2.

		\item Whatever the source of this discrepancy may be, we present in 
		Appendix~\ref{sec:sfe_variations} a variation of our fiducial model 
		with a significantly different assumption about~$\tau_\star$, and 
		demonstrate that this decision does not impact our general 
		conclusions. We reserve discussion on potential sources of this 
		discrepancy to Appendix~\ref{sec:sfe_variations} as well. {\color{red} 
		This discussion may move back to this section, but I had some ideas 
		on this, so I moved stuff later so that the methods section doesn't 
		get lost in minutia. }
	\end{itemize} 
\end{itemize}

\subsection{Summary} 
\label{sec:methods:summary}

\begin{itemize} 
	\item In summary, our fiducial model has an inside-out SFH (see~\S 
	\ref{sec:methods:sfhs}) with the star formation law as described in~\S 
	\ref{sec:methods:sfe}, radial migration the proceeds according to the 
	diffusion model (see~\S~\ref{sec:methods:migration}), and yields and 
	outflows as described in~\S~\ref{sec:methods:yields}.

	\item We have also conducted runs with the three other SFHs, the three 
	other migration prescriptions, and the three other SFE prescriptions - a 
	total of 64 simulations, as well as a variety of other test cases. In this 
	paper, we present results wherever the model predictions are sensitive to 
	the assumptions. However, in general the differences can be understood 
	with only the variations in star formation history and the qualitative 
	notion that many stars have moved beyond their birth radius.

	\item To ensure that resolution does not affect our results, we ran the 
	same set of models with~$n$ = 2 stellar populations per zone per 
	timestep, and found similar predictions. 
\end{itemize}

\section{Metallicity Space} 
\label{sec:metallicity_space}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.28]{ofe_feh_densitymap.pdf} 
\caption{[O/Fe]-[Fe/H] diagrams for 15 galactic regions spanning five bins in 
$R_\text{gal}$ and~$\left|z\right|$. Each region has its own panel, with radial 
bins shown in columns denoted at the top of the figure, and with 
$\left|z\right|$ bins shown in rows denoted in text in the middle column. In 
each panel, we plot $N$ = 10,000 points sampled from our simulated 
stellar populations in each region predicted by our inside-out SFH, where the 
probability of sampling is proportional to the present-day mass of each stellar 
population. In all panels points are color-coded according to the 
Galactocentric radius of birth of the stellar population. For reference, we 
plot in a solid black line in all panels the gas-phase [O/Fe]-[Fe/H] track 
predicted by the same SFH in the $R_\text{gal}$ = 8 kpc annulus, but with the 
post-processing migration model; this curve is the same in all panels. }
\label{fig:ofe_feh_diagram} 
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.42]{tracks.pdf} 
\caption{\textbf{Left}: Gas phase evolutionary tracks in the [O/Fe]-[Fe/H] 
plane for our inside-out SFH with either post-processing (dotted lines) or 
diffusion (solid lines) migration models. We plot tracks for seven annuli, 
color-coded according to their Galactocentric radius and denoted by the legend 
in the lower-left. We mark simulation times of 2, 4, 6, 8, 10, and 12.7 Gyr in 
X's for the diffusion model and points for the post-processing model. 
\textbf{Right}: The proxy for the SN Ia rate defined in equation 
\refp{eq:ia_rate_proxy} as a function of simulation time for the same annuli 
as in the left-hand panel. We multiply rates at each radii here by various 
prefactors to improve of clarity. }
\label{fig:tracks} 
\end{figure*}

\begin{itemize} 
	\item Fig.~\ref{fig:ofe_feh_diagram} shows a scatter plot of 10,000 
	randomly sampled stellar populations in five bins of $R_\text{gal}$ and 
	three bins of $\left|z\right|$ ($R_\text{gal}$ = 3 - 5 kpc, 5 - 7 kpc, 
	7 - 9 kpc, 9 - 11 kpc, and 11 - 13 kpc; $\left|z\right|$ = 0 - 0.5 kpc, 
	0.5 - 1 kpc, and 1 - 2 kpc). These are the same bins and same scheme for 
	organizing the panels as in Fig. 4 of~\citet{Hayden2015}.

	\item The width of the low-$\alpha$ sequence predicted by the model comes 
	from radial migration. Though this is somewhat guaranteed by our model 
	in choosing equilibrium abundances that reflect a realistic metallicity 
	gradient, it is in good agreement with~\citet{Schoenrich2009} and 
	\citet{Nidever2014}.

	\item The low-$\alpha$ sequence shifts from a high [Fe/H] locus at small 
	$R_\text{gal}$ to low [Fe/H] at high~$R_\text{gal}$, in agreement with the 
	observed distributions in APOGEE presented in~\citet{Hayden2015}.

	\item High-$\alpha$ stars are most prevalent at low~$R_\text{gal}$ and 
	high~$\left|z\right|$, and conversely for the low-$\alpha$ stars, also 
	in agreement with~\citet{Hayden2015}. 
	\begin{itemize} 
		\item Similar results are found for different SFHs. This suggests that 
		this observed result is a natural consequence of stellar migration.

		\item Only minor difference worth noting is that the starburst models 
		predict a slightly higher characteristic [O/Fe] ($\sim$+0.1) for the 
		low-$\alpha$ sequence. This is a natural consequence of the starburst 
		producing young,~$\alpha$-enhanced stars~\citep{Johnson2020}. 
	\end{itemize}

	\item Left-hand panel of Fig.~\ref{fig:tracks} compares the tracks 
	predicted by our fiducial, inside-out SFH assuming diffusion migration 
	(sudden) versus post-processing (dotted) for the gas-phase of a handful of 
	radii denoted by the legend. Predicted [O/Fe]-[Fe/H] tracks for the 
	diffusion model show significant deviations from the post-processing 
	model. We demonstrate here that this is due to variability in the SN Ia 
	rate induced by the time-dependent radial migration of the diffusion 
	model. Simulation times of 2, 4, 6, 8, 10, and 12.7 Gyr shown in points 
	and X's for the two models.

	\begin{itemize} 
		\item For each zone,~\texttt{VICE} provides in its outputs the rates 
		of infall and star formation, the mass of the ISM, and the relevant 
		abundance information for each element along with the associated 
		MDFs at the final timestep. To determine the SN Ia rates, we therefore 
		have to approximate from the output.

		\item The time-derivative of the mass of Fe in a given annulus is 
		given by: 
		\begin{equation}
		\dot{M}_\text{Fe} \approx y_\text{Fe}^\text{CC}\dot{M}_\star + 
		y_\text{Fe}^\text{Ia}\langle\dot{M}_\star\rangle_\text{Ia} - 
		\frac{M_\text{Fe}}{M_g}\dot{M}_\star(1 + \eta(R_\text{gal}) - r) 
		\end{equation} 
		where this is an approximation because in detail, there is a small 
		contribution from AGB stars, and the recycling in the simulation is 
		done continuously, whereas here we simply take $r \approx$ 0.4 
		(appropriate for a~\citetalias{Kroupa2001} IMF; 
		\citealp{Weinberg2017}). This equation can be derived from the 
		\citet{Weinberg2017} analytic models assuming CCSN and SN Ia 
		enrichment for Fe with instantaneous recycling of previously produced 
		Fe.~\texttt{VICE}'s science documentation could also be referenced 
		here; it has a nice detailed section on its treatment of each term in 
		handling enrichment rates \footnote{
			\url{https://vice-astro.readthedocs.io/en/latest/science_documentation/enrichment/index.html}
		}. 
		Rearranging this for the term describing the rate of injection due to 
		SNe Ia events, and normalizing by $M_\text{Fe}$ yields the following 
		proxy with units of frequency: 
		\begin{equation} 
		\frac{
			y_\text{Fe}^\text{Ia}\langle\dot{M}_\star\rangle_\text{Ia}
		}{
			M_\text{Fe} 
		} \approx 
		\frac{\dot{M}_\text{Fe}}{M_\text{Fe}} - y_\text{Fe}^\text{CC}\frac{
			\dot{M}_\star 
		}{
			M_\text{Fe} 
		} + \frac{\dot{M}_\star}{M_g}(1 + \eta(R_\text{gal}) - r) 
		\label{eq:ia_rate_proxy} 
		\end{equation} 
		This term on the left-hand side can be substituted with 
		$m_\text{Fe}^\text{Ia}\dot{N}_\text{Ia}/M_\text{Fe}$, where 
		$m_\text{Fe}^\text{Ia}$ is the average mass of Fe produced by a single 
		SN Ia event, and $\dot{N}_\text{Ia}$ is the SN Ia rate itself. For 
		this reason, this equation constitutes a straight-forward proxy for 
		the SN Ia rate at any given time.

		\item This proxy is plotted against simulation time in the right-hand 
		panel of Fig.~\ref{fig:tracks} for the same annuli as in the left-hand 
		panel, with multiplicative factors added for visual clarity, diffusion 
		model again shown in solid lines, post-processing in dotted lines. 
		Whenever and wherever there is a deficit in SN Ia events relative to 
		the post-processing model, the diffusion model tends toward higher 
		[O/Fe] values than the post-processing scenario. Conversely, lower 
		[O/Fe] for an excess in SN Ia events.

		\item SN Ia rates show high-amplitude variability on Gyr timescales, 
		with low-amplitude white-noise on shorter timescales, potentially 
		introduced at least in part by our discretization of the disc into 
		annuli and the evolution into timesteps. The log-scaled y-axis makes 
		it clear that the fractional amplitude is higher near the outskirts 
		of the disc. This makes physical sense, because the stellar number 
		density is much lower there, and as such would be much more 
		susceptible to sampling noise - that is, a single star migrating 
		has a larger fractional impact on the stellar density and thus the 
		supernova rates at large radii than small radii. 
	\end{itemize}

	\item This is proof of concept that radial migration of nucleosynthetic 
	yields can occur alongside stellar migration for delayed sources. In 
	principle, it is reasonable to expect similar effects for s-process 
	elements like carbon, nitrogen, strontium, yttrium, zirconium, etc. which 
	are produced in AGB stars, though we do not investigate the impact for 
	these elements here.

	\item In the literature, it's not uncommon to adopt tracks for different 
	Galactocentric radii in the [O/Fe]-[Fe/H] plane to infer birth radii for 
	observed stars. While an additional dimension such as age could mitigate 
	these potential issues, we caution against inferring birth radii in this 
	manner, because the tracks themselves appear to be sensitive to the 
	dynamical history of the Galaxy. Based on the left-hand panel of Fig. 
	\ref{fig:tracks}, this effect could bias the inferred radii by many kpc. 
	This however doesn't appear to be an issue for the low-$\alpha$ sequence, 
	where the width of the [Fe/H] distribution appears to come from migration 
	itself, as it did in~\citet{Schoenrich2009} and~\citet{Nidever2014}. 
	We therefore recommend that such a technique be restricted to 
	[O/Fe]~$\lesssim$+0.1 stars.

	\item Demonstrate in~\S~\ref{sec:age_alpha:migration} that this is a means 
	with which to form $\alpha$-rich and $\alpha$-poor stars - or rather 
	Fe-poor and Fe-rich, respectively. 
\end{itemize}

\section{Metallicity Gradient} 
\label{sec:metallicity_gradient}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{metallicity_gradient.pdf} 
\caption{Radial abundance gradients in [O/H] (top, red) [Fe/H] (top, blue), 
and [O/Fe] (bottom) for our four fiducial SFHs - constant (far left), 
inside-out (left-middle), late-burst (right-middle), and outer-burst (far 
right). We plot the gas phase abundance at the present day as a function of 
Galactocentric radius in solid lines. Stars denote the mode of the stellar 
MDF of the 100-pc width annulus at a given radius, with shaded regions 
marking the 16th and 84th percentiles thereof. Black lines in the top panels 
denote our target [$\alpha$/H] gradient of mode([$\alpha$/H]) = +0.3 at 
$R_\text{gal}$ = 4 kpc with a slope of -0.08 kpc$^{-1}$. } 
\label{fig:metallicity_gradient} 
\end{figure*}

\begin{itemize} 
	\item Scaling of $\eta$ with $R_\text{gal}$ based on reproducing the 
	observed mode([$\alpha$/H])-$R_\text{gal}$ trend, neglecting radial 
	migration (see~\S~\ref{sec:methods:yields}). The target gradient is 
	shown in a solid black line in the top panels of Fig. 
	\ref{fig:metallicity_gradient}.

	\item In the top panels, red and blue stars show the mode O and Fe 
	abundances in each annulus, and the shaded region shows the 16th and 
	84th percentiles of the MDF in that zone. Solid lines show the gas-phase 
	abundance gradient at the present day. Bottom panels show the same thing 
	for [O/Fe].

	\item Gradient is indeed recovered in [O/H], and radial migration appears 
	to only induce scatter. While Fe did not enter into our procedure for 
	setting the metallicity gradient, the model predicts a similar gradient 
	for [Fe/H].

	\item Clear that the MDF shows a metal-rich mode and skew-negative shape 
	in the inner galaxy for both O and Fe. $\alpha$-enhanced tail there as 
	well. We demonstrate in~\S~\ref{sec:metallicity_gradient} that the MDF 
	does shift to skew-positive in the outer galaxy, though this isn't as 
	visually obvious from this plot due to the scatter in the mode at these 
	radii.

	\item Details of the [O/Fe] gradient seem to be sensitive to differences 
	in our SFHs, especially in the inner galaxy.

	\item Constant SFH is the only model in which the present-day gas phase 
	gradient matches the stellar gradient at all radii. In remaining models, 
	the present-day gas-phase abundance is above the majority of the stars 
	because the star formation rate has decreased. We therefore expect 
	observational studies of abundance gradients to differ noticeably between 
	gas and stars.

	\item Stellar gradient is somewhat shallower in the late-burst model; this 
	is because of the dilution associated with the starburst. Target gradient 
	represents the equilibrium abundance at all radii, and we deliberately 
	perturbed it from equilibrium, so any deviations from the expectation are 
	a consequence of that.

	\item Late-burst model has super-equilibrium gas phase abundance at the 
	present day. Can be seen by comparing it to the outer-burst model's 
	gas phase gradient and seeing that it has a break at $R_\text{gal}$ = 6 
	kpc, the threshold for the late starburst in this model. This is a 
	consequence of the starburst as well - in infall driven starbursts, 
	re-enrichment can produce super-equilibrium abundances which then decay 
	back to the equilibrium abundance as the star formation rate declines 
	\citep{Johnson2020}. 
\end{itemize}

% \subsection{The Observed Sample} 
% \label{sec:methods:observed_sample}

% \begin{itemize} 
% 	\item For the age-metallicity and age-[$\alpha$/Fe] relations, we compare 
% 	to the results of~\citet{Feuillet2019}. Also compared 
% 	to~\citet{Feuillet2018}, the primary difference being that solar 
% 	metallicity stars are found to be considerably younger in the earlier 
% 	study.

% 	\item While we make use of DR16 in comparing our predicted MDFs to the 
% 	APOGEE data,~\citet{Feuillet2018} and~\citet{Feuillet2019} made use of the 
% 	14th data release (DR14;~\citealp{Abolfathi2014}). We don't expect this 
% 	slight difference to impact our conclusions. 
% \end{itemize}

\section{Metallicity Distribution Functions} 
\label{sec:mdfs}

\subsection{[O/H] and [Fe/H]} 
\label{sec:mdfs:oh_feh}

\begin{itemize} 
	\item MDFs in bins of Galactocentric radius are a fundamental observable 
	to test the validity of any chemical evolution model. In this section we 
	compare our predicted MDFs to those observed in the 16th data release 
	(DR16;~\citealp{Ahumada2020}) of the Apache Point Observatory Galaxy 
	Evolution Experiment (APOGEE;~\citealp{Majewski2017}). The data is 
	reduced using the APOGEE Stellar Parameters and Chemical Abundances 
	Pipeline (ASPCAP;~\citealp{Holtzman2015, GarciaPerez2016}). For further 
	details on the APOGEE survey, a brief summary can be found in~\S~2 of 
	\citet{Weinberg2019}. 
	% A part of the Sloan 
	% Digital Sky Survey (SDSS), APOGEE data is collected with a 300-fiber 
	% H-band spectrograph~\citep{Wilson2020} on the 2.5-meter Sloan Foundation 
	% telescope at Apache Point Observatory~\citep{Gunn2006}. The APOGEE sample 
	% largely consists of evolved stars with 2MASS~\citep{Skrutskie2006} 
	% magnitudes in the range 7 < $H$ < 13.8 sampled on a grid of sightlines 
	% at Galactic latitudes $b$ = -8$^\circ$, -4$^\circ$, 0$^\circ$, +4$^\circ$, 
	% and +8$^\circ$ and a wide range of longitudes. \citet{Nidever2015} 
	% describes the data processing pipeline for APOGEE, providing the input to 
	% the APOGEE Stellar Parameters and Chemical Abundances Pipeline (ASPCAP; 
	% \citealp{Holtzman2015,GarciaPerez2016}). ASPCAP simultaneously fits 
	% elemental abundances, effective temperatures, and surface gravities using a 
	% grid of synthetic spectra predicted by 1-dimensional stellar atmospheric 
	% models assuming local thermodynamic equilibrium~\citep{Meszaros2012, 
	% Zamora2015} and the spectral line list provided in~\citep{Shetrone2015}. 
	% {\color{red} (1-D LTE correct?)}

	\item We restrict our sample to stars with effective temperatures of 4000 
	K $\leq T_\text{eff} \leq$ 4600 K, surface gravities of 1.0 
	$\leq \log g \leq$ 2.5, and signal-to-noise ratios of at least 100. These 
	cuts ensure that our sample consists of stars on the upper red giant 
	branch, safely excluding red clump stars to avoid obvious systematics in 
	the abundance distributions. 
\end{itemize}

\begin{figure} 
\centering 
\includegraphics[scale = 0.34]{mdf_3panel_fe.pdf} 
\caption{Metallicity Distribution Functions in [Fe/H] predicted by our 
late-burst model (left) and as observed in APOGEE DR16 (right), for stars and 
simulated stellar populations with present day $\left|z\right|$ = 0 - 0.5 kpc 
(bottom), 0.5 - 1 kpc (middle), and 1 - 2 kpc (top). MDFs are shown in bins 
of Galactocentric radius: 3 - 5 kpc (black), 5 - 7 kpc (red), 7 - 9 kpc 
(yellow), 9 - 11 kpc (green), 11 - 13 kpc (blue), and 13 - 15 kpc (purple). 
The points near the top of the bottom panels denote what the mode abundance 
would be if it followed our target gradient of [Fe/H] = +0.3 at $R_\text{gal}$ 
= 4 kpc and a slope of -0.08 kpc$^{-1}$, assuming the inner radius of each bin 
(i.e. there is no point plotted for 15 kpc). All distributions are smoothed 
with a box-car width of [Fe/H]~$\pm$~0.1. } 
\label{fig:mdf_3panel_fe} 
\end{figure}

\begin{figure} 
\centering 
\includegraphics[scale = 0.34]{mdf_3panel_o.pdf} 
\caption{The same as Fig.~\ref{fig:mdf_3panel_fe}, but for [O/H].} 
\label{fig:mdf_3panel_o} 
\end{figure}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{ofe_mdfs_insideout.pdf} 
\caption{Predicted distributions in [O/Fe] in 15 Galactic regions and in two 
bins in [Fe/H]. Columns correspond to bins in~$R_\text{gal}$, denoted at the 
top of each column. Rows correspond to bins in~$\left|z\right|$, denoted in 
text in the left-hand column. Distributions are color-coded according to the 
[Fe/H] the sample is drawn from, denoted by the legend in the upper right 
panel. Solid lines represent that predicted by our inside-out SFH, while 
dashed lines correspond the fits to the APOGEE DR16 data presented in Vincenzo 
et al. (2021, in prep), which quantify the intrinsic distributions accounting 
for observational uncertainties and the APOGEE selection function. Our 
simulated distributions are smoothed with a box-car width of [O/Fe]~$\pm$~0.02 
to improve clarity. }
\label{fig:ofe_mdfs_insideout} 
\end{figure*}

\begin{itemize} 
	\item Previously known that the MDFs in the disc midplane as observed in 
	APOGEE show mode [$\alpha$/H] and [Fe/H] abundances that depend on 
	Galactocentric radius, with a skew-negative distribution in the inner 
	Galaxy and a skew-positive distribution in the outer Galaxy. Off the 
	midplane, the MDFs merge and converge on [$\alpha$/H]~$\approx$~[Fe/H] 
	$\approx$~-0.5~\citep{Hayden2015, Weinberg2019}. This result is 
	replicated for the observations in the right-hand column of panels in Fig. 
	\ref{fig:mdf_3panel_fe} and Fig.~\ref{fig:mdf_3panel_o}. 
	\begin{itemize} 
		\item Similar mode [O/H] and [Fe/H] between the 3 - 5 and 5 - 7 kpc 
		in the APOGEE observations. What could be the origin of this? 
		Cessation of star formation in the inner Galaxy? (see Fig. 1 of 
		\citealp{Peek2009} and Fig. 2 of~\citealp{Fraternali2012}). This 
		would imply very few stars formed in the most metal-rich regions of 
		the Galaxy, cutting off the MDF at high [O/H], [Fe/H]. This would 
		suggest that the Milky Way has begun the quenching of star formation, 
		a process believed to begin the centres of galaxies at this mass 
		\citep[e.g.][]{Ellison2020a}. 
	\end{itemize}

	\item Left-hand panels of Figs.~\ref{fig:mdf_3panel_fe} 
	and~\ref{fig:mdf_3panel_o} show the distributions predicted by our 
	late-burst model. They successfully replicate the qualitative result that 
	the mode [X/H] varies with present-day Galactocentric radius, but fail to 
	show a similar mode abundance between the 3 - 5 and 5 - 7 kpc bins. 
	Potentially linked to the cessation of star formation in inner 
	Galaxy~\citep{Peek2009, Fraternali2012}, not included in our models.

	\item Beyond the midplane, our models fail to fully replicate the 
	convergence of the MDFs at [X/H]~$\approx$~-0.5. The observed MDF at 
	small radii shifts from skew-negative with a metal-rich mode to 
	skew-positive with a metal-poor mode with increasing $\left|z\right|$. In 
	our predicted MDFs for the inner galaxy, the mode does shift to lower 
	[X/H], though not to the same extent as in the observations. There is also 
	very little change in skewness with~$\left|z\right|$ predicted, in tension 
	with observations. 
	\begin{itemize} 
		\item Could this point to a breakdown of our assumption that vertical 
		mixing is efficient? 
	\end{itemize}

	\item We note that our models do a good job of producing a mode [X/H] 
	abundance in each radial bin close to our target gradient (shown as 
	points plotted at the top of the bottom panels in Fig. 
	\ref{fig:mdf_3panel_fe} and~\ref{fig:mdf_3panel_o} for the inner radius of 
	each 2 kpc bin). In the inner galaxy bins, the predicted mode is 
	moderately lower than the target, but this is due to the effect of 
	dilution (see discussion in~\S~\ref{sec:amr}). In our inside-out and 
	outer-burst models, the difference in target and predicted mode [X/H] is 
	considerably smaller. 
\end{itemize}

\subsection{[O/Fe]} 
\label{sec:mdfs:ofe}

\begin{itemize} 
	\item In this section we compare our model predicted [O/Fe] distributions 
	to those published in Vincenzo et al. (2021, in prep). These are intended 
	to simultaneously remove the effects of observational errors in [O/Fe] 
	and the APOGEE selection function in these Galactic regions; that is, 
	these are estimates of the~\textit{intrinsice} [O/Fe] distributions that, 
	when convolved with observational uncertainties and the APOGEE selection 
	function, would resemble the observed MDFs.

	\item Fig.~\ref{fig:ofe_mdfs_insideout} show distributions in [O/Fe] in 
	two bins of [Fe/H] across 15 Galactic regions predicted by our inside-out 
	SFH (solid lines). Dashed lines show the Vincenzo et al. (2021, in prep) 
	distributions.

	\item At fixed~$R_\text{gal}$ and [Fe/H], the Vincenzo et al. (2021, 
	in prep) MDFs show two peaks in the distribution which do not change with 
	$\left|z\right|$; only their relative heights vary. This is an assumption 
	built into the model, but the agreement with the APOGEE data is good. 
	At small~$R_\text{gal}$, the observed distributions may shift slightly to 
	higher [Mg/Fe], but only at the~$\lesssim$0.05 level between 
	$\left|z\right|\leq$~0.5 and 1~$\leq\left|z\right|\leq$~2.0 (see their Fig. 
	X). In contrast, our model predicted distributions show an increase in the 
	mode [O/Fe] of~$\sim$~0.1 over the same dynamic range in~$\left|z\right|$. 
	This suggests that our model overpredicts the increase of [O/Fe] with 
	increasing~$\left|z\right|$ compared to the APOGEE distributions. 
	{\color{red} As of now, I don't have a good explanation for why this is 
	the case. Maybe the fact that we see this at small~$R_\text{gal}$ suggests 
	the evolution of the bulge may have something to do with it? We're not 
	modeling that here.}

	\item We note that the inside-out model fails to reproduce a Milky 
	Way-like bimodality. Such a model prediction would appear as good 
	agreement between the solid and dashed lines in Fig. 
	\ref{fig:ofe_mdfs_insideout}, but that is not the case. There may be 
	decent agreement in a given metallicity bin and Galactic region, but the 
	agreement would need to be seen everywhere and at all metallicities.

	\item In the inner galaxy, we overestimate the [O/Fe] of the highest 
	[Fe/H] stars at all $\left|z\right|$, and the differences in the 
	distributions gets smaller with increasing~$R_\text{gal}$. The lower 
	[Fe/H] bins don't seem to have this problem. 
	\begin{itemize} 
		\item Since these are in specific bins in [Fe/H], this is an 
		indication that our model is overpredicting the O abundances of these 
		stars, rather than underpredicting [Fe/H].

		\item This could point to various things. Perhaps the Milky Way has 
		different gradients in [O/H] than [Fe/H], an effect which is not 
		captured by these models. Perhaps the innermost radii of the Milky 
		Way has some contamination from bulge stars, another effect which is 
		not captured by our models. Impact of bar evolution maybe? 
	\end{itemize}

	\item Similar results are found for our other SFHs.

	\item While the notion that an [$\alpha$/Fe] dichotomy can arise out of 
	radial migration alone was put forth in~\citet{Schoenrich2009}, and later 
	explored by~\citet{Nidever2014}, this suggests that an inside-out star 
	formation history combined with stellar migration is not conducive to 
	predicting this observed result. The principle failure of this model is 
	that it overpredicts the abundance of intermediate [$\alpha$/Fe] stars. 
	This could point to a handful of things. 
	\begin{itemize} 
		\item If the bimodality is to arise out of inside-out galaxy 
		evolution and radial migration alone, the transition between low- and 
		high-$\alpha$ sequences needs to occur faster than it does in these 
		models. Applying the analytic model of~\citet{Weinberg2017}, this can 
		be occur only with an adequately short~$\tau_\star$. Here we have 
		adopted a star formation law which is motivated by observations (see 
		discussion in~\S~\ref{sec:methods:sfe}); this suggests that the 
		observed rates of star formation are not conducive to an adequately 
		short transition between the two sequences such as to predict the 
		dichotomy in the models as it is observed in the Milky Way.

		\item Under our current assumptions, the simplest way to achieve this 
		is to simply shut off star formation during the intermediate 
		[$\alpha$/Fe] phase in the simulations. This is indicative that 
		two-infall evolutionary histories~\citep[e.g.][]{Chiappini1997, 
		Chiappini2001, Romano2010, Grisoni2017, Noguchi2018, Spitoni2016, 
		Spitoni2018, Spitoni2019, Spitoni2020} would improve the 
		agreement between our model predictions and the observed 
		distributions.

		\item Alternatively, there is observational evidence for a SN Ia Fe 
		yield which scales inversely with metallicity (see discussion of 
		\citealp{Brown2019} in~\S~\ref{sec:methods:yields}). If this is the 
		case, the decrease in [O/Fe] ratios at low [Fe/H] at the onset of 
		the first SN Ia events may occur faster than in our models. This may 
		predict the observed bimodality by ensuring that the transition 
		between high- and low-$\alpha$ sequences is naturally fast due to 
		supernova rates. 
	\end{itemize}

	\item This is at 
	odds with the findings of~\citet{Sharma2020}, who claim to reproduce the 
	[$\alpha$/Fe] dichotomy with an analytic chemical evolution model with 
	an inside-out SFH and stellar migration. 
	\begin{itemize} 
		\item {\color{red} We'll need to be careful in our final draft of the 
		paper so that our language here isn't too strong. Below I've given my 
		honest critiques of the~\citet{Sharma2020} paper. }

		\item They assume parameterized forms for [Fe/H] and [$\alpha$/Fe] as 
		functions of radius and time, chosen deliberately so 
		that they agree with the observed data. Based on dynamical arguments 
		similar to those in~\citet{Schoenrich2009}, their migration model has 
		free parameters which then require fitting to observed data. Since the 
		observed data is known to exhibit the dichotomy, their model's 
		reproduction of the observed dichotomy is not a prediction but rather 
		an assumption characterized a priori. For this reason, rather than 
		learning about the physical origins of the [$\alpha$/Fe] dichotomy 
		from~\citet{Sharma2020}, we instead get a robust mathematical 
		characterization of the data.

		\item They find a dichotomy in the [$\alpha$/Fe]-[Fe/H] plane to 
		arise out of a fast transition in the gas phase between high-$\alpha$ 
		and low-$\alpha$. As we discussed here, we find in practice that this 
		is only the case if~$\tau_\star$ is sufficiently short, and our 
		observationally motivated scaling would suggest that the required 
		values are unphysically short ($\lesssim$1 Gyr; we find that our 
		$\tau_{\star,0}$ = 1 Gyr model also fails to reproduce an adequaately 
		fast transition).

		\item We therefore argue that the claim of~\citet{Sharma2020} that 
		the observed dichotomy can arise purely out of inside-out galaxy 
		formation with radial migration is likely contingent upon SN Ia rates 
		scaling inversely with metallicity, as suggested by the findings of 
		\citet{Brown2019}. Under the parameters of our inside-out SFH model, 
		this is the only physically realistic means with which the predicted 
		transition between high- and low-$\alpha$ is adequately fast. 
	\end{itemize}

	\item These findings suggest that an inside-out SFH combined with radial 
	migration, even when a late starburst is taken into account (as motivated 
	by the findings of~\citealp{Isern2019} and~\citealp{Mor2019}), 
	is~\textit{not} conducive to producing the observed [$\alpha$/Fe] 
	dichotomy. This suggests that more dramatic evolutionary events are 
	likely responsible, such as a two-infall model 
	\citep[e.g.][]{Chiappini1997, Chiappini2001, Romano2010, Grisoni2017, 
	Noguchi2018, Spitoni2016, Spitoni2018, Spitoni2019, Spitoni2020}. 
\end{itemize}

\section{The Age-[$\alpha$/Fe] Relation} 
\label{sec:age_alpha}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.34]{age_ofe_migration_comparison.pdf} 
\includegraphics[scale = 0.34]{age_ofe_sfh_comparison.pdf} 
\caption{
\textbf{Left}: A comparison of the predicted age-[O/Fe] relation for the 
solar annulus ($R_\text{gal}$ = 7 - 9 kpc and $\left|z\right|\leq$ 0.5 kpc) 
between the post-processing (upper left), diffusion (upper right), sudden 
(lower left), and linear (lower right) migration models, assuming our 
inside-out SFH. 
\textbf{Right}: The same as the left-hand panels, instead comparing the impact 
of our constant (upper left), inside-out (upper right), late-burst (lower 
left), and outer-burst (lower-right) SFHs. 
In all panels, red triangles and error bars denote the observed mean age and 
dispersion thereof in bins of [O/Fe] as reported by~\citet{Feuillet2019}; here 
we include only the bins containing at least 15 stars. Black squares denote 
the mass-weighted median age in 0.02-dex bins in [O/Fe] predicted by the 
simulations, with error bras denoting the 16th and 84th percentiles of the 
mass-weighted age distribution in those bins. Points in the background denote 
each individual stellar population from the simulation with a final position 
in the solar annulus, color-coded according to their Galactocentric radius of 
birth. 
} 
\label{fig:age_alpha} 
\end{figure*}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.32]{age_alpha_regions.pdf} 
\caption{The age-[O/Fe] relation in 12 galactic regions predicted by 
our inside-out SFH. Bins in Galactocentric radius are shown in columns, 
and labeled at the top. Bins in the height $\left|z\right|$ above/below the 
disc midplane are shown in rows, noted in the left-hand column. Red triangles, 
black squares, error bars, and background points are as in 
Fig.~\ref{fig:age_alpha} for the corresponding Galactic 
region. 
} 
\label{fig:age_alpha_regions} 
\end{figure*}

\begin{itemize} 
	\item In this section, we compare our model predictions to the 
	observational results of~\citet{Feuillet2019}. While we made use of 
	APOGEE DR16 data in comparing our model predictions to the observed 
	MDFs~\citep{Ahumada2020, Majewski2017}, they make use of DR14 stars which 
	have Gaia parallax measurements available~\citep[][for details on the 
	APOGEE survey, see discussion in~\S~\ref{sec:mdfs}]{Abolfathi2014, 
	GaiaDR2}. With their spatial and quality cuts, the final sample consisted 
	of 77,562 stars.

	\item \citet{Feuillet2019} ages are measured via isochrone matching. 
	{\color{red} Potentially give a little more detail, but that may be 
	adequate for our purposes.}

	\item In bins of [O/Fe], they assume a gaussian age distribution, and fit 
	the mean and standard deviation to the observed sample. Because they 
	assume a gaussian, they would report an equal mean and median. This is an 
	important caveat in comparing our predicted relations to their results, 
	because our model-predicted age distributions in bins of abundace are 
	highly non-gaussian.

	\item The stellar populations from our simulations have different masses, 
	so the age-distributions must be weighted by mass, since that scales with 
	the number of stars that each stellar population represents. We therefore 
	adopt a mass-weighted median age in bins of abundance as the appropriate 
	comparison to the~\citet{Feuillet2019} data. Physically, in a given bin 
	[O/Fe], this is the age corresponding to the 50th percentile of the 
	mass-weighted age distribution of our simulated stellar populations. For 
	these reasons the comparison between our simulations and 
	\citet{Feuillet2019} isn't exactly one-to-one. {\color{red} Potentially 
	worth mentioning some of the systematics in calculating ages here as 
	well, as that's relevant information.} 
\end{itemize}

\subsection{The Impact of Radial Migration} 
\label{sec:age_alpha:migration} 
\begin{itemize} 
	\item Fig.~\ref{fig:age_alpha} shows a comparison 
	between the predicted age-[$\alpha$/Fe] relations in the solar annulus for 
	our four migration models assuming our inside-out SFH.

	\item All models show reasonable agreement with the~\citet{Feuillet2019} 
	data; the population-averaged trend appears insensitive to the assumed 
	migration model.

	\item Diffusion predicts the most intrinsic scatter, followed by linear, 
	then sudden, then post-processing. This is a consequence of the variations 
	in the SN Ia rates induced by time-dependent migration (see discussion in 
	\S~\ref{sec:metallicity_space}). Further demonstration that under 
	certain migration models, the radial migration of nucleosynthetic yields 
	is statistically significant. This is also proof of concept that the 
	effect is significant for abundance ratios of elements where at least one 
	is produced by delayed nucleosynthetic sources. We therefore conclude that 
	the time-dependence of radial migration is a necessary ingredient to 
	chemical evolution models of galaxies where migration plays an important 
	role, such as our own Milky Way. The level of scatter also appears to 
	depend noticeably on which model for the time-dependence is adopted.

	\item This mechanism can produce populations of Fe-poor or Fe-rich stars, 
	which can be misinterpreted as $\alpha$-enhanced or $\alpha$-deficient 
	stars. Due to young stars migrating into or out of a given annulus, the SN 
	Ia rate may be higher or lower than the expectation from a post-processing 
	migration model. If this difference in the SN Ia rate is sustained for of 
	order one depletion time, the ISM will be either Fe-poor or Fe-rich, and 
	the stars that form there will inherit that composition.\footnote{
		{\color{red} Potentially note the~\citet{Weinberg2017} definition: 
		$\tau_\text{dep} \equiv \tau_\star/(1 + \eta - r)$. Even with 
		$\tau_\star$ as high as~$\sim$5 Gyr at large Galactocentric radii, 
		depletion times are still short due to the high values of $\eta$ 
		there.}
	} The stars that form out of that patch of ISM can then migrate to the 
	solar annulus. This effect is most significant at large Galactocentric 
	radii where the fractional amplitude of the variability in the SN Ia rate 
	is largest, and for that reason the young Fe-poor population predicted by 
	our diffusion model originates at large radii ($\gtrsim$ 12 kpc).

	\item \citet{SilvaAguirre2018} demonstrated that the observed young 
	$\alpha$-rich stars in the solar annulus have kinematics similar to the 
	rest of the high-$\alpha$ population, and suggested that this may be the 
	result of stellar mergers or mass transfer events, producing a population 
	of truly old stars masquerading as young stars. This would imply that the 
	observed young $\alpha$-rich population is actually just older, 
	high-$\alpha$ stars that have gone through some special class of stellar 
	evolution. Our model predicts intrinsically young, Fe-poor stars to 
	explain the observations, but these interpretations are not mutually 
	exclusive. It's possible that some of the observed stars are truly young, 
	Fe-poor stars, and that others underwent some stellar interaction event. 
	Ascertaining the origins of this population therefore has implications for 
	which of the migration models investigated here is the most realistic. 
\end{itemize}

\subsection{The Impact of the Star Formation SFH} 
\label{sec:age_alpha:sfh} 
\begin{itemize} 
	\item Fig.~\ref{fig:age_alpha} shows a comparison between 
	the predicted age-[$\alpha$/Fe] relations in the solar annulus for our 
	four SFHs assuming diffusion migration.

	\item Constant and inside-out SFHs describe the observed data the best. 
	Both late starburst models show a population-averaged increase in 
	[$\alpha$/Fe] at young ages which is not observed in the data. This 
	challenges the results of~\citet{Isern2019} and~\citet{Mor2019}, 
	suggesting that these results on the Milky Way recent SFH are not 
	consistent with chemical evolution models. If the Milky Way truly 
	experienced a recent starburst, something not included in our models had 
	to occur to prevent this global increase in [$\alpha$/Fe].

	\item Below [O/Fe]~$\approx$ +0.1, the~\citet{Feuillet2019} data seem to 
	follow a slightly steeper age-[$\alpha$/Fe] than our inside-out model 
	predicts. This likely points to inaccuracies in the detailed form of the 
	SFH or the SN Ia DTD, both of which are very plausible. 
\end{itemize}

\subsection{Beyond the Solar Annulus} 
\label{sec:age_alpha:beyond_solar_annulus} 
\begin{itemize} 
	\item Fig.~\ref{fig:age_alpha_regions} presents a comparison of our 
	simulation data to the~\citet{Feuillet2019} observational data in 12 
	Galactic regions assuming the inside-out SFH.

	\item In the disc, the inside-out SFH is a reasonable description of the 
	data for ages~$\lesssim$ 5 Gyr, above which the median ages are 
	overpredicted relative to~\citet{Feuillet2019}. Far from the midplane, our 
	model overpredicts the ages at nearly all abundances 
	where~\citet{Feuillet2019} have data, with the exception of the 
	$R_\text{gal}$ = 7 - 9 kpc and $\left|z\right|$ = 0.5 - 1 kpc region.

	\item Differences in ages are interesting though - nearly everywhere we 
	overpredict ages relative to~\citet{Feuillet2019}, their data are 
	reasonably described by the stellar populations from our simulations that 
	we would classify as Fe-poor (see discussion in~\S 
	\ref{sec:age_alpha:migration}). Especially noticeable in the
	$R_\text{gal}$ = 5 - 7 kpc, where the observed sample agrees nearly 
	perfectly with one particular Fe-poor population in the 
	$\left|z\right|\leq$~0.5 kpc and 0.5~$\leq\left|z\right|\leq$~1.0 kpc 
	regions. In the~$\left|z\right|\leq$ 0.5 kpc population, the observed 
	data even show an abrupt increase in age near the maximum [O/Fe] ratio of 
	this particular subset of our stellar populations, and have one data point 
	that agrees with the population-averaged trend in our simulation. 
	\begin{itemize} 
		\item Taking the~\citet{Feuillet2019} data at face value, this would 
		suggest that our simulation is overpredicting the rate of Fe injection 
		from SN Ia, implying a SN Ia DTD whose characteristic timescales are 
		longer than we employ here, thus slowing the decrease of [$\alpha$/Fe] 
		with time.

		\item Taking the simulation results at face value, this would suggest 
		that APOGEE+Gaia target selection favors the stars we would classify 
		as Fe-poor.

		\item This is another instance where a two-infall model would help 
		improve the fit, however~\citep[e.g.][]{Chiappini1997, Chiappini2001, 
		Romano2010, Grisoni2017, Noguchi2018, Spitoni2016, Spitoni2018, 
		Spitoni2019, Spitoni2020}. Through a perturbation of 
		the ratio of CCSN to SN Ia rates~\citep[e.g.][]{Johnson2020}, the 
		model would predict an increase in [$\alpha$/Fe] at ages of 
		$\sim$8 - 10 Gyr following the formation of the high-$\alpha$ 
		sequence, decreasing toward younger ages. Although this would worsen 
		the agreement in the solar annulus, it would improve it in other 
		Galactic regions. 
	\end{itemize}

	\item We note that the intrinsic scatter in the age-[$\alpha$/Fe] relation 
	predicted by the model grows with increasing~$R_\text{gal}$. Not only is 
	the scatter in the colored background points visibly larger, but the error 
	bars on the black points are as well, indicating that the age distribution 
	is getting statistically significantly wider at fixed [$\alpha$/Fe] with 
	increasing~$R_\text{gal}$. 
	\begin{itemize} 
		\item This is due to the variability in the SN Ia rates in each of 
		our model's annuli that we described in~\S~\ref{sec:metallicity_space}. 
		There, we demonstrated that the highest amplitude variability in the 
		SN Ia rate in our model galaxy is in the outskirts of the disc. This 
		arises out of time-dependent migration inducing a variability; this 
		variability gets larger in our models in regions where the stellar 
		number density is low.

		\item With a higher variability in the SN Ia rate comes a higher 
		variability in the rate of Fe production. Therefore, stars at large 
		$R_\text{gal}$ form out of an ISM with an [O/Fe] ratio that is more 
		variable, the observational signature of which is the intrinsic 
		scatter in the age-[$\alpha$/Fe] relation growing with~$R_\text{gal}$. 
	\end{itemize} 
\end{itemize}

\section{The Age-Metallicity Relation} 
\label{sec:amr}

\begin{figure} 
\centering 
\includegraphics[scale = 0.35]{amr_static_o.pdf} 
\caption{The age-[O/H] relation predicted by our constant SFR model for 
$R_\text{gal}$ = 7 - 9 kpc (left) and 11 - 13 kpc (right). Each panel plots 
only the~$\left|z\right|\leq$0.5 kpc population. The colored points in the 
background and the black squares with error bars are as in Fig. 
\ref{fig:age_alpha}, but with our binned, simulation prediction quantified in 
0.05-dex bins in [O/H]. } 
\label{fig:age_oh_static} 
\end{figure}

\begin{figure} 
\centering 
\includegraphics[scale = 0.45]{amr_solar_annulus.pdf} 
\caption{The age-[O/H] (top) and age-[Fe/H] (bottom) relations for the 
solar annulus (i.e.~$R_\text{gal}$ = 7 - 9 kpc,~$\left|z\right|\leq$ 0.5 kpc) 
as predicted by our inside-out SFH. Red triangles, black squares, error bars, 
and background points are as in Fig.~\ref{fig:age_alpha}, 
but with our simulation prediction quantified in 0.05-dex bins in [O/H] and 
[Fe/H]. For comparison, we plot the~\citet{Feuillet2018} data in a solid black 
line, omitting the associated uncertainties for the sake of clarity. } 
\label{fig:amr_solar_annulus} 
\end{figure}

\begin{figure*} 
\centering 
\includegraphics[scale = 0.35]{amr_insideout_vs_lateburst_fe.pdf} 
\caption{The age-[Fe/H] relation predicted by our inside-out (top) and 
late-burst (bottom) SFHs for~$R_\text{gal}$ = 5 - 7 kpc (left), 7 - 9 kpc 
(left middle), 9 - 11 kpc (right middle), and 11 - 13 kpc (right). Each panel 
plots only the~$\left|z\right|\leq$ 0.5 kpc population. Red triangles, black 
squares, error bars, and background points are as in 
Fig.~\ref{fig:age_alpha} for the corresponding 
Galactic region, but with our simulation prediction quantified in 
0.05-dex bins in [Fe/H]. } 
\label{fig:amr_insideout_vs_lateburst_fe} 
\end{figure*}

% \begin{figure*} 
% \centering 
% \includegraphics[scale = 0.32]{amr_lateburst_Fe.pdf} 
% \caption{The age-[Fe/H] relation in 12 Galactic regions predicted by our 
% late-burst SFH. Bins in Galactocentric radius are shown in columns, and 
% labeled at the top. Bins in height~$\left|z\right|$ above/below the disc 
% midplane are shown in rows, noted in the left-hand column. Red triangles, 
% black squares, error bars, and background points are as in 
% Fig.~\ref{fig:age_alpha} for the corresponding Galactic 
% region, but with our simulated prediction quantified in 0.05-dex bins in 
% [Fe/H]. } 
% \label{fig:age_feh_regions} 
% \end{figure*}

\begin{itemize} 
	\item Fig.~\ref{fig:age_oh_static} presents the age-[O/H] relation 
	predicted by our constant-SFH model for the~$\left|z\right|\leq$ 0.5 kpc 
	population at~$R_\text{gal}$ = 5 - 7, 7 - 9, 9 - 11, and 11 - 13 kpc. The 
	black points quantify the same mass-weighted median age in bins of 
	[O/H] as in~\S~\ref{sec:age_alpha}. Colored points in the background are 
	also the same - individual stellar populations color-coded according to 
	birth radius.

	\item \citet{Feuillet2019} argued using the~\citet{Weinberg2017} analytic 
	models of chemical evolution that the non-monotonicity of the observed 
	AMR was due to radial migration. The youngest stars at a given radius 
	should reflect recent abundances of the local ISM, since young stars could 
	not have migrated significant distances. Old stars, however, could have 
	migrated from a wide range of radii, and can therefore reflect a wide 
	range of abundances.

	\item Fig.~\ref{fig:age_oh_static} extends our understanding of this 
	effect. In all regions plotted, the intrinsic scatter in the bulk 
	age-[O/H] relation increases noticeably with increasing age, and the 
	color-coding of the background points makes it clear that this arises out 
	of radial migration.

	\item Furthermore, the characteristic metallicity of the youngest stars 
	in a given radial bin decreases with increasing radius. This is a natural 
	consequence of the abundance gradient that we've built in at late times, 
	but interestingly, the effect is strong enough that at large radii, the 
	median trend is nearly monotonically increasing with age. This is 
	completely backwards from what is expected from one-zone models of 
	chemical evolution for any radius. Since this is our constant-SFR model, 
	it is not subject to the effects of a time-varying SFH, quantifying only 
	what is caused by radial migration.

	\item Similar things are found for Fe, but the variations in the black 
	squares a bit bigger so we demonstrate the effect with [O/H].

	\item Fig.~\ref{fig:amr_solar_annulus} shows the age-[O/H] (top panel) 
	and the age-[Fe/H] (bottom panel) relations predicted by our fiducial 
	inside-out SFH in the solar annulus ($R_\text{gal}$ = 7 - 9 kpc and 
	$\left|z\right|\leq$~0.5 kpc), under the same plotting convention as in 
	\S~\ref{sec:age_alpha}. We add a solid black line to denote the 
	\citet{Feuillet2018} AMR in comparison to that of~\citet{Feuillet2019}. 
	\begin{itemize} 
		\item We note that we find similar results with regard to the 
		age-[O/H] relation predicted by our models.

		\item \citet{Feuillet2018} shows a significantly younger median age at 
		solar metallicity in both O and Fe ($\sim$1 - 2 Gyr as opposed to 
		$\sim$2 - 3 Gyr).

		\item Fiducial, inside-out SFH performs decently at explaining the 
		\citet{Feuillet2019} AMR, but the ages at solar metallicity in the 
		\citet{Feuillet2018} study are too young for this model. Comparing the 
		black points in this figure to those in Fig.~\ref{fig:age_oh_static} 
		suggests that the constant SFR model can't explain ages that young 
		either. If we were to take the~\citet{Feuillet2018} results at face 
		value in comparison to these models, this would strongly suggest a 
		recent enhancement at least in the local star formation rate of the 
		solar annulus to increase the frequency of~$\sim$1 Gyr old, solar 
		metallicity stars close to the sun.

		\item Such a burst is indeed supported by the findings of 
		\citet{Mor2019}, who find a factor of~$\sim$2 enhancement in the SFH 
		of the Milky Way~$\sim$2 Gyr ago by comparing population synthesis 
		models to observed stellar luminosity functions and color-magnitude 
		diagrams with Gaia data~\citep{GaiaDR2}.~\citet{Isern2019} reach 
		similar conclusions modeling white dwarf luminosity functions in the 
		solar neighborhood with Gaia parallaxes. 
	\end{itemize}

	\item Fig.~\ref{fig:amr_insideout_vs_lateburst_fe} shows a comparison of 
	the predicted age-[Fe/H] relation for~$\left|z\right|\leq$~0.5 kpc stars 
	in the~$R_\text{gal}$ = 5 - 7, 7 - 9, 9 - 11, and 11 - 13 kpc annuli. 
	Points are plotted in the same manner as in Fig.~\ref{fig:age_oh_static} 
	and Fig.~\ref{fig:amr_solar_annulus} in this section. 
	\begin{itemize} 
		\item Beyond the solar annuulus, we note that our inside-out SFH 
		model in general overpredicts the characteristic ages of stars 
		compared to~\citet{Feuillet2019} except for [Fe/H]~$\approx$~+0.4 and 
		-0.5. We also remark that in the trend is not very well reproduced 
		either, particularly in the~$R_\text{gal}$ = 5 - 7 kpc bin.

		\item In the bottom row of panels, we show the same relation for our 
		late-burst SFH. Interestingly, the late-burst model improves upon the 
		failures of the inside-out model significantly. In particular, the 
		over-prediction of ages of solar and intermediate metallicity stars is 
		fixed by the late-burst model. 
		\begin{itemize} 
			\item In our recent starburst models,~\texttt{VICE} calculates 
			that there is a significant amount of zero metallicity gas infall 
			required to sustain such an increase in star formation under our 
			adopted~$\dot{\Sigma}_\star-\Sigma_\text{gas}$ relation (see 
			bottom two panels of Fig.~\ref{fig:evol} and~\S~
			\ref{sec:methods:sfe}).

			\item Denoting the ages and compositions of the individual stellar 
			populations from our simulations, the colored points in the 
			background of these panels trace the metallicity of the gas as a 
			function of time at various radii. That is, the blue points also 
			represent the [Fe/H] of the gas phase at small radii at various 
			lookback times, and the same for the green points and large radii.

			\item This demonstrates that at a lookback time of~$\sim$2 Gyr, by 
			construction, the ISM at nearly all Galactocentric radii decreased 
			in metallicity. At the same time, the star formation rates 
			increased by a factor of~$\sim$2, again by construction (see the 
			right-hand panels of Fig.~\ref{fig:evol}). The result is that at 
			any radius, the frequency of~$-0.5~\lesssim$~[O/H]~$\lesssim~0$ 
			stars at ages of~$\sim$2 Gyr is increases by a factor of~$\sim$2 
			from the inside-out model, decreasing the characteristic ages of 
			stars at these metallicities.

			\item Although there appears to be an offset between the 
			\citet{Feuillet2019} data and our predicted AMR at high 
			$R_\text{gal}$, the late-burst model describes the observed trend 
			noticeably better than the inside-out model. Although the ages of 
			modestly sub-solar metallicity stars in the solar annulus are 
			slightly under-predicted by the model, the same can be said about 
			the trend here and at 5 - 7 kpc as well.

			\item The parameters which control this offset are the yields of 
			Fe and the mass-loading factor as a function of~$R_\text{gal}$. 
			If we were to take a slightly higher yield of Fe, it would however 
			increase the overall normalization at~$R_\text{gal}$~< 9 kpc as 
			well, where we do not see this discrepancy. It's possible that the 
			mass-loading factor~$\eta$ (see discussion in~\S 
			\ref{sec:methods:yields}) increases too quickly at large 
			$R_\text{gal}$ in our models, or that outflows are more efficient 
			at removing individual elements from the star forming reservoir. 
			Variable metal-loading factors~$\eta_Z$ would be supported by the 
			observations of~\citet*{Chisholm2018}.

			\item We remark that the late-burst model predicts extremely young 
			characteristic ages for the highest [Fe/H] bins in the 5 - 7 kpc 
			annulus. This is merely a consequence of the re-enrichment that 
			accompanies the ensuing starburst; in infall-driven starbursts 
			such as this, the abundances often reach super-equilibrium values 
			while the star formation rate is still perturbed, which then decay 
			together back to their pre-burst, equilibrium values 
			\citep{Johnson2020}. On 
			Fig.~\ref{fig:amr_insideout_vs_lateburst_fe}, this is noticeable 
			by the abundances on the left-hand edge of each panel being 
			higher in the late-burst scenario. The points that we have 
			plotted as characteristic ages represent that 50th percentile of 
			the mass-weighted age distribution of our stellar populations in 
			a bin of abundance; in other words, a mass-weighted 
			\textit{median}. The age-distribution at these abundances is 
			bimodal, noticeable by the colored points in the background, 
			indicating that the median may not be the best statistic for these 
			few stellar populations. We note that the outer-burst model, in 
			which $R_\text{gal}$~< 6kpc do not experience the starburst, does 
			not suffer from this issue. The minutia of the AMR at different 
			radii in our late starburst models is sensitive to the detailed 
			time-dependence of the straburst in each annulus. 
		\end{itemize} 
	\end{itemize}

	\item Conclude that the AMR reported by~\citet{Feuillet2019} is better 
	described by our late starburst models than the inside-out model. This is 
	at odds with our findings in the same simulations with the same 
	observational dataset with regard to the age-[$\alpha$/Fe] relation. 
	Perhaps the differences can be reconciled. 
	\begin{itemize} 
		\item The models would be able to have their cake and eat it too if 
		there is a recent starburst with no ensuing $\alpha$-enhancement. This 
		is difficult to rationalize, however, because an increase in 
		[$\alpha$/Fe] in the wake of a starburst is a direct consequence of 
		the perturbed ratio of CCSN-SN Ia rates caused by the burst 
		\citep{Johnson2020}. We argue based on this that it is unlikely that 
		the detailed timing of a recent starburst would mitigate this issue.

		\item It's possible that the Milky Way experienced dilution with no 
		ensuing starburst. This could be the case if the accreted gas was 
		mostly in the form of HI or HII that has not yet cooled and been 
		available for star formation, but has been mixing with the 
		nucleosynthetic products of ongoing star formation in the Galaxy. With 
		dilution playing a noticeable role in the AMR predicted by our burst 
		models, it's possible a model of this nature could agree with both 
		the AMR and the age-[$\alpha$/Fe] relation. This would require 
		future studies which include a treatment of a multi-phase ISM. 
	\end{itemize}

	\item As a general result here, we caution future studies against 
	leveraging the agreement between a chemical evolution model and 
	observational data based on the solar annulus alone. Fig. 
	\ref{fig:amr_solar_annulus} presents the comparison of our fiducial, 
	inside-out SFH model predictions in the solar annulus to the 
	\citet{Feuillet2019} data, and Fig.~\ref{fig:amr_insideout_vs_lateburst_fe} 
	compares the inside-out and late-burst predictions in a larger range of 
	radii. Had we only considered the solar annulus, we would have concluded 
	that the fiducial, inside-out model agrees with the~\citet{Feuillet2019} 
	data well. However, in considering other regions of the Galaxy, we found 
	that the inside-out model actually had a handful of failures which were 
	mitigated by our late-burst model.

	\item With our age-[O/H] and age-[Fe/H] relations, we find similar results 
	as in~\S~\ref{sec:age_alpha:beyond_solar_annulus} whereby our model 
	in general overpredicts the observed ages of stars at high 
	$\left|z\right|$. Discussion of potential sources of this can be found 
	in~\S~\ref{sec:age_alpha:beyond_solar_annulus}. 
\end{itemize}

\section{Conclusions} 
\label{sec:conclusions} 
\begin{itemize} 
	\item We have modeled the Milky Way as a series of concentric annuli with 
	$\Delta R_\text{gal}$ = 100 pc width, describing each annulus as a 
	conventional one-zone model of chemical evolution, and allowing the 
	exchange of stellar populations between zones to model the impact of 
	stellar migration on enrichment in the Galaxy. The resulting ``multi-zone'' 
	is a technique that has received attention from only a handful of 
	chemical evolution studies to date~\citep{Matteucci1989, 
	Schoenrich2009, Minchev2013, Sharma2020}. In so doing, we adopted star 
	particles from the~\texttt{h277} zoom-in, hydrodynamical simulation to 
	describe the dynamical history of a Milky Way-like galaxy at face value. 
	This yields a model for radial migration which does not have any free 
	parameters (see discussion in~\S~\ref{sec:methods:h277}).

	\item We found that similar numbers of star particles in~\texttt{h277} 
	migrated inward as outward, and that the two proceed on different 
	timescales, indicating that they're potentially linked to different 
	physical processes. We found that distributions of birth radii in bins of 
	final radii showing a mode which depends strongly on age is a 
	consequence of the surface density gradient. It's not that stars in general 
	migrate outward, it's simply that there are many many stars born at small 
	radii presently at large radii due to the fact that there are so many more 
	stars born at small radii, a consequence of the steep nature of the 
	surface density gradient~\citep[e.g.][]{Bland-Hawthorn2016}.

	\item We found that the e-folding timescales for star formation indicated 
	by population averaged observations of Milky Way like galaxies are long 
	($\sim$15 Gyr in the solar annulus;~\citealp{Sanchez2020}).

	\item We find that through stellar migration our models naturally 
	reproduce the observed result that high-$\alpha$ stars are more common at 
	small~$R_\text{gal}$ and high-$\left|z\right|$, and the opposite for 
	low-$\alpha$ stars (\citealp{Hayden2015}; see Fig. 
	\ref{fig:ofe_feh_diagram} and associated discussion in~\S 
	\ref{sec:metallicity_space}).

	\item We demonstrate that the time-dependence of radial migration has a 
	significant impact on the [O/Fe] ratios as a function of time and radius 
	by inducing variability in the SN Ia rate and therefore the Fe abundance 
	(see Fig.~\ref{fig:tracks} and the associated discussion in~\S 
	\ref{sec:metallicity_space}). Although we haven't investigated it here, we 
	expect similar arguements to extend to other delayed sources such as AGB 
	stars and the associated s-process elements such as carbon, nitrogen, 
	strontium, yttrium, and zirconium. This is proof of concept that under 
	certain models for the time-dependence of radial migration, the migration 
	of nucleosynthetic yields proceeding alongside stellar migration is a 
	statistically significant effect. We therefore recommend future studies 
	relax the assumption that stars do not contribute to nucleosynthesis 
	beyond their birth radius.

	\item We find that our models naturally reproduce the variations in the 
	observed metallicity distribution functions (MDFs) with Galactocentric 
	radius in the disc midplane ($\left|z\right|\leq$~0.5 kpc). At low 
	$R_\text{gal}$, the mode abundance in both [O/H] and [Fe/H] is high, and 
	conversely low at high~$R_\text{gal}$, with skewness in qualitative 
	agreement with the observations (\citealp[e.g.][]{Hayden2015}; see Fig. 
	\ref{fig:mdf_3panel_fe} and Fig.~\ref{fig:mdf_3panel_o} and the associated 
	discussion in~\S~\ref{sec:mdfs:oh_feh}). In some sense, 
	however, this is more a consequence of our building a realistic abundance 
	gradient into our models than a prediction on its own. In the observations, 
	the mode abundance in the midplane at $R_\text{gal}$ = 3 - 5 kpc is 
	strikingly similar to that at 5 - 7 kpc. Our models fail to reproduce this, 
	though it may be tied to a cessation of star formation in the inner 
	galaxy, as suggestted by~\citet{Peek2009} and~\citet{Fraternali2012}. Off 
	the midplane, our models predict a slight shift of the MDFs at small 
	$R_\text{gal}$ to lower metallicity, where in the observations, those for 
	all radii converge at [Fe/H]~$\approx$~[O/H]~$\approx$~-0.5.

	\item We find that none of our models predict a Milky Way-like dichotomy 
	in [$\alpha$/Fe], as observed by many studies. The principle failure is 
	that the frequency of intermediate [$\alpha$/Fe] stars is overpredicted 
	relative to the observations (\citealp{Hayden2015}; Vincenzo et al. 2021, 
	in prep). This suggests that inside-out galaxy grouth combined with 
	radial migration, even if a recent starburst is included 
	\citep[e.g.][]{Mor2019, Isern2019}, is not adequate to explain the 
	observed dichotomy. This is at odds with the findings of 
	\citet{Sharma2020}, though we believe our study to have a more physically 
	motivated treatment of the chemical evolution models (see discussion in 
	\S~\ref{sec:mdfs:ofe}). The over-prediction of intermediate [$\alpha$/Fe] 
	stars in general suggests that shutting off star formation for the 
	intermediate-$\alpha$ phase would mitigate the problems suffered by our 
	models; we therefore postulate that a two-infall model may be necessary 
	to explain the observed dichotomy~\citep[e.g.][]{Chiappini1997, 
	Chiappini2001, Romano2010, Grisoni2017, Noguchi2018, Spitoni2016, 
	Spitoni2018, Spitoni2019, Spitoni2020}. Alternatively, we 
	speculate that the issues may be mitigated by an effective SN Ia yield of 
	Fe which depends inversely on metallicity, based on the findings of 
	\citet{Brown2019}.

	\item We found that our recipe for setting the gradients in both stellar 
	surface density and metallicity yields the correct result. This is an 
	indication that radial migration does not change the profile of these 
	observed trends, only inducing scatter. 
	\begin{itemize} 
		\item We found that slightly different predictions in the stellar 
		and gas-phase metallicity gradient are natural consequences of 
		variations in the SFH.

		\item We found that different models for the SFH predicted different 
		[O/Fe] gradients at the present day.

		\item See Fig.~\ref{fig:metallicity_gradient} and the associated 
		disccusion in~\S~\ref{sec:metallicity_gradient} for the metallicity 
		gradient; Fig.~\ref{fig:surface_density} and discussion in 
		\S~\ref{sec:methods:surface_density_gradient} for the surface 
		density gradient. 
	\end{itemize}

	\item We found that the observationally motivated approach to modeling the 
	efficiency of star formation ($\tau_\star \equiv \Sigma_\text{gas} / 
	\dot{\Sigma}_\star$) adopted in our simulations in general overpredicts 
	the molecular fractions by mass of the model Galaxy. The discrepancy arose 
	out of an underabundance of HI/HII rather than an overabundance of H$_2$ 
	in the global demographics predicted by our simulation. Nonetheless, we 
	demonstrate in Appendix~\ref{sec:sfe_variations} that relaxing these 
	assumptions do not impact our model predictions. We also discuss a handful 
	of potential sources of the discrepancy there.

	\item We found that the time-dependence of radial migration indeed does 
	have an impact on enrichment. Previous studies in the literature have 
	assumed that this is not the case, due to the slow nature of migration 
	\citep[e.g.][]{Minchev2013}. However, we find that even for young stars, 
	the tails of the present-day $R_\text{gal}$ distribution are adequately 
	long that when age-dependent migration is taken into account, the model 
	predicts variations in the SN Ia rate that then impact predicted abundance 
	ratios. We demonstrated that this is a means with which stellar migration 
	may produce young, Fe-poor stars which can migrate to the solar annulus, 
	and potentially be misinterpreted as young, $\alpha$-rich stars. This is 
	proof of concept that the radial migration of nucleosynthetic yields can 
	proceed alongside the radial migration of stars, depending on which model 
	for migration that you believe. 
	\begin{itemize} 
		\item These stars have been seen in observed data from APOGEE 
		\citep[e.g.][]{SilvaAguirre2018}. They postulate that since these stars 
		have kinematics similar to the rest of the high-$\alpha$ population, 
		that perhaps they are the consequence of stellar mergers or mass 
		transfer events, producing truly old stars that simply appear to be 
		younger. While these interpretations are not mutually exclusive, an 
		observational test to ascertain the origins of the observed young 
		$\alpha$-rich population would have implications for which of the 
		models for radial migration investigated here are the most realistic. 
	\end{itemize}

	\item In the observations, the high-$\alpha$ sequence is known to be most 
	prominent at low~$R_\text{gal}$ and high~$\left|z\right|$, and conversely, 
	the low-$\alpha$ population at high~$R_\text{gal}$ and low~$\left|z\right|$ 
	\citep[e.g.][]{Hayden2015}.  We found that this is a natural consequence of 
	stellar migration, though the detailed distributions depend on the SFH and 
	the relative yields of $\alpha$ and iron-peak elements, both of which are 
	highly uncertain, and we do not model them in detail here.

	\item We found that our inside-out model predicts an age-[$\alpha$/Fe] 
	relation which is in good agreement with the observed relation reported 
	by~\citet{Feuillet2019}. Our recent starburst models predict a global 
	$\alpha$-enhancement that simply isn't seen in the data. This suggests 
	that our current understanding of chemical evolution may be at odds with 
	the findings of~\citet{Mor2019} and~\citet{Isern2019} suggesting a recent 
	factor of~$\sim$2 enhancement in the Milky Way SFH peaking~$\sim$2 Gyr ago.

	\item We find that where our recent starburst models fail to agree with 
	the age-[O/Fe] relation reported by~\citet{Feuillet2019}, it tends to 
	overpredict ages at a given [O/Fe]. However, it tends to fail in a manner 
	such that the~\citet{Feuillet2019} relation agrees with the stars that we 
	would call Fe-poor - that is, the stars that are $\alpha$-enhanced due to 
	forming out of an Fe-poor ISM due to the same variations in the SN Ia rate 
	that can produce young, $\alpha$-rich stars. While this may be coincidence, 
	if we take the observations at face value, it would suggest that our model 
	is overpredicting the rate of Fe injection, and that perhaps SN Ia yields 
	of Fe should be lower. If we take the model at face value, it suggests that 
	APOGEE+Gaia targets preferentially sample young, $\alpha$-rich stars 
	(\citealp{Feuillet2019} used APOGEE data for stars with Gaia parallaxes).

	\item We found that the age-metallicity relation (AMR) in both [O/H] and 
	[Fe/H] reported by~\citet{Feuillet2019} is better fit by our late 
	starburst models. This is at odds with the findings regarding the 
	age-[O/Fe] relation, where the inside-out model agreed with the data much 
	better than the starburst models. This is interesting, because different 
	observables are favoring different models for the SFH, suggesting that 
	something more complicated is going on. 
	\begin{itemize} 
		\item The starburst models agreeing with the observed AMR has to do 
		with dilution as well as the starburst itself. It's possible that the 
		Milky Way experienced a dilution event that was primarily HI/HII gas 
		that has not yet cooled to be available for star formation. This could 
		mitigate the discrepancy. It would, however, be at odds with the 
		observed results of~\citet{Mor2019} and~\citet{Isern2019} suggesting 
		such a recent enhancement in star formation.

		\item Off the midplane, our model-predicted AMR overestimates ages 
		relative to~\citet{Feuillet2019}, just like in the age-[O/Fe] relation. 
		We speculate that this may be related to the Sagitarrius dwarf 
		galaxy; it's important to remember that our model galaxy does not have 
		the Milky Way's dynamical history, but~\texttt{h277}'s dynamical 
		history. {\color{red} Jon and I are looking into this, but as I 
		understand it, what I've written next is in general true.}~\texttt{h277} 
		did not have a Sagitarrius-like accretion event. Since Sagitarrius 
		has made multiple pericentric passages nearly head-on with the Milky 
		Way disc, it's possible that young stars were kinematically heated to 
		high~$\left|z\right|$, an effect that would not be present in 
		\texttt{h277} without such an event. This would decrease our model 
		predicted median ages at these heights by directly adding more young 
		stars, and potentially not having noticeable effect in the midplane due 
		to the much larger number of stars there. 
	\end{itemize}

	\item We remark on the low number of multi-zone 
	chemical evolution models in the literature. We call for more studies 
	which adopt a similar approach; with only a handful of simulations which 
	can be ran in a combined time interval of less than a single working day, 
	we were able to assess model predictions of various chemical evolution 
	scenarios in comparison to a wide range of observables. With a wealth of 
	one-zone chemical evolution models (both numerical and analytic) and 
	high-resolution hydrodynamical simulations already in the literature, 
	there is a true void in the literature for these medium resolution, medium 
	computational expense models which which can teach us a great deal about 
	the enrichment history of the Milky Way. For this reason,~\texttt{VICE} 
	is open source software, and its~\texttt{milkyway} object which ran our 
	simulations adopts many of this paper's physically and observationally 
	motivated assumptions as default values. Alternative zone configurations 
	can be achieved by subclassing the~\texttt{multizone} object and 
	specifying how gas and stars should move between the individual zones, as 
	we have already done for the~\texttt{milkyway} object.

	\item \texttt{VICE} is publicly available and open-source. It can be 
	installed via~\texttt{pip} (\url{https://pypi.org/project/vice}). 
	Documentation is available at~\url{https://vice-astro.readthedocs.io}. 
	Source code is hosted at~\url{https://github.com/giganano/VICE.git}. 
	\texttt{Python} code which runs the simulations presented in this paper 
	are included as supplementary material in the~\texttt{git} repository; 
	our models can be ran directly from a~\texttt{bash} terminal without 
	modifying the source code, and are capable of predicting abundances for 
	$\sim$2 million stellar populations in only~$\sim$2 CPU hours with a 
	single core on personal computers. 
\end{itemize}

\section{Acknowledgements} 
\label{sec:acknowledgements} 
We are grateful to Diane Feuillet for sharing the data 
from~\citet{Feuillet2018} and~\citet{Feuillet2019} with us. {\color{red} There 
will be others added, depending on whether or not they go here or on the 
author's list. I'll also need to add the SDSS acknowledgements since we made 
use of APOGEE data.} 
\par 
\textit{Software}: Matplotlib~\citep{Matplotlib}; Astropy~\citep{Astropy2013, 
Astropy2018}; NumPy~\citep{NumPy}.

\section{Data Availability} 
{\color{red} In case anyone hasn't seen one of these Data Availability 
statements yet, this is now a requirement by MNRAS. It wasn't when I submitted 
my last paper, but was by the time we were finished with the referee report, 
so I wound up having to add one. They just want you to say if the data are 
available to the reader or not, and where/how they can get it if they are. }
\texttt{VICE} is open source software, and as such the source code for these 
simulations is publicly available.\footnote{
	\url{https://pypi.org/project/vice} \\ 
	\url{https://vice-astro.readthedocs.io} \\ 
	\url{https://github.com/giganano/VICE.git} 
} The source code which produces the outputs presented in this paper as well as 
the figures are included as secondary material in the GitHub repository. 
While the aggregate of all outputs analyzed in this paper are sufficiently 
large that it is not conducive to store them on GitHub, we provide instructions 
on how to run our simulations and variations thereof. All observational data 
appearing in this paper is publicly available, and is also included with the 
source code for our simulations and figures.

\newpage 
\begin{appendices}

\section{Normalizing a Fiducial Star Formation History} 
\label{sec:normalize_sfh} 
\begin{itemize} 
	\item Derive formula for normalizing an SFH given the time-dependence at 
	a given radius $f(t|R_\text{gal})$ and the radial dependence of the 
	desired surface density gradient at late times $g(R_\text{gal})$. Neither 
	need be normalized. 
	\begin{equation} 
	\dot{\Sigma}_\star(R_\text{gal}, t) = \dot{\Sigma}_{\star,0}(R_\text{gal}) 
	f(t|R_\text{gal}) 
	\end{equation} 
	\begin{equation} 
	\Sigma_\star(r) = \Sigma_{\star,0} g(R_\text{gal}) 
	\end{equation}

	\item Integrate surface density of star formation with time and you get 
	the present day surface density gradient at that radius. This yields the 
	unknown $\dot{\Sigma}_{\star,0}$ in terms of $\Sigma_\star(R_\text{gal})$ 
	and subsequently the unknown $\Sigma_{\star,0}$. 
	\begin{subequations}\begin{align} 
	\Sigma_\star(R_\text{gal}) 
	&\approx (1 - r) \int_0^T \dot{\Sigma}_\star(R_\text{gal}, t) dt \\ 
	&= (1 - r) \dot{\Sigma}_{\star,0}(R_\text{gal}) \int_0^T f(t|R_\text{gal}) 
	dt \\ 
	\implies \dot{\Sigma}_{\star,0}(R_\text{gal}) &= 
	\Sigma_\star(R_\text{gal}) \left[(1 - r)\int_0^T f(t|R_\text{gal}) dt
	\right]^{-1} \\ 
	&= \Sigma_{\star,0}g(R_\text{gal}) \left[(1 - r) \int_0^T f(t|R_\text{gal}) 
	dt\right]^{-1} 
	\end{align}\end{subequations}

	\item Integrate surface density over area of the disc and you get the 
	present day Milky Way stellar mass. This solves for the unknown 
	$\Sigma_{\star,0}$: 
	\begin{subequations}\begin{align} 
	M_\star^\text{MW} &= \int_0^R \Sigma_\star(R_\text{gal}) 2\pi R_\text{gal} 
	dR_\text{gal} \\ 
	&= \Sigma_{\star,0}\int_0^R g(R_\text{gal}) 2\pi R_\text{gal} dR_\text{gal} 
	\\ 
	\implies \Sigma_{\star,0} &= M_\star^\text{MW} 
	\left[\int_0^R g(R_\text{gal}) 2\pi R_\text{gal}dR_\text{gal}\right]^{-1} 
	\end{align}\end{subequations}

	\item Combine the last two equations into 
	$\dot{\Sigma}_\star(R_\text{gal}, t)$ and obtain the following equation: 
	\begin{equation} 
	\dot{\Sigma}_\star(R_\text{gal}, t) = A f(t|R_\text{gal}) g(R_\text{gal}) 
	\end{equation} 
	where 
	\begin{equation} 
	A = M_\star^\text{MW}\left[(1 - r)\int_0^R g(R_\text{gal}) 2\pi 
		R_\text{gal} dR_\text{gal} \int_0^T f(t|R_\text{gal}) dt\right]^{-1} 
	\end{equation} 
	This result makes intuitive sense: $f(t|R_\text{gal})$ specifies the 
	time-dependence of the SFH and $g(R_\text{gal})$ specifies the radial 
	dependence by construction, and $M_\star^\text{MW}$ sets the overall 
	normalization.

	\item This recipe implicitly assumes that radial migration does not 
	significantly alter the surface density profile, and we have demonstrated 
	in~\S~\ref{sec:methods:surface_density_gradient} that this is the case for 
	the Galactocentric radii of interest in this paper. It introduces scatter, 
	but does not alter the overall dependence. This recipe can be employed in 
	disc galaxy models as long as this is not violated. 
\end{itemize}

\newpage 
\section{Variations in Star Formation Efficiency} 
\label{sec:sfe_variations} 
{\color{red} It'd be good to present a comparison of our fiducial, inside-out 
SFH model to a case where we make a significantly different assumption about 
$\tau_\star$, and demonstrate that it doesn't impact the conclusions. This 
could motivate some of the discussion below as well, so that this Appendix can 
still tell a generally interesting story beyond just a comparison. }

\begin{itemize} 
	\item {\color{red} Here are some of my thoughts on what could be 
	causing the discrepancy with this $\tau_\star$ business. Since 
	this is for discussion purposes, I haven't looked in detail at any 
	of this; I'm simply speculating for the sake of discussion in the 
	text. }

	\item As discussed in~\S~\ref{sec:methods:sfe}, our fiducial inside-out 
	SFH overpredicts the molecular fraction~$f_\text{mol}$ relative to 
	observed results in the Milky Way. This is a result of both an 
	underpredicted HI + HII mass and an overpredicted H$_2$ mass. The 
	predicted HI + HII mass is~$5.54\times10^9$~M$_\odot$ relative to an 
	observed value of~$\sim10^{10}$~M$_\odot$~\citep{Kalberla2009}. The 
	predicted H$_2$ mass is~$7.14\times10^9$~M$_\odot$, compared to an 
	observed values of~$2.5\times10^9$~M$_\odot$ from~\citet{Kalberla2009} and 
	$1\times10^9$~M$_\odot$ from~\citet{Heyer2015}. Here we discuss potential 
	sources of this discrepancy, and demonstrate that the assumed form of the 
	star formation law does not impact our conclusions.

	\item First, the overpredicted H$_2$ mass. Our fiducial inside-out model, 
	whose SFH is normalized to predict the same total stellar mass as that 
	reported by~\citet{Licquia2015} with the surface density gradient of 
	\citet{Bland-Hawthorn2016} (see discussion in~\S~\ref{sec:methods:sfhs} 
	and~\ref{sec:methods:surface_density_gradient}). This model predicts a 
	present-day SFR of 4.89 M$_\odot$~yr$^{-1}$, an overprediction relative to 
	the observed value of 1.65 M$_\odot$~yr$^{-1}$~\citep{Licquia2015}. 
	However, our model predicts a gradient in the present-day surface density 
	of star formation with radius which decreases monotonically (see the top 
	row, left-center panel of Fig.~\ref{fig:evol}), whereas the observations 
	of \citet{Peek2009} and~\citet{Fraternali2012} would suggest that the 
	Milky Way has begun the process of inside-out quenching. Fig. 2 of 
	\citet{Fraternali2012} suggests that the surface density of star 
	formation is significantly lower within~$R_\text{gal} \lesssim$ 4 kpc. 
	Cutting off our summation of the H$_2$ mass and present-day SFR at 
	4 kpc yields a present-day star formation rate of 3.06 M$_\odot$ 
	yr$^{-1}$, and an H$_2$ mass of~$4.48\times10^9$~M$_\odot$, still an 
	overprediction relative to~\citet{Licquia2015} and 
	\citet{Kalberla2009}. Instead cutting the summation off at 6 kpc 
	yields $\dot{M}_\star$ = 1.97 M$_\odot$~yr$^{-1}$ and H$_2$ = 
	$2.88\times10^9$~M$_\odot$, still a slight overprediction, but in 
	better agreement still. Based on these calculations, we argue that the 
	overpredicted H$_2$ mass in our fiducial inside-out model is a consequence 
	of an overpredicted SFR at the present day. A model with either a more 
	steeply declining SFH or quenching of star formation in the inner Galaxy 
	as suggested by~\citet{Peek2009} and~\citet{Fraternali2012} should resolve 
	this discrepancy.

	\item Next, the under-predicted HI + HII mass. We speculate over a couple 
	possible explanations of this. 
	\begin{itemize} 
		\item At first glance, this could point to a breakdown in the 
		fundamental assumption of our adopted model for star formation 
		efficiency. As discussed in~\S~\ref{sec:methods:sfe}, we adopte the 
		assumption that our model Galaxy follows the observed trend in the 
		mean~$\dot{\Sigma}_\star-\Sigma_\text{gas}$ relation, even though 
		there is evidence that individual galaxies do not follow such a 
		relation~\citep{Ellison2020b}.~\citet{Kennicutt2020} however argue 
		that such a prescription should still be a valid recipe in galaxy 
		evolution models.

		\item An important caveat in understanding our ISM masses is that 
		because we treat the ISM as being available for star formation in its 
		entirety, they therefore track only the amount of gas in the 
		\textit{star forming reservoir}. Zero metallicity gas infall simply 
		appears in each annulus to balance the amount of gas lost to star 
		formation and outflows at each timestep in order to sustain the 
		level of star formation at the next timestep. Based on our model, if 
		gas is removed from the star forming reservoir, but remains in a 
		spatially confined region reasonably defining the Galaxy, our model 
		will treat it it as an outflow and remove it from the ISM, though in 
		nature it would still show up in observations and be counted as part 
		of the Milky Way's gas content. {\color{red} It's therefore plausible 
		that the difference could simply be nuanced semantics regarding what 
		we refer to as an outflow numerically and what would be considered an 
		outflow in an observational study (i.e. ejection from the disc).} 
		\begin{itemize} 
			\item Based on this argument, one potential source of the 
			difference could be infall from the circum- and inter-galactic 
			media that have not yet been made available for star formation. 
			This would show up as HI and HII observed in the ISM, but would 
			not be counted in our models if it is not yet incorporated into 
			the star forming reservoir.

			\item Another potential source could be star formation efficiency 
			in the meaning that the ISM/feedback literature often takes: the 
			fraction of molecular cloud masses that are converted into stars. 
			To first order, this value is a few percent with some intrinsic 
			scatter ({\color{red} citation}). This means that in our models, 
			a significant multiplier ($\sim$30) of the stellar mass formed in 
			a given timestep should be added to the hot phase of the ISM in 
			the form of HII through feedback processes. If this gas is never 
			again made available for star formation, our model would treat it 
			as an outflow, removing it from the ISM mass, while in nature it 
			is still observed within the reasonably confined region defining 
			the Galaxy.

			\item Together, these effects may constitute the remaining factor 
			of~$\sim$ of warm and hot gas that our fiducial model is missing. 
			However, an investigation of the impact of a multi-phase ISM on 
			models such as these is outside the scope of this paper. 
		\end{itemize} 
	\end{itemize}

	\item Whatever the source of this discrepancy may be, the decision 
	about the mathematical form of~$\tau_\star$ does not significantly 
	impact our conclusions, as demonstrated in the remainder of this Appendix. 
\end{itemize}

\end{appendices}

\newpage 
\bibliographystyle{mnras} 
\bibliography{outline2}

\label{lastpage} 
\end{document}

### 2021-08-04 chemev/MWbimodality/paper/outline3/outline3.tex
migration paper referee response

--- 2021-08-04 chemev/MWbimodality/paper/outline2/outline2.tex
@@
 \newcommand{\refp}[1]{(\ref{#1})} 
+\newcommand{\msun}{\ensuremath{\text{M}_\odot}} 
+\newcommand{\persqkpc}{\ensuremath{\text{kpc}^{-2}}} 
 \providecommand{\noopsort}[1]{} 
@@
 
-\title{Stellar Migration and Chemical Enrichment in the Milky Way}
+\title[Stellar Migration and Chemical Enrichment]{Stellar Migration and 
+Chemical Enrichment in the Milky Way Disk: Predictions of a Hybrid Model}
 
@@
 a late starburst model; no one model investigated here fits both 
-simultaneously. We also find that our models predict a dichotomy in 
-[$\alpha$/Fe], but that they do not resemble that observed in the Milky Way 
-due to an overabundance of intermediate [$\alpha$/Fe] stars. This suggests 
+simultaneously. Our model successfully reproduces the broad nature of the 
+[$\alpha$/Fe] distribution at fixed [Fe/H] in a given Galactic region; however, 
+an overprediction of the frequency of intermediate [$\alpha$/Fe] stars prevents 
+it from explaining the observed results in detail. This suggests 
 that inside-out galaxy growth combined with radial migration, even with a late 
@@
 	\item Known for some time that stars undergo radial migration 
-	\citep[e.g.][]{Wielen1996}, but to date there are only a handful of 
-	chemical evolution models that take this into account 
-	\citep[e.g.][]{Schoenrich2009, Minchev2013, Sharma2020}. This effect can 
-	have a considerable impact on observed abundance trends by mixing stars 
-	that formed out of Galactic regions with significantly different 
-	enrichment histories, and if not taken into account, will impact the 
-	conclusions of chemical evolution studies.
-
-	\item The Age-Metallicity Relation (AMR) 
-	\begin{itemize} 
-		\item Age-metallicity relation in the solar neighbourhood exhibits 
-		considerable intrinsic scatter~\citep{Edvardsson1993}, usually 
-		attributed to radial migration of metal-rich (metal-poor) stars formed 
-		at smaller (larger) Galactocentric radii~\citep{Sellwood2002, 
-		Haywood2008, Roskar2008b, Schoenrich2009}.
-
-		\item \citet{Feuillet2018} reveal that super-solar metallicity stars 
-		are statistically older than solar metallicity stars (their Fig. 3). 
-		Contrasts with simple one-zone models where enrichment proceeds 
-		alongside star formation yielding a monotonic 
-		AMR~\citep[e.g.][]{Andrews2017, Weinberg2017}. One-zone models of 
-		starbursts can produce non-monotonic AMR due to the effect of 
-		dilution~\citep{Johnson2020}, but they by construction do not predict 
-		multiple abundances at fixed age. Argued using 
-		the~\citet{Weinberg2017} 
-		% the~\mniiiauthor{Weinberg}{Andrews}{Freudenburg}  
-		analytic models that this is a consequence of radial migration - for a 
-		smooth star formation history (SFH), the youngest stars at any given 
-		radius will have composition reflective of the local equilibrium 
-		abundance, and only older stars will have had adequate time to 
-		migrate to a similar Galactocentric radius. 
-	\end{itemize}
-
-	\item The Young Alpha-Rich Population 
-	\begin{itemize} 
-		\item Population of young ($\sim$few Gyr), [$\alpha$/Fe]~$\sim$ 
-		0.1-0.2 stars in the solar neighbourhood.
-
-		\item Found using stellar ages estimated from carbon-to-nitrogen 
-		ratios~\citep{Martig2016}, isochrone matching~\citep{Feuillet2018, 
-		Feuillet2019}, and with the asteroseismic ages in the original APOKASC 
-		catalog~\citep{Chiappini2015, SilvaAguirre2018, Pinsonneault2014}. 
-		\citet{SilvaAguirre2018} demonstrated that these stars have 
-		kinematics similar to the rest of the high-$\alpha$ population, and 
-		argued based on this that they may be the consequence of stellar 
-		mergers or mass transfer events, making truly old stars simply appear 
-		younger.
-
-		\item \citet{Mor2019} infer a factor of~$\sim$2 enhancement in the 
-		SFH of the Milky Way~$\sim$2 Gyr ago by comparing population synthesis 
-		models to observed stellar luminosity functions and color-magnitude 
-		diagrams from Gaia data~\citep{GaiaDR2}.~\citet{Isern2019} reach 
-		similar conclusions by modeling the white dwarf luminosity function in 
-		the solar neighbourhood with Gaia parallaxes. Motivated by these 
-		results, \citet{Johnson2020} demonstrate using one-zone chemical 
-		evolution models that a recent starburst can produce young, 
-		$\alpha$-enhanced stars. Caveat: burst would have had to be 
-		sufficiently localized such that the young,~$\alpha$-rich stars remain 
-		outliers from an otherwise monotonically descreasing age-[$\alpha$/Fe] 
-		relation. 
+	\citep[e.g.][]{Wielen1996}; this is an effect which could considerably 
+	impact chemical evolution in galaxies by mixing stars that formed in 
+	different galactic regions with significantly different enrichment 
+	histories.
+
+	\item To date there are only a handful of models which attempt to include 
+	this information, all focused on the Milky Way~\citep[e.g.][]{Matteucci1989, 
+	Schoenrich2009, Minchev2013, Sharma2020}. Each of these 
+	studies treated the Milky Way as a series of concentric annuli, each 
+	described by a conventional one-zone model with parameters that change from 
+	annulus to annulus. In the resultant ``multi-zone'' model, stars and gas 
+	migrate between zones under some prescription to account for mixing 
+	processes. In this paper, we adopt an approach similar to that used by 
+	\citet{Minchev2013}, in which the mixing processes are informed by star 
+	particles from a hydrodynamical simulation ran from cosmological initial 
+	conditions. With parameters tuned to reproduce observed results, such as 
+	abundance and surface density gradients, we can then assess the model 
+	predictions to address the following question: when combining simple, 
+	conventional assumptions about the star formation and dynamical histories 
+	of the Milky Way, what observed results can be replicated?
+
+	\item The observables that we focus on are: 
+	\begin{itemize} 
+		\item Metallicity distributions and abundance gradients
+
+		\item The [$\alpha$/Fe] bimodality
+
+		\item The age-metallicty relation (AMR)
+
+		\item The young, $\alpha$-rich population
 	\end{itemize}
@@
 
-		\item \citet{Spitoni2019} demonstrate that two-infall models can 
-		reproduce solar annulus data with good agreement. This plus 
-		radial migration is yet unexplored.
+		\item \citet{Spitoni2019, Spitoni2020} demonstrate that two-infall 
+		models can reproduce solar annulus data with good agreement. Recently, 
+		\citet{Spitoni2021} argued that this extends to other regions of the 
+		Galactic disc by reproducing APOGEE DR16 abundances by means of a 
+		chemical evolution model with three annuli centered on 4, 8, and 12 
+		kpc. Although they're able to reproduce the data for different regions 
+		of the Galaxy, their model does not include a treatment for the 
+		migration of stars beyond their birth radius; though with 4-kpc annuli, 
+		it's not likely there would be much impact given the coarse nature of 
+		the binning.
 
@@
 
-	\item This paper is meant to address the following simple question: When 
-	combining simple, conventional assumptions about the star formation and 
-	dynamical histories of the Milky Way, what observed results can be 
-	replicated? 
+	\item The Age-Metallicity Relation (AMR) 
+	\begin{itemize} 
+		\item Age-metallicity relation in the solar neighbourhood exhibits 
+		considerable intrinsic scatter~\citep{Edvardsson1993}, usually 
+		attributed to radial migration of metal-rich (metal-poor) stars formed 
+		at smaller (larger) Galactocentric radii~\citep{Sellwood2002, 
+		Haywood2008, Roskar2008b, Schoenrich2009}.
+
+		\item \citet{Feuillet2018} reveal that super-solar metallicity stars 
+		are statistically older than solar metallicity stars (their Fig. 3). 
+		Contrasts with simple one-zone models where enrichment proceeds 
+		alongside star formation yielding a monotonic 
+		AMR~\citep[e.g.][]{Andrews2017, Weinberg2017}. One-zone models of 
+		starbursts can produce non-monotonic AMR due to the effect of 
+		dilution~\citep{Johnson2020}, but they by construction do not predict 
+		multiple abundances at fixed age. Argued using 
+		the~\citet{Weinberg2017} 
+		analytic models that this is a consequence of radial migration - for a 
+		smooth star formation history (SFH), the youngest stars at any given 
+		radius will have composition reflective of the local equilibrium 
+		abundance, and only older stars will have had adequate time to 
+		migrate to a similar Galactocentric radius. 
+	\end{itemize}
+
+	\item The Young Alpha-Rich Population 
+	\begin{itemize} 
+		\item Population of young ($\sim$few Gyr), [$\alpha$/Fe]~$\sim$ 
+		0.1-0.2 stars in the solar neighbourhood.
+
+		\item Found using stellar ages estimated from carbon-to-nitrogen 
+		ratios~\citep{Martig2016}, isochrone matching~\citep{Feuillet2018, 
+		Feuillet2019}, and with the asteroseismic ages in the original APOKASC 
+		catalog~\citep{Chiappini2015, SilvaAguirre2018, Pinsonneault2014}. 
+		\citet{SilvaAguirre2018} demonstrated that these stars have 
+		kinematics similar to the rest of the high-$\alpha$ population, and 
+		argued based on this that they may be the consequence of stellar 
+		mergers or mass transfer events, making truly old stars simply appear 
+		younger.
+
+		\item \citet{Mor2019} infer a factor of~$\sim$2 enhancement in the 
+		SFH of the Milky Way~$\sim$2 Gyr ago by comparing population synthesis 
+		models to observed stellar luminosity functions and color-magnitude 
+		diagrams from Gaia data~\citep{GaiaDR2}.~\citet{Isern2019} reach 
+		similar conclusions by modeling the white dwarf luminosity function in 
+		the solar neighbourhood with Gaia parallaxes. Motivated by these 
+		results, \citet{Johnson2020} demonstrate using one-zone chemical 
+		evolution models that a recent starburst can produce young, 
+		$\alpha$-enhanced stars. Caveat: burst would have had to be 
+		sufficiently localized such that the young,~$\alpha$-rich stars remain 
+		outliers from an otherwise monotonically descreasing age-[$\alpha$/Fe] 
+		relation. 
+		\begin{itemize} 
+			\item The impact of such evolutionary histories combined with a 
+			model for stellar migration is, to our knowledge, yet unexplored in 
+			the literature. 
+		\end{itemize} 
+	\end{itemize}
+
+	\item A viable model for the detailed enrichment history of the Milky Way 
+	would explain simultaneously all of these observed results and their 
+	variations in different Galactic regions, while also taking into account 
+	effects like mixing and observational systematics. In this paper, we aim to 
+	assess the extent to which conventional assumptions about the evolutionary 
+	history of the Milky Way can account for these results, entertaining a 
+	handful of models describing the star formation history and time-dependence 
+	of radial migration. 
+	\begin{itemize} 
+		\item Motivated by the general result that Galaxies grow in radius 
+		(i.e. ``inside-out'' growth;~\citealp{Bird2013}), our base-line model 
+		has a star formation history whose e-folding timescales grow with 
+		Galactocentric radius. Motivated by the findings of~\citet{Mor2019} 
+		and~\citet{Isern2019}, we also construct models which exhibit a recent 
+		enhancement in the star formation rate. For comparison, we also 
+		construct a model in which the SFH is constant with time at fixed 
+		radius; this is interesting primarily from a theoretical perspective, 
+		removing the effects of a time-varying SFH to quantify only what is 
+		predicted by ongoing star formation with radial mixing.
+
+		\item While we make use of a hydrodynamical simulation to include the 
+		effects of radial migration, we do~\textit{not} make use of its star 
+		formation history. While~\citet{Minchev2013} also made use of a 
+		hydrodynamical simulation in their study, ours differs from theirs in 
+		this key aspect. The~\citet{Schoenrich2009} and~\citet{Sharma2020} 
+		studies, on the other hand, chose a model for radial migration that was 
+		based on dynamical arguments, which introduced free parameters that 
+		then required fitting to data. An advantage of our decision to make use 
+		of a hydrodynamical simulation over dynamical arguments is that it's 
+		unclear the extent to which fitting to observed data biases the model 
+		into agreement with parts of the data that weren't part of the fit. A 
+		hydrodynamical simulation, while still an approximation of reality, 
+		is motivated by first principles in that it models the gravitational 
+		interactions of star particles with gas and other star particles as 
+		well as the diffuse dark matter halo. The primary disadvantage of this 
+		choice is a consequence of the lack of free parameters - the model is 
+		rigid, and we cannot explore slight variations. However, in principle 
+		one could compare the predictions made by our chemical evolution models 
+		but with different hydrodynamical simulations. 
+	\end{itemize}
+
 \end{itemize}
@@
 \begin{itemize} 
-	\item To address the main goal of this paper, we make use of multi-zone 
-	chemical evolution models in which the Milky Way is described by a series 
-	of concentric annuli. Examples of similar methodologies already in 
-	the literature can be found in~\citet{Matteucci1989}, 
-	\citet{Schoenrich2009},~\citet{Minchev2013}, and~\citet{Sharma2020}. Here 
-	we entertain a handful of models describing the star formation history and 
-	the time-dependence of radial migration, then simply assess their 
-	predictions in comparison to the results discussed in~\S~\ref{sec:intro}.
-
-	\item Multizone models are a means of extending traditional one-zone 
-	models to take into account the motions of stars and gas by allowing the 
-	exchange of both between zones.
-
-	\item Our fiducial model has an inside-out star formation history (SFH) 
-	with parameters motivated by various observational constraints. Motivated 
-	by the findings of~\citet{Mor2019} and~\citet{Isern2019}, we construct a 
-	model with a late burst of star formation for comparison. A starburst of 
-	similar form was investigated in one-zone models in~\citet{Johnson2020}. 
-	For comparison, we also construct a model in which the SFH is constant 
-	with time at fixed Galactocentric radius. This is interesting primarily 
-	from a theoretical perspective; it removes the effects of a time-varying 
-	SFH and quantifies what is predicted when there is ongoing star formation 
-	with radial migration.
-
-	\item To include the effects of 
-	stellar migration, we make use of data from a hydrodynamical simulation, 
-	discussed in~\S~\ref{sec:methods:h277}. This allows us to adopt the 
-	dynamical history of a much more sophisticated simulation at face value, 
-	providing us with a model for radial migration that requires no free 
-	parameters. 
-	\begin{itemize} 
-		\item The~\citet{Schoenrich2009},~\citet{Minchev2013}, and 
-		\citet{Sharma2020} studies chose a model for radial migration that 
-		was based on dynamical arguments, which introduced free parameters 
-		that then required fitting to data. An advantage of our decision to 
-		make use of a hydrodynamical simulation over dynamical arguments is 
-		that it's unclear the extent to which fitting to observed data biases 
-		the model into agreement with parts of the data that weren't involved 
-		in the fit. A hydrodynamical simulation, while still an approximation 
-		of reality, is motivated by first principles in that it models the 
-		gravitational interactions of star particles with gas and other star 
-		particles as well as the diffuse dark matter halo. Furthermore, we 
-		choose here a hydrodynamical simulation which is ran from cosmological 
-		initial conditions.
-
-		\item The primary disadvantage of this choice is a consequence of the 
-		lack of free parameters - the model is rigid, and we cannot explore 
-		slight variations. However, in principle one could compare the 
-		predictions made by the same chemical evolution models but with 
-		different hydrodynamical simulations. 
-	\end{itemize}
-
 	\item To fulfill the goals of this paper, we develop and make use of 
@@
 	kinds of simulation with a wide range of flexibility. We reserve 
-	description of~\texttt{VICE}'s algorithm for~\S 
-	\ref{sec:methods:migration}, first describing our sample of star 
+	description of~\texttt{VICE}'s algorithm and our simulation parameters 
+	for~\S~\ref{sec:methods:migration}, first describing our sample of star 
 	particles from the hydrodynamical simulation.
+
+	\item We emphasize that the star particles from the hydrodynamical 
+	simulation are used~\textit{only} in the mixing component of our models. 
+	We make use of neither its star formation nor chemical enrichment 
+	histories; rather, these are exactly what we explore variations of in this 
+	paper. There is no N-body integration involved in our models. 
 \end{itemize}
@@
 
+% fig 1 
 \begin{figure*} 
@@
 
-	\item We find that only~$\sim$3\% of~\texttt{h277}'s star particles formed 
-	within the first 1 Gyr of its 13.7 Gyr run, indicating that $T$ = 1 Gyr 
-	is a much better estimate of the onset of star formation and thus the 
-	chemical evolution in~\texttt{h277} than $T$ = 0. We thus remove the star 
-	particles that were born in the first Gyr of evolution, and subtract 1 Gyr 
-	from their formation times, thus running our disc models for 12.7 Gyr. As 
-	a result, our simulations run from a redshift of~$z \approx$ 3 to the 
-	present day.
-
 	\item Of particular importance to have accurately measured formation radii 
@@
 
+	\item Of the star particles with ages at first snapshot of~$\leq$~150 Myr, 
+	the oldest star is 12.26 Gyr old at the present day. Since~\texttt{h277} 
+	ran for 13.7 Gyr, we therefore subtract 1.5 Gyr from the formation times of 
+	all star particles, and run our disc models for 12.2 Gyr. This value of 
+	$T$ = 1.5 Gyr is likely tied to the onset of star formation in the 
+	\texttt{h277} disc, which would have occurred some time following the 
+	cosmological initial conditions at a lookback time of 13.7 Gyr. As a result, 
+	our disc models trace the chemical evolution of the Milky Way out to a 
+	lookback time of 12.2 Gyr, or a redshift of~$z \approx$ 3.
+
+	\item We further restrict the sample of star particles to only those with 
+	both formation and final radii of~$R_\text{gal} \leq$~20 kpc, and to have 
+	formed within~$\left|z\right|\leq$~3 kpc of the disc midplane. These 
+	criteria ensure that we're only using star particles which formed in-situ. 
+	While it's possible that some star particles formed in a dwarf galaxy as it 
+	was infalling which would satisfy these criteria, these star particles 
+	are small in number, and are only relevant at large $R_\text{gal}$ and high 
+	ages, a region of parameter space where few stars form anyway.
+
 	\item Based on a kinematic decomposition performed on the present-day 
-	phase space distribution of the~\texttt{h277} star particles, we exclude 
-	halo stars, but include bulge, pseudobulge, and thin- and thick-disc 
-	stars. Even though we are not modeling the abundances in the bulge in this 
-	paper, the bulge is believed to have formed in-situ ({\color{red} 
-	citation}), while a significant fraction of halo stars are believed to 
-	have been accreted ({\color{red} citation}). It's also likely that the 
-	Milky Way bulge and disc exchanged statistically significant amounts of 
-	stars and gas ({\color{red} citation}), coupling the chemical evolution of 
-	the two at least slightly. This effect can be addressed in our models by 
-	simply including these star particles in our sample. This yields a sample 
-	of 3,019,521 star particles from~\texttt{h277}.
+	phase space distribution of the~\texttt{h277} star particles, we include 
+	all stars with bulge, pseudobulge, and disc-like kinematics, excluding the 
+	halo stars. While we're not modeling the evolution of the bulge here, these 
+	star particles are overwhelmingly located at~$R_\text{gal} \leq$~3 kpc at 
+	the present day anyway, while we're interested in~$R_\text{gal} \geq$~3 kpc 
+	in this paper since we're modeling the disc. This yields a sample of 
+	3,000,556 star particles from~\texttt{h277}.
 
 	\item \texttt{h277} had a transient bar during its evolution, but does 
-	not have a bar at $z$ = 0. This could mean that the star particles 
-	in~\texttt{h277} migrated in a manner which does not reflect the dynamical 
-	history of the Milky Way, but at present inferring a star's birth radius 
-	observationally is notoriously difficult anyway ({\color{red} citation}), 
-	so its likely the impact of this decision is within current 
-	observational uncertainties. Nonetheless, it is worth noting that 
-	the~\citet{Minchev2013} model, and by extension the~\citet{Minchev2014} 
-	and~\citet{Minchev2017} studies as well, selected a hydrodynamical 
-	simulation specifically so that it would have a bar at $z$ = 0. A detailed 
-	investigation of the impact of bar evolution on stellar migration and thus 
-	chemical evolution is outside the scope of this paper, though can be 
-	conducted in principle by simply swapping the birth times and initial and 
-	final radii of~\texttt{h277} within~\texttt{VICE}, rerunning the 
-	simulations, and comparing the results.
+	not have a bar at $z$ = 0. The~\citet{Minchev2013} model, and by extension 
+	the~\citet{Minchev2014} and~\citet{Minchev2017} models as well, selected a 
+	hydrodynamical simulation specifically so that it would have a bar at 
+	$z$ = 0. This could mean that the dynamical history of our models Galaxies 
+	do not reflect that of the~\citet{Minchev2013} model, and perhaps the 
+	Milky Way itself. A detailed investigation on the impact of bar evolution 
+	on stellar migration and thus chemical evolution is outside the scope of 
+	this paper, though can be conducted in principle by simply swapping the 
+	\texttt{h277} data within~\texttt{VICE} for another simulation, then 
+	rerunning our numerical models and comparing the results.
 
@@
 	defaults, it adopts the stellar migration model described in this section 
-	{\color{red}and our star formation law described in~\S 
-	\ref{sec:methods:sfe}.}
+	and our star formation law described in~\S~\ref{sec:methods:sfe}.
 
@@
 	~\texttt{VICE}'s~\texttt{milkyway} object assumes stellar populations to 
-	be born at the centres of each annulus. 
-	For a stellar population born at time $T$ and Galactocentric radius 
-	$R_\text{gal}$, it searches for star particles from~\texttt{h277} that formed at $T \pm$ 300 Myr and $R_\text{gal} \pm$ 250 pc. It then randomly 
-	selects a star particle from this subsample with no bias to act as 
-	an~\textit{analog}. Adopts the final radius of the analog star particle at 
-	face value, and moves from its radius of birth to the final radius at $T$ 
-	= 12.7 Gyr with some time dependence. If no candidate analogs are found, 
-	search is widened to $T \pm$ 600 Myr and $R_\text{gal} \pm$ 500 pc. If 
-	still no candidate analogs are found in this widened search, the stellar 
-	population is assumed to remain at its birth radius {\color{red} and to 
-	have a final height above the disc midplane of $z$ = 100 kpc.} These 
-	stellar populations are few in number. In our fiducial model with an 
-	inside-out SFH (see~\S~\ref{sec:methods:sfhs}), these stellar populations 
-	account for~$\sim$4.9\% of the simulated stellar populations by number, 
-	but only~$\sim$0.56\% by mass. Making up such a small portion of the mass 
-	budget, it's not likely they contribute significantly to the chemical 
-	evolution of our model Galaxy. 
-	\begin{itemize} 
-		\item We have zones for each annulus from $R_\text{gal}$ = 0 to 
-		20 kpc; there are no zones off the midplane. This retains the 
-		assumption that the gas-phase abundances are vertically and 
-		azimuthally well-mixed. Each stellar population simply assumes the 
-		final height~$\left|z\right|$ above the disc midplane of its assigned 
-		analog, though this doesn't enter into the simulations at all; it's 
-		purely post-processing information. 
-	\end{itemize}
+	be born at the centres of each annulus. For a stellar population born at a 
+	time~$T$ and Galactocentric radius~$R_\text{gal}$, it first searches for 
+	star particles from~\texttt{h277} that formed at~$T \pm$ 250 Myr and 
+	$R_\text{gal} \pm$ 250 pc. It then randomly selects a star particle from 
+	this subsample with no bias to act as an~\textit{analog}. This stellar 
+	population then assumes the change in orbital radius~$\Delta R_\text{gal}$ 
+	of its analog at face value, and moves from its birth radius to the implied 
+	final radius at $T$ = 12.2 Gyr with some time dependence. If no candidate 
+	analogs are found,~\texttt{VICE} widens the search to~$T \pm$ 500 Myr and 
+	$R_\text{gal} \pm$ 500 pc. While the maximum allowed difference in birth 
+	times caps here at 500 Myr, we allow the difference in birth radii to 
+	continue increasing by 250 pc until a candidate analog is found. 
+	\begin{itemize} 
+		\item In principle this allows stellar populations to be assigned 
+		analogs with significantly different birth radii; however, this is only 
+		an issue for small~$T$ and large~$R_\text{gal}$ where there are few 
+		star particles from~\texttt{h277}, and where few stars form in nature 
+		anyway due to the inside-out growth of Galaxies. Furthermore, due to 
+		the similarity of the histograms in the top row of Fig. 
+		\ref{fig:h277_decomposition}, we expect taking~$\Delta R_\text{gal}$ 
+		from a star particle which formed at a similar time but different birth 
+		radius in these instances to be accurate enough for our purposes.
+
+		\item Each annulus in our models does not contain any vertical 
+		information; that is, the displacements of stars from the disc midplane 
+		$\left|z\right|$ does not enter into our models at all. After running 
+		a~\texttt{VICE} simulation, each stellar population is simply assumed 
+		to be located at the present-day~$z_\text{final}$ of its assigned 
+		analog. In effect, this retains the assumption that the gas-phase 
+		abundances are verticaly and azimuthally well-mixed, and that changes 
+		in the gas composition at a given time happen only in the radial 
+		direction.
 
 		\item When a star particle is assigned as an analog to a stellar 
-	population in our simulations, it is~\textit{not} thrown out of the sample 
-	of candidate analogs, in theory allowing a star particle to act as an 
-	analog for multiple stellar populations. This is a difference between 
-	the~\citet{Minchev2013} model and ours. Where we assign star particles to 
-	stellar populations for which~\texttt{VICE} then calculates a stellar mass 
-	and composition based on an assumed star formation history, the 
-	\citet{Minchev2013} model assigns compositions to star particles.
-
+		population in our simulations, it is~\textit{not} thrown out of the 
+		sample of candidate analogs, in theory allowing a star particle to act 
+		as an analog for multiple stellar populations. This is a difference 
+		between the~\citet{Minchev2013} model and ours. Where we assign star 
+		particles to stellar populations for which~\texttt{VICE} then 
+		calculates a stellar mass and composition based on an assumed star 
+		formation history, the~\citet{Minchev2013} model assigns compositions 
+		to star particles. 
+	\end{itemize}
+
+% fig 2 
 \begin{figure} 
@@
 	\begin{itemize} 
-		\item All neglect radial gas flows, this paper instead focusing on 
-		four simple models for how the radius of a stellar population's orbit 
-		changes with time. Investigation of our models with radial gas flows 
-		would be an interesting extension to this paper.
+		\item With our data from the~\texttt{h277} simulation 
+		providing a stellar population born at some radius~$R_\text{gal}$ and 
+		time~$T$ with the required~$\Delta R_\text{gal}$, we construct the 
+		following four models describing the time-dependence with which a 
+		stellar population moves to its final radius.
+
+		\item All models here neglect radial gas flows, this paper instead 
+		focusing on these simple models describing how orbital radii change 
+		with time. Investigation of our models with radial gas flows would be 
+		an interesting extension to this paper.
 
@@
 		corresponds to a scenario in which the random walk carries out the 
-		diffusion of angular momentum.
+		diffusion of angular momentum. This is qualitatively similar to 
+		\citet{Frankel2018, Frankel2020}, who also model radial orbit migration 
+		with a~$\sqrt{\tau}$ dependence.
 
@@
 
-	\item We have a sample of 3,019,521 candidate analog star particles 
-	from~\texttt{h277}, only~$\sim$57\% of which are disc stars. Since we're 
-	modeling the thin and thick disc populations here,~$\sim$1.72 million is a 
+	\item We have a sample of 3,000,556 candidate analog star particles from 
+	\texttt{h277}, only~$\sim$57\% of which are disc stars. Since we're 
+	modeling the thin and thick disc populations here,~$\sim$1.71 million is a 
 	much better estimate of the number of analogs that we can realistically 
-	sample from. We let star formation extend out to 15.5 kpc, beyond which 
-	we force the star formation rate to zero at all times.~\texttt{VICE} does 
-	form stellar populations at all timesteps in the annuli; they simply have 
-	zero mass and thus do not contribute to the chemical evolution or 
-	recycling, though they do contribute to the computational overhead. We 
-	take $\Delta R_\text{gal}$ = 100 pc as the width of each annulus from 
-	$R_\text{gal}$ = 0 to 20 kpc and a timestep size of $\Delta T$ = 10 Myr 
-	from $T$ = 0 to 12.7 Gyr (see discussion in~\S~\ref{sec:methods:h277} for 
-	our choice of time-interval). With the resulting 200 zones and 1,271 
-	timesteps, we let~\texttt{VICE} form~$n$ = 8 stellar 
-	populations per zone per timestep, resulting in 2,033,600 stellar 
-	populations with predicted masses and abundances, 1,574,800 of which form 
-	between~$R_\text{gal}$ = 0 and 15.5 kpc and have nonzero mass, reasonably 
-	within the limit of what we can sample. These simulations run in~$\sim$2 
-	hours and take up~$\sim$235 MB of disc space per output, including the 
-	extra data that we record for each stellar population's analog star 
+	sample from. We take~$\Delta R_\text{gal}$ = 100 pc as the width of each 
+	annulus from~$R_\text{gal}$ = 0 to 20 kpc and a timestep size of 
+	$\Delta T$ = 10 Myr from $T$ = 0 to 12.2 Gyr (see discussion in~\S 
+	\ref{sec:methods:h277} for our choice of time-interval). With the resulting 
+	200 zones and 1,221 timesteps, we let~\texttt{VICE} from~$n$ = 9 stellar 
+	populations per zone per timestep, resulting in 2,197,800 total stellar 
+	populations with predicted masses and abundances. While this is more than 
+	the number of disc particles in our sample of candidate analogs, we force 
+	the star formation rate to zero beyond~$R_\text{gal}$ = 15.5 kpc; while 
+	these stellar populations exist within~\texttt{VICE} and are a part of the 
+	computational overhead, they have zero mass and thus do not contribute to 
+	the chemical evolution. This results in 1,692,306 stellar populations 
+	with~\textit{non-zero} masses and abundances predicted by~\texttt{VICE}, 
+	reasonably within the limit of what we can sample. These simulations run in 
+	$\sim$6 hours and take up~$\sim$235 MB of disc space per output, including 
+	the extra data that we record for each stellar population's analog star 
 	particle.
+
+	\item We emphasize that~\texttt{h277} provides our model with~\textit{only} 
+	the~$\Delta R_\text{gal}$ and~$z_\text{final}$ for each individual stellar 
+	population. We do not use the SFH of~\texttt{h277} or its chemical 
+	enrichment history in any way, making use of only the dynamical history. 
+	There is no N-body algorithm embedded within~\texttt{VICE} determining the 
+	positions of stars at times between their birth and the present day. 
 \end{itemize}
@@
 \begin{itemize} 
-	% \item Brief background on~\texttt{VICE}'s algorithm: we form a given 
-	% number of stellar populations in each zone and at each timestep. They 
-	% then migrate between zones according to our algorithm and eject CCSN and 
-	% SN Ia products as smooth functions of time according to our yields.
-
 	\item \textit{Fractional net} yields, as required by~\texttt{VICE}. 
@@
 		$x$ and ejected to the ISM, neglecting outflows.
-
-		\item \texttt{VICE} includes functionality with which to calculate 
-		the value of $y_x^\text{CC}$ for a handful of nucleosynthetic yield 
-		studies. Details can be found in~\S~2 of~\citet{Johnson2020} and in 
-		\texttt{VICE}'s documentation. A detailed investigation of 
-		CCSN nucleosynthetic yields which releases new features to these 
-		calculations will be presented in Griffith et al. (2021, in prep).
 
@@
 
-	\item Similar to SN Ia, the equation detailing asymptotic giant brach 
-	(AGB) star enrichment changes from an integral over the SFH to a summation 
-	over the stellar populations in a given zone at some time.~\texttt{VICE} 
-	in its current iteration forces AGB enrichment to be included in its 
-	simulations, though the yields of O and Fe from AGB stars are negligible 
-	compared to their supernova yields, and the results presented in this 
-	paper can be interpreted as if they were zero. 
-	\begin{itemize} 
-		\item The algorithm is based on determining the fraction of a single 
-		stellar population's mass that is in the form of stars that will have 
-		ended their post-main-sequence lifetime during the next timestep. 
-		The mass of those stars and their birth metallicity can then be 
-		used to determine a yield given a table of $y_x^\text{AGB}$ values 
-		sampled on a grid of stellar mass and metallicity, for which we take 
-		values from the FRUITY database of net yeilds~\citep{Cristallo2011}. 
-		Since these yields are not important for this paper, however, we do 
-		not go into further detail. More information on \texttt{VICE}'s 
-		treatment of AGB enrichment can be found in its documentation and in 
-		\S~2.6 of~\citet{Johnson2020}. 
-	\end{itemize}
-
-	\item Outflows are directly tied to nucleosynthetic yields, because the 
-	absolute scaling of nucleosynthetic yields and the efficiency with which 
-	galactic winds remove them from the star forming reservoir determine the 
-	\textit{effective} yield: the amount of metals that are not only produced 
-	but added to the star forming reservoir. 
-	\begin{itemize} 
-		\item Based on studies of galactic fountains demonstrating that 
-		ejected metals tend to fall back to a similar radius at which they 
-		were produced~\citep[e.g.][]{Melioli2008, Melioli2009, Spitoni2008, 
-		Spitoni2009}, a number of chemical evolution models 
-		\citep[e.g.][]{Minchev2013, Spitoni2019} neglect outflows, arguing 
-		that they are not a necessary ingredient to chemical evolution models. 
-		However, with the yields we've adopted, our models require significant 
-		metal ejection to predict realistic abundances. For this reason, 
-		studies which neglect outflows adopt significantly lower 
-		nucleosynthetic yields as a consequence.
-
-		\item There is a near one-to-one degeneracy between the scaling of 
-		nucleosynthetic yields and the efficiency of metal ejection in 
-		galaxies. With nucleosynthetic yields that were conventional at the 
-		time,~\citet{Dalcanton2007} demonstrated that significant outflows 
-		are required to lower effective yields and predict abundances in 
-		agreement with observations. This is a solution to the so-called 
-		``G-dwarf problem'' in which closed-box models of chemical evolution 
-		\citep[see the review in, e.g.,][]{Tinsley1980}  catastrophically 
-		over-predict the number of super-solar metallicity stars 
-		\citep{vandenBergh1962, Pagel1975}. However, recent findings with 
-		regard to black hole formation and stellar explodability have 
+	\item Our model assumes that all supernova yields of O and Fe are 
+	independent of metallicity. While this appears to be empirically true in 
+	the Milky Way~\citep{Weinberg2019, Griffith2020}, our CCSN yields are based 
+	on supernova explosion models in which all >8 M$_\odot$ progenitor produces 
+	a CCSN event~\citep[e.g.][]{Chieffi2004, Chieffi2013}. Recent findings 
+	with regard to black hole formation and stellar explodability have 
 	demonstrated that many massive stars simply do not produce a supernova 
-		event (see theoretical discussion by, e.g.,~\citealp{Pejcha2015, 
-		Sukhbold2016}, and observation evidence from~\citealp{Gerke2015, 
-		Adams2017, Basinger2020}). This challenges the results of 
-		\citet{Dalcanton2007}, suggesting that nucleosynthetic yields are 
-		intrinsically low, and the extent to which theoretically predicted 
-		stellar explodability models reduce the need for outflowing winds 
-		remains an unanswered question for future studies. 
-	\end{itemize}
-
-	\item Mass-loading factor $\eta$ defined as the ratio of mass outflow 
-	rates from the ISM to the SFR: 
+	explosion (see theoretical discussion by, e.g.,~\citealp{Pejcha2015}; 
+	\citealp{Sukhbold2016}, and observational evidence from 
+	\citealp{Gerke2015, Adams2017, Basinger2020}). Such effects would 
+	necessarily lower CCSN yields of all elements. While~\texttt{VICE} includes 
+	functionality with which to calculate $y_x^\text{CC}$ for some element $x$ 
+	using built-in tables from supernova nucleosynthesis studies, an in-depth 
+	investigation of the impact of these effects is outside the scope of this 
+	paper. Such an investigation which expands the capabilities of~\texttt{VICE} 
+	will be presented in Griffith et al. (2021, in prep). With regard to our SN 
+	Ia yields,~\citet{Brown2019} demonstrate that the local specific SN Ia rate 
+	shows a strong, inverse dependence on galaxy stellar mass. They argue that 
+	this may imply a metallicity dependent~$R_\text{Ia}$ that produces more SN 
+	Ia events at early times when the metallicity is low. However, these 
+	metallicities are only present in our models at very early times. 
+	Furthermore, when outflows are taken into account, these yields are known 
+	to predict observationally plausible abundances~\citep{Andrews2017, 
+	Weinberg2017}.
+
+	\item \citet{Weinberg2017} demonstrate that, to first order, the 
+	nucleosynthetic yields of a given element and the strength of outflowing 
+	winds determine the late-time equilibrium abundance in the ISM. We retain 
+	their characterization of outflows here, in terms of a mass-loading 
+	factor~$\eta$: 
 	\begin{equation} 
@@
 	\end{equation} 
-	\citet{Weinberg2017} demonstrate that, to first order, this parameter and 
-	the yields of a given element set the late-time equilibrium abundance. 
-	Here we adopt a scaling of~$\eta$ with Galactocentric radius~$R_\text{gal}$ 
-	such that the equilibrium abundance as a function of~$R_\text{gal}$ 
-	reproduces a metallicity gradient in agreement with observations.
-
-	\item A fundamental observable, the observed metallicity gradient in the 
-	Milky Way has been the focus of a considerable number of studies to date. 
-	\begin{itemize} 
-		\item \citet{Nordstroem2004a} find a gradient of -0.099 kpc$^{-1}$ in 
-		[Fe/H] in main sequence stars from GCS~\citep{Nordstroem2004b, 
-		Holmberg2007}.
-
-		\item \citet{Daflon2009} find a gradient of -0.04 kpc$^{-1}$ in 
-		[S/H] in OB stars
-
-		\item \citet{Frinchaboy2013} find a gradient of -0.09 kpc$^{-1}$ in 
-		[M/H] in open clusters.
-
-		\item \citet{Hayden2014} also find -0.09 kpc$^{-1}$ in [M/H] for 
-		$R_\text{gal}\gtrsim$ 6 kpc for low-$\alpha$ stars. For 
-		$R_\text{gal}\lesssim$ 6 kpc, they find a relatively flat gradient.
-
-		\item \citet{Weinberg2019} finds -0.06 kpc$^{-1}$ in mode([Mg/H]) for 
-		upper red giant branch disc stars (see their Fig. 23). 
-	\end{itemize}
+	Here we adopt a scaling of~$\eta$ with~$R_\text{gal}$ such that the 
+	late-time equilibrium abundance as a function of radius describes a 
+	metallicity gradient in agreement with observations; a similar methodology 
+	was employed by~\citet{Nidever2014}.
 
 	\item The procedure outlined in this section makes two assumptions: 1) 
-	that the mode abundance at a given radius reflects the equilibrium 
-	value at that radius, and 2) that radial migration does not significantly 
+	that the equilibrium abundance at a given radius corresponds to the mode 
+	of the observed MDF, and 2) that radial migration does not significantly 
 	impact the overall form of the gradient. We demonstrate that this holds in 
-	our simulations in~\S~\ref{sec:metallicity_gradient}.
+	our simulations in~\S~\ref{sec:comp_obs:metallicity_gradient}.
 
@@
 	where $r$ is the recycling parameter ($\approx$ 0.4 for the sake of this 
-	scaling with a~\citetalias{Kroupa2001} IMF; see discussion near the end of 
-	this section). Solving for $\eta(R_\text{gal})$ yields: 
+	scaling with a~\citetalias{Kroupa2001} IMF; see discussion in their~\S~2.2). 
+	Solving for $\eta(R_\text{gal})$ yields: 
 	\begin{equation} 
@@
 	} + r - 1 
-	= \frac{y_\alpha^\text{CC}}{Z_{\alpha,\odot}}10^{-\text{mode([X/H])}
+	= \frac{y_\alpha^\text{CC}}{Z_{\alpha,\odot}}10^{-\text{mode([$\alpha$/H])}
 	(R_\text{gal})} + r - 1 
@@
 
+	\item A fundamental observable, the observed metallicity gradient in the 
+	Milky Way has been the focus of a considerable number of studies to date. 
+	\begin{itemize} 
+		\item \citet{Nordstroem2004a} find a gradient of -0.099 kpc$^{-1}$ in 
+		[Fe/H] in main sequence stars from GCS~\citep{Nordstroem2004b, 
+		Holmberg2007}.
+
+		\item \citet{Daflon2009} find a gradient of -0.04 kpc$^{-1}$ in 
+		[S/H] in OB stars
+
+		\item \citet{Frinchaboy2013} find a gradient of -0.09 kpc$^{-1}$ in 
+		[M/H] in open clusters.
+
+		\item \citet{Hayden2014} also find -0.09 kpc$^{-1}$ in [M/H] for 
+		$R_\text{gal}\gtrsim$ 6 kpc for low-$\alpha$ stars. For 
+		$R_\text{gal}\lesssim$ 6 kpc, they find a relatively flat gradient.
+
+		\item \citet{Weinberg2019} finds -0.06 kpc$^{-1}$ in mode([Mg/H]) for 
+		upper red giant branch disc stars (see their Fig. 23). 
+	\end{itemize}
+
 	\item We assume a slope of -0.08 kpc$^{-1}$, in tentative agreement with 
 	the previous studies that quote the slope of the gradient mentioned above. 
-	To set the normalization, we assume the mode([X/H]) to be~$\sim$+0.3 at 
-	$R_\text{gal}$ = 4 kpc, since this would produce mode([X/H])~$\approx$~0 at 
-	$R_\text{gal}\approx$ 7 - 9 kpc. This results in the following form for 
-	$\eta$ as a function of Galactocentric radius: 
+	To set the normalization, we assume the mode([$\alpha$/H]) to be~$\sim$+0.3 
+	at $R_\text{gal}$ = 4 kpc, since this would produce mode([$\alpha$/H]) 
+	$\approx$~0 at~$R_\text{gal}\approx$ 7 - 9 kpc. This results in the 
+	following form for $\eta$ as a function of Galactocentric radius: 
 	\begin{equation} 
@@
 	where we adopt our yield of O for $y_\alpha^\text{CC}$ and the solar 
-	abundance of O of $Z_{\text{O},\odot}$ = 0.00572 from~\citet{Asplund2009}.
+	abundance of O of $Z_{\text{O},\odot}$ = 0.00572 based 
+	on~\citet{Asplund2009}.
 
@@
 
+% fig 3 
 \begin{figure} 
 \centering 
-\includegraphics[scale = 0.65]{eta_tau_sfh.pdf} 
+\includegraphics[scale = 0.45]{eta_tau_sfh.pdf} 
 \caption{\textbf{Top}: Our implemented scaling of the mass loading factor 
@@
 \begin{itemize} 
-	\item \citet{Weinberg2017} defined the~\textit{cumulative return fraction}
-	$r$ to be the fraction of a single stellar population's initial mass that 
-	has been returned to the ISM. In detail, $r$ is a complicated function of 
-	the age of a stellar population $\tau$ which depends on the assumptions 
-	about stellar lifetimes, the IMF, and an initial-remnant mass 
-	relation~\citep[e.g.][]{Kalirai2008}. 
-	\begin{itemize} 
-		\item \citet{Weinberg2017} demonstrated that the assumption 
-		of~\textit{instantaneous recycling} is a reasonable approximation, 
-		where instantaneous recycling refers only to~\textit{previously 
-		produced} nucleosynthetic products. We clarify that previous studies 
-		have made this approximation for newly produced material as well; 
-		while that assumption is valid for prompt sources like CCSNe, it fails 
-		for enrichment channels with significant DTDs, such as SNe Ia or 
-		AGB stars.~\citet{Weinberg2017} demonstrate that $r$ = 0.4 (0.2) is a 
-		good approximation for a~\citetalias{Kroupa2001} (
-		\citetalias{Salpeter1955}) IMF. However, this was demonstrated for 
-		smooth star formation histories 
-		and in parameter spaces conducive to analytic solution. Because 
-		numerical integration of $r(\tau)$ is neither challenging nor 
-		time-consuming,~\texttt{VICE} by default implements continuous 
-		recycling by solving $r(\tau)$ at the beginning of each simulation 
-		given the IMF, the~\citet{Kalirai2008} initial-remnant mass model, and 
-		the assumption that $\tau = \tau_\odot(M/M_\odot)^{-3.5}$. We also 
-		assume a post-main sequence lifetime of 10\% of the main sequence 
-		lifetime for all stars. Further details on the detailed form of 
-		$r(\tau)$ and its numerical integration within~\texttt{VICE} can be 
-		found in its documentation. 
-	\end{itemize}
-
-	\item In a one-zone model, the recycling rate can be expressed as an 
-	integral over the star formation history: 
-	\begin{equation} 
-	\dot{M}_x^\text{r} = \int_0^t Z_x(t') \dot{M}_\star(t') \dot{r}(t - t') dt' 
-	\end{equation} 
-	where $Z_x$ is the abundance by mass of the element~$x$ in the ISM at a 
-	time $t'$. Like SN Ia enrichment rates, extending this to multi-zone models 
-	changes the integral over the star formation history to a summation over 
-	the stellar populations in a given zone at some time: 
-	\begin{equation} 
-	\dot{M}_x^\text{r} = \sum_i Z_{x,i} M_i \dot{r}(\tau_i) 
-	\end{equation} 
-	In the case of the gas recycling rate, the equation has the same form, but 
-	without the weighting by metallicity.
-
-	\item We implement continuous recycling in our simulations, but make use 
-	of the instantaneous approximation in a handful of places in this paper 
-	(e.g. in our scaling of $\eta$ with $R_\text{gal}$, and in approximating 
-	SN Ia rates in~\S~\ref{sec:metallicity_space}). 
+	\item Both AGB star enrichment and the recycling of previously produced 
+	nucleosynthetic material in this paper proceed as they did in 
+	\citet{Johnson2020}, with the caveat that the mass is added to the annulus 
+	that a stellar population is in at a given time, which may or may not be 
+	the annulus it was born in.~\texttt{VICE} in its current version forces an 
+	AGB enrichment channel in all models; for this reason, it is also included 
+	in our models here, for which we adopt the yields sampled on a table of 
+	initial stellar mass and metallicity from~\citet{Cristallo2011}. However, 
+	the AGB star yields of O and Fe are negligible compared to their supernova
+	yields.
+
+	\item While we make use of these new simulation features in~\texttt{VICE} 
+	here, it includes a number of useful features not relevant to the current 
+	paper (e.g. CCSN yield calculations using built-in tables from supernova 
+	studies, z-dependent CCSN and SN Ia yields, user-constructed AGB yields as 
+	functions of stellar mass and metallicity, the exchange of gas between 
+	zones in a multi-zone model). {\color{red} Potentially move these 
+	statements to the conclusions section near the end, where it's already 
+	mentioned that~\texttt{VICE} is publicly available. } 
 \end{itemize}
@@
 
+% fig 4 
 \begin{figure*} 
@@
 \caption{The surface densities of star formation $\dot{\Sigma}_\star$ (top 
-row), infall $\dot{\Sigma}_\text{in}$ (middle row), and gas $\Sigma_\text{gas}$ 
+row), infall $\dot{\Sigma}_\text{in}$ (middle row), and gas $\Sigma_\text{g}$ 
 (bottom row) as functions of simulation time for our four fiducial SFHs: 
@@
 	formation mode, since we are after specific forms for the star formation 
-	histories of our models.
+	histories of our models. This means that changing our assumptions about the 
+	star formation law described in~\S~\ref{sec:methods:sfe} would not change 
+	the star formation rate, but would change the surface density of gas at 
+	each timestep, and thus also the implied infall rates.
 
@@
 		and~\citet{Mor2019}. Here we take $A_\text{b}$ = 1.5, $t_\text{b}$ = 
-		10.8 Gyr, and $\sigma_\text{b}$ = 1 Gyr.
+		10.2 Gyr, and $\sigma_\text{b}$ = 1 Gyr.
 
@@
 		\end{equation}
+
+		\item Although we do not investigate it here, an investigation into the 
+		impact of more episodic star formation histories would be an 
+		interesting extension of this paper. For example,~\texttt{VICE} has all 
+		of the necessary features to handle models in which major episodes of 
+		star formation coincide with the close passages of the Sagittarius 
+		dwarf~\citep[e.g.][]{RuizLara2020}. 
 	\end{itemize}
@@
 
-\subsection{Surface Density Gradient} 
-\label{sec:methods:surface_density_gradient}
-
+\subsection{Star Formation Efficiency} 
+\label{sec:methods:sfe}
+
+% fig 5 
 \begin{figure} 
 \centering 
-\includegraphics[scale = 0.45]{surface_density_gradient.pdf} 
-\caption{The surface density of gas (blue) and stars (red) as predicted by our 
-inside-out SFH model. The dotted black line with the higher normalization 
-denotes a thin disc profile with scale length $R_t$ = 2.5 kpc; the other 
-denotes a thick disc profile with scale length $R_T$ = 2.0 kpc, and a ratio of 
-$\Sigma_T/\Sigma_t$ = 0.27 at $R_\text{gal}$ = 0. The black line denotes the 
-sum of the two; this is the surface density gradient of the Milky Way as 
-reported by~\citet{Bland-Hawthorn2016}, renormalized to imply the same total 
-stellar mass within the disc. } 
-\label{fig:surface_density} 
-\end{figure}
-
-\begin{itemize} 
-	\item As discussed in~\S~\ref{sec:methods:sfhs}, Appendix 
-	\ref{sec:normalize_sfh} presents justification of a recipe in which we 
-	select a unitless, unnormalized form describing the scaling of the 
-	stellar surface density with Galactocentric radius, denoted 
-	$g(R_\text{gal})$. Here we adopt the following double exponential form, 
-	describing the thin and thick discs of the Milky Way: 
-	\begin{equation} 
-	g(R_\text{gal}) = e^{-R/R_t} + \frac{\Sigma_T}{\Sigma_t}e^{-R/R_T} 
-	\end{equation} 
-	where $R_t$ and $R_T$ are the scale radii of the thin and thick discs, 
-	respectively, and $\Sigma_T/\Sigma_t$ is the ratio of their surface 
-	densities at $R_\text{gal}$ = 0. In this paper, we adopt $R_t$ = 2.5 kpc, 
-	$R_T$ = 2.0 kpc, and $\Sigma_T/\Sigma_t$ = 0.27 from the findings of 
-	\citet{Bland-Hawthorn2016}.
-
-	\item Adopt the~\citet{Licquia2015} total stellar mass of 
-	$(6.08\pm1.14)\times10^{10}~M_\odot$. We're including bulge star particles 
-	in our sample of candidate analogs from~\texttt{h277}, so we model the 
-	entire stellar mass as opposed to just the disc, for 
-	which~\citet{Licquia2015} found $(5.17\pm1.11)\times10^{10}~M_\odot$.
-
-	\item Surface density gradient from fiducial model with inside-out SFH, 
-	plotted in Fig.~\ref{fig:surface_density} (stars in red and gas in blue). 
-	Radial migration indeed didn't change the overall scaling of 
-	$\Sigma_\star$ with $R_\text{gal}$ at the radii that we care about in 
-	this paper (3 kpc~$\lesssim R_\text{gal} \lesssim$~15 kpc), only 
-	introducing scatter. Gas disc appears to be flatten at 
-	$R_\text{gal}~\gtrsim$ 6 kpc; this is a consequence of our model for star 
-	formation efficiency (see discussion in~\S~\ref{sec:methods:sfe}). Black 
-	dotted lines show the individual thin and thick disc components that we 
-	adopt from~\citet{Bland-Hawthorn2016}, with the solid line denoting the 
-	sum of the two, all re-normalized such that the integral over the surface 
-	area of the model Galaxy implies a total stellar mass in agreement with 
-	our adopted value from~\citet{Licquia2015}. 
-\end{itemize}
-
-\subsection{Star Formation Efficiency} 
-\label{sec:methods:sfe}
-
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.6]{sfe.pdf} 
+\includegraphics[scale = 0.45]{sfe.pdf} 
 \caption{The star formation efficiency timescale $\tau_\star$ as a 
 function of Galactocentric radius at simulation times of 2 Gyr (red), 4 Gyr 
-(yellow), 6 Gyr (green), 8 Gyr (blue), 10 Gyr (purple), and 12.7 Gyr (i.e. 
+(yellow), 6 Gyr (green), 8 Gyr (blue), 10 Gyr (purple), and 12.2 Gyr (i.e. 
 the present day, black) predicted by our inside-out SFH model. }
@@
 	within some gas reservoir and the mass of the gas reservoir itself: 
-	$\tau_\star \equiv \Sigma_\text{gas}/\dot{\Sigma}_\star$. High (Low) 
+	$\tau_\star \equiv \Sigma_\text{g}/\dot{\Sigma}_\star$. High (Low) 
 	values of $\tau_\star$ indicate slow (fast) star formation and thus low 
 	(high) SFE; when we refer to SFE here, we're referring to the definition 
-	based on this timescale. 
-	\begin{itemize} 
-		\item Potentially note that this is often referred to as the 
-		``depletion time'' in star formation literature, and the 
-		\citet{Weinberg2017} definition of depletion 
-		time:~$\tau_\text{dep} \equiv \tau_\star/ (1 + \eta - r)$. 
-	\end{itemize}
-
-	\item This is a topic of intense observational inquiry, results of which 
-	we review in this section in the interest of obtaining an observationally 
-	motivated star formation law. 
-	\begin{itemize} 
-		\item In practice, many chemical evolution studies adopt a simple 
-		power-law for the Kennicutt-Schmidt law relating~$\Sigma_\text{gas}$ 
-		and~$\dot{\Sigma}_\star$: $\dot{\Sigma}_\star~\sim 
-		\Sigma_\text{gas}^N$, where~\citet{Kennicutt1998} infer 
-		$N = 1.4 \pm 0.15$ across a sample of quiescent spiral galaxies and 
-		infrared and circumnuclear starbursts.~\citet{delosReyes2019} derive a 
-		similar value of $N = 1.41 \pm 0.07$ for local quiescent spiral, 
-		dwarf, and low surface brightness galaxies, further demonstrating that 
-		much of the observed scatter is intrinsic.
-
-		\item \citet{Liu2015} demonstrate that the derived value of~$N$ is 
-		sensitive to the assumed form of the CO-to-H$_2$ conversion factor 
-		($\alpha_\text{CO}$); for fixed~$\alpha_\text{CO}$, they find 
-		$N = 1.14 \pm 0.02$, but~$N = 1.60 \pm 0.03$ for a continuously varying 
-		$\alpha_\text{CO}$ for a sample of 181 local galaxies with infrared 
-		luminosities spanning nearly five orders of magnitude. Much of the 
-		uncertainty in the detailed form of the star formation law is likely 
-		a consequence of the ongoing debate about~$\alpha_\text{CO}$ (and 
-		other mathematical defintions of the conversion factor as well, such 
-		as X(CO); see discussion in~\citealp{Kennicutt2012}).
-
-		\item In extending the~\citet{delosReyes2019} study to the most 
-		extreme infrared-luminous and circumnuclear starburst galaxies, 
-		\citet{Kennicutt2020} recently found a value of~$N = 1.50 \pm 0.05$. 
-		Although they determine that a single power law is a reasonable recipe 
-		for models of Galaxy evolution, they demonstrate that there is 
-		evidence for significant breaks in both the power-law indeces and the 
-		zeropoints. They argue that these breaks are physical in origin, and 
-		speculate that it is tied to the transition from a mixed atomic and 
-		molecular ISM in normal disc galaxies to a nearly fully molecular ISM 
-		in starburst galaxies. A transition to a linear 
-		$\dot{\Sigma}_\star-\Sigma_\text{gas}$ relation at a surface density 
-		above which the molecular fraction~$f_\text{mol} \approx 1$ is 
-		consistent with the finding that star formation proceeds only in the 
-		molecular phase~\citep[e.g.][]{Leroy2008, Leroy2013}.
-
-		\item Consistent with the finding that the intrinsic scatter in the 
-		observed~$\dot{\Sigma}_\star-\Sigma_\text{gas}$ relation is physical 
-		in origin,~\citet{Ellison2020b} demonstrate that this relation (among 
-		other fundamental correlations) shows significant galaxy-to-galaxy 
-		variations in both slope and normalization, suggesting that it is not 
-		universal between galaxies. \citet{Leroy2013} also find evidence that 
+	based on this timescale. In the star formation literature, this parameter 
+	is often referred to as the ``depletion time.''
+
+	\item Based on the findings of~\citet{Kennicutt1998}, it is common practice 
+	for chemical evolution studies to implement a single power-law star 
+	formation law of the form: 
+	\begin{equation} 
+	\dot{\Sigma}_\star \sim \Sigma_\text{g}^N 
+	\end{equation} 
+	where~$\dot{\Sigma}_\star$ and~$\Sigma_\text{g}$ are the surface 
+	densities of star formation and ISM gas, respectively, and 
+	\citet{Kennicutt1998} derive~$N = 1.4 \pm$ 0.15 relating the total 
+	$\dot{\Sigma}_\star$ and $\Sigma_\text{g}$ within the disc across a 
+	sample of quiescent spiral galaxies and infrared and circumnuclear 
+	starbursts. However, recent studies have found evidence that much of the 
+	observed scatter is physical in origin~\citep{delosReyes2019} and that 
+	there are significant breaks in both the power-law index and zeropoints 
+	\citep{Kennicutt2020}. Much of the uncertainty surrounding the details of 
+	the star formation law is a consequence of the ongoing debate about the 
+	CO-to-H$_2$ conversion factor~\citep{Kennicutt2012, Liu2015}. Although 
+	\citet{Ellison2020a} demonstrate that there are significant 
+	galaxy-to-galaxy variations in the star formation law, suggesting that 
+	individual galaxies do not follow the population-averaged trend, 
+	\citet{delosReyes2019} argue that this is still a reasonable recipe for 
+	Galaxy evolution models. We adopt such a formalism here.
+
+	\item \citet{Krumholz2018} compare model-predicted star formation laws to 
+	the observational data from~\citet{Bigiel2010} and~\citet{Leroy2013} (see 
+	their Fig. 2). We find that the following by-eye fit to the power-law 
+	index~$N$ is a reasonable description of the aggregate data: 
+	\begin{equation} 
+	N = \begin{cases} 
+	1.0 & (\Sigma_\text{g} \geq \Sigma_{\text{g},2}) 
+	\\ 
+	3.6 & (\Sigma_{\text{g},1} \leq \Sigma_\text{g} \leq \Sigma_{\text{g},2}) 
+	\\ 
+	1.7 & (\Sigma_\text{g} \leq \Sigma_{\text{g},1})  
+	\end{cases} 
+	\label{eq:ks_law_indeces}  
+	\end{equation} 
+	where~$\Sigma_{\text{g},1} = 5\times10^6~\msun~\persqkpc$ and 
+	$\Sigma_{\text{g},2} = 2\times10^7~\msun~\persqkpc$.
+
+	\item The apparent linearity of the relationship above~$\sim2\times10^7$ 
+	$\msun~\persqkpc$ suggests that in this regime, star formation is 
+	proceeding at the fastest possible rate, and that $\tau_\star$ = 
+	$\Sigma_\text{g}/\dot{\Sigma}_\star$ = constant. The results of 
+	\citet{Leroy2008, Leroy2013} and~\citet{Kennicutt2020} would suggest that 
+	this is the regime in which the molecular fraction 
+	$f_\text{mol} = M_{\text{H}_2} / (M_\text{HI} + M_{\text{H}_2}) \approx$ 1. 
+	We therefore adopt the assumption that above $\Sigma_\text{g}$ = 
+	$2\times10^7$~M$_\odot$~kpc$^{-2}$,~$\tau_\star$ reaches its minimum value, 
+	and increases with decreasing~$f_\text{mol}$. We denote this value as 
 	$\tau_\text{mol}$, the value of $\tau_\star$ for a gas reservoir with 
-		$f_\text{mol}$ = 1, is multivalued at fixed $\Sigma_{\text{H}_2}$, 
-		suggesting that the rate of star formation is set not only by the 
-		density of the gas reservoir, but other environmental parameters as 
-		well. 
-	\end{itemize}
-
-	\item Although we acknowledge the collective result that an individual 
-	galaxy would not obey the observed, population-averaged 
-	$\dot{\Sigma}_\star-\Sigma_\text{gas}$ relation, we decide to adopt 
-	such a prescription for our models here. Our motivation for doing so 
-	is two-fold. 
-	\begin{itemize} 
-		\item In practice, we find that our mathematical formalism for 
-		$\tau_\star$ does not significantly impact our conclusions; we 
-		demonstrate this in Appendix~\ref{sec:sfe_variations}. For this 
-		reason, a simple formalism is its own reward for our purposes.
-
-		\item As discussed in~\S~\ref{sec:methods:sfhs}, we are running 
-		\texttt{VICE} in star formation mode; this simply means that we 
-		have specified the~\textit{star formation history} of the Galaxy, 
-		rather than the infall history or the ISM surface density as 
-		functions of simulation time and radius. While many galaxy 
-		evolution models use these observed star formation laws to infer 
-		the star formation rate from the ISM surface density, here we are 
-		doing the inverse - inferring the ISM surface density from the 
-		star formation rate. We therefore do not know the properties of 
-		the ISM in our simulations a priori, and must resort to simple 
-		assumptions anyway. An investigation of more detailed 
-		prescriptions for star formation efficiency in models for 
-		enrichment in the Milky Way is an interesting which we must 
-		reserve for future work due to how we have constructed the 
-		simulations presented in this paper. 
-	\end{itemize}
-
-	\item Motivated by these recent results suggesting nuance within the 
-	star formation law~\citep{Leroy2013, Ellison2020b, Kennicutt2020}, we 
-	implement in our simulations a three-component power-law based on the 
-	results presented in~\citet{Krumholz2018}. They construct a turbulence and 
-	mass-transfer driven theoretical model for star formation in disc galaxies, 
-	and present a comparison of its predictions under a handful of parameter 
-	choices to the data from~\citet{Bigiel2010} and~\citet{Leroy2013} (see 
-	their Fig. 2). We find that the following by-eye fit is a reasonable 
-	description of the aggregate data: 
-	\begin{subequations}\begin{align} 
-	\dot{\Sigma}_\star &\sim \Sigma_\text{gas}^N \\ 
-	N &= \begin{cases} 
-	1.0 & (\Sigma_\text{gas} \geq 2\times10^7~\text{M}_\odot~\text{kpc}^{-2}) 
+	$f_\text{mol}$ = 1. This, combined with our three-component power-law index 
+	$N$ results in the following final form for our adopted star formation 
+	law:
+
+	\begin{equation} 
+	\dot{\Sigma}_\star =\begin{cases} 
+	\Sigma_\text{g} \tau_\text{mol}^{-1} & (\Sigma_\text{g} \geq 
+	\Sigma_{\text{g},2})  
 	\\ 
-	3.6 & (5\times10^6~\text{M}_\odot~\text{kpc}^{-2} \leq \Sigma_\text{gas} 
-		\leq 2\times10^7~\text{M}_\odot~\text{kpc}^{-2}) 
+	\Sigma_\text{g} \tau_\text{mol}^{-1} \left(\frac{
+		\Sigma_\text{g} 
+	}{
+		\Sigma_{\text{g},2}
+	}\right)^{2.6} & (\Sigma_{\text{g},1} \leq \Sigma_\text{g} \leq 
+	\Sigma_{\text{g},2}) 
 	\\ 
-	1.7 & (\Sigma_\text{gas} \leq 5\times10^6~\text{M}_\odot~\text{kpc}^{-2}) 
+	\Sigma_\text{g} \tau_\text{mol}^{-1} \left(\frac{
+		\Sigma_{\text{g},1} 
+	}{
+		\Sigma_{\text{g},2} 
+	}\right)^{2.6} \left(\frac{
+		\Sigma_\text{g} 
+	}{
+		\Sigma_{\text{g},1} 
+	}\right)^{0.7} & (\Sigma_\text{g} \leq \Sigma_{\text{g},1}) 
 	\end{cases} 
 	\label{eq:ks_law} 
-	\end{align}\end{subequations}
-
-	\item The apparent linearity of the relationship above~$\sim2\times10^7$ 
-	M$_\odot$ kpc$^{-2}$ suggests that in this regime, star formation is 
-	proceeding at the fastest possible rate, and that $\tau_\star$ = 
-	$\Sigma_\text{gas}/\dot{\Sigma}_\star$ = constant. The results of 
-	\citet{Leroy2008, Leroy2013} and~\citet{Kennicutt2020} would suggest that 
-	this is the regime in which~$f_\text{mol}$ = 1. We therefore adopt the 
-	assumptions that $f_\text{mol}$ is unity above an ISM surface density of 
-	$\Sigma_\text{gas} = 2\times10^7$~M$_\odot$~kpc$^{-2}$ and that 
-	$\tau_\star$ assumes that value of $\tau_\text{mol}$ at these densities, 
-	increasing with decreasing~$f_\text{mol}$.
-
-	\item With the formulation of the Kennicutt-Schmidt Law described by 
-	equation~\refp{eq:ks_law} and the mathematical definition 
-	$\tau_\star \equiv \Sigma_\text{gas}/\dot{\Sigma}_\star$, we can derive 
-	$\tau_\star-\Sigma_\text{gas}$ or $\tau_\star-\dot{\Sigma}_\star$ 
-	relationships as required by~\texttt{VICE}. With~$\tau_\star$ = 
-	$\tau_\text{mol}$ at~$\Sigma_\text{gas}~\geq~2\times10^7$~M$_\odot$ 
-	kpc$^{-2}$ setting the overall normalization, the following describes the 
-	resultant~$\tau_\star-\Sigma_\text{gas}$ relationship: 
-	\begin{equation}
-	\tau_\star = \begin{cases} 
-	\tau_\text{mol} & (\Sigma_\text{gas} \geq \Sigma_\text{gas,1}) 
-	\\ 
-	\tau_\text{mol} \left(\frac{\Sigma_\text{gas}}{\Sigma_\text{gas,1}}
-		\right)^{\beta_1} & (\Sigma_\text{gas,2} \leq \Sigma_\text{gas} \leq 
-		\Sigma_\text{gas,1}) 
-	\\ 
-	\tau_\text{mol} \left(\frac{\Sigma_\text{gas,2}}{\Sigma_\text{gas,1}}
-		\right)^{\beta_1} \left(\frac{\Sigma_\text{gas}}{\Sigma_\text{gas,2}}
-		\right)^{\beta_2} & (\Sigma_\text{gas} \leq \Sigma_\text{gas,2}) 
-	\end{cases} 
 	\end{equation} 
-	where we adopt~$\Sigma_\text{gas,1} = 2\times10^7$ M$_\odot$ kpc$^{-2}$, 
-	$\Sigma_\text{gas,2} = 5\times10^6$ M$_\odot$ kpc$^{-2}$,~$\beta_1$ = 
-	-2.6, and~$\beta_2$ = -0.7\footnote{
-		$\beta = 1 - N$, where N is the power-law index of the 
-		$\dot{\Sigma}_\star-\Sigma_\text{gas}$ relationship. 
-	}. The additional factor of 
-	$(\Sigma_\text{gas,2}/\Sigma_\text{gas,1})^{\beta_1}$ simply ensures that 
-	this formalism is piecewise-continuous.
+	where we chose the power-law indeces such that this formalism is consistent 
+	with equation~\refp{eq:ks_law_indeces}, and prefactors are added to ensure 
+	piece-wise continuity. In implementation,~\texttt{VICE} requires the 
+	$\tau_\star-\Sigma_\text{g}$ relationship when ran in infall and gas 
+	modes, and the~$\tau_\star-\dot{\Sigma}_\star$ relationship when ran in 
+	star formation mode. Both follow from this relationship given the 
+	substitution~$\tau_\star \equiv \Sigma_\text{g}/\dot{\Sigma}_\star$. 
+	\begin{itemize} 
+		\item Although it is more physically motivated to use an adopted star 
+		formation law to infer a star formation rate from the ISM properties at 
+		a given timestep, as discussed in~\S~\ref{sec:methods:sfhs}, we are 
+		using~\texttt{VICE} in star formation mode, meaning that it is 
+		$\dot{\Sigma}_\star$ rather than~$\Sigma_\text{g}$ or 
+		$\dot{\Sigma}_\text{in}$ which is specified~\textit{a priori}. 
+		Therefore, our models are inferring~$\Sigma_\text{g}$ from 
+		$\dot{\Sigma}_\star$, not the other way around. 
+	\end{itemize}
 
@@
 	\tau_\text{mol} = \tau_{\text{mol},0}(t/t_0)^\gamma 
+	\label{eq:tau_mol}
 	\end{equation} 
@@
 
+	\item At all timesteps in our models,~$\Sigma_\text{g}$ is inferred from 
+	$\dot{\Sigma}_\star$ directly from equations~\refp{eq:ks_law} and 
+	\refp{eq:tau_mol}. The infall rate is subsequently calculated from the 
+	amount of gas lost to new stars and outflows within a given timestep and 
+	the amount of gas implied by the star formation rate at the next timestep, 
+	and is assumed to be zero metallicity.
+
 	\item Fig.~\ref{fig:sfe} shows $\tau_\star$ as a function of $R_\text{gal}$ 
 	at six different time stamps predicted by our fiducial, inside-out SFH 
-	model. Wherever~$\tau_\star$ is at its minimum value is where the ISM in 
-	that annulus is fully molecular. 
-	\begin{itemize} 
-		\item In the fiducial inside-out model, the molecular fraction is near 
-		unity out to~$R_\text{gal} \approx$~6 kpc at all times.
-
-		\item From the actual value of $\tau_\star$ at a given radius and time 
-		and the assumed $\tau_\text{mol}$ in the model, we can derive the 
-		model predicted molecular fractions within the disk via 
-		$f_\text{mol} = \tau_\text{mol}/\tau_\star$, then subsequently the 
-		HI + HII and H$_2$ masses from $f_\text{mol}$ and the total gas supply 
-		after subtracting 27\% to account for helium.
-
-		\item These post-processing calculations suggest that our fiducial 
-		inside-out model predicts an HI + HII mass of~$5.54\times10^9$ 
-		M$_\odot$ and an H$_2$ mass of~$7.14\times10^9$~M$_\odot$ within 
-		$R_\text{gal}$ = 20 kpc, the maximum radius in our model. This 
-		predicts a total H mass of~$1.27\times10^{10}$~M$_\odot$, and a total 
-		ISM mass of~$1.74\times10^{10}$~M$_\odot$ after adding 27\% back to 
-		account for helium. This yields a global molecular fraction of 
-		$f_\text{mol}$ = H$_2$ / (HI + HII + H$_2$) = 56\%. In comparison with 
-		observed results, this is an overprediction of~$f_\text{mol}$; 
-		\citet{Kalberla2009} report a value of~$8\times10^9$ and 
-		$2.5\times10^9$~M$_\odot$ for the HI and H$_2$ masses within 60 kpc, 
-		the bulk of which is in the disk. They report an additional 
-		$\sim2\times10^9$~M$_\odot$ in the warm ionized medium (HII). 
-		\citet{Heyer2015} argue for a lower H$_2$ mass of~$1\times10^9$ 
-		M$_\odot$. Our fiducial model is over-predicting the H$_2$ mass by a 
-		factor of~$\sim$3 and under-predicting the HI + HII mass by a factor 
-		of~$\sim$2.
-
-		\item Whatever the source of this discrepancy may be, we present in 
-		Appendix~\ref{sec:sfe_variations} a variation of our fiducial model 
-		with a significantly different assumption about~$\tau_\star$, and 
-		demonstrate that this decision does not impact our general 
-		conclusions. We reserve discussion on potential sources of this 
-		discrepancy to Appendix~\ref{sec:sfe_variations} as well. {\color{red} 
-		This discussion may move back to this section, but I had some ideas 
-		on this, so I moved stuff later so that the methods section doesn't 
-		get lost in minutia. }
-	\end{itemize} 
+	model. At~$R_\text{gal} \lesssim$6 kpc,~$\tau_\star$ is near 
+	$\tau_\text{mol}$ at all times, implying a molecular fraction of unity at 
+	these radii. Although this prediction is likely unrealistic ({\color{red} 
+	citation?}), relaxing our assumptions about the star formation law does not 
+	significantly impact our conclusions. In collecting results for this paper, 
+	we investigated purely linear, purely power-law, and broken power-law star 
+	formation laws, finding similar predictions in all cases. In practice we 
+	find that the detailed form the star formation history and, to some extent, 
+	the time-dependence of radial migration have much more power over the model 
+	predictions. We interpret this as an indication that the details of the 
+	star formation law are at most secondary effects in establishing the model 
+	behavior. 
+\end{itemize}
+
+\subsection{Surface Density Gradient} 
+\label{sec:methods:surface_density_gradient}
+
+% fig 6 
+\begin{figure} 
+\centering 
+\includegraphics[scale = 0.45]{surface_density_gradient.pdf} 
+\caption{The surface density of gas (blue) and stars (red) as predicted by our 
+inside-out SFH model. The dotted black line with the higher normalization 
+denotes a thin disc profile with scale length $R_t$ = 2.5 kpc; the other 
+denotes a thick disc profile with scale length $R_T$ = 2.0 kpc, and a ratio of 
+$\Sigma_T/\Sigma_t$ = 0.27 at $R_\text{gal}$ = 0. The solid black line denotes 
+the sum of the two; this is the surface density gradient of the Milky Way as 
+reported by~\citet{Bland-Hawthorn2016}, renormalized to imply the same total 
+stellar mass within the disc. } 
+\label{fig:surface_density} 
+\end{figure}
+
+\begin{itemize} 
+	\item As discussed in~\S~\ref{sec:methods:sfhs}, Appendix 
+	\ref{sec:normalize_sfh} presents justification of a recipe in which we 
+	select a unitless, unnormalized form describing the scaling of the 
+	stellar surface density with Galactocentric radius, denoted 
+	$g(R_\text{gal})$. Here we adopt the following double exponential form, 
+	describing the thin and thick discs of the Milky Way: 
+	\begin{equation} 
+	g(R_\text{gal}) = e^{-R/R_t} + \frac{\Sigma_T}{\Sigma_t}e^{-R/R_T} 
+	\end{equation} 
+	where $R_t$ and $R_T$ are the scale radii of the thin and thick discs, 
+	respectively, and $\Sigma_T/\Sigma_t$ is the ratio of their surface 
+	densities at $R_\text{gal}$ = 0. In this paper, we adopt $R_t$ = 2.5 kpc, 
+	$R_T$ = 2.0 kpc, and $\Sigma_T/\Sigma_t$ = 0.27 from the findings of 
+	\citet{Bland-Hawthorn2016}. These are illustrated by the two dotted black 
+	lines in Fig.~\ref{fig:surface_density}, with the solid one denoting the 
+	sum of the two. Both have been re-normalized such that the integral over 
+	the surface area of the model Galaxy implies a total stellar mass in 
+	agreement with our adopted value.
+
+	\item Adopt the~\citet{Licquia2015} total stellar mass of 
+	$(6.08\pm1.14)\times10^{10}~M_\odot$. We're including bulge star particles 
+	in our sample of candidate analogs from~\texttt{h277}, so we model the 
+	entire stellar mass as opposed to just the disc, for 
+	which~\citet{Licquia2015} found $(5.17\pm1.11)\times10^{10}~M_\odot$. 
+	This choice only matters in setting the overall normalization of our 
+	adopted star formation histories~$\dot{\Sigma}_\star$ as a function of 
+	radius and time, in turn affecting the inferred gas surface density 
+	$\Sigma_\text{g}$ via our adopted star formation law (see discussion in 
+	\S~\ref{sec:methods:sfe}). In short, lower (higher) stellar masses suggest 
+	longer (shorter) values of~$\tau_\star$ at all times. This only impacts our 
+	models insofar as our choice about the star formation law matters; as 
+	discussed in~\S~\ref{sec:methods:sfe}, we find in practice that varying 
+	those assumptions don't impact our conclusions. We find the same for models 
+	with a different present-day stellar mass.
+
+	\item Surface density gradient from fiducial model with inside-out SFH, 
+	plotted in Fig.~\ref{fig:surface_density} (stars in red and gas in blue). 
+	Radial migration indeed didn't change the overall scaling of 
+	$\Sigma_\star$ with $R_\text{gal}$ at the radii that we care about in 
+	this paper (3 kpc~$\lesssim R_\text{gal} \lesssim$~15 kpc), only 
+	introducing scatter. Gas disc appears to flatten at 
+	$R_\text{gal}~\gtrsim$ 6 kpc; this is a consequence of our model for star 
+	formation efficiency (see discussion in~\S~\ref{sec:methods:sfe}). The 
+	radius at which~$\Sigma_\text{g}$ shows a break in Fig. 
+	\ref{fig:surface_density} coincides with the radius at which 
+	$\Sigma_\text{g}$ is low enough to transition from the 
+	$\dot{\Sigma}_\star \sim \Sigma_\text{g}$ to the 
+	$\dot{\Sigma}_\star \sim \Sigma_\text{g}^{3.6}$ piece of our adopted star 
+	formation law. With our star formation histories specified 
+	\textit{a priori}, these choices impact the radial profile of 
+	$\Sigma_\text{g}$. 
 \end{itemize}
@@
 
-\section{Metallicity Space} 
-\label{sec:metallicity_space}
-
+\section{Comparison to Observations} 
+\label{sec:comp_obs}
+
+% fig 7 
 \begin{figure*} 
@@
 
+% fig 8 
 \begin{figure*} 
@@
 color-coded according to their Galactocentric radius and denoted by the legend 
-in the lower-left. We mark simulation times of 2, 4, 6, 8, 10, and 12.7 Gyr in 
+in the lower-left. We mark simulation times of 2, 4, 6, 8, 10, and 12.2 Gyr in 
 X's for the diffusion model and points for the post-processing model. 
-\textbf{Right}: The proxy for the SN Ia rate defined in equation 
-\refp{eq:ia_rate_proxy} as a function of simulation time for the same annuli 
-as in the left-hand panel. We multiply rates at each radii here by various 
-prefactors to improve of clarity. }
+\textbf{Right}: As a function of simulation time, a proxy for the SN Ia rate 
+using the total time-derivative of the Fe mass in a given annulus, calculated 
+by subtracting the contribution from recycling and CCSN enrichment and adding 
+back that lost to star formation and outflows. We show these rates for the 
+same annuli as in the left-hand panel, multiplying them by various prefactors 
+to improve clarity. } 
 \label{fig:tracks} 
@@
 	\item The width of the low-$\alpha$ sequence predicted by the model comes 
-	from radial migration. Though this is somewhat guaranteed by our model 
-	in choosing equilibrium abundances that reflect a realistic metallicity 
-	gradient, it is in good agreement with~\citet{Schoenrich2009} and 
-	\citet{Nidever2014}.
+	from radial migration. Though this wouldn't occur without radial migration, 
+	our models by construction predict an ISM which spends most of its time 
+	near the equilibrium abundance along the low-$\alpha$ sequence with a 
+	built-in metallicity gradient. For this reason, it's only natural that our 
+	models predict this to be the case, although nonetheless it is in good 
+	agreement with~\citet{Schoenrich2009} and~\citet{Nidever2014}.
 
@@
 	\end{itemize} 
+\end{itemize}
+
+\subsection{Abundance Gradients} 
+\label{sec:comp_obs:metallicity_gradient}
+
+\begin{itemize}
 
@@
 	predicted by our fiducial, inside-out SFH assuming diffusion migration 
-	(sudden) versus post-processing (dotted) for the gas-phase of a handful of 
-	radii denoted by the legend. Predicted [O/Fe]-[Fe/H] tracks for the 
-	diffusion model show significant deviations from the post-processing 
+	(solid lines) versus post-processing (dotted lines) for the gas-phase of a 
+	handful of radii denoted by the legend. Predicted [O/Fe]-[Fe/H] tracks for 
+	the diffusion model show significant deviations from the post-processing 
 	model. We demonstrate here that this is due to variability in the SN Ia 
 	rate induced by the time-dependent radial migration of the diffusion 
-	model. Simulation times of 2, 4, 6, 8, 10, and 12.7 Gyr shown in points 
+	model. Simulation times of 2, 4, 6, 8, 10, and 12.2 Gyr shown in points 
 	and X's for the two models.
@@
 
-		\item The time-derivative of the mass of Fe in a given annulus is 
-		given by: 
-		\begin{equation}
-		\dot{M}_\text{Fe} \approx y_\text{Fe}^\text{CC}\dot{M}_\star + 
-		y_\text{Fe}^\text{Ia}\langle\dot{M}_\star\rangle_\text{Ia} - 
-		\frac{M_\text{Fe}}{M_g}\dot{M}_\star(1 + \eta(R_\text{gal}) - r) 
-		\end{equation} 
-		where this is an approximation because in detail, there is a small 
-		contribution from AGB stars, and the recycling in the simulation is 
-		done continuously, whereas here we simply take $r \approx$ 0.4 
-		(appropriate for a~\citetalias{Kroupa2001} IMF; 
-		\citealp{Weinberg2017}). This equation can be derived from the 
-		\citet{Weinberg2017} analytic models assuming CCSN and SN Ia 
-		enrichment for Fe with instantaneous recycling of previously produced 
-		Fe.~\texttt{VICE}'s science documentation could also be referenced 
-		here; it has a nice detailed section on its treatment of each term in 
-		handling enrichment rates \footnote{
-			\url{https://vice-astro.readthedocs.io/en/latest/science_documentation/enrichment/index.html}
-		}. 
-		Rearranging this for the term describing the rate of injection due to 
-		SNe Ia events, and normalizing by $M_\text{Fe}$ yields the following 
-		proxy with units of frequency: 
-		\begin{equation} 
-		\frac{
-			y_\text{Fe}^\text{Ia}\langle\dot{M}_\star\rangle_\text{Ia}
-		}{
-			M_\text{Fe} 
-		} \approx 
-		\frac{\dot{M}_\text{Fe}}{M_\text{Fe}} - y_\text{Fe}^\text{CC}\frac{
-			\dot{M}_\star 
-		}{
-			M_\text{Fe} 
-		} + \frac{\dot{M}_\star}{M_g}(1 + \eta(R_\text{gal}) - r) 
-		\label{eq:ia_rate_proxy} 
-		\end{equation} 
-		This term on the left-hand side can be substituted with 
-		$m_\text{Fe}^\text{Ia}\dot{N}_\text{Ia}/M_\text{Fe}$, where 
-		$m_\text{Fe}^\text{Ia}$ is the average mass of Fe produced by a single 
-		SN Ia event, and $\dot{N}_\text{Ia}$ is the SN Ia rate itself. For 
-		this reason, this equation constitutes a straight-forward proxy for 
-		the SN Ia rate at any given time.
+		\item From the~\texttt{VICE} outputs of our models, we extract a 
+		proxy for the SN Ia rate by isolating the contribution from SNe Ia to 
+		the time derivative of the Fe mass. The total time derivative can be 
+		obtained by the difference in Fe mass across two timesteps; then 
+		subtracting the contribution from CCSNe and approximately correcting 
+		for recycling yields an estimate of~$\dot{M}_\text{Fe}^\text{Ia}$.
 
@@
 		supernova rates at large radii than small radii.
+
+		\item Fluctuations in the SN Ia rate at these amplitudes can be 
+		understood through a comparison of the timescales associated with 
+		orbital migration and SN Ia event delays. In the top panels of Fig. 
+		\ref{fig:h277_decomposition}, we note that the distribution of 
+		$R_\text{Final}$ is significantly more peaked in the 0 - 2 Gyr age bin 
+		than for older stars. Despite this, the value of the PDF in all radial 
+		bins implies~$\sim$40-50\% of~\texttt{h277} star particles migrated 
+		significantly beyond their birth radius by the time they were 2 Gyr 
+		old. Though we adopt a different form in detail here, the SN Ia DTD is 
+		to order of magnitude a $t^{-1}$ power-law with a minimum delay of 
+		$\sim$100 Myr~\citep{Maoz2012, Maoz2017}. With this DTD, there are the 
+		same number of SN Ia events with delay-times between 100 Myr and 1 Gyr 
+		as between 1 Gyr and 10 Gyr. Combining these two pieces of information 
+		would suggest that a significant fraction of SN Ia progenitors migrate 
+		significantly beyond their birth radius. That is, while radial 
+		migration is often described as a slow process, so is the SN Ia DTD due 
+		to its long tail. With this realization, variability in the SN Ia rate 
+		at the levels seen in our models is not surprising. 
 	\end{itemize}
@@
 	yields can occur alongside stellar migration for delayed sources. In 
+	general, the characteristic delay-time for SN Ia events is~$\sim$1 Gyr, and 
+	stellar migration is proceeding on similar timescales in our models. In 
 	principle, it is reasonable to expect similar effects for s-process 
 	elements like carbon, nitrogen, strontium, yttrium, zirconium, etc. which 
-	are produced in AGB stars, though we do not investigate the impact for 
-	these elements here.
-
-	\item In the literature, it's not uncommon to adopt tracks for different 
-	Galactocentric radii in the [O/Fe]-[Fe/H] plane to infer birth radii for 
-	observed stars. While an additional dimension such as age could mitigate 
-	these potential issues, we caution against inferring birth radii in this 
-	manner, because the tracks themselves appear to be sensitive to the 
-	dynamical history of the Galaxy. Based on the left-hand panel of Fig. 
-	\ref{fig:tracks}, this effect could bias the inferred radii by many kpc. 
-	This however doesn't appear to be an issue for the low-$\alpha$ sequence, 
-	where the width of the [Fe/H] distribution appears to come from migration 
-	itself, as it did in~\citet{Schoenrich2009} and~\citet{Nidever2014}. 
-	We therefore recommend that such a technique be restricted to 
-	[O/Fe]~$\lesssim$+0.1 stars.
-
-	\item Demonstrate in~\S~\ref{sec:age_alpha:migration} that this is a means 
+	are produced in AGB stars and thus have similar characteristic delay-times, 
+	though we do not investigate the impact for these elements here.
+
+	\item What we really learn from this investigation is that when stellar 
+	migration is taken into account, tracks are not simple functions. To first 
+	order, they are characterized by the late-time equilibrium abundance and 
+	the value of~$\tau_\star$ setting the position of the ``knee'' 
+	\citep{Weinberg2017}, though migration causes noticeable variations,
+
+	\item Demonstrate in~\S~\ref{sec:comp_obs:age_alpha} that this is a means 
 	with which to form $\alpha$-rich and $\alpha$-poor stars - or rather 
@@
 
-\section{Metallicity Gradient} 
-\label{sec:metallicity_gradient}
-
+% fig 9 
 \begin{figure*} 
@@
 right). We plot the gas phase abundance at the present day as a function of 
-Galactocentric radius in solid lines. Stars denote the mode of the stellar 
-MDF of the 100-pc width annulus at a given radius, with shaded regions 
-marking the 16th and 84th percentiles thereof. Black lines in the top panels 
-denote our target [$\alpha$/H] gradient of mode([$\alpha$/H]) = +0.3 at 
-$R_\text{gal}$ = 4 kpc with a slope of -0.08 kpc$^{-1}$. } 
+Galactocentric radius in solid lines. Stars denote the median of the stellar 
+MDF of the 100-pc width annulus at a given radius, with shaded regions marking 
+the 16th and 84th percentiles thereof. Black lines in the top panels denote our 
+target [$\alpha$/H] gradient of mode([$\alpha$/H]) = +0.3 at~$R_\text{gal}$ = 
+4 kpc with a slope of -0.08 kpc$^{-1}$. 
+} 
 \label{fig:metallicity_gradient} 
@@
 \begin{itemize} 
-	\item Scaling of $\eta$ with $R_\text{gal}$ based on reproducing the 
-	observed mode([$\alpha$/H])-$R_\text{gal}$ trend, neglecting radial 
-	migration (see~\S~\ref{sec:methods:yields}). The target gradient is 
-	shown in a solid black line in the top panels of Fig. 
-	\ref{fig:metallicity_gradient}.
-
-	\item In the top panels, red and blue stars show the mode O and Fe 
-	abundances in each annulus, and the shaded region shows the 16th and 
-	84th percentiles of the MDF in that zone. Solid lines show the gas-phase 
-	abundance gradient at the present day. Bottom panels show the same thing 
-	for [O/Fe].
+	\item The top row of Fig.~\ref{fig:metallicity_gradient} shows the radial 
+	[O/H] and [Fe/H] gradients, with the [O/Fe] gradient in the bottom row. In 
+	all panels, stars show the median abundance in each annulus, and the shaded 
+	regions denote the 16th and 84th percentiles of the MDF in that zone. Solid 
+	lines show the gas-phase gradient at the present day. Although we built the 
+	abundance gradient into our models based on the mode abundance at a given 
+	radius, we illustrate the gradients here according to the median. We find 
+	that with annuli as narrow as~$\Delta R_\text{gal}$ = 100 pc, the mode is a 
+	sufficiently noisy statistic to introduce noticeably more scatter in this 
+	relation. Nonetheless, we have verified that it follows the trend implied 
+	by our target gradient (see~\S~\ref{sec:methods:yields}), illustrated by 
+	the solid black line in the top panels. We note that the median gradient 
+	follows a slightly shallower trend that the mode, which is expected when 
+	the metallicity distribution is skew-negative in the inner Galaxy and 
+	skew-positive in the outer Galaxy.
 
@@
 	in the inner galaxy for both O and Fe. $\alpha$-enhanced tail there as 
-	well. We demonstrate in~\S~\ref{sec:metallicity_gradient} that the MDF 
-	does shift to skew-positive in the outer galaxy, though this isn't as 
+	well. We demonstrate in~\S~\ref{sec:comp_obs:metallicity_gradient} that the 
+	MDF does shift to skew-positive in the outer galaxy, though this isn't as 
 	visually obvious from this plot due to the scatter in the mode at these 
-	radii.
-
-	\item Details of the [O/Fe] gradient seem to be sensitive to differences 
-	in our SFHs, especially in the inner galaxy.
-
-	\item Constant SFH is the only model in which the present-day gas phase 
-	gradient matches the stellar gradient at all radii. In remaining models, 
-	the present-day gas-phase abundance is above the majority of the stars 
-	because the star formation rate has decreased. We therefore expect 
-	observational studies of abundance gradients to differ noticeably between 
-	gas and stars.
+	radii. We investigate the MDFs at different radii in detail in 
+	\S~\ref{sec:comp_obs:mdfs}.
+
+	\item All models predict the [O/Fe] gradient to be relatively flat 
+	throughout the disk, steepening only in the inner~$\sim$few kpc and beyond 
+	15.5 kpc, where we shut off star formation. The trend in our predicted 
+	abundances toward higher [$\alpha$/Fe] at large~$R_\text{gal}$ is expected 
+	for this reason; all stellar populations currently at~$R_\text{gal}$ > 15.5 
+	kpc formed in the disc and migrated there. Only the stars old enough to 
+	migrate to such radii will be located there at the present day, and since 
+	these stars are old, they're also~$\alpha$-enhanced. This is consistent 
+	with the findings of~\citet{RadburnSmith2012}, who argue that the outskirts 
+	of the NGC 7793 disc formed largely out of radial migration of stars.
+
+	\item We note that there are differences between the stellar and gas-phase 
+	gradients in all models. We therefore argue that it'd be reasonable to 
+	expect differences in reported slopes and normalizations of the gradient 
+	in observational studies, particularly in the inner Galaxy.
 
@@
 
-\section{Metallicity Distribution Functions} 
-\label{sec:mdfs}
-
-\subsection{[O/H] and [Fe/H]} 
-\label{sec:mdfs:oh_feh}
+\subsection{Metallicity Distribution Functions} 
+\label{sec:comp_obs:mdfs}
 
@@
 
+% fig 10 
 \begin{figure} 
@@
 \caption{Metallicity Distribution Functions in [Fe/H] predicted by our 
-late-burst model (left) and as observed in APOGEE DR16 (right), for stars and 
+fiducial model (left) and as observed in APOGEE DR16 (right), for stars and 
 simulated stellar populations with present day $\left|z\right|$ = 0 - 0.5 kpc 
@@
 
+% fig 11 
 \begin{figure} 
@@
 
+% fig 12 
 \begin{figure*} 
 \centering 
-\includegraphics[scale = 0.32]{ofe_mdfs_insideout.pdf} 
+\includegraphics[scale = 0.32]{ofe_mdfs.pdf} 
 \caption{Predicted distributions in [O/Fe] in 15 Galactic regions and in two 
@@
 [Fe/H] the sample is drawn from, denoted by the legend in the upper right 
-panel. Solid lines represent that predicted by our inside-out SFH, while 
-dashed lines correspond the fits to the APOGEE DR16 data presented in Vincenzo 
-et al. (2021, in prep), which quantify the intrinsic distributions accounting 
-for observational uncertainties and the APOGEE selection function. Our 
-simulated distributions are smoothed with a box-car width of [O/Fe]~$\pm$~0.02 
-to improve clarity. }
+panel. Solid lines represent that predicted by our inside-out SFH in 
+$\Delta$[O/Fe] = 0.04 bins, while dashed lines correspond the fits to the 
+APOGEE DR16 data presented in \citet{Vincenzo2021}, which quantify the 
+intrinsic distributions accounting for observational uncertainties and the 
+APOGEE selection function. }
 \label{fig:ofe_mdfs_insideout} 
@@
 		\item Similar mode [O/H] and [Fe/H] between the 3 - 5 and 5 - 7 kpc 
-		in the APOGEE observations. What could be the origin of this? 
-		Cessation of star formation in the inner Galaxy? (see Fig. 1 of 
-		\citealp{Peek2009} and Fig. 2 of~\citealp{Fraternali2012}). This 
-		would imply very few stars formed in the most metal-rich regions of 
-		the Galaxy, cutting off the MDF at high [O/H], [Fe/H]. This would 
-		suggest that the Milky Way has begun the quenching of star formation, 
-		a process believed to begin the centres of galaxies at this mass 
-		\citep[e.g.][]{Ellison2020a}. 
+		in the APOGEE observations. What could be the origin of this? One 
+		possibility is that our formalism for~$\eta(R_\text{gal})$ is 
+		incorrect. We would expect a both a flat [X/H] gradient and MDFs with 
+		similar modes if we simply chose it to be so by letting $\eta$ be 
+		constant in the inner galaxy. Another possibility is the cessation of 
+		star formation in the inner Galaxy (see Fig. 1 of~\citealp{Peek2009} 
+		and Fig. 2 of~\citealp{Fraternali2012}), an effect which also isn't 
+		included in our models. If the Milky Way has begun quenching, a process 
+		believed to begin in the centres of galaxies at this mass 
+		\citep[e.g.][]{Ellison2020b}, then few stars would form in the most 
+		metal-rich regions, cutting off the MDF at high [O/H] and [Fe/H]. 
 	\end{itemize}
@@
 	with observations.
-	\begin{itemize} 
-		\item Could this point to a breakdown of our assumption that vertical 
-		mixing is efficient? 
-	\end{itemize}
 
@@
 	moderately lower than the target, but this is due to the effect of 
-	dilution (see discussion in~\S~\ref{sec:amr}). In our inside-out and 
-	outer-burst models, the difference in target and predicted mode [X/H] is 
-	considerably smaller. 
-\end{itemize}
-
-\subsection{[O/Fe]} 
-\label{sec:mdfs:ofe}
+	dilution (see discussion in~\S~\ref{sec:comp_obs:amr}). In our inside-out 
+	and outer-burst models, the difference in target and predicted mode [X/H] 
+	is considerably smaller. 
+\end{itemize}
+
+\subsection{[O/Fe] Distributions in Bins of [Fe/H]} 
+\label{sec:comp_obs:mdfs:ofe}
 
@@
 	\item In this section we compare our model predicted [O/Fe] distributions 
-	to those published in Vincenzo et al. (2021, in prep). These are intended 
+	to those published in~\citet{Vincenzo2021}. These are intended 
 	to simultaneously remove the effects of observational errors in [O/Fe] 
 	and the APOGEE selection function in these Galactic regions; that is, 
-	these are estimates of the~\textit{intrinsice} [O/Fe] distributions that, 
+	these are estimates of the~\textit{intrinsic} [O/Fe] distributions that, 
 	when convolved with observational uncertainties and the APOGEE selection 
@@
 	two bins of [Fe/H] across 15 Galactic regions predicted by our inside-out 
-	SFH (solid lines). Dashed lines show the Vincenzo et al. (2021, in prep) 
-	distributions.
-
-	\item At fixed~$R_\text{gal}$ and [Fe/H], the Vincenzo et al. (2021, 
-	in prep) MDFs show two peaks in the distribution which do not change with 
-	$\left|z\right|$; only their relative heights vary. This is an assumption 
-	built into the model, but the agreement with the APOGEE data is good. 
-	At small~$R_\text{gal}$, the observed distributions may shift slightly to 
-	higher [Mg/Fe], but only at the~$\lesssim$0.05 level between 
-	$\left|z\right|\leq$~0.5 and 1~$\leq\left|z\right|\leq$~2.0 (see their Fig. 
-	X). In contrast, our model predicted distributions show an increase in the 
-	mode [O/Fe] of~$\sim$~0.1 over the same dynamic range in~$\left|z\right|$. 
-	This suggests that our model overpredicts the increase of [O/Fe] with 
-	increasing~$\left|z\right|$ compared to the APOGEE distributions. 
-	{\color{red} As of now, I don't have a good explanation for why this is 
-	the case. Maybe the fact that we see this at small~$R_\text{gal}$ suggests 
-	the evolution of the bulge may have something to do with it? We're not 
-	modeling that here.}
-
-	\item We note that the inside-out model fails to reproduce a Milky 
-	Way-like bimodality. Such a model prediction would appear as good 
-	agreement between the solid and dashed lines in Fig. 
-	\ref{fig:ofe_mdfs_insideout}, but that is not the case. There may be 
-	decent agreement in a given metallicity bin and Galactic region, but the 
-	agreement would need to be seen everywhere and at all metallicities.
+	SFH (solid lines). Dashed lines show the~\citet{Vincenzo2021} distributions.
+
+	\item We note that our model adequately reproduces the broad nature of the 
+	[O/Fe] distributions at fixed [Fe/H] seen in the APOGEE data. A number of 
+	distributions show a bimodality in decent agreement with the observations 
+	(e.g. the -0.4~$\leq$ [Fe/H]~$\leq$ -0.2 bin at~$R_\text{gal}$ = 3 - 5 kpc 
+	and~$\left|z\right|\leq$ 0.5 kpc), but this is not true of all Galactic 
+	regions in both metallicity bins. Instead, the the principle failure of a 
+	number of these distributions is that they overpredict the number of 
+	intermediate [O/Fe] stars. While our model is successful in some ways with 
+	regards to reproducing these distributions, it fails to describe the 
+	observations in detail in this way.
 
@@
 	\begin{itemize} 
-		\item Since these are in specific bins in [Fe/H], this is an 
-		indication that our model is overpredicting the O abundances of these 
-		stars, rather than underpredicting [Fe/H].
-
-		\item This could point to various things. Perhaps the Milky Way has 
-		different gradients in [O/H] than [Fe/H], an effect which is not 
-		captured by these models. Perhaps the innermost radii of the Milky 
-		Way has some contamination from bulge stars, another effect which is 
-		not captured by our models. Impact of bar evolution maybe? 
+		\item At fixed~$R_\text{gal}$ and [Fe/H], the Vincenzo et al. (2021, 
+		in prep) MDFs show two peaks in the distribution which do not change 
+		with~$\left|z\right|$; only their relative heights vary. This is an 
+		assumption built into the model, but the agreement with the APOGEE data 
+		is good. At small~$R_\text{gal}$, the observed distributions may shift 
+		slightly to higher [Mg/Fe], but only at the~$\lesssim$0.05 level 
+		between~$\left|z\right|\leq$~0.5 and 1~$\leq\left|z\right|\leq$~2.0 
+		(see their Fig. X). In contrast, our model predicted distributions show 
+		an increase in the mode [O/Fe] of~$\sim$~0.1 over the same dynamic 
+		range in~$\left|z\right|$. This suggests that our model overpredicts 
+		the increase of [O/Fe] with increasing~$\left|z\right|$ compared to the 
+		APOGEE distributions.
+
+		\item Small~$R_\text{gal}$ and high~$\left|z\right|$ is a Galactic 
+		region where the APOGEE data are few, and the stellar number density is 
+		high, so it's possible the observations aren't well characterized. 
+		Indeed, in the~$R_\text{gal}$ = 3 - 5 and 5 - 7 kpc bins at 
+		$\left|z\right|$ = 1 - 2 kpc, the~\citet{Vincenzo2021} model 
+		is fit to 31 and 17 stars, respectively. In comparison, there are 109 
+		in the solar annulus, and all other bins have >75 stars in the fit.
+
+		\item If this discrepancy persists in subsequent APOGEE data releases, 
+		it's possible the origin is tied to the Sagittarius dwarf. The 
+		\texttt{h277} simulation had a major merger at a lookback time of 
+		$\sim$10 Gyr, and another close to the present day ({\color{red} verify 
+		this, and provide citation}), different timing than the pericentric 
+		passages of the Sagittarius dwarf~\citep{RuizLara2020}. More 
+		pericentric passages of a massive satellite could kinematically 
+		heat low-[$\alpha$/Fe] disc stars to higher~$\left|z\right|_\text{max}$ 
+		orbits, shifting these distributions to lower [O/Fe]. {\color{red} This 
+		is another instance where running these models with a different 
+		hydro-sim's star particles could be enlightening. }
+
+		\item Another possibility: details of the dynamical history? Could 
+		bar evolution have something to do with it? Again, a different 
+		dynamical history via another hydro-sim would be enlightening. 
 	\end{itemize}
@@
 	\begin{itemize} 
-		\item If the bimodality is to arise out of inside-out galaxy 
-		evolution and radial migration alone, the transition between low- and 
+		\item If the bimodality is to arise out of inside-out Galaxy evolution 
+		and radial migration alone, the transition between low- and 
 		high-$\alpha$ sequences needs to occur faster than it does in these 
-		models. Applying the analytic model of~\citet{Weinberg2017}, this can 
-		be occur only with an adequately short~$\tau_\star$. Here we have 
-		adopted a star formation law which is motivated by observations (see 
-		discussion in~\S~\ref{sec:methods:sfe}); this suggests that the 
-		observed rates of star formation are not conducive to an adequately 
-		short transition between the two sequences such as to predict the 
-		dichotomy in the models as it is observed in the Milky Way.
+		models. The analytic models of~\citet{Weinberg2017} suggest that the 
+		approach to chemical equilibrium occurs on the order of the SFE 
+		timescale~$\tau_\star$. Although we've adopted a star formation law 
+		which is motivated by observational results (see discussion in~\S 
+		\ref{sec:methods:sfe}), the failure of these models to reproduce the 
+		observed results suggests that inside-out Galaxy growth with such a 
+		star formation law is not conducive to forming the infamous 
+		dichotomy.
 
@@
 		Chiappini2001, Romano2010, Grisoni2017, Noguchi2018, Spitoni2016, 
-		Spitoni2018, Spitoni2019, Spitoni2020} would improve the 
+		Spitoni2018, Spitoni2019, Spitoni2020, Spitoni2021} would improve the 
 		agreement between our model predictions and the observed 
 		distributions. 
-
-		\item Alternatively, there is observational evidence for a SN Ia Fe 
-		yield which scales inversely with metallicity (see discussion of 
-		\citealp{Brown2019} in~\S~\ref{sec:methods:yields}). If this is the 
-		case, the decrease in [O/Fe] ratios at low [Fe/H] at the onset of 
-		the first SN Ia events may occur faster than in our models. This may 
-		predict the observed bimodality by ensuring that the transition 
-		between high- and low-$\alpha$ sequences is naturally fast due to 
-		supernova rates. 
-	\end{itemize}
-
-	\item This is at 
-	odds with the findings of~\citet{Sharma2020}, who claim to reproduce the 
-	[$\alpha$/Fe] dichotomy with an analytic chemical evolution model with 
-	an inside-out SFH and stellar migration. 
-	\begin{itemize} 
-		\item {\color{red} We'll need to be careful in our final draft of the 
-		paper so that our language here isn't too strong. Below I've given my 
-		honest critiques of the~\citet{Sharma2020} paper. }
-
-		\item They assume parameterized forms for [Fe/H] and [$\alpha$/Fe] as 
-		functions of radius and time, chosen deliberately so 
-		that they agree with the observed data. Based on dynamical arguments 
-		similar to those in~\citet{Schoenrich2009}, their migration model has 
-		free parameters which then require fitting to observed data. Since the 
-		observed data is known to exhibit the dichotomy, their model's 
-		reproduction of the observed dichotomy is not a prediction but rather 
-		an assumption characterized a priori. For this reason, rather than 
-		learning about the physical origins of the [$\alpha$/Fe] dichotomy 
-		from~\citet{Sharma2020}, we instead get a robust mathematical 
-		characterization of the data.
-
-		\item They find a dichotomy in the [$\alpha$/Fe]-[Fe/H] plane to 
-		arise out of a fast transition in the gas phase between high-$\alpha$ 
-		and low-$\alpha$. As we discussed here, we find in practice that this 
-		is only the case if~$\tau_\star$ is sufficiently short, and our 
-		observationally motivated scaling would suggest that the required 
-		values are unphysically short ($\lesssim$1 Gyr; we find that our 
-		$\tau_{\star,0}$ = 1 Gyr model also fails to reproduce an adequaately 
-		fast transition).
-
-		\item We therefore argue that the claim of~\citet{Sharma2020} that 
-		the observed dichotomy can arise purely out of inside-out galaxy 
-		formation with radial migration is likely contingent upon SN Ia rates 
-		scaling inversely with metallicity, as suggested by the findings of 
-		\citet{Brown2019}. Under the parameters of our inside-out SFH model, 
-		this is the only physically realistic means with which the predicted 
-		transition between high- and low-$\alpha$ is adequately fast. 
-	\end{itemize}
-
-	\item These findings suggest that an inside-out SFH combined with radial 
-	migration, even when a late starburst is taken into account (as motivated 
-	by the findings of~\citealp{Isern2019} and~\citealp{Mor2019}), 
-	is~\textit{not} conducive to producing the observed [$\alpha$/Fe] 
-	dichotomy. This suggests that more dramatic evolutionary events are 
-	likely responsible, such as a two-infall model 
-	\citep[e.g.][]{Chiappini1997, Chiappini2001, Romano2010, Grisoni2017, 
-	Noguchi2018, Spitoni2016, Spitoni2018, Spitoni2019, Spitoni2020}. 
-\end{itemize}
-
-\section{The Age-[$\alpha$/Fe] Relation} 
-\label{sec:age_alpha}
-
+	\end{itemize}
+
+\end{itemize}
+
+\subsection{The Age-[$\alpha$/Fe] Relation} 
+\label{sec:comp_obs:age_alpha}
+
+% fig 13 
 \begin{figure*} 
@@
 of our constant (upper left), inside-out (upper right), late-burst (lower 
-left), and outer-burst (lower-right) SFHs. 
+left), and outer-burst (lower-right) SFHs, assuming diffusion migration. 
 In all panels, red triangles and error bars denote the observed mean age and 
@@
 
+% fig 14 
 \begin{figure*} 
@@
 Fig.~\ref{fig:age_alpha} for the corresponding Galactic 
-region. 
+region. The solid black line connects the black squares in the bottom, 
+left-middle panel, and is replicated in elsewhere for reference. 
 } 
@@
 	have Gaia parallax measurements available~\citep[][for details on the 
-	APOGEE survey, see discussion in~\S~\ref{sec:mdfs}]{Abolfathi2014, 
+	APOGEE survey, see discussion in~\S~\ref{sec:comp_obs:mdfs}]{Abolfathi2014, 
 	GaiaDR2}. With their spatial and quality cuts, the final sample consisted 
@@
 
-	\item In bins of [O/Fe], they assume a gaussian age distribution, and fit 
-	the mean and standard deviation to the observed sample. Because they 
+	\item In bins of [O/Fe], they assume a gaussian log-age distribution, and 
+	fit the mean and standard deviation to the observed sample. Because they 
 	assume a gaussian, they would report an equal mean and median. This is an 
@@
 	well, as that's relevant information.}
-\end{itemize}
-
-\subsection{The Impact of Radial Migration} 
-\label{sec:age_alpha:migration} 
-\begin{itemize} 
+
 	\item Fig.~\ref{fig:age_alpha} shows a comparison 
@@
 	in the SN Ia rates induced by time-dependent migration (see discussion in 
-	\S~\ref{sec:metallicity_space}). Further demonstration that under 
+	\S~\ref{sec:comp_obs}). Further demonstration that under 
 	certain migration models, the radial migration of nucleosynthetic yields 
@@
 	order one depletion time, the ISM will be either Fe-poor or Fe-rich, and 
-	the stars that form there will inherit that composition.\footnote{
-		{\color{red} Potentially note the~\citet{Weinberg2017} definition: 
-		$\tau_\text{dep} \equiv \tau_\star/(1 + \eta - r)$. Even with 
-		$\tau_\star$ as high as~$\sim$5 Gyr at large Galactocentric radii, 
-		depletion times are still short due to the high values of $\eta$ 
-		there.}
-	} The stars that form out of that patch of ISM can then migrate to the 
-	solar annulus. This effect is most significant at large Galactocentric 
-	radii where the fractional amplitude of the variability in the SN Ia rate 
-	is largest, and for that reason the young Fe-poor population predicted by 
-	our diffusion model originates at large radii ($\gtrsim$ 12 kpc).
+	the stars that form there will inherit that composition. The stars that 
+	form out of that patch of ISM can then migrate to the solar annulus. This 
+	effect is most significant at large Galactocentric radii where the 
+	fractional amplitude of the variability in the SN Ia rate is largest, and 
+	for that reason the young Fe-poor population predicted by our diffusion 
+	model originates at large radii ($\gtrsim$ 12 kpc).
 
@@
 	result of stellar mergers or mass transfer events, producing a population 
-	of truly old stars masquerading as young stars. This would imply that the 
-	observed young $\alpha$-rich population is actually just older, 
-	high-$\alpha$ stars that have gone through some special class of stellar 
-	evolution. Our model predicts intrinsically young, Fe-poor stars to 
-	explain the observations, but these interpretations are not mutually 
-	exclusive. It's possible that some of the observed stars are truly young, 
-	Fe-poor stars, and that others underwent some stellar interaction event. 
-	Ascertaining the origins of this population therefore has implications for 
-	which of the migration models investigated here is the most realistic. 
-\end{itemize}
-
-\subsection{The Impact of the Star Formation SFH} 
-\label{sec:age_alpha:sfh} 
-\begin{itemize} 
+	of truly old stars masquerading as young stars. In a sample of 51 of these 
+	stars on the red giant branch,~\citet{Hekker2019} demonstrate that a 
+	portion of these stars have carbon-to-nitrogen ratios consistent with 
+	mass transfer events, but that others do not, indicating that either 
+	they're truly young stars or the results of mergers on the main sequence. 
+	Our model's prediction of intrinsically young, high [O/Fe] stars is 
+	independent of this mass transfer scenario;~\texttt{VICE} does not include 
+	any statistical treatment of mass transfer events. Ascertaining the origins 
+	of this population therefore has implications for which of the migration 
+	models investigated here is the most realistic.
+
 	\item Fig.~\ref{fig:age_alpha} shows a comparison between 
@@
 	follow a slightly steeper age-[$\alpha$/Fe] than our inside-out model 
-	predicts. This likely points to inaccuracies in the detailed form of the 
-	SFH or the SN Ia DTD, both of which are very plausible. 
-\end{itemize}
-
-\subsection{Beyond the Solar Annulus} 
-\label{sec:age_alpha:beyond_solar_annulus} 
-\begin{itemize} 
+	predicts. This could point to inaccuracies in the detailed form of the SFH 
+	or the SN Ia DTD, our supernova yields, or observational [O/Fe] errors, all 
+	of which are very plausible.
+
 	\item Fig.~\ref{fig:age_alpha_regions} presents a comparison of our 
@@
 
-	\item Differences in ages are interesting though - nearly everywhere we 
-	overpredict ages relative to~\citet{Feuillet2019}, their data are 
-	reasonably described by the stellar populations from our simulations that 
-	we would classify as Fe-poor (see discussion in~\S 
-	\ref{sec:age_alpha:migration}). Especially noticeable in the
-	$R_\text{gal}$ = 5 - 7 kpc, where the observed sample agrees nearly 
-	perfectly with one particular Fe-poor population in the 
-	$\left|z\right|\leq$~0.5 kpc and 0.5~$\leq\left|z\right|\leq$~1.0 kpc 
-	regions. In the~$\left|z\right|\leq$ 0.5 kpc population, the observed 
-	data even show an abrupt increase in age near the maximum [O/Fe] ratio of 
-	this particular subset of our stellar populations, and have one data point 
-	that agrees with the population-averaged trend in our simulation. 
-	\begin{itemize} 
-		\item Taking the~\citet{Feuillet2019} data at face value, this would 
-		suggest that our simulation is overpredicting the rate of Fe injection 
-		from SN Ia, implying a SN Ia DTD whose characteristic timescales are 
-		longer than we employ here, thus slowing the decrease of [$\alpha$/Fe] 
-		with time.
-
-		\item Taking the simulation results at face value, this would suggest 
-		that APOGEE+Gaia target selection favors the stars we would classify 
-		as Fe-poor.
-
-		\item This is another instance where a two-infall model would help 
-		improve the fit, however~\citep[e.g.][]{Chiappini1997, Chiappini2001, 
-		Romano2010, Grisoni2017, Noguchi2018, Spitoni2016, Spitoni2018, 
-		Spitoni2019, Spitoni2020}. Through a perturbation of 
-		the ratio of CCSN to SN Ia rates~\citep[e.g.][]{Johnson2020}, the 
-		model would predict an increase in [$\alpha$/Fe] at ages of 
-		$\sim$8 - 10 Gyr following the formation of the high-$\alpha$ 
-		sequence, decreasing toward younger ages. Although this would worsen 
-		the agreement in the solar annulus, it would improve it in other 
-		Galactic regions. 
-	\end{itemize}
+	\item \citet{Feuillet2019} report ages for~$\alpha$-rich stars that are 
+	younger at large~$R_\text{gal}$ and high~$\left|z\right|$, though in most 
+	cases only by~$\sim$20\%. Our model, however, does not capture this effect. 
+	To illustrate this, we connect the black squares in the panel corresponding 
+	to the solar annulus with a solid black line, and reproduce this line in 
+	all panels as a reference. If the observational result is correct, this is 
+	an interesting result that our model doesn't reproduce in any of the 
+	variants we have examined.
 
@@
 	\begin{itemize} 
-		\item This is due to the variability in the SN Ia rates in each of 
-		our model's annuli that we described in~\S~\ref{sec:metallicity_space}. 
-		There, we demonstrated that the highest amplitude variability in the 
-		SN Ia rate in our model galaxy is in the outskirts of the disc. This 
-		arises out of time-dependent migration inducing a variability; this 
-		variability gets larger in our models in regions where the stellar 
-		number density is low.
-
-		\item With a higher variability in the SN Ia rate comes a higher 
-		variability in the rate of Fe production. Therefore, stars at large 
-		$R_\text{gal}$ form out of an ISM with an [O/Fe] ratio that is more 
-		variable, the observational signature of which is the intrinsic 
-		scatter in the age-[$\alpha$/Fe] relation growing with~$R_\text{gal}$. 
-	\end{itemize} 
-\end{itemize}
-
-\section{The Age-Metallicity Relation} 
-\label{sec:amr}
-
+		\item We identify two sources driving the increase in scatter at large 
+		$R_\text{gal}$. The bulk of the scatter, at least at [O/Fe] 
+		$\gtrsim$ +0.05, arises from the variability in SN Ia rates as 
+		described in~\S~\ref{sec:comp_obs:metallicity_gradient}. There, we 
+		demonstrated that the highest amplitude variability in the SN Ia rate 
+		in our model Galaxy occurs in the outskirts of the disc where the 
+		stellar number density is low. With higher variability in the SN Ia 
+		rate comes a higher variability in the gas-phase [O/Fe] ratio, 
+		resulting in an in-situ population whose age-[O/Fe] relation shows more 
+		intrinsic scatter compared to that at small radii. The second source is 
+		the change in normalization of the age-[O/Fe] relation expected for 
+		different star formation timescales. With decreasing~$\tau_\text{sfh}$, 
+		the age-[O/Fe] relation becomes shallower due to the delayed SN Ia 
+		enrichment channel depositing Fe into a depleted gas reservoir 
+		\citep{Weinberg2017}. This, coupled with the fact that the relation is 
+		intrinsically shallow at young ages, produces noticeable scatter near 
+		solar [O/Fe]. The comparison between the post-processing and diffusion 
+		migration models in Fig.~\ref{fig:age_alpha} makes this fairly clear. 
+	\end{itemize} 
+\end{itemize}
+
+\subsection{The Age-Metallicity Relation} 
+\label{sec:comp_obs:amr}
+
+% fig 15 
 \begin{figure} 
@@
 
+% fig 16 
 \begin{figure} 
@@
 but with our simulation prediction quantified in 0.05-dex bins in [O/H] and 
-[Fe/H]. For comparison, we plot the~\citet{Feuillet2018} data in a solid black 
+[Fe/H]. For comparison, we plot the~\citet{Feuillet2018} data in a dark red 
 line, omitting the associated uncertainties for the sake of clarity. } 
@@
 
+% fig 17 
 \begin{figure*} 
@@
 
-% \begin{figure*} 
-% \centering 
-% \includegraphics[scale = 0.32]{amr_lateburst_Fe.pdf} 
-% \caption{The age-[Fe/H] relation in 12 Galactic regions predicted by our 
-% late-burst SFH. Bins in Galactocentric radius are shown in columns, and 
-% labeled at the top. Bins in height~$\left|z\right|$ above/below the disc 
-% midplane are shown in rows, noted in the left-hand column. Red triangles, 
-% black squares, error bars, and background points are as in 
-% Fig.~\ref{fig:age_alpha} for the corresponding Galactic 
-% region, but with our simulated prediction quantified in 0.05-dex bins in 
-% [Fe/H]. } 
-% \label{fig:age_feh_regions} 
-% \end{figure*}
-
-\begin{itemize} 
-	\item Fig.~\ref{fig:age_oh_static} presents the age-[O/H] relation 
-	predicted by our constant-SFH model for the~$\left|z\right|\leq$ 0.5 kpc 
-	population at~$R_\text{gal}$ = 5 - 7, 7 - 9, 9 - 11, and 11 - 13 kpc. The 
-	black points quantify the same mass-weighted median age in bins of 
-	[O/H] as in~\S~\ref{sec:age_alpha}. Colored points in the background are 
-	also the same - individual stellar populations color-coded according to 
-	birth radius.
-
-	\item \citet{Feuillet2019} argued using the~\citet{Weinberg2017} analytic 
-	models of chemical evolution that the non-monotonicity of the observed 
-	AMR was due to radial migration. The youngest stars at a given radius 
-	should reflect recent abundances of the local ISM, since young stars could 
-	not have migrated significant distances. Old stars, however, could have 
-	migrated from a wide range of radii, and can therefore reflect a wide 
-	range of abundances.
+\begin{itemize} 
+	\item Although the age-metallicity relation (AMR) is usually formulated in 
+	age-[Fe/H], it is also interesting to look at age-[O/H] because it is not 
+	affected by SN Ia enrichment. The extent to which they differ indicates the 
+	extent to which the delayed timescale and impact of migration on SN Ia 
+	enrichment is important in shaping the age-[Fe/H] relation. Fig. 
+	\ref{fig:age_oh_static} presents the age-[O/H] relation predicted by our 
+	constant-SFH model for the~$\left|z\right|\leq$ 0.5 kpc population at 
+	$R_\text{gal}$ = 5 - 7, 7 - 9, 9 - 11, and 11 - 13 kpc. The black points 
+	quantify the same mass-weighted median age in bins of [O/H] as in~\S 
+	\ref{sec:comp_obs:age_alpha}. Colored points in the background are also the 
+	same - individual stellar populations color-coded according to birth 
+	radius. We choose the constant SFH model here because it is not subject to 
+	the effect of a time-varying SFH, as our fiducial inside-out SFH model is.
+
+	\item The intrinsic scatter in the observed AMR has been interpreted as 
+	evidence for radial mixing for some time~\citep[e.g.][]{Edvardsson1993}. 
+	\citet{Feuillet2018} found that most of the metal-rich stars in the solar 
+	neighborhood were older than solar metallicity stars. Using the 
+	\citet{Weinberg2017} analytic models of one-zone chemical evolution, they 
+	argue that this is the result of old stars born at small~$R_\text{gal}$ 
+	where the equilibrium abundance is high migrating to the solar 
+	neighborhood. The fact that only the old stars are seen in the solar 
+	annulus can then be explained by the slow nature of radial migration.
 
@@
 	color-coding of the background points makes it clear that this arises out 
-	of radial migration.
+	of radial migration. At any given radius, the youngest stars form with a 
+	composition reflective of the local ISM, which in our models, is in turn 
+	reflective of the late-time equilibrium abundance at that radius. Stars 
+	with significantly different compositions were born in different Galactic 
+	regions and underwent radial migration. 
+	\begin{itemize} 
+		\item An interesting implication of this effect arises in the outer 
+		Galaxy, visible in the~$R_\text{gal}$ = 11 - 13 kpc bin. There, the 
+		equilibrium abundance is low, and the model predicts that nearly all 
+		other regions of the Galaxy are forming stars at higher abundances. 
+		When migration is taken into account, the result is an AMR which is 
+		nearly monotonically~\textit{increasing} with age, entirely the 
+		opposite of what is predicted by one-zone models. 
+	\end{itemize}
 
@@
 	$\left|z\right|\leq$~0.5 kpc), under the same plotting convention as in 
-	\S~\ref{sec:age_alpha}. We add a solid black line to denote the 
+	\S~\ref{sec:comp_obs:age_alpha}. We add a solid black line to denote the 
 	\citet{Feuillet2018} AMR in comparison to that of~\citet{Feuillet2019}. 
@@
 			\item In our recent starburst models,~\texttt{VICE} calculates 
-			that there is a significant amount of zero metallicity gas infall 
+			that there is a significant amount of low metallicity gas infall 
 			required to sustain such an increase in star formation under our 
-			adopted~$\dot{\Sigma}_\star-\Sigma_\text{gas}$ relation (see 
+			adopted~$\dot{\Sigma}_\star-\Sigma_\text{g}$ relation (see 
 			bottom two panels of Fig.~\ref{fig:evol} and~\S~
@@
 		the AMR and the age-[$\alpha$/Fe] relation. This would require 
-		future studies which include a treatment of a multi-phase ISM. 
+		future studies which include a treatment of a multi-phase ISM. This 
+		would however be at odds with the findings of~\citet{Mor2019} and 
+		\citet{Isern2019}. 
 	\end{itemize}
@@
 	\item With our age-[O/H] and age-[Fe/H] relations, we find similar results 
-	as in~\S~\ref{sec:age_alpha:beyond_solar_annulus} whereby our model 
+	as in~\S~\ref{sec:comp_obs:age_alpha} whereby our model 
 	in general overpredicts the observed ages of stars at high 
 	$\left|z\right|$. Discussion of potential sources of this can be found 
-	in~\S~\ref{sec:age_alpha:beyond_solar_annulus}. 
+	in~\S~\ref{sec:comp_obs:age_alpha}. 
 \end{itemize}
@@
 	exchange of stellar populations between zones to model the impact of 
-	stellar migration on enrichment in the Galaxy. The resulting ``multi-zone'' 
-	is a technique that has received attention from only a handful of 
-	chemical evolution studies to date~\citep{Matteucci1989, 
-	Schoenrich2009, Minchev2013, Sharma2020}. In so doing, we adopted star 
-	particles from the~\texttt{h277} zoom-in, hydrodynamical simulation to 
-	describe the dynamical history of a Milky Way-like galaxy at face value. 
-	This yields a model for radial migration which does not have any free 
-	parameters (see discussion in~\S~\ref{sec:methods:h277}).
-
-	\item We found that similar numbers of star particles in~\texttt{h277} 
-	migrated inward as outward, and that the two proceed on different 
-	timescales, indicating that they're potentially linked to different 
-	physical processes. We found that distributions of birth radii in bins of 
-	final radii showing a mode which depends strongly on age is a 
-	consequence of the surface density gradient. It's not that stars in general 
-	migrate outward, it's simply that there are many many stars born at small 
-	radii presently at large radii due to the fact that there are so many more 
-	stars born at small radii, a consequence of the steep nature of the 
-	surface density gradient~\citep[e.g.][]{Bland-Hawthorn2016}.
-
-	\item We found that the e-folding timescales for star formation indicated 
-	by population averaged observations of Milky Way like galaxies are long 
-	($\sim$15 Gyr in the solar annulus;~\citealp{Sanchez2020}).
-
-	\item We find that through stellar migration our models naturally 
-	reproduce the observed result that high-$\alpha$ stars are more common at 
-	small~$R_\text{gal}$ and high-$\left|z\right|$, and the opposite for 
-	low-$\alpha$ stars (\citealp{Hayden2015}; see Fig. 
-	\ref{fig:ofe_feh_diagram} and associated discussion in~\S 
-	\ref{sec:metallicity_space}).
-
-	\item We demonstrate that the time-dependence of radial migration has a 
-	significant impact on the [O/Fe] ratios as a function of time and radius 
-	by inducing variability in the SN Ia rate and therefore the Fe abundance 
-	(see Fig.~\ref{fig:tracks} and the associated discussion in~\S 
-	\ref{sec:metallicity_space}). Although we haven't investigated it here, we 
-	expect similar arguements to extend to other delayed sources such as AGB 
-	stars and the associated s-process elements such as carbon, nitrogen, 
-	strontium, yttrium, and zirconium. This is proof of concept that under 
-	certain models for the time-dependence of radial migration, the migration 
-	of nucleosynthetic yields proceeding alongside stellar migration is a 
-	statistically significant effect. We therefore recommend future studies 
-	relax the assumption that stars do not contribute to nucleosynthesis 
-	beyond their birth radius.
-
-	\item We find that our models naturally reproduce the variations in the 
-	observed metallicity distribution functions (MDFs) with Galactocentric 
-	radius in the disc midplane ($\left|z\right|\leq$~0.5 kpc). At low 
-	$R_\text{gal}$, the mode abundance in both [O/H] and [Fe/H] is high, and 
-	conversely low at high~$R_\text{gal}$, with skewness in qualitative 
-	agreement with the observations (\citealp[e.g.][]{Hayden2015}; see Fig. 
-	\ref{fig:mdf_3panel_fe} and Fig.~\ref{fig:mdf_3panel_o} and the associated 
-	discussion in~\S~\ref{sec:mdfs:oh_feh}). In some sense, 
-	however, this is more a consequence of our building a realistic abundance 
-	gradient into our models than a prediction on its own. In the observations, 
-	the mode abundance in the midplane at $R_\text{gal}$ = 3 - 5 kpc is 
-	strikingly similar to that at 5 - 7 kpc. Our models fail to reproduce this, 
-	though it may be tied to a cessation of star formation in the inner 
-	galaxy, as suggestted by~\citet{Peek2009} and~\citet{Fraternali2012}. Off 
-	the midplane, our models predict a slight shift of the MDFs at small 
-	$R_\text{gal}$ to lower metallicity, where in the observations, those for 
-	all radii converge at [Fe/H]~$\approx$~[O/H]~$\approx$~-0.5.
-
-	\item We find that none of our models predict a Milky Way-like dichotomy 
-	in [$\alpha$/Fe], as observed by many studies. The principle failure is 
-	that the frequency of intermediate [$\alpha$/Fe] stars is overpredicted 
-	relative to the observations (\citealp{Hayden2015}; Vincenzo et al. 2021, 
-	in prep). This suggests that inside-out galaxy grouth combined with 
-	radial migration, even if a recent starburst is included 
-	\citep[e.g.][]{Mor2019, Isern2019}, is not adequate to explain the 
-	observed dichotomy. This is at odds with the findings of 
-	\citet{Sharma2020}, though we believe our study to have a more physically 
-	motivated treatment of the chemical evolution models (see discussion in 
-	\S~\ref{sec:mdfs:ofe}). The over-prediction of intermediate [$\alpha$/Fe] 
-	stars in general suggests that shutting off star formation for the 
-	intermediate-$\alpha$ phase would mitigate the problems suffered by our 
-	models; we therefore postulate that a two-infall model may be necessary 
-	to explain the observed dichotomy~\citep[e.g.][]{Chiappini1997, 
-	Chiappini2001, Romano2010, Grisoni2017, Noguchi2018, Spitoni2016, 
-	Spitoni2018, Spitoni2019, Spitoni2020}. Alternatively, we 
-	speculate that the issues may be mitigated by an effective SN Ia yield of 
-	Fe which depends inversely on metallicity, based on the findings of 
-	\citet{Brown2019}.
-
-	\item We found that our recipe for setting the gradients in both stellar 
-	surface density and metallicity yields the correct result. This is an 
-	indication that radial migration does not change the profile of these 
-	observed trends, only inducing scatter. 
-	\begin{itemize} 
-		\item We found that slightly different predictions in the stellar 
-		and gas-phase metallicity gradient are natural consequences of 
-		variations in the SFH.
-
-		\item We found that different models for the SFH predicted different 
-		[O/Fe] gradients at the present day.
-
-		\item See Fig.~\ref{fig:metallicity_gradient} and the associated 
-		disccusion in~\S~\ref{sec:metallicity_gradient} for the metallicity 
-		gradient; Fig.~\ref{fig:surface_density} and discussion in 
-		\S~\ref{sec:methods:surface_density_gradient} for the surface 
-		density gradient. 
-	\end{itemize}
-
-	\item We found that the observationally motivated approach to modeling the 
-	efficiency of star formation ($\tau_\star \equiv \Sigma_\text{gas} / 
-	\dot{\Sigma}_\star$) adopted in our simulations in general overpredicts 
-	the molecular fractions by mass of the model Galaxy. The discrepancy arose 
-	out of an underabundance of HI/HII rather than an overabundance of H$_2$ 
-	in the global demographics predicted by our simulation. Nonetheless, we 
-	demonstrate in Appendix~\ref{sec:sfe_variations} that relaxing these 
-	assumptions do not impact our model predictions. We also discuss a handful 
-	of potential sources of the discrepancy there.
-
-	\item We found that the time-dependence of radial migration indeed does 
-	have an impact on enrichment. Previous studies in the literature have 
-	assumed that this is not the case, due to the slow nature of migration 
-	\citep[e.g.][]{Minchev2013}. However, we find that even for young stars, 
-	the tails of the present-day $R_\text{gal}$ distribution are adequately 
-	long that when age-dependent migration is taken into account, the model 
-	predicts variations in the SN Ia rate that then impact predicted abundance 
-	ratios. We demonstrated that this is a means with which stellar migration 
-	may produce young, Fe-poor stars which can migrate to the solar annulus, 
-	and potentially be misinterpreted as young, $\alpha$-rich stars. This is 
-	proof of concept that the radial migration of nucleosynthetic yields can 
-	proceed alongside the radial migration of stars, depending on which model 
-	for migration that you believe. 
-	\begin{itemize} 
-		\item These stars have been seen in observed data from APOGEE 
-		\citep[e.g.][]{SilvaAguirre2018}. They postulate that since these stars 
-		have kinematics similar to the rest of the high-$\alpha$ population, 
-		that perhaps they are the consequence of stellar mergers or mass 
-		transfer events, producing truly old stars that simply appear to be 
-		younger. While these interpretations are not mutually exclusive, an 
-		observational test to ascertain the origins of the observed young 
-		$\alpha$-rich population would have implications for which of the 
-		models for radial migration investigated here are the most realistic. 
-	\end{itemize}
-
-	\item In the observations, the high-$\alpha$ sequence is known to be most 
-	prominent at low~$R_\text{gal}$ and high~$\left|z\right|$, and conversely, 
-	the low-$\alpha$ population at high~$R_\text{gal}$ and low~$\left|z\right|$ 
-	\citep[e.g.][]{Hayden2015}.  We found that this is a natural consequence of 
-	stellar migration, though the detailed distributions depend on the SFH and 
-	the relative yields of $\alpha$ and iron-peak elements, both of which are 
-	highly uncertain, and we do not model them in detail here.
-
-	\item We found that our inside-out model predicts an age-[$\alpha$/Fe] 
-	relation which is in good agreement with the observed relation reported 
-	by~\citet{Feuillet2019}. Our recent starburst models predict a global 
-	$\alpha$-enhancement that simply isn't seen in the data. This suggests 
-	that our current understanding of chemical evolution may be at odds with 
-	the findings of~\citet{Mor2019} and~\citet{Isern2019} suggesting a recent 
-	factor of~$\sim$2 enhancement in the Milky Way SFH peaking~$\sim$2 Gyr ago.
-
-	\item We find that where our recent starburst models fail to agree with 
-	the age-[O/Fe] relation reported by~\citet{Feuillet2019}, it tends to 
-	overpredict ages at a given [O/Fe]. However, it tends to fail in a manner 
-	such that the~\citet{Feuillet2019} relation agrees with the stars that we 
-	would call Fe-poor - that is, the stars that are $\alpha$-enhanced due to 
-	forming out of an Fe-poor ISM due to the same variations in the SN Ia rate 
-	that can produce young, $\alpha$-rich stars. While this may be coincidence, 
-	if we take the observations at face value, it would suggest that our model 
-	is overpredicting the rate of Fe injection, and that perhaps SN Ia yields 
-	of Fe should be lower. If we take the model at face value, it suggests that 
-	APOGEE+Gaia targets preferentially sample young, $\alpha$-rich stars 
-	(\citealp{Feuillet2019} used APOGEE data for stars with Gaia parallaxes).
-
-	\item We found that the age-metallicity relation (AMR) in both [O/H] and 
-	[Fe/H] reported by~\citet{Feuillet2019} is better fit by our late 
-	starburst models. This is at odds with the findings regarding the 
-	age-[O/Fe] relation, where the inside-out model agreed with the data much 
-	better than the starburst models. This is interesting, because different 
-	observables are favoring different models for the SFH, suggesting that 
-	something more complicated is going on. 
-	\begin{itemize} 
-		\item The starburst models agreeing with the observed AMR has to do 
-		with dilution as well as the starburst itself. It's possible that the 
-		Milky Way experienced a dilution event that was primarily HI/HII gas 
-		that has not yet cooled to be available for star formation. This could 
-		mitigate the discrepancy. It would, however, be at odds with the 
-		observed results of~\citet{Mor2019} and~\citet{Isern2019} suggesting 
-		such a recent enhancement in star formation.
-
-		\item Off the midplane, our model-predicted AMR overestimates ages 
-		relative to~\citet{Feuillet2019}, just like in the age-[O/Fe] relation. 
-		We speculate that this may be related to the Sagitarrius dwarf 
-		galaxy; it's important to remember that our model galaxy does not have 
-		the Milky Way's dynamical history, but~\texttt{h277}'s dynamical 
-		history. {\color{red} Jon and I are looking into this, but as I 
-		understand it, what I've written next is in general true.}~\texttt{h277} 
-		did not have a Sagitarrius-like accretion event. Since Sagitarrius 
-		has made multiple pericentric passages nearly head-on with the Milky 
-		Way disc, it's possible that young stars were kinematically heated to 
-		high~$\left|z\right|$, an effect that would not be present in 
-		\texttt{h277} without such an event. This would decrease our model 
-		predicted median ages at these heights by directly adding more young 
-		stars, and potentially not having noticeable effect in the midplane due 
-		to the much larger number of stars there. 
+	stellar migration on enrichment in the Galaxy. Though there have been a 
+	number of studies to date with a similar treatment of the Galaxy 
+	\citep[e.g.][]{Matteucci1989, Schoenrich2009, Nidever2014, Sharma2020}, 
+	ours and the~\citet{Minchev2013, Minchev2014, Minchev2017} model are the 
+	only which make use of hydrodynamical simulation to describe radial mixing, 
+	for which we take the~\texttt{h277} zoom-in simulation. This yields a model 
+	for migration which does not have any free parameters (see discussion in 
+	\S~\ref{sec:methods:h277}).
+
+	\item Our model assumes nucleosynthetic yields and a SN Ia DTD based on a 
+	combination of theoretical and empirical constrants. The main free 
+	parameters are the star formation law ($\tau_\star(R_\text{gal}, T)$, see 
+	\S~\ref{sec:methods:sfe}), the mass-loading factor~$\eta(R_\text{gal})$ 
+	(assumed to be time-independent, see~\S~\ref{sec:methods:yields}), and the 
+	SFH. The first we choose from the observed 
+	$\dot{\Sigma}_\star-\Sigma_\text{g}$ relation in local spirals. The second 
+	is chosen to match the metallicity gradient. The fiducial model then has an 
+	inside-out SFH calibrated to the~\citet{Sanchez2020} data. We also consider 
+	models with a late starburst, motivated by~\citet{Mor2019} and 
+	\citet{Isern2019}, and a constant-SFH model with a theoretical motivation.
+
+	\item Our model predicts masses and abundances for simple stellar 
+	populations, a given number of which form in a given annulus and timestep. 
+	From the hydrodynamical simulation, each stellar population finds a star 
+	particle from~\texttt{h277} to act as its~\textit{analog}, assigned such 
+	that it the star particle was born at a similar Galactocentric radius and 
+	time. The stellar population in our chemical evolution model then assumes 
+	the change in radius~$\Delta R_\text{gal}$ and final height above/below the 
+	disc midplane~$\left|z\right|$ of its analog at face value.
+
+	\item We demonstrate that the dependence of the number of high- and 
+	low-$\alpha$ sequence stars on Galactic region is at least in part a 
+	natural consequence of radial migration. In our models, low [Fe/H], high 
+	[$\alpha$/Fe] stars are located at low~$R_\text{gal}$ and high 
+	$\left|z\right|$; conversely, the high [Fe/H], low [$\alpha$/Fe] stars are 
+	preferentially found at high~$R_\text{gal}$ and low~$\left|z\right|$. We 
+	clarify that this is not an explanation for the~\textit{origin} of the 
+	two sequences - only the positional dependence thereof.
+
+	\item We find that migration-induced fluctuations in the SN Ia rate are a 
+	significant effect. The characteristic delay time of a SN Ia rate is of 
+	order 1 Gyr~\citep{Maoz2012, Maoz2017}, while stars are migrating a 
+	significant distance in the radial direction on similar timescales in our 
+	models. The result is a SN Ia rate which, at fixed radius, tends to follow 
+	what is expected in a one-zone model with the same SFH, but shows 
+	significant variability on~$\sim$Gyr timescales. Our model also predicts 
+	this variability to grow with increasing radius due to sampling noise 
+	having a greater impact where the stellar number density is low. 
+	\begin{itemize} 
+		\item We demonstrate that this is a mechanism with which truly young, 
+		high [$\alpha$/Fe] stars can be formed. In a region of time and space 
+		where the SN Ia rate is lower than expected from the SFH, the ISM will 
+		become Fe-poor, increasing the gas-phase [$\alpha$/Fe] ratio on 
+		timescales comparable to the local gas depletion time. Stars 
+		then form in this region of the ISM, encoding this composition in their 
+		atmospheres, and then migrate to the solar annulus, where they're seen 
+		in observations as young, super-solar [$\alpha$/Fe] stars. While 
+		there's an observational argument that at least some fraction of these 
+		stars are mass transfer events~\citep[e.g.][]{SilvaAguirre2018, 
+		Hekker2019}, our model suggests that some fraction of the remaining 
+		stars are truly young, not~$\alpha$-enhanced but Fe-poor stars.
+
+		\item In general, our results are broadly consistent with 
+		\citet{Kubryk2013} and~\citet{Khoperskov2021}, who argue that radial 
+		migration has a negligible impact on the [$\alpha$/Fe]-[Fe/H] 
+		distribution over time. While we find significant deviations in the 
+		gas-phase tracks between the post-processing and diffusion migration 
+		models, the differences in the stellar distributions are not 
+		significantly sensitive to this. We argue that radial migration plays a 
+		role in establishing scatter in the age-metallicity and 
+		age-[$\alpha$/Fe] relations, but not in the population-averaged 
+		trends. 
+	\end{itemize}
+
+	\item While our procedure for building in a radial metallicity gradient 
+	ensured that the stellar abundances as a function of~$R_\text{gal}$ match 
+	observations, we find that the model-predicted stellar [O/Fe] gradient as 
+	well as the gas-phase [O/H] and [Fe/H] gradients are sensitive to the 
+	that assumption about the SFH. The differences are most noticeable in where 
+	there are offsets between the gas and the stellar gradients, and in the 
+	case of the [O/Fe] gradient, its shape in the inner Galaxy.
+
+	\item We find that our model adequately reproduces the differences in MDFs 
+	in bins of~$R_\text{gal}$ in the disc. While there is potential for 
+	improvement in the~$R_\text{gal}$ = 3 - 5 kpc bin, the model nonetheless 
+	performs well. With increasing~$\left|z\right|$, however, the prediction 
+	breaks down somewhat. Where the observational data show a convergence of 
+	the MDFs at all radii to a skew-positive distribution with mode 
+	[O/H]~$\approx$~mode [Fe/H]~$\approx$~-0.5, our model predicts the mode of 
+	the distributions at small~$R_\text{gal}$ to decrease slightly, but not as 
+	much as the observations, while those at large~$R_\text{gal}$ remain 
+	largely unchanged. While there is an effect of the right sign, our models 
+	cannot explain this entirely.
+
+	\item Our model successfully reproduces the broad nature of the [O/Fe] 
+	distributions at fixed [Fe/H] in bins of~$R_\text{gal}$ and 
+	$\left|z\right|$ as observed in APOGEE~\citep{Hayden2015}. The 
+	position of the mode of the distribution is generally well-reproduced as 
+	well, the exception being at small~$R_\text{gal}$ and high~$\left|z\right|$; 
+	this is, however, the region of the Galaxy with the fewest number of stars 
+	in APOGEE. The principle shortcoming of our model in comparison to the 
+	observed data is an overpredicted frequency of intermediate [O/Fe] stars. 
+	While the model predicts broad [O/Fe] distributions, and in some bins in 
+	[Fe/H] and Galactic regions may show a convincing two-peak profile, it 
+	does not reproduce the observations in detail. {\color{red} Remark on the 
+	discrepancy with~\citet{Sharma2020} closer to the end of the conclusion, 
+	after going through results as they appear in the text.}
+
+	\item We find that the age-[O/Fe] as reported by~\citet{Feuillet2019} is 
+	well-fit by our fiducial inside-out SFH model. In the case of our recent 
+	starburst models, the global nature of the burst implies an overall 
+	increase in the bulk population-averaged [O/Fe] of young stars which 
+	simply isn't seen in the data. The inside-out SFH model, on the other hand, 
+	predicts a monotonically declining age-[O/Fe] relation as observed.
+
+	\item {\color{red} Potentially something on the~$R_\text{gal}$ and 
+	$\left|z\right|$-dependencies of the age-[$\alpha$/Fe] relation, and/or 
+	the larger scatter with increasing~$R_\text{gal}$, the latter pending a 
+	comparison to the post-processing migration model. Regardless, the 
+	increased scatter might be worth highlighting here; Jennifer tells me that 
+	they're still trying to make sense of Jack Warfield's results, and higher 
+	scatter in age-[O/Fe] with increasing~$R_\text{gal}$ can explain a lot. }
+
+	\item We find that the AMR (both age-[O/H] and age-[Fe/H]) in the solar 
+	annulus is well-described by our fiducial, inside-out SFH model. However, 
+	when the comparison is extended to a wider range of Galactocentric radii, 
+	there are a number of noticeable shortcomings. Specifically, the model 
+	over-predicts the ages of [Fe/H]~$\approx$-0.5 - -0.2 stars at 
+	$R_\text{gal}$ = 5 - 7 kpc, and fails to reproduce the observed trend at 
+	nearly all radii. Where it originally failed to accurately describe the 
+	observed age-[$\alpha$/Fe] relation, our late-burst SFH model improves 
+	significantly on these failures of the inside-out model; both the 
+	over-predicted ages of sub-solar [Fe/H] stars at 5 - 7 kpc and the 
+	population-averaged trends favor the late-burst model over the inside-out 
+	model.
+
+	\item Discussion of late-burst vs. inside-out 
+	\begin{itemize} 
+		\item The late-burst model, motivated by observationally inferred 
+		recent SFH of the Galaxy, has little impact on MDFs and the overall 
+		[O/Fe]-[Fe/H] structure, but impacts the age-[O/Fe] and age-[Fe/H] 
+		relations significantly. While it worsens the agreement with the 
+		observed age-[O/Fe] relation considerably, it improves it with the 
+		age-[Fe/H] also rather strikingly. {\color{red} In general, I would 
+		assert based on this that since different observables favor different 
+		models for the recent SFH of the Galaxy, that likely means there's 
+		some piece of physics that our model isn't capturing. That'd be worth 
+		highlighting in the conclusion, because finding where to go look to 
+		potentially find new physics is always exciting. } 
+	\end{itemize}
+
+	\item Discussion of [$\alpha$/Fe] dichotomy 
+	\begin{itemize} 
+		\item The [O/Fe] distributions predicted by our models are less bimodal 
+		than in the observations, and this is true for all of our models. 
+		Radial mixing does produce broad [O/Fe] distributions at fixed [Fe/H] 
+		in bins of~$R_\text{gal}$ and~$\left|z\right|$, but with the accretion 
+		and SF histories adopted here, there are too many intermediate 
+		[$\alpha$/Fe] stars to describe the data in detail. Specifically, our 
+		models fail in such a manner that a two-infall model
+		\citep[e.g.][]{Chiappini1997, Chiappini2001, Romano2010, Grisoni2017, 
+		Noguchi2018, Spitoni2016, Spitoni2018, Spitoni2019, Spitoni2020, 
+		Spitoni2021} may significantly improve the agreement. Alternative forms 
+		of the SFH which do predict a Milky Way-like [$\alpha$/Fe] bimodality 
+		is of particular interest for future work.
+
+		\item These findings are at odds with~\citet{Sharma2020}, who claim to 
+		reproduce the dichotomy using only an inside-out SFH and radial 
+		migration. In their model, the evolution of the gas-phase [Fe/H] and 
+		[O/Fe] are parameterized a priori by assumed parameterized functions 
+		of~$R_\text{gal}$ and~$T$ which are selected to agree with the 
+		observations. This means that the enrichment and star formation 
+		histories of their models are not necessarily internally consistent. 
+		In~\texttt{VICE}, the enrichment history is determined from the star 
+		formation history via assumptions about the yields and delay-time 
+		distributions of nucleosynthetic channels, internally consistent by 
+		construction. We therefore contend that the models explored in this 
+		paper are the more self-consistent of the two. {\color{red} To be 
+		completely honest here, I have no scope for what would be considered 
+		too harsh for a paper - my first time in this position. Obviously, the 
+		last thing I want to do is anger the~\citet{Sharma2020} authors, but 
+		this is my honest critique of their paper. } 
 	\end{itemize}
@@
 
-\newpage 
-\section{Variations in Star Formation Efficiency} 
-\label{sec:sfe_variations} 
-{\color{red} It'd be good to present a comparison of our fiducial, inside-out 
-SFH model to a case where we make a significantly different assumption about 
-$\tau_\star$, and demonstrate that it doesn't impact the conclusions. This 
-could motivate some of the discussion below as well, so that this Appendix can 
-still tell a generally interesting story beyond just a comparison. }
-
-\begin{itemize} 
-	\item {\color{red} Here are some of my thoughts on what could be 
-	causing the discrepancy with this $\tau_\star$ business. Since 
-	this is for discussion purposes, I haven't looked in detail at any 
-	of this; I'm simply speculating for the sake of discussion in the 
-	text. }
-
-	\item As discussed in~\S~\ref{sec:methods:sfe}, our fiducial inside-out 
-	SFH overpredicts the molecular fraction~$f_\text{mol}$ relative to 
-	observed results in the Milky Way. This is a result of both an 
-	underpredicted HI + HII mass and an overpredicted H$_2$ mass. The 
-	predicted HI + HII mass is~$5.54\times10^9$~M$_\odot$ relative to an 
-	observed value of~$\sim10^{10}$~M$_\odot$~\citep{Kalberla2009}. The 
-	predicted H$_2$ mass is~$7.14\times10^9$~M$_\odot$, compared to an 
-	observed values of~$2.5\times10^9$~M$_\odot$ from~\citet{Kalberla2009} and 
-	$1\times10^9$~M$_\odot$ from~\citet{Heyer2015}. Here we discuss potential 
-	sources of this discrepancy, and demonstrate that the assumed form of the 
-	star formation law does not impact our conclusions.
-
-	\item First, the overpredicted H$_2$ mass. Our fiducial inside-out model, 
-	whose SFH is normalized to predict the same total stellar mass as that 
-	reported by~\citet{Licquia2015} with the surface density gradient of 
-	\citet{Bland-Hawthorn2016} (see discussion in~\S~\ref{sec:methods:sfhs} 
-	and~\ref{sec:methods:surface_density_gradient}). This model predicts a 
-	present-day SFR of 4.89 M$_\odot$~yr$^{-1}$, an overprediction relative to 
-	the observed value of 1.65 M$_\odot$~yr$^{-1}$~\citep{Licquia2015}. 
-	However, our model predicts a gradient in the present-day surface density 
-	of star formation with radius which decreases monotonically (see the top 
-	row, left-center panel of Fig.~\ref{fig:evol}), whereas the observations 
-	of \citet{Peek2009} and~\citet{Fraternali2012} would suggest that the 
-	Milky Way has begun the process of inside-out quenching. Fig. 2 of 
-	\citet{Fraternali2012} suggests that the surface density of star 
-	formation is significantly lower within~$R_\text{gal} \lesssim$ 4 kpc. 
-	Cutting off our summation of the H$_2$ mass and present-day SFR at 
-	4 kpc yields a present-day star formation rate of 3.06 M$_\odot$ 
-	yr$^{-1}$, and an H$_2$ mass of~$4.48\times10^9$~M$_\odot$, still an 
-	overprediction relative to~\citet{Licquia2015} and 
-	\citet{Kalberla2009}. Instead cutting the summation off at 6 kpc 
-	yields $\dot{M}_\star$ = 1.97 M$_\odot$~yr$^{-1}$ and H$_2$ = 
-	$2.88\times10^9$~M$_\odot$, still a slight overprediction, but in 
-	better agreement still. Based on these calculations, we argue that the 
-	overpredicted H$_2$ mass in our fiducial inside-out model is a consequence 
-	of an overpredicted SFR at the present day. A model with either a more 
-	steeply declining SFH or quenching of star formation in the inner Galaxy 
-	as suggested by~\citet{Peek2009} and~\citet{Fraternali2012} should resolve 
-	this discrepancy.
-
-	\item Next, the under-predicted HI + HII mass. We speculate over a couple 
-	possible explanations of this. 
-	\begin{itemize} 
-		\item At first glance, this could point to a breakdown in the 
-		fundamental assumption of our adopted model for star formation 
-		efficiency. As discussed in~\S~\ref{sec:methods:sfe}, we adopte the 
-		assumption that our model Galaxy follows the observed trend in the 
-		mean~$\dot{\Sigma}_\star-\Sigma_\text{gas}$ relation, even though 
-		there is evidence that individual galaxies do not follow such a 
-		relation~\citep{Ellison2020b}.~\citet{Kennicutt2020} however argue 
-		that such a prescription should still be a valid recipe in galaxy 
-		evolution models.
-
-		\item An important caveat in understanding our ISM masses is that 
-		because we treat the ISM as being available for star formation in its 
-		entirety, they therefore track only the amount of gas in the 
-		\textit{star forming reservoir}. Zero metallicity gas infall simply 
-		appears in each annulus to balance the amount of gas lost to star 
-		formation and outflows at each timestep in order to sustain the 
-		level of star formation at the next timestep. Based on our model, if 
-		gas is removed from the star forming reservoir, but remains in a 
-		spatially confined region reasonably defining the Galaxy, our model 
-		will treat it it as an outflow and remove it from the ISM, though in 
-		nature it would still show up in observations and be counted as part 
-		of the Milky Way's gas content. {\color{red} It's therefore plausible 
-		that the difference could simply be nuanced semantics regarding what 
-		we refer to as an outflow numerically and what would be considered an 
-		outflow in an observational study (i.e. ejection from the disc).} 
-		\begin{itemize} 
-			\item Based on this argument, one potential source of the 
-			difference could be infall from the circum- and inter-galactic 
-			media that have not yet been made available for star formation. 
-			This would show up as HI and HII observed in the ISM, but would 
-			not be counted in our models if it is not yet incorporated into 
-			the star forming reservoir.
-
-			\item Another potential source could be star formation efficiency 
-			in the meaning that the ISM/feedback literature often takes: the 
-			fraction of molecular cloud masses that are converted into stars. 
-			To first order, this value is a few percent with some intrinsic 
-			scatter ({\color{red} citation}). This means that in our models, 
-			a significant multiplier ($\sim$30) of the stellar mass formed in 
-			a given timestep should be added to the hot phase of the ISM in 
-			the form of HII through feedback processes. If this gas is never 
-			again made available for star formation, our model would treat it 
-			as an outflow, removing it from the ISM mass, while in nature it 
-			is still observed within the reasonably confined region defining 
-			the Galaxy.
-
-			\item Together, these effects may constitute the remaining factor 
-			of~$\sim$ of warm and hot gas that our fiducial model is missing. 
-			However, an investigation of the impact of a multi-phase ISM on 
-			models such as these is outside the scope of this paper. 
-		\end{itemize} 
-	\end{itemize}
-
-	\item Whatever the source of this discrepancy may be, the decision 
-	about the mathematical form of~$\tau_\star$ does not significantly 
-	impact our conclusions, as demonstrated in the remainder of this Appendix. 
-\end{itemize}
-
 \end{appendices}
@@
 \bibliographystyle{mnras} 
-\bibliography{outline2}
+\bibliography{outline3}
 

### 2021-08-04 chemev/MWbimodality/paper/plots/age_metallicity.py

@@ -1,0 +1,242 @@
+
+import matplotlib.pyplot as plt 
+from matplotlib.ticker import FormatStrFormatter as fsf 
+import plots 
+plots.mpltoolkit.load_mpl_presets() 
+from astropy.io import fits 
+import numpy as np 
+import vice 
+import sys 
+
+OUTPUTSDIR = "/Users/astrobeard/Work/Research/VICErepos/VICE/migration/outputs" 
+STATIC = "%s/high-resolution/2Gyr/diffusion/static" % (OUTPUTSDIR)
+INSIDEOUT = "%s/high-resolution/2Gyr/diffusion/insideout" % (OUTPUTSDIR) 
+LATEBURST = "%s/high-resolution/2Gyr/diffusion/lateburst" % (OUTPUTSDIR) 
+OUTERBURST = "%s/high-resolution/2Gyr/diffusion/outerburst" % (OUTPUTSDIR)
+# INSIDEOUT = "../../simulations/paper_noburst" 
+# LATEBURST = "../../simulations/paper_withburst" 
+STEM = "age_metallicity" 
+CMAP = "winter" 
+ZONE_WIDTH = 0.1 
+ZONE_MIN = int(7 / ZONE_WIDTH) 
+ZONE_MAX = int((9 - ZONE_WIDTH) / ZONE_WIDTH) 
+LOGAGE = True 
+
+
+def setup_axes(): 
+	fig = plt.figure(figsize = (20, 10)) 
+	axes = 2 * [None] 
+	for i in range(len(axes)): 
+		axes[i] = 4 * [None] 
+		for j in range(len(axes[i])): 
+			axes[i][j] = fig.add_subplot(241 + 4 * i + j, facecolor = "white") 
+			if i != 1: plt.setp(axes[i][j].get_xticklabels(), visible = False) 
+			if j != 0: plt.setp(axes[i][j].get_yticklabels(), visible = False) 
+			if LOGAGE: 
+				axes[i][j].set_xscale("log") 
+				axes[i][j].set_xlim([0.2, 18]) 
+				axes[i][j].xaxis.set_major_formatter(fsf("%g")) 
+			else: 
+				axes[i][j].set_xlim([-1, 14]) 
+			if i: 
+				axes[i][j].set_ylim([-1.1, 0.7]) 
+				axes[i][j].yaxis.set_ticks([-1. + 0.2 * i for i in range(9)]) 
+			else: 
+				axes[i][j].set_ylim([-0.9, 0.7]) 
[…]

### 2021-08-04 chemev/MWbimodality/paper/plots/young_alpha_rich.py

@@ -1,0 +1,225 @@
+
+import matplotlib.pyplot as plt 
+from matplotlib import colors, cm 
+import plots 
+plots.mpltoolkit.load_mpl_presets() 
+from astropy.io import fits 
+import numpy as np 
+import math as m 
+import vice 
+from vice.yields.presets import JW20 
+vice.yields.sneia.settings['fe'] *= 10**0.1 
+import sys 
+sys.path.append("/Users/astrobeard/Work/Research/VICErepos/VICE/migration") 
+import src 
+
+OUTPUTSDIR = "/Users/astrobeard/Work/Research/VICErepos/VICE/migration/outputs" 
+FULL = "%s/high-resolution/2Gyr/diffusion/insideout" % (OUTPUTSDIR) 
+SIMPLE = "%s/high-resolution/2Gyr/post-process/insideout" % (OUTPUTSDIR) 
+STEM = "yar_insideout_highres" 
+# FULL = "../../simulations/paper_noburst" 
+# SIMPLE = "../../simulations/paper_noburst_simple"  
+ZONE_WIDTH = 0.1 
+CMAP = "jet" 
+ZONE_MIN = int(7 / ZONE_WIDTH) 
+ZONE_MAX = int((9 - ZONE_WIDTH) / ZONE_WIDTH) 
+
+# cm1 = colors.LinearSegmentedColormap.from_list("MyCmap", ["r", "b"]) 
+# cnorm = colors.Normalize(vmin = 0, vmax = 15) 
+# cpick = cm.ScalarMappable(norm = cnorm, cmap = cm1) 
+# cpick.set_array([]) 
+
+
+
+def setup_axes(): 
+	fig = plt.figure(figsize = (15, 6)) 
+	axes = 3 * [None] 
+	for i in range(3): 
+		axes[i] = fig.add_subplot(131 + i, facecolor = "white") 
+	plt.subplots_adjust(top = 0.8, bottom = 0.16, right = 0.98, left = 0.09) 
+	pos0 = axes[0].get_position() 
+	pos1 = axes[1].get_position() 
+	pos1.x1 -= pos1.x0 - pos0.x1 
+	pos1.x0 = pos0.x1 
+	axes[1].set_position(pos1) 
+	axes[0].set_ylabel("[O/Fe]") 
+	axes[2].set_ylabel(r"$\propto\dot{N}_\text{Ia}$ [Gyr$^{-1}$]") 
+	axes[2].set_xlabel("Time [Gyr]") 
[…]

### 2021-09-17 chemev/MWbimodality/paper/response/response.tex
final paper updates

@@
 \par 
-Having strived for transparency, we are glad that Dr. Mackereth believes that 
-we achieved this goal and that it improves the quality of the paper! 
-Although novel predictions are always interesting, we believe that one of the 
-most important results from this paper is that some observables can be 
-explained by ongoing star formation combined with stellar migration, but that 
-simultaneously fitting all of them is extremely challenging. 
-None of the models we present are able to achieve this goal despite how well 
-one model may agree with a particular observable. 
-Largely because we find that different observables from the same dataset favor 
-different models, an important lesson to learn from this paper is that we as a 
-community need to be careful to compare our models to as many observables in as 
-many Galactic regions as possible. 
-This was our motivation behind emphasizing the comparison with data.
+We are pleased that the referee appreciates the clarity and transparency of
+the paper. 
+The comment that we focus on comparison to existing data rather than 
+predictions for future data is a fair one. 
+There are several reasons for this focus: 
+(a) many of the observational constraints we compare to are relatively recent 
+results from APOGEE, and no previous models have been compared to them 
+systematically as a set; 
+(b) our modeling framework still involves multiple parameters/choices, most 
+notably the smooth vs. bursty star formation history, and many predictions 
+depend on those choices; 
+(c) as stated in the paper, within the range of parameters we have 
+investigated, some of the existing observations remain difficult to fit, 
+especially the bimodality of [alpha/Fe]. 
+\par 
+We have added sentences after the numbered list of conclusions in Section 4 
+to say that the predictive power of the models can be extended by including 
+elements with large AGB contributions, since these have different timescales 
+and metallicity dependent yields. 
+These sentences are a prospect rather than an actual prediction, but they are 
+a direction we are pursuing, limited mainly by the fact that we don't consider 
+yield predictions reliable enough to be taken at face value without empirical 
+calibration. 
+\par 
+Our other main changes to the paper, discussed further below, are 
+the addition of a table of model parameters, greater clarity on the 
+choice of analogues for migration calculations, and further explanation 
+of the SNIa rate fluctuations as a potential explanation for young 
+alpha-rich stars. 
+% Having strived for transparency, we are glad that Dr. Mackereth believes that 
+% we achieved this goal and that it improves the quality of the paper! 
+% Although novel predictions are always interesting, we believe that one of the 
+% most important results from this paper is that some observables can be 
+% explained by ongoing star formation combined with stellar migration, but that 
+% simultaneously fitting all of them is extremely challenging. 
+% None of the models we present are able to achieve this goal despite how well 
+% one model may agree with a particular observable. 
+% Largely because we find that different observables from the same dataset favor 
+% different models, an important lesson to learn from this paper is that we as a 
+% community need to be careful to compare our models to as many observables in as 
+% many Galactic regions as possible. 
+% This was our motivation behind emphasizing the comparison with data.
 
@@
 We have added a few sentences to this effect to paragraph 4 of~\S~2.2 so 
-that uninitiated readers can be assured that our models assign outer rather 
-than inner disc star particles to these outer disc stellar populations. 
+that readers can be assured that our models assign outer rather than inner 
+disc star particles to these outer disc stellar populations. 
+The fact that there are occasionally analogue separations of 2 or more kpc is 
+the reason why we assign final particle radii as~$R_\text{final} = 
+R_\text{initial} + \Delta R_\text{analogue}$ as opposed 
+to~$R_\text{final} = R_\text{final,analogue}$. 
 \par 
@@
 the search too far inward. 
-A change to our model such that stars stay at their birth radius if they do not 
-find an analogue within~$R~\pm$~500 pc and~$T~\pm$~500 Myr makes similar 
-predictions (see previous). 
-Particularly at large~$R$, this is a substantial change to the dynamics of the 
-stellar populations such that the search may as well have not even been 
-conducted for some of them, and our conclusions are still unaffected. 
+Even if we make a large change to our model such that stars stay at their 
+birth radius if they do not find an analogue within~$R~\pm$~500 pc 
+and~$T~\pm$~500 Myr, our conclusions are still unaffected. 
 We hope that the aforementioned addition of text to paragraph 4 of~\S~2.2 
@@
 instead occurs~$\sim$7.5 - 8 Gyr ago. 
+As discussed in the text, our choice of~$\tau_\text{sfh}(R)$ is motivated by 
+observed radial age gradients of disc galaxies comparable to the Milky Way. 
 Whether or not this is accurate for the Milky Way, it at least to some extent 
@@
 \par 
-This is an excellent point! 
+This is an excellent point. 
 We have added a reference to the metallicity map published in Bovy et al. 
@@
 For this reason, we are skeptical that changing the surface density profile 
-would significantly impact the MDFs, but we have not ran models with different 
+would significantly impact the MDFs, but we have not run models with different 
 choices for the surface density gradient, so we cannot say for certain. 
@@
 \par 
-We thank Dr. Mackereth for pointing out that this is confusing. 
+We have expanded and clarified the text on this point. 
 It is true that at some annuli radial migration is efficient and mixes stars 
@@
 \par 
-We thank Dr. Mackereth for letting us know that this explanation is confusing. 
 In general, the inside-out model overpredicts ages for solar and sub-solar 
@@
 of the AMR as observed by Feuillet et al. (2019). 
-Although there appears to be a difference in normalization at large~$R$ in the 
-late-burst model, this could be due to a number of minor details: a 
-mis-calibration of our yields or the mass-loading factor, slight differences in 
-the time-dependence of the burst as a function of radius, etc. 
 We have revised our discussion in~\S~3.5 to address this. 
-Perhaps this difference is shown more clearly in the age-[O/H] relation, which 
-is unaffected by SN Ia enrichment; this is shown in Fig. 18.
+Perhaps the difference is visualized more clearly in the age-[O/H] relation, 
+which is unaffected by SN Ia enrichment; this is shown in Fig. 18.
 
@@
 \par 
-We thank Dr. Mackereth for pointing this out! 
-We have updated the draft to cite his 2018 paper.
+We have updated the draft to cite the 2018 paper.
 
@@
 \par 
-We thank Dr. Mackereth for catching these editing mistakes!
+Good catch - fixed.
 

### 2021-09-17 chemev/MWbimodality/paper/draft3/comparison_observations.tex
final paper updates

@@
 
-% fig 9 
-\begin{figure*} 
-\centering 
-\includegraphics[scale = 0.32]{metallicity_gradient.pdf} 
-\caption{Radial abundance gradients in [O/H] (top, red), [Fe/H] (top, blue), 
-and [O/Fe] (bottom) for our four SFHs with diffusion migration - constant (far 
-left), inside-out (left-middle), late-burst (right-middle), and outer-burst 
-(far right). We plot the gas-phase abundance at the present day as a function 
-of Galactocentric radius in solid lines. Points denote the median of the stellar 
-MDF of the 100-pc width ring at a given radius, with shaded regions marking 
-the 16th and 84th percentiles thereof. Black lines in the top panels denote our 
-target [$\alpha$/H] gradient of mode([$\alpha$/H]) = +0.3 at~$R_\text{gal}$~= 
-4 kpc with a slope of -0.08 kpc$^{-1}$. } 
-\label{fig:metallicity_gradient} 
-\end{figure*}
-
 We begin the comparison of our model predictions to observational data with the 
@@
 \label{sec:obs_comp:gradient}
+
+% fig 9 
+\begin{figure*} 
+\centering 
+\includegraphics[scale = 0.32]{metallicity_gradient.pdf} 
+\caption{Radial abundance gradients in [O/H] (top, red), [Fe/H] (top, blue), 
+and [O/Fe] (bottom) for our four SFHs with diffusion migration - constant (far 
+left), inside-out (left-middle), late-burst (right-middle), and outer-burst 
+(far right). We plot the gas-phase abundance at the present day as a function 
+of Galactocentric radius in solid lines. Points denote the median of the stellar 
+MDF of the 100-pc width ring at a given radius, with shaded regions marking 
+the 16th and 84th percentiles thereof. Black lines in the top panels denote our 
+target [$\alpha$/H] gradient of mode([$\alpha$/H]) = +0.3 at~$R_\text{gal}$~= 
+4 kpc with a slope of -0.08 kpc$^{-1}$. } 
+\label{fig:metallicity_gradient} 
+\end{figure*}
 
@@
 {\color{red} 
-It's also possible that the differences at 3 - 5 kpc are due to stars 
+It is also possible that the differences at 3 - 5 kpc are due to stars 
 associated with the Milky Way's strong bar, which~\citet{Bovy2019} demonstrate 
@@
 fluctuates upward in the ISM. 
-In a starburst event, the ISM becomes~$\alpha$-enhanced because the CCSN rate 
+An alternative explanation for young~$\alpha$-rich stars is a burst of 
+star formation, when the ISM becomes~$\alpha$-enhanced because the CCSN rate 
 increases~\citep{Johnson2020}. 
@@
 }
-\par 
+\par\null\par 
 The presence of young and intermediate-age~$\alpha$-enhanced stars in APOGEE 
@@
 {\color{red} 
-We clarify that this result does not refute the previously suggested mass 
-transfer origin; this mechanism explains the truly young, 
-intrinsically~$\alpha$-enhanced stars which appear to make up a portion of the 
+Our model does not refute mass transfer as an origin for some massive, 
+$\alpha$-rich stars, but it can explain the truly young, intrinsically 
+$\alpha$-enhanced stars which appear to make up a portion of the 
 young~$\alpha$-rich population separate from those which formed via mass 
@@
 to~$\sim$solar, with multiple peaks indicative of separate sub-populations. 
-Although small sample sizes have prevented the detailed analaysis of 
-the [Fe/H] distribution of the young~$\alpha$-rich population, this 
-qualitatively agrees with the findings of~\citet{SilvaAguirre2018} (see their 
-Figs. 8 and 10) and~\citet{Miglio2021} (see their Fig. 5). 
-However, a direct comparison to data is not free of nuance, because the 
-young~$\alpha$-rich stars which formed via mass transfer likely outnumber those 
-which are intrinsically young~\citep{Miglio2021}. 
-} 
-\par 
+This large spread qualitatively agrees with the findings 
+of~\citet{SilvaAguirre2018} (see their Figs. 8 and 10) and~\citet{Miglio2021} 
+(see their Fig. 5). 
+A direct comparison to data is not free of nuance, because the 
+young~$\alpha$-rich stars which formed via mass transfer may outnumber 
+those which are intrinsically young~\citep{Miglio2021}. 
+}
+
+% fig 15 
+\begin{figure} 
+\centering 
+\includegraphics[scale = 0.35]{amr_static_o.pdf} 
+\caption{The age-[O/H] relation predicted by our constant SFR model for 
+$R_\text{gal}$~= 7 - 9 kpc (left) and 11 - 13 kpc (right). Each panel plots 
+only the~$\left|z\right|\leq$~0.5 kpc population. The colored points in the 
+background and the black squares with error bars are as in Fig. 
+\ref{fig:age_alpha}, but with the model prediction quantified in bins 
+of~$\Delta$[O/H] = 0.05. } 
+\label{fig:age_oh_static} 
+\end{figure}
+
 The right panels of Fig.~\ref{fig:age_alpha} compare the model predictions of 
@@
 
-% fig 15 
-\begin{figure} 
-\centering 
-\includegraphics[scale = 0.35]{amr_static_o.pdf} 
-\caption{The age-[O/H] relation predicted by our constant SFR model for 
-$R_\text{gal}$~= 7 - 9 kpc (left) and 11 - 13 kpc (right). Each panel plots 
-only the~$\left|z\right|\leq$~0.5 kpc population. The colored points in the 
-background and the black squares with error bars are as in Fig. 
-\ref{fig:age_alpha}, but with the model prediction quantified in bins 
-of~$\Delta$[O/H] = 0.05. } 
-\label{fig:age_oh_static} 
-\end{figure}
-
 % fig 16 
@@
 \centering 
-\includegraphics[scale = 0.44]{amr_solar_annulus.pdf} 
+\includegraphics[scale = 0.45]{amr_solar_annulus.pdf} 
 \caption{The age-[O/H] (top) and age-[Fe/H] (bottom) relations for the solar 
@@
 reasons as in age-[Fe/H], but perhaps more clearly when comparing bin-by-bin. 
-Although none of these models reproduce the data perfectly, the detailed form 
-of the AMR in our models is sensitive to the nature of the recent starburst or 
-lackthereof, and its true form was likely more complicated than our 
-parameterization. 
+% Although none of these models reproduce the data perfectly, the detailed form 
+% of the AMR in our models is sensitive to the nature of the recent starburst or 
+% lackthereof, and its true form was likely more complicated than our 
+% parameterization. 
 } 

### 2021-09-17 chemev/MWbimodality/paper/draft3/conclusions.tex
final paper updates

@@
 Milky Way disc's abundance structure as a significant success of the models. 
-However, at least within the framework explored here, it appears that models 
-with smooth star formation are not able to explain the pronounced bimodality 
-of the observed~\afe~distribution. As discussed by~\citet{Vincenzo2021a}, 
-we expect that this problem is generic: a one-zone model with a smooth SFH 
-produces an~\afe~distribution that peaks at low values, so it is difficult 
-to create a superposition of such models that has a bimodal distribution. 
+{\color{red} 
+In future work, we will extend the models' predictive power by including 
+elements that have large contributions from AGB star enrichment, which occurs 
+on a timescale different from CCSN or SN Ia and often has strongly 
+metallicity dependent yields~\citep[e.g.][]{Cristallo2011, Cristallo2015}. 
+These properties should help break degeneracies between radial migration and 
+star formation history, and they might enable distinction between a reduced 
+SN Ia rate versus an enhanced CCSN rate as an explanation for 
+young~$\alpha$-rich stars. 
+Model prediction for these AGB elements can be tested against data from 
+APOGEE (e.g. C, N, and Ce) and GALAH\footnote{
+	GALAH = GALactic Archaeology with HERMES 
+	(survey overview:~\citealp{Martell2017}; 
+	recent data release:~\citealp{Buder2021}) 
+} (e.g. Y and Ba), though uncertainties in yields present a significant 
+complication.
+} 
 \par 
+At least within the framework explored here, it appears that models 
+with radial migration and smooth star formation are not able to explain the 
+pronounced bimodality of the observed~\afe~distribution. 
+As discussed by~\citet{Vincenzo2021a}, we expect that this problem is generic: 
+a one-zone model with a smooth SFH produces an~\afe~distribution that peaks at 
+low values, so it is difficult to create a superposition of such models that 
+has a bimodal distribution. 
 The most widely explored solution to this problem involves a two-phase SFH, 

### 2021-09-17 chemev/MWbimodality/paper/draft3/methods.tex
final paper updates

@@
 $\Delta \rgal$ of its analogue, and moves from its birth radius to the 
-implied final radius at~$T$ = 13.2 Gyr with an assumed time dependence (see 
-below). 
+implied final radius and~$z$ at~$T$ = 13.2 Gyr with an assumed time dependence 
+(see below). 
 If no candidate analogues are found,~\vice~widens the search to~$T \pm$~500 Myr 
@@
 sampled on a table of stellar initial mass and metallicity from the FRUITY 
-database \citep{Cristallo2011}. 
+database~\citep{Cristallo2011, Cristallo2015}. 
 However, the AGB star yields of O and Fe are tiny compared to their 
@@
 	peak at lookback times of~$\sim$7 - 8 Gyr, qualitatively consistent with 
-	the radial growth of the Galaxy~\citep[e.g.][]{Bird2012, Bird2013}. 
+	the radial growth of disc galaxies~\citep{Bird2013, Bird2021, Frankel2019}. 
 	} 
@@
 the onset of star formation occurring later in the outer disc to better capture 
-the radial growth of the Galaxy~\citep[e.g.][]{Bird2012, Bird2013}, can be 
+the radial growth of the Galaxy~\citep[e.g.][]{Frankel2019}, can be 
 explored easily using~\vice, but we do not explore such models here. 
@@
 $z$ & \ref{sec:methods:migration} & Present day distance to Galactic midplane; 
-adopted from~\hsim~analogue star particle & $-3 - +3$ kpc 
+adopted from~\hsim~analogue star particle & [$-3$, 3] kpc 
 \\ 
@@
 not significantly altered the overall form of the gradient, as we assumed in 
-Appendix~\ref{sec:normalize_sfh}; we find this to also be true for our sample 
-of star particles from~\hsim. 
+Appendix~\ref{sec:normalize_sfh}. 
+We find this to also be true for our sample of star particles from~\hsim, 
+a result which is expected given the roughly symmetric shapes of the 
+histograms in the top row of Fig.~\ref{fig:h277_decomposition} and consistent 
+with previous arguments that radial migration does not significantly alter the 
+vertical and radial structure of the disc~\citep[e.g.][]{Sellwood2014, 
+VeraCiro2014}. 
 }

### 2021-09-17 chemev/MWbimodality/paper/draft3/vice.tex
final paper updates

@@
 for Linux. 
-It requires~\texttt{python >=}~3.6 and can be installed in a terminal via 
-\texttt{pip install vice}, after which~\texttt{vice -{}-docs} will launch a web 
-browser to the documentation at \url{https://vice-astro.readthedocs.io}. 
+The latest version (1.2.1) requires~\texttt{python >=}~3.6 and can be 
+installed in a terminal via~\texttt{pip install vice}, after 
+which~\texttt{vice -{}-docs} will launch a web browser to the documentation 
+at~\url{https://vice-astro.readthedocs.io}. 
 \texttt{vice -{}-tutorial} will also 

### 2021-10-01 chemev/MWbimodality/paper/draft3/acknowledgements.tex
final paper updates
paper updates

--- 2021-08-04 chemev/MWbimodality/paper/draft2/acknowledgements.tex
@@
 
+% {\color{red} 
+We are grateful to the referee, Ted Mackereth, for valuable comments which 
+helped improve this manuscript. 
+% } 
 We acknowledge valuable discussion with Jennifer Johnson, Adam Leroy, Grace 

### 2021-10-01 chemev/MWbimodality/paper/draft3/methods.tex
paper updates

@@
 first place. 
-{\color{red} 
+% {\color{red} 
 A summary of our chemical evolution model parameters can be found in 
 Table~\ref{tab:params}. 
-}
+% }
 
@@
 radii and the final midplane distance. 
-{\color{red}\textit{
+% {\color{red}
+\textit{
 	We emphasize that these are the only quantities from~\hsim~which we make 
@@
 	nucleosynthetic yields, outflow prescriptions, etc.
-}}
+}
+% }
 \hsim~did not record the exact birth radius of each star particle; however, 
@@
 \textit{analogue}. 
-This stellar population then adopts the {\color{red} present day midplane 
-distance~$z$ and the} change in orbital radius 
+This stellar population then adopts the %{\color{red} 
+present day midplane 
+distance~$z$ and the
+%} 
+change in orbital radius 
 $\Delta \rgal$ of its analogue, and moves from its birth radius to the 
@@
 Myr, and assigns it as the analogue. 
-{\color{red} 
+% {\color{red} 
 Because we remove bulge, pseudobulge, and halo star particles from our sample 
@@
 have similar but not identical abundances. 
-}
+% }
 \par 
@@
 with significantly different birth radii, this is only an issue for small~$T$ 
-and large~$\rgal$ where {\color{red} only a small fraction of~\hsim's star 
-particles reside,} 
+and large~$\rgal$ where %{\color{red} 
+only a small fraction of~\hsim's star 
+particles reside,
+% } 
 % there are few star particles from~\hsim, 
@@
 galaxies~\citep[e.g.][]{Bird2013}. 
-{\color{red} 
+% {\color{red} 
 In practice, we find that our sample of star particles is sufficiently large 
@@
 particles. 
-}
+% }
 Furthermore, due to the similarity of the histograms in the top row of 
@@
 these instances to be accurate enough for our purposes. 
-{\color{red}
+% {\color{red}
 In exploratory work for this paper, we also considered a migration model in 
@@
 history. 
-}
+% }
 % When an~\hsim~star particle is assigned as an analogue, it is~\textit{not} 
@@
 not significantly alter the form of~$g(\rgal)$. 
-{\color{red} 
+% {\color{red} 
 We find this to be true for our sample of~\hsim~star particles, and we 
@@
 adopted form of~$g(\rgal)$. 
-}
+% }
 % We demonstrate that this assumption holds 
@@
 	Gyr, roughly corresponding to a redsfhit of~$z \approx$ 2.5. 
-	{\color{red} 
+	% {\color{red} 
 	In detail, however, the time of peak star formation increases 
@@
 	the radial growth of disc galaxies~\citep{Bird2013, Bird2021, Frankel2019}. 
-	} 
+	% } 
 	% We discuss the choice of~$\tau_\text{sfh}$ below.
@@
 recent data. 
-{\color{red} 
+% {\color{red} 
 More complex scenarios, such as multiple bursts induced by repeated satellite 
@@
 explored easily using~\vice, but we do not explore such models here. 
-} 
+% } 
 % More complex scenarios with multiple bursts induced by repeated satellite 
@@
 modestly from its 2 Gyr peak in the inside-out model. 
-{\color{red} 
+% {\color{red} 
 The gas supply, whose value at all timesteps is known via the star formation 
@@
 illustrated in the bottom row of Fig.~\ref{fig:evol}. 
-}
+% }
 % At all timesteps, the gas supply is known via the star formation efficiency 
@@
 % stellar surface density gradient~$g(\rgal)$. 
-{\color{red} 
+% {\color{red} 
 As discussed in~\S~\ref{sec:methods:sfhs}, Appendix~\ref{sec:normalize_sfh} 
@@
 surface density gradient~$g(\rgal)$. 
-}
+% }
 In setting the normalization, our model ensures that the integral of~$g(\rgal)$ 
@@
 \ref{eq:gradient}) denoted by the solid black line. 
-{\color{red} 
+% {\color{red} 
 Simply introducing scatter around the adopted trend, stellar migration has 
@@
 VeraCiro2014}. 
-}
+% }
 % Stellar migration has not altered the overall form of the gradient, simply 
@@
 
-{\color{red} 
+% {\color{red} 
 Table~\ref{tab:params} presents a breakdown of our model parameters, their 
 values, and references to the sections where relevant discussion can be found. 
-}
+% }
 In summary, our fiducial model has an inside-out SFH with e-folding timescales 
